### 2017-02-21 multiclass_classification_with_kernel_embeddings.tex
Legacy work

\documentclass[a4paper, 12pt]{article}
\usepackage{geometry}
\geometry{
	a4paper,
	left=30mm,
	top=20mm,
}

\bibliographystyle{apalike}
\usepackage[square, authoryear, comma, sort&compress]{natbib}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathbbol}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{longtable}
\usepackage{tcolorbox}
\usepackage[colorlinks = true, linkcolor = black, urlcolor  = cyan, citecolor = black, anchorcolor = black]{hyperref}
\usepackage{listings}
\usepackage{wrapfig}
\usepackage{cleveref}
\usepackage{vector}

\lstdefinelanguage{Python}{
	keywords={typeof, null, catch, switch, in, int, str, float, self},
	keywordstyle=\color{ForestGreen}\bfseries,
	ndkeywords={boolean, throw, import},
	ndkeywords={return, class, if ,elif, endif, while, do, else, True, False , catch, def},
	ndkeywordstyle=\color{BrickRed}\bfseries,
	identifierstyle=\color{black},
	sensitive=false,
	comment=[l]{\#},
	morecomment=[s]{/*}{*/},
	commentstyle=\color{purple}\ttfamily,
	stringstyle=\color{red}\ttfamily,
}

\newcommand{\argmax}{\operatornamewithlimits{argmax}}

\title{Multiclass Classification with Kernel Embeddings}

\author{Kelvin Hsu}

\date{\today}

\setlength{\parskip}{1em}

\begin{document}
\maketitle

\section{Motivation}

	Most classification algorithms are binary classifiers, which can only handle the case where the output can only take instances from one of two classes. This is true for both SVM classifiers and GP classifiers. Part of the reason for that is that it works by learning a continuous latent function which basically represents the `strength' of one of the classes, and so it is really just inferring how likely an input is from class A and if not it would be from class B. To build a multiclass classifier, a simple approach is to train multiple binary classifiers to tell apart pairs of classes or sets of classes, and somehow fuse these results together. Notable examples are One Versus All (OVA) and All Versus All (AVA) approaches, as well as binary tree approaches.

	\href{http://www.vision.caltech.edu/malaa/publications/aly05multiclass.pdf}{Here} is a 2005 Survey which summarises the state-of-the-art in multiclass classification at the time, which supports what I just said above. It does not seem like the above scenario has fundamentally changed in the past 10+ years, although more sophisticated versions of what was described above has been proposed and tested.

\section{Idea}

	The idea I am proposing here is actually very simple and intuitive. Suppose the training data is $\{\bvec{x}_{i}, y_{i}\}_{i = 1}^{n}$ where $\bvec{x}_{i} \in \mathcal{X}, y_{i} \in \mathbb{N}_{m}$ for all $i \in \mathbb{N}_{n}$ with $\mathbb{N}_{m} := \{1, 2, \cdots, m\}$. To clarify, $n$ is the number of training points, $m$ is the number of classes involved, and $\mathcal{X}$ is usually a subset of some euclidean space $\mathbb{R}^{d}$ but it does not necessarily have to be so (which is an advantage in kernel methods in general, such as GPs). The idea is to use the kernel embedding framework to compute a conditional embedding empirically from those training points. We then show that class probabilities can be computed from the conditional embedding if we place a Kronecker delta kernel on the space of the outputs, $\mathbb{N}_{m}$. We show that these class probabilities estimates are consistent estimates of the true class probabilities. Furthermore, the corresponding Shannon information entropy estimate at each query input can be computed, in two different ways, and we explore the performance of each of these approaches. In this way, we propose a natural probabilistic classifier for multiclass classification.

	Computationally, this probabilistic classifier is to do the following. Given a set of training points $\{\bvec{x}_{i}, y_{i}\}_{i = 1}^{n}$ and a set of query inputs $\{\bvec{x}^{\star}_{i}\}_{i = 1}^{n^{\star}}$, our classifier can output $\hat{P}^{\star} = \{\hat{\bvec{p}}^{\star}_{i}\}_{i = 1}^{n^{\star}}$, the estimated class probabilities at the query points, and also $\bvec{h}^{\star} = \{\hat{h}^{\star}_{i}\}_{i = 1}^{n^{\star}}$, the estimated information entropy at the query points.

\section{Methodology}

	To construct a conditional embedding corresponding to the distribution $\mathbb{P}_{Y | X}$ where $X : \Omega \to \mathcal{X}$ and $Y: \Omega \to \mathcal{Y}$ are measurable random variables, a kernel $k$ for the input space $\mathcal{X}$ and another kernel $l$ for the output space $\mathcal{Y}$ is chosen. They each describe how similarity is measured within each of the respective spaces.

	The empirical conditional embedding (I need to cite this) is then given by

	\begin{equation}
		\hat{\mu}_{Y | X} = \Psi (K + \lambda I)^{-1} \Phi^{T},
	\end{equation}

	where $K := \{k(\bvec{x}_{i}, \bvec{x}_{j})\}_{i = 1, j = 1}^{n, n}$, $\Phi := \begin{bmatrix} k(\bvec{x}_{1}, \cdot) & k(\bvec{x}_{2}, \cdot) & \dots & k(\bvec{x}_{n}, \cdot) \end{bmatrix}$, $\Psi := \begin{bmatrix} l(y_{1}, \cdot) & l(y_{2}, \cdot) & \dots & l(y_{n}, \cdot) \end{bmatrix}$, and $\lambda$ is the regularisation parameter to make sure $C_{X X}$ covers the right range (I will check on the exact technical wording of this but this is not important in the discussion here).

	In our context, the output is finite and discrete, taking values only in $\mathcal{Y} = \mathbb{N}_{m}$. Naturally, we choose the Kronecker delta kernel $\delta : \mathbb{N}_{m} \times \mathbb{N}_{m} \to \{0, 1\}$ for the output space, where inputs that are the same has unit similarity and outputs that are different have no similarity. That is, for all $y_{i}, y_{j} \in \mathcal{Y}$,

	\begin{equation}
		\delta(y_{i}, y_{j}) = \begin{cases}
			1 & \mathrm{if } \quad y_{i} = y_{j} \\
			0 & \mathrm{otherwise}.
		\end{cases}
	\end{equation}

	One can easily check that this is a positive definite kernel and is characteristic.

	Notice that this kernel has no hyperparameters to tune or learn, so that the hyperparameters only come from the kernel of the input space and the regularisation parameter $\lambda$.

	Let the reproducing kernel Hilbert space (RKHS) defined by the Kronecker delta kernel be denoted as $\mathcal{H}_{\delta}$.

	Recall that the RKHS of a kernel is the closure of the span of the kernel feature basis as follows (from \href{http://www.jmlr.org/papers/volume10/xu09a/xu09a.pdf}{here})

	\begin{equation}
		\mathcal{H}_{l} = \overline{\mathrm{span}\{l(y, \cdot) : y \in \mathcal{Y}\}}
	\end{equation}

	For $\mathcal{Y} = \mathbb{N}_{m}$, this means that any real-valued function $g$ whose domain is $\mathbb{N}_{m}$ is in the RKHS of $\delta$.

	In particular, indicator functions on $\mathbb{N}_{m}$ are in the RKHS, since

	\begin{equation}
		\mathbb{1}_{c}(y) = \begin{cases}
			1 & \mathrm{if } \quad y = c \\
			0 & \mathrm{otherwise}.
		\end{cases} = \delta(c, y).
	\end{equation}

	That is, indicator functions $\mathbb{1}_{c} = \delta(c, \cdot)$ for all $c \in \mathbb{N}_{m}$ are simply the canonical kernel features of the RKHS.

	We know that the expectation of a function in the RKHS can be written as the inner product of the conditional embedding and the function. When the true conditional embedding is not available, the expectation can be approximated by the inner product of the empirical conditional embedding and the function (I need to cite this, and look up the convergence rate). That is,

	\begin{equation}
		\mathbb{E}[g(Y) | \bvec{X} = \bvec{x}^{\star}] = \langle \mu_{Y | \bvec{X} = \bvec{x}^{\star}}, g \rangle \approx \langle \hat{\mu}_{Y | \bvec{X} = \bvec{x}^{\star}}, g \rangle.
	\end{equation}

	for all $g \in \mathcal{H}_{l}$.

	So, for our case of $\mathcal{H}_{\delta}$ being the RKHS corresponding to the output space, since $\mathbb{1}_{c} \in \mathcal{H}_{\delta}$, we have

	\begin{equation}
		p^{\star}_{c} := \mathbb{P}[Y = c | \bvec{X} = \bvec{x}^{\star}] = \mathbb{E}[\mathbb{1}_{c}(Y) | \bvec{X} = \bvec{x}^{\star}] = \langle \mu_{Y | \bvec{X} = \bvec{x}^{\star}}, \mathbb{1}_{c}  \rangle \approx \langle \hat{\mu}_{Y | \bvec{X} = \bvec{x}^{\star}}, \mathbb{1}_{c}  \rangle.
	\end{equation}

	Note that all quantities are conditioned on the training set and thus is dropped from the notation. This is in turn equal to the following,

	\begin{equation}
		\begin{aligned}
			& \langle \hat{\mu}_{Y | X = x}, \mathbb{1}_{c}  \rangle \\
			= & \mathbb{1}_{c}^{T} \Psi (K + \lambda I)^{-1} \Phi^{T} k(\bvec{x}^{\star}, \cdot) \\
			= & \mathbb{1}_{c}^{T} \begin{bmatrix} l(y_{1}, \cdot) & l(y_{2}, \cdot) & \dots & l(y_{n}, \cdot) \end{bmatrix} (K + \lambda I)^{-1} \begin{bmatrix} k(\bvec{x}_{1}, \cdot)^{T} \\ k(\bvec{x}_{2}, \cdot)^{T} \\ \vdots \\ k(\bvec{x}_{n}, \cdot)^{T} \end{bmatrix} k(\bvec{x}^{\star}, \cdot) \\
			= & \begin{bmatrix} \mathbb{1}_{c}^{T}l(y_{1}, \cdot) & \mathbb{1}_{c}^{T}l(y_{2}, \cdot) & \dots & \mathbb{1}_{c}^{T}l(y_{n}, \cdot) \end{bmatrix} (K + \lambda I)^{-1} \begin{bmatrix} k(\bvec{x}_{1}, \cdot)^{T} k(\bvec{x}^{\star}, \cdot) \\ k(\bvec{x}_{2}, \cdot)^{T} k(\bvec{x}^{\star}, \cdot)\\ \vdots \\ k(\bvec{x}^{\star}_{n}, \cdot)^{T} k(\bvec{x}^{\star}, \cdot) \end{bmatrix} \\
			= & \begin{bmatrix} \mathbb{1}_{c}(y_{1}) & \mathbb{1}_{c}(y_{2}) & \dots & \mathbb{1}_{c}(y_{n}) \end{bmatrix} (K + \lambda I)^{-1} \begin{bmatrix} k(\bvec{x}_{1}, \bvec{x}^{\star}) \\ k(\bvec{x}_{2}, \bvec{x}^{\star}) \\ \vdots \\ k(\bvec{x}_{n}, \bvec{x}^{\star}) \end{bmatrix} \\
			= & \bvec{1}_{c}^{T} (K + \lambda I)^{-1} \bvec{k}_{\bvec{x}^{\star}},
		\end{aligned}
	\end{equation}

	where $\bvec{1}_{c} := \{\mathbb{1}_{c}(y_{i})\}_{i = 1}^{n}$ and $\bvec{k}_{\bvec{x}^{\star}} := \{k(\bvec{x}_{i}, \bvec{x}^{\star})\}_{i = 1}^{n}$.

	Hence, our main result is

	\begin{equation}
		\hat{p}^{\star}_{c} = \bvec{1}_{c}^{T} (K + \lambda I)^{-1} \bvec{k}_{\bvec{x}^{\star}}.
	\label{eq:probabilities}
	\end{equation}

	Computationally, this can also be vectorised over multiple classes as

	\begin{equation}
		\hat{\bvec{p}}^{\star} = B^{T} (K + \lambda I)^{-1} \bvec{k}_{\bvec{x}^{\star}} \in \mathbb{R}^{m},
	\end{equation}

	where $B = \begin{bmatrix} \bvec{1}_{1} & \bvec{1}_{2} & \cdots & \bvec{1}_{m} \end{bmatrix} \in \{0, 1\}^{n \times m}$. I choose $B$ as the notation to stand for binary, since the matrix can only take on values of $0$s and $1$s.

	It can further be vectorised over multiple query points $\{\bvec{x}^{\star}_{i}\}_{i = 1}^{n^{\star}}$ as usual through

	\begin{equation}
		\hat{P}^{\star} = B^{T} (K + \lambda I)^{-1} K^{\star} \in \mathbb{R}^{m},
	\end{equation}

	where $K^{\star} = \{k(\bvec{x}_{i}, \bvec{x}_{j}^{\star})\}_{i = 1, j = 1}^{n, n^{\star}}$.

	Of course, this is only an estimate, which will converge to the true probabilities as $n$ increases due to the convergence properties of kernel embeddings (cite this). As such, it does not necessarily sum up to one, nor does it necessarily have to be within the range $[0, 1]$, although it will be very close to it.

	For prediction, this is not a problem, as for each query point $\bvec{x}^{\star}$ we simply taken the class that has the highest estimated probability to be the prediction. That is, at the query point $\bvec{x}^{\star}$ the prediction is

	\begin{equation}
		\hat{y}^{\star} = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}^{\star}.
	\end{equation}

	If proper probabilities are required for interpretation, visualisation, or other purposes, the probabilities can be clip normalised as follows,

	\begin{equation}
		\tilde{p}^{\star}_{c} := \frac{\max\{\hat{p}^{\star}_{c}, 0\}}{\sum_{j = 1}^{m} \max\{\hat{p}^{\star}_{j}, 0\}}.
	\end{equation}

	Experiments verify the fact that clip normalisation does not alter the probabilities by that much, merely making sure they are valid probabilities by slight scaling.

	\subsection{Entropy}

		The information entropy of our predictions can also be computed. This is ideal for detecting the decision boundaries of the classifier and quantifying how uncertain the prediction is.

		There are two ways the information entropy can be approximated or computed. The first way is straight forward, which involves simply computing the information entropy with the clip normalised probabilities, at each query point,

		\begin{equation}
			\tilde{h}^{\star} := - \sum_{c = 1}^{m} \tilde{p}^{\star}_{c} \log{\tilde{p}^{\star}_{c}}.
		\end{equation}

		The second and more principled way is to also express the entropy as an inner product of an RKHS function with the conditional embedding.

		The entropy of the prediction at an output is

		\begin{equation}
			\begin{aligned}
				\mathbb{H}[Y | \bvec{X} = \bvec{x}^{\star}] &= - \sum_{c = 1}^{m} \mathbb{P}[Y = c| \bvec{X} = \bvec{x}^{\star}] \log{\mathbb{P}[Y = c | \bvec{X} = \bvec{x}^{\star}]} \\
				&= \mathbb{E}[- \log{\mathbb{P}[Y | \bvec{X} = \bvec{x}^{\star}]} | \bvec{X} = \bvec{x}^{\star}] \\
				&= \mathbb{E}[g(Y) | \bvec{X} = \bvec{x}^{\star}],
			\end{aligned}
		\end{equation}

		where

		\begin{equation}
			g(y) := - \log{\mathbb{P}[Y = y | \bvec{X} = \bvec{x}^{\star}]}.
		\end{equation}

		If $g$ is in the RKHS $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by the inner product of the empirical conditional embedding and the function.

		Now we can write $g$ in the following manner

		\begin{equation}
			g(y) = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | \bvec{X} = \bvec{x}^{\star}]} \delta(c, y).
		\end{equation}

		This shows that $g$ is in the span of the kernel feature and is thus in the RKHS.

		Hence, similar to the case with the prediction probabilities, we can write

		\begin{equation}
			\mathbb{H}[Y | \bvec{X} = \bvec{x}^{\star}] = \langle \mu_{Y | \bvec{X} = \bvec{x}^{\star}}, g \rangle \approx \langle \hat{\mu}_{Y | \bvec{X} = \bvec{x}^{\star}}, g \rangle.
		\end{equation}

		Similar to before the approximation can be written as

		\begin{equation}
			\langle \hat{\mu}_{Y | \bvec{X} = \bvec{x}^{\star}}, g \rangle = \bvec{g}^{T} (K + \lambda I)^{-1} \bvec{k}_{\bvec{x}^{\star}},
		\end{equation}

		where $\bvec{g} := \{g(y_{i})\}_{i = 1}^{n}$.

		Unfortunately, $g$ is not known exactly, since $\mathbb{P}[Y = c | \bvec{X} = \bvec{x}^{\star}]$ is not known exactly. Instead, we consider the approximation $\hat{g}$ of this function $g$ using \eqref{eq:probabilities},

		\begin{equation}
			\hat{g}(y) := - \log{\hat{p}^{\star}_{y}} U(\hat{p}^{\star}_{y}),
		\end{equation}

		where $U$ is the heaviside function to avoid contributions from negative values.

		We then approximate the entropy with

		\begin{equation}
			\mathbb{H}[Y | \bvec{X} = \bvec{x}^{\star}] \approx \langle \hat{\mu}_{Y | \bvec{X} = \bvec{x}^{\star}}, \hat{g} \rangle = \hat{\bvec{g}}^{T} (K + \lambda I)^{-1} \bvec{k}_{\bvec{x}^{\star}},
		\end{equation}

		where $\hat{\bvec{g}} := \{\hat{g}(y_{i})\}_{i = 1}^{n}$.

		Again, the information entropy here can be negative, as an artefact of the approximation. We then show that this converges to the actual entropy as $n$ increases (need to do this).

\section{Discussion}

	TALK ABOUT HYPERPARAMETER LEARNING

	TALK ABOUT USING BAYESIAN LEARNING OF HYPERPARAMETERS FOR THE INPUT SPACE AND WHY IT STILL MAY NOT BE IDEAL

	\subsection{Results}

		The results below is obtained through training under a 10-fold cross validation scheme. The kernel used is Gaussian with a sensitivity and a length scale parameter. The regularisation parameter was also trained. Hence, a total of three hyperparameters are used in the model and all of them are trained.

		\begin{figure}[!htbp]
			\centering
			\includegraphics[width=0.8\linewidth]{figures/10cv/figure1.eps}
			\caption{Kernel Embedding Classifier Results: 10-fold cross validation}
			\label{fig:figure_1}
		\end{figure}

		\begin{figure}[!htbp]
			\centering
			\includegraphics[width=0.8\linewidth]{figures/10cv/figure2.eps}
			\caption{Kernel Embedding Classifier Results: 10-fold cross validation}
			\label{fig:figure_2}
		\end{figure}

		\begin{figure}[!htbp]
			\centering
			\includegraphics[width=0.8\linewidth]{figures/10cv/figure3.eps}
			\caption{Kernel Embedding Classifier Results: 10-fold cross validation}
			\label{fig:figure_3}
		\end{figure}

		\begin{figure}[!htbp]
			\centering
			\includegraphics[width=0.8\linewidth]{figures/10cv/figure4.eps}
			\caption{Kernel Embedding Classifier Results: 10-fold cross validation}
			\label{fig:figure_4}
		\end{figure}

		\newpage
		WHY CROSS-VAL IS NOT IDEAL

		Well, as you can see below, I used 5-fold cross validation and the results are vastly different. Not to mention if I kept it at 10-folds but split the folds differently I would also get slightly different results.

		The next step is to try to figure out how to train this classifier without cross validation, hopefully under a Bayesian learning scheme.

		\begin{figure}[!htbp]
			\centering
			\includegraphics[width=0.8\linewidth]{figures/5cv/figure_1.png}
			\caption{Kernel Embedding Classifier Results: 5-fold cross validation}
			\label{fig:5figure_1}
		\end{figure}

		\begin{figure}[!htbp]
			\centering
			\includegraphics[width=0.8\linewidth]{figures/5cv/figure_2.png}
			\caption{Kernel Embedding Classifier Results: 5-fold cross validation}
			\label{fig:5figure_2}
		\end{figure}

		\begin{figure}[!htbp]
			\centering
			\includegraphics[width=0.8\linewidth]{figures/5cv/figure_3.png}
			\caption{Kernel Embedding Classifier Results: 5-fold cross validation}
			\label{fig:5figure_3}
		\end{figure}

		\begin{figure}[!htbp]
			\centering
			\includegraphics[width=0.8\linewidth]{figures/5cv/figure_4.png}
			\caption{Kernel Embedding Classifier Results: 5-fold cross validation}
			\label{fig:5figure_4}
		\end{figure}

	\newpage
	\subsection{Comparisons}

		On the other hand, this is what support vector machines spit out (using sklearn).

		Empirically, they are very similar, with similar performances (both 99.3\% accuracy so far).

		However, theoretically the kernel embedding classifier is much nicer. For support vector classifiers, the multi-class classifier is built from multiple binary classifiers, whereas the kernel embedding classifier works the same way no matter how many classes there are and handles it very naturally. For the support vector classifier, the probabilities are computed in a very roundabout way, unlike the kernel embedding formulation (check out the 2004 paper by Ting-Fan Wu for how those probabilities in SVMs are calculated). In some sense, both the probabilities and entropy from the SVM are a bit artificial, where as the kernel embedding classifier deals with probability distributions naturally.

		\begin{figure}[!htbp]
			\centering
			\includegraphics[width=0.8\linewidth]{figures/10cv/figure5.eps}
			\caption{Support Vector Classifier Results}
			\label{fig:figure_5}
		\end{figure}

		\begin{figure}[!htbp]
			\centering
			\includegraphics[width=0.8\linewidth]{figures/10cv/figure6.eps}
			\caption{Support Vector Classifier Results}
			\label{fig:figure_6}
		\end{figure}

		\begin{figure}[!htbp]
			\centering
			\includegraphics[width=0.8\linewidth]{figures/10cv/figure7.eps}
			\caption{Support Vector Classifier Results}
			\label{fig:figure_7}
		\end{figure}

%\bibliography{}

\end{document}

### 2017-04-15 kernel_embedding_classifier.tex
Update section titles, update section 5, 8, and 9

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
\PassOptionsToPackage{square, authoryear, comma, sort&compress}{natbib}
% before loading nips_2016
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2016}

\usepackage[final]{nips_2016}

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2016}

\usepackage[utf8x]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[colorlinks=true,linkcolor=green,citecolor=cyan]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

% My Packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathbbol}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{vector}
\usepackage{cleveref}
\usepackage[dvipsnames]{xcolor}

\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newcommand{\note}[1]{{\color{orange} #1}}
\newcommand{\edit}[1]{{\color{forestgreen} #1}}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}[theorem]
\newtheorem{claim}{Claim}[theorem]

\usepackage{algorithm}
\usepackage{algorithmic}

\title{Probabilistic Multiclass Kernel Embedding Classifier}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
  Kelvin Y.S. Hsu, Richard Nock, Fabio T. Ramos \\
  University of Sydney, Australia\\
  DATA61, CSIRO\\
  \texttt{\{Kelvin.Hsu, Richard.Nock, Fabio.Ramos\}@\{sydney.edu.au, data61.csiro.au\}} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}
\label{sec:introduction}

	- Currently, most classification algorithms are binary classifiers, which focuses on the case where the target label can only come from one of two classes.

	- Examples include ...

	- However, many applications require multiclass classifiers

	- Examples include ...

	- Most solve this by doing OVA, AVA, or decision trees on binary classifiers \citep{aly2005survey}

	- Furthermore, those probabilities are usually artificial, by passing through a link function that may or may not be valid, and in many cases like the GPC, is not analytically tractible and requires further approximations. No convergence gaurantees of convergence to the actual decision probabilities

	In this paper, we cast the multiclass classification problem into the kernel conditional embedding framework, where learning the classifier is done by learning a corresponding conditional embedding from data. We show that by placing a Kronecker delta kernel over the label space, decision probabilities can be expressed as inner products in the correspondingly induced reproducing kernel Hilbert space, which can be consistantly estimated from data using the conditional embedding framework. In this way, we propose a natural probabilistic classifier for multiclass classification.

	- Our contributions are ...

	\begin{itemize}
		\item A novel probabilistic multiclass classifier, the kernel embedding classifier (KEC), based on the theory and framework of kernel embedding of conditional distributions with convergence guarantees.
		\item A novel hyperparameter training algorithm based on gradient descent and, most importantly, stochastic gradient descent. Reducing the complexity of KEC training from $O(n^{3})$ to $O(n_{b}^{3})$ in time and from $O(n^{2})$ to $O(n_{b}^{2})$ for a training dataset of size $n$ and a batch size of $n_{b} << n$. 
		\item Two techniques to estimate the information entropy of a classification prediction with convergence guarantees
		\item Mode reconstruction of the inputs, where we compute the most representative example of each class
	\end{itemize}

%	Most classification algorithms are binary classifiers, which can only handle the case where the output can only take instances from one of two classes. This is true for both SVM classifiers and GP classifiers. Part of the reason for that is that it works by learning a continuous latent function which basically represents the `strength' of one of the classes, and so it is really just inferring how likely an input is from class A and if not it would be from class B. To build a multiclass classifier, a simple approach is to train multiple binary classifiers to tell apart pairs of classes or sets of classes, and somehow fuse these results together. Notable examples are One Versus All (OVA) and All Versus All (AVA) approaches, as well as binary tree approaches.
%	
%	\href{http://www.vision.caltech.edu/malaa/publications/aly05multiclass.pdf}{Here} is a 2005 Survey which summarises the state-of-the-art in multiclass classification at the time, which supports what I just said above. It does not seem like the above scenario has fundamentally changed in the past 10+ years, although more sophisticated versions of what was described above has been proposed and tested.
%	
%	The idea I am proposing here is actually very simple and intuitive. Suppose the training data is $\{\bvec{x}_{i}, y_{i}\}_{i = 1}^{n}$ where $\bvec{x}_{i} \in \mathcal{X}, y_{i} \in \mathbb{N}_{m}$ for all $i \in \mathbb{N}_{n}$ with $\mathbb{N}_{m} := \{1, 2, \cdots, m\}$. To clarify, $n$ is the number of training points, $m$ is the number of classes involved, and $\mathcal{X}$ is usually a subset of some euclidean space $\mathbb{R}^{d}$ but it does not necessarily have to be so (which is an advantage in kernel methods in general, such as GPs). The idea is to use the kernel embedding framework to compute a conditional embedding empirically from those training points. We then show that class probabilities can be computed from the conditional embedding if we place a Kronecker delta kernel on the space of the outputs, $\mathbb{N}_{m}$. We show that these class probabilities estimates are consistent estimates of the true class probabilities. Furthermore, the corresponding Shannon information entropy estimate at each query input can be computed, in two different ways, and we explore the performance of each of these approaches. In this way, we propose a natural probabilistic classifier for multiclass classification.
%	
%	Computationally, this probabilistic classifier is to do the following. Given a set of training points $\{\bvec{x}_{i}, y_{i}\}_{i = 1}^{n}$ and a set of query inputs $\{\bvec{x}^{\star}_{i}\}_{i = 1}^{n^{\star}}$, our classifier can output $\hat{P}^{\star} = \{\hat{\bvec{p}}^{\star}_{i}\}_{i = 1}^{n^{\star}}$, the estimated class probabilities at the query points, and also $\bvec{h}^{\star} = \{\hat{h}^{\star}_{i}\}_{i = 1}^{n^{\star}}$, the estimated information entropy at the query points.
%	\\
%	\\
%
%	In \cref{sec:kernel_embedding_classifier}, by expressing decision probabilities as expectations of indicator functions in the RKHS, we derived a consistent estimate of the decision probabilities from an inner product between the empirical conditional embedding and the indicator function. Likewise, in \cref{sec:information_entropy}, by expressing information entropy as expected information in the RKHS, we derived a consistent estimate of the information entropy from an inner product between the empirical conditional embedding and the information function.

\section{Hilbert Space Embeddings of Conditional Probability Distributions}
\label{sec:background}

	We begin by providing an overview of Hilbert space embeddings, where probability distributions are represented by mean embeddings in a reproducing kernel Hilbert space (RKHS) through positive definite kernels. Specifically, in the supervised learning context for which we are primarily interested in, we focus on conditional distributions and its representations in the RKHS.

	To construct a conditional embedding map $\mathcal{U}_{Y | X}$ corresponding to the distribution $\mathbb{P}_{Y | X}$ where $X : \Omega \to \mathcal{X}$ and $Y: \Omega \to \mathcal{Y}$ are measurable random variables, we choose a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ for the input space $\mathcal{X}$ and another kernel $l : \mathcal{Y} \times \mathcal{Y} \to \mathbb{R}$ for the output space $\mathcal{Y}$. These kernels $k$ and $l$ each describe how similarity is measured within each of their respective domains $\mathcal{X}$ and $\mathcal{Y}$, and are symmetric and positive definite such that they uniquely define the RKHS $\mathcal{H}_{k}$ and $\mathcal{H}_{l}$. Such a conditional embedding map is then defined by

	\begin{equation}
		\mathcal{U}_{Y | X} := C_{YX} C_{XX}^{-1},
	\label{eq:conditional_embedding}
	\end{equation}

	where $C_{YX} := \mathbb{E}[l(Y, \cdot) \otimes k(X, \cdot)]$ and $C_{XX} := \mathbb{E}[k(X, \cdot) \otimes k(X, \cdot)]$ \citep{song2009hilbert}. The conditional embedding map can be seen as an operator map from $\mathcal{H}_{k}$ to $\mathcal{H}_{l}$. In this sense, it sweeps out a family of conditional embeddings $\mu_{Y | X = x}$ in $\mathcal{H}_{l}$, each indexed by the input variable $x$, via the property $\mu_{Y | X = x} := \mathbb{E}[l(Y, \cdot) | X = x] = \mathcal{U}_{Y | X} k(x, \cdot)$.

	Under the assumption that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$, \cite{song2009hilbert} proved that the conditional expectation of a function $g \in \mathcal{H}_{l}$ can be expressed as an inner product,  % Theorem 4

	\begin{equation}
		\mathbb{E}[g(Y) | X = x] = \langle \mu_{Y | X = x}, g \rangle.
	\label{eq:conditional_expectation}
	\end{equation}

	While the assumptions that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$ and $k(x, \cdot) \in \mathrm{image}(C_{XX})$ holds for finite input domains $\mathcal{X}$ for characteristic kernels $k$, it is not necessarily true when $\mathcal{X}$ is a continuous domain \citep{fukumizu2004dimensionality}, which is the scenario for many classification problems. In this case, $C_{YX} C_{XX}^{-1}$ becomes only an approximation to $\mathcal{U}_{Y | X}$, and we instead regularise the inverse and use $C_{YX} (C_{XX} + \lambda I)^{-1}$, which also serves to avoid overfitting \citep[p. 13]{song2013kernel}.

	On top of this, in practice we do not have access to the distribution $\mathbb{P}_{X Y}$ to compute such expectations from the definitions of $C_{YX}$ and $C_{XX}$. Instead, we have a finite collection of data points $\{x_{i}, y_{i}\} \in \mathcal{X} \times \mathcal{Y}$, $i \in \mathbb{N}_{n} := \{1, \dots, n\}$, for which the conditional embedding map $\mathcal{U}_{Y | X}$ can be estimated by

	\begin{equation}
		\hat{\mathcal{U}}_{Y | X} = \Psi (K + n \lambda I)^{-1} \Phi^{T},
	\label{eq:empirical_conditional_embedding}
	\end{equation}

	where $K := \{k(x_{i}, x_{j})\}_{i = 1, j = 1}^{n, n}$, $\Phi := \begin{bmatrix} k(x_{1}, \cdot) & \dots & k(x_{n}, \cdot) \end{bmatrix}$, $\Psi := \begin{bmatrix} l(y_{1}, \cdot) & \dots & l(y_{n}, \cdot) \end{bmatrix}$, and $\lambda$ is the regularisation parameter for the conditional operator \citep{song2013kernel}. We then define the empirical conditional embedding by $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$, which stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \citep{song2009hilbert}. That is, % Theorem 6

	\begin{equation}
		\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists M_{\epsilon} > 0 \quad s.t. \quad \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
	\label{eq:empirical_conditional_embedding_stochastic_convergence}
	\end{equation}

	This allows us to approximate the conditional expectation \eqref{eq:conditional_expectation} with $\langle \hat{\mu}_{Y | X = x}, g \rangle$ instead,

	\begin{equation}
		\mathbb{E}[g(Y) | X = x] \approx \langle \hat{\mu}_{Y | X = x}, g \rangle = \bvec{g}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x},
	\label{eq:empirical_conditional_expectation}
	\end{equation}

	where $\bvec{g} := \{g(y_{i})\}_{i = 1}^{n}$ and $\bvec{k}_{x} := \{k(x_{i}, x\}_{i = 1}^{n}$, knowing that it would converge to the true expectation as $n$ increases for sufficiently small $\lambda$.

	\note{Note: I believe \eqref{eq:empirical_conditional_expectation} is a very well known result. It is very easy to derive. However, I have not found a paper that explicitly states this as a result or theorem yet. Perhaps I will include a short derivation of this in the appendix if we find it necessary.}

%	The conditional operator $C_{Y X} C^{-1}_{XX}$ only acts as an approximation of the conditional mean embedding $C_{Y | X}$ for continuous domains because the assumption that for all $g \in \mathcal{H}_{l}$ , the conditional expectation $\mathbb{E}[g(Y) | X = \cdot]$ is an element of $\mathcal{H}_{k}$ may not hold in general \citep{fukumizu2004dimensionality, song2009hilbert}. It also serves to avoid overfitting \citep[p. 13]{song2013kernel}.

\section{Kernel Embedding Classifier}
\label{sec:kernel_embedding_classifier}

	In this section, we formulate a kernel embedding based probabilistic classifier by casting it into the conditional embedding framework.

	In the multiclass classification context, the output label space is finite and discrete, taking values only in $\mathcal{Y} = \mathbb{N}_{m} := \{1, \dots, m\}$. Naturally, we first choose the Kronecker delta kernel $\delta : \mathbb{N}_{m} \times \mathbb{N}_{m} \to \{0, 1\}$ as the output kernel $l$, where labels that are the same has unit similarity and labels that are different have no similarity. That is, for all pairs of labels $y_{i}, y_{j} \in \mathcal{Y}$,

	\begin{equation}
		\delta(y_{i}, y_{j}) = \begin{cases}
		1 & \mathrm{if } \quad y_{i} = y_{j}, \\
		0 & \mathrm{otherwise}.
		\end{cases}
	\end{equation}

	As $\delta$ is an integrally strictly positive definite kernel on $\mathbb{N}_{m}$, it is therefore characteristic \citep[Theorem 7]{sriperumbudur2010hilbert}. As such, by definition of characteristic kernels, $\delta$ uniquely defines a RKHS $\mathcal{H}_{\delta}$ \citep{fukumizu2004dimensionality}. Notice that this kernel has no parameters, so that the model hyperparameters only come from the kernel of the input space and the regularisation parameter $\lambda$.

	Recall that the RKHS induced by a positive definite kernel is the closure of the span of its kernel induced features \citep{xu2009refinement}, so that $\mathcal{H}_{l} = \overline{\mathrm{span}\{l(y, \cdot) : y \in \mathcal{Y}\}}$. For $\mathcal{Y} = \mathbb{N}_{m}$ and $l = \delta$, this means that any real-valued function $g : \mathbb{N}_{m} \to \mathbb{R}$ that is bounded on its discrete domain $\mathbb{N}_{m}$ is in the RKHS of $\delta$, because we can always write $g = \sum_{y = 1}^{m} g(y) \delta(y, \cdot) \in \mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}$.

	In particular, indicator functions on $\mathbb{N}_{m}$ are in the RKHS $\mathcal{H}_{\delta}$, since

	\begin{equation}
		\mathbb{1}_{c}(y) = \begin{cases}
		1 & \mathrm{if } \quad y = c \\
		0 & \mathrm{otherwise}
		\end{cases} = \delta(c, y).
	\label{eq:indicator_function}
	\end{equation}

	That is, indicator functions $\mathbb{1}_{c} = \delta(c, \cdot)$, $c \in \mathbb{N}_{m}$ are simply the canonical kernel features of $\mathcal{H}_{\delta}$.

	While such properties does not becessarily hold for continuous domains in general, this convenient property in the case of a discrete domain $\mathcal{Y}$ with a Kronecker delta kernel $\delta$ is what allows consistent estimations of decision probabilities used in multiclass classification, which we turn to next.

	Let $p_{c}(x) := \mathbb{P}[Y = c | X = x]$ be the \textit{decision probability function} for class $c \in \mathbb{N}_{m}$, which is the probability of the class label $Y$ being $c$ when the example $X$ is $x$. We begin by writing this probability as an expectation of indicator functions,

	\begin{equation}
		p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mathbb{P}[Y \in \{c\} | X = x] = \mathbb{E}[\mathbb{1}_{c}(Y) | X = x].
	\label{eq:decision_probability}
	\end{equation}

	With $\mathbb{1}_{c} \in \mathcal{H}_{\delta}$, we let $g = \mathbb{1}_{c}$ in \eqref{eq:empirical_conditional_expectation} and $\bvec{1}_{c} := \{\mathbb{1}_{c}(y_{i})\}_{i = 1}^{n}$ to estimate the right hand side of \eqref{eq:decision_probability} by

	\begin{equation}
		\hat{p}_{c}(x) = f_{c}(x) := \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x}.
	\label{eq:empirical_decision_probability}
	\end{equation}

	Therefore, the vector of empirical decision probability functions over the possible classes $c \in \mathbb{N}_{m}$ is

	\begin{equation}
		\hat{\bvec{p}}(x) = \bvec{f}(x) := B^{T} (K + n \lambda I)^{-1} \bvec{k}_{x} \in \mathbb{R}^{m},
	\label{eq:empirical_decision_probability_vector}
	\end{equation}

	where $B = \begin{bmatrix} \bvec{1}_{1} & \bvec{1}_{2} & \cdots & \bvec{1}_{m} \end{bmatrix} \in \{0, 1\}^{n \times m}$, which is simply the one hot encoding form for the training labels $\{y_{i}\}_{i = 1}^{n}$. This can be further vectorised over multiple query points $\{x^{\star}_{j}\}_{j = 1}^{n^{\star}}$ through

	\begin{equation}
		\hat{P}^{\star} = B^{T} (K + n \lambda I)^{-1} K^{\star} \in \mathbb{R}^{m},
	\label{eq:empirical_decision_probability_matrix}
	\end{equation}

	where $K^{\star} = \{k(x_{i}, x_{j}^{\star})\}_{i = 1, j = 1}^{n, n^{\star}}$ and $n^{\star}$ is the number of query points.

	Finally, to perform classification, we simply take the class with the highest empirical decision probability for the given query point $x^{\star} \in \mathcal{X}$,

	\begin{equation}
		\hat{y}^{\star} = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x^{\star}).
	\label{eq:classification}
	\end{equation}

	We proceed to show that the empirical decision probabilities given by \eqref{eq:empirical_decision_probability} is a consistent estimator for the actual decision probabilities as the dataset increases.

	\begin{theorem}[Pointwise Uniform Convergence of Empirical Decision Probability Function]
	\label{thm:probability_convergence}
		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges pointwise and uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.

	\begin{proof}
		Consider the pointwise absolute difference between the decision probability and its empirical estimate,

		\begin{equation}
		\begin{aligned}
			| \hat{p}_{c}(x) - p_{c}(x) | &= | \langle \hat{\mu}_{Y | X = x}, \mathbb{1}_{c} \rangle - \langle \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
			&= | \langle \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
			&\leq \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}},
		\end{aligned}
		\end{equation}

		where the last inequality follows from the Cauchy–Schwarz inequality in a Hilbert space.

		From \eqref{eq:indicator_function}, since $\mathbb{1}_{c} = \delta(c, \cdot)$ and using the fact that $\delta$ is a reproducing kernel, we have that for all $c \in \mathcal{Y} = \mathbb{N}_{m}$,

		\begin{equation}
		\begin{aligned}
			\big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}}^{2} = \langle \mathbb{1}_{c}, \mathbb{1}_{c} \rangle = \langle \delta(c, \cdot), \delta(c, \cdot) \rangle = \delta(c, c) = 1.
		\end{aligned}
		\end{equation}

%		Consequently, $| \hat{p}_{c}(x) - p_{c}(x) | \leq \big\| \hat{\mu}_{Y | X = x}^{(n)} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}}$ for all $x \in \mathcal{X}$, where the right hand side of which approaches zero stochastically at rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, so that $\hat{p}_{c}$ converges pointwise to $p_{c}$ at least at this rate. The convergence rate does not depend on $x \in \mathcal{X}$, so this (stochastic) convergence is pointwise uniform.

		Consequently, for all $x \in \mathcal{X}$ and $c \in \mathcal{Y}$, we have

		\begin{equation}
			| \hat{p}_{c}(x) - p_{c}(x) | \leq \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}}.
		\label{eq:uniform_convergence}
		\end{equation}

		This is true for all possible datasets represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$. Thus, for any constant $C$, the implication statement $\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C \implies | \hat{p}_{c}(x) - p_{c}(x) | \leq C$ holds for all possible data observation events $\omega \in \Omega$. Writing this explicitly in event space translates this to a probability statement,

		\begin{equation}
		\begin{aligned}
			\{\omega \in \Omega : \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C\} &\subseteq \{\omega \in \Omega : | \hat{p}_{c}(x) - p_{c}(x) | \leq C\} \\
			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C\Big] &\leq \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | \leq C \Big].
		\label{eq:probability_statement}
		\end{aligned}
		\end{equation}

		Since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is valid. By letting $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ in \eqref{eq:probability_statement}, we immediately have that the probability inequality in statement \eqref{eq:probability_statement} is also true if we replace $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|$ with $| \hat{p}_{c}(x) - p_{c}(x) |$, % the RKHS norm between the empirical and true embeddings to the absolute difference between the empirical decision probability and the true decision probability,

		\begin{equation}
		\begin{aligned}
			\mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
			\implies 1 - \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
			\implies \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
			\implies 1 - \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
			\implies \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon.
		\end{aligned}	
		\end{equation}

		In other words, the function $\hat{p}_{c}$ stochastically converges pointwise to $p_{c} := \mathbb{P}[Y = c | X = \cdot]$ with a rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$. The convergence rate does not depend on $x \in \mathcal{X}$ nor $c \in \mathbb{N}_{m}$, so this stochastic convergence is pointwise uniform in its domain $\mathcal{X}$ across all label classes.

	\end{proof}
	\end{theorem}

	\note{Note: The above proof is for pointwise uniform convergence over all $x \in \mathcal{X}$. From what the experiments seem to suggest, for stationary zero-centred kernels, I believe that we can actually do better than this convergence rate for areas of high data density. Basically, at the subspace of $\mathcal{X}$ where we have observed our data, the convergence rate should be higher, because the kernel effects are stronger at these regions. The worse case convergence rate described in the theorem would be a tight lower bound for regions in $\mathcal{X}$ where we do not have a lot of data, where the kernel effects have decayed and most empirical probabilities are near zero and further from summing up to one.}

	While the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ will converge to the true decision probability function  $p_{c} : \mathcal{X} \to [0, 1]$ in the limit, for finite $n$ and a given regulariser $\lambda > 0$, the stochasticity in the empirical estimates implies that these probabilities may not necessarily sum up to one, nor are they strictly resctricted to the range $[0, 1]$. However, they will usually be very close to the true predicted probabilities. Moreover, such stochasticity also does not principally affect the classification prediction, since we simply take the argmax of the empirical decision probability vector as in \eqref{eq:classification}.

	If strict, valid probabilities are required for interpretation, visualisation, or other purposes, the probabilities can be clipped at zero then normalised to one - a procedure we refer to as \textit{clip-normalisation},

	\begin{equation}
		\tilde{p}_{c}(x) := \frac{\max\{\hat{p}_{c}(x), 0\}}{\sum_{j = 1}^{m} \max\{\hat{p}_{j}(x), 0\}}.
	\label{eq:probability_clip_normalise}
	\end{equation}

	Notice that for classification prediction, the argmax solution over the classes of the empirical decision probabilities \eqref{eq:empirical_decision_probability} and its clip-normalised version \eqref{eq:probability_clip_normalise} remain the same. Furthermore, since $\hat{p}_{c}(x)$ converges to valid probabilities $p_{c}(x)$ according to \cref{thm:probability_convergence}, the effect of clip-normalisation reduces as $n$ increases such that $\tilde{p}_{c}(x)$ becomes very close to $\hat{p}_{c}(x)$ and $p_{c}(x)$. Experiments verify that clip-normalisation only adjusts the probabilities slightly, as the empirical estimates are usually already close to satisfying normalisation and range properties (see \cref{app:design_choices}).

\section{Information Entropy}
\label{sec:information_entropy}

	The kernel embedding classifier provides decision probabilities instead of just a single label prediction. Such a probabilistic classifier allows us to quantify the uncertainty of its predictions for any given example $x \in \mathcal{X}$ through the information entropy \citep{shannon1951prediction, jaynes1957information}. This is ideal for detecting the decision boundaries of the classifier and areas of low data density.

	We present two main approaches for inferring the information entropy from the classifier. Specifically, we would like to infer estimates for $h(x) := \mathbb{H}[Y | X = x] = - \sum_{c = 1}^{m} p_{c}(x) \log{p_{c}(x)} $, the information entropy of the possible labels $Y$ for a given example $X = x$.

	The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref{eq:probability_clip_normalise}, at the query point $x \in \mathcal{X}$,

	\begin{equation}
		\tilde{h}(x) := - \sum_{c = 1}^{m} \tilde{p}_{c}(x) \log{\tilde{p}_{c}(x)}.
	\label{eq:entropy_clip_normalise}
	\end{equation}

	We call \eqref{eq:entropy_clip_normalise} the \textit{clip-normalised information entropy}. Since $\tilde{p}_{c}(x)$ converges pointwise to $p_{c}(x)$ with increasing data, $\tilde{h}(x)$ also converges pointwise to $h(x)$.

	Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information \footnote{Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$.},

	\begin{equation}
	\begin{aligned}
		\mathbb{H}[Y | X = x] &= - \sum_{c = 1}^{m} \mathbb{P}[Y = c| X = x] \log{\mathbb{P}[Y = c | X = x]} \\
		&= \mathbb{E}[- \log{\mathbb{P}[Y | X = x]} | X = x] \\
		&= \mathbb{E}[u_{x}(Y) | X = x],
	\end{aligned}
	\end{equation}

	where $u_{x}(y) := - \log{\mathbb{P}[Y = y | X = x]}$ is the \textit{information} (in nats) we would gain when we discover that example $x$ actually has label $y$. If $u_{x} : \mathbb{N}_{m} \to \mathbb{R}$ is in the RKHS $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by $\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle$. This is the basis of our second approach.

	Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$. We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the RKHS. Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref{eq:empirical_conditional_expectation} and estimate $h(x)$ by

	\begin{equation}
		\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle = \bvec{u}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x}.
	\end{equation}

	Unfortunately, $u_{x}$ is not known exactly, since $\mathbb{P}[Y = y | X = x]$ is not known exactly. Instead, since $\hat{p}_{c}(x)$ is a consistent estimate for $\mathbb{P}[Y = c | X = x]$ (\cref{thm:probability_convergence}), we propose to replace $u_{x}$ with the negative log of $\hat{p}_{y}(x)$. However, we cannot simply take the log of this estimator, as $\hat{p}_{y}(x)$ may produce non-positive estimates to the prediction probabilities. The straight forward way to mitigate this problem is to clip $\hat{p}_{y}(x)$ from the bottom by a very small number, before taking the log. However, experiments show that this produces non-smooth estimates over $\mathcal{X}$ and the degree of smoothness varies drastically between different choices of that small number (see \cref{app:design_choices}). Instead, in virtue of the fact that $\lim_{p \to 0} - p \log{p} = 0$ even though $\lim_{p \to 0} - \log{p} = \infty$, we simply define the information estimate $\hat{u}_{x}(y)$ as zero if the empirical decision probability is non-positive,

	\begin{equation}
		\hat{u}_{x}(y) := \begin{cases}
		- \log{\hat{p}_{y}(x)} & \mathrm{if } \quad \hat{p}_{y}(x) > 0 \\
		0 & \mathrm{otherwise}. \end{cases}
	\label{eq:empirical_information}
	\end{equation}

	It remains to show that $\hat{u}_{x} \in \mathcal{H}_{\delta}$. Indeed, the identity $\hat{u}_{x} = \sum_{c = 1}^{m} \hat{u}_{x}(c) \delta(c, \cdot)$ holds and thus $\hat{u}_{x}$ is in the span of the kernel canonical features. We then arrive at the following estimate for $h(x)$,

	\begin{equation}
		\hat{h}(x) := \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle = \hat{\bvec{u}}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x},
		\label{eq:empirical_information_entropy}
	\end{equation}

	where $\hat{\bvec{u}}_{x} := \{\hat{u}_{x}(y_{i})\}_{i = 1}^{n}$. Similar to the case with decision probabilities \eqref{eq:decision_probability}, the information entropy estimate \eqref{eq:empirical_information_entropy} is not guaranteed to be non-negative. However, in practice these negative values are close to zero. Furthermore, negative estimated information entropy implies that the model is very confident about its prediction, and it suffices to simply clip the entropy at zero if strict information entropy is required (see \cref{app:design_choices}). We give the proof of convergence of \eqref{eq:empirical_information_entropy} in \cref{app:theorems_derivations}.

	\subsection{Cross Entropy and Kullback–Leibler Divergence}

\section{Hyperparameter Training}
\label{sec:hyperparameter_learning}

	The formulation of the kernel embedding classifier requires the specification of a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ over the input space $\mathcal{X}$, or rather, a class of kernels $\{k_{\theta}\}_{\theta \in \Theta}$ parametrised by the kernel parameters $\theta \in \Theta$. It also requires the specification of a regularisation parameter $\lambda$ for the conditional embedding as in \eqref{eq:empirical_conditional_embedding}. These are hyperparameters of the kernel embedding classifier which needs to be learned in order to produce a reasonable model with high prediction accuracy.

	In the kernel embedding literature, hyperparameters has been notoriously difficult to tune, and its learning is usually only restricted to inelegant methods such as cross validation with either some form of misclassification loss or the negative log probability (cross entropy) as the objective.

%	Inspired by the log marginal likelihood learning objective used to learn the hyperparameters of a Gaussian process \citep{rasmussen2006gaussian}, \cite{flaxman2016bayesian} derived a log marginal likelihood expression for kernel embeddings by placing a Gaussian process prior on the mean embedding, and constructing a Gaussian likelihood of the empirical mean embedding given the true mean embedding. With a Gaussian prior and a Gaussian likelihood, inference becomes tractable and a closed form solution to the corresponding log marginal likelihood objective can be obtained with a slight change of variable factor. However, this formulation is only capable of learning the kernel parameters of a joint embedding, and not the kernel and regularisation parameters of a conditional embedding.

	In this paper, we take a learning theoretic approach to learn the hyperparameters of the KEC, inspired by the original training procedure of support vector classifiers (SVC) as described by \cite[p. 185]{m2001introduction}. Assuming a perfectly separable case, the training of a SVC begins by introducing a \textit{prediction constraint} on the training set, where the classifier is constrained to correctly classify all the available training examples. The strategy is to minimise the \textit{complexity} of the SVC model while ensuring perfect classification over training examples. The model complexity in the SVC context is measured by the VC dimension $h$ of the binary classifier, which has an upper bound $h \leq \lVert \bvec{w} \rVert^{2} R^{2} + 1$. Since it is difficult to compute the VC dimension explicitly, we instead minimise its upper bound, which is equivalent to and leads to the common interpretation of maximising the margin $\frac{2}{\lVert \bvec{w} \rVert}$.

	Similarly, we propose to train our kernel embedding classifier with the same high level formulation: minimise the model complexity without compromising classification performance on the training data. Instead of employing the VC dimension as the complexity measure of our model, which is defined mainly for binary classifiers, we consider the \textit{Rademacher complexity} \citep{bartlett2002rademacher} of the kernel embedding classifier.

%	For a multi-label predictor parametrised as $f(x; W) = W^{T} x$ where $W \in \mathbb{R}^{d \times L}$ and $L$ is the number of target binary labels,  \cite{yu2014large} showed that the global Rademacher complexity of $W$ is upper-bounded in terms of its trace norm, $\mathrm{trace}(W^{T} W)$. Albeit formulated for multiclass instead of multi-label prediction, the empirical decision probabilities \eqref{eq:empirical_decision_probability_vector} also has the same analytical form, where the input $x$ is replaced by some feature vector $\phi(x)$.

%	\begin{algorithm}[tb]
%		\caption{Kernel Embedding Classifier Training with Gradient Descent}
%		\label{alg:training_gradient_descent}
%		\begin{algorithmic}[1]
%			\STATE {\bfseries Input:} kernel family $k_{\theta}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial kernel parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$
%			\STATE $\theta \leftarrow \theta_{0}$
%			\STATE $\lambda \leftarrow \lambda_{0}$
%			\REPEAT
%			\STATE $B \leftarrow \{\delta(y_{i}, c) : i \in \mathbb{N}_{n}, c \in \mathbb{N}_{m}\} \in \{0, 1\}^{n \times m} $ 
%			\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathbb{N}_{n}, j \in \mathbb{N}_{n}\} \in \mathbb{R}^{n \times n}$
%			\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n \lambda I)$
%			\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash B)$
%			\STATE $r(\theta, \lambda) \leftarrow \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
%			\STATE $\theta \leftarrow \theta - \eta \frac{\partial r}{\partial \theta}(\theta, \lambda)$
%			\STATE $\lambda \leftarrow \lambda - \eta \frac{\partial r}{\partial \lambda}(\theta, \lambda)$
%			\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial r}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial r}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{1} < \epsilon$}
%			\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
%		\end{algorithmic}
%	\end{algorithm}

	For a predictor parametrised as $f(x; W) = W^{T} x$, \cite{yu2014large} showed that the global Rademacher complexity of $W$ is upper-bounded in terms of its trace norm, $\sqrt{\mathrm{trace}(W^{T} W)}$. This was originally discussed in the context of multi-label classification, where $W \in \mathbb{R}^{d \times L}$ and $f$ produces a binary vector of length $L$ indicating the multiple labels that describes the input $x \in \mathbb{R}^{d}$. In the context of the kernel embedding classifier, the empirical decision probabilities \eqref{eq:empirical_decision_probability_vector} also has the same analytical form, where the input $x$ is replaced by some feature vector $\phi(x)$. By using the canonical feature map $\phi(x) = k(x, \cdot)$ and the reproducing property $\langle \phi(x), \phi(x') \rangle = k(x, x')$ in the RKHS, we can write \eqref{eq:empirical_decision_probability_vector} as $\hat{\bvec{p}}(x) = \bvec{f}(x) := B^{T} (K + n \lambda I)^{-1} \Phi^{T} \phi(x) = W^{T} \phi(x)$, where instead of mapping input examples in $\mathbb{R}^{d}$ to output multi-label vector $\mathbb{R}^{L}$, $W^{T}$ maps features in the RKHS $\mathcal{H}_{k}$ to the a vector of multiclass probabilities in $\mathbb{R}^{m}$. Using the reproducing property $K = \Phi^{T} \Phi$ again, the squared trace norm for such a predictor is then $\mathrm{trace}(W^{T} W) = \mathrm{trace}(B^{T} (K + n \lambda I)^{-1} K (K + n \lambda I)^{-1} B)$. We therefore propose to use this quantity as an upper bound measure of the kernel embedding classifier model complexity, which is to be minimised for hyperparameter training,

	\begin{equation}
		\min_{\theta \in \Theta, \lambda \in (0, \infty)} \sqrt{\mathrm{trace}\bigg(B^{T} (K_{\theta} + n \lambda I)^{-1} K_{\theta} (K_{\theta} + n \lambda I)^{-1} B\bigg)},
	\label{eq:trace_norm_optimisation}
	\end{equation}

	where we use the subscript $\theta$ to make explicit the dependence on the kernel parameters. We employ gradient descent to train the kernel embedding classifier with this complexity bound objective. The gradients of the complexity bound objective with respect to the hyperparameters is to be computed automatically using standard back-propagation.

	While it may be tempting to instead minimise the square of the trace norm \eqref{eq:trace_norm_optimisation} to remove the square root, experiments show that, without the square root, the magnitude of the gradients grows large at regions of higher trace norms. For instance, this can happen when the optimisation is initialised at a location far away from the optimum. This makes the optimisation unstable, and may cause the hyperparameters to diverge to a numerically unstable scenario where the Cholesky decomposition of the regularised gram matrix does not exist. That being said, one can instead choose to minimise the log of the squared trace norm, $\log{\mathrm{trace}(B^{T} (K + n \lambda I)^{-1} K (K + n \lambda I)^{-1} B)}$, which experiments show are also quite numerically stable during optimisation.

	If one were to follow the philosophy of minimising the model complexity without compromising performance on training data, then either a further training performance constraint should be added to the optimisation, or a training error term should be added to the objective. However, we found that this was unnecessary for the kernel embedding classifier. We postulate that minimising the model complexity, or the upper bound thereof, is both sufficient and desirable for a classifier that is to generalise classification performance to new test examples.

	Contrary to parametric models, kernel methods are nonparametric, and thus its model capacity grows with increasing data. Within a large enough family of kernels $k_{\theta}$, the kernel embedding classifier always has the capacity to shatter the training data and produce zero training error. Given that it has such capabilities, we instead focus on learning the simplest model that can generalise well to new test data. If we instead choose to train the classifier by adding some measure of training error as a penalty term to \eqref{eq:trace_norm_optimisation}, such as the training cross entropy loss, then it can very easily overfit by adapting its model capacity to the training data closely. The Rademacher complexity regularises this behaviour to learn a good balance between training error and unseen test error. In short, while parametric models have limited capacity and thus trying to learn to perform well on a training set to its best ability is a good indicator to test performance, nonparametric models has infinite capacity and need to learn not to exploit this capacity on training data and instead learn the simplest pattern it can to be able to infer about new test instances. Indeed, experiments show that KEC training usually starts with high training accuracy and very low cross entropy loss, and eventually learns the simplest model while maintaining that training accuracy, or even relaxes the training accuracy if the model is simply too complicated and unlikely to generalise well. That is, the training usually starts from a state of overfitting, and eventually learns simpler patterns and structures. This is in contrast with parameteric models, where training usually begins with low training accuracy that is to be improved as training continues.

	\begin{algorithm}[tb]
		\caption{Kernel Embedding Classifier Hyperparameter Training with Stochastic Gradient Descent}
		\label{alg:training_stochastic_gradient_descent}
		\begin{algorithmic}[1]
			\STATE {\bfseries Input:} kernel family $k_{\theta}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial kernel parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
			\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
			\REPEAT
			\STATE Sample $\mathcal{I} \subseteq \mathbb{N}_{n}$ such that $| \mathcal{I} | = n_{b}$ \hspace{\fill} For gradient descent, $n_{b} = n$ and $\mathcal{I} = \mathbb{N}_{n}$
			\STATE $B \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
			\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathcal{I}, j \in \mathcal{I}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
			\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n \lambda I) \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
			\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash B) \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
			\STATE $r(\theta, \lambda) \leftarrow \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$ \hspace{\fill} Alternatively, $r(\theta, \lambda) \leftarrow \log{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
			\STATE $\theta \leftarrow \theta - \eta \frac{\partial r}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial r}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} Gradients are computed through back-propagation
			\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial r}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial r}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} Stop if magnitude of all gradients are below $\epsilon$
			\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
		\end{algorithmic}
	\end{algorithm}

	\subsection{Stochastic Gradient Descent}
	\label{sec:stochastic_gradient_descent}

		With standard gradient descent, the time complexity of each training iteration is dominated by the Cholesky decomposition of the regularised gram matrix $K_{\theta} + n \lambda I$ of size $n \times n$, which has a time complexity of $O(n^{3})$. In order to scale the hyperparameter training of kernel embedding classifiers to large dataset, we propose to optimise the complexity objective with stochastic gradient descent.

		For gradient descent, pick $n_{b} = n$ so that $\mathcal{I} = \mathbb{N}_{n}$ and the full dataset is used to compute the gradients.

		SGD Coefficient ratio for gradient update can be absorbed into the learning rate so don't need to worry about it

		Also learning rate can be left to the same

		Convergence can usually be left to the same gradient error tolerance

		\textbf{Why does SGD work?} It is not immediately clear to me why SGD works. What we can see from experiments is that the batch data complexity bound is usually a biased estimator of the full data complexity bound. This bias is expected for one primary reason. The first is that this quantity is a data complexity bound to begin with, and thus while the actual batch data complexity may be an unbiased estimator of the full data complexity, the tightness of the upper bound is expected to change with growing datasets and thus this bias comes from the varying degrees of tightness in the bound as data increases. While this bias exists, we do see from experiments that, as we optimise the hyperparameters, both the batch data complexity bound and full data complexity bound decreases at a proportional pace. At first it may seem that there is simply a multiplicative factor (possibly in log scale or square root scale with respect to the data size) relationship between them, although it is unclear how this multiplicative factor can be computed. We did try seeing if the average complexity bound of disjoint batches is the complexity bound of the full batch. The answer is no but it is close, through numerical simulation. However, again this should be expected as the tightness of the bound is expected to change for varying data size. Perhaps the complexity itself is additive.

		Idea: Last time in my derivation I can derive that the full complexity bound is the sum of the batch complexity bound plus some co-varying terms (which can be negative). If I can show that the magnitude of such co-varying terms are upper bounded by the batch complexity bounds, then I can say that as the batch complexity bounds are minimised, so is the full complexity bound!

		We know that the SGD works because the gradients computed from each batch is consistently vanishing as we optimise the hyperparameters. Surprisingly, it seems to be on the same scale of the full GD case and suggests that the batch gradient is possibly a (scaled) consistent estimator of the full gradient as well.

		Furthermore, not only does SGD reduce the time and space complexity of each training iteration drastically, it does not increase the number of iterations required for convergence either (at least for a Gaussian kernel), and, in many cases actually takes less iterations than the full GD solution. This could be because the SGD gradients are usually under-biased compared to the full GD gradients, and thus reach the gradient error tolerance faster.

		Of course, the usual drawbacks of SGD holds here to. Specifically, if the optimisation is non-convex, the SGD may converge to a local optimum that is different to the one that the full GD approach would reach. Nevertheless, it does not necessarily mean that the SGD solution is worse. Sometimes it can actually do better, when the full GD solution was going to converge to a sub-optimal solution already, since the stochasticity in the SGD approach may allow it to find some other solution that is better.

		Round Shifts: Instead of taking completely random batches from the full dataset each time, what one can do instead is to use a ``round shift'' setup to choose the batches. That is, we first choose a batch size $n_{b}$. The first batch is the first $n_{b}$ data points in the dataset, the second batch is the second $n_{b}$ data points in the dataset, and so on. When the whole dataset is scanned through once, we repeat and start from the beginning again. Experiments show that this converges to basically the same solution with the full GD approach and also the vanilla SGD approach. However, it does take longer iterations to reach the solution. Our guess is that the data points we use each time in our batch complexity bound estimation is not independent from each other enough such that the gradients are more correlated to each other and is thus less adaptive.

\section{End-to-End Classifier Training for Deep Kernel Embeddings}
\label{sec:deep_kernel_embeddings}

\section{Full Probabilistic Inference and Mode Reconstruction}
\label{sec:mode_reconstruction}

	Being formulated and represented as a conditional embedding in a reproducing kernel Hilbert space, the kernel embedding classifier is able to learn a discriminative model to nonparametrically infer about the distribution of discrete labels $Y$ given an example input $X$. In the previous section, we devised a training algorithm for learning the optimal hyperparameters for the conditional embedding corresponding to the classifier. Now that the conditional embedding is learned, we can

\section{Experiments}

	\note{Note that while it would certainly be great, the point of developing this kernel embedding classifier is not to beat other existing classification algorithms. The purpose is to develop a simple and elegant fully probabilistic multiclass classifier based on embedding the observed data directly into a reproducing kernel Hilbert space, with a quantifiable notion of model complexity. This is what we will aim to show here in the experiments as well. Below is just a summary of what has been done but has not been put together neatly yet.}

	\textbf{Experiments to Show}: We are aiming to do experiments on one toy dataset for illustration and visualisation, and on two real world datasets for benchmarking performance. So far, I am using the iris dataset for the toy dataset, and MNIST for one of the real world datasets. We should still find a third real world dataset that will really benefit from such a flexible nonparametric, probabilistic multiclass classifier.

	\begin{itemize}
		\item A toy 2D classification tasks for visualising the properties and capabilities of the kernel embedding classifier. An simple example is the iris dataset, where we take only 2 attributes. There are three classes, so the probabilities can be visualised using RGB. We first use the first two attributes of the dataset, where the training examples are very non-separable. The point is to demonstrate that the kernel embedding classifier learns a simple and reasonable model that does not overfit, even though it has the capacity to shatter all the training data and have 100\% training accuracy. We then show that if we use the standard cross entropy loss as the objective for training, then we easily overfit the data.
		\item We also show plots illustrating how the training objective, performance of the classifier, and the hyperparameters changes during the training procedure.
		\item We then show results for training using SGD, which reveals that at a faster speed we arrive at the same solution as before.
		\item We can then move on to actual real world datasets, like MNIST.
		\item The MNIST dataset has 60000 training images and 10000 test images. So far I have results for only giving the first 500 training images to the kernel embedding classifier (much smaller than the dimensionality of the problem, which is 784), and it is to perform on the whole 10000 test images. We show that with a Gaussian kernel, we get around 82\% accuracy. Then, with a simple extension by adding three convolutional layers before give it to the Gaussian kernel, we get around 92\% accuracy. Of course, we also report the cross entropy loss. We do this with both gradient descent and SGD. We then compare this to support vector classifiers and Gaussian process classifiers. Then also compare this to state of the art convolutional neural networks with 500 observations for training data.
		\item More to come...
	\end{itemize}

	We will also open-source the code on GitHub. All the core algorithms presented in this paper will be available and implemented in TensorFlow, while having the same API as \texttt{scikit-learn} models so that it is straightforward to use.

%	\begin{figure}
%		\begin{center}
%			\includegraphics[width=0.48\linewidth]{figures/iris_2017_4_11_0_43_24_anisotropic_gd_tol_01_complexity_attributes_0_1/figure4.eps}
%			\includegraphics[width=0.48\linewidth]{figures/iris_2017_4_11_0_43_55_anisotropic_sgd_batch_27_tol_01_complexity_attributes_0_1/figure4.eps}
%			\includegraphics[width=0.48\linewidth]{figures/iris_2017_4_11_0_47_23_anisotropic_gd_tol_001_cross_entropy_attributes_0_1/figure4.eps}
%			\includegraphics[width=0.48\linewidth]{figures/iris_2017_4_11_0_48_54_anisotropic_sgd_batch_27_tol_001_cross_entropy_attributes_0_1/figure4.eps}
%		\end{center}
%		\caption{\small Kernel Embedding Classifier}
%		\label{fig:kec}
%	\end{figure}
%	
%	\begin{figure}
%		\begin{center}
%			\includegraphics[width=0.9\linewidth]{figures/iris_2017_4_11_0_43_24_anisotropic_gd_tol_01_complexity_attributes_0_1/figure14.eps}
%		\end{center}
%		\caption{\small Kernel Embedding Classifier}
%%		\label{fig:kec}
%	\end{figure}

\section{Conclusion}

	\note{Summarise main contribution. Specifically, the guaranteed convergence of the kernel embedding classifier in both decision probability and information entropy, the Rademacher complexity based hyperparameter training scheme, the stochastic gradient descent version thereof which allows scalable training, the application of such flexible training methods to train deep convolutional features, and the fully probabilistic inference on both inputs and outputs. Focus the point of the paper as that this is a new and elegant formulation of a fully probabilistic classifier (not just in the outputs, but even in the inputs) with complexity bound based training. Being formulated as type of kernel conditional embedding learning, all the nice properties from the Hilbert space embedding world can be imported into this framework. In practice, even though the mathematical theory of kernel embeddings can be tricky, the resulting algorithms are very elegant and simple, so that implementation is quick and easy. Being very general, there should be a lot of things we can do in the future to improve it or build upon it.}

	\textbf{Future Work}: \note{(Not that polished)}

	\begin{itemize}
		\item \textbf{Hyperparameter Training through Local Rademacher Complexity.} In parallel with the work of \cite{xu2016local}, we can derive an upper bound for the \textit{local Rademacher complexity} of our kernel embedding classifier. In contrast to the global Rademacher complexity, the local Rademacher complexity of a model produces a sharper generalization error bound and a faster convergence rate. Specifically, for our classifier, it is upper bounded by the tail sum of the sorted eigenvalues of $B^{T} (K + n \lambda I)^{-1} K (K + n \lambda I)^{-1} B$. The complication is that there is an extra design choice to be made: from which eigenvalue should the tail sum start. Preliminary experiments that we have done so far shows that this choice affects the training a lot, and thus more work is needed to theorise how this choice should be done, and if it really improves classification performance consistently at the end of the day.

		\item \textbf{Multiple Kernel Learning and Shallow-Deep Kernels.} With kernel methods, newer and more flexible kernel classes can always be formed by convex combinations of simpler positive definite kernels. We can explore kernel and hyperparameter learning for these architectures under the kernel embedding classification framework that we developed in this paper.

		\textbf{Multiple Kernel Learning}. In summary, multiple kernel learning is traditionally interested in forming a new kernel $k(x, x') := \sum_{i = 1}^{p} \alpha_{i} k_{i}(x, x')$ from simpler kernels $k_{i}(x, x')$ by finding the optimal coefficient vector $\{\alpha_{i}\}_{i = 1}^{p}$ with respect to its learning task under convexity constraints. While this convex optimisation problem is quite tractable, each kernel component $k_{i}$ stays fixed, so that it is up to the practitioners to choose and tune each kernel component a-priori. With the kernel embedding classification framework, hyperparameter training is very general, and makes no restrictions on where the trainable parameters must appear (with the trade-off being that the optimisation may become non-convex). As such, we can construct newer kernels through $k(x, x'; \theta) := \sum_{i = 1}^{p} \alpha_{i} k_{i}(x, x'; \theta_{i})$ and generalise the multiple kernel learning problem to one that finds the optimal coefficient vector $\{\alpha_{i}\}_{i = 1}^{p}$ and kernel parameters $\{\theta_{i}\}_{i = 1}^{p}$. Of course, the regularisation parameter $\lambda$ is jointly learned at the same time.

		\textbf{Shallow-Deep Kernels}. Similarly, another way of convexly combining kernels is through a simple tensor multiplication, $k([x, z]^{T}, [x', z']^{T}; \theta_{\mathcal{X}}, \theta_{\mathcal{Z}}) := k_{\mathcal{X}}(x, x'; \theta_{\mathcal{X}}) k_{\mathcal{Z}}(z, z'; \theta_{\mathcal{Z}})$. In this scenario, we can let $x \in \mathcal{X}$ to be the original unaltered example inputs, while $z = f(x; w) \in \mathcal{Z}$ be the output of the last hidden layer of a neural network, where we use $w$ to collectively denote all the weight and bias parameters of the neural network. In this way, $k_{\mathcal{X}}$ is a shallow kernel allowing a direct connection from input to output, while $k_{\mathcal{Z}}$ is a deep kernel performing multiple layers of feature extraction from the input before it is connected to the output. Again, because hyperparameter training is very general in the kernel embedding classification framework, it should be possible to jointly learn the kernel hyperparameters $\theta_{\mathcal{X}}, \theta_{\mathcal{Z}}$, the neural network weights and biases $w$, and the regularisation parameter $\lambda$.

		\item \textbf{Connection to other kernel models.} It should not be too surprising if we can find many connections or even equivalences to other kernel techniques. For example, if we look at the form of our decision probability estimator, it is also the same as the mean prediction of a Gaussian process regression, except we replace the real-valued targets in the regression case with the one-hot encoded class targets for our classification task. Of course, the main difference thereafter is how we train the two models. We turned to complexity based training partly because, unlike a Gaussian process, it is very difficult to find the marginal likelihood for a kernel embedding, and this has worked out well. However, future work can look into the direction of actually finding a way to compute or approximate the marginal likelihood for the kernel embedding classifier, making the link between Gaussian processes and kernel embeddings even stronger.

		Another simpler connection may be the k-nearest-neighbour classifier. For any stationary and radially symmetric kernel like the Gaussian and Matern kernels, shorter length scales usually produces a nearest-neighbour effect on the inference of kernel embedding classifiers. Of course, this is suboptimal, and the complexity based training developed in this paper would know better to not learn such a length scale. However, this link would illustrate the purpose and effectiveness of a complexity based training scheme for kernel methods.

		\item \textbf{Sampling and Generative Models.} While the kernel embedding classifier is trained as a discriminative model, at its core it is simply just a condition embedding of $\mathbb{P}_{Y | X}$. As such, we can do full probabilistic inference entirely in reproducing kernel Hilbert spaces and obtain the Hilbert space embeddings of $\mathbb{P}_{X | Y}$, similar to what we have touched upon in \cref{sec:mode_reconstruction}, or even simply of the marginals $\mathbb{P}_{X}$ and $\mathbb{P}_{Y}$. If we can recover these distributions as densities ($\mathbb{P}_{Y}$ would correspond to a probability mass function over a finite and discrete space $\mathbb{N}_{m}$ which is identical to the mean embedding already, and so this step would be trivial for $\mathbb{P}_{Y}$), then we would be able to model our data in a fully generative manner. In fact, in \cref{sec:mode_reconstruction} we have have already done so indirectly through reversing the embedding. Of course, this would require us to solve the pre-image problem of kernel embeddings, for which no general methodology exists yet besides a few heuristics with various assumptions. Nevertheless, assuming we can recover the densities well enough, we can then generate samples from those distributions. Alternatively, if we can instead sample from those distributions \textit{without} finding the pre-image, but by directly using the mean embeddings instead, that would make the kernel embedding classifier very useful as a generative modelling tool.

		\item \textbf{Target Label Kernel.} In this paper, we proposed to place a Kronecker delta kernel $l = \delta$ over the label space $\mathcal{Y} = \mathbb{N}_{m}$ as it is the simplest kernel over a discrete and finite domain. However, it is possible to place other kernels over the label space. A simple kernel is to have a `generalised Kronecker delta kernel' that has unit similarity when labels are the same, but a small, positive yet non-zero similarity when labels are different. If we set these cross similarity to be the same across all non-identical pairs of labels, then it is straight forward to show that the inference algorithm we developed in this paper stays the same. However, if we allow them to vary amongst each other as kernel parameters (between the range $(0, 1)$, in order to stay positive definite), then we suspect that these cross similarity coefficients would act as correlation factors between classes. The training algorithm we developed here does not prevent the target label kernel to have its own hyperparameters. As such, we should be able to learn the correlation effects between the classes effectively using the same training scheme. We suspect that this would make the empirical decision probabilities converge to a valid probability distribution faster. However, we also suspect that the training may become even more non-convex and optimisation to become more difficult.

		These factors may even give rise to new interpretable insights in terms of how different classes may be more related to each other. For example, in an image recognition task of animals, it may learn that, the class `horse' and 'pony' are much more similar than `horse' and `elephant' from the input features, and start to use the output correlations to focus on inferring about them as a group instead.
		\end{itemize}

\small
\bibliographystyle{apalike}
\bibliography{kernel_embedding}

\newpage
\appendix

\section{Theorems and Derivations}
\label{app:theorems_derivations}

	In this section we provide a few theorems, lemmas, and derivations which proves the convergence properties of our kernel embedding classifier.

	Because the label space $\mathcal{Y} = \mathbb{N}_{m}$ is discrete and finite, \textit{bounded} functions $g \in \mathcal{H}_{\delta}$ in the RKHS are actually equivalent to their vector representations $\bvec{g} := \{g(c)\}_{c = 1}^{m}$, because one can always write $g = \sum_{c = 1}^{m} g(c) \delta(c, \cdot)$. This immediately implies that inner products in this space are simply the usual dot products in a Euclidean space, since

	\begin{equation}
	\begin{aligned}
			\langle g_{1}, g_{2} \rangle_{\mathcal{H}_{\delta}} &= \bigg\langle \sum_{c = 1}^{m} g_{1}(c) \delta(c, \cdot), \sum_{c' = 1}^{m} g_{2}(c') \delta(c', \cdot)  \bigg\rangle_{\mathcal{H}_{\delta}} \\
			&= \sum_{c = 1}^{m} \sum_{c' = 1}^{m} g_{1}(c) g_{2}(c') \langle \delta(c, \cdot), \delta(c', \cdot) \rangle_{\mathcal{H}_{\delta}} \\
			&= \sum_{c = 1}^{m} g_{1}(c) g_{2}(c) \\
			&= \bvec{g}_{1} \cdot \bvec{g}_{2}.
	\end{aligned}
	\end{equation}

	Consequently, the RKHS norm for bounded functions $g \in \mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of its vector representation $\bvec{g}$,

	\begin{equation}
		\lVert g \rVert_{\mathcal{H}_{\delta}} = \lVert \bvec{g} \rVert_{\ell_{2}}.
	\label{eq:rkhs_norm_is_l2_norm}
	\end{equation}

	\begin{claim}[Decision Probabilities are Conditional Embeddings]
	\label{thm:probability_is_embedding}

		The decision probability for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,

		\begin{equation}
			p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mu_{Y | X = x}(c).
		\end{equation}

		\begin{proof} Since indicator functions are the canonical features of the label RKHS $\mathcal{H}_{\delta}$, we employ the fact that expectations of indicator functions are probabilities to prove this claim,

			\begin{equation}
			\begin{aligned}
				\mu_{Y | X = x}(c) :=& \mathbb{E}[l(Y, c) | X = x ]= \mathbb{E}[\delta(Y, c) | X = x] \\
				=& \mathbb{E}[\mathbb{1}_{c}(Y) | X = x] = \mathbb{P}[Y \in \{c\} | X = x] \\
				=& \mathbb{P}[Y = c | X = x] := p_{c}(x).
			\end{aligned}
			\end{equation}
		\end{proof}

	\end{claim}

	\begin{claim}[Empirical Decision Probabilities are Empirical Conditional Embeddings]
	\label{thm:empirical_probability_is_embedding}

		The empirical decision probability \eqref{eq:empirical_decision_probability} for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the empirical conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,

		\begin{equation}
			\hat{p}_{c}(x) = \hat{\mu}_{Y | X = x}(c).
		\end{equation}

		\begin{proof}

			Let the canonical feature maps of $\mathcal{X}$ and $\mathcal{Y}$ be $\phi(x) = k(x, \cdot)$ and $\psi(y) = l(y, \cdot) = \delta(y, \cdot)$, then the empirical conditional embedding is defined by

			\begin{equation}
				\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} \phi(x)
			\end{equation}

			By the reproducing property, the evaluation of $\hat{\mu}_{Y | X = x} \in \mathcal{H}_{l}$ is given by a dot product,

			\begin{equation}
			\begin{aligned}
				\hat{\mu}_{Y | X = x}(c) &= \langle l(c, \cdot), \hat{\mu}_{Y | X = x} \rangle \\
				&= \langle \psi(c), \hat{\mu}_{Y | X = x} \rangle \\
				&= \psi(c)^{T} \hat{\mu}_{Y | X = x} \\
				&= \psi(c)^{T} \hat{\mathcal{U}}_{Y | X} \phi(x) \\
				&= \psi(c)^{T} \Psi (K + n \lambda I)^{-1} \Phi^{T} \phi(x) \\
				&= \bvec{l}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x} \\
			\end{aligned}
			\end{equation}

			where $\bvec{l}_{c} := \{l(y_{i}, c)\}_{i = 1}^{n}$ and $\bvec{k}_{x} := \{k(x_{i}, x)\}_{i = 1}^{n}$. While the notation $\bvec{l}_{y}$ is usually avoided due do its similarity to $\bvec{1}_{c}$, in this context they happen to represent equal quantities,

			\begin{equation}
				\bvec{l}_{c} := \{l(y_{i}, c)\}_{i = 1}^{n} = \{\delta(y_{i}, c)\}_{i = 1}^{n} = \{\mathbb{1}_{c}(y_{i})\}_{i = 1}^{n} =: \bvec{1}_{c}.
			\end{equation}

			The claim then immediately follows by the definition of our decision probability estimator,

			\begin{equation}
				\hat{\mu}_{Y | X = x}(c) = \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x} =: \hat{p}_{c}(x).
			\end{equation}
		\end{proof}

	\end{claim}

	\begin{lemma}[Pointwise Uniform Convergence of Empirical Decision Probability Vector Function in $\ell_{1}$ and $\ell_{2}$]
	\label{thm:probability_vector_convergence}

		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability vector function $\hat{\bvec{p}} : \mathcal{X} \to \mathbb{R}^{m}$ \eqref{eq:empirical_decision_probability_vector} converges pointwise and uniformly to the true decision probability vector function $\bvec{p} : \mathcal{X} \to [0, 1]^{m}$ in the $\ell_{2}$-norm, where $\bvec{p}(x) := \{p_{c}(x)\}_{c = 1}^{m}$, at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.

		\begin{proof}
			For convergence in $\ell_{1}$, we simply extend \cref{thm:probability_convergence}, which proved that each entry of $\hat{\bvec{p}}(x)$ converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$. The $\ell_{1}$-norm distance is simply

			\begin{equation}
				{\lVert \hat{\bvec{p}}(x) - \bvec{p}(x) \rVert}_{\ell_{1}} = \sum_{c = 1}^{m} | \hat{p}_{c}(x) - p_{c}(x) |.
			\end{equation}

			It is straight forward to show if each term in the sum converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the sum, which proves the convergence in $\ell_{1}$.

			For convergence in $\ell_{2}$, we show that the $\ell_{2}$-norm of the difference between the true and empirical decision probability vector functions is the same as the RKHS norm of the difference between the true and empirical conditional embedding, which converges to zero at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $x \in \mathcal{X}$ and $c \in \mathcal{Y} = \mathbb{N}_{m}$ \citep{song2009hilbert}. To this end, we use \cref{thm:probability_is_embedding} and \cref{thm:empirical_probability_is_embedding} and write

			\begin{equation}
			\begin{aligned}
				{\lVert \hat{\bvec{p}}(x)  - \bvec{p}(x) \rVert}_{\ell_{2}} &= {\lVert \{ \hat{p}_{c}(x) \}_{c = 1}^{m} - \{ p_{c}(x) \}_{c = 1}^{m} \rVert}_{\ell_{2}} \\
				&= {\lVert \{ \hat{p}_{c}(x) - p_{c}(x) \}_{c = 1}^{m} \rVert}_{\ell_{2}} \\
				&= {\lVert \{ \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c)\}_{c = 1}^{m} \rVert}_{\ell_{2}} \\
				&= {\lVert \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}\rVert}_{\mathcal{H}_{\delta}},
			\end{aligned}
			\end{equation}

			where the last equality comes from \eqref{eq:rkhs_norm_is_l2_norm} and the fact that the empirical and true conditional embeddings are bounded functions in the RKHS. Since this is true for all $x \in \mathcal{X}$, the convergence is pointwise uniform.
		\end{proof}

	\end{lemma}

\section{Design Choices}
\label{app:design_choices}

	In this section we discuss the various design choices we make in formulating the kernel embedding classifier.

	\subsection{Decision Probabilities: Why clip-normalise and not softmax-normalise or softplus-normalise?}

		For \eqref{eq:probability_clip_normalise}...

		\note{\textbf{Unpolished.}} The simple reason is that it works better. The more theoretical reason is that our raw probability estimates usually produces predictions with low cross entropy loss. This means that it assigns high probability for the correct class and low probability to other classes. Because the decision probability estimates are not guaranteed to be strictly positive, the lower probabilities for those other classes can sometimes be slightly negative, and clip-normalisation would simply make them zero, as that would be closer to what the kernel embedding classifier is trying to express: it is so unlikely it has even assigned it negative probabilities, so it might as well be zero. When normalising after clipping, the zeroed-out probabilities do not come into play and the high probabilities get to keep their high values. Softmax and softplus operations would instead assign small positive probabilities to those slightly negative instances. When normalising after this, because the unlikely classes has taken up some probabilities, the class with high probabilities will have their high probabilities slightly reduces, making the cross entropy loss slightly higher and the predictions less confident.

	\subsection{Information Entropy: Why define information gain to be zero despite being infinitely surprised?}

		For \eqref{eq:empirical_information}...

		\note{\textbf{Unpolished.}} This is really for numerical and experimental reasons. The information entropy map obtained this way are just simply much smoother and intuitive. The alternative is to first clip the raw probability predictions at some very small tolerance, such as $\epsilon = 10^{-15}$, before we pass it through the log, as what is done in many information or entropy based computations, such as the cross entropy computation implemented in \texttt{scipy}. When we tried this, we saw that this produces an unnecessarily non-smooth estimate of the information entropy map. Furthermore, by adjusting the tolerance $\epsilon$ slightly to other small numbers, such as $10^{-10}$ or $10^{-20}$, the information entropy map changes in where the non-smoothness occurs and in what magnitude. This was simply too ugly for us to accept. Instead, defining the information gain to zero despite being infinitely surprised gave us very smooth estimates that is very close to both the map we expect and the map we obtain from computing the information entropy directly from the clip-normalised decision probabilities.

	\subsection{Information Entropy: Why clip from below at zero?}

		For \eqref{eq:empirical_information_entropy}...

		\note{\textbf{Unpolished.}} Similar to the reason for clip-normalising decision probabilities, if the inference algorithm has produces an information entropy that is slightly less than zero, this just means that it is very confident at those regions. As such, in the limit, we expect that this would converge back to zero. Therefore, for finite data, we clip it from below at zero to indicate what the current data suggests the true information entropy should be when we have infinite data.

\end{document}

### 2017-04-16 kernel_embedding_classifier.tex
Add draft for sections 2, 3, 4, 5, 8, 9

@@
 
+		\note{Note: The proof can just stop right here really.
+Every time we have some estimator error being upper bounded by some constant (in this case, $1$) times the RKHS norm of the difference between the empirical and true conditional embeddings, we can simply say that if the right hand side goes to zero at a stochastic rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the left hand side.
+The constant needs to be independent of $n \in \mathbb{N}_{+}$ for this to be true.
+If the constant is independent of $x \in \mathcal{X}$, then the convergence is uniform.
+If not, then the convergence is non-uniform.}
+
 %		Consequently, $| \hat{p}_{c}(x) - p_{c}(x) | \leq \big\| \hat{\mu}_{Y | X = x}^{(n)} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}}$ for all $x \in \mathcal{X}$, where the right hand side of which approaches zero stochastically at rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, so that $\hat{p}_{c}$ converges pointwise to $p_{c}$ at least at this rate.
@@
 
-	\subsection{Stochastic Gradient Descent}
+	\subsection{Mini-Batch Stochastic Gradient Descent}
 	\label{sec:stochastic_gradient_descent}
@@
 		With standard gradient descent, the time complexity of each training iteration is dominated by the Cholesky decomposition of the regularised gram matrix $K_{\theta} + n \lambda I$ of size $n \times n$, which has a time complexity of $O(n^{3})$.
-In order to scale the hyperparameter training of kernel embedding classifiers to large dataset, we propose to optimise the complexity objective with stochastic gradient descent.
+In order to scale the hyperparameter training of kernel embedding classifiers to large datasets, we propose to optimise the complexity objective with stochastic gradient descent.
+
+		We begin by selecting a mini-batch size $n_{b} << n$ that is much smaller than $n$. The objective \eqref{eq:trace_norm_optimisation} is then computed only for the mini-batch
 
@@
 		\begin{proof}
-			For convergence in $\ell_{1}$, we simply extend \cref{thm:probability_convergence}, which proved that each entry of $\hat{\bvec{p}}(x)$ converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-The $\ell_{1}$-norm distance is simply
+			For convergence in $\ell_{1}$, we simply extend \cref{thm:probability_convergence}, which proved that each entry of $\hat{\bvec{p}}(x)$ converges pointwise uniformly at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ to the corresponding entry of $\bvec{p}(x)$.
+The $\ell_{1}$-norm of the difference is simply
 
@@
 
-			It is straight forward to show if each term in the sum converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the sum, which proves the convergence in $\ell_{1}$.
+			Since each term in the sum converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the sum, which proves the pointwise uniform convergence in $\ell_{1}$.
 
@@
 			where the last equality comes from \eqref{eq:rkhs_norm_is_l2_norm} and the fact that the empirical and true conditional embeddings are bounded functions in the RKHS.
-Since this is true for all $x \in \mathcal{X}$, the convergence is pointwise uniform.
+Since this is true for all $x \in \mathcal{X}$ and the rate does not depend on $x \in \mathcal{X}$, the convergence is pointwise uniform.
 		\end{proof}

### 2017-04-16 kernel_embedding_classifier.tex
Edit proofs to use a general convergence theorem

@@
 \newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}{Corollary}[theorem]
-\newtheorem{lemma}{Lemma}[theorem]
-\newtheorem{claim}{Claim}[theorem]
+\newtheorem{corollary}{Corollary}[section]
+\newtheorem{lemma}{Lemma}[section]
+\newtheorem{claim}{Claim}[section]
 
@@
 	We proceed to show that the empirical decision probabilities given by \eqref{eq:empirical_decision_probability} is a consistent estimator for the actual decision probabilities as the dataset increases.
-
-	\begin{theorem}[Pointwise Uniform Convergence of Empirical Decision Probability Function]
-	\label{thm:probability_convergence}
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges pointwise and uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-
-	\begin{proof}
-		Consider the pointwise absolute difference between the decision probability and its empirical estimate,
-
-		\begin{equation}
-		\begin{aligned}
-			| \hat{p}_{c}(x) - p_{c}(x) | &= | \langle \hat{\mu}_{Y | X = x}, \mathbb{1}_{c} \rangle - \langle \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
-			&= | \langle \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
-			&\leq \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}},
-		\end{aligned}
-		\end{equation}
-
-		where the last inequality follows from the Cauchy–Schwarz inequality in a Hilbert space.
-
-		From \eqref{eq:indicator_function}, since $\mathbb{1}_{c} = \delta(c, \cdot)$ and using the fact that $\delta$ is a reproducing kernel, we have that for all $c \in \mathcal{Y} = \mathbb{N}_{m}$,
-
-		\begin{equation}
-		\begin{aligned}
-			\big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}}^{2} = \langle \mathbb{1}_{c}, \mathbb{1}_{c} \rangle = \langle \delta(c, \cdot), \delta(c, \cdot) \rangle = \delta(c, c) = 1.
-		\end{aligned}
-		\end{equation}
-
-		\note{Note: The proof can just stop right here really.
-Every time we have some estimator error being upper bounded by some constant (in this case, $1$) times the RKHS norm of the difference between the empirical and true conditional embeddings, we can simply say that if the right hand side goes to zero at a stochastic rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the left hand side.
-The constant needs to be independent of $n \in \mathbb{N}_{+}$ for this to be true.
-If the constant is independent of $x \in \mathcal{X}$, then the convergence is uniform.
-If not, then the convergence is non-uniform.}
-
-%		Consequently, $| \hat{p}_{c}(x) - p_{c}(x) | \leq \big\| \hat{\mu}_{Y | X = x}^{(n)} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}}$ for all $x \in \mathcal{X}$, where the right hand side of which approaches zero stochastically at rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, so that $\hat{p}_{c}$ converges pointwise to $p_{c}$ at least at this rate.
-The convergence rate does not depend on $x \in \mathcal{X}$, so this (stochastic) convergence is pointwise uniform.
-
-		Consequently, for all $x \in \mathcal{X}$ and $c \in \mathcal{Y}$, we have
-
-		\begin{equation}
-			| \hat{p}_{c}(x) - p_{c}(x) | \leq \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}}.
-		\label{eq:uniform_convergence}
-		\end{equation}
-
-		This is true for all possible datasets represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$.
-Thus, for any constant $C$, the implication statement $\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C \implies | \hat{p}_{c}(x) - p_{c}(x) | \leq C$ holds for all possible data observation events $\omega \in \Omega$.
-Writing this explicitly in event space translates this to a probability statement,
-
-		\begin{equation}
-		\begin{aligned}
-			\{\omega \in \Omega : \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C\} &\subseteq \{\omega \in \Omega : | \hat{p}_{c}(x) - p_{c}(x) | \leq C\} \\
-			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C\Big] &\leq \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | \leq C \Big].
-		\label{eq:probability_statement}
-		\end{aligned}
-		\end{equation}
-
-		Since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is valid.
-By letting $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ in \eqref{eq:probability_statement}, we immediately have that the probability inequality in statement \eqref{eq:probability_statement} is also true if we replace $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|$ with $| \hat{p}_{c}(x) - p_{c}(x) |$, % the RKHS norm between the empirical and true embeddings to the absolute difference between the empirical decision probability and the true decision probability,
-
-		\begin{equation}
-		\begin{aligned}
-			\mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
-			\implies 1 - \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
-			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
-			\implies \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
-			\implies 1 - \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
-			\implies \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon.
-		\end{aligned}	
-		\end{equation}
-
-		In other words, the function $\hat{p}_{c}$ stochastically converges pointwise to $p_{c} := \mathbb{P}[Y = c | X = \cdot]$ with a rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-The convergence rate does not depend on $x \in \mathcal{X}$ nor $c \in \mathbb{N}_{m}$, so this stochastic convergence is pointwise uniform in its domain $\mathcal{X}$ across all label classes.
-
-	\end{proof}
-	\end{theorem}
-
-	\note{Note: The above proof is for pointwise uniform convergence over all $x \in \mathcal{X}$.
-From what the experiments seem to suggest, for stationary zero-centred kernels, I believe that we can actually do better than this convergence rate for areas of high data density.
-Basically, at the subspace of $\mathcal{X}$ where we have observed our data, the convergence rate should be higher, because the kernel effects are stronger at these regions.
-The worse case convergence rate described in the theorem would be a tight lower bound for regions in $\mathcal{X}$ where we do not have a lot of data, where the kernel effects have decayed and most empirical probabilities are near zero and further from summing up to one.}
 
@@
 
-	In this section we provide a few theorems, lemmas, and derivations which proves the convergence properties of our kernel embedding classifier.
+	In this section we provide a few theorems, lemmas, and derivations which proves the convergence properties of estimators derived from our kernel embedding classifier.
 
-	Because the label space $\mathcal{Y} = \mathbb{N}_{m}$ is discrete and finite, \textit{bounded} functions $g \in \mathcal{H}_{\delta}$ in the RKHS are actually equivalent to their vector representations $\bvec{g} := \{g(c)\}_{c = 1}^{m}$, because one can always write $g = \sum_{c = 1}^{m} g(c) \delta(c, \cdot)$.
-This immediately implies that inner products in this space are simply the usual dot products in a Euclidean space, since
+	We consider the case in which a dataset, represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$, is collected in a \textit{iid} fashion from some distribution $\mathbb{P}_{X Y}$.
+That is $\{X_{i}, Y_{i}\} \sim \mathbb{P}_{X Y}$ for all $i \in \mathbb{N}_{n}$ and each observed sample is independent from each other.
+Suppose we have an estimator function $\hat{f}^{(n)} : \mathcal{X} \to \mathbb{R}$ which is to estimate some target function  $f : \mathcal{X} \to \mathbb{R}$, usually but not necessarily derived from $\mathbb{P}_{Y |X }$, empirically using the collected dataset $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of size $n \in \mathbb{N}_{+}$.
+Here, we use the superscript $(n)$ to denote the estimator's dependence on the dataset.
+From this point on, we drop this superscript to avoid cluttered notation.
+However, one should keep in mind that $\hat{f}$ is estimated using the dataset $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ and is thus random over the possible data observation events $\omega \in \Omega$.
+We would like to provide a sense of the stochastic convergence of $\hat{f}$ to $f$ by providing an upper bound of their absolute pointwise difference $| \hat{f}(x) - f(x) |$ which we know convergences to zero at some stochastic rate.
+Since the kernel embedding classifier is based on conditional embeddings, this upper bound will be provided by the RKHS norm of the error between empirical and true conditional embeddings.
+
+	\begin{theorem}[Pointwise and Uniform Convergence of Estimators based on Conditional Embeddings]
+		\label{thm:pointwise_uniform_convergence}
+		Suppose that $k(x, \cdot)$ is in the image of $C_{XX}$ and that there exists $0 \leq \gamma(x) < \infty$ such that for some estimator function $\hat{f} : \mathcal{X} \to \mathbb{R}$ and target function  $f : \mathcal{X} \to \mathbb{R}$,
+
+		\begin{equation}
+			| \hat{f}(x) - f(x) | \leq \gamma(x) \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}}, \forall x \in \mathcal{X},
+		\label{eq:estimator_error_bound}
+		\end{equation}
+
+		then the estimator $\hat{f}$ converges pointwise to the target $f$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+Further, if $\gamma(x) = \gamma$ is independent of $x \in \mathcal{X}$, then this convergence is uniform.
+
+		\begin{proof}
+
+			Suppose that there exists $0 \leq \gamma(x) < \infty$ such that \eqref{eq:estimator_error_bound} is satisfied.
+Note that this statement holds for all possible datasets represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$.
+Thus, for any constant $C$, the implication statement $\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C \implies | \hat{f}(x) - f(x) | \leq C \gamma(x)$ holds for all possible data observation events $\omega \in \Omega$.
+Writing this explicitly in event space translates this to a probability statement,
 
@@
 			\begin{aligned}
-			\langle g_{1}, g_{2} \rangle_{\mathcal{H}_{\delta}} &= \bigg\langle \sum_{c = 1}^{m} g_{1}(c) \delta(c, \cdot), \sum_{c' = 1}^{m} g_{2}(c') \delta(c', \cdot)  \bigg\rangle_{\mathcal{H}_{\delta}} \\
-			&= \sum_{c = 1}^{m} \sum_{c' = 1}^{m} g_{1}(c) g_{2}(c') \langle \delta(c, \cdot), \delta(c', \cdot) \rangle_{\mathcal{H}_{\delta}} \\
-			&= \sum_{c = 1}^{m} g_{1}(c) g_{2}(c) \\
-			&= \bvec{g}_{1} \cdot \bvec{g}_{2}.
+				\{\omega \in \Omega : \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq C\} &\subseteq \{\omega \in \Omega : | \hat{f}(x) - f(x) | \leq C \gamma(x)\} \\
+				\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq C\Big] &\leq \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq C \gamma(x) \Big].
+			\label{eq:probability_statement}
 			\end{aligned}
@@
 
-	Consequently, the RKHS norm for bounded functions $g \in \mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of its vector representation $\bvec{g}$,
+			Since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is valid.
+By letting $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ in \eqref{eq:probability_statement}, we immediately have that the probability inequality in statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is also true if we replace $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|$ with $| \hat{f}(x) - f(x) |$ and $M_{\epsilon}$ with $\gamma(x) M_{\epsilon}$,
 
 			\begin{equation}
-		\lVert g \rVert_{\mathcal{H}_{\delta}} = \lVert \bvec{g} \rVert_{\ell_{2}}.
-	\label{eq:rkhs_norm_is_l2_norm}
+			\begin{aligned}
+			\mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
+			\implies 1 - \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
+			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
+			\implies \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
+			\implies 1 - \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
+			\implies \mathbb{P}\Big[| \hat{f}(x) - f(x) | > \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon.
+			\end{aligned}	
 			\end{equation}
+
+			where we employed statement \eqref{eq:probability_statement} between the third and fourth line for $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+Therefore, since $M_{\epsilon}$ is arbitrary, define $\tilde{M}_{\epsilon}(x) := \gamma(x) M_{\epsilon}$ so that, with the above result, the statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} implies the following,
+
+			\begin{equation}
+				\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists \tilde{M}_{\epsilon}(x) > 0 \quad s.t.
+\quad \mathbb{P}\Big[\big| \hat{f}(x) - f(x) \big| > \tilde{M}_{\epsilon}(x) \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
+			\end{equation}
+
+			In other words, the function $\hat{f}$ stochastically converges pointwise to $f$ with a rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+The convergence is pointwise as the constant $\tilde{M}_{\epsilon}(x)$ may be different for each point $x \in \mathcal{X}$.
+If $\gamma(x) = \gamma$ such that $\tilde{M}_{\epsilon}(x) = \tilde{M}_{\epsilon}$ does not depend on $x \in \mathcal{X}$, then this stochastic convergence is uniform in its domain $\mathcal{X}$.
+		\end{proof}
+
+	\end{theorem}
+	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
+		\label{thm:probability_convergence}
+		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+
+		\begin{proof}
+			Consider the pointwise absolute difference between the decision probability and its empirical estimate,
+
+			\begin{equation}
+			\begin{aligned}
+				| \hat{p}_{c}(x) - p_{c}(x) | &= | \langle \hat{\mu}_{Y | X = x}, \mathbb{1}_{c} \rangle - \langle \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
+				&= | \langle \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
+				&\leq \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}},
+			\label{eq:decision_probability_error_upper_bound}
+			\end{aligned}
+			\end{equation}
+
+			where the last inequality follows from the Cauchy–Schwarz inequality in a Hilbert space.
+
+			From \eqref{eq:indicator_function}, since $\mathbb{1}_{c} = \delta(c, \cdot)$ and using the fact that $\delta$ is a reproducing kernel, we have that for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+
+			\begin{equation}
+			\begin{aligned}
+				\big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}}^{2} = \langle \mathbb{1}_{c}, \mathbb{1}_{c} \rangle = \langle \delta(c, \cdot), \delta(c, \cdot) \rangle = \delta(c, c) = 1.
+			\label{eq:indicator_rkhs_norm}
+			\end{aligned}
+			\end{equation}
+
+			Therefore, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, $\hat{p}_{c}$ converges uniformly to $p_{c}$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$
+
+			%		Consequently, $| \hat{p}_{c}(x) - p_{c}(x) | \leq \big\| \hat{\mu}_{Y | X = x}^{(n)} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}}$ for all $x \in \mathcal{X}$, where the right hand side of which approaches zero stochastically at rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, so that $\hat{p}_{c}$ converges pointwise to $p_{c}$ at least at this rate.
+The convergence rate does not depend on $x \in \mathcal{X}$, so this (stochastic) convergence is pointwise uniform.
+
+%			Consequently, for all $x \in \mathcal{X}$ and $c \in \mathcal{Y}$, we have 
+%			
+%			\begin{equation}
+%				| \hat{p}_{c}(x) - p_{c}(x) | \leq \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}}.
+%			\label{eq:uniform_convergence}
+%			\end{equation}
+%			
+%			This is true for all possible datasets represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$.
+Thus, for any constant $C$, the implication statement $\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C \implies | \hat{p}_{c}(x) - p_{c}(x) | \leq C$ holds for all possible data observation events $\omega \in \Omega$.
+Writing this explicitly in event space translates this to a probability statement,
+%			
+%			\begin{equation}
+%			\begin{aligned}
+%			\{\omega \in \Omega : \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C\} &\subseteq \{\omega \in \Omega : | \hat{p}_{c}(x) - p_{c}(x) | \leq C\} \\
+%			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C\Big] &\leq \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | \leq C \Big].
+%			\label{eq:probability_statement}
+%			\end{aligned}
+%			\end{equation}
+%			
+%			Since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is valid.
+By letting $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ in \eqref{eq:probability_statement}, we immediately have that the probability inequality in statement \eqref{eq:probability_statement} is also true if we replace $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|$ with $| \hat{p}_{c}(x) - p_{c}(x) |$, % the RKHS norm between the empirical and true embeddings to the absolute difference between the empirical decision probability and the true decision probability,
+%			
+%			\begin{equation}
+%			\begin{aligned}
+%			\mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
+%			\implies 1 - \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
+%			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
+%			\implies \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
+%			\implies 1 - \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
+%			\implies \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon.
+%			\end{aligned}	
+%			\end{equation}
+%			
+%			In other words, the function $\hat{p}_{c}$ stochastically converges pointwise to $p_{c} := \mathbb{P}[Y = c | X = \cdot]$ with a rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+The convergence rate does not depend on $x \in \mathcal{X}$ nor $c \in \mathbb{N}_{m}$, so this stochastic convergence is pointwise uniform in its domain $\mathcal{X}$ across all label classes.
+
+		\end{proof}
+	\end{theorem}
+
+	\note{Note: The above proof is for uniform convergence over all $x \in \mathcal{X}$.
+From what the experiments seem to suggest, for stationary zero-centred kernels, I believe that we can actually do better than this convergence rate for areas of high data density.
+Basically, at the subspace of $\mathcal{X}$ where we have observed our data, the convergence rate should be higher, because the kernel effects are stronger at these regions.
+The worse case convergence rate described in the theorem would be a tight lower bound for regions in $\mathcal{X}$ where we do not have a lot of data, where the kernel effects have decayed and most empirical probabilities are near zero and further from summing up to one.}
 
@@
 				&= \psi(c)^{T} \Psi (K + n \lambda I)^{-1} \Phi^{T} \phi(x) \\
-				&= \bvec{l}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x} \\
+				&= \bvec{l}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x}, \\
 			\end{aligned}
@@
 			where $\bvec{l}_{c} := \{l(y_{i}, c)\}_{i = 1}^{n}$ and $\bvec{k}_{x} := \{k(x_{i}, x)\}_{i = 1}^{n}$.
-While the notation $\bvec{l}_{y}$ is usually avoided due do its similarity to $\bvec{1}_{c}$, in this context they happen to represent equal quantities,
+While the notation $\bvec{l}_{c}$ is usually avoided due do its similarity to $\bvec{1}_{c}$, in this context they happen to represent equal quantities,
 
@@
 
-	\begin{lemma}[Pointwise Uniform Convergence of Empirical Decision Probability Vector Function in $\ell_{1}$ and $\ell_{2}$]
+	Because the label space $\mathcal{Y} = \mathbb{N}_{m}$ is discrete and finite, \textit{bounded} functions $g \in \mathcal{H}_{\delta}$ in the RKHS are actually equivalent to their vector representations $\bvec{g} := \{g(c)\}_{c = 1}^{m}$, because one can always write $g = \sum_{c = 1}^{m} g(c) \delta(c, \cdot)$.
+This immediately implies that inner products in this space are simply the usual dot products in a Euclidean space, since
+
+	\begin{equation}
+	\begin{aligned}
+	\langle g_{1}, g_{2} \rangle_{\mathcal{H}_{\delta}} &= \bigg\langle \sum_{c = 1}^{m} g_{1}(c) \delta(c, \cdot), \sum_{c' = 1}^{m} g_{2}(c') \delta(c', \cdot)  \bigg\rangle_{\mathcal{H}_{\delta}} \\
+	&= \sum_{c = 1}^{m} \sum_{c' = 1}^{m} g_{1}(c) g_{2}(c') \langle \delta(c, \cdot), \delta(c', \cdot) \rangle_{\mathcal{H}_{\delta}} \\
+	&= \sum_{c = 1}^{m} g_{1}(c) g_{2}(c) \\
+	&= \bvec{g}_{1} \cdot \bvec{g}_{2}.
+	\end{aligned}
+	\end{equation}
+
+	Consequently, the RKHS norm for bounded functions $g \in \mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of its vector representation $\bvec{g}$,
+
+	\begin{equation}
+	\lVert g \rVert_{\mathcal{H}_{\delta}} = \lVert \bvec{g} \rVert_{\ell_{2}}.
+	\label{eq:rkhs_norm_is_l2_norm}
+	\end{equation}
+
+	\begin{lemma}[Uniform Convergence of Empirical Decision Probability Vector Function in $\ell_{1}$ and $\ell_{2}$]
 	\label{thm:probability_vector_convergence}
 
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability vector function $\hat{\bvec{p}} : \mathcal{X} \to \mathbb{R}^{m}$ \eqref{eq:empirical_decision_probability_vector} converges pointwise and uniformly to the true decision probability vector function $\bvec{p} : \mathcal{X} \to [0, 1]^{m}$ in the $\ell_{2}$-norm, where $\bvec{p}(x) := \{p_{c}(x)\}_{c = 1}^{m}$, at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability vector function $\hat{\bvec{p}} : \mathcal{X} \to \mathbb{R}^{m}$ \eqref{eq:empirical_decision_probability_vector} converges uniformly to the true decision probability vector function $\bvec{p} : \mathcal{X} \to [0, 1]^{m}$ in the $\ell_{2}$-norm, where $\bvec{p}(x) := \{p_{c}(x)\}_{c = 1}^{m}$, at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
 
@@
 			For convergence in $\ell_{1}$, we simply extend \cref{thm:probability_convergence}, which proved that each entry of $\hat{\bvec{p}}(x)$ converges pointwise uniformly at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ to the corresponding entry of $\bvec{p}(x)$.
-The $\ell_{1}$-norm of the difference is simply
+Since each entry converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the entire vector.
+More formally, from \eqref{eq:decision_probability_error_upper_bound} and \eqref{eq:indicator_rkhs_norm}, the $\ell_{1}$-norm of the difference can be bounded,
 
 			\begin{equation}
-				{\lVert \hat{\bvec{p}}(x) - \bvec{p}(x) \rVert}_{\ell_{1}} = \sum_{c = 1}^{m} | \hat{p}_{c}(x) - p_{c}(x) |.
+			\begin{aligned}
+				{\lVert \hat{\bvec{p}}(x) - \bvec{p}(x) \rVert}_{\ell_{1}} :=& \sum_{c = 1}^{m} | \hat{p}_{c}(x) - p_{c}(x) | \\
+				\leq& \sum_{c = 1}^{m} \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \\
+				=& m \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}}
+			\end{aligned}
 			\end{equation}
 
-			Since each term in the sum converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the sum, which proves the pointwise uniform convergence in $\ell_{1}$.
+			Therefore, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = m$ independent of $x \in \mathcal{X}$, we have uniform convergence in $\ell_{1}$ where we replace all instances of $| \hat{f}(x) - f(x) |$ in the proof of \cref{thm:pointwise_uniform_convergence} with ${\lVert \hat{\bvec{p}}(x) - \bvec{p}(x) \rVert}_{\ell_{1}}$.
 
@@
 			where the last equality comes from \eqref{eq:rkhs_norm_is_l2_norm} and the fact that the empirical and true conditional embeddings are bounded functions in the RKHS.
-Since this is true for all $x \in \mathcal{X}$ and the rate does not depend on $x \in \mathcal{X}$, the convergence is pointwise uniform.
+Again, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, we have uniform convergence in $\ell_{2}$.
 		\end{proof}

### 2017-04-16 kernel_embedding_classifier.tex
Add convergence proof for information entropy

@@
 \usepackage{cleveref}
+\usepackage{bm}
 \usepackage[dvipsnames]{xcolor}
@@
 
-	While the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ will converge to the true decision probability function  $p_{c} : \mathcal{X} \to [0, 1]$ in the limit, for finite $n$ and a given regulariser $\lambda > 0$, the stochasticity in the empirical estimates implies that these probabilities may not necessarily sum up to one, nor are they strictly resctricted to the range $[0, 1]$.
+	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
+		\label{thm:probability_convergence_copy}
+		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+
+		\begin{proof}
+			See \cref{thm:probability_convergence} of \cref{app:theorems_derivations}.
+		\end{proof}
+	\end{theorem}
+
+	While the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ will converge to the true decision probability function  $p_{c} : \mathcal{X} \to [0, 1]$ in the limit, for finite $n$ and a given regulariser $\lambda > 0$, the stochasticity in the empirical estimates implies that these probabilities may not necessarily sum up to one, nor are they strictly restricted to the range $[0, 1]$.
 However, they will usually be very close to the true predicted probabilities.
@@
 
-	\subsection{Cross Entropy and Kullback–Leibler Divergence}
+	\begin{theorem}[Uniform Convergence of Empirical Information Entropy Function]
+		\label{thm:entropy_convergence_copy}
+		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical information entropy function $\hat{h} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_information_entropy} converges uniformly to the true information entropy function $h : \mathcal{X} \to [0, \infty)$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+
+		\begin{proof}
+			See \cref{thm:entropy_convergence} in \cref{app:theorems_derivations}.
+		\end{proof}
+	\end{theorem}
+
+	\subsection{Cross Entropy and Kullback–Leibler Divergence between Input Instances}
 
@@
 	\end{theorem}
+
+	With \cref{thm:pointwise_uniform_convergence}, we can now show the convergence of various estimators based on the conditional embedding, as long as we can show that their estimator error is upper bounded by a multiple of the conditional embedding error in the RKHS norm.
+As such, we turn to the convergence of the empirical decision probability function \eqref{eq:empirical_decision_probability} below.
+
 	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
@@
 
+	Because the label space $\mathcal{Y} = \mathbb{N}_{m}$ is discrete and finite, \textit{bounded} functions $g \in \mathcal{H}_{\delta}$ in the RKHS are actually equivalent to their vector representations $\bvec{g} := \{g(c)\}_{c = 1}^{m}$, because one can always write $g = \sum_{c = 1}^{m} g(c) \delta(c, \cdot)$.
+This immediately implies that inner products in this space are simply the usual dot products in a Euclidean space, since
+
+	\begin{equation}
+	\begin{aligned}
+	\langle g_{1}, g_{2} \rangle_{\mathcal{H}_{\delta}} &= \bigg\langle \sum_{c = 1}^{m} g_{1}(c) \delta(c, \cdot), \sum_{c' = 1}^{m} g_{2}(c') \delta(c', \cdot)  \bigg\rangle_{\mathcal{H}_{\delta}} \\
+	&= \sum_{c = 1}^{m} \sum_{c' = 1}^{m} g_{1}(c) g_{2}(c') \langle \delta(c, \cdot), \delta(c', \cdot) \rangle_{\mathcal{H}_{\delta}} \\
+	&= \sum_{c = 1}^{m} g_{1}(c) g_{2}(c) \\
+	&= \bvec{g}_{1} \cdot \bvec{g}_{2}.
+	\end{aligned}
+	\end{equation}
+
+	Consequently, the RKHS norm for bounded functions $g \in \mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of its vector representation $\bvec{g}$,
+
+	\begin{equation}
+	\lVert g \rVert_{\mathcal{H}_{\delta}} = \lVert \bvec{g} \rVert_{\ell_{2}}.
+	\label{eq:rkhs_norm_is_l2_norm}
+	\end{equation}
+
+	A special and convenient result that arises due to this discrete and finite label space is that the decision probabilities and its empirical estimate are simply the conditional embeddings and its empirical estimate.
+
 	\begin{claim}[Decision Probabilities are Conditional Embeddings]
@@
 
-	Because the label space $\mathcal{Y} = \mathbb{N}_{m}$ is discrete and finite, \textit{bounded} functions $g \in \mathcal{H}_{\delta}$ in the RKHS are actually equivalent to their vector representations $\bvec{g} := \{g(c)\}_{c = 1}^{m}$, because one can always write $g = \sum_{c = 1}^{m} g(c) \delta(c, \cdot)$.
-This immediately implies that inner products in this space are simply the usual dot products in a Euclidean space, since
-
-	\begin{equation}
-	\begin{aligned}
-	\langle g_{1}, g_{2} \rangle_{\mathcal{H}_{\delta}} &= \bigg\langle \sum_{c = 1}^{m} g_{1}(c) \delta(c, \cdot), \sum_{c' = 1}^{m} g_{2}(c') \delta(c', \cdot)  \bigg\rangle_{\mathcal{H}_{\delta}} \\
-	&= \sum_{c = 1}^{m} \sum_{c' = 1}^{m} g_{1}(c) g_{2}(c') \langle \delta(c, \cdot), \delta(c', \cdot) \rangle_{\mathcal{H}_{\delta}} \\
-	&= \sum_{c = 1}^{m} g_{1}(c) g_{2}(c) \\
-	&= \bvec{g}_{1} \cdot \bvec{g}_{2}.
-	\end{aligned}
-	\end{equation}
-
-	Consequently, the RKHS norm for bounded functions $g \in \mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of its vector representation $\bvec{g}$,
-
-	\begin{equation}
-	\lVert g \rVert_{\mathcal{H}_{\delta}} = \lVert \bvec{g} \rVert_{\ell_{2}}.
-	\label{eq:rkhs_norm_is_l2_norm}
-	\end{equation}
+	Since we have identified the equivalence of decision probabilities and the conditional embedding, we can now also show that the empirical decision probability vector also converges to the true decision probability vector.
 
@@
 				&= {\lVert \{ \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c)\}_{c = 1}^{m} \rVert}_{\ell_{2}} \\
+				&= \| \hat{\bm{\mu}}_{Y | X = x} - \bm{\mu}_{Y | X = x}  \|_{\ell_{2}} \\
 				&= {\lVert \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}\rVert}_{\mathcal{H}_{\delta}},
@@
 		\end{proof}
-
 	\end{lemma}
+
+	In \cref{sec:information_entropy}, we proposed an estimator for the information entropy $h(x)$ for a prediction at $x \in \mathcal{X}$.
+Since this estimator is now based on the inner product between the empirical conditional embedding and another empirically estimate function, instead of between the empirical conditional embedding and a known function, it is not immediately clear that such an estimator converges.
+Nevertheless, intuition tells us that the inner product between two converging quantities should converge.
+We proceed to show that this intuition is correct.
+
+	\begin{theorem}[Uniform Convergence of Empirical Information Entropy Function]
+		\label{thm:entropy_convergence}
+		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical information entropy function $\hat{h} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_information_entropy} converges uniformly to the true information entropy function $h : \mathcal{X} \to [0, \infty)$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+
+		\begin{proof}
+			Since we are interested in the asymptotic properties of our estimators when $n \to \infty$, and we have proved that the empirical decision probabilities converges to the true probabilities (\cref{thm:probability_convergence}), the condition $\hat{p}_{c}(x) > 0$ holds for large $n$ such that we simply have $\hat{u}_{x}(c) = - \log{\hat{p}_{c}(x)}$.
+That is, the effects of clipping for the information estimate \eqref{eq:empirical_information} vanishes.
+
+			Consider the pointwise absolute difference between the empirical and true information entropy,
+
+			\begin{equation}
+			\begin{aligned}
+				| \hat{h}(x) - h(x) | &= | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
+				&= | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} + \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
+				&\leq | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | + | \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
+				&= | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} - u_{x} \rangle_{\mathcal{H}_{\delta}} | + | \langle \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
+				&\leq \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}} + \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| u_{x} \|_{\mathcal{H}_{\delta}},
+			\label{eq:information_entropy_bound}
+			\end{aligned}
+			\end{equation}
+
+			where the we used the triangle inequality and Cauchy–Schwarz inequality in a Hilbert space respectively.
+
+			Now, since $l = \delta$ is bounded, so is $\hat{\mu}_{Y | X = x}(c) = \sum_{i = 1}^{n} w_{i} \delta(y_{i}, c)$ for some embedding weights $w_{i}$ and all $c \in \mathbb{N}_{m}$, and thus its RKHS norm is finite.
+Similarly, assuming that $p_{c}(x)$ is never exactly zero, $u_{x}(c)$ is also finite for all $c \in \mathbb{N}_{m}$ and thus so is its RKHS norm.
+We already know that $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$ stochastically converges to zero at the rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ \citep{song2009hilbert}.
+Thus, it remains to bound $\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}}$ by a multiple of $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$.
+
+			To this end, we first use \cref{thm:probability_is_embedding} and \cref{thm:empirical_probability_is_embedding} and to express the theoretical and empirical information as the negative log of the embedding, so that it is explicitly written as a function of $c \in \mathcal{Y}$ in $\mathcal{H}_{\delta}$ indexed by $x \in \mathcal{X}$,
+
+			\begin{equation}
+			\begin{aligned}
+				u_{x}(c) &= - \log{p_{c}(x)} = -\log{\mu_{Y | X = x}(c)}, \\
+				\hat{u}_{x}(c) &= - \log{\hat{p}_{c}(x)} = -\log{\hat{\mu}_{Y | X = x}(c)}. \\
+			\end{aligned}
+			\end{equation}
+
+			Since $\log$ is a concave function, we have the property that $\log{a} - \log{b} \leq \frac{1}{b} (a - b)$.
+This allows us to bound $| \hat{u}_{x}(c) - u_{x}(c) |$ by $| \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |$ for all $c \in \mathbb{N}_{m}$,
+
+			\begin{equation}
+			\begin{aligned}
+				| \hat{u}_{x}(c) - u_{x}(c) | &= | \log{\hat{\mu}_{Y | X = x}(c)} - \log{\mu_{Y | X = x}(c)} | \\
+				&\leq \frac{1}{| \mu_{Y | X = x}(c) |} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) | \\
+				&= \alpha_{x} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |,
+			\end{aligned}
+			\end{equation}
+
+			where we define $\alpha_{x} := \max_{c \in \mathbb{N}_{m}} \frac{1}{| \mu_{Y | X = x}(c) |}$.
+Since the RKHS norm of bounded functions in $\mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of their vector representations \eqref{eq:rkhs_norm_is_l2_norm}, we have
+
+			\begin{equation}
+			\begin{aligned}
+				\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}}^{2} &= \| \hat{\bvec{u}}_{x} - \bvec{u}_{x} \|_{\ell_{2}}^{2} \\
+				&= \sum_{c = 1}^{m} | \hat{u}_{x}(c) - u_{x}(c) |^{2} \\
+				&\leq \sum_{c = 1}^{m} \alpha_{x}^{2} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |^{2} \\
+				&\leq \alpha_{x}^{2} \sum_{c = 1}^{m} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |^{2} \\
+				&\leq \alpha_{x}^{2} \| \hat{\bm{\mu}}_{Y | X = x} - \bm{\mu}_{Y | X = x}  \|_{\ell_{2}}^{2} \\
+				&\leq \alpha_{x}^{2} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}^{2}. \\
+			\end{aligned}
+			\end{equation}
+
+			Therefore, $\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}} \leq \alpha_{x} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$, and \eqref{eq:information_entropy_bound} becomes
+
+			\begin{equation}
+			\begin{aligned}
+				| \hat{h}(x) - h(x) | &\leq \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}} + \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| u_{x} \|_{\mathcal{H}_{\delta}} \\
+				&= \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| u_{x} \|_{\mathcal{H}_{\delta}} \\
+				&= ( \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| u_{x} \|_{\mathcal{H}_{\delta}} ) \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} \\
+			\end{aligned}
+			\end{equation}
+
+			Hence, with $\gamma(x) = \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| u_{x} \|_{\mathcal{H}_{\delta}}$, \cref{thm:pointwise_uniform_convergence} implies that $\hat{h}$ converges pointwise to $h$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+		\end{proof}
+	\end{theorem}
 

### 2017-04-16 kernel_embedding_classifier.tex
Add unpolished discussion about why SGD works

@@
 
-		We begin by selecting a mini-batch size $n_{b} << n$ that is much smaller than $n$. The objective \eqref{eq:trace_norm_optimisation} is then computed only for the mini-batch
-
-		For gradient descent, pick $n_{b} = n$ so that $\mathcal{I} = \mathbb{N}_{n}$ and the full dataset is used to compute the gradients.
-
-		SGD Coefficient ratio for gradient update can be absorbed into the learning rate so don't need to worry about it
-
-		Also learning rate can be left to the same
-
-		Convergence can usually be left to the same gradient error tolerance
-
-		\textbf{Why does SGD work?} It is not immediately clear to me why SGD works.
+		We begin by selecting a mini-batch size $n_{b} << n$ that is much smaller than $n$.
+At each training iteration, we sample a mini-batch of size $n_{b}$ from the full dataset.
+The objective \eqref{eq:trace_norm_optimisation} and hence its gradients with respect to each hyperparameter is then computed only for the mini-batch.
+This stochastic gradient is then used to make hyperparameter updates in that training iteration.
+This continues until the magnitude of the stochastic gradients fall below a certain range.
+This training algorithm is presented in \cref{alg:training_stochastic_gradient_descent}.
+This implementation also generalises the gradient descent approach, where $n_{b} = n$ so that $\mathcal{I} = \mathbb{N}_{n}$ and the full dataset is used to compute the gradients.
+
+		\note{I have written some not-so-polished comments about why SGD works below.}
+
+		\textbf{Why does SGD work?} It is not immediately obvious that a stochastic gradient descent approach would work for a kernel-based classifier.
+Unlike the cross-entropy loss, the complexity bound objective \eqref{eq:trace_norm_optimisation} is not expressed as a sum of terms each depending on one observation from the dataset.
+Even if it is, being a kernel-based classifier, each term of such a objective would still require the computation of an entire gram matrix and its regularised inverse.
+As such, taking a mini-batch implies that we are only taking a block portion of the entire gram matrix and its regularised inverse.
+
 		What we can see from experiments is that the batch data complexity bound is usually a biased estimator of the full data complexity bound.
 This bias is expected for one primary reason.
-The first is that this quantity is a data complexity bound to begin with, and thus while the actual batch data complexity may be an unbiased estimator of the full data complexity, the tightness of the upper bound is expected to change with growing datasets and thus this bias comes from the varying degrees of tightness in the bound as data increases.
+The objective \eqref{eq:trace_norm_optimisation} is a data complexity bound to begin with, and thus while the actual batch data complexity may be an unbiased estimator of the full data complexity, the tightness of the upper bound is expected to change with growing datasets and thus this bias comes from the varying degrees of tightness in the bound as data increases.
 While this bias exists, we do see from experiments that, as we optimise the hyperparameters, both the batch data complexity bound and full data complexity bound decreases at a proportional pace.
@@
 
-		Idea: Last time in my derivation I can derive that the full complexity bound is the sum of the batch complexity bound plus some co-varying terms (which can be negative).
-If I can show that the magnitude of such co-varying terms are upper bounded by the batch complexity bounds, then I can say that as the batch complexity bounds are minimised, so is the full complexity bound!
-
-		We know that the SGD works because the gradients computed from each batch is consistently vanishing as we optimise the hyperparameters.
+		However, it is also not that unintuitive if we realise that each mini-batch is an independently sampled subset of the full dataset.
+This means that the complexity of the model learned from each mini-batch should not be too different from one another, as they are all data from the same probability distribution.
+This gives intuition of how each stochastic gradient is on average correct if we want to learn a low complexity model \textit{for a dataset of the same size as the mini-batch}.
+However, this may not translate to a low complexity model for the full dataset.
+In fact, we do expect that the mini-batch complexity bound to be smaller than the full dataset complexity bound, since models learned on less data tend to be simpler than models learned on more data.
+Nevertheless, intuitively, it also makes sense that a low complexity model for a small dataset would mean that the model is also of low complexity for a larger dataset, as long as the small dataset can capture, albeit to smaller degrees, many of the variations of the larger dataset.
+We achieve this by randomly shuffle the mini-batch being used in each iteration.
+If it does not capture all such variations, the learned model may be too simple when applied on the full dataset.
+
+		We know that, experimentally, SGD works, because the gradients computed from each batch is consistently vanishing as we optimise the hyperparameters.
 Surprisingly, it seems to be on the same scale of the full GD case and suggests that the batch gradient is possibly a (scaled) consistent estimator of the full gradient as well.
 
-		Furthermore, not only does SGD reduce the time and space complexity of each training iteration drastically, it does not increase the number of iterations required for convergence either (at least for a Gaussian kernel), and, in many cases actually takes less iterations than the full GD solution.
+		Furthermore, not only does SGD reduce the time and space complexity of each training iteration drastically, it does not increase the number of iterations required for convergence either (at least for a few simple kernels like the Gaussian kernel), and, in many cases actually takes less iterations than the full GD solution.
 This could be because the SGD gradients are usually under-biased compared to the full GD gradients, and thus reach the gradient error tolerance faster.
@@
 		Round Shifts: Instead of taking completely random batches from the full dataset each time, what one can do instead is to use a ``round shift'' setup to choose the batches.
-That is, we first choose a batch size $n_{b}$.
-The first batch is the first $n_{b}$ data points in the dataset, the second batch is the second $n_{b}$ data points in the dataset, and so on.
+That is, the first batch is the first $n_{b}$ data points in the dataset, the second batch is the second $n_{b}$ data points in the dataset, and so on.
 When the whole dataset is scanned through once, we repeat and start from the beginning again.
@@
 Our guess is that the data points we use each time in our batch complexity bound estimation is not independent from each other enough such that the gradients are more correlated to each other and is thus less adaptive.
+
+		Optimisation Setup: We mentioned that it is possible that the expectation of the gradients of the SGD is a scaled version of the full GD gradients.
+In that case, what is commonly done is to multiply the SGD gradients by the correct ratio.
+However, here we choose to leave that out, as such a ratio can simply be absorbed into the learning rate.
+Also, this can be advantageous as such a ratio is usually greater than $1$ (in order to scale up the estimate to the same scale as the full GD case), and if we do multiply this ratio to the stochastic gradients, the learning rate should usually be decreased, in order to dampen out the stochasticity from the stochastic gradients and avoid divergence.
+From experiments we see that by not multiplying this ratio, the learning rate can usually be left to the same as the full GD approach.
+For the same reason, when we switch from full GD to SGD this way, the same gradient error tolerance can also be used.
+
+		Proof Idea: I suspect that the full complexity bound is the sum of the batch complexity bound plus some co-varying terms (which can be negative).
+If I can show that the magnitude of such co-varying terms are upper bounded by the batch complexity bounds, then I can say that as the batch complexity bounds are minimised (randomly), so is the full complexity bound!
 

### 2017-04-16 kernel_embedding_classifier.tex
Add draft for 'End-to-End Classifier Training for Deep Kernel Embedding Network'

@@
 
+%\author{
+%  Kelvin Y.S. Hsu, Richard Nock, Fabio T. Ramos \\
+%  University of Sydney, Australia\\
+%  DATA61, CSIRO\\
+%  \texttt{\{Kelvin.Hsu, Richard.Nock, Fabio.Ramos\}@\{sydney.edu.au, data61.csiro.au\}} \\
+%  %% examples of more authors
+%  %% \And
+%  %% Coauthor \\
+%  %% Affiliation \\
+%  %% Address \\
+%  %% \texttt{email} \\
+%  %% \AND
+%  %% Coauthor \\
+%  %% Affiliation \\
+%  %% Address \\
+%  %% \texttt{email} \\
+%  %% \And
+%  %% Coauthor \\
+%  %% Affiliation \\
+%  %% Address \\
+%  %% \texttt{email} \\
+%  %% \And
+%  %% Coauthor \\
+%  %% Affiliation \\
+%  %% Address \\
+%  %% \texttt{email} \\
+%}
+
 \author{
-  Kelvin Y.S. Hsu, Richard Nock, Fabio T. Ramos \\
+	Kelvin Y.S. Hsu \\
 	University of Sydney, Australia\\
 	DATA61, CSIRO\\
-  \texttt{\{Kelvin.Hsu, Richard.Nock, Fabio.Ramos\}@\{sydney.edu.au, data61.csiro.au\}} \\
+	\texttt{Kelvin.Hsu@\{sydney.edu.au, data61.csiro.au\}} \\
 	%% examples of more authors
-  %% \And
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
+	\And
+	Richard Nock \\
+	Australian National University, Australia\\
+	University of Sydney, Australia\\
+	DATA61, CSIRO\\
+	\texttt{Richard.Nock@data61.csiro.au} \\
+	\And
+	Fabio T. Ramos \\
+	University of Sydney, Australia\\
+	DATA61, CSIRO\\
+	\texttt{Fabio.Ramos@\{sydney.edu.au, data61.csiro.au\}} \\
 	%% \texttt{email} \\
@@
 
+		\note{Note: A very simple extension to the above is the cross entropy and Kullback-Leibler divergence between two input location $x, x' \in \mathcal{X}$.
+The convergence proof is basically identical.
+However, I am not sure how useful this result would be in practice.
+What would be more useful, in my opinion, is the joint entropy of multiple input locations.}
 \section{Hyperparameter Training}
@@
 
-\section{End-to-End Classifier Training for Deep Kernel Embeddings}
+\section{End-to-End Classifier Training for Deep Kernel Embedding Network}
 \label{sec:deep_kernel_embeddings}
 
-\section{Full Probabilistic Inference and Mode Reconstruction}
+	The kernel embedding classifier is developed in a very general manner and can be trained under any choice of a family of positive definite kernels $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$, $\theta \in \Theta$.
+There are a variety of ways to construct richer kernels from simpler kernels, such as through convex combination of multiple kernels.
+In this section, we focus on deep kernels, in which inputs $x, x' \in \mathcal{X}$ is to undergo various stages of feature transformations before being fed into a simple positive definite kernel.
+Specifically, we pay particular attention to feature transformations in the form of a perceptron, so that the cumulative stages of feature transformation become the (feed-forward) multi-layer perceptron that is familiar within the neural network literature.
+Although our approach can generalise to other architectures, such as recurrent neural networks, we omit such consideration for simplicity.
+
+	Let $\mathcal{F}_{0} := \mathcal{X}$ be the original input space.
+The $j^{\mathrm{th}}$ layer of the network $\varphi^{(j)}_{\theta_{j}} : \mathcal{F}_{j - 1} \to \mathcal{F}_{j}, j = 1, 2, \dots, q$ is to transform features from the previous layer to features in the current layer, where $q$ is the total number of such feature transformation layers, and $\theta_{j} \in \Theta_{j}$ parametrises each of those transformations.
+
+	For example, in a typical multi-layer perceptron context, each layer can be written as $\varphi^{(j)}_{\theta_{j}}(x) = \sigma(W_{j}^{T} x + b_{j})$, where $W$ and $b$ are the weight and bias parameters of the layer, and $\sigma$ is an element-wise activation function, typically the rectified linear unit (ReLU) or the sigmoid.
+In this case, the layer is parametrised by $\theta_{j} = \{W_{j}, b_{j}\}$.
+The setup for a feed-forward convolutional neural network is also very similar.
+
+	Our aim is to construct a positive definite kernel $k$ which can learn representations of the inputs at various levels before such these representations are passed into a simpler kernel $\kappa$ which captures the similarity between the representations.
+
+	Let $\kappa_{\theta_{\kappa}} : \mathcal{F}_{p} \times \mathcal{F}_{p} \to \mathbb{R}$ be parametrised by $\theta_{\kappa} \in \Theta_{\kappa}$. We will construct our kernel network $k$ by
+
+	\begin{equation}
+		k_{\theta}(x, x') := \kappa_{\theta_{\kappa}}\Bigg(
+		\varphi^{(p)}_{\theta_{p}}\bigg(\varphi^{(p - 1)}_{\theta_{p - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x)\big)\Big)\bigg),
+		\varphi^{(p)}_{\theta_{p}}\bigg(\varphi^{(p - 1)}_{\theta_{p - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x')\big)\Big)\bigg)
+		\Bigg)
+	\label{eq:deep_kernel_embedding_network}
+	\end{equation}
+
+	where $\theta = \{\theta_{1}, \theta_{2}, \dots, \theta_{p -1}, \theta_{p}, \theta_{\kappa}\} \in \Theta = \Theta_{1} \otimes \Theta_{2} \otimes \dots \otimes \Theta_{p - 1} \otimes \Theta_{p} \otimes \Theta_{\kappa}$ are the collection of all parameters of each layer and the kernel $\kappa$.
+
+	\note{Note: I think it would be nice to add a figure to visualise the several convolutional layers and how it is passed into a positive definite kernel at the end.}
+
+	Due to the very general training algorithm we developed in \cref{sec:hyperparameter_learning}, we propose to train the kernel network end-to-end by minimising the global Rademacher complexity bound \eqref{eq:trace_norm_optimisation} as before.
+
+	\note{Talk about the advantages and disadvantages of such an approach. The results with three convolutional layer will be put into the experiments section.}
+
+	\subsection{Deep Convolutional Kernel Embedding Network}
+
+		\note{Note: Might be good to relate our work with \citep{mairal2014convolutional}.}
+
+\section{Full Probabilistic Inference and Mode Representation Reconstruction}
 \label{sec:mode_reconstruction}
 
-	Being formulated and represented as a conditional embedding in a reproducing kernel Hilbert space, the kernel embedding classifier is able to learn a discriminative model to nonparametrically infer about the distribution of discrete labels $Y$ given an example input $X$.
+	Formulated as a conditional embedding learning task in a reproducing kernel Hilbert space, the kernel embedding classifier is able to learn a discriminative model to nonparametrically infer about the distribution of discrete labels $Y$ given an example input $X$.
 In the previous section, we devised a training algorithm for learning the optimal hyperparameters for the conditional embedding corresponding to the classifier.
-Now that the conditional embedding is learned, we can
+Now that the conditional embedding is learned, we can perform full probabilistic inference between all the observed and hidden variables (if any) of the kernel embedding network.
 

### 2017-04-16 kernel_embedding_classifier.tex
Clear up some contributions

@@
 
-	- Currently, most classification algorithms are binary classifiers, which focuses on the case where the target label can only come from one of two classes.
-
-	- Examples include ...
-
-	- However, many applications require multiclass classifiers
-
-	- Examples include ...
-
-	- Most solve this by doing OVA, AVA, or decision trees on binary classifiers \citep{aly2005survey}
+	\note{Note: Introduction will need a thorough discussion of related work.}
+
+	- Currently, most classification algorithms are binary classifiers, which focuses on the case where the target label can only come from one of two classes. Examples include ...
+
+	- However, many applications require multiclass classifiers. Examples include ...
+
+	- Most solve this by doing binary relevance, such as OVA, AVA, or decision trees on binary classifiers \citep{aly2005survey}
 
 	- Furthermore, those probabilities are usually artificial, by passing through a link function that may or may not be valid, and in many cases like the GPC, is not analytically tractible and requires further approximations.
-No convergence gaurantees of convergence to the actual decision probabilities
+No convergence gaurantees of convergence to the actual decision probabilities.
+
+	- SVMs also are binary by nature. They also do not provide probabilities.
 
@@
 	\begin{itemize}
-		\item A novel probabilistic multiclass classifier, the kernel embedding classifier (KEC), based on the theory and framework of kernel embedding of conditional distributions with convergence guarantees.
-		\item A novel hyperparameter training algorithm based on gradient descent and, most importantly, stochastic gradient descent.
-Reducing the complexity of KEC training from $O(n^{3})$ to $O(n_{b}^{3})$ in time and from $O(n^{2})$ to $O(n_{b}^{2})$ for a training dataset of size $n$ and a batch size of $n_{b} << n$.
-		\item Two techniques to estimate the information entropy of a classification prediction with convergence guarantees
-		\item Mode reconstruction of the inputs, where we compute the most representative example of each class
+		\item A novel probabilistic multiclass classifier, the kernel embedding classifier (KEC), based on the theory and framework of kernel embedding of conditional distributions with convergence guarantees on probability and entropy estimates.
+		\item A novel training algorithm based on minimising the Rademacher complexity of our kernel embedding classifier in the reproducing kernel Hilbert space, which provides greater generalisation capabilities to the classifier.
+		\item A mini-batch stochastic gradient descent variant of the above training algorithm, reducing training complexity from $O(n^{3})$ to $O(n_{b}^{3})$ in time and from $O(n^{2})$ to $O(n_{b}^{2})$ in space for a training dataset of size $n$ and a mini-batch size of $n_{b} << n$.
+		\item The application of such a training scheme to learn a deep kernel embedding network and deep convolutional kernel embedding network for image recognition tasks.
+		\item Probabilistic inference and mode reconstruction of the inputs, where we quantify and obtain the most representative sample of each class, amongst other statistics.
+		\item Probabilistic inference and mode reconstruction on hidden layers of the deep kernel embedding network.
 	\end{itemize}
@@
 
-\section{Full Probabilistic Inference and Mode Representation Reconstruction}
+\section{Full Probabilistic Inference and Mode Reconstruction}
 \label{sec:mode_reconstruction}
@@
 Now that the conditional embedding is learned, we can perform full probabilistic inference between all the observed and hidden variables (if any) of the kernel embedding network.
+
+	\note{Note: Not completed yet.}
+
+	\subsection{Hidden Representation Reconstruction}
+
+		\note{Note: Observed quantities are done, but hidden quantities needs experimental verification.}
 

### 2017-04-16 kernel_embedding_classifier.tex
Add draft for introduction

--- 2017-04-16 kernel_embedding_classifier.tex
@@
 \begin{abstract}
-
+%	We propose a novel probabilistic multiclass classifier, the kernel embedding classifier, by casting the multiclass classification problem into the kernel conditional embedding framework in a principled manner.
+We provide convergence guarantees of the classifier in both decision probability and information entropy, and develop a novel training objective based on Rademacher complexity bounds
+%Specifically, the guaranteed convergence of the kernel embedding classifier in both decision probability and information entropy, the Rademacher complexity based hyperparameter training scheme, the stochastic gradient descent version thereof which allows scalable training, the application of such flexible training methods to train deep convolutional features, and the fully probabilistic inference on both inputs and outputs.
+Focus the point of the paper as that this is a new and elegant formulation of a fully probabilistic classifier (not just in the outputs, but even in the inputs) with complexity bound based training.
+Being formulated as type of kernel conditional embedding learning, all the nice properties from the Hilbert space embedding world can be imported into this framework.
+In practice, even though the mathematical theory of kernel embeddings can be tricky, the resulting algorithms are very elegant and simple, so that implementation is quick and easy.
+Being very general, there should be a lot of things we can do in the future to improve it or build upon it.
 \end{abstract}
@@
 
-	- Currently, most classification algorithms are binary classifiers, which focuses on the case where the target label can only come from one of two classes.
-
-	- Examples include ...
-
-	- However, many applications require multiclass classifiers
-
-	- Examples include ...
-
-	- Most solve this by doing OVA, AVA, or decision trees on binary classifiers \citep{aly2005survey}
-
-	- Furthermore, those probabilities are usually artificial, by passing through a link function that may or may not be valid, and in many cases like the GPC, is not analytically tractible and requires further approximations.
-No convergence gaurantees of convergence to the actual decision probabilities
-
-	In this paper, we cast the multiclass classification problem into the kernel conditional embedding framework, where learning the classifier is done by learning a corresponding conditional embedding from data.
-We show that by placing a Kronecker delta kernel over the label space, decision probabilities can be expressed as inner products in the correspondingly induced reproducing kernel Hilbert space, which can be consistantly estimated from data using the conditional embedding framework.
-In this way, we propose a natural probabilistic classifier for multiclass classification.
-
-	- Our contributions are ...
+	\note{Draft: Introduction will need a more thorough discussion of motivation, related work, theoretical and practical implications, and contribution.}
+
+	Classification is perhaps one of the most important and thoroughly developed topics in machine learning and pattern recognition.
+Despite this, principled probabilistic classification on multiclass problems remains a difficult and challenging task, and most solutions tackle this issue rather indirectly.
+\note{Maybe elaborate on why multiclass problems are important and why we want probabilities estimates in our predictions.}
+
+	Support vector classifiers (SVC) \citep{m2001introduction}, for example, are originally designed for non-probabilistic binary classification.
+Its simple and convex optimisation structure makes the model very attractive both theoretically and in practice.
+However, in order to cope with overfitting, slack constraints introduce hyperparameters for which training does not directly addressed except through standard cross-validation.
+In order to extend to multiclass scenarios, binary relevance such as one-against-all, one-against-one, or decision trees are used to build a multiclass classifier from multiple binary classifiers \citep{aly2005survey, hsu2002comparison}.
+There are also no straightforward way of assigning probabilities to SVC, and in many approaches probabilities are simply arbitrary score measures that has been normalised \citep{zadrozny2002transforming, franc2011support} (\note{Check this}).
+As such, while the original SVC formulation is certainly elegant and practical, its multitude of variants for probabilistic multiclass classification becomes rather convoluted.
+
+	Within the similar domain of kernel-based classification, Gaussian process classifiers (GPC) \citep{rasmussen2006gaussian} are Bayesian models for which probability distributions are analysed in a principled manner by constructing a latent model that is distributed as a Gaussian process.
+Nevertheless, the posterior class probabilities are not analytically tractable due to a non-Gaussian likelihood, which requires methods such as Monte Carlo Markov Chain, expectation propagation, or variation inference to approximate.
+The GPC is also formulated as a binary classifier, and multiclass classification is either approached with binary relevance, or through introducing multiple latent functions that are to be squashed together through a softmax function if probabilistic outputs are to be retained.
+
+	On the other end of the spectrum, parametric models are limited in its ability to grow in capacity as the dataset grows.
+Neural networks \citep{lecun2015deep} mitigates this issue by growing deep instead of wide so that each layer of the network extract meaningful features from the dataset.
+While it requires large amounts of data in order to work, neural networks has been shown to be able to learn almost any complex function.
+However, the choice of the network architecture remains, and principled probabilistic methods are still undergoing active research.
+
+	In this paper, we propose a new and natural probabilistic multiclass classifier, the kernel embedding classifier (KEC), by casting multiclass classification problems into the kernel conditional embedding framework.
+Kernel embedding of probability distributions is a principled method for representing and manipulating general probability distributions nonparametrically in a reproducing kernel Hilbert space (RKHS) that is associated with a positive definite kernel.
+In this way, probability distributions do not need to be restricted to a parametric form, but instead fully expressed by the dataset in a nonparametric manner.
+In our approach, learning the classifier is done by learning a corresponding conditional embedding from data.
+We show that by placing a Kronecker delta kernel over the label space, decision probabilities and information entropies can be expressed as inner products in the correspondingly induced reproducing kernel Hilbert space, which can be consistently estimated from data using the conditional embedding framework.
+This method is very general and makes no distinction between binary and multiclass classification, presenting a unified and principled method for all probabilistic classification tasks.
+
+	Being developed very generally for any choice of positive definite kernel $k$, the kernel embedding classifier requires the specification of various hyperparameters.
+In the current kernel embedding literature, there is no standard method to train the hyperparameters besides cross-validation.
+We further propose and develop a hyperparameter training scheme based on Rademacher complexity bounds, which appropriately balances the accuracy and generalisation capabilities of the classifier.
+We then develop a mini-batch stochastic gradient descent version of such a training procedure, which brings the notorious complexity of all kernel methods that is cubic in the size of the dataset down to only cubic in the mini-batch size.
+
+	With no restrictions on the type of kernel used for our classifier, we apply our training algorithm to learn kernels with deep convolutional features on standard image recognition tasks such as the MNIST dataset (\note{Mention more on experiments later when they are ready}).
+The fully nonparametric and probabilistic nature of the classifier also allows us to perform probabilistic inference on the inputs and, most interestingly, the hidden layers if using a deep kernel.
+Specifically, we can quantify and obtain the most representative input sample and hidden features of each class.
+
+	In summary, our contributions are:
 
 	\begin{itemize}
-		\item A novel probabilistic multiclass classifier, the kernel embedding classifier (KEC), based on the theory and framework of kernel embedding of conditional distributions with convergence guarantees.
-		\item A novel hyperparameter training algorithm based on gradient descent and, most importantly, stochastic gradient descent.
-Reducing the complexity of KEC training from $O(n^{3})$ to $O(n_{b}^{3})$ in time and from $O(n^{2})$ to $O(n_{b}^{2})$ for a training dataset of size $n$ and a batch size of $n_{b} << n$.
-		\item Two techniques to estimate the information entropy of a classification prediction with convergence guarantees
-		\item Mode reconstruction of the inputs, where we compute the most representative example of each class
+		\item A novel probabilistic multiclass classifier, the kernel embedding classifier (KEC), based on the theory and framework of kernel embedding of conditional distributions;
+		\item Convergence guarantees on corresponding decision probability and information entropy estimates;
+		\item A novel training algorithm based on minimising Rademacher complexity bounds of our kernel embedding classifier in a reproducing kernel Hilbert space, which balances classification performance and provides greater generalisation capabilities to the classifier;
+		\item A mini-batch stochastic gradient descent variant of the above training algorithm, reducing training complexity from $O(n^{3})$ to $O(n_{b}^{3})$ in time and from $O(n^{2})$ to $O(n_{b}^{2})$ in space for a training dataset of size $n$ and a mini-batch size of $n_{b} << n$;
+		\item The application of such a training scheme to learn a deep kernel embedding network and deep convolutional kernel embedding network for image recognition tasks;
+		\item Probabilistic inference and mode reconstruction of the inputs, where we quantify and obtain the most representative sample of each class, amongst other statistics; And,
+		\item Probabilistic inference and mode reconstruction on hidden feature layers of the deep kernel embedding network.
 	\end{itemize}

### 2017-05-06 kernel_embedding_classifier.tex
Save first draft

@@
 
+\usepackage{multirow}
+
 \usepackage{algorithm}
@@
 
-\title{Probabilistic Multiclass Kernel Embedding Classifier}
+\title{CAKE: Classification avec Kernel Embeddings \\ with Rademacher Complexity Bounds}
 
@@
 \end{abstract}
-
+	\note{Alternative Paper Names: \\ 
+		\begin{itemize}
+			\item (Original Name) Probabilistic Multiclass Kernel Embedding Classifier
+			\item CAKE: Classification avec Kernel Embeddings
+			\item CAKE: Classification avec Kernel Embeddings: A Principled Probabilistic Nonparametric Multiclass Classifier
+			\item Probabilistic Nonparametric Multiclass Classification with Kernel Embeddings of Conditional Distributions
+			\item The Kernel Embedding Classifier
+			\item Probabilistic Classification via Hilbert Space Embeddings
+			\item Probabilistic Classification with Kernel Embeddings under Rademacher Complexity
+			\item ...
+		\end{itemize}
+		Simple acronyms makes it all the more memorable and fun :) %When the draft is done I might actually just replace KEC (Kernel Embedding Classifier) with CAKE (Classification avec Kernel Embeddings).
+	}
+
+	Current state of the paper
+
+	\begin{itemize}
+		\item Introduction: Completed, but may need more discussion on motivation and related work.
+		\item Hilbert Space Embeddings of Conditional Probability Distributions (Background): Completed.
+		\item Classification avec Kernel Embeddings: Completed.
+		\item Information Entropy: Completed. There is a subsection for cross entropy and KL divergence that I am not sure if I want to include it in the paper so I have not written it yet.
+		\item Hyperparameter Learning with Rademacher Complexity Bounds: Completed.
+The subsection for mini-batch stochastic gradient descent current contains not-so-polished speculative discussion on the technique.
+		\item End-to-End Classifier Training for Deep Kernel Embedding Network: Draft not completed. Perhaps 1/3 done.
+		\item Full Probabilistic Inference and Mode Reconstruction: Not completed.
+		\item Experiments: Currently only has an outline of what to put into this section.
+		\item Conclusion: Current has notes on what to mention when the paper is done. Also has a detailed list of possible future work to the paper.
+		\item Appendix: Theorems and Derivations: Completed.
+		\item Appendix: Design Choices: Rough unpolished draft.
+	\end{itemize}
 \section{Introduction}
@@
 
-	Within the similar domain of kernel-based classification, Gaussian process classifiers (GPC) \citep{rasmussen2006gaussian} are Bayesian models for which probability distributions are analysed in a principled manner by constructing a latent model that is distributed as a Gaussian process.
-Nevertheless, the posterior class probabilities are not analytically tractable due to a non-Gaussian likelihood, which requires methods such as Monte Carlo Markov Chain, expectation propagation, or variation inference to approximate.
+	Within the similar domain of kernel-based classification, Gaussian process classifiers (GPC) \citep{rasmussen2006gaussian} are Bayesian models for which probability distributions are analysed in a principled manner, by constructing a latent model that is distributed as a Gaussian process.
+Nevertheless, the posterior class probabilities are not analytically tractable due to a non-Gaussian likelihood, which require methods such as Monte Carlo Markov Chain, expectation propagation, or variation inference to approximate.
 The GPC is also formulated as a binary classifier, and multiclass classification is either approached with binary relevance, or through introducing multiple latent functions that are to be squashed together through a softmax function if probabilistic outputs are to be retained.
@@
 Neural networks \citep{lecun2015deep} mitigates this issue by growing deep instead of wide so that each layer of the network extract meaningful features from the dataset.
-While it requires large amounts of data in order to work, neural networks has been shown to be able to learn almost any complex function.
+While they require large amounts of data in order to work, neural networks has been shown to be able to learn almost any complex function.
 However, the choice of the network architecture remains, and principled probabilistic methods are still undergoing active research.
+In domains where the available data is scarce, neural networks also become very difficult to design and train.
 
 	In this paper, we propose a new and natural probabilistic multiclass classifier, the kernel embedding classifier (KEC), by casting multiclass classification problems into the kernel conditional embedding framework.
-Kernel embedding of probability distributions is a principled method for representing and manipulating general probability distributions nonparametrically in a reproducing kernel Hilbert space (RKHS) that is associated with a positive definite kernel.
+Kernel embedding of probability distributions is a principled method for representing and manipulating general probability distributions, nonparametrically, in a reproducing kernel Hilbert space (RKHS) that is associated with a positive definite kernel.
 In this way, probability distributions do not need to be restricted to a parametric form, but instead fully expressed by the dataset in a nonparametric manner.
@@
 
-	Being developed very generally for any choice of positive definite kernel $k$, the kernel embedding classifier requires the specification of various hyperparameters.
-In the current kernel embedding literature, there is no standard method to train the hyperparameters besides cross-validation.
+	Being developed very generally for any choice of positive definite kernel $k$, the kernel embedding classifier places no limit on the family of kernels and the structure of its hyperparameters.
+In the current kernel embedding literature, there is no standard method to train the hyperparameters of a conditional embedding besides cross-validation.
 We further propose and develop a hyperparameter training scheme based on Rademacher complexity bounds, which appropriately balances the accuracy and generalisation capabilities of the classifier.
-We then develop a mini-batch stochastic gradient descent version of such a training procedure, which brings the notorious complexity of all kernel methods that is cubic in the size of the dataset down to only cubic in the mini-batch size.
+We then develop a mini-batch stochastic gradient descent version of such a training procedure, which brings the notorious complexity of kernel methods that is cubic in the size of the dataset down to only cubic in the mini-batch size.
 
 	With no restrictions on the type of kernel used for our classifier, we apply our training algorithm to learn kernels with deep convolutional features on standard image recognition tasks such as the MNIST dataset (\note{Mention more on experiments later when they are ready}).
+Specifically, we also test the performance of our classifier on ``high $d$, low $n$'' domains where the dimensionality of the problem is large compared to the number of observations, by restricting the size of the dataset to be less than the dimensionality of the problem.
+
 	The fully nonparametric and probabilistic nature of the classifier also allows us to perform probabilistic inference on the inputs and, most interestingly, the hidden layers if using a deep kernel.
@@
 		\item A novel probabilistic multiclass classifier, the kernel embedding classifier (KEC), based on the theory and framework of kernel embedding of conditional distributions;
-		\item Convergence guarantees on corresponding decision probability and information entropy estimates;
+		\item Convergence guarantees on decision probability and information entropy estimates;
 		\item A novel training algorithm based on minimising Rademacher complexity bounds of our kernel embedding classifier in a reproducing kernel Hilbert space, which balances classification performance and provides greater generalisation capabilities to the classifier;
 		\item A mini-batch stochastic gradient descent variant of the above training algorithm, reducing training complexity from $O(n^{3})$ to $O(n_{b}^{3})$ in time and from $O(n^{2})$ to $O(n_{b}^{2})$ in space for a training dataset of size $n$ and a mini-batch size of $n_{b} << n$;
-		\item The application of such a training scheme to learn a deep kernel embedding network and deep convolutional kernel embedding network for image recognition tasks;
-		\item Probabilistic inference and mode reconstruction of the inputs, where we quantify and obtain the most representative sample of each class, amongst other statistics; And,
-		\item Probabilistic inference and mode reconstruction on hidden feature layers of the deep kernel embedding network.
+		\item A deep convolutional network extension to the kernel embedding classifier to learn a deep convolutional kernel embedding network for image recognition tasks; And,
+		\item A methodology to perform probabilistic inference and mode reconstruction of the inputs and hidden feature layers, where we quantify and obtain the most representative sample and hidden features of each class.
 	\end{itemize}
@@
 
-\section{Kernel Embedding Classifier}
+\section{Classification avec Kernel Embeddings}
 \label{sec:kernel_embedding_classifier}
@@
 	Unfortunately, $u_{x}$ is not known exactly, since $\mathbb{P}[Y = y | X = x]$ is not known exactly.
-Instead, since $\hat{p}_{c}(x)$ is a consistent estimate for $\mathbb{P}[Y = c | X = x]$ (\cref{thm:probability_convergence}), we propose to replace $u_{x}$ with the negative log of $\hat{p}_{y}(x)$.
+Instead, since $\hat{p}_{c}(x)$ is a consistent estimate for $\mathbb{P}[Y = c | X = x]$ by \cref{thm:probability_convergence}, we propose to replace $u_{x}(y)$ with the negative log of $\hat{p}_{y}(x)$.
 However, we cannot simply take the log of this estimator, as $\hat{p}_{y}(x)$ may produce non-positive estimates to the prediction probabilities.
@@
 What would be more useful, in my opinion, is the joint entropy of multiple input locations.}
-\section{Hyperparameter Training}
+\section{Hyperparameter Learning with Rademacher Complexity Bounds}
 \label{sec:hyperparameter_learning}
@@
 
-	In the kernel embedding literature, hyperparameters has been notoriously difficult to tune, and its learning is usually only restricted to inelegant methods such as cross validation with either some form of misclassification loss or the negative log probability (cross entropy) as the objective.
+	In the kernel embedding literature, hyperparameters has been notoriously difficult to tune, and its learning is usually only restricted to inelegant methods such as cross validation with either some form of misclassification loss or the negative log probability (cross entropy) loss as the objective.
 
@@
 	Similarly, we propose to train our kernel embedding classifier with the same high level formulation: minimise the model complexity without compromising classification performance on the training data.
-Instead of employing the VC dimension as the complexity measure of our model, which is defined mainly for binary classifiers, we consider the \textit{Rademacher complexity} \citep{bartlett2002rademacher} of the kernel embedding classifier.
+Instead of employing the VC dimension as the complexity measure of our model, which is defined mainly for binary classifiers, we consider the \textit{Rademacher complexity} of the kernel embedding classifier.
+\cite[Theorem 5]{bartlett2002rademacher} has shown that the test error for a class of functions, such as a classifier, is stochastically bounded by the training error plus a term that is monotonically increasing with the Rademacher complexity and a constant, similar to the case with the VC dimension.
+As such, if we can minimise the model complexity in the sense of the Rademacher complexity while maintaining a low training error, we can optimise generalisation ability in the sense of low expected test error.
 
@@
 			\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathcal{I}, j \in \mathcal{I}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
-			\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n \lambda I) \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
+			\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n_{b} \lambda I_{n_{b}}) \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
 			\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash B) \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
@@
 
-	For example, in a typical multi-layer perceptron context, each layer can be written as $\varphi^{(j)}_{\theta_{j}}(x) = \sigma(W_{j}^{T} x + b_{j})$, where $W$ and $b$ are the weight and bias parameters of the layer, and $\sigma$ is an element-wise activation function, typically the rectified linear unit (ReLU) or the sigmoid.
+	For example, in a typical multi-layer perceptron context, each layer can be written as $\varphi^{(j)}_{\theta_{j}}(x) = \sigma(W_{j} x + b_{j})$, where $W$ and $b$ are the weight and bias parameters of the layer, and $\sigma$ is an element-wise activation function, typically the rectified linear unit (ReLU) or the sigmoid.
 In this case, the layer is parametrised by $\theta_{j} = \{W_{j}, b_{j}\}$.
@@
 Now that the conditional embedding is learned, we can perform full probabilistic inference between all the observed and hidden variables (if any) of the kernel embedding network.
+That is,
 
@@
 
-	\note{Note that while it would certainly be great, the point of developing this kernel embedding classifier is not to beat other existing classification algorithms.
+%	\note{Note that while it would certainly be great, the point of developing this kernel embedding classifier is not to beat other existing classification algorithms.
 The purpose is to develop a simple and elegant fully probabilistic multiclass classifier based on embedding the observed data directly into a reproducing kernel Hilbert space, with a quantifiable notion of model complexity.
@@
 Below is just a summary of what has been done but has not been put together neatly yet.}
-
-	\textbf{Experiments to Show}: We are aiming to do experiments on one toy dataset for illustration and visualisation, and on two real world datasets for benchmarking performance.
+%	
+%	\textbf{Experiments to Show}: We are aiming to do experiments on one toy dataset for illustration and visualisation, and on two real world datasets for benchmarking performance.
 So far, I am using the iris dataset for the toy dataset, and MNIST for one of the real world datasets.
 We should still find a third real world dataset that will really benefit from such a flexible nonparametric, probabilistic multiclass classifier.
-
-	\begin{itemize}
-		\item A toy 2D classification tasks for visualising the properties and capabilities of the kernel embedding classifier.
+%	
+%	\begin{itemize}
+%		\item A toy 2D classification tasks for visualising the properties and capabilities of the kernel embedding classifier.
 An simple example is the iris dataset, where we take only 2 attributes.
@@
 We then show that if we use the standard cross entropy loss as the objective for training, then we easily overfit the data.
-		\item We also show plots illustrating how the training objective, performance of the classifier, and the hyperparameters changes during the training procedure.
-		\item We then show results for training using SGD, which reveals that at a faster speed we arrive at the same solution as before.
-		\item We can then move on to actual real world datasets, like MNIST.
-		\item The MNIST dataset has 60000 training images and 10000 test images.
+%		\item We also show plots illustrating how the training objective, performance of the classifier, and the hyperparameters changes during the training procedure.
+%		\item We then show results for training using SGD, which reveals that at a faster speed we arrive at the same solution as before.
+%		\item We can then move on to actual real world datasets, like MNIST.
+%		\item The MNIST dataset has 60000 training images and 10000 test images.
 So far I have results for only giving the first 500 training images to the kernel embedding classifier (much smaller than the dimensionality of the problem, which is 784), and it is to perform on the whole 10000 test images.
@@
 Then also compare this to state of the art convolutional neural networks with 500 observations for training data.
-		\item More to come...
-	\end{itemize}
+%		\item We can also use the learned length scale of a stationary kernel to visualise the most discriminative pixels in the image useful to the classifier.
+%		\item More to come...
+%	\end{itemize}
 
@@
 
-%	\begin{figure}
-%		\begin{center}
-%			\includegraphics[width=0.48\linewidth]{figures/iris_2017_4_11_0_43_24_anisotropic_gd_tol_01_complexity_attributes_0_1/figure4.eps}
-%			\includegraphics[width=0.48\linewidth]{figures/iris_2017_4_11_0_43_55_anisotropic_sgd_batch_27_tol_01_complexity_attributes_0_1/figure4.eps}
-%			\includegraphics[width=0.48\linewidth]{figures/iris_2017_4_11_0_47_23_anisotropic_gd_tol_001_cross_entropy_attributes_0_1/figure4.eps}
-%			\includegraphics[width=0.48\linewidth]{figures/iris_2017_4_11_0_48_54_anisotropic_sgd_batch_27_tol_001_cross_entropy_attributes_0_1/figure4.eps}
-%		\end{center}
-%		\caption{\small Kernel Embedding Classifier}
-%		\label{fig:kec}
-%	\end{figure}
-%	
-%	\begin{figure}
-%		\begin{center}
-%			\includegraphics[width=0.9\linewidth]{figures/iris_2017_4_11_0_43_24_anisotropic_gd_tol_01_complexity_attributes_0_1/figure14.eps}
-%		\end{center}
-%		\caption{\small Kernel Embedding Classifier}
-%%		\label{fig:kec}
-%	\end{figure}
+	\begin{table}[t]
+		\begin{center}
+			\begin{tabular}{ l l || c || c c || c }
+				\hline
+				\multicolumn{6}{ c }{Classification Accuracy on UCI Datasets} \\
+				\hline
+				\hline
+%				& & & \multicolumn{2}{ c }{Accuracy} & \\
+%				\hline				
+				Dataset & & Method & Train & Test & Test (Literature) \\
+				\hline
+				\hline
+				\multirow{6}{*}{}
+				& $n = 1372$ & CE + RC & 99.59 & 100 & Artificial Neural Network: 99.78 \\
+				\texttt{banknote} & $d = 4$ & CE & 99.59 & 100 & \citep{kaya2016banknote} \\
+				& $m = 2$ & RC & 99.59 & 100 &  \\
+				\hline
+				\hline
+				\multirow{6}{*}{}
+				& $n = 336$ & CE + RC & 92.05 & 91.18 & Probabilistic Binary Tree: 81.1 \\
+				\texttt{ecoli} & $d = 7$ & CE & 94.04 & 85.29 & \citep{horton1996probabilistic} \\
+				& $m = 8$ & RC & 91.05 & 88.24 &  \\
+				\hline
+				\hline
+				\multirow{6}{*}{}
+				& $n = 150$ & CE + RC & 97.78 & 100 & SVM: 94.67 \\
+				\texttt{iris} & $d = 4$ & CE & 97.04 & 100 & \citep{koggalage2004reducing}\\
+				& $m = 3$ & RC & 97.78 & 100 & ANN: 83.33 \citep{swain2012approach} \\
+				\hline
+				\hline
+				\multirow{6}{*}{}
+				& $n = 7797$ & CE + RC &   &   & \\
+				\texttt{isolet} & $d = 617$ & CE &   &   & \\
+				& $m = 26$ & RC &   &   &  \\
+				\hline
+				\hline
+				\multirow{6}{*}{}
+				& $n = 2310$ & CE + RC & 99.37 & 97.40 & Decision Trees \& Neural Nets: \\
+				\texttt{segment} & $d = 19$ & CE & 97.84 & 96.97 &  99.14 - 99.98 \\
+				& $m = 7$ & RC & 97.35 & 96.10 & \citep{lim2000comparison} \\
+				\hline
+				\hline
+				\multirow{6}{*}{}
+				& $n = 178$ & CE + RC & 100 & 100 & RDA: 100, QDA: 99.4, \\
+				\texttt{wine} & $d = 13$ & CE & 100 & 100 & LDA: 98.9, 1NN: 96.1 \\
+				& $m = 3$ & RC & 100 & 100 & \citep{aeberhard1992comparison} \\
+				\hline
+				\hline
+				\multirow{6}{*}{}
+				& $n = 6497$ & CE + RC & & & \\
+				\texttt{wine-quality} & $d = 12$ & CE & & & \\
+				& $m = 2$ & RC & & &  \\
+				\hline
+				\hline
+				\multirow{6}{*}{}
+				& $n = 1484$ & CE + RC & 67.04 & 57.72 & Probabilistic Binary Tree: 55.0 \\
+				\texttt{yeast} & $d = 8$ & CE & 68.24 & 56.38 & \citep{horton1996probabilistic} \\
+				& $m = 10$ & RC & 62.25 & 56.38 &  \\
+				\hline
+				\hline
+			\end{tabular}
+		\end{center}
+		\caption{Classification Accuracy of the Kernel Embedding Classifier on standard UCI Datasets.}
+		\label{tab:experiments}
+	\end{table}
 
@@
 
-			Therefore, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, $\hat{p}_{c}$ converges uniformly to $p_{c}$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$
+			Therefore, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, $\hat{p}_{c}$ converges uniformly to $p_{c}$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
 
@@
 
-			Now, since $l = \delta$ is bounded, so is $\hat{\mu}_{Y | X = x}(c) = \sum_{i = 1}^{n} w_{i} \delta(y_{i}, c)$ for some embedding weights $w_{i}$ and all $c \in \mathbb{N}_{m}$, and thus its RKHS norm is finite.
+			Now, since $l = \delta$ is bounded, so is $\hat{\mu}_{Y | X = x}(c) = \sum_{i = 1}^{n} w_{i} \delta(y_{i}, c)$ for some embedding weights $w_{i}$ and all $c \in \mathbb{N}_{m}$, and thus its RKHS norm is finite for all $n \in \mathbb{N}_{n}$.
 Similarly, assuming that $p_{c}(x)$ is never exactly zero, $u_{x}(c)$ is also finite for all $c \in \mathbb{N}_{m}$ and thus so is its RKHS norm.
@@
 				&= \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| u_{x} \|_{\mathcal{H}_{\delta}} \\
-				&= ( \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| u_{x} \|_{\mathcal{H}_{\delta}} ) \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} \\
+				&= ( \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| u_{x} \|_{\mathcal{H}_{\delta}} ) \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}. \\
 			\end{aligned}

### 2017-05-10 kernel_embedding_classifier.tex
Add first iteration of special cases and most importantly bounds theorems!

@@
 \newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{claim}{Claim}[section]
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{claim}[theorem]{Claim}
 
@@
 
-\title{CAKE: Classification avec Kernel Embeddings \\ with Rademacher Complexity Bounds}
+\title{CAKE: Classification avec Kernel Embeddings \\ with Rademacher complexity bounds}
 
@@
 \end{abstract}
-	\note{Alternative Paper Names: \\ 
-		\begin{itemize}
-			\item (Original Name) Probabilistic Multiclass Kernel Embedding Classifier
-			\item CAKE: Classification avec Kernel Embeddings
-			\item CAKE: Classification avec Kernel Embeddings: A Principled Probabilistic Nonparametric Multiclass Classifier
-			\item Probabilistic Nonparametric Multiclass Classification with Kernel Embeddings of Conditional Distributions
-			\item The Kernel Embedding Classifier
-			\item Probabilistic Classification via Hilbert Space Embeddings
-			\item Probabilistic Classification with Kernel Embeddings under Rademacher Complexity
-			\item ...
-		\end{itemize}
-		Simple acronyms makes it all the more memorable and fun :) %When the draft is done I might actually just replace KEC (Kernel Embedding Classifier) with CAKE (Classification avec Kernel Embeddings).
-	}
-
-	Current state of the paper
-
-	\begin{itemize}
-		\item Introduction: Completed, but may need more discussion on motivation and related work.
-		\item Hilbert Space Embeddings of Conditional Probability Distributions (Background): Completed.
-		\item Classification avec Kernel Embeddings: Completed.
-		\item Information Entropy: Completed. There is a subsection for cross entropy and KL divergence that I am not sure if I want to include it in the paper so I have not written it yet.
-		\item Hyperparameter Learning with Rademacher Complexity Bounds: Completed.
-The subsection for mini-batch stochastic gradient descent current contains not-so-polished speculative discussion on the technique.
-		\item End-to-End Classifier Training for Deep Kernel Embedding Network: Draft not completed. Perhaps 1/3 done.
-		\item Full Probabilistic Inference and Mode Reconstruction: Not completed.
-		\item Experiments: Currently only has an outline of what to put into this section.
-		\item Conclusion: Current has notes on what to mention when the paper is done. Also has a detailed list of possible future work to the paper.
-		\item Appendix: Theorems and Derivations: Completed.
-		\item Appendix: Design Choices: Rough unpolished draft.
-	\end{itemize}
+
+- We address the need for a principled way of obtaining probabilistic outputs from a multiclass classifier.
+- It works in domains with not a lot of data, and we later provide a way for which it can scale
+- We address hyperparameter learning for a kernel embedding model
+- We do not rely on priors
+
 \section{Introduction}
@@
 
-\section{Hilbert Space Embeddings of Conditional Probability Distributions}
-\label{sec:background}
-
-	We begin by providing an overview of Hilbert space embeddings, where probability distributions are represented by mean embeddings in a reproducing kernel Hilbert space (RKHS) through positive definite kernels.
-Specifically, in the supervised learning context for which we are primarily interested in, we focus on conditional distributions and its representations in the RKHS.
-
-	To construct a conditional embedding map $\mathcal{U}_{Y | X}$ corresponding to the distribution $\mathbb{P}_{Y | X}$ where $X : \Omega \to \mathcal{X}$ and $Y: \Omega \to \mathcal{Y}$ are measurable random variables, we choose a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ for the input space $\mathcal{X}$ and another kernel $l : \mathcal{Y} \times \mathcal{Y} \to \mathbb{R}$ for the output space $\mathcal{Y}$.
-These kernels $k$ and $l$ each describe how similarity is measured within each of their respective domains $\mathcal{X}$ and $\mathcal{Y}$, and are symmetric and positive definite such that they uniquely define the RKHS $\mathcal{H}_{k}$ and $\mathcal{H}_{l}$.
-Such a conditional embedding map is then defined by
-
-	\begin{equation}
-		\mathcal{U}_{Y | X} := C_{YX} C_{XX}^{-1},
-	\label{eq:conditional_embedding}
-	\end{equation}
-
-	where $C_{YX} := \mathbb{E}[l(Y, \cdot) \otimes k(X, \cdot)]$ and $C_{XX} := \mathbb{E}[k(X, \cdot) \otimes k(X, \cdot)]$ \citep{song2009hilbert}.
-The conditional embedding map can be seen as an operator map from $\mathcal{H}_{k}$ to $\mathcal{H}_{l}$.
-In this sense, it sweeps out a family of conditional embeddings $\mu_{Y | X = x}$ in $\mathcal{H}_{l}$, each indexed by the input variable $x$, via the property $\mu_{Y | X = x} := \mathbb{E}[l(Y, \cdot) | X = x] = \mathcal{U}_{Y | X} k(x, \cdot)$.
-
-	Under the assumption that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$, \cite{song2009hilbert} proved that the conditional expectation of a function $g \in \mathcal{H}_{l}$ can be expressed as an inner product,  % Theorem 4
-
-	\begin{equation}
-		\mathbb{E}[g(Y) | X = x] = \langle \mu_{Y | X = x}, g \rangle.
-	\label{eq:conditional_expectation}
-	\end{equation}
-
-	While the assumptions that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$ and $k(x, \cdot) \in \mathrm{image}(C_{XX})$ holds for finite input domains $\mathcal{X}$ for characteristic kernels $k$, it is not necessarily true when $\mathcal{X}$ is a continuous domain \citep{fukumizu2004dimensionality}, which is the scenario for many classification problems.
-In this case, $C_{YX} C_{XX}^{-1}$ becomes only an approximation to $\mathcal{U}_{Y | X}$, and we instead regularise the inverse and use $C_{YX} (C_{XX} + \lambda I)^{-1}$, which also serves to avoid overfitting \citep[p.
-13]{song2013kernel}.
-
-	On top of this, in practice we do not have access to the distribution $\mathbb{P}_{X Y}$ to compute such expectations from the definitions of $C_{YX}$ and $C_{XX}$.
-Instead, we have a finite collection of data points $\{x_{i}, y_{i}\} \in \mathcal{X} \times \mathcal{Y}$, $i \in \mathbb{N}_{n} := \{1, \dots, n\}$, for which the conditional embedding map $\mathcal{U}_{Y | X}$ can be estimated by
-
-	\begin{equation}
-		\hat{\mathcal{U}}_{Y | X} = \Psi (K + n \lambda I)^{-1} \Phi^{T},
-	\label{eq:empirical_conditional_embedding}
-	\end{equation}
-
-	where $K := \{k(x_{i}, x_{j})\}_{i = 1, j = 1}^{n, n}$, $\Phi := \begin{bmatrix} k(x_{1}, \cdot) & \dots & k(x_{n}, \cdot) \end{bmatrix}$, $\Psi := \begin{bmatrix} l(y_{1}, \cdot) & \dots & l(y_{n}, \cdot) \end{bmatrix}$, and $\lambda$ is the regularisation parameter for the conditional operator \citep{song2013kernel}.
-We then define the empirical conditional embedding by $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$, which stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \citep{song2009hilbert}.
-That is, % Theorem 6
-
-	\begin{equation}
-		\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists M_{\epsilon} > 0 \quad s.t.
-\quad \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
-	\label{eq:empirical_conditional_embedding_stochastic_convergence}
-	\end{equation}
-
-	This allows us to approximate the conditional expectation \eqref{eq:conditional_expectation} with $\langle \hat{\mu}_{Y | X = x}, g \rangle$ instead,
-
-	\begin{equation}
-		\mathbb{E}[g(Y) | X = x] \approx \langle \hat{\mu}_{Y | X = x}, g \rangle = \bvec{g}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x},
-	\label{eq:empirical_conditional_expectation}
-	\end{equation}
-
-	where $\bvec{g} := \{g(y_{i})\}_{i = 1}^{n}$ and $\bvec{k}_{x} := \{k(x_{i}, x\}_{i = 1}^{n}$, knowing that it would converge to the true expectation as $n$ increases for sufficiently small $\lambda$.
-
-	\note{Note: I believe \eqref{eq:empirical_conditional_expectation} is a very well known result.
-It is very easy to derive.
-However, I have not found a paper that explicitly states this as a result or theorem yet.
-Perhaps I will include a short derivation of this in the appendix if we find it necessary.}
-
-%	The conditional operator $C_{Y X} C^{-1}_{XX}$ only acts as an approximation of the conditional mean embedding $C_{Y | X}$ for continuous domains because the assumption that for all $g \in \mathcal{H}_{l}$ , the conditional expectation $\mathbb{E}[g(Y) | X = \cdot]$ is an element of $\mathcal{H}_{k}$ may not hold in general \citep{fukumizu2004dimensionality, song2009hilbert}.
-It also serves to avoid overfitting \citep[p.
-13]{song2013kernel}.
-
-\section{Classification avec Kernel Embeddings}
-\label{sec:kernel_embedding_classifier}
-
-	In this section, we formulate a kernel embedding based probabilistic classifier by casting it into the conditional embedding framework.
-
-	In the multiclass classification context, the output label space is finite and discrete, taking values only in $\mathcal{Y} = \mathbb{N}_{m} := \{1, \dots, m\}$.
-Naturally, we first choose the Kronecker delta kernel $\delta : \mathbb{N}_{m} \times \mathbb{N}_{m} \to \{0, 1\}$ as the output kernel $l$, where labels that are the same has unit similarity and labels that are different have no similarity.
-That is, for all pairs of labels $y_{i}, y_{j} \in \mathcal{Y}$,
-
-	\begin{equation}
-		\delta(y_{i}, y_{j}) = \begin{cases}
-		1 & \mathrm{if } \quad y_{i} = y_{j}, \\
-		0 & \mathrm{otherwise}.
-		\end{cases}
-	\end{equation}
-
-	As $\delta$ is an integrally strictly positive definite kernel on $\mathbb{N}_{m}$, it is therefore characteristic \citep[Theorem 7]{sriperumbudur2010hilbert}.
-As such, by definition of characteristic kernels, $\delta$ uniquely defines a RKHS $\mathcal{H}_{\delta}$ \citep{fukumizu2004dimensionality}.
-Notice that this kernel has no parameters, so that the model hyperparameters only come from the kernel of the input space and the regularisation parameter $\lambda$.
-
-	Recall that the RKHS induced by a positive definite kernel is the closure of the span of its kernel induced features \citep{xu2009refinement}, so that $\mathcal{H}_{l} = \overline{\mathrm{span}\{l(y, \cdot) : y \in \mathcal{Y}\}}$.
-For $\mathcal{Y} = \mathbb{N}_{m}$ and $l = \delta$, this means that any real-valued function $g : \mathbb{N}_{m} \to \mathbb{R}$ that is bounded on its discrete domain $\mathbb{N}_{m}$ is in the RKHS of $\delta$, because we can always write $g = \sum_{y = 1}^{m} g(y) \delta(y, \cdot) \in \mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}$.
-
-	In particular, indicator functions on $\mathbb{N}_{m}$ are in the RKHS $\mathcal{H}_{\delta}$, since
-
-	\begin{equation}
-		\mathbb{1}_{c}(y) = \begin{cases}
-		1 & \mathrm{if } \quad y = c \\
-		0 & \mathrm{otherwise}
-		\end{cases} = \delta(c, y).
-	\label{eq:indicator_function}
-	\end{equation}
-
-	That is, indicator functions $\mathbb{1}_{c} = \delta(c, \cdot)$, $c \in \mathbb{N}_{m}$ are simply the canonical kernel features of $\mathcal{H}_{\delta}$.
-
-	While such properties does not becessarily hold for continuous domains in general, this convenient property in the case of a discrete domain $\mathcal{Y}$ with a Kronecker delta kernel $\delta$ is what allows consistent estimations of decision probabilities used in multiclass classification, which we turn to next.
-
-	Let $p_{c}(x) := \mathbb{P}[Y = c | X = x]$ be the \textit{decision probability function} for class $c \in \mathbb{N}_{m}$, which is the probability of the class label $Y$ being $c$ when the example $X$ is $x$.
-We begin by writing this probability as an expectation of indicator functions,
-
-	\begin{equation}
-		p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mathbb{P}[Y \in \{c\} | X = x] = \mathbb{E}[\mathbb{1}_{c}(Y) | X = x].
-	\label{eq:decision_probability}
-	\end{equation}
-
-	With $\mathbb{1}_{c} \in \mathcal{H}_{\delta}$, we let $g = \mathbb{1}_{c}$ in \eqref{eq:empirical_conditional_expectation} and $\bvec{1}_{c} := \{\mathbb{1}_{c}(y_{i})\}_{i = 1}^{n}$ to estimate the right hand side of \eqref{eq:decision_probability} by
-
-	\begin{equation}
-		\hat{p}_{c}(x) = f_{c}(x) := \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x}.
-	\label{eq:empirical_decision_probability}
-	\end{equation}
-
-	Therefore, the vector of empirical decision probability functions over the possible classes $c \in \mathbb{N}_{m}$ is
-
-	\begin{equation}
-		\hat{\bvec{p}}(x) = \bvec{f}(x) := B^{T} (K + n \lambda I)^{-1} \bvec{k}_{x} \in \mathbb{R}^{m},
-	\label{eq:empirical_decision_probability_vector}
-	\end{equation}
-
-	where $B = \begin{bmatrix} \bvec{1}_{1} & \bvec{1}_{2} & \cdots & \bvec{1}_{m} \end{bmatrix} \in \{0, 1\}^{n \times m}$, which is simply the one hot encoding form for the training labels $\{y_{i}\}_{i = 1}^{n}$.
-This can be further vectorised over multiple query points $\{x^{\star}_{j}\}_{j = 1}^{n^{\star}}$ through
-
-	\begin{equation}
-		\hat{P}^{\star} = B^{T} (K + n \lambda I)^{-1} K^{\star} \in \mathbb{R}^{m},
-	\label{eq:empirical_decision_probability_matrix}
-	\end{equation}
-
-	where $K^{\star} = \{k(x_{i}, x_{j}^{\star})\}_{i = 1, j = 1}^{n, n^{\star}}$ and $n^{\star}$ is the number of query points.
-
-	Finally, to perform classification, we simply take the class with the highest empirical decision probability for the given query point $x^{\star} \in \mathcal{X}$,
-
-	\begin{equation}
-		\hat{y}^{\star} = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x^{\star}).
-	\label{eq:classification}
-	\end{equation}
-
-	We proceed to show that the empirical decision probabilities given by \eqref{eq:empirical_decision_probability} is a consistent estimator for the actual decision probabilities as the dataset increases.
-
-	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
-		\label{thm:probability_convergence_copy}
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-
-		\begin{proof}
-			See \cref{thm:probability_convergence} of \cref{app:theorems_derivations}.
-		\end{proof}
-	\end{theorem}
-
-	While the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ will converge to the true decision probability function  $p_{c} : \mathcal{X} \to [0, 1]$ in the limit, for finite $n$ and a given regulariser $\lambda > 0$, the stochasticity in the empirical estimates implies that these probabilities may not necessarily sum up to one, nor are they strictly restricted to the range $[0, 1]$.
-However, they will usually be very close to the true predicted probabilities.
-Moreover, such stochasticity also does not principally affect the classification prediction, since we simply take the argmax of the empirical decision probability vector as in \eqref{eq:classification}.
-
-	If strict, valid probabilities are required for interpretation, visualisation, or other purposes, the probabilities can be clipped at zero then normalised to one - a procedure we refer to as \textit{clip-normalisation},
-
-	\begin{equation}
-		\tilde{p}_{c}(x) := \frac{\max\{\hat{p}_{c}(x), 0\}}{\sum_{j = 1}^{m} \max\{\hat{p}_{j}(x), 0\}}.
-	\label{eq:probability_clip_normalise}
-	\end{equation}
-
-	Notice that for classification prediction, the argmax solution over the classes of the empirical decision probabilities \eqref{eq:empirical_decision_probability} and its clip-normalised version \eqref{eq:probability_clip_normalise} remain the same.
-Furthermore, since $\hat{p}_{c}(x)$ converges to valid probabilities $p_{c}(x)$ according to \cref{thm:probability_convergence}, the effect of clip-normalisation reduces as $n$ increases such that $\tilde{p}_{c}(x)$ becomes very close to $\hat{p}_{c}(x)$ and $p_{c}(x)$.
-Experiments verify that clip-normalisation only adjusts the probabilities slightly, as the empirical estimates are usually already close to satisfying normalisation and range properties (see \cref{app:design_choices}).
-
-\section{Information Entropy}
-\label{sec:information_entropy}
-
-	The kernel embedding classifier provides decision probabilities instead of just a single label prediction.
-Such a probabilistic classifier allows us to quantify the uncertainty of its predictions for any given example $x \in \mathcal{X}$ through the information entropy \citep{shannon1951prediction, jaynes1957information}.
-This is ideal for detecting the decision boundaries of the classifier and areas of low data density.
-
-	We present two main approaches for inferring the information entropy from the classifier.
-Specifically, we would like to infer estimates for $h(x) := \mathbb{H}[Y | X = x] = - \sum_{c = 1}^{m} p_{c}(x) \log{p_{c}(x)} $, the information entropy of the possible labels $Y$ for a given example $X = x$.
-
-	The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref{eq:probability_clip_normalise}, at the query point $x \in \mathcal{X}$,
-
-	\begin{equation}
-		\tilde{h}(x) := - \sum_{c = 1}^{m} \tilde{p}_{c}(x) \log{\tilde{p}_{c}(x)}.
-	\label{eq:entropy_clip_normalise}
-	\end{equation}
-
-	We call \eqref{eq:entropy_clip_normalise} the \textit{clip-normalised information entropy}.
-Since $\tilde{p}_{c}(x)$ converges pointwise to $p_{c}(x)$ with increasing data, $\tilde{h}(x)$ also converges pointwise to $h(x)$.
-
-	Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information \footnote{Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$.},
-
-	\begin{equation}
-	\begin{aligned}
-		\mathbb{H}[Y | X = x] &= - \sum_{c = 1}^{m} \mathbb{P}[Y = c| X = x] \log{\mathbb{P}[Y = c | X = x]} \\
-		&= \mathbb{E}[- \log{\mathbb{P}[Y | X = x]} | X = x] \\
-		&= \mathbb{E}[u_{x}(Y) | X = x],
-	\end{aligned}
-	\end{equation}
-
-	where $u_{x}(y) := - \log{\mathbb{P}[Y = y | X = x]}$ is the \textit{information} (in nats) we would gain when we discover that example $x$ actually has label $y$.
-If $u_{x} : \mathbb{N}_{m} \to \mathbb{R}$ is in the RKHS $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by $\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle$.
-This is the basis of our second approach.
-
-	Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$.
-We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the RKHS.
-Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref{eq:empirical_conditional_expectation} and estimate $h(x)$ by
-
-	\begin{equation}
-		\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle = \bvec{u}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x}.
-	\end{equation}
-
-	Unfortunately, $u_{x}$ is not known exactly, since $\mathbb{P}[Y = y | X = x]$ is not known exactly.
-Instead, since $\hat{p}_{c}(x)$ is a consistent estimate for $\mathbb{P}[Y = c | X = x]$ by \cref{thm:probability_convergence}, we propose to replace $u_{x}(y)$ with the negative log of $\hat{p}_{y}(x)$.
-However, we cannot simply take the log of this estimator, as $\hat{p}_{y}(x)$ may produce non-positive estimates to the prediction probabilities.
-The straight forward way to mitigate this problem is to clip $\hat{p}_{y}(x)$ from the bottom by a very small number, before taking the log.
-However, experiments show that this produces non-smooth estimates over $\mathcal{X}$ and the degree of smoothness varies drastically between different choices of that small number (see \cref{app:design_choices}).
-Instead, in virtue of the fact that $\lim_{p \to 0} - p \log{p} = 0$ even though $\lim_{p \to 0} - \log{p} = \infty$, we simply define the information estimate $\hat{u}_{x}(y)$ as zero if the empirical decision probability is non-positive,
-
-	\begin{equation}
-		\hat{u}_{x}(y) := \begin{cases}
-		- \log{\hat{p}_{y}(x)} & \mathrm{if } \quad \hat{p}_{y}(x) > 0 \\
-		0 & \mathrm{otherwise}. \end{cases}
-	\label{eq:empirical_information}
-	\end{equation}
-
-	It remains to show that $\hat{u}_{x} \in \mathcal{H}_{\delta}$.
-Indeed, the identity $\hat{u}_{x} = \sum_{c = 1}^{m} \hat{u}_{x}(c) \delta(c, \cdot)$ holds and thus $\hat{u}_{x}$ is in the span of the kernel canonical features.
-We then arrive at the following estimate for $h(x)$,
-
-	\begin{equation}
-		\hat{h}(x) := \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle = \hat{\bvec{u}}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x},
-		\label{eq:empirical_information_entropy}
-	\end{equation}
-
-	where $\hat{\bvec{u}}_{x} := \{\hat{u}_{x}(y_{i})\}_{i = 1}^{n}$.
-Similar to the case with decision probabilities \eqref{eq:decision_probability}, the information entropy estimate \eqref{eq:empirical_information_entropy} is not guaranteed to be non-negative.
-However, in practice these negative values are close to zero.
-Furthermore, negative estimated information entropy implies that the model is very confident about its prediction, and it suffices to simply clip the entropy at zero if strict information entropy is required (see \cref{app:design_choices}).
-We give the proof of convergence of \eqref{eq:empirical_information_entropy} in \cref{app:theorems_derivations}.
-
-	\begin{theorem}[Uniform Convergence of Empirical Information Entropy Function]
-		\label{thm:entropy_convergence_copy}
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical information entropy function $\hat{h} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_information_entropy} converges uniformly to the true information entropy function $h : \mathcal{X} \to [0, \infty)$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-
-		\begin{proof}
-			See \cref{thm:entropy_convergence} in \cref{app:theorems_derivations}.
-		\end{proof}
-	\end{theorem}
-
-	\subsection{Cross Entropy and Kullback–Leibler Divergence between Input Instances}
-
-		\note{Note: A very simple extension to the above is the cross entropy and Kullback-Leibler divergence between two input location $x, x' \in \mathcal{X}$.
-The convergence proof is basically identical.
-However, I am not sure how useful this result would be in practice.
-What would be more useful, in my opinion, is the joint entropy of multiple input locations.}
-\section{Hyperparameter Learning with Rademacher Complexity Bounds}
-\label{sec:hyperparameter_learning}
-
-	The formulation of the kernel embedding classifier requires the specification of a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ over the input space $\mathcal{X}$, or rather, a class of kernels $\{k_{\theta}\}_{\theta \in \Theta}$ parametrised by the kernel parameters $\theta \in \Theta$.
-It also requires the specification of a regularisation parameter $\lambda$ for the conditional embedding as in \eqref{eq:empirical_conditional_embedding}.
-These are hyperparameters of the kernel embedding classifier which needs to be learned in order to produce a reasonable model with high prediction accuracy.
-
-	In the kernel embedding literature, hyperparameters has been notoriously difficult to tune, and its learning is usually only restricted to inelegant methods such as cross validation with either some form of misclassification loss or the negative log probability (cross entropy) loss as the objective.
-
-%	Inspired by the log marginal likelihood learning objective used to learn the hyperparameters of a Gaussian process \citep{rasmussen2006gaussian}, \cite{flaxman2016bayesian} derived a log marginal likelihood expression for kernel embeddings by placing a Gaussian process prior on the mean embedding, and constructing a Gaussian likelihood of the empirical mean embedding given the true mean embedding.
-With a Gaussian prior and a Gaussian likelihood, inference becomes tractable and a closed form solution to the corresponding log marginal likelihood objective can be obtained with a slight change of variable factor.
-However, this formulation is only capable of learning the kernel parameters of a joint embedding, and not the kernel and regularisation parameters of a conditional embedding.
-
-	In this paper, we take a learning theoretic approach to learn the hyperparameters of the KEC, inspired by the original training procedure of support vector classifiers (SVC) as described by \cite[p.
-185]{m2001introduction}.
-Assuming a perfectly separable case, the training of a SVC begins by introducing a \textit{prediction constraint} on the training set, where the classifier is constrained to correctly classify all the available training examples.
-The strategy is to minimise the \textit{complexity} of the SVC model while ensuring perfect classification over training examples.
-The model complexity in the SVC context is measured by the VC dimension $h$ of the binary classifier, which has an upper bound $h \leq \lVert \bvec{w} \rVert^{2} R^{2} + 1$.
-Since it is difficult to compute the VC dimension explicitly, we instead minimise its upper bound, which is equivalent to and leads to the common interpretation of maximising the margin $\frac{2}{\lVert \bvec{w} \rVert}$.
-
-	Similarly, we propose to train our kernel embedding classifier with the same high level formulation: minimise the model complexity without compromising classification performance on the training data.
-Instead of employing the VC dimension as the complexity measure of our model, which is defined mainly for binary classifiers, we consider the \textit{Rademacher complexity} of the kernel embedding classifier.
-\cite[Theorem 5]{bartlett2002rademacher} has shown that the test error for a class of functions, such as a classifier, is stochastically bounded by the training error plus a term that is monotonically increasing with the Rademacher complexity and a constant, similar to the case with the VC dimension.
-As such, if we can minimise the model complexity in the sense of the Rademacher complexity while maintaining a low training error, we can optimise generalisation ability in the sense of low expected test error.
-
-%	For a multi-label predictor parametrised as $f(x; W) = W^{T} x$ where $W \in \mathbb{R}^{d \times L}$ and $L$ is the number of target binary labels,  \cite{yu2014large} showed that the global Rademacher complexity of $W$ is upper-bounded in terms of its trace norm, $\mathrm{trace}(W^{T} W)$.
-Albeit formulated for multiclass instead of multi-label prediction, the empirical decision probabilities \eqref{eq:empirical_decision_probability_vector} also has the same analytical form, where the input $x$ is replaced by some feature vector $\phi(x)$.
-
-%	\begin{algorithm}[tb]
-%		\caption{Kernel Embedding Classifier Training with Gradient Descent}
-%		\label{alg:training_gradient_descent}
-%		\begin{algorithmic}[1]
-%			\STATE {\bfseries Input:} kernel family $k_{\theta}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial kernel parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$
-%			\STATE $\theta \leftarrow \theta_{0}$
-%			\STATE $\lambda \leftarrow \lambda_{0}$
-%			\REPEAT
-%			\STATE $B \leftarrow \{\delta(y_{i}, c) : i \in \mathbb{N}_{n}, c \in \mathbb{N}_{m}\} \in \{0, 1\}^{n \times m} $ 
-%			\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathbb{N}_{n}, j \in \mathbb{N}_{n}\} \in \mathbb{R}^{n \times n}$
-%			\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n \lambda I)$
-%			\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash B)$
-%			\STATE $r(\theta, \lambda) \leftarrow \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
-%			\STATE $\theta \leftarrow \theta - \eta \frac{\partial r}{\partial \theta}(\theta, \lambda)$
-%			\STATE $\lambda \leftarrow \lambda - \eta \frac{\partial r}{\partial \lambda}(\theta, \lambda)$
-%			\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial r}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial r}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{1} < \epsilon$}
-%			\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
-%		\end{algorithmic}
-%	\end{algorithm}
-
-	For a predictor parametrised as $f(x; W) = W^{T} x$, \cite{yu2014large} showed that the global Rademacher complexity of $W$ is upper-bounded in terms of its trace norm, $\sqrt{\mathrm{trace}(W^{T} W)}$.
-This was originally discussed in the context of multi-label classification, where $W \in \mathbb{R}^{d \times L}$ and $f$ produces a binary vector of length $L$ indicating the multiple labels that describes the input $x \in \mathbb{R}^{d}$.
-In the context of the kernel embedding classifier, the empirical decision probabilities \eqref{eq:empirical_decision_probability_vector} also has the same analytical form, where the input $x$ is replaced by some feature vector $\phi(x)$.
-By using the canonical feature map $\phi(x) = k(x, \cdot)$ and the reproducing property $\langle \phi(x), \phi(x') \rangle = k(x, x')$ in the RKHS, we can write \eqref{eq:empirical_decision_probability_vector} as $\hat{\bvec{p}}(x) = \bvec{f}(x) := B^{T} (K + n \lambda I)^{-1} \Phi^{T} \phi(x) = W^{T} \phi(x)$, where instead of mapping input examples in $\mathbb{R}^{d}$ to output multi-label vector $\mathbb{R}^{L}$, $W^{T}$ maps features in the RKHS $\mathcal{H}_{k}$ to the a vector of multiclass probabilities in $\mathbb{R}^{m}$.
-Using the reproducing property $K = \Phi^{T} \Phi$ again, the squared trace norm for such a predictor is then $\mathrm{trace}(W^{T} W) = \mathrm{trace}(B^{T} (K + n \lambda I)^{-1} K (K + n \lambda I)^{-1} B)$.
-We therefore propose to use this quantity as an upper bound measure of the kernel embedding classifier model complexity, which is to be minimised for hyperparameter training,
-
-	\begin{equation}
-		\min_{\theta \in \Theta, \lambda \in (0, \infty)} \sqrt{\mathrm{trace}\bigg(B^{T} (K_{\theta} + n \lambda I)^{-1} K_{\theta} (K_{\theta} + n \lambda I)^{-1} B\bigg)},
-	\label{eq:trace_norm_optimisation}
-	\end{equation}
-
-	where we use the subscript $\theta$ to make explicit the dependence on the kernel parameters.
-We employ gradient descent to train the kernel embedding classifier with this complexity bound objective.
-The gradients of the complexity bound objective with respect to the hyperparameters is to be computed automatically using standard back-propagation.
-
-	While it may be tempting to instead minimise the square of the trace norm \eqref{eq:trace_norm_optimisation} to remove the square root, experiments show that, without the square root, the magnitude of the gradients grows large at regions of higher trace norms.
-For instance, this can happen when the optimisation is initialised at a location far away from the optimum.
-This makes the optimisation unstable, and may cause the hyperparameters to diverge to a numerically unstable scenario where the Cholesky decomposition of the regularised gram matrix does not exist.
-That being said, one can instead choose to minimise the log of the squared trace norm, $\log{\mathrm{trace}(B^{T} (K + n \lambda I)^{-1} K (K + n \lambda I)^{-1} B)}$, which experiments show are also quite numerically stable during optimisation.
-
-	If one were to follow the philosophy of minimising the model complexity without compromising performance on training data, then either a further training performance constraint should be added to the optimisation, or a training error term should be added to the objective.
-However, we found that this was unnecessary for the kernel embedding classifier.
-We postulate that minimising the model complexity, or the upper bound thereof, is both sufficient and desirable for a classifier that is to generalise classification performance to new test examples.
-
 	Contrary to parametric models, kernel methods are nonparametric, and thus its model capacity grows with increasing data.
@@
 
+\section{Hilbert Space Embeddings of Conditional Probability Distributions}
+\label{sec:background}
+
+	We begin by providing an overview of Hilbert space embeddings, where probability distributions are represented by mean embeddings in a reproducing kernel Hilbert space (RKHS) through positive definite kernels.
+Specifically, in the supervised learning context for which we are primarily interested in, we focus on conditional distributions and its representations in the RKHS.
+
+	To construct a conditional embedding map $\mathcal{U}_{Y | X}$ corresponding to the distribution $\mathbb{P}_{Y | X}$ where $X : \Omega \to \mathcal{X}$ and $Y: \Omega \to \mathcal{Y}$ are measurable random variables, we choose a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ for the input space $\mathcal{X}$ and another kernel $l : \mathcal{Y} \times \mathcal{Y} \to \mathbb{R}$ for the output space $\mathcal{Y}$.
+These kernels $k$ and $l$ each describe how similarity is measured within each of their respective domains $\mathcal{X}$ and $\mathcal{Y}$, and are symmetric and positive definite such that they uniquely define the RKHS $\mathcal{H}_{k}$ and $\mathcal{H}_{l}$.
+Such a conditional embedding map is then defined by
+	\begin{equation}
+		\mathcal{U}_{Y | X} := C_{YX} C_{XX}^{-1},
+	\label{eq:conditional_embedding}
+	\end{equation}
+	where $C_{YX} := \mathbb{E}[l(Y, \cdot) \otimes k(X, \cdot)]$ and $C_{XX} := \mathbb{E}[k(X, \cdot) \otimes k(X, \cdot)]$ \citep{song2009hilbert}.
+The conditional embedding map can be seen as an operator map from $\mathcal{H}_{k}$ to $\mathcal{H}_{l}$.
+In this sense, it sweeps out a family of conditional embeddings $\mu_{Y | X = x}$ in $\mathcal{H}_{l}$, each indexed by the input variable $x$, via the property $\mu_{Y | X = x} := \mathbb{E}[l(Y, \cdot) | X = x] = \mathcal{U}_{Y | X} k(x, \cdot)$.
+
+	Under the assumption that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$, \cite{song2009hilbert} proved that the conditional expectation of a function $g \in \mathcal{H}_{l}$ can be expressed as an inner product,  % Theorem 4
+	\begin{equation}
+		\mathbb{E}[g(Y) | X = x] = \langle \mu_{Y | X = x}, g \rangle.
+	\label{eq:conditional_expectation}
+	\end{equation}
+	While the assumptions that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$ and $k(x, \cdot) \in \mathrm{image}(C_{XX})$ holds for finite input domains $\mathcal{X}$ for characteristic kernels $k$, it is not necessarily true when $\mathcal{X}$ is a continuous domain \citep{fukumizu2004dimensionality}, which is the scenario for many classification problems.
+In this case, $C_{YX} C_{XX}^{-1}$ becomes only an approximation to $\mathcal{U}_{Y | X}$, and we instead regularise the inverse and use $C_{YX} (C_{XX} + \lambda I)^{-1}$, which also serves to avoid overfitting \citep[p.
+13]{song2013kernel}.
+
+	On top of this, in practice we do not have access to the distribution $\mathbb{P}_{X Y}$ to compute such expectations from the definitions of $C_{YX}$ and $C_{XX}$.
+Instead, we have a finite collection of data points $\{x_{i}, y_{i}\} \in \mathcal{X} \times \mathcal{Y}$, $i \in \mathbb{N}_{n} := \{1, \dots, n\}$, for which the conditional embedding map $\mathcal{U}_{Y | X}$ can be estimated by
+	\begin{equation}
+		\hat{\mathcal{U}}_{Y | X} = \Psi (K + n \lambda I)^{-1} \Phi^{T},
+	\label{eq:empirical_conditional_embedding}
+	\end{equation}
+	where $K := \{k(x_{i}, x_{j})\}_{i = 1, j = 1}^{n, n}$, $\Phi := \begin{bmatrix} k(x_{1}, \cdot) & \dots & k(x_{n}, \cdot) \end{bmatrix}$, $\Psi := \begin{bmatrix} l(y_{1}, \cdot) & \dots & l(y_{n}, \cdot) \end{bmatrix}$, and $\lambda$ is the regularisation parameter for the conditional operator \citep{song2013kernel}.
+We then define the empirical conditional embedding by $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$, which stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \citep{song2009hilbert}.
+That is, % Theorem 6
+	\begin{equation}
+		\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists M_{\epsilon} > 0 \quad s.t.
+\quad \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
+	\label{eq:empirical_conditional_embedding_stochastic_convergence}
+	\end{equation}
+	This allows us to approximate the conditional expectation \eqref{eq:conditional_expectation} with $\langle \hat{\mu}_{Y | X = x}, g \rangle$ instead, 
+	\begin{equation}
+		\mathbb{E}[g(Y) | X = x] \approx \langle \hat{\mu}_{Y | X = x}, g \rangle = \bvec{g}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x},
+	\label{eq:empirical_conditional_expectation}
+	\end{equation}
+	where $\bvec{g} := \{g(y_{i})\}_{i = 1}^{n}$ and $\bvec{k}_{x} := \{k(x_{i}, x\}_{i = 1}^{n}$, knowing that it would converge to the true expectation as $n$ increases for sufficiently small $\lambda$.
+
+\section{Kernel Embedding Classifier}
+\label{sec:kernel_embedding_classifier}
+
+	In this section, we formulate a kernel embedding based probabilistic classifier by casting it into the conditional embedding framework.
+
+	In the multiclass classification context, the output label space is finite and discrete, taking values only in $\mathcal{Y} = \mathbb{N}_{m} := \{1, \dots, m\}$.
+Naturally, we first choose the Kronecker delta kernel $\delta : \mathbb{N}_{m} \times \mathbb{N}_{m} \to \{0, 1\}$ as the output kernel $l$, where labels that are the same has unit similarity and labels that are different have no similarity.
+That is, for all pairs of labels $y_{i}, y_{j} \in \mathcal{Y}$,
+	\begin{equation}
+		\delta(y_{i}, y_{j}) := \begin{cases}
+		1 & \mathrm{if } \quad y_{i} = y_{j}, \\
+		0 & \mathrm{otherwise}.
+		\end{cases}
+	\end{equation}
+	As $\delta$ is an integrally strictly positive definite kernel on $\mathbb{N}_{m}$, it is therefore characteristic \citep[Theorem 7]{sriperumbudur2010hilbert}.
+As such, by definition of characteristic kernels, $\delta$ uniquely defines a RKHS $\mathcal{H}_{\delta}$ \citep{fukumizu2004dimensionality}.
+Notice that this kernel has no parameters, so that the model hyperparameters only come from the kernel of the input space and the regularisation parameter $\lambda$.
+
+	Recall that the RKHS induced by a positive definite kernel is the closure of the span of its kernel induced features \citep{xu2009refinement}, so that $\mathcal{H}_{l} = \overline{\mathrm{span}\{l(y, \cdot) : y \in \mathcal{Y}\}}$.
+For $\mathcal{Y} = \mathbb{N}_{m}$ and $l = \delta$, this means that any real-valued function $g : \mathbb{N}_{m} \to \mathbb{R}$ that is bounded on its discrete domain $\mathbb{N}_{m}$ is in the RKHS of $\delta$, because we can always write $g = \sum_{y = 1}^{m} g(y) \delta(y, \cdot) \in \mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}$.
+
+	In particular, indicator functions on $\mathbb{N}_{m}$ are in the RKHS $\mathcal{H}_{\delta}$, since
+	\begin{equation}
+		\mathbb{1}_{c}(y) := \mathbb{1}_{\{c\}}(y) := \begin{cases}
+		1 & \mathrm{if } \quad y \in \{c\} \\
+		0 & \mathrm{otherwise}
+		\end{cases} = \delta(c, y).
+	\label{eq:indicator_function}
+	\end{equation}
+	That is, indicator functions $\mathbb{1}_{c} = \delta(c, \cdot)$, $c \in \mathbb{N}_{m}$ are simply the canonical kernel features of $\mathcal{H}_{\delta}$.
+
+	While such properties does not becessarily hold for continuous domains in general, this convenient property in the case of a discrete domain $\mathcal{Y}$ with a Kronecker delta kernel $\delta$ is what allows consistent estimations of decision probabilities used in multiclass classification, which we turn to next.
+
+	Let $p_{c}(x) := \mathbb{P}[Y = c | X = x]$ be the \textit{decision probability function} for class $c \in \mathbb{N}_{m}$, which is the probability of the class label $Y$ being $c$ when the example $X$ is $x$.
+We begin by writing this probability as an expectation of indicator functions,
+	\begin{equation}
+		p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mathbb{P}[Y \in \{c\} | X = x] = \mathbb{E}[\mathbb{1}_{c}(Y) | X = x].
+	\label{eq:decision_probability}
+	\end{equation}	
+	With $\mathbb{1}_{c} \in \mathcal{H}_{\delta}$, we let $g = \mathbb{1}_{c}$ in \eqref{eq:empirical_conditional_expectation} and $\bvec{1}_{c} := \{\mathbb{1}_{c}(y_{i})\}_{i = 1}^{n}$ to estimate the right hand side of \eqref{eq:decision_probability} by
+	\begin{equation}
+		\hat{p}_{c}(x) = f_{c}(x) := \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x}.
+	\label{eq:empirical_decision_probability}
+	\end{equation}
+	Therefore, the vector of empirical decision probability functions over the classes $c \in \mathbb{N}_{m}$ is
+	\begin{equation}
+		\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x} \in \mathbb{R}^{m},
+	\label{eq:empirical_decision_probability_vector}
+	\end{equation}
+	where $\bvec{Y} := \begin{bmatrix} \bvec{1}_{1} & \bvec{1}_{2} & \cdots & \bvec{1}_{m} \end{bmatrix} \in \{0, 1\}^{n \times m}$ is simply the one hot encoded labels $\{y_{i}\}_{i = 1}^{n}$.
+
+	We proceed to show that the empirical decision probabilities \eqref{eq:empirical_decision_probability} is a consistent estimator for the actual decision probabilities as the dataset increases (See \cref{thm:probability_convergence} of \cref{app:convergence_theorems} for proof).
+	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
+		\label{thm:probability_convergence_copy}
+		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+	\end{theorem}
+	Finally, to perform classification at a query point $x^{\star} \in \mathcal{X}$, we simply take the class with the highest empirical decision probability, $\hat{y}^{\star} = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x^{\star})$.
+
+	While the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ will converge to the true decision probability function  $p_{c} : \mathcal{X} \to [0, 1]$ in the limit, for finite $n$ and a fixed regulariser $\lambda > 0$, the stochasticity in the empirical estimates implies that these probabilities may not necessarily sum up to one, nor are they strictly restricted to the range $[0, 1]$.
+However, they will usually be very close to the true predicted probabilities.
+Moreover, such stochasticity also does not principally affect the classification prediction, since we simply take the argmax of the empirical decision probability vector \eqref{eq:empirical_decision_probability_vector}.
+
+	If strict, valid probabilities are required for interpretation, visualisation, or other purposes, the probabilities can be clipped at zero then normalised to one - a procedure we refer to as \textit{clip-normalisation},
+	\begin{equation}
+		\tilde{p}_{c}(x) := \frac{\max\{\hat{p}_{c}(x), 0\}}{\sum_{j = 1}^{m} \max\{\hat{p}_{j}(x), 0\}}.
+	\label{eq:probability_clip_normalise}
+	\end{equation}
+	Notice that for classification prediction, the argmax solution over the classes of the empirical decision probabilities \eqref{eq:empirical_decision_probability} and its clip-normalised version \eqref{eq:probability_clip_normalise} remain the same.
+Furthermore, since $\hat{p}_{c}(x)$ converges to valid probabilities $p_{c}(x)$ according to \cref{thm:probability_convergence}, the effect of clip-normalisation reduces as $n$ increases such that $\tilde{p}_{c}(x)$ becomes very close to $\hat{p}_{c}(x)$ and $p_{c}(x)$.
+Experiments verify that clip-normalisation only adjusts the probabilities slightly, as the empirical estimates are usually already close to satisfying normalisation and range properties (see \cref{app:design_choices}).
+
+\section{Information Entropy}
+\label{sec:information_entropy}
+
+	The kernel embedding classifier provides decision probabilities instead of just a single label prediction.
+Such a probabilistic classifier allows us to quantify the uncertainty of its predictions for any given example $x \in \mathcal{X}$ through the information entropy \citep{shannon1951prediction, jaynes1957information}.
+This is ideal for detecting the decision boundaries of the classifier and areas of low data density.
+
+	We present two main approaches for inferring the information entropy from the classifier.
+Specifically, we would like to infer estimates for $h(x) := \mathbb{H}[Y | X = x] = - \sum_{c = 1}^{m} p_{c}(x) \log{p_{c}(x)} $, the information entropy of the possible labels $Y$ for a given example $X = x$.
+
+	The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref{eq:probability_clip_normalise}, at the query point $x \in \mathcal{X}$,
+	\begin{equation}
+		\tilde{h}(x) := - \sum_{c = 1}^{m} \tilde{p}_{c}(x) \log{\tilde{p}_{c}(x)}.
+	\label{eq:entropy_clip_normalise}
+	\end{equation}
+	We call \eqref{eq:entropy_clip_normalise} the \textit{clip-normalised information entropy}.
+Since $\tilde{p}_{c}(x)$ converges pointwise to $p_{c}(x)$ with increasing data, $\tilde{h}(x)$ also converges pointwise to $h(x)$.
+
+	Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information \footnote{Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$.},
+	\begin{equation}
+	\begin{aligned}
+		\mathbb{H}[Y | X = x] &= - \sum_{c = 1}^{m} \mathbb{P}[Y = c| X = x] \log{\mathbb{P}[Y = c | X = x]} \\
+		&= \mathbb{E}[- \log{\mathbb{P}[Y | X = x]} | X = x] \\
+		&= \mathbb{E}[u_{x}(Y) | X = x],
+	\end{aligned}
+	\end{equation}
+	where $u_{x}(y) := - \log{\mathbb{P}[Y = y | X = x]}$ is the \textit{information} (in nats) we would gain when we discover that example $x$ actually has label $y$.
+If $u_{x} : \mathbb{N}_{m} \to \mathbb{R}$ is in the RKHS $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by $\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle$.
+This is the basis of our second approach.
+
+	Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$.
+We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the RKHS.
+Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref{eq:empirical_conditional_expectation} and estimate $h(x)$ by
+	\begin{equation}
+		\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle = \bvec{u}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x}.
+	\end{equation}
+	Unfortunately, $u_{x}$ is not known exactly, since $\mathbb{P}[Y = y | X = x]$ is not known exactly.
+Instead, since $\hat{p}_{c}(x)$ is a consistent estimate for $\mathbb{P}[Y = c | X = x]$ by \cref{thm:probability_convergence}, we propose to replace $u_{x}(y)$ with the negative log of $\hat{p}_{y}(x)$.
+However, we cannot simply take the log of this estimator, as $\hat{p}_{y}(x)$ may produce non-positive estimates to the prediction probabilities.
+The straight forward way to mitigate this problem is to clip $\hat{p}_{y}(x)$ from the bottom by a very small number, before taking the log.
+However, experiments show that this produces non-smooth estimates over $\mathcal{X}$ and the degree of smoothness varies drastically between different choices of that small number (see \cref{app:design_choices}).
+Instead, in virtue of the fact that $\lim_{p \to 0} - p \log{p} = 0$ even though $\lim_{p \to 0} - \log{p} = \infty$, we simply define the information estimate $\hat{u}_{x}(y)$ as zero if the empirical decision probability is non-positive,
+	\begin{equation}
+		\hat{u}_{x}(y) := \begin{cases}
+		- \log{\hat{p}_{y}(x)} & \mathrm{if } \quad \hat{p}_{y}(x) > 0 \\
+		0 & \mathrm{otherwise}. \end{cases}
+	\label{eq:empirical_information}
+	\end{equation}
+	It remains to show that $\hat{u}_{x} \in \mathcal{H}_{\delta}$.
+Indeed, the identity $\hat{u}_{x} = \sum_{c = 1}^{m} \hat{u}_{x}(c) \delta(c, \cdot)$ holds and thus $\hat{u}_{x}$ is in the span of the kernel canonical features.
+We then arrive at the following estimate for $h(x)$,
+	\begin{equation}
+		\hat{h}(x) := \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle = \hat{\bvec{u}}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x},
+		\label{eq:empirical_information_entropy}
+	\end{equation}
+	where $\hat{\bvec{u}}_{x} := \{\hat{u}_{x}(y_{i})\}_{i = 1}^{n}$.
+Similar to the case with decision probabilities \eqref{eq:decision_probability}, the information entropy estimate \eqref{eq:empirical_information_entropy} is not guaranteed to be non-negative.
+However, in practice these negative values are close to zero.
+Furthermore, negative estimated information entropy implies that the model is very confident about its prediction, and it suffices to simply clip the entropy at zero if strict information entropy is required (see \cref{app:design_choices}).
+We give the proof of convergence of \eqref{eq:empirical_information_entropy} in \cref{app:convergence_theorems}.
+	\begin{theorem}[Uniform Convergence of Empirical Information Entropy Function]
+		\label{thm:entropy_convergence_copy}
+		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical information entropy function $\hat{h} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_information_entropy} converges uniformly to the true information entropy function $h : \mathcal{X} \to [0, \infty)$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+	\end{theorem}
+
+\section{Hyperparameter Learning with Rademacher Complexity Bounds}
+\label{sec:hyperparameter_learning}
+
+	The formulation of the kernel embedding classifier requires the specification of a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ over the input space $\mathcal{X}$, or rather, a class of kernels $\{k_{\theta}\}_{\theta \in \Theta}$ parametrised by the kernel parameters $\theta \in \Theta$.
+It also requires the specification of a regularisation parameter $\lambda$ for the conditional embedding as in \eqref{eq:empirical_conditional_embedding}.
+These are hyperparameters of the kernel embedding classifier which needs to be learned in order to produce a reasonable classifier model.
+While decision probability estimates \eqref{eq:empirical_decision_probability} converge to the true decision probabilities \eqref{eq:decision_probability} for any choice of positive definite kernels $k_{\theta}$ (\cref{thm:probability_convergence_copy}), for finite $n$ we would like to find the kernel from the kernel family which produces the most appropriately discriminative model to perform classification tasks.
+
+	In the kernel embedding literature, hyperparameters has been notoriously difficult to tune, and its learning is usually only restricted to heuristics or methods such as cross validation which requires pre-selecting the number of folds and the split of the folds.
+In this paper, we take a learning theoretic approach to learn the hyperparameters of the KEC, inspired by the original training procedure of support vector classifiers (SVC) as described by \cite[p.
+185]{m2001introduction}.
+Assuming a perfectly separable case, the training of a SVC begins by introducing a \textit{prediction constraint} on the training set, where the classifier is constrained to correctly classify all the available training examples.
+The strategy is to minimise the \textit{complexity} of the SVC model while ensuring perfect classification over training examples.
+The model complexity in the SVC context is measured by the VC dimension $h$ of the binary classifier, which has an upper bound $h \leq \lVert \bvec{w} \rVert^{2} R^{2} + 1$.
+Since it is difficult to compute the VC dimension explicitly, we instead minimise its upper bound, which is equivalent to and leads to the common interpretation of maximising the margin $\frac{2}{\lVert \bvec{w} \rVert}$.
+
+	Similarly, we propose to train our kernel embedding classifier with the same high level formulation: minimise the model complexity without compromising classification performance on the training data.
+Instead of employing the VC dimension as the complexity measure of our model, which is defined mainly for binary classifiers, we consider the \textit{Rademacher complexity} of the kernel embedding classifier.
+Given a function class $\mathcal{F}$ and a loss function $\mathcal{L}(y, \bvec{f}(x))$, the expected test loss $\mathbb{E}[\mathcal{L}(Y, \bvec{f}(X))]$ is bounded by the expected training loss $\frac{1}{n}\sum_{i = 1}^{n} \mathcal{L}(y_{i}, \bvec{f}(x_{i}))$ plus the Rademacher complexity and a constant with high probability, similar to the case with the VC dimension \citep{bartlett2002rademacher}.
+As such, if we can minimise the model complexity in the sense of the Rademacher complexity while maintaining a low training loss, we can optimise generalisation ability in the sense of low expected test loss.
+
+	For a predictor parametrised as $f(x; W) = W^{T} x$, \cite{yu2014large} showed that the global Rademacher complexity of such a predictor is upper-bounded in terms of its trace norm, $\sqrt{\mathrm{trace}(W^{T} W)}$.
+This was originally discussed in the context of multi-label classification, where $W \in \mathbb{R}^{d \times L}$ and $f$ produces a binary vector of length $L$ indicating the multiple labels that describes the input $x \in \mathbb{R}^{d}$.
+In the context of the kernel embedding classifier, the empirical decision probabilities \eqref{eq:empirical_decision_probability_vector} also has the same analytical form, where the input $x$ is replaced by some feature vector $\phi(x)$.
+By using the canonical feature map $\phi(x) = k(x, \cdot)$ and the reproducing property $\langle \phi(x), \phi(x') \rangle = k(x, x')$ in the RKHS, we can write \eqref{eq:empirical_decision_probability_vector} as $\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \Phi^{T} \phi(x) = W^{T} \phi(x)$, where instead of mapping input examples in $\mathbb{R}^{d}$ to output multi-label vector $\mathbb{R}^{L}$, $W^{T}$ maps features in the RKHS $\mathcal{H}_{k}$ to the a vector of multiclass probabilities in $\mathbb{R}^{m}$.
+Using the reproducing property $K = \Phi^{T} \Phi$ again, the squared trace norm for such a predictor is then $\mathrm{trace}(W^{T} W) = \mathrm{trace}(\bvec{Y}^{T} (K + n \lambda I)^{-1} K (K + n \lambda I)^{-1} \bvec{Y})$.
+We therefore propose to use this trace norm as an upper bound measure of the kernel embedding classifier model complexity,
+	\begin{equation}
+		r(\theta, \lambda) := \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} K_{\theta} (K_{\theta} + n \lambda I)^{-1} \bvec{Y}\bigg)},
+	\label{eq:trace_norm}
+	\end{equation}
+	where we use the subscript $\theta$ to make explicit the dependence on the kernel parameters. Therefore, with high probability and up to a constant term, an upper bound of the test loss is
+	\begin{equation}
+		q(\theta, \lambda) := \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}(y_{i}, \hat{\bvec{p}}_{\theta, \lambda}(x_{i})) + r(\theta, \lambda).
+	\label{eq:objective}
+	\end{equation}
+	We employ gradient based methods to train the kernel embedding classifier with this training loss and complexity bound objective.
+The gradients of the learning objective with respect to the hyperparameters is obtained using automatic differentiation.
+
 	\begin{algorithm}[tb]
-		\caption{Kernel Embedding Classifier Hyperparameter Training with Stochastic Gradient Descent}
-		\label{alg:training_stochastic_gradient_descent}
+		\caption{Kernel Embedding Classifier Training with Stochastic Gradient Descent}
+		\label{alg:kernel_embedding_classifier_training}
 		\begin{algorithmic}[1]
-			\STATE {\bfseries Input:} kernel family $k_{\theta}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial kernel parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
+			\STATE {\bfseries Input:} kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial kernel parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
 			\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
 			\REPEAT
-			\STATE Sample $\mathcal{I} \subseteq \mathbb{N}_{n}$ such that $| \mathcal{I} | = n_{b}$ \hspace{\fill} For gradient descent, $n_{b} = n$ and $\mathcal{I} = \mathbb{N}_{n}$
-			\STATE $B \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
+			\STATE Sample the next batch batch $\mathcal{I} \subseteq \mathbb{N}_{n}$, $| \mathcal{I} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I} = \mathbb{N}_{n}$)
+			\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
 			\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathcal{I}, j \in \mathcal{I}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
 			\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n_{b} \lambda I_{n_{b}}) \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
-			\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash B) \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-			\STATE $r(\theta, \lambda) \leftarrow \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$ \hspace{\fill} Alternatively, $r(\theta, \lambda) \leftarrow \log{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
-			\STATE $\theta \leftarrow \theta - \eta \frac{\partial r}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial r}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} Gradients are computed through back-propagation
-			\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial r}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial r}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} Stop if magnitude of all gradients are below $\epsilon$
+			\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Y) \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
+			\STATE $r(\theta, \lambda) \leftarrow \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
+			\STATE $P_{\theta, \lambda} \leftarrow K_{\theta} V_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
+			\STATE $q(\theta, \lambda) \leftarrow \mathrm{loss}(Y, P_{\theta, \lambda}) + r(\theta, \lambda)$ \hspace{\fill} (For example, use the cross entropy loss or squared loss)
+			\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
+			\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial r}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial r}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
 			\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
@@
 		With standard gradient descent, the time complexity of each training iteration is dominated by the Cholesky decomposition of the regularised gram matrix $K_{\theta} + n \lambda I$ of size $n \times n$, which has a time complexity of $O(n^{3})$.
-In order to scale the hyperparameter training of kernel embedding classifiers to large datasets, we propose to optimise the complexity objective with stochastic gradient descent.
+In order to scale the hyperparameter training of kernel embedding classifiers to large datasets, we propose to optimise the objective \eqref{eq:objective} with stochastic gradient descent.
 
@@
 At each training iteration, we sample a mini-batch of size $n_{b}$ from the full dataset.
-The objective \eqref{eq:trace_norm_optimisation} and hence its gradients with respect to each hyperparameter is then computed only for the mini-batch.
+The objective \eqref{eq:objective} and its gradients with respect to the hyperparameters are then computed only for the mini-batch.
 This stochastic gradient is then used to make hyperparameter updates in that training iteration.
 This continues until the magnitude of the stochastic gradients fall below a certain range.
-This training algorithm is presented in \cref{alg:training_stochastic_gradient_descent}.
+This training algorithm is presented in \cref{alg:kernel_embedding_classifier_training}.
 This implementation also generalises the gradient descent approach, where $n_{b} = n$ so that $\mathcal{I} = \mathbb{N}_{n}$ and the full dataset is used to compute the gradients.
 
-		\note{I have written some not-so-polished comments about why SGD works below.}
-
-		\textbf{Why does SGD work?} It is not immediately obvious that a stochastic gradient descent approach would work for a kernel-based classifier.
-Unlike the cross-entropy loss, the complexity bound objective \eqref{eq:trace_norm_optimisation} is not expressed as a sum of terms each depending on one observation from the dataset.
-Even if it is, being a kernel-based classifier, each term of such a objective would still require the computation of an entire gram matrix and its regularised inverse.
-As such, taking a mini-batch implies that we are only taking a block portion of the entire gram matrix and its regularised inverse.
-
-		What we can see from experiments is that the batch data complexity bound is usually a biased estimator of the full data complexity bound.
-This bias is expected for one primary reason.
-The objective \eqref{eq:trace_norm_optimisation} is a data complexity bound to begin with, and thus while the actual batch data complexity may be an unbiased estimator of the full data complexity, the tightness of the upper bound is expected to change with growing datasets and thus this bias comes from the varying degrees of tightness in the bound as data increases.
-While this bias exists, we do see from experiments that, as we optimise the hyperparameters, both the batch data complexity bound and full data complexity bound decreases at a proportional pace.
-At first it may seem that there is simply a multiplicative factor (possibly in log scale or square root scale with respect to the data size) relationship between them, although it is unclear how this multiplicative factor can be computed.
-We did try seeing if the average complexity bound of disjoint batches is the complexity bound of the full batch.
-The answer is no but it is close, through numerical simulation.
-However, again this should be expected as the tightness of the bound is expected to change for varying data size.
-Perhaps the complexity itself is additive.
-
-		However, it is also not that unintuitive if we realise that each mini-batch is an independently sampled subset of the full dataset.
-This means that the complexity of the model learned from each mini-batch should not be too different from one another, as they are all data from the same probability distribution.
-This gives intuition of how each stochastic gradient is on average correct if we want to learn a low complexity model \textit{for a dataset of the same size as the mini-batch}.
-However, this may not translate to a low complexity model for the full dataset.
-In fact, we do expect that the mini-batch complexity bound to be smaller than the full dataset complexity bound, since models learned on less data tend to be simpler than models learned on more data.
-Nevertheless, intuitively, it also makes sense that a low complexity model for a small dataset would mean that the model is also of low complexity for a larger dataset, as long as the small dataset can capture, albeit to smaller degrees, many of the variations of the larger dataset.
-We achieve this by randomly shuffle the mini-batch being used in each iteration.
-If it does not capture all such variations, the learned model may be too simple when applied on the full dataset.
-
-		We know that, experimentally, SGD works, because the gradients computed from each batch is consistently vanishing as we optimise the hyperparameters.
-Surprisingly, it seems to be on the same scale of the full GD case and suggests that the batch gradient is possibly a (scaled) consistent estimator of the full gradient as well.
-
-		Furthermore, not only does SGD reduce the time and space complexity of each training iteration drastically, it does not increase the number of iterations required for convergence either (at least for a few simple kernels like the Gaussian kernel), and, in many cases actually takes less iterations than the full GD solution.
-This could be because the SGD gradients are usually under-biased compared to the full GD gradients, and thus reach the gradient error tolerance faster.
-
-		Of course, the usual drawbacks of SGD holds here to.
-Specifically, if the optimisation is non-convex, the SGD may converge to a local optimum that is different to the one that the full GD approach would reach.
-Nevertheless, it does not necessarily mean that the SGD solution is worse.
-Sometimes it can actually do better, when the full GD solution was going to converge to a sub-optimal solution already, since the stochasticity in the SGD approach may allow it to find some other solution that is better.
-
-		Round Shifts: Instead of taking completely random batches from the full dataset each time, what one can do instead is to use a ``round shift'' setup to choose the batches.
-That is, the first batch is the first $n_{b}$ data points in the dataset, the second batch is the second $n_{b}$ data points in the dataset, and so on.
-When the whole dataset is scanned through once, we repeat and start from the beginning again.
-Experiments show that this converges to basically the same solution with the full GD approach and also the vanilla SGD approach.
-However, it does take longer iterations to reach the solution.
-Our guess is that the data points we use each time in our batch complexity bound estimation is not independent from each other enough such that the gradients are more correlated to each other and is thus less adaptive.
-
-		Optimisation Setup: We mentioned that it is possible that the expectation of the gradients of the SGD is a scaled version of the full GD gradients.
-In that case, what is commonly done is to multiply the SGD gradients by the correct ratio.
-However, here we choose to leave that out, as such a ratio can simply be absorbed into the learning rate.
-Also, this can be advantageous as such a ratio is usually greater than $1$ (in order to scale up the estimate to the same scale as the full GD case), and if we do multiply this ratio to the stochastic gradients, the learning rate should usually be decreased, in order to dampen out the stochasticity from the stochastic gradients and avoid divergence.
-From experiments we see that by not multiplying this ratio, the learning rate can usually be left to the same as the full GD approach.
-For the same reason, when we switch from full GD to SGD this way, the same gradient error tolerance can also be used.
-
-		Proof Idea: I suspect that the full complexity bound is the sum of the batch complexity bound plus some co-varying terms (which can be negative).
-If I can show that the magnitude of such co-varying terms are upper bounded by the batch complexity bounds, then I can say that as the batch complexity bounds are minimised (randomly), so is the full complexity bound!
-
-\section{End-to-End Classifier Training for Deep Kernel Embedding Network}
-\label{sec:deep_kernel_embeddings}
-
-	The kernel embedding classifier is developed in a very general manner and can be trained under any choice of a family of positive definite kernels $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$, $\theta \in \Theta$.
-There are a variety of ways to construct richer kernels from simpler kernels, such as through convex combination of multiple kernels.
-In this section, we focus on deep kernels, in which inputs $x, x' \in \mathcal{X}$ is to undergo various stages of feature transformations before being fed into a simple positive definite kernel.
-Specifically, we pay particular attention to feature transformations in the form of a perceptron, so that the cumulative stages of feature transformation become the (feed-forward) multi-layer perceptron that is familiar within the neural network literature.
-Although our approach can generalise to other architectures, such as recurrent neural networks, we omit such consideration for simplicity.
-
-	Let $\mathcal{F}_{0} := \mathcal{X}$ be the original input space.
-The $j^{\mathrm{th}}$ layer of the network $\varphi^{(j)}_{\theta_{j}} : \mathcal{F}_{j - 1} \to \mathcal{F}_{j}, j = 1, 2, \dots, q$ is to transform features from the previous layer to features in the current layer, where $q$ is the total number of such feature transformation layers, and $\theta_{j} \in \Theta_{j}$ parametrises each of those transformations.
-
-	For example, in a typical multi-layer perceptron context, each layer can be written as $\varphi^{(j)}_{\theta_{j}}(x) = \sigma(W_{j} x + b_{j})$, where $W$ and $b$ are the weight and bias parameters of the layer, and $\sigma$ is an element-wise activation function, typically the rectified linear unit (ReLU) or the sigmoid.
-In this case, the layer is parametrised by $\theta_{j} = \{W_{j}, b_{j}\}$.
-The setup for a feed-forward convolutional neural network is also very similar.
-
-	Our aim is to construct a positive definite kernel $k$ which can learn representations of the inputs at various levels before such these representations are passed into a simpler kernel $\kappa$ which captures the similarity between the representations.
-
-	Let $\kappa_{\theta_{\kappa}} : \mathcal{F}_{p} \times \mathcal{F}_{p} \to \mathbb{R}$ be parametrised by $\theta_{\kappa} \in \Theta_{\kappa}$. We will construct our kernel network $k$ by
-
-	\begin{equation}
-		k_{\theta}(x, x') := \kappa_{\theta_{\kappa}}\Bigg(
-		\varphi^{(p)}_{\theta_{p}}\bigg(\varphi^{(p - 1)}_{\theta_{p - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x)\big)\Big)\bigg),
-		\varphi^{(p)}_{\theta_{p}}\bigg(\varphi^{(p - 1)}_{\theta_{p - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x')\big)\Big)\bigg)
-		\Bigg)
-	\label{eq:deep_kernel_embedding_network}
-	\end{equation}
-
-	where $\theta = \{\theta_{1}, \theta_{2}, \dots, \theta_{p -1}, \theta_{p}, \theta_{\kappa}\} \in \Theta = \Theta_{1} \otimes \Theta_{2} \otimes \dots \otimes \Theta_{p - 1} \otimes \Theta_{p} \otimes \Theta_{\kappa}$ are the collection of all parameters of each layer and the kernel $\kappa$.
-
-	\note{Note: I think it would be nice to add a figure to visualise the several convolutional layers and how it is passed into a positive definite kernel at the end.}
-
-	Due to the very general training algorithm we developed in \cref{sec:hyperparameter_learning}, we propose to train the kernel network end-to-end by minimising the global Rademacher complexity bound \eqref{eq:trace_norm_optimisation} as before.
-
-	\note{Talk about the advantages and disadvantages of such an approach. The results with three convolutional layer will be put into the experiments section.}
-
-	\subsection{Deep Convolutional Kernel Embedding Network}
-
-		\note{Note: Might be good to relate our work with \citep{mairal2014convolutional}.}
-
-\section{Full Probabilistic Inference and Mode Reconstruction}
-\label{sec:mode_reconstruction}
-
-	Formulated as a conditional embedding learning task in a reproducing kernel Hilbert space, the kernel embedding classifier is able to learn a discriminative model to nonparametrically infer about the distribution of discrete labels $Y$ given an example input $X$.
-In the previous section, we devised a training algorithm for learning the optimal hyperparameters for the conditional embedding corresponding to the classifier.
-Now that the conditional embedding is learned, we can perform full probabilistic inference between all the observed and hidden variables (if any) of the kernel embedding network.
-That is,
-
-	\note{Note: Not completed yet.}
-
-	\subsection{Hidden Representation Reconstruction}
-
-		\note{Note: Observed quantities are done, but hidden quantities needs experimental verification.}
+		\note{Justify with the bound after discussing with Richard}
 
@@
 	We will also open-source the code on GitHub.
-All the core algorithms presented in this paper will be available and implemented in TensorFlow, while having the same API as \texttt{scikit-learn} models so that it is straightforward to use.
+All the core algorithms presented in this paper will be available and implemented in TensorFlow \citep{abadi2016tensorflow}, while having the same API as \texttt{scikit-learn} models so that it is straightforward to use.
 
@@
 	\end{table}
+
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_50.eps}
+		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_100.eps}
+		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_250.eps}
+		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_500.eps}
+		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_750.eps}
+		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_1000.eps}
+		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_1500.eps}
+		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_2000.eps}
+		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_5000.eps}
+		\includegraphics[width=\linewidth]{figures/test_performance.eps}
+		\caption{Training the kernel embedding classifier on the MNIST digits dataset with an anisotropic Gaussian kernel. Top: Learned length scales for each pixel; Bottom: Performance on the test set.}
+		\label{fig:pixel_relevance}
+	\end{figure}
 
@@
 
-\section{Theorems and Derivations}
-\label{app:theorems_derivations}
+\section{Convergence Theorems}
+\label{app:convergence_theorems}
 
@@
 
-	\note{Note: The above proof is for uniform convergence over all $x \in \mathcal{X}$.
-From what the experiments seem to suggest, for stationary zero-centred kernels, I believe that we can actually do better than this convergence rate for areas of high data density.
-Basically, at the subspace of $\mathcal{X}$ where we have observed our data, the convergence rate should be higher, because the kernel effects are stronger at these regions.
-The worse case convergence rate described in the theorem would be a tight lower bound for regions in $\mathcal{X}$ where we do not have a lot of data, where the kernel effects have decayed and most empirical probabilities are near zero and further from summing up to one.}
+	The above proof is for uniform convergence over all $x \in \mathcal{X}$ at the stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+Intuitively, however, for stationary zero-centred kernels like the Gaussian kernel, the convergence rate may be higher at regions of high data density, since the kernel effects, being centred around the training data, are stronger at these regions.
+The worse case convergence rate described here in the theorem would be a tight lower bound for regions in $\mathcal{X}$ with lower data density, where the kernel effects have decayed and most empirical probabilities are smaller and further from summing up to one.
 
@@
 
-	\begin{theorem}[Uniform Convergence of Empirical Information Entropy Function]
+	\begin{theorem}[Convergence of Empirical Information Entropy Function]
 		\label{thm:entropy_convergence}
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical information entropy function $\hat{h} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_information_entropy} converges uniformly to the true information entropy function $h : \mathcal{X} \to [0, \infty)$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical information entropy function $\hat{h} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_information_entropy} converges pointwise to the true information entropy function $h : \mathcal{X} \to [0, \infty)$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
 
@@
 
-\section{Design Choices}
+\section{Learning Theoretic Bounds for the Kernel Embedding Classifiers}
+\label{app:learning_theoretic_bounds}
+
+	In this section we derive the Rademacher complexity bound of the kernel embedding classifier, and show that it can be used in conjunction with the training loss to bound the expected risk with high probability.
+With such a bound, we devise a training objective to learn the hyperparameters for the kernel embedding classifier.
+
+	\subsection{Rademacher Complexity Bounds}
+	\label{app:rademacher_complexity_theorems}
+
+		Suppose a set of training data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ is drawn from $\mathbb{P}_{X Y}$ in an \textit{iid} fashion.
+We denote the one hot encoded target labels of $\{y_{i}\}_{i = 1}^{n}$ by $\bvec{y}_{i} := \{\mathbb{1}_{c}(y_{i})\}_{c = 1}^{m} \in \{0, 1\}^{m}$ and $\bvec{Y} := \begin{bmatrix} \bvec{y}_{1} & \bvec{y}_{2} & \cdots & \bvec{y}_{n} \end{bmatrix}^{T} \in \{0, 1\}^{n \times m}$.
+Similarly, let $\bvec{y} \in \{0, 1\}^{m}$ denote the one hot encoded target labels for a generic label $y \in \mathcal{Y}$.
+Let $k_{\theta} : \mathcal{X} \times \mathcal{X} \to [0, \infty)$ be a family of positive definite kernels indexed by $\theta \in \Theta$.
+As before, we define the shorthand notation for the gram matrices $K_{\theta} := \{k_{\theta}(x_{i}, x_{j}) : i \in \mathbb{N}_{n}, j \in \mathbb{N}_{n}\}$ and $\bvec{k}_{\theta}(x) := \{k_{\theta}(x_{i}, x) : i \in \mathbb{N}_{n}\}$, and $\lambda$ denotes the regularisation parameter of the conditional embedding \eqref{eq:empirical_conditional_embedding}.
+The kernel embedding classifier has a predictor form $\hat{\bvec{p}}(x) = \bvec{f}_{\theta, \lambda}(x)$ \eqref{eq:empirical_decision_probability_vector} defined by
+
+		\begin{equation}
+			\bvec{f}_{\theta, \lambda}(x) := \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \bvec{k}_{\theta}(x),
+		\label{eq:predictor}
+		\end{equation}
+
+		where each entry of the predictor $\bvec{f}_{\theta, \lambda}(x)$ is the decision probability estimate for $p_{c}(x)$.
+This defines the function class of the predictor for any given training set and kernel family,
+
+		\begin{equation}
+			F = \{ \bvec{f}_{\theta, \lambda}(x) : \theta \in \Theta, \lambda \in \Lambda \}.
+		\label{eq:predictor_class}
+		\end{equation}
+
+		The predictor form \eqref{eq:predictor} is linear in the reproducing kernel Hilbert space $\mathcal{H}_{k_{\theta}}$ induced by $k_{\theta}$ in the sense that
+
+		\begin{equation}
+			\begin{aligned}
+				\bvec{f}_{\theta, \lambda}(x) &:= W_{\theta, \lambda}^{T} \phi_{\theta}(x), \\
+				W_{\theta, \lambda} &:= \Phi_{\theta} (K_{\theta} + n \lambda I)^{-1} \bvec{Y},
+			\end{aligned}
+		\label{eq:linear_predictor}
+		\end{equation}
+
+		where we decompose $\bvec{k}_{\theta}(x) = \Phi_{\theta}^{T} \phi_{\theta}(x)$ by the reproducing property.
+
+		\begin{theorem}[Rademacher Complexity Bound for the Kernel Embedding Classifier]
+		\label{thm:rademacher_complexity_bound}
+
+			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
+Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}} = k_{\theta}(x, x) \leq \alpha^{2}$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
+The Rademacher complexity of the class of kernel embedding classifiers $F$ \eqref{eq:predictor_class} defined over $\theta \in \Theta, \lambda \in \Lambda$ is bounded by
+
+			\begin{equation}
+				\mathcal{R}(F) \leq 2 \alpha \rho.
+			\label{eq:rademacher_complexity_bound}
+			\end{equation}
+
+			\begin{proof}
+
+				The Rademacher complexity \citep[Definition 2]{bartlett2002rademacher} of a function class $F$ is
+
+				\begin{equation}
+					\mathcal{R}_{n}(F) := \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \frac{2}{n} \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg] = \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg],
+				\end{equation}
+
+				where $\sigma_{i}$ are \textit{iid} Rademacher random variables, taking values in $\{-1, 1\}$ with equal probability, and $X_{i}$ are \textit{iid} random variables from the same distribution $\mathbb{P}_{X}$ of our training data.
+We further define $\bm{\sigma} := \{\sigma_{i}\}_{i = 1}^{n}$.
+
+				We first bound the term inside the suprenum using the Cauchy Schwarz inequality,
+
+				\begin{equation}
+					\begin{aligned}
+						\Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\| &= \Big\| \sum_{i = 1}^{n} \sigma_{i} W_{\theta, \lambda}^{T} \phi_{\theta}(X_{i}) \Big\| \\
+						&= \Big\| W_{\theta, \lambda}^{T} \bm{\Phi}_{\theta} \bm{\sigma} \Big\| \\
+						&\leq \| W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \bm{\sigma} \| \\
+						&\leq \| W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta}^{T} \|_{\mathrm{tr}} \| \bm{\sigma} \| \\
+						&= \| W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} \| \bm{\sigma} \|,
+					\end{aligned}
+				\end{equation}
+
+				where we define the random operator $\bm{\Phi}_{\theta} := \begin{bmatrix} \phi(X_{1}) & \phi(X_{2}) & \cdots & \phi(X_{n}) \end{bmatrix}$.
+Note that this is distinct from $\Phi_{\theta}$, whose columns are the canonical RKHS features at the training observations and is not random.
+Now, random or not, $\bm{\sigma} := \{\sigma_{i}\}_{i = 1}^{n}$ is just a collection of values that are either $-1$ or $1$, so its norm is simply $\| \bm{\sigma} \| = \sqrt{n}$.
+We can then also compute the trace norm of the other random component $\bm{\Phi}_{\theta}$,
+
+				\begin{equation}
+					\begin{aligned}
+						\| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} :=& \sqrt{\mathrm{trace}(\bm{\Phi}_{\theta}^{T} \bm{\Phi}_{\theta})} \\
+						=& \sqrt{\mathrm{trace}(\bvec{K}_{\theta})} \\
+						=& \sqrt{\sum_{i = 1}^{n} k_{\theta}(X_{i}, X_{i})} \\
+						=& \sqrt{n} \sqrt{ \frac{1}{n} \sum_{i = 1}^{n} k_{\theta}(X_{i}, X_{i})} \\
+						\leq& \sqrt{n} \sqrt{ \frac{1}{n} \sum_{i = 1}^{n} \alpha^{2}} \\
+						=& \sqrt{n} \alpha,
+					\end{aligned}
+				\end{equation}
+
+				where the inequality comes from the assertion that $k_{\theta}(x, x) \leq \alpha^{2}$ for all $x \in \mathcal{X}, \theta \in \Theta$.
+This bounds all the random components in the expectation by a constant, so that later the expectation can vanish.
+
+				Using the assertion that $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ for all $\theta \in \Theta, \lambda \in \Lambda$, we can now bound Rademacher complexity,
+
+				\begin{equation}
+					\begin{aligned}
+						\mathcal{R}_{n}(F) &= \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg] \\
+						&\leq \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} \| \bm{\sigma} \| \bigg] \\
+						&= \frac{2}{n} \sqrt{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} \bigg] \\
+						&\leq \frac{2}{n} \sqrt{n} \sqrt{n} \alpha \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \bigg] \\
+						&\leq 2 \alpha \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \bigg] \\
+						&= 2 \alpha \sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \\
+						&\leq 2 \alpha \rho.
+					\end{aligned}
+				\end{equation}
+			\end{proof}
+		\end{theorem}
+
+		\Cref{thm:rademacher_complexity_bound} provides a generic Rademacher complexity bound for any type of kernel embedding classifier with a bounded positive definite kernel and bounded trace norm.
+One of the most widely used kernels in practice are the family of stationary kernels.
+We provide a more specific bound for the case of stationary kernels below.
+
+		\begin{corollary}[Rademacher Complexity Bound for Stationary Kernels]
+		\label{thm:rademacher_complexity_stationary_kernels_bound}
+
+			Suppose that $k_{\theta}$ is a family of positive definite stationary kernels.
+That is, $k_{\theta} (x, x') = \tilde{k}_{\theta}( \| x - x' \| )$ for some real-valued function $\tilde{k} : [0, \infty) \to [0, \infty)$.
+Further suppose there exists $\tilde{\theta} \in \Theta$ such that that $k_{\theta}(0, 0) \leq k_{\tilde{\theta}}(0, 0)$ for all $\theta \in \Theta$.
+The Rademacher complexity of the class of kernel embedding classifiers $F$ defined over $\theta \in \Theta, \lambda \in \Lambda$ is bounded by
+
+			\begin{equation}
+				\mathcal{R}_{n}(F) \leq 2 \rho \sqrt{k_{\tilde{\theta}}(0, 0)}.
+			\end{equation}
+
+			\begin{proof}
+
+				Observe that $k_{\tilde{\theta}}(0, 0)$ is an upper bound for $k_{\theta}(x, x)$ for all $x \in \mathcal{X}$ and $\theta \in \Theta$,
+
+				\begin{equation}
+					\begin{aligned}
+						k_{\theta}(x, x) = \tilde{k}_{\theta}( \| x - x \| ) = \tilde{k}_{\theta}( \| 0 \| ) = k_{\theta}(0, 0) \leq k_{\tilde{\theta}}(0, 0),
+					\end{aligned}
+				\end{equation}
+
+				We simply choose $\alpha^{2} = k_{\tilde{\theta}}(0, 0)$ in \cref{thm:rademacher_complexity_bound}.
+			\end{proof}
+
+		\end{corollary}
+
+	\subsection{Expected Risk Bounds}
+	\label{thm:expected_risk_bound}
+
+		In order to quantify the performance of the kernel embedding classifier, we specify a loss function $\mathcal{L} : \mathcal{Y} \times \mathcal{A} \to [0, \infty)$, where $\mathcal{L}(y, f(x))$ measures the loss of a decision function $f : \mathcal{X} \to \mathcal{A}$ on a paired example $x \in \mathcal{X}$ and $y \in \mathcal{Y}$.
+In the kernel embedding classification context, the decision function is $\bvec{f}_{\theta, \lambda} : \mathcal{X} \to \mathbb{R}^{m}$, with $\mathcal{A} = \mathbb{R}^{m}$ and $\mathcal{Y} = \mathbb{N}_{m}$.
+The loss function is to capture the desire for $\bvec{y}^{T} \bvec{f}_{\theta, \lambda}(x) = \bvec{f}_{y}^{(\theta, \lambda)}(x)$ to be high for all likely test points $x \in \mathcal{X}$ and $y \in \mathcal{Y}$.
+
+		A suitable choice of the loss function in the probabilistic multiclass classification context is the cross entropy loss,
+
+		\begin{equation}
+			\mathcal{L}(y, \hat{\bvec{p}}(x)) := - \log{\bvec{y}^{T} \hat{\bvec{p}}(x)} = - \log{\hat{p}_{y}(x)},
+		\end{equation}
+
+		where $\hat{\bvec{p}}(x)$ are the inferred probabilities of each class for the example $x \in \mathcal{X}$.
+Since logarithms explode at zero, in practice the probability estimate is often clipped beforehand at a small threshold $\epsilon \in (0, 1)$,
+
+		\begin{equation}
+			\mathcal{L}_{\epsilon}(y, \hat{\bvec{p}}(x)) := - \log{\max \{\bvec{y}^{T} \hat{\bvec{p}}(x), \epsilon \} } = - \log{\max \{ \hat{p}_{y}(x), \epsilon \}}.
+		\label{eq:cross_entropy_loss}
+		\end{equation}
+
+		In some approaches, the probabilities are clipped subject to the constraint that they sum up to one.
+This simply amounts to a rescaling to the decision function.
+For brevity, we will keep the above setup and notation.
+There is, however, one type of rescaling that simplifies subsequent analysis.
+That is, we could avoid introducing more scaling factors in our bounds if we first normalise the loss to lie within the unit range,
+
+		\begin{equation}
+			\begin{aligned}
+				\bar{\mathcal{L}}_{\epsilon}(y, \hat{\bvec{p}}(x)) &:= \frac{1}{M_{\epsilon}} \mathcal{L}_{\epsilon}(y, \hat{\bvec{p}}(x)) = - \frac{1}{M_{\epsilon}} \log{\max \{ \hat{p}_{y}(x), \epsilon \}}, \\
+				M_{\epsilon} &:= - \log{\epsilon}.
+			\end{aligned}
+		\label{eq:normalised_cross_entropy_loss}
+		\end{equation}
+
+		We will refer to \eqref{eq:normalised_cross_entropy_loss} as the normalised cross entropy loss. We then further define the centred normalised cross entropy loss,
+
+		\begin{equation}
+			\tilde{\mathcal{L}}_{\epsilon}(y, \hat{\bvec{p}}(x)) := \bar{\mathcal{L}}_{\epsilon}(y, \hat{\bvec{p}}(x)) - \bar{\mathcal{L}}_{\epsilon}(y, \bvec{0}) = - \frac{1}{M_{\epsilon}} \log{\max \{ \hat{p}_{y}(x), \epsilon \}} - 1.
+		\label{eq:centred_normalised_cross_entropy_loss}
+		\end{equation}
+
+		With the normalised cross entropy loss \eqref{eq:normalised_cross_entropy_loss} as our loss function, we now employ Theorem 8 of \cite{bartlett2002rademacher} for this loss and provide a bound for the expected normalised cross entropy loss for an unseen test example.
+
+		\begin{corollary}[Expected Risk Bound]
+		\label{thm:expected_normalised_cross_entropy_loss_bound}
+			For any integer $n \in \mathbb{N}_{+}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F$ satisfies
+
+			\begin{equation}
+				\frac{1}{M_{\epsilon}} \mathbb{E}[\mathcal{L}_{\epsilon}(Y, f(X))] \leq \frac{1}{n M_{\epsilon}} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + \mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}}.
+			\label{eq:expected_loss_bound}
+			\end{equation}
+
+			\begin{proof}
+				Since $\bar{\mathcal{L}}_{\epsilon} : \mathcal{Y} \times \mathcal{A} \to [0, 1]$ has a unit range and dominates itself, $\bar{\mathcal{L}}_{\epsilon}(y, f(x)) \leq \bar{\mathcal{L}}_{\epsilon}(y, f(x))$, the result follows directly from Theorem 8 of \cite{bartlett2002rademacher}.
+We then use the definition \eqref{eq:normalised_cross_entropy_loss} for the normalised cross entropy loss.
+			\end{proof}
+		\end{corollary}
+
+		The bound \eqref{eq:expected_loss_bound} involves the Rademacher complexity $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F)$ of the centred normalised cross entropy loss applied onto the class of functions $F$, and not just the Rademacher complexity $\mathcal{R}_{n}(F)$ of the class of functions $F$ itself.
+In \cref{thm:rademacher_complexity_bound}, we have bounded the latter.
+We now proceed to bound the former with the latter, so that the former is also bounded by the bound on the latter \eqref{eq:rademacher_complexity_bound}.
+
+		\begin{lemma}[Rademacher Complexity Bound with Cross Entropy Loss]
+		\label{thm:rademacher_complexity_bound_with_cross_entropy_loss}
+
+			The Rademacher complexity of the class of cross entropy loss applied onto the kernel embedding classifier is bounded by
+
+			\begin{equation}
+				\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F) \leq 2 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \mathcal{R}_{n}(F),
+			\label{eq:composed_rademacher_complexity_bound}
+			\end{equation}
+
+			where $\tilde{\mathcal{L}}_{\epsilon} \circ F := \{(x, y) \mapsto \tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}_{\theta, \lambda}(x)) : \theta \in \Theta, \lambda \in \Lambda\}$.
+
+			\begin{proof}
+				Let $\tilde{\psi}(z) := - \frac{1}{M_{\epsilon}} \log{\max \{z, \epsilon \}} - 1$ so that $\tilde{\psi} : \mathbb{R} \to \mathbb{R}$ satisfies $\tilde{\psi}(0) = 0$.
+Then, the centered normalised cross entropy loss can be written as $\tilde{\mathcal{L}}_{\epsilon}(y, \hat{\bvec{p}}(x)) = \tilde{\psi}(\hat{p}_{y}(x))$.
+In particular, $\tilde{\psi}(z)$ is piecewise differentiable.
+We proceed to show that $\tilde{\psi}$ is Lipschitz by showing that the suprenum of its absolute derivative over all piecewise regions is finite, and thus infer its Lipschitz constant.
+
+				The real-valued function $\tilde{\psi}$ can be split into two piecewise regions over the real domain,
+
+				\begin{equation}
+					\tilde{\psi}(z) = \begin{cases}
+						0, \qquad &z \leq \epsilon, \\
+						- \frac{1}{M_{\epsilon}}\log{z} - 1, \qquad &z > \epsilon.
+					\end{cases}
+				\end{equation}
+
+				The derivative over the region $z \leq \epsilon$ is thus $0$ and the local Lipschitz constant over that region is thus $0$. We then focus on the other region,
+
+				\begin{equation}
+					\begin{aligned}
+						\sup_{z \in (\epsilon, \infty)} | \tilde{\psi}'(z) | = \sup_{z \in (\epsilon, \infty)} \Big| - \frac{1}{z M_{\epsilon}} \Big| = \Big| - \frac{1}{\epsilon M_{\epsilon}} \Big| = \Big| \frac{1}{\epsilon \log{\epsilon}} \Big| = \frac{1}{\epsilon \log{\frac{1}{\epsilon}}}.
+					\end{aligned}
+				\end{equation}
+
+				Thus, $\tilde{\psi}$ is Lipschitz with a Lipschitz constant of $L_{\tilde{\psi}} = \frac{1}{\epsilon \log{\frac{1}{\epsilon}}}$.
+
+				For a given general loss function $\mathcal{L}$, \citet[Corollary 3.17]{ledoux2013probability} proved that if there exists a Lipschitz real-valued function $\psi : \mathbb{R} \to \mathbb{R}$, $\psi(0) = 0$, with constant $L_{\tilde{\psi}}$ such that $\mathcal{L}(y, f(x)) = \psi(f_{y}(x))$, then $\mathcal{R}_{n}(\mathcal{L} \circ F) \leq 2 L_{\psi} \mathcal{R}_{n}(F)$.
+This result is also described in \citet[Theorem 12.4]{bartlett2002rademacher}.
+
+				Applying this result to our loss function $\tilde{\mathcal{L}}_{\epsilon}$ with $\psi = \tilde{\psi}$ and $F$ the function class of the kernel embedding classifier over $\theta \in \Theta$ and $\lambda \in \Lambda$, we have $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F) \leq 2 L_{\tilde{\psi}} \mathcal{R}_{n}(F)$, which proves the claim.
+			\end{proof}
+		\end{lemma}
+
+		The bound \eqref{eq:composed_rademacher_complexity_bound} in \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss} will be the bridge that relates the expected cross entropy loss over our function class to the Rademacher complexity of our function class.
+We now proceed to state the main theorem which forms the backbone of our learning algorithm for the kernel embedding classifier.
+
+		\begin{theorem}[General Expected Risk Bound for the Kernel Embedding Classifier]
+			\label{thm:expected_loss_bound_for_kec}
+
+			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
+Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}} = k_{\theta}(x, x) \leq \alpha^{2}$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
+For any integer $n \in \mathbb{N}_{+}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F$ satisfies
+
+			\begin{equation}
+				\frac{1}{M_{\epsilon}} \mathbb{E}[\mathcal{L}_{\epsilon}(Y, f(X))] \leq \frac{1}{n M_{\epsilon}} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
+			\label{eq:expected_loss_bound_for_kec}
+			\end{equation}
+
+			for any $\epsilon \in (0, 1)$. Equivalently, the bound \eqref{eq:expected_loss_bound_for_kec} holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
+
+			\begin{proof}
+				The claim is a direct consequence of \cref{thm:rademacher_complexity_bound} and \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss}.
+			\end{proof}
+		\end{theorem}
+
+		Similar to many learning theoretic bounds, the expected risk bound \eqref{eq:expected_loss_bound_for_kec} is composed of three qualitatively different terms.
+The first term is a training loss or data fit term, which is a measure of how poorly the decision function $f$ is performing on a given training dataset.
+The second term is a model complexity or regularisation term, which measures how complicated the model is.
+In this case, the model complexity is measured by the Rademacher complexity, which captures the expressiveness of the function class by quantifying how well the function class is able to shatter pure noise.
+The third term is a statistical constant which plays no specific role to the function class.
+
+		We will eventually be minimising the first two terms over some class of functions $f \in F$ with some approach, as a proxy to minimising the actual expected risk.
+It would be fruitful to develop an intuition for the tightness of the bound from the contributions of the training loss term and the model complexity term.
+Since, like the expected loss, the training loss term is always in the unit range $[0, 1]$, we focus on understanding the tightness of the bound contributed from the complexity term.
+
+%		Consider a clipped cross entropy loss with a very small clipping factor, $0 < \epsilon << 1$.
+In this scenario, $M_{\epsilon} = - \log{\epsilon}$ would be very large, shooting up to infinity exponentially quickly as $\epsilon$ gets smaller, and the coefficient on the training loss term would then be very small.
+On the other hand, $\epsilon \log{\frac{1}{\epsilon}}$ would be very small, so that the coefficient on the complexity term would then be very large.
+In other words, as $\epsilon$ gets smaller, the training loss term becomes exponentially smaller while the complexity term becomes exponentially larger.
+This raises a major concern.
+The first concern is that the bound unlikely to be tight due to the exploding coefficient on the complexity term.
+Since we will likely be using some sort of gradient-based optimisation to minimise this upper bound, the second concern is that the gradient contribution coming from the training objective is vastly diminished while the gradient contribution from the complexity term is vastly amplified, potentially causing an imbalance in the optimisation to bias towards simpler models that do not perform well on the training data.
+%		
+%		A large clipping factor $\epsilon$ near one also raises similar concerns.
+The coefficient on the complexity term also explodes.
+Meanwhile, although the coefficient on the training loss is now larger, the loss is constant (at one) for probability estimates under $\epsilon$ and approaches the zero-one loss, for which the gradients are zero for most scenarios of the
+%
+
+		Consider a clipped cross entropy loss with either a very small clipping factor $\epsilon \approx 0$, or a very large clipping factor $\epsilon \approx 1$.
+In this scenario, $\epsilon \log{\frac{1}{\epsilon}}$ would be very small, so that the coefficient on the complexity term would then be very large, regardless of what the complexity bound factors $\alpha$ and $\rho$ are.
+As a result, intuitively, this bound is unlikely to be tight due to the large coefficient on the complexity term.
+
+		Consequently, it would then be natural to consider a middle-ground choice of the cross entropy loss where this bound is the most tight by varying $\epsilon \in (0, 1)$.
+Since $\epsilon \log{\frac{1}{\epsilon}}$ is maximised at $\epsilon = \frac{1}{e}$ for a maximal value of $\frac{1}{e}$, such a choice in the clipping factor would indeed yield the tightest bound for the complexity bound in terms of the bounding slack of the result stated in \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss}.
+
+		This is great news for the complexity term.
+What about the the training loss term?
+Intuition tells us that, with a clipping factor of $\epsilon = e^{-1}$ that is slightly more than a third of the way into the interval $(0, 1)$ from zero, the classifier is not being penalised as strongly for assigning probabilities smaller than $e^{-1}$ to observed classes as compared to very small values of $\epsilon$.
+Furthermore, beyond the clipping point, assigning even lower probabilities to the observations does not result in a higher loss.
+In practice, the cross entropy loss is renowned for its rapidly growing penalty as the probability assignment gets lower, which is advantageous when using a gradient based optimisation scheme.
+In this case, the gradients are large in magnitude and the classifier can adjust and fix these assignment errors relatively quickly.
+In other words, by using a slightly larger clipping factor than usual, we have seemingly lost the faster convergence properties from using a cross entropy loss.
+
+		Nevertheless, observe that for such a clipping factor $\epsilon = e^{-1}$, the normalisation constant becomes $M_{e^{-1}} = - \log{\frac{1}{e}} = 1$, so that it is effectively removed.
+Furthermore, we also have the following simple upper bound for the cross entropy loss clipped at $\epsilon = e^{-1}$,
+
+		\begin{equation}
+			\bar{\mathcal{L}}_{e^{-1}}(y, f(x)) = \mathcal{L}_{e^{-1}}(y, f(x)) \leq \mathcal{L}_{\epsilon}(y, f(x)) \quad \forall \epsilon \in (0, e^{-1}), x \in \mathcal{X}, y \in \mathcal{Y}.
+		\label{eq:loss_inequality}
+		\end{equation}
+
+%		In fact, the inequality $\mathcal{L}_{\epsilon_{1}}(y, f(x)) \leq \mathcal{L}_{\epsilon_{2}}(y, f(x))$ holds in general for all $\epsilon_{1} \leq \epsilon_{2}, x \in \mathcal{X}, y \in \mathcal{Y}$.
+
+		To see why inequality \eqref{eq:loss_inequality} holds, note that $\max \{ \hat{p}_{y}(x), \epsilon \} \leq \max \{ \hat{p}_{y}(x), e^{-1} \}$ holds for all $\epsilon \in (0, e^{-1}), x \in \mathcal{X}, y \in \mathcal{Y}$.
+Applying negative log to both sides yields the inequality from definition \eqref{eq:cross_entropy_loss}.
+
+		Therefore, we propose to choose $\epsilon = e^{-1}$, and then replace replace $\mathcal{L}_{e^{-1}}$ with $\mathcal{L}_{\epsilon}$ for some new generic $\epsilon \in (0, e^{-1})$ much smaller than $e^{-1}$.
+In this way, we still maintain an upper bound for the training loss term.
+While this bound would not necessarily be tight for high training losses, the gradients from the high training loss would drive the system to a lower training loss, where the bound would become tight again.
+
+		The above intuition motivates the result in the following theorem.
+
+		\begin{theorem}[Specific Expected Risk Bound for the Kernel Embedding Classifier]
+			\label{thm:specific_expected_loss_bound_for_kec}
+
+			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
+Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}} = k_{\theta}(x, x) \leq \alpha^{2}$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
+For any integer $n \in \mathbb{N}_{+}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F$ satisfies
+
+			\begin{equation}
+			\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 e \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
+			\label{eq:specific_expected_loss_bound_for_kec}
+			\end{equation}
+
+			for any $\epsilon \in (0, e^{-1})$.
+Equivalently, the bound \eqref{eq:specific_expected_loss_bound_for_kec} holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
+
+			\begin{proof}
+				The claim is a direct consequence of applying \cref{thm:expected_loss_bound_for_kec} with $\epsilon = e^{-1}$, and using \eqref{eq:loss_inequality} to further bound each of the cross entropy loss terms that has a clip factor $\epsilon = e^{-1}$ with the corresponding cross entropy loss term that has a generic clip factor $\epsilon \in (0, e^{-1})$ again.
+
+				We first apply \cref{thm:expected_loss_bound_for_kec} with $\epsilon = e^{-1}$,
+
+				\begin{equation}
+					\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{e^{-1}}(Y_{i}, f(X_{i})) + 4 e \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}}.
+				\end{equation}
+
+				For any $\epsilon \in (0, e^{-1})$, the inequality $\mathcal{L}_{e^{-1}}(Y_{i}, f(X_{i})) \leq \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i}))$ holds almost surely (a.s.) due to the deterministic inequality \eqref{eq:loss_inequality}.
+These sets of inequalities together proves the claim.
+			\end{proof}
+		\end{theorem}
+
+	\subsection{Training Objective}
+	\label{app:training_objective}
+
+		In this section, we use the result of \cref{thm:specific_expected_loss_bound_for_kec} to derive a training objective to learn the hyperparameters of the kernel embedding classifier.
+We focus on kernels $k_{\theta}$ that are bounded over the domain $\mathcal{X}$ in the sense that for each $\theta \in \Theta$, $k_{\theta}(x, x) < \infty$ for all $x \in \mathcal{X}$.
+
+		For some kernel parameters $\tilde{\theta} \in \Theta$ and regularisation parameter $\tilde{\lambda} \in \Lambda$, we construct the subset of kernel parameters $\Theta(\tilde{\theta}, \tilde{\lambda}) \subseteq \Theta$ and regularisation parameters $\Lambda(\tilde{\theta}, \tilde{\lambda}) \subseteq \Lambda$ such that
+
+%		\begin{equation}
+%			\begin{aligned}
+%				\Xi(\tilde{\theta}, \tilde{\lambda}) := \{ (\theta, \lambda) \in \Theta \times \Lambda : \| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}, \; k_{\theta}(x, x) \leq \alpha^{2}(\tilde{\theta}) := \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x) \}
+%			\end{aligned}
+%		\end{equation}
+
+		\begin{equation}
+			\begin{aligned}
+				\Theta(\tilde{\theta}, \tilde{\lambda}) &:= \{ \theta \in \Theta : \| W_{\theta, \tilde{\lambda}} \|_{\mathrm{tr}} \leq \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}} \; \forall \lambda \in \Lambda, \; k_{\theta}(x, x) \leq \alpha^{2}(\tilde{\theta}) := \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x) \}, \\
+				\Lambda(\tilde{\theta}, \tilde{\lambda}) &:= \{ \lambda \in \Lambda : \| W_{\tilde{\theta}, \lambda} \|_{\mathrm{tr}} \leq \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}} \; \forall \theta \in \Theta(\tilde{\theta}, \tilde{\lambda}) \}.
+			\end{aligned}
+		\end{equation}
+
+		Clearly, these subsets are non-empty, since $\tilde{\theta} \in \Theta(\tilde{\theta}, \tilde{\lambda})$ and $\tilde{\lambda} \in \Lambda(\tilde{\theta}, \tilde{\lambda})$ are themselves elements of these subsets.
+Note that $\alpha : \Theta \to \mathbb{R}_{+}$ must necessarily exist as the kernel $k_{\theta}$ is assumed to be bounded over the domain $\mathcal{X}$.
+The class of kernel embedding classifiers over this subset of hyperparameters is
+
+		\begin{equation}
+			F(\tilde{\theta}, \tilde{\lambda}) = \{\bvec{f}_{\theta, \lambda}(x) : \theta \in \Theta(\tilde{\theta}, \tilde{\lambda}), \lambda \in \Lambda(\tilde{\theta}, \tilde{\lambda}) \}.
+		\end{equation}
+
+		Thus, we can assert that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ is bounded for all $\theta \in \Theta(\tilde{\theta}, \tilde{\lambda}), \lambda \in \Lambda(\tilde{\theta}, \tilde{\lambda})$, and that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}} = k_{\theta}(x, x) \leq \alpha^{2} = \alpha^{2}(\tilde{\theta})$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta(\tilde{\theta}, \tilde{\lambda})$.
+By \cref{thm:specific_expected_loss_bound_for_kec}, we can now claim the following.
+
+		\begin{claim}[Specific Expected Risk Bound for the Kernel Embedding Classifier]
+			\label{thm:specific_expected_loss_bound_for_kec_applied}
+
+			For any integer $n \in \mathbb{N}_{+}$ and $\epsilon \in (0, e^{-1})$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $\theta \in \Theta(\tilde{\theta}, \tilde{\lambda}), \lambda \in \Lambda(\tilde{\theta}, \tilde{\lambda})$ satisfies
+
+			\begin{equation}
+				\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e \alpha(\tilde{\theta}) \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}} + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
+			\label{eq:specific_expected_loss_bound_for_kec_applied}
+			\end{equation}
+
+			where
+
+			\begin{equation}
+				\begin{aligned}
+					\bvec{f}_{\theta, \lambda}(x) :=& \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \bvec{k}_{\theta}(x), \\
+					\| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}} =& \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\tilde{\theta}} + n \tilde{\lambda} I)^{-1} K_{\tilde{\theta}} (K_{\tilde{\theta}} + n \tilde{\lambda} I)^{-1} \bvec{Y}\bigg)}.
+				\end{aligned}
+			\end{equation}
+		\end{claim}
+
+		Since $\tilde{\theta} \in \Theta(\tilde{\theta}, \tilde{\lambda})$ and $\tilde{\lambda} \in \Lambda(\tilde{\theta}, \tilde{\lambda})$, we choose $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
+Further more, since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:specific_expected_loss_bound_for_kec_applied} is true with probability $1 - \beta$ if we replace all the random variables $X_{i}, Y_{i}$ with the training observations $x_{i}, y_{i}$.
+
+		Therefore, in order to minimise the expected test loss, we propose the following training objective for the kernel embedding classifier,
+
+			\begin{equation}
+				\begin{aligned}
+					q(\tilde{\theta}, \tilde{\lambda}) &:= \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(y_{i}, \bvec{f}_{\tilde{\theta}, \tilde{\lambda}}(x_{i})) + 4 e r(\tilde{\theta}, \tilde{\lambda}), \quad \mathrm{where}\\
+					r(\tilde{\theta}, \tilde{\lambda}) &:= \alpha(\tilde{\theta}) \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\tilde{\theta}} + n \tilde{\lambda} I)^{-1} K_{\tilde{\theta}} (K_{\tilde{\theta}} + n \tilde{\lambda} I)^{-1} \bvec{Y}\bigg)}.
+				\label{eq:training_objective}
+				\end{aligned}
+			\end{equation}
+
+\newpage
+\section{Special Cases of the Kernel Embedding Classifier}
+\label{app:special_cases}
+
+	For a kernel embedding classifier, the modelling lies in the choice of the kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ over the input space $\mathcal{X}$.
+The only requirement for the kernel $k$ is that it is symmetric and positive definite.
+In some cases, positive semi-definite kernels also suffice.
+There are no other requirements, and thus we may construct richer and more expressive kernel families in any way we prefer, subject to those requirements.
+Once such a kernel family is constructed, the kernel parameters $\theta$, as well as the regularisation parameter $\lambda$, can be learned effectively using the training algorithm described in \cref{sec:hyperparameter_learning}.
+
+	One way to construct richer and more expressive kernels is to compose them from simpler kernels.
+For example, we can construct new kernels through convex combinations or products of multiple simpler kernels \citep{genton2001classes}.
+Alternatively, there may be domain specific structures or representations within the data that can be exploited.
+We can then construct the kernel family by incorporating such structural representations into the kernel.
+Even better, we can construct the kernel family so that it is capable or learning such structural representations by itself.
+
+	In this section, we focus on special cases of the kernel embedding classifier where the kernel family is constructed through explicit feature maps.
+This construction allows the incorporation of trainable domain specific structures and enables scalability to larger datasets.
+We first begin by introducing the linear kernel embedding classifier (LKEC, Linear CAKE, or LAKE) in \cref{app:linear_kernel_embedding_classifier}, where explicit feature maps can be learned while enabling scalability to larger datasets.
+We then construct the deep kernel embedding network (DKEN, or Deep CAKE) in \cref{app:deep_kernel_embeddings}, where the kernel family is formed from multiple layers of learned representations before a simpler kernel encodes their similarity for inference.
+Finally, we marry both constructions into the deep linear kernel embedding network (DLKEN, or Deep LAKE) in \cref{app:deep_linear_kernel_embedding_network}, which provides a scalable and more applicable version of the deep kernel embedding network by placing a linear kernel on the last layer of the network.
+
+	In essence, we can categorise the kernel embedding classifier using two properties: the model width and the model depth.
+The model width represents the dimensionality of the feature space used to construct the linear decision boundaries.
+The model depth represents the number of transformations used to map examples from the input space to the feature space.
+By implicitly defining a high dimensional feature space through simple transformations, typical nonlinear kernels produces classifiers that have a shallow but wide architecture.
+In contrast, the three kernel embedding classifier variants to be introduced in this section form other combinations of model architecture in both depth and width.
+We summarise those architectures in \cref{tab:kernel_embedding_classifier_variants}.
+
+%		\begin{table}[t]
+%			\begin{center}
+%				\begin{tabular}{ l || c c }
+%					& Wide Width & Narrow Width\\
+%					\hline
+%					Shallow Depth & Standard KEC & Linear KEC \\
+%					Deep Depth & Deep KEN & Deep Linear KEN \\ 
+%				\end{tabular}
+%			\end{center}
+%			\caption{Examples of kernel embedding classifier architectures}
+%			\label{tab:kernel_embedding_classifier_architectures}
+%		\end{table}
+
+		\begin{table}[t]
+			\begin{center}
+				\begin{tabular}{ l || c c c c c}
+					KEC Variant & Width & Depth & Scalability & Flexibility & Typical Datasets  \\
+					\hline
+					Nonlinear KEC & Wide & Shallow & Low & High & High or Low $d$, Low $n$ \\
+					Linear KEC & Narrow & Shallow & High & Low & Low $d$, High $n$ \\
+					Deep Nonlinear KEN &  Wide & Deep & Low & High & Structured $d$, Low $n$ \\
+					Deep Linear KEN & Narrow & Deep & High & High & Structured $d$, High $n$ \\ 
+				\end{tabular}
+			\end{center}
+			\caption{Properties of kernel embedding classifier architectures}
+			\label{tab:kernel_embedding_classifier_variants}
+		\end{table}
+
+	\subsection{Linear Kernel Embedding Classifier}
+	\label{app:linear_kernel_embedding_classifier}
+
+		The advantage of using a kernel-based classifier is that the kernel $k$ allows us to express nonlinearities in a simple way.
+It does this by implicitly mapping the input space $\mathcal{X}$ to a high dimensional feature space $\mathcal{H}_{k}$ of non-linear basis functions such that decision boundaries become linear in that space.
+For many kernels, such as the Gaussian kernel defined over the Euclidean space, the feature space $\mathcal{H}_{k}$ has dimensionality that is uncountably infinite.
+Nevertheless, by virtue of the Representer Theorem \citep{kimeldorf1971some}, the resulting decision functions can be represented by a finite linear combination of kernels centred at the training data, and the kernel embedding classifier is no exception.
+This elegant and convenient result enables exact inference to be performed while only requiring a finite kernel gram matrix of the size of the dataset ($n \times n$) to be computed.
+In this way, the capacity of the model grows with the size of the dataset, which makes kernel methods nonparametric and very flexible, as it can adapt to the complexity of a dataset even with relatively simple kernels.
+
+		However, this elegant property is also the very reason that prevents kernel-based methods from scaling to larger datasets, as the size of such a matrix grows very quickly by $O(n^{2})$ as the dataset grows.
+Furthermore, many kernel-based methods require the inversion of a regularised gram matrix, which has a time complexity of $O(n^{3})$, and cannot be easily parallelised unlike standard matrix multiplications.
+As such, inference on datasets beyond tens of thousands of observations quickly becomes impractical to perform with kernel-based techniques.
+
+		Furthermore, in many situations, simple conventional kernels such as the Gaussian kernel is not able to fully represent the underlying structure of the data for the specific application domain at hand.
+For example, in an image recognition task, a Gaussian kernel over the flattened pixels of an image is unable to capture the local relationships between nearby pixels in the original image.
+In this example, inference would greatly benefit from using convolutional features.
+In general, we would like to be able to compose kernels from any features that can potentially learn to capture structural information within the data.
+
+		These two insights motivate a special case of the kernel embedding classifier, the linear kernel embedding classifier.
+As its name implies, instead of placing a kernel over the input space directly and let it implicitly define the feature space, we simply explicitly define a finite dimensional feature space $\mathbb{R}^{p}$ of dimension $p$ and place a linear kernel over it.
+By explicitly defining a finite dimensional feature space, the matrix to be inverted during both learning and inference in the kernel embedding classifier can be reduced from size $n \times n$ to size $p \times p$ by using a special case of the Woodbury matrix identity.
+
+		However, with a fixed and finite amount of feature basis, the model becomes parametric and its flexibility is compromised.
+We therefore employ the deep learning philosophy, where the flexibility of a model comes from a narrow but deep architecture instead of a wide but shallow architecture such as the one defined by a kernel with implicit infinite dimensional features.
+
+		\begin{equation}
+		k_{\theta}(x, x') = \varphi_{\theta}(x)^{T} \varphi_{\theta}(x')
+		\end{equation}
+
+		\begin{algorithm}[tb]
+			\caption{Linear Kernel Embedding Classifier Training with Stochastic Gradient Descent}
+			\label{alg:linear_kernel_embedding_classifier_training}
+			\begin{algorithmic}[1]
+				\STATE {\bfseries Input:} feature family $\varphi_{\theta} : \mathcal{X} \to \mathcal{Z} \subseteq \mathbb{R}^{p}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial feature parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
+				\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
+				\REPEAT
+				\STATE Sample the next batch batch $\mathcal{I} \subseteq \mathbb{N}_{n}$, $| \mathcal{I} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I} = \mathbb{N}_{n}$)
+				\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
+				\STATE $Z_{\theta} \leftarrow \{\varphi_{\theta}(x_{i}) : i \in \mathcal{I}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times p}$
+				\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(Z_{\theta}^{T} Z_{\theta} + n_{b} \lambda I_{p}) \hspace{\fill} \in \mathbb{R}^{p \times p}$
+				\STATE $W_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Z_{\theta}^{T} Y) \hspace{\fill} \in \mathbb{R}^{p \times m}$
+				\STATE $r(\theta, \lambda) \leftarrow \sqrt{\sum_{c = 1}^{m} \sum_{j = 1}^{p} (W_{\theta, \lambda})_{j, c}^{2}}$
+				\STATE $P_{\theta, \lambda} \leftarrow Z_{\theta} W_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
+				\STATE $q(\theta, \lambda) \leftarrow \mathrm{loss}(Y, P_{\theta, \lambda}) + r(\theta, \lambda)$ \hspace{\fill} (For example, use the cross entropy loss or squared loss)
+				\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
+				\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial r}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial r}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
+				\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
+			\end{algorithmic}
+		\end{algorithm}
+
+		\note{Choose each batch to be greater than the dimensionality of the last layer to avoid numerical instability with Cholesky Decomposition as the upper bound is not tight for small $n$ and the gradients may send it off to some unstable region instead}
+
+	\subsection{Deep Kernel Embedding Network}
+	\label{app:deep_kernel_embeddings}
+
+		For many application domains, there are natural structures in the data.
+For example, in image recognition, pixel dimensions are spatially correlated: nearby pixels are more related, and ordering between the pixel dimensions matter.
+One would expect that convolutional features \citep{lecun1998gradient} would be natural in this domain and provide a performance boost to our classifier should it be included.
+In this way, we can often benefit by including domain specific structures and features into our model.
+
+		In this section, we focus on constructing kernels, in which inputs $x, x' \in \mathcal{X}$ is to undergo various stages of feature transformations before being fed into a simple positive definite kernel.
+Specifically, we pay particular attention to feature transformations in the form of a perceptron, so that the cumulative stages of feature transformation become the (feed-forward) multi-layer perceptron that is familiar within the neural network literature.
+Although our approach can generalise to other architectures, such as recurrent neural networks, we omit such consideration for simplicity.
+
+		Formally, let $\mathcal{F}_{0} := \mathcal{X}$ be the original input space.
+The $j^{\mathrm{th}}$ layer of the network $\varphi^{(j)}_{\theta_{j}} : \mathcal{F}_{j - 1} \to \mathcal{F}_{j}, j = 1, 2, \dots, q$ is to transform features from the previous layer to features in the current layer, where $q$ is the total number of such feature transformation layers, and $\theta_{j} \in \Theta_{j}$ parametrises each of those transformations.
+
+		For example, in a typical multi-layer perceptron context, each layer can be written as $\varphi^{(j)}_{\theta_{j}}(x) = \sigma(W_{j} x + b_{j})$, where $W$ and $b$ are the weight and bias parameters of the layer, and $\sigma$ is an element-wise activation function, typically the rectified linear unit (ReLU) or the sigmoid.
+In this case, the layer is parametrised by $\theta_{j} = \{W_{j}, b_{j}\}$.
+The setup for a feed-forward convolutional neural network is also very similar.
+
+		Our aim is to construct a positive definite kernel $k$ which can learn representations of the inputs at various levels before such these representations are passed into a simpler kernel $\kappa$ which captures the similarity between the representations.
+
+		Let $\kappa_{\theta_{\kappa}} : \mathcal{F}_{p} \times \mathcal{F}_{p} \to \mathbb{R}$ be parametrised by $\theta_{\kappa} \in \Theta_{\kappa}$. We will construct our kernel network $k$ by
+
+		\begin{equation}
+		k_{\theta}(x, x') := \kappa_{\theta_{\kappa}}\Bigg(
+		\varphi^{(p)}_{\theta_{p}}\bigg(\varphi^{(p - 1)}_{\theta_{p - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x)\big)\Big)\bigg),
+		\varphi^{(p)}_{\theta_{p}}\bigg(\varphi^{(p - 1)}_{\theta_{p - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x')\big)\Big)\bigg)
+		\Bigg)
+		\label{eq:deep_kernel_embedding_network}
+		\end{equation}
+
+		where $\theta = \{\theta_{1}, \theta_{2}, \dots, \theta_{p -1}, \theta_{p}, \theta_{\kappa}\} \in \Theta = \Theta_{1} \otimes \Theta_{2} \otimes \dots \otimes \Theta_{p - 1} \otimes \Theta_{p} \otimes \Theta_{\kappa}$ are the collection of all parameters of each layer and the kernel $\kappa$.
+
+	\subsection{Deep Linear Kernel Embedding Network}
+	\label{app:deep_linear_kernel_embedding_network}
+
+\section{Full Probabilistic Inference and Mode Reconstruction}
+\label{app:mode_reconstruction}
+
+	Formulated as a conditional embedding learning task in a reproducing kernel Hilbert space, the kernel embedding classifier is able to learn a discriminative model to nonparametrically infer about the distribution of discrete labels $Y$ given an example input $X$.
+In the previous section, we devised a training algorithm for learning the optimal hyperparameters for the conditional embedding corresponding to the classifier.
+Now that the conditional embedding is learned, we can perform full probabilistic inference between all the observed and hidden variables (if any) of the kernel embedding network.
+That is,
+
+	\note{Note: Not completed yet.}
+
+	\subsection{Hidden Representation Reconstruction}
+
+		\note{Note: Observed quantities are done, but hidden quantities needs experimental verification.}
+
+\section{Design Choices and More Discussion}
 \label{app:design_choices}
@@
 
-		\note{\textbf{Unpolished.}} The simple reason is that it works better.
+		The simple reason is that it works better.
 The more theoretical reason is that our raw probability estimates usually produces predictions with low cross entropy loss.
@@
 
+	\subsection{Cross Entropy Loss: Why use the raw decision probabilities?}
+
+	\subsection{More about the training objective}
+
+		The training objective \eqref{eq:objective} for the kernel embedding classifier is composed of two terms: a training loss (or data fit) term and a model complexity (or regularisation) term.
+In this section we provide some intuition towards the relative effects of each term for two types of kernel models: a radial basis type kernel and a linear kernel.
+
+		Consider a typical radial basis type kernels such as the Gaussian (squared exponential) or Mat\'{e}rn kernel $k_{\theta}$.
+These types of kernels are usually placed on top of subsets of Euclidean spaces $\mathcal{X} \subseteq \mathbb{R}^{d}$ where $d$ is the dimensionality of an input $x \in \mathcal{X}$.
+Here, the hyperparameters $\theta$ usually includes length scale parameters ($1$ parameter for isotropic kernels, $d$ parameters for anisotropic kernels, or $\frac{d (d - 1)}{2}$ parameters for non-diagonal kernels) and possibly a sensitivity parameter which is simply a multiplicative constant that scales the magnitude of the kernel.
+
+		These types of kernels implicitly map the input space $\mathcal{X}$ to an uncountably infinite dimensional RKHS $\mathcal{H}_{k_{\theta}}$, making the model nonparametric.
+This means that the feature space $\mathcal{H}_{k_{\theta}}$ is already quite flexible for any $\theta \in \Theta$, since for any $\theta \in \Theta$ it has an uncountably infinite amount of feature basis to use for creating linear decision boundaries.
+As such, and it is relatively easy to find linear decision boundaries within such a high dimensional space.
+In this way, experiments show that for most datasets, most initialisations of $\theta$ already produces a very reasonable model of low training loss.
+In fact, there is often a subset of length scales and sensitivity parameters within $\Theta$ in which the training loss is relatively constant.
+
+		In these scenarios, the gradients from the training loss term is usually very small, and the gradient from the training objective is dominated by the complexity term.
+Intuitively, the training objective communicating the following message: ``the model is already performing quite well, or at least as best as it can, on the dataset, so let us focus on finding the simplest model that can still produce a similar performance''.
+
+		This is in contrast to the case with linear kernels $k_{\theta}(x, x') = \varphi_{\theta}(x)^{T} \varphi_{\theta}(x')$.
+In this case, the input space $\mathcal{X}$, usually but not necessarily also a subset of the Euclidean space $\mathbb{R}^{d}$, is explicitly mapped to a finite dimensional RKHS $\mathcal{H}_{k_{\theta}} = \mathcal{Z} \subseteq \mathbb{R}^{p}$ through the feature map $\varphi_{\theta} : \mathcal{X} \to \mathcal{Z}$.
+With only finitely many feature basis, the model becomes parametric, and the number of features is fixed at $p$ so that its capacity does not grow with the size of the dataset like a nonparametric model.
+In \cref{app:linear_kernel_embedding_classifier}, we focused on linear kernel embedding classifiers with deep neural network features, where the flexibility of such a narrow model comes from the deep architecture instead.
+This is in contrast to the case of radial basis type kernels which has a shallow architecture and the flexibility comes from the wide collection of feature basis (uncountably many) which becomes more expressive as we observe more data.
+
+		In this case, for most initialisations of the model parameters $\theta \in \Theta$, the model will not necessarily perform well on the training data.
+As such, the training loss is large and its gradients will be larger in magnitude, in order to drive the model towards a better model fit.
+
+		On the other hand, the complexity term is comparatively smaller.
+Recall that the model complexity is measured in the RKHS $\mathcal{H}_{k_{\theta}}$, which in this case is the space of the last layer $\mathcal{Z} \subseteq \mathbb{R}^{p}$ of the neural network.
+Earlier layers are free to learn very complicated feature extractions.
+As long as the learned feature representations in the last layer is simple, the complexity term will be small.
+Since the number of features is fixed, the capacity of the model is limited, and thus the complexity term is usually not as big as the training loss term.
+In this way, the gradients from the training objective is dominated by the training loss term.
+Intuitively, the training objective is communicating the following message: ``the model is performing very poorly on the dataset, so let us first focus on learning representations to explain the dataset before we worry about finding the simplest model''.
+
 \end{document}

### 2017-05-10 kernel_embedding_classifier.tex
Complete bounds appendix

@@
 
-\title{CAKE: Classification avec Kernel Embeddings \\ with Rademacher complexity bounds}
+\title{CAKE: Classification avec Kernel Embeddings \\ with Rademacher Complexity Bounds}
 
@@
 \begin{abstract}
-%	We propose a novel probabilistic multiclass classifier, the kernel embedding classifier, by casting the multiclass classification problem into the kernel conditional embedding framework in a principled manner.
-We provide convergence guarantees of the classifier in both decision probability and information entropy, and develop a novel training objective based on Rademacher complexity bounds
-%Specifically, the guaranteed convergence of the kernel embedding classifier in both decision probability and information entropy, the Rademacher complexity based hyperparameter training scheme, the stochastic gradient descent version thereof which allows scalable training, the application of such flexible training methods to train deep convolutional features, and the fully probabilistic inference on both inputs and outputs.
-Focus the point of the paper as that this is a new and elegant formulation of a fully probabilistic classifier (not just in the outputs, but even in the inputs) with complexity bound based training.
-Being formulated as type of kernel conditional embedding learning, all the nice properties from the Hilbert space embedding world can be imported into this framework.
-In practice, even though the mathematical theory of kernel embeddings can be tricky, the resulting algorithms are very elegant and simple, so that implementation is quick and easy.
-Being very general, there should be a lot of things we can do in the future to improve it or build upon it.
+	Kernel embedding of probability distributions are a 
 \end{abstract}
@@
 
-	On top of this, in practice we do not have access to the distribution $\mathbb{P}_{X Y}$ to compute such expectations from the definitions of $C_{YX}$ and $C_{XX}$.
+	On top of this, in practice we do not have access to the distribution $\mathbb{P}_{X Y}$ to analytically derive the conditional embedding.
 Instead, we have a finite collection of data points $\{x_{i}, y_{i}\} \in \mathcal{X} \times \mathcal{Y}$, $i \in \mathbb{N}_{n} := \{1, \dots, n\}$, for which the conditional embedding map $\mathcal{U}_{Y | X}$ can be estimated by
@@
 	\end{equation}
-	where $K := \{k(x_{i}, x_{j})\}_{i = 1, j = 1}^{n, n}$, $\Phi := \begin{bmatrix} k(x_{1}, \cdot) & \dots & k(x_{n}, \cdot) \end{bmatrix}$, $\Psi := \begin{bmatrix} l(y_{1}, \cdot) & \dots & l(y_{n}, \cdot) \end{bmatrix}$, and $\lambda$ is the regularisation parameter for the conditional operator \citep{song2013kernel}.
-We then define the empirical conditional embedding by $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$, which stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \citep{song2009hilbert}.
-That is, % Theorem 6
-	\begin{equation}
-		\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists M_{\epsilon} > 0 \quad s.t.
-\quad \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
-	\label{eq:empirical_conditional_embedding_stochastic_convergence}
-	\end{equation}
+	where $K := \{k(x_{i}, x_{j})\}_{i = 1, j = 1}^{n, n}$, $\Phi := \begin{bmatrix} \phi(x_{1}) & \dots & \phi(x_{n}) \end{bmatrix}$, $\Psi := \begin{bmatrix} \psi(y_{1}) & \dots & \psi(y_{n}) \end{bmatrix}$, $\phi(x) := k(x, \cdot)$, $\psi(y) := l(y, \cdot)$, and $\lambda$ is the regularisation parameter for the conditional operator \citep{song2013kernel}.
+We then define the empirical conditional embedding by $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$, which stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \citet[Theorem 6]{song2009hilbert}.
 This allows us to approximate the conditional expectation \eqref{eq:conditional_expectation} with $\langle \hat{\mu}_{Y | X = x}, g \rangle$ instead,
@@
 	Notice that for classification prediction, the argmax solution over the classes of the empirical decision probabilities \eqref{eq:empirical_decision_probability} and its clip-normalised version \eqref{eq:probability_clip_normalise} remain the same.
-Furthermore, since $\hat{p}_{c}(x)$ converges to valid probabilities $p_{c}(x)$ according to \cref{thm:probability_convergence}, the effect of clip-normalisation reduces as $n$ increases such that $\tilde{p}_{c}(x)$ becomes very close to $\hat{p}_{c}(x)$ and $p_{c}(x)$.
-Experiments verify that clip-normalisation only adjusts the probabilities slightly, as the empirical estimates are usually already close to satisfying normalisation and range properties (see \cref{app:design_choices}).
-
-\section{Information Entropy}
-\label{sec:information_entropy}
-
-	The kernel embedding classifier provides decision probabilities instead of just a single label prediction.
-Such a probabilistic classifier allows us to quantify the uncertainty of its predictions for any given example $x \in \mathcal{X}$ through the information entropy \citep{shannon1951prediction, jaynes1957information}.
-This is ideal for detecting the decision boundaries of the classifier and areas of low data density.
-
-	We present two main approaches for inferring the information entropy from the classifier.
-Specifically, we would like to infer estimates for $h(x) := \mathbb{H}[Y | X = x] = - \sum_{c = 1}^{m} p_{c}(x) \log{p_{c}(x)} $, the information entropy of the possible labels $Y$ for a given example $X = x$.
-
-	The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref{eq:probability_clip_normalise}, at the query point $x \in \mathcal{X}$,
-	\begin{equation}
-		\tilde{h}(x) := - \sum_{c = 1}^{m} \tilde{p}_{c}(x) \log{\tilde{p}_{c}(x)}.
-	\label{eq:entropy_clip_normalise}
-	\end{equation}
-	We call \eqref{eq:entropy_clip_normalise} the \textit{clip-normalised information entropy}.
-Since $\tilde{p}_{c}(x)$ converges pointwise to $p_{c}(x)$ with increasing data, $\tilde{h}(x)$ also converges pointwise to $h(x)$.
-
-	Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information \footnote{Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$.},
-	\begin{equation}
-	\begin{aligned}
-		\mathbb{H}[Y | X = x] &= - \sum_{c = 1}^{m} \mathbb{P}[Y = c| X = x] \log{\mathbb{P}[Y = c | X = x]} \\
-		&= \mathbb{E}[- \log{\mathbb{P}[Y | X = x]} | X = x] \\
-		&= \mathbb{E}[u_{x}(Y) | X = x],
-	\end{aligned}
-	\end{equation}
-	where $u_{x}(y) := - \log{\mathbb{P}[Y = y | X = x]}$ is the \textit{information} (in nats) we would gain when we discover that example $x$ actually has label $y$.
-If $u_{x} : \mathbb{N}_{m} \to \mathbb{R}$ is in the RKHS $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by $\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle$.
-This is the basis of our second approach.
-
-	Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$.
-We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the RKHS.
-Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref{eq:empirical_conditional_expectation} and estimate $h(x)$ by
-	\begin{equation}
-		\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle = \bvec{u}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x}.
-	\end{equation}
-	Unfortunately, $u_{x}$ is not known exactly, since $\mathbb{P}[Y = y | X = x]$ is not known exactly.
-Instead, since $\hat{p}_{c}(x)$ is a consistent estimate for $\mathbb{P}[Y = c | X = x]$ by \cref{thm:probability_convergence}, we propose to replace $u_{x}(y)$ with the negative log of $\hat{p}_{y}(x)$.
-However, we cannot simply take the log of this estimator, as $\hat{p}_{y}(x)$ may produce non-positive estimates to the prediction probabilities.
-The straight forward way to mitigate this problem is to clip $\hat{p}_{y}(x)$ from the bottom by a very small number, before taking the log.
-However, experiments show that this produces non-smooth estimates over $\mathcal{X}$ and the degree of smoothness varies drastically between different choices of that small number (see \cref{app:design_choices}).
-Instead, in virtue of the fact that $\lim_{p \to 0} - p \log{p} = 0$ even though $\lim_{p \to 0} - \log{p} = \infty$, we simply define the information estimate $\hat{u}_{x}(y)$ as zero if the empirical decision probability is non-positive,
-	\begin{equation}
-		\hat{u}_{x}(y) := \begin{cases}
-		- \log{\hat{p}_{y}(x)} & \mathrm{if } \quad \hat{p}_{y}(x) > 0 \\
-		0 & \mathrm{otherwise}. \end{cases}
-	\label{eq:empirical_information}
-	\end{equation}
-	It remains to show that $\hat{u}_{x} \in \mathcal{H}_{\delta}$.
-Indeed, the identity $\hat{u}_{x} = \sum_{c = 1}^{m} \hat{u}_{x}(c) \delta(c, \cdot)$ holds and thus $\hat{u}_{x}$ is in the span of the kernel canonical features.
-We then arrive at the following estimate for $h(x)$,
-	\begin{equation}
-		\hat{h}(x) := \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle = \hat{\bvec{u}}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x},
-		\label{eq:empirical_information_entropy}
-	\end{equation}
-	where $\hat{\bvec{u}}_{x} := \{\hat{u}_{x}(y_{i})\}_{i = 1}^{n}$.
-Similar to the case with decision probabilities \eqref{eq:decision_probability}, the information entropy estimate \eqref{eq:empirical_information_entropy} is not guaranteed to be non-negative.
-However, in practice these negative values are close to zero.
-Furthermore, negative estimated information entropy implies that the model is very confident about its prediction, and it suffices to simply clip the entropy at zero if strict information entropy is required (see \cref{app:design_choices}).
-We give the proof of convergence of \eqref{eq:empirical_information_entropy} in \cref{app:convergence_theorems}.
-	\begin{theorem}[Uniform Convergence of Empirical Information Entropy Function]
-		\label{thm:entropy_convergence_copy}
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical information entropy function $\hat{h} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_information_entropy} converges uniformly to the true information entropy function $h : \mathcal{X} \to [0, \infty)$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-	\end{theorem}
+Furthermore, since $\hat{p}_{c}(x)$ converges to valid probabilities $p_{c}(x)$ according to \cref{thm:probability_convergence_copy}, the effect of clip-normalisation reduces as $n$ increases such that $\tilde{p}_{c}(x)$ becomes very close to $\hat{p}_{c}(x)$ and $p_{c}(x)$.
 
@@
 As such, if we can minimise the model complexity in the sense of the Rademacher complexity while maintaining a low training loss, we can optimise generalisation ability in the sense of low expected test loss.
+
+			Further more, since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:specific_expected_loss_bound_for_kec_applied} is true with probability $1 - \beta$ if we replace all the random variables $X_{i}, Y_{i}$ with the training observations $x_{i}, y_{i}$.
+
+			Therefore, in order to minimise the expected test loss, we propose the following training objective for the kernel embedding classifier,
 
@@
 			\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Y) \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-			\STATE $r(\theta, \lambda) \leftarrow \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
 			\STATE $P_{\theta, \lambda} \leftarrow K_{\theta} V_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-			\STATE $q(\theta, \lambda) \leftarrow \mathrm{loss}(Y, P_{\theta, \lambda}) + r(\theta, \lambda)$ \hspace{\fill} (For example, use the cross entropy loss or squared loss)
+			\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
 			\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
@@
 
+\section{Information Entropy}
+\label{sec:information_entropy}
+
+	The kernel embedding classifier provides decision probabilities instead of just a single label prediction.
+Such a probabilistic classifier allows us to quantify the uncertainty of its predictions for any given example $x \in \mathcal{X}$ through the information entropy \citep{shannon1951prediction, jaynes1957information}.
+This is ideal for detecting the decision boundaries of the classifier and areas of low data density.
+
+	We present two main approaches for inferring the information entropy from the classifier.
+Specifically, we would like to infer estimates for $h(x) := \mathbb{H}[Y | X = x] = - \sum_{c = 1}^{m} p_{c}(x) \log{p_{c}(x)} $, the information entropy of the possible labels $Y$ for a given example $X = x$.
+
+	The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref{eq:probability_clip_normalise}, at the query point $x \in \mathcal{X}$,
+	\begin{equation}
+		\tilde{h}(x) := - \sum_{c = 1}^{m} \tilde{p}_{c}(x) \log{\tilde{p}_{c}(x)}.
+	\label{eq:entropy_clip_normalise}
+	\end{equation}
+	We call \eqref{eq:entropy_clip_normalise} the \textit{clip-normalised information entropy}.
+Since $\tilde{p}_{c}(x)$ converges pointwise to $p_{c}(x)$ with increasing data, $\tilde{h}(x)$ also converges pointwise to $h(x)$.
+
+	Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information \footnote{Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$.},
+	\begin{equation}
+	\begin{aligned}
+		\mathbb{H}[Y | X = x] &= - \sum_{c = 1}^{m} \mathbb{P}[Y = c| X = x] \log{\mathbb{P}[Y = c | X = x]} \\
+		&= \mathbb{E}[- \log{\mathbb{P}[Y | X = x]} | X = x] \\
+		&= \mathbb{E}[u_{x}(Y) | X = x],
+	\end{aligned}
+	\end{equation}
+	where $u_{x}(y) := - \log{\mathbb{P}[Y = y | X = x]}$ is the \textit{information} (in nats) we would gain when we discover that example $x$ actually has label $y$.
+If $u_{x} : \mathbb{N}_{m} \to \mathbb{R}$ is in the RKHS $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by $\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle$.
+This is the basis of our second approach.
+
+	Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$.
+We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the RKHS.
+Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref{eq:empirical_conditional_expectation} and estimate $h(x)$ by
+	\begin{equation}
+		\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle = \bvec{u}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x}.
+	\end{equation}
+	Unfortunately, $u_{x}$ is not known exactly, since $\mathbb{P}[Y = y | X = x]$ is not known exactly.
+Instead, since $\hat{p}_{c}(x)$ is a consistent estimate for $\mathbb{P}[Y = c | X = x]$ by \cref{thm:probability_convergence}, we propose to replace $u_{x}(y)$ with the negative log of $\hat{p}_{y}(x)$.
+However, we cannot simply take the log of this estimator, as $\hat{p}_{y}(x)$ may produce non-positive estimates to the prediction probabilities.
+The straight forward way to mitigate this problem is to clip $\hat{p}_{y}(x)$ from the bottom by a very small number, before taking the log.
+However, experiments show that this produces non-smooth estimates over $\mathcal{X}$ and the degree of smoothness varies drastically between different choices of that small number (see \cref{app:design_choices}).
+Instead, in virtue of the fact that $\lim_{p \to 0} - p \log{p} = 0$ even though $\lim_{p \to 0} - \log{p} = \infty$, we simply define the information estimate $\hat{u}_{x}(y)$ as zero if the empirical decision probability is non-positive,
+	\begin{equation}
+		\hat{u}_{x}(y) := \begin{cases}
+		- \log{\hat{p}_{y}(x)} & \mathrm{if } \quad \hat{p}_{y}(x) > 0 \\
+		0 & \mathrm{otherwise}. \end{cases}
+	\label{eq:empirical_information}
+	\end{equation}
+	It remains to show that $\hat{u}_{x} \in \mathcal{H}_{\delta}$.
+Indeed, the identity $\hat{u}_{x} = \sum_{c = 1}^{m} \hat{u}_{x}(c) \delta(c, \cdot)$ holds and thus $\hat{u}_{x}$ is in the span of the kernel canonical features.
+We then arrive at the following estimate for $h(x)$,
+	\begin{equation}
+		\hat{h}(x) := \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle = \hat{\bvec{u}}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x},
+		\label{eq:empirical_information_entropy}
+	\end{equation}
+	where $\hat{\bvec{u}}_{x} := \{\hat{u}_{x}(y_{i})\}_{i = 1}^{n}$.
+Similar to the case with decision probabilities \eqref{eq:decision_probability}, the information entropy estimate \eqref{eq:empirical_information_entropy} is not guaranteed to be non-negative.
+However, in practice these negative values are close to zero.
+Furthermore, negative estimated information entropy implies that the model is very confident about its prediction, and it suffices to simply clip the entropy at zero if strict information entropy is required (see \cref{app:design_choices}).
+We give the proof of convergence of \eqref{eq:empirical_information_entropy} in \cref{app:convergence_theorems}.
+	\begin{theorem}[Uniform Convergence of Empirical Information Entropy Function]
+		\label{thm:entropy_convergence_copy}
+		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical information entropy function $\hat{h} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_information_entropy} converges uniformly to the true information entropy function $h : \mathcal{X} \to [0, \infty)$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+	\end{theorem}
+
 \section{Convergence Theorems}
@@
 Since the kernel embedding classifier is based on conditional embeddings, this upper bound will be provided by the RKHS norm of the error between empirical and true conditional embeddings.
+Specifically, the empirical conditional embedding stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \citet[Theorem 6]{song2009hilbert}.
+That is,
+
+		\begin{equation}
+			\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists M_{\epsilon} > 0 \quad s.t.
+\quad \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
+		\label{eq:empirical_conditional_embedding_stochastic_convergence}
+		\end{equation}
 
@@
 
+\newpage
 \section{Learning Theoretic Bounds for the Kernel Embedding Classifiers}
@@
 		where each entry of the predictor $\bvec{f}_{\theta, \lambda}(x)$ is the decision probability estimate for $p_{c}(x)$.
-This defines the function class of the predictor for any given training set and kernel family,
-
-		\begin{equation}
-			F = \{ \bvec{f}_{\theta, \lambda}(x) : \theta \in \Theta, \lambda \in \Lambda \}.
+This defines the function class of the predictor over the kernel family and a set of regularisation parameters for a given training set $\{x_{i}, y_{i}\}_{i = 1}^{n}$,
+
+		\begin{equation}
+			F_{n}(\Theta, \Lambda) := \{ \bvec{f}_{\theta, \lambda}(x) : \theta \in \Theta, \lambda \in \Lambda \}.
 		\label{eq:predictor_class}
@@
 			\begin{equation}
-				\mathcal{R}(F) \leq 2 \alpha \rho.
+				\mathcal{R}(F_{n}(\Theta, \Lambda)) \leq 2 \alpha \rho.
 			\label{eq:rademacher_complexity_bound}
@@
 
-				The Rademacher complexity \citep[Definition 2]{bartlett2002rademacher} of a function class $F$ is
-
-				\begin{equation}
-					\mathcal{R}_{n}(F) := \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \frac{2}{n} \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg] = \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg],
+				The Rademacher complexity \citep[Definition 2]{bartlett2002rademacher} of the function class $F_{n}(\Theta, \Lambda)$ is
+
+				\begin{equation}
+					\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) := \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \frac{2}{n} \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg] = \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg],
 				\end{equation}
@@
 					\begin{aligned}
-						\mathcal{R}_{n}(F) &= \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg] \\
+						\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) &= \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg] \\
 						&\leq \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} \| \bm{\sigma} \| \bigg] \\
@@
 			\begin{equation}
-				\mathcal{R}_{n}(F) \leq 2 \rho \sqrt{k_{\tilde{\theta}}(0, 0)}.
+				\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) \leq 2 \rho \sqrt{k_{\tilde{\theta}}(0, 0)}.
 			\end{equation}
@@
 
-		In some approaches, the probabilities are clipped subject to the constraint that they sum up to one.
-This simply amounts to a rescaling to the decision function.
-For brevity, we will keep the above setup and notation.
-There is, however, one type of rescaling that simplifies subsequent analysis.
-That is, we could avoid introducing more scaling factors in our bounds if we first normalise the loss to lie within the unit range,
+		In our subsequent analysis, we require that our loss function has an image in $[0, 1]$. To do this, we simply rescale the loss function by dividing it by its largest value,
 
@@
 
-		We will refer to \eqref{eq:normalised_cross_entropy_loss} as the normalised cross entropy loss. We then further define the centred normalised cross entropy loss,
+		We will refer to \eqref{eq:normalised_cross_entropy_loss} as the normalised cross entropy loss \footnote{Of course, the above normalisation only ensures that the loss function attains a maximum of one, but can still be negative if $\hat{p}_{y}(x)$ higher than $1$.
+We can enforce this requirement by clipping the loss function at zero through $\max\{\cdot, 0\}$.
+However, for brevity, we will avoid explicitly writing this clipping operation, as it does not principally affect our subsequent analysis.
+It should nevertheless be understood that all losses discussed in this section are clipped from below at zero or, equivalently, the probability estimates $\hat{p}_{y}(x)$ are clipped from above at one.}.
+We then further define the centred normalised cross entropy loss,
 
@@
 			\begin{equation}
-				\frac{1}{M_{\epsilon}} \mathbb{E}[\mathcal{L}_{\epsilon}(Y, f(X))] \leq \frac{1}{n M_{\epsilon}} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + \mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}}.
+				\frac{1}{M_{\epsilon}} \mathbb{E}[\mathcal{L}_{\epsilon}(Y, f(X))] \leq \frac{1}{n M_{\epsilon}} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + \mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}}.
 			\label{eq:expected_loss_bound}
@@
 
-		The bound \eqref{eq:expected_loss_bound} involves the Rademacher complexity $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F)$ of the centred normalised cross entropy loss applied onto the class of functions $F$, and not just the Rademacher complexity $\mathcal{R}_{n}(F)$ of the class of functions $F$ itself.
+		The bound \eqref{eq:expected_loss_bound} involves the Rademacher complexity $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda))$ of the centred normalised cross entropy loss applied onto the class of functions $F_{n}(\Theta, \Lambda)$, and not just the Rademacher complexity $\mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$ of the class of functions $F_{n}(\Theta, \Lambda)$ itself.
 In \cref{thm:rademacher_complexity_bound}, we have bounded the latter.
@@
 			\begin{equation}
-				\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F) \leq 2 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \mathcal{R}_{n}(F),
+				\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 2 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \mathcal{R}_{n}(F_{n}(\Theta, \Lambda)),
 			\label{eq:composed_rademacher_complexity_bound}
@@
 
-			where $\tilde{\mathcal{L}}_{\epsilon} \circ F := \{(x, y) \mapsto \tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}_{\theta, \lambda}(x)) : \theta \in \Theta, \lambda \in \Lambda\}$.
+			where $\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda) := \{(x, y) \mapsto \tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}_{\theta, \lambda}(x)) : \theta \in \Theta, \lambda \in \Lambda\}$.
 
@@
 
-				Applying this result to our loss function $\tilde{\mathcal{L}}_{\epsilon}$ with $\psi = \tilde{\psi}$ and $F$ the function class of the kernel embedding classifier over $\theta \in \Theta$ and $\lambda \in \Lambda$, we have $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F) \leq 2 L_{\tilde{\psi}} \mathcal{R}_{n}(F)$, which proves the claim.
+				Applying this result to our loss function $\tilde{\mathcal{L}}_{\epsilon}$ with $\psi = \tilde{\psi}$ and $F = F_{n}(\Theta, \Lambda)$ the function class of the kernel embedding classifier over $\theta \in \Theta$ and $\lambda \in \Lambda$, we have $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 2 L_{\tilde{\psi}} \mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$, which proves the claim.
 			\end{proof}
@@
 Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}} = k_{\theta}(x, x) \leq \alpha^{2}$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
-For any integer $n \in \mathbb{N}_{+}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F$ satisfies
+For any integer $n \in \mathbb{N}_{+}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
 
@@
 
-		We will eventually be minimising the first two terms over some class of functions $f \in F$ with some approach, as a proxy to minimising the actual expected risk.
+		We will eventually be minimising the first two terms over some class of functions $f \in F_{n}(\Theta, \Lambda)$ with some approach, as a proxy to minimising the actual expected risk.
 It would be fruitful to develop an intuition for the tightness of the bound from the contributions of the training loss term and the model complexity term.
@@
 
-	\subsection{Training Objective}
-	\label{app:training_objective}
-
-		In this section, we use the result of \cref{thm:specific_expected_loss_bound_for_kec} to derive a training objective to learn the hyperparameters of the kernel embedding classifier.
+	\subsection{Hyperparameter Specific Bounds for Learning}
+	\label{sec:hyperparamter_bounds}
+
+		We are now ready to use the result of \cref{thm:specific_expected_loss_bound_for_kec} to derive a specific expected risk bound for a given choice of hyperparameters $\theta \in \Theta$ and $\lambda \in \Lambda$ of the kernel embedding classifier, and not just for a general set of hyperparameters.
 We focus on kernels $k_{\theta}$ that are bounded over the domain $\mathcal{X}$ in the sense that for each $\theta \in \Theta$, $k_{\theta}(x, x) < \infty$ for all $x \in \mathcal{X}$.
 
-		For some kernel parameters $\tilde{\theta} \in \Theta$ and regularisation parameter $\tilde{\lambda} \in \Lambda$, we construct the subset of kernel parameters $\Theta(\tilde{\theta}, \tilde{\lambda}) \subseteq \Theta$ and regularisation parameters $\Lambda(\tilde{\theta}, \tilde{\lambda}) \subseteq \Lambda$ such that
-
-%		\begin{equation}
-%			\begin{aligned}
-%				\Xi(\tilde{\theta}, \tilde{\lambda}) := \{ (\theta, \lambda) \in \Theta \times \Lambda : \| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}, \; k_{\theta}(x, x) \leq \alpha^{2}(\tilde{\theta}) := \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x) \}
-%			\end{aligned}
-%		\end{equation}
-
-		\begin{equation}
-			\begin{aligned}
-				\Theta(\tilde{\theta}, \tilde{\lambda}) &:= \{ \theta \in \Theta : \| W_{\theta, \tilde{\lambda}} \|_{\mathrm{tr}} \leq \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}} \; \forall \lambda \in \Lambda, \; k_{\theta}(x, x) \leq \alpha^{2}(\tilde{\theta}) := \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x) \}, \\
-				\Lambda(\tilde{\theta}, \tilde{\lambda}) &:= \{ \lambda \in \Lambda : \| W_{\tilde{\theta}, \lambda} \|_{\mathrm{tr}} \leq \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}} \; \forall \theta \in \Theta(\tilde{\theta}, \tilde{\lambda}) \}.
-			\end{aligned}
-		\end{equation}
-
-		Clearly, these subsets are non-empty, since $\tilde{\theta} \in \Theta(\tilde{\theta}, \tilde{\lambda})$ and $\tilde{\lambda} \in \Lambda(\tilde{\theta}, \tilde{\lambda})$ are themselves elements of these subsets.
-Note that $\alpha : \Theta \to \mathbb{R}_{+}$ must necessarily exist as the kernel $k_{\theta}$ is assumed to be bounded over the domain $\mathcal{X}$.
+		For some kernel parameters $\tilde{\theta} \in \Theta$ and regularisation parameter $\tilde{\lambda} \in \Lambda$, we construct a subset of hyperparameters (kernel parameters and regularisation parameters) $\Xi(\tilde{\theta}, \tilde{\lambda}) \subseteq \Theta \times \Lambda$ such that
+
+		\begin{equation}
+			\Xi(\tilde{\theta}, \tilde{\lambda}) := \{ (\theta, \lambda) \in \Theta \times \Lambda : \| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}, \; k_{\theta}(x, x) \leq \alpha^{2}(\tilde{\theta}) := \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x) \} \\
+			\label{eq:hyperparameter_subset_definition}
+		\end{equation}
+
+		Clearly, this subset is non-empty, since $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ it itself an element of this subset.
+Note that $\alpha : \Theta \to \mathbb{R}_{+}$ must necessarily exist as the kernel family $k_{\theta}$ is assumed to be bounded over the domain $\mathcal{X}$.
 The class of kernel embedding classifiers over this subset of hyperparameters is
@@
 		\begin{equation}
-			F(\tilde{\theta}, \tilde{\lambda}) = \{\bvec{f}_{\theta, \lambda}(x) : \theta \in \Theta(\tilde{\theta}, \tilde{\lambda}), \lambda \in \Lambda(\tilde{\theta}, \tilde{\lambda}) \}.
-		\end{equation}
-
-		Thus, we can assert that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ is bounded for all $\theta \in \Theta(\tilde{\theta}, \tilde{\lambda}), \lambda \in \Lambda(\tilde{\theta}, \tilde{\lambda})$, and that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}} = k_{\theta}(x, x) \leq \alpha^{2} = \alpha^{2}(\tilde{\theta})$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta(\tilde{\theta}, \tilde{\lambda})$.
+			F_{n}(\Xi(\tilde{\theta}, \tilde{\lambda})) := \{\bvec{f}_{\theta, \lambda}(x) : (\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda}) \}.
+		\end{equation}
+
+		Thus, we can assert that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ is bounded for all $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, and that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}} = k_{\theta}(x, x) \leq \alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$ is bounded in RKHS norm for all $x \in \mathcal{X}, (\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$.
 By \cref{thm:specific_expected_loss_bound_for_kec}, we can now claim the following.
 
-		\begin{claim}[Specific Expected Risk Bound for the Kernel Embedding Classifier]
-			\label{thm:specific_expected_loss_bound_for_kec_applied}
-
-			For any integer $n \in \mathbb{N}_{+}$ and $\epsilon \in (0, e^{-1})$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $\theta \in \Theta(\tilde{\theta}, \tilde{\lambda}), \lambda \in \Lambda(\tilde{\theta}, \tilde{\lambda})$ satisfies
-
-			\begin{equation}
-				\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e \alpha(\tilde{\theta}) \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}} + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
-			\label{eq:specific_expected_loss_bound_for_kec_applied}
+		\begin{claim}
+			\label{thm:general_trace_norm_bound}
+
+			For any integer $n \in \mathbb{N}_{+}$ and $\epsilon \in (0, e^{-1})$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ satisfies
+
+			\begin{equation}
+				\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e \sqrt{\sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)} \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}} + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
+			\label{eq:general_trace_norm_bound}
 			\end{equation}
@@
 			\end{equation}
+
+			\begin{proof}
+				This result is a direct consequence of applying \cref{thm:specific_expected_loss_bound_for_kec} with the choice of $\rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ and $\alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$.
+The inequality \eqref{eq:specific_expected_loss_bound_for_kec} then only holds for a subset of kernel parameter and regularisation $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ as defined by \eqref{eq:hyperparameter_subset_definition}.
+			\end{proof}
 		\end{claim}
 
-		Since $\tilde{\theta} \in \Theta(\tilde{\theta}, \tilde{\lambda})$ and $\tilde{\lambda} \in \Lambda(\tilde{\theta}, \tilde{\lambda})$, we choose $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
-Further more, since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:specific_expected_loss_bound_for_kec_applied} is true with probability $1 - \beta$ if we replace all the random variables $X_{i}, Y_{i}$ with the training observations $x_{i}, y_{i}$.
-
-		Therefore, in order to minimise the expected test loss, we propose the following training objective for the kernel embedding classifier,
-
-			\begin{equation}
-				\begin{aligned}
-					q(\tilde{\theta}, \tilde{\lambda}) &:= \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(y_{i}, \bvec{f}_{\tilde{\theta}, \tilde{\lambda}}(x_{i})) + 4 e r(\tilde{\theta}, \tilde{\lambda}), \quad \mathrm{where}\\
-					r(\tilde{\theta}, \tilde{\lambda}) &:= \alpha(\tilde{\theta}) \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\tilde{\theta}} + n \tilde{\lambda} I)^{-1} K_{\tilde{\theta}} (K_{\tilde{\theta}} + n \tilde{\lambda} I)^{-1} \bvec{Y}\bigg)}.
-				\label{eq:training_objective}
-				\end{aligned}
-			\end{equation}
+		Since inequality \eqref{eq:general_trace_norm_bound} holds for any $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ and we know that $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, we choose $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
+We now arrive at our final result from which we construct our training objective, where the bound is specific to a choice of hyperparameters $\theta \in \Theta$ and $\lambda \in \Lambda$.
+
+		\begin{theorem}[Expected Risk Bound under Trace Norm of the Kernel Embedding Classifier]
+			\label{thm:trace_norm_bound}
+
+			For any integer $n \in \mathbb{N}_{+}$ and $\epsilon \in (0, e^{-1})$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $\theta \in \Theta$ and $\lambda \in \Lambda$,
+
+			\begin{equation}
+				\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e r(\theta, \lambda) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
+			\label{eq:trace_norm_bound}
+			\end{equation}
+
+			where
+
+			\begin{equation}
+				\begin{aligned}
+					\bvec{f}_{\theta, \lambda}(x) &:= \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \bvec{k}_{\theta}(x), \\
+					r(\theta, \lambda) &:= \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} K_{\theta} (K_{\theta} + n \lambda I)^{-1} \bvec{Y}\bigg) \sup_{x \in \mathcal{X}} k_{\theta}(x, x)}.
+				\end{aligned}
+			\end{equation}
+
+			\begin{proof}
+				This result is a direct consequence of applying \cref{thm:general_trace_norm_bound} with the choice of $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
+We then replace the notation $\tilde{\theta} \rightarrow \theta$ and $\tilde{\lambda} \rightarrow \lambda$ back to avoid cluttered notation.
+Note that this should not be confused with the general $\theta$ and $\lambda$ from earlier theorems.
+			\end{proof}
+		\end{theorem}
 
@@
 
-%		\begin{table}[t]
-%			\begin{center}
-%				\begin{tabular}{ l || c c }
-%					& Wide Width & Narrow Width\\
-%					\hline
-%					Shallow Depth & Standard KEC & Linear KEC \\
-%					Deep Depth & Deep KEN & Deep Linear KEN \\ 
-%				\end{tabular}
-%			\end{center}
-%			\caption{Examples of kernel embedding classifier architectures}
-%			\label{tab:kernel_embedding_classifier_architectures}
-%		\end{table}
-
-		\begin{table}[t]
+		\begin{table}[h]
 			\begin{center}
@@
 
+\newpage
 \section{Full Probabilistic Inference and Mode Reconstruction}
@@
 
+\newpage
 \section{Design Choices and More Discussion}

### 2017-05-10 kernel_embedding_classifier.tex
Add Abstract

@@
 \begin{abstract}
-	Kernel embedding of probability distributions are a 
+	We propose learning-theoretic bounds for learning the hyperparameters of kernel embeddings in the probabilistic multiclass classification context.
+Kernel embeddings are nonparametric methods to represent probability distributions directly through observed data in a reproducing kernel Hilbert space (RKHS).
+However, the problem of hyperparameter learning for kernel embeddings remains challenging, often relying on heuristics and domain specific knowledge.
+We begin by developing the kernel embedding classifier (KEC), and prove the stochastic convergence of its probabilistic predictions.
+We then prove that expected classification risk can be bounded by using a data dependent Rademacher complexity measure in the probably approximately correct (PAC) framework.
+We use this bound to propose a scalable kernel learning algorithm for probabilistic multiclass classification.
+Classification performance is benchmarked on standard UCI datasets.
+We further apply our proposed kernel learning algorithm to learn feature representations of a deep convolutional network, with improved accuracy as compared to the original network, demonstrating the generality of this approach.
 \end{abstract}
@@
 
+Data dependent risk bounds
 \section{Introduction}
@@
 
-	\note{Draft: Introduction will need a more thorough discussion of motivation, related work, theoretical and practical implications, and contribution.}
+	Kernel embeddings are a principled way to represent probability distributions in a nonparametric setting.
+
+	learning theoretic (be specific and mention PAC)
+	(complexity penalty terms that are not data dependent cannot be universally effective) \citep{kearns1997experimental}
 

### 2017-05-10 kernel_embedding_classifier.tex
Draft for special cases completed

@@
 
-\title{CAKE: Classification avec Kernel Embeddings \\ with Rademacher Complexity Bounds}
+\title{CAKE: Classification avec Kernel Embeddings \\ with Rademacher Complexity based Risk Bounds}
 
@@
 We begin by developing the kernel embedding classifier (KEC), and prove the stochastic convergence of its probabilistic predictions.
-We then prove that expected classification risk can be bounded by using a data dependent Rademacher complexity measure in the probably approximately correct (PAC) framework.
+We then prove that expected classification error can be bounded with high probability using Rademacher complexity based risk bounds.
 We use this bound to propose a scalable kernel learning algorithm for probabilistic multiclass classification.
@@
 Data dependent risk bounds
+
 \section{Introduction}
@@
 	(complexity penalty terms that are not data dependent cannot be universally effective) \citep{kearns1997experimental}
-
-	Classification is perhaps one of the most important and thoroughly developed topics in machine learning and pattern recognition.
-Despite this, principled probabilistic classification on multiclass problems remains a difficult and challenging task, and most solutions tackle this issue rather indirectly.
-\note{Maybe elaborate on why multiclass problems are important and why we want probabilities estimates in our predictions.}
-
-	Support vector classifiers (SVC) \citep{m2001introduction}, for example, are originally designed for non-probabilistic binary classification.
-Its simple and convex optimisation structure makes the model very attractive both theoretically and in practice.
-However, in order to cope with overfitting, slack constraints introduce hyperparameters for which training does not directly addressed except through standard cross-validation.
-In order to extend to multiclass scenarios, binary relevance such as one-against-all, one-against-one, or decision trees are used to build a multiclass classifier from multiple binary classifiers \citep{aly2005survey, hsu2002comparison}.
-There are also no straightforward way of assigning probabilities to SVC, and in many approaches probabilities are simply arbitrary score measures that has been normalised \citep{zadrozny2002transforming, franc2011support} (\note{Check this}).
-As such, while the original SVC formulation is certainly elegant and practical, its multitude of variants for probabilistic multiclass classification becomes rather convoluted.
-
-	Within the similar domain of kernel-based classification, Gaussian process classifiers (GPC) \citep{rasmussen2006gaussian} are Bayesian models for which probability distributions are analysed in a principled manner, by constructing a latent model that is distributed as a Gaussian process.
-Nevertheless, the posterior class probabilities are not analytically tractable due to a non-Gaussian likelihood, which require methods such as Monte Carlo Markov Chain, expectation propagation, or variation inference to approximate.
-The GPC is also formulated as a binary classifier, and multiclass classification is either approached with binary relevance, or through introducing multiple latent functions that are to be squashed together through a softmax function if probabilistic outputs are to be retained.
-
-	On the other end of the spectrum, parametric models are limited in its ability to grow in capacity as the dataset grows.
-Neural networks \citep{lecun2015deep} mitigates this issue by growing deep instead of wide so that each layer of the network extract meaningful features from the dataset.
-While they require large amounts of data in order to work, neural networks has been shown to be able to learn almost any complex function.
-However, the choice of the network architecture remains, and principled probabilistic methods are still undergoing active research.
-In domains where the available data is scarce, neural networks also become very difficult to design and train.
-
-	In this paper, we propose a new and natural probabilistic multiclass classifier, the kernel embedding classifier (KEC), by casting multiclass classification problems into the kernel conditional embedding framework.
-Kernel embedding of probability distributions is a principled method for representing and manipulating general probability distributions, nonparametrically, in a reproducing kernel Hilbert space (RKHS) that is associated with a positive definite kernel.
-In this way, probability distributions do not need to be restricted to a parametric form, but instead fully expressed by the dataset in a nonparametric manner.
-In our approach, learning the classifier is done by learning a corresponding conditional embedding from data.
-We show that by placing a Kronecker delta kernel over the label space, decision probabilities and information entropies can be expressed as inner products in the correspondingly induced reproducing kernel Hilbert space, which can be consistently estimated from data using the conditional embedding framework.
-This method is very general and makes no distinction between binary and multiclass classification, presenting a unified and principled method for all probabilistic classification tasks.
-
-	Being developed very generally for any choice of positive definite kernel $k$, the kernel embedding classifier places no limit on the family of kernels and the structure of its hyperparameters.
-In the current kernel embedding literature, there is no standard method to train the hyperparameters of a conditional embedding besides cross-validation.
-We further propose and develop a hyperparameter training scheme based on Rademacher complexity bounds, which appropriately balances the accuracy and generalisation capabilities of the classifier.
-We then develop a mini-batch stochastic gradient descent version of such a training procedure, which brings the notorious complexity of kernel methods that is cubic in the size of the dataset down to only cubic in the mini-batch size.
-
-	With no restrictions on the type of kernel used for our classifier, we apply our training algorithm to learn kernels with deep convolutional features on standard image recognition tasks such as the MNIST dataset (\note{Mention more on experiments later when they are ready}).
-Specifically, we also test the performance of our classifier on ``high $d$, low $n$'' domains where the dimensionality of the problem is large compared to the number of observations, by restricting the size of the dataset to be less than the dimensionality of the problem.
-
-	The fully nonparametric and probabilistic nature of the classifier also allows us to perform probabilistic inference on the inputs and, most interestingly, the hidden layers if using a deep kernel.
-Specifically, we can quantify and obtain the most representative input sample and hidden features of each class.
-
-	In summary, our contributions are:
-
-	\begin{itemize}
-		\item A novel probabilistic multiclass classifier, the kernel embedding classifier (KEC), based on the theory and framework of kernel embedding of conditional distributions;
-		\item Convergence guarantees on decision probability and information entropy estimates;
-		\item A novel training algorithm based on minimising Rademacher complexity bounds of our kernel embedding classifier in a reproducing kernel Hilbert space, which balances classification performance and provides greater generalisation capabilities to the classifier;
-		\item A mini-batch stochastic gradient descent variant of the above training algorithm, reducing training complexity from $O(n^{3})$ to $O(n_{b}^{3})$ in time and from $O(n^{2})$ to $O(n_{b}^{2})$ in space for a training dataset of size $n$ and a mini-batch size of $n_{b} << n$;
-		\item A deep convolutional network extension to the kernel embedding classifier to learn a deep convolutional kernel embedding network for image recognition tasks; And,
-		\item A methodology to perform probabilistic inference and mode reconstruction of the inputs and hidden feature layers, where we quantify and obtain the most representative sample and hidden features of each class.
-	\end{itemize}
-
-%	Most classification algorithms are binary classifiers, which can only handle the case where the output can only take instances from one of two classes.
-This is true for both SVM classifiers and GP classifiers.
-Part of the reason for that is that it works by learning a continuous latent function which basically represents the `strength' of one of the classes, and so it is really just inferring how likely an input is from class A and if not it would be from class B.
-To build a multiclass classifier, a simple approach is to train multiple binary classifiers to tell apart pairs of classes or sets of classes, and somehow fuse these results together.
-Notable examples are One Versus All (OVA) and All Versus All (AVA) approaches, as well as binary tree approaches.
-%	
-%	\href{http://www.vision.caltech.edu/malaa/publications/aly05multiclass.pdf}{Here} is a 2005 Survey which summarises the state-of-the-art in multiclass classification at the time, which supports what I just said above.
-It does not seem like the above scenario has fundamentally changed in the past 10+ years, although more sophisticated versions of what was described above has been proposed and tested.
-%	
-%	The idea I am proposing here is actually very simple and intuitive.
-Suppose the training data is $\{\bvec{x}_{i}, y_{i}\}_{i = 1}^{n}$ where $\bvec{x}_{i} \in \mathcal{X}, y_{i} \in \mathbb{N}_{m}$ for all $i \in \mathbb{N}_{n}$ with $\mathbb{N}_{m} := \{1, 2, \cdots, m\}$.
-To clarify, $n$ is the number of training points, $m$ is the number of classes involved, and $\mathcal{X}$ is usually a subset of some euclidean space $\mathbb{R}^{d}$ but it does not necessarily have to be so (which is an advantage in kernel methods in general, such as GPs).
-The idea is to use the kernel embedding framework to compute a conditional embedding empirically from those training points.
-We then show that class probabilities can be computed from the conditional embedding if we place a Kronecker delta kernel on the space of the outputs, $\mathbb{N}_{m}$.
-We show that these class probabilities estimates are consistent estimates of the true class probabilities.
-Furthermore, the corresponding Shannon information entropy estimate at each query input can be computed, in two different ways, and we explore the performance of each of these approaches.
-In this way, we propose a natural probabilistic classifier for multiclass classification.
-%	
-%	Computationally, this probabilistic classifier is to do the following.
-Given a set of training points $\{\bvec{x}_{i}, y_{i}\}_{i = 1}^{n}$ and a set of query inputs $\{\bvec{x}^{\star}_{i}\}_{i = 1}^{n^{\star}}$, our classifier can output $\hat{P}^{\star} = \{\hat{\bvec{p}}^{\star}_{i}\}_{i = 1}^{n^{\star}}$, the estimated class probabilities at the query points, and also $\bvec{h}^{\star} = \{\hat{h}^{\star}_{i}\}_{i = 1}^{n^{\star}}$, the estimated information entropy at the query points.
-%	\\
-%	\\
-%
-%	In \cref{sec:kernel_embedding_classifier}, by expressing decision probabilities as expectations of indicator functions in the RKHS, we derived a consistent estimate of the decision probabilities from an inner product between the empirical conditional embedding and the indicator function.
-Likewise, in \cref{sec:information_entropy}, by expressing information entropy as expected information in the RKHS, we derived a consistent estimate of the information entropy from an inner product between the empirical conditional embedding and the information function.
-
-	Contrary to parametric models, kernel methods are nonparametric, and thus its model capacity grows with increasing data.
-Within a large enough family of kernels $k_{\theta}$, the kernel embedding classifier always has the capacity to shatter the training data and produce zero training error.
-Given that it has such capabilities, we instead focus on learning the simplest model that can generalise well to new test data.
-If we instead choose to train the classifier by adding some measure of training error as a penalty term to \eqref{eq:trace_norm_optimisation}, such as the training cross entropy loss, then it can very easily overfit by adapting its model capacity to the training data closely.
-The Rademacher complexity regularises this behaviour to learn a good balance between training error and unseen test error.
-In short, while parametric models have limited capacity and thus trying to learn to perform well on a training set to its best ability is a good indicator to test performance, nonparametric models has infinite capacity and need to learn not to exploit this capacity on training data and instead learn the simplest pattern it can to be able to infer about new test instances.
-Indeed, experiments show that KEC training usually starts with high training accuracy and very low cross entropy loss, and eventually learns the simplest model while maintaining that training accuracy, or even relaxes the training accuracy if the model is simply too complicated and unlikely to generalise well.
-That is, the training usually starts from a state of overfitting, and eventually learns simpler patterns and structures.
-This is in contrast with parameteric models, where training usually begins with low training accuracy that is to be improved as training continues.
 
@@
 	where $K := \{k(x_{i}, x_{j})\}_{i = 1, j = 1}^{n, n}$, $\Phi := \begin{bmatrix} \phi(x_{1}) & \dots & \phi(x_{n}) \end{bmatrix}$, $\Psi := \begin{bmatrix} \psi(y_{1}) & \dots & \psi(y_{n}) \end{bmatrix}$, $\phi(x) := k(x, \cdot)$, $\psi(y) := l(y, \cdot)$, and $\lambda$ is the regularisation parameter for the conditional operator \citep{song2013kernel}.
-We then define the empirical conditional embedding by $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$, which stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \citet[Theorem 6]{song2009hilbert}.
+We then define the empirical conditional embedding by $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$, which stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \cite[Theorem 6]{song2009hilbert}.
 This allows us to approximate the conditional expectation \eqref{eq:conditional_expectation} with $\langle \hat{\mu}_{Y | X = x}, g \rangle$ instead,
 	\begin{equation}
-		\mathbb{E}[g(Y) | X = x] \approx \langle \hat{\mu}_{Y | X = x}, g \rangle = \bvec{g}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x},
+		\mathbb{E}[g(Y) | X = x] \approx \langle \hat{\mu}_{Y | X = x}, g \rangle = \bvec{g}^{T} (K + n \lambda I)^{-1} \bvec{k}(x),
 	\label{eq:empirical_conditional_expectation}
 	\end{equation}
-	where $\bvec{g} := \{g(y_{i})\}_{i = 1}^{n}$ and $\bvec{k}_{x} := \{k(x_{i}, x\}_{i = 1}^{n}$, knowing that it would converge to the true expectation as $n$ increases for sufficiently small $\lambda$.
+	where $\bvec{g} := \{g(y_{i})\}_{i = 1}^{n}$ and $\bvec{k}(x) := \{k(x_{i}, x\}_{i = 1}^{n}$, knowing that it would converge to the true expectation as $n$ increases for sufficiently small $\lambda$.
 
@@
 	\begin{equation}
-		\hat{p}_{c}(x) = f_{c}(x) := \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x}.
+		\hat{p}_{c}(x) = f_{c}(x) := \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x).
 	\label{eq:empirical_decision_probability}
@@
 	\begin{equation}
-		\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x} \in \mathbb{R}^{m},
+		\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \bvec{k}(x) \in \mathbb{R}^{m},
 	\label{eq:empirical_decision_probability_vector}
@@
 
-	We proceed to show that the empirical decision probabilities \eqref{eq:empirical_decision_probability} is a consistent estimator for the actual decision probabilities as the dataset increases (See \cref{thm:probability_convergence} of \cref{app:convergence_theorems} for proof).
+	We proceed to prove that the empirical decision probabilities \eqref{eq:empirical_decision_probability} converges to the true decision probabilities with more data.
+We direct the reader to the supplementary material for proof.
 	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
@@
 
-	If strict, valid probabilities are required for interpretation, visualisation, or other purposes, the probabilities can be clipped at zero then normalised to one - a procedure we refer to as \textit{clip-normalisation},
+	If strict, valid probabilities are required for interpretation, visualisation, or other purposes, the probabilities can be clipped at zero then normalised to one, a procedure we refer to as \textit{clip-normalisation},
 	\begin{equation}
@@
 	Notice that for classification prediction, the argmax solution over the classes of the empirical decision probabilities \eqref{eq:empirical_decision_probability} and its clip-normalised version \eqref{eq:probability_clip_normalise} remain the same.
-Furthermore, since $\hat{p}_{c}(x)$ converges to valid probabilities $p_{c}(x)$ according to \cref{thm:probability_convergence_copy}, the effect of clip-normalisation reduces as $n$ increases such that $\tilde{p}_{c}(x)$ becomes very close to $\hat{p}_{c}(x)$ and $p_{c}(x)$.
-
-\section{Hyperparameter Learning with Rademacher Complexity Bounds}
+Furthermore, since $\hat{p}_{c}(x)$ converges to true probabilities $p_{c}(x)$ according to \cref{thm:probability_convergence_copy}, the effect of clip-normalisation reduces as $n$ increases such that $\tilde{p}_{c}(x)$ becomes very close to $\hat{p}_{c}(x)$ and $p_{c}(x)$.
+
+\section{Learning with Rademacher Complexity based Risk Bounds}
 \label{sec:hyperparameter_learning}
@@
 	\begin{algorithm}[tb]
-		\caption{Kernel Embedding Classifier Training with Stochastic Gradient Descent}
+		\caption{KEC Hyperparameter Learning with Batch Stochastic Gradient Descent}
 		\label{alg:kernel_embedding_classifier_training}
@@
 			\REPEAT
-			\STATE Sample the next batch batch $\mathcal{I} \subseteq \mathbb{N}_{n}$, $| \mathcal{I} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I} = \mathbb{N}_{n}$)
+			\STATE Sample the next batch $\mathcal{I} \subseteq \mathbb{N}_{n}$, $| \mathcal{I} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I} = \mathbb{N}_{n}$)
 			\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
@@
 
-	\subsection{Mini-Batch Stochastic Gradient Descent}
+	\subsection{Batch Stochastic Gradient Descent}
 	\label{sec:stochastic_gradient_descent}
@@
 \section{Experiments}
-
-%	\note{Note that while it would certainly be great, the point of developing this kernel embedding classifier is not to beat other existing classification algorithms.
-The purpose is to develop a simple and elegant fully probabilistic multiclass classifier based on embedding the observed data directly into a reproducing kernel Hilbert space, with a quantifiable notion of model complexity.
-This is what we will aim to show here in the experiments as well.
-Below is just a summary of what has been done but has not been put together neatly yet.}
-%	
-%	\textbf{Experiments to Show}: We are aiming to do experiments on one toy dataset for illustration and visualisation, and on two real world datasets for benchmarking performance.
-So far, I am using the iris dataset for the toy dataset, and MNIST for one of the real world datasets.
-We should still find a third real world dataset that will really benefit from such a flexible nonparametric, probabilistic multiclass classifier.
-%	
-%	\begin{itemize}
-%		\item A toy 2D classification tasks for visualising the properties and capabilities of the kernel embedding classifier.
-An simple example is the iris dataset, where we take only 2 attributes.
-There are three classes, so the probabilities can be visualised using RGB.
-We first use the first two attributes of the dataset, where the training examples are very non-separable.
-The point is to demonstrate that the kernel embedding classifier learns a simple and reasonable model that does not overfit, even though it has the capacity to shatter all the training data and have 100\% training accuracy.
-We then show that if we use the standard cross entropy loss as the objective for training, then we easily overfit the data.
-%		\item We also show plots illustrating how the training objective, performance of the classifier, and the hyperparameters changes during the training procedure.
-%		\item We then show results for training using SGD, which reveals that at a faster speed we arrive at the same solution as before.
-%		\item We can then move on to actual real world datasets, like MNIST.
-%		\item The MNIST dataset has 60000 training images and 10000 test images.
-So far I have results for only giving the first 500 training images to the kernel embedding classifier (much smaller than the dimensionality of the problem, which is 784), and it is to perform on the whole 10000 test images.
-We show that with a Gaussian kernel, we get around 82\% accuracy.
-Then, with a simple extension by adding three convolutional layers before give it to the Gaussian kernel, we get around 92\% accuracy.
-Of course, we also report the cross entropy loss.
-We do this with both gradient descent and SGD.
-We then compare this to support vector classifiers and Gaussian process classifiers.
-Then also compare this to state of the art convolutional neural networks with 500 observations for training data.
-%		\item We can also use the learned length scale of a stationary kernel to visualise the most discriminative pixels in the image useful to the classifier.
-%		\item More to come...
-%	\end{itemize}
 
@@
 \section{Information Entropy}
-\label{sec:information_entropy}
+\label{app:information_entropy}
 
@@
 	\begin{equation}
-		\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle = \bvec{u}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x}.
+		\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle = \bvec{u}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x).
 	\end{equation}
@@
 	\begin{equation}
-		\hat{h}(x) := \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle = \hat{\bvec{u}}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x},
+		\hat{h}(x) := \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle = \hat{\bvec{u}}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x),
 		\label{eq:empirical_information_entropy}
@@
 Since the kernel embedding classifier is based on conditional embeddings, this upper bound will be provided by the RKHS norm of the error between empirical and true conditional embeddings.
-Specifically, the empirical conditional embedding stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \citet[Theorem 6]{song2009hilbert}.
+Specifically, the empirical conditional embedding stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \cite[Theorem 6]{song2009hilbert}.
 That is,
@@
 				&= \psi(c)^{T} \Psi (K + n \lambda I)^{-1} \Phi^{T} \phi(x) \\
-				&= \bvec{l}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x}, \\
+				&= \bvec{l}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x), \\
 			\end{aligned}
@@
 			\begin{equation}
-				\hat{\mu}_{Y | X = x}(c) = \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}_{x} =: \hat{p}_{c}(x).
+				\hat{\mu}_{Y | X = x}(c) = \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x) =: \hat{p}_{c}(x).
 			\end{equation}
@@
 
-	In \cref{sec:information_entropy}, we proposed an estimator for the information entropy $h(x)$ for a prediction at $x \in \mathcal{X}$.
+	In \cref{app:information_entropy}, we proposed an estimator for the information entropy $h(x)$ for a prediction at $x \in \mathcal{X}$.
 Since this estimator is now based on the inner product between the empirical conditional embedding and another empirically estimate function, instead of between the empirical conditional embedding and a known function, it is not immediately clear that such an estimator converges.
@@
 Similarly, assuming that $p_{c}(x)$ is never exactly zero, $u_{x}(c)$ is also finite for all $c \in \mathbb{N}_{m}$ and thus so is its RKHS norm.
-We already know that $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$ stochastically converges to zero at the rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ \citep{song2009hilbert}.
+We already know that $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$ stochastically converges to zero at the rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ \citep[Theorem 6]{song2009hilbert}.
 Thus, it remains to bound $\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}}$ by a multiple of $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$.
@@
 	In this section we derive the Rademacher complexity bound of the kernel embedding classifier, and show that it can be used in conjunction with the training loss to bound the expected risk with high probability.
-With such a bound, we devise a training objective to learn the hyperparameters for the kernel embedding classifier.
 
@@
 		where each entry of the predictor $\bvec{f}_{\theta, \lambda}(x)$ is the decision probability estimate for $p_{c}(x)$.
-This defines the function class of the predictor over the kernel family and a set of regularisation parameters for a given training set $\{x_{i}, y_{i}\}_{i = 1}^{n}$,
+This defines the function class of the predictor over the kernel family and a set of regularisation parameters for any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$,
 
@@
 Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}} = k_{\theta}(x, x) \leq \alpha^{2}$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
-The Rademacher complexity of the class of kernel embedding classifiers $F$ \eqref{eq:predictor_class} defined over $\theta \in \Theta, \lambda \in \Lambda$ is bounded by
-
-			\begin{equation}
-				\mathcal{R}(F_{n}(\Theta, \Lambda)) \leq 2 \alpha \rho.
+For any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of kernel embedding classifiers $F_{n}(\Theta, \Lambda)$ \eqref{eq:predictor_class} defined over $\theta \in \Theta, \lambda \in \Lambda$ is bounded by
+
+			\begin{equation}
+				\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) \leq 2 \alpha \rho.
 			\label{eq:rademacher_complexity_bound}
@@
 Further suppose there exists $\tilde{\theta} \in \Theta$ such that that $k_{\theta}(0, 0) \leq k_{\tilde{\theta}}(0, 0)$ for all $\theta \in \Theta$.
-The Rademacher complexity of the class of kernel embedding classifiers $F$ defined over $\theta \in \Theta, \lambda \in \Lambda$ is bounded by
+For any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of kernel embedding classifiers $F_{n}(\Theta, \Lambda)$ defined over $\theta \in \Theta, \lambda \in \Lambda$ is bounded by
 
@@
 	\subsection{Expected Risk Bounds}
-	\label{thm:expected_risk_bound}
+	\label{app:expected_risk_bounds}
 
@@
 		\begin{equation}
-			\mathcal{L}(y, \hat{\bvec{p}}(x)) := - \log{\bvec{y}^{T} \hat{\bvec{p}}(x)} = - \log{\hat{p}_{y}(x)},
-		\end{equation}
-
-		where $\hat{\bvec{p}}(x)$ are the inferred probabilities of each class for the example $x \in \mathcal{X}$.
-Since logarithms explode at zero, in practice the probability estimate is often clipped beforehand at a small threshold $\epsilon \in (0, 1)$,
-
-		\begin{equation}
-			\mathcal{L}_{\epsilon}(y, \hat{\bvec{p}}(x)) := - \log{\max \{\bvec{y}^{T} \hat{\bvec{p}}(x), \epsilon \} } = - \log{\max \{ \hat{p}_{y}(x), \epsilon \}}.
+			\mathcal{L}(y, \bvec{f}(x)) := - \log{\bvec{y}^{T} \bvec{f}(x)} = - \log{f_{y}(x)},
+		\end{equation}
+
+		where $\bvec{f}(x)$ are the inferred decision probability estimates of each class for the example $x \in \mathcal{X}$.
+Since logarithms explode at zero, in practice the probability estimate is often clipped from below at a predetermined threshold $\epsilon \in (0, 1)$.
+Furthermore, it is also convenient to clip the probability estimate from above at one to avoid negative losses, as further reward for high prediction probabilities are not necessary.
+In other words, assigning a probability estimate greater than one to the correct label is really just correctly assigning a probability estimate of one but with slight approximation error.
+Consequently, with the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$, we define the effective cross entropy loss as
+
+		\begin{equation}
+			\mathcal{L}_{\epsilon}(y, \bvec{f}(x)) := - \log{ [\bvec{y}^{T} \bvec{f}(x)]_{\epsilon}^{1} } = - \log{ [f_{y}(x)]_{\epsilon}^{1} },
 		\label{eq:cross_entropy_loss}
@@
 
-		In our subsequent analysis, we require that our loss function has an image in $[0, 1]$. To do this, we simply rescale the loss function by dividing it by its largest value,
-
-		\begin{equation}
-			\begin{aligned}
-				\bar{\mathcal{L}}_{\epsilon}(y, \hat{\bvec{p}}(x)) &:= \frac{1}{M_{\epsilon}} \mathcal{L}_{\epsilon}(y, \hat{\bvec{p}}(x)) = - \frac{1}{M_{\epsilon}} \log{\max \{ \hat{p}_{y}(x), \epsilon \}}, \\
+		In this way, our cross entropy loss \eqref{eq:cross_entropy_loss} is both bounded and positive.
+In our subsequent analysis, we require that our loss function has an image in $[0, 1]$.
+To do this, we simply rescale the loss function by dividing it by its largest value,
+
+		\begin{equation}
+			\begin{aligned}
+				\bar{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) &:= \frac{1}{M_{\epsilon}} \mathcal{L}_{\epsilon}(y, \bvec{f}(x)) = - \frac{1}{M_{\epsilon}} \log{ [f_{y}(x)]_{\epsilon}^{1} }, \\
 				M_{\epsilon} &:= - \log{\epsilon}.
@@
 		\begin{equation}
-			\tilde{\mathcal{L}}_{\epsilon}(y, \hat{\bvec{p}}(x)) := \bar{\mathcal{L}}_{\epsilon}(y, \hat{\bvec{p}}(x)) - \bar{\mathcal{L}}_{\epsilon}(y, \bvec{0}) = - \frac{1}{M_{\epsilon}} \log{\max \{ \hat{p}_{y}(x), \epsilon \}} - 1.
+			\tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) := \bar{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) - \bar{\mathcal{L}}_{\epsilon}(y, \bvec{0}) = - \frac{1}{M_{\epsilon}} \log{ [f_{y}(x)]_{\epsilon}^{1} } - 1.
 		\label{eq:centred_normalised_cross_entropy_loss}
@@
 
-		\begin{corollary}[Expected Risk Bound]
+		\begin{lemma}[Expected Risk Bound]
 		\label{thm:expected_normalised_cross_entropy_loss_bound}
-			For any integer $n \in \mathbb{N}_{+}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F$ satisfies
+			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
 
@@
 			\end{proof}
-		\end{corollary}
-
+		\end{lemma}
+
+		Equivalently, by definition \eqref{eq:predictor_class}, this result holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
 The bound \eqref{eq:expected_loss_bound} involves the Rademacher complexity $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda))$ of the centred normalised cross entropy loss applied onto the class of functions $F_{n}(\Theta, \Lambda)$, and not just the Rademacher complexity $\mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$ of the class of functions $F_{n}(\Theta, \Lambda)$ itself.
@@
 
-			The Rademacher complexity of the class of cross entropy loss applied onto the kernel embedding classifier is bounded by
+			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of cross entropy loss applied onto the kernel embedding classifier is bounded by
 
@@
 			\begin{proof}
-				Let $\tilde{\psi}(z) := - \frac{1}{M_{\epsilon}} \log{\max \{z, \epsilon \}} - 1$ so that $\tilde{\psi} : \mathbb{R} \to \mathbb{R}$ satisfies $\tilde{\psi}(0) = 0$.
-Then, the centered normalised cross entropy loss can be written as $\tilde{\mathcal{L}}_{\epsilon}(y, \hat{\bvec{p}}(x)) = \tilde{\psi}(\hat{p}_{y}(x))$.
+				Let $\tilde{\psi}(z) := - \frac{1}{M_{\epsilon}} \log{[z]_{\epsilon}^{1}} - 1$ so that $\tilde{\psi} : \mathbb{R} \to \mathbb{R}$ satisfies $\tilde{\psi}(0) = 0$.
+Then, the centered normalised cross entropy loss can be written as $\tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) = \tilde{\psi}(f_{y}(x))$.
 In particular, $\tilde{\psi}(z)$ is piecewise differentiable.
@@
 
-				The real-valued function $\tilde{\psi}$ can be split into two piecewise regions over the real domain,
+				The real-valued function $\tilde{\psi}$ can be split into three piecewise regions over the real domain,
 
@@
 					\tilde{\psi}(z) = \begin{cases}
-						0, \qquad &z \leq \epsilon, \\
-						- \frac{1}{M_{\epsilon}}\log{z} - 1, \qquad &z > \epsilon.
+						0, \qquad &z \in (-\infty, \epsilon], \\
+						- \frac{1}{M_{\epsilon}}\log{z} - 1, \qquad & z \in (\epsilon, 1), \\
+						-1, & z \in [1, \infty).
 					\end{cases}
@@
 
-				The derivative over the region $z \leq \epsilon$ is thus $0$ and the local Lipschitz constant over that region is thus $0$. We then focus on the other region,
-
-				\begin{equation}
-					\begin{aligned}
-						\sup_{z \in (\epsilon, \infty)} | \tilde{\psi}'(z) | = \sup_{z \in (\epsilon, \infty)} \Big| - \frac{1}{z M_{\epsilon}} \Big| = \Big| - \frac{1}{\epsilon M_{\epsilon}} \Big| = \Big| \frac{1}{\epsilon \log{\epsilon}} \Big| = \frac{1}{\epsilon \log{\frac{1}{\epsilon}}}.
+				The derivative over the regions $z \in (-\infty, \epsilon]$ and $z \in [1, \infty)$ is thus $0$ and the local Lipschitz constant over that region is thus $0$. We then focus on the other region,
+
+				\begin{equation}
+					\begin{aligned}
+						\sup_{z \in (\epsilon, 1)} | \tilde{\psi}'(z) | = \sup_{z \in (\epsilon, 1)} \bigg| - \frac{1}{z M_{\epsilon}} \bigg| = \sup_{z \in (\epsilon, 1)} \frac{1}{z M_{\epsilon}} = \frac{1}{\epsilon M_{\epsilon}} = \frac{1}{\epsilon \log{\frac{1}{\epsilon}}}.
 					\end{aligned}
@@
 
-				For a given general loss function $\mathcal{L}$, \citet[Corollary 3.17]{ledoux2013probability} proved that if there exists a Lipschitz real-valued function $\psi : \mathbb{R} \to \mathbb{R}$, $\psi(0) = 0$, with constant $L_{\tilde{\psi}}$ such that $\mathcal{L}(y, f(x)) = \psi(f_{y}(x))$, then $\mathcal{R}_{n}(\mathcal{L} \circ F) \leq 2 L_{\psi} \mathcal{R}_{n}(F)$.
+				For a given general loss function $\mathcal{L}$, \citet[Corollary 3.17]{ledoux2013probability} proved that if there exists a Lipschitz real-valued function $\psi : \mathbb{R} \to \mathbb{R}$, $\psi(0) = 0$, with constant $L_{\psi}$ such that $\mathcal{L}(y, f(x)) = \psi(f_{y}(x))$, then $\mathcal{R}_{n}(\mathcal{L} \circ F) \leq 2 L_{\psi} \mathcal{R}_{n}(F)$ for any class of functions $F$.
 This result is also described in \citet[Theorem 12.4]{bartlett2002rademacher}.
 
-				Applying this result to our loss function $\tilde{\mathcal{L}}_{\epsilon}$ with $\psi = \tilde{\psi}$ and $F = F_{n}(\Theta, \Lambda)$ the function class of the kernel embedding classifier over $\theta \in \Theta$ and $\lambda \in \Lambda$, we have $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 2 L_{\tilde{\psi}} \mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$, which proves the claim.
+				Applying this result to our loss function with $\mathcal{L} = \tilde{\mathcal{L}}_{\epsilon}$ with $\psi = \tilde{\psi}$ and $F = F_{n}(\Theta, \Lambda)$, we have $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 2 L_{\tilde{\psi}} \mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$, which proves the claim.
 			\end{proof}
@@
 
-		\begin{theorem}[General Expected Risk Bound for the Kernel Embedding Classifier]
+		\begin{lemma}[General Expected Risk Bound for the Kernel Embedding Classifier]
 			\label{thm:expected_loss_bound_for_kec}
@@
 Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}} = k_{\theta}(x, x) \leq \alpha^{2}$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
-For any integer $n \in \mathbb{N}_{+}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
+For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
 
@@
 			\end{proof}
-		\end{theorem}
+		\end{lemma}
 
@@
 
-		To see why inequality \eqref{eq:loss_inequality} holds, note that $\max \{ \hat{p}_{y}(x), \epsilon \} \leq \max \{ \hat{p}_{y}(x), e^{-1} \}$ holds for all $\epsilon \in (0, e^{-1}), x \in \mathcal{X}, y \in \mathcal{Y}$.
+		To see why inequality \eqref{eq:loss_inequality} holds, note that $[f_{y}(x)]_{\epsilon}^{1} \leq [f_{y}(x)]_{e^{-1}}^{1}$ holds for all $\epsilon \in (0, e^{-1}), x \in \mathcal{X}, y \in \mathcal{Y}$.
 Applying negative log to both sides yields the inequality from definition \eqref{eq:cross_entropy_loss}.
@@
 Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}} = k_{\theta}(x, x) \leq \alpha^{2}$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
-For any integer $n \in \mathbb{N}_{+}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F$ satisfies
+For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
 
@@
 
-	\subsection{Hyperparameter Specific Bounds for Learning}
-	\label{sec:hyperparamter_bounds}
+	\subsection{Expected Risk Bounds for Hyperparameter Learning}
+	\label{app:expected_risk_bounds_for_hyperparameter_learning}
 
@@
 
-		\begin{claim}
-			\label{thm:general_trace_norm_bound}
-
-			For any integer $n \in \mathbb{N}_{+}$ and $\epsilon \in (0, e^{-1})$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ satisfies
+		\begin{lemma}[General Expected Risk Bound for KEC Hyperparameter Learning]
+			\label{thm:general_expected_risk_bound_hyperparameter_learning}
+
+			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ satisfies
 
@@
 				\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e \sqrt{\sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)} \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}} + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
-			\label{eq:general_trace_norm_bound}
-			\end{equation}
-
-			where
+			\label{eq:general_expected_risk_bound_hyperparameter_learning}
+			\end{equation}
+
+			for every $\epsilon \in (0, e^{-1})$, where
 
@@
 			\end{proof}
-		\end{claim}
-
-		Since inequality \eqref{eq:general_trace_norm_bound} holds for any $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ and we know that $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, we choose $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
-We now arrive at our final result from which we construct our training objective, where the bound is specific to a choice of hyperparameters $\theta \in \Theta$ and $\lambda \in \Lambda$.
-
-		\begin{theorem}[Expected Risk Bound under Trace Norm of the Kernel Embedding Classifier]
-			\label{thm:trace_norm_bound}
-
-			For any integer $n \in \mathbb{N}_{+}$ and $\epsilon \in (0, e^{-1})$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $\theta \in \Theta$ and $\lambda \in \Lambda$,
+		\end{lemma}
+
+		Since inequality \eqref{eq:general_expected_risk_bound_hyperparameter_learning} holds for any $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ and we know that $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, we choose $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
+We now arrive at our final result from which we can bound the expected risk for a specific choice of hyperparameters $\theta \in \Theta$ and $\lambda \in \Lambda$.
+
+		\begin{theorem}[Expected Risk Bound for KEC Hyperparameter Learning]
+			\label{thm:expected_risk_bound_hyperparameter_learning}
+
+			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $\theta \in \Theta$ and $\lambda \in \Lambda$ satisfies
 
@@
 				\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e r(\theta, \lambda) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
-			\label{eq:trace_norm_bound}
-			\end{equation}
-
-			where
+			\label{eq:expected_risk_bound_hyperparameter_learning}
+			\end{equation}
+
+			for every $\epsilon \in (0, e^{-1})$, where
 
@@
 			\begin{proof}
-				This result is a direct consequence of applying \cref{thm:general_trace_norm_bound} with the choice of $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
+				This result is a direct consequence of applying \cref{thm:general_expected_risk_bound_hyperparameter_learning} with the choice of $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
 We then replace the notation $\tilde{\theta} \rightarrow \theta$ and $\tilde{\lambda} \rightarrow \lambda$ back to avoid cluttered notation.
@@
 For example, we can construct new kernels through convex combinations or products of multiple simpler kernels \citep{genton2001classes}.
+Any new parameters, such as coefficients for linear combinations of simpler kernels, can be included into the kernel parameters $\theta$ and learned in the same way as before.
 Alternatively, there may be domain specific structures or representations within the data that can be exploited.
@@
 This construction allows the incorporation of trainable domain specific structures and enables scalability to larger datasets.
-We first begin by introducing the linear kernel embedding classifier (LKEC, Linear CAKE, or LAKE) in \cref{app:linear_kernel_embedding_classifier}, where explicit feature maps can be learned while enabling scalability to larger datasets.
-We then construct the deep kernel embedding network (DKEN, or Deep CAKE) in \cref{app:deep_kernel_embeddings}, where the kernel family is formed from multiple layers of learned representations before a simpler kernel encodes their similarity for inference.
-Finally, we marry both constructions into the deep linear kernel embedding network (DLKEN, or Deep LAKE) in \cref{app:deep_linear_kernel_embedding_network}, which provides a scalable and more applicable version of the deep kernel embedding network by placing a linear kernel on the last layer of the network.
+We first begin by introducing the linear kernel embedding classifier (Linear KEC) in \cref{app:linear_kernel_embedding_classifier}, where explicit feature maps can be learned while enabling scalability to larger datasets.
+We then construct the deep nonlinear kernel embedding network (Deep Nonlinear KEN) in \cref{app:deep_kernel_embeddings}, where the kernel family is formed from multiple layers of learned representations before a simpler yet potentially nonlinear kernel encodes their similarity for inference.
+Finally, we marry both constructions into the deep linear kernel embedding network (Deep Linear KEN) in \cref{app:deep_linear_kernel_embedding_network}, which provides a scalable and more applicable version of the deep kernel embedding network by placing a linear kernel on the last layer of the network.
 
@@
 		However, this elegant property is also the very reason that prevents kernel-based methods from scaling to larger datasets, as the size of such a matrix grows very quickly by $O(n^{2})$ as the dataset grows.
-Furthermore, many kernel-based methods require the inversion of a regularised gram matrix, which has a time complexity of $O(n^{3})$, and cannot be easily parallelised unlike standard matrix multiplications.
+Many kernel-based methods also require the inversion of a regularised gram matrix, which has a time complexity of $O(n^{3})$, and cannot be easily parallelised like standard matrix multiplications.
 As such, inference on datasets beyond tens of thousands of observations quickly becomes impractical to perform with kernel-based techniques.
 
-		Furthermore, in many situations, simple conventional kernels such as the Gaussian kernel is not able to fully represent the underlying structure of the data for the specific application domain at hand.
-For example, in an image recognition task, a Gaussian kernel over the flattened pixels of an image is unable to capture the local relationships between nearby pixels in the original image.
-In this example, inference would greatly benefit from using convolutional features.
-In general, we would like to be able to compose kernels from any features that can potentially learn to capture structural information within the data.
-
-		These two insights motivate a special case of the kernel embedding classifier, the linear kernel embedding classifier.
-As its name implies, instead of placing a kernel over the input space directly and let it implicitly define the feature space, we simply explicitly define a finite dimensional feature space $\mathbb{R}^{p}$ of dimension $p$ and place a linear kernel over it.
-By explicitly defining a finite dimensional feature space, the matrix to be inverted during both learning and inference in the kernel embedding classifier can be reduced from size $n \times n$ to size $p \times p$ by using a special case of the Woodbury matrix identity.
+		In order to scale to big datasets, instead of placing a kernel over the input space directly and let it implicitly define the feature space, we explicitly define a finite dimensional feature space $\mathcal{Z} \subseteq \mathbb{R}^{p}$ of dimension $p$, where $p < n$, and place a linear kernel over it.
+That is, we specify a family of explicit features maps $\varphi_{\theta} : \mathcal{X} \to \mathcal{Z}$, and place a linear kernel on top of these explicit features,
+
+		\begin{equation}
+			k_{\theta}(x, x') = \varphi_{\theta}(x)^{T} \varphi_{\theta}(x').
+		\end{equation}
+
+		By explicitly defining a finite dimensional feature space, the matrix to be inverted during both learning and inference in the kernel embedding classifier can be reduced from size $n \times n$ to size $p \times p$ by using the Woodbury matrix identity.
+We use this identity to modify \cref{alg:kernel_embedding_classifier_training} to \cref{alg:linear_kernel_embedding_classifier_training} to exploit this computational speed up.
+
+%		\note{Choose each batch to be greater than the dimensionality of the last layer to avoid numerical instability with Cholesky Decomposition as the upper bound is not tight for small $n$ and the gradients may send it off to some unstable region instead}
 
 		However, with a fixed and finite amount of feature basis, the model becomes parametric and its flexibility is compromised.
-We therefore employ the deep learning philosophy, where the flexibility of a model comes from a narrow but deep architecture instead of a wide but shallow architecture such as the one defined by a kernel with implicit infinite dimensional features.
-
-		\begin{equation}
-		k_{\theta}(x, x') = \varphi_{\theta}(x)^{T} \varphi_{\theta}(x')
-		\end{equation}
+In other words, the model is narrow in the number of feature representations, and also shallow in the number of transformations used to define each feature.
+We therefore turn to multi-layered feature compositions, where the flexibility of a model comes from the deep architecture instead of implicit high dimensional features.
 
 		\begin{algorithm}[tb]
-			\caption{Linear Kernel Embedding Classifier Training with Stochastic Gradient Descent}
+			\caption{Linear KEC Hyperparameter Learning with Batch Stochastic Gradient Descent}
 			\label{alg:linear_kernel_embedding_classifier_training}
@@
 				\STATE $W_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Z_{\theta}^{T} Y) \hspace{\fill} \in \mathbb{R}^{p \times m}$
-				\STATE $r(\theta, \lambda) \leftarrow \sqrt{\sum_{c = 1}^{m} \sum_{j = 1}^{p} (W_{\theta, \lambda})_{j, c}^{2}}$
 				\STATE $P_{\theta, \lambda} \leftarrow Z_{\theta} W_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-				\STATE $q(\theta, \lambda) \leftarrow \mathrm{loss}(Y, P_{\theta, \lambda}) + r(\theta, \lambda)$ \hspace{\fill} (For example, use the cross entropy loss or squared loss)
+				\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \alpha(\theta) \sqrt{\sum_{c = 1}^{m} \sum_{j = 1}^{p} (W_{\theta, \lambda})_{j, c}^{2}}$
 				\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
@@
 
-		\note{Choose each batch to be greater than the dimensionality of the last layer to avoid numerical instability with Cholesky Decomposition as the upper bound is not tight for small $n$ and the gradients may send it off to some unstable region instead}
-
 	\subsection{Deep Kernel Embedding Network}
@@
 
-		In this section, we focus on constructing kernels, in which inputs $x, x' \in \mathcal{X}$ is to undergo various stages of feature transformations before being fed into a simple positive definite kernel.
+		In this section, we focus on constructing kernels for which inputs $x, x' \in \mathcal{X}$ is to undergo various stages of feature transformations before such it is passed into a simpler kernel $\kappa$ which captures the similarity between the representations.
 Specifically, we pay particular attention to feature transformations in the form of a perceptron, so that the cumulative stages of feature transformation become the (feed-forward) multi-layer perceptron that is familiar within the neural network literature.
@@
 		Formally, let $\mathcal{F}_{0} := \mathcal{X}$ be the original input space.
-The $j^{\mathrm{th}}$ layer of the network $\varphi^{(j)}_{\theta_{j}} : \mathcal{F}_{j - 1} \to \mathcal{F}_{j}, j = 1, 2, \dots, q$ is to transform features from the previous layer to features in the current layer, where $q$ is the total number of such feature transformation layers, and $\theta_{j} \in \Theta_{j}$ parametrises each of those transformations.
+The $j^{\mathrm{th}}$ layer of the network $\varphi^{(j)}_{\theta_{j}} : \mathcal{F}_{j - 1} \to \mathcal{F}_{j}, j = 1, 2, \dots, L$ is to transform features from the previous layer to features in the current layer, where $L$ is the total number of such feature transformation layers, and $\theta_{j} \in \Theta_{j}$ parametrises each of those transformations.
 
@@
 
-		Our aim is to construct a positive definite kernel $k$ which can learn representations of the inputs at various levels before such these representations are passed into a simpler kernel $\kappa$ which captures the similarity between the representations.
-
-		Let $\kappa_{\theta_{\kappa}} : \mathcal{F}_{p} \times \mathcal{F}_{p} \to \mathbb{R}$ be parametrised by $\theta_{\kappa} \in \Theta_{\kappa}$. We will construct our kernel network $k$ by
-
-		\begin{equation}
-		k_{\theta}(x, x') := \kappa_{\theta_{\kappa}}\Bigg(
-		\varphi^{(p)}_{\theta_{p}}\bigg(\varphi^{(p - 1)}_{\theta_{p - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x)\big)\Big)\bigg),
-		\varphi^{(p)}_{\theta_{p}}\bigg(\varphi^{(p - 1)}_{\theta_{p - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x')\big)\Big)\bigg)
-		\Bigg)
+		Let $\kappa_{\theta_{0}} : \mathcal{F}_{p} \times \mathcal{F}_{p} \to \mathbb{R}$ be parametrised by $\theta_{0} \in \Theta_{0}$. We will construct our kernel network $k$ by
+
+		\begin{equation}
+			k_{\theta}(x, x') := \kappa_{\theta_{0}}\Bigg( \varphi^{(L)}_{\theta_{L}}\bigg(\varphi^{(L - 1)}_{\theta_{L - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x)\big)\Big)\bigg), \varphi^{(L)}_{\theta_{L}}\bigg(\varphi^{(L - 1)}_{\theta_{L - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x')\big)\Big)\bigg) \Bigg)
 		\label{eq:deep_kernel_embedding_network}
@@
 
-		where $\theta = \{\theta_{1}, \theta_{2}, \dots, \theta_{p -1}, \theta_{p}, \theta_{\kappa}\} \in \Theta = \Theta_{1} \otimes \Theta_{2} \otimes \dots \otimes \Theta_{p - 1} \otimes \Theta_{p} \otimes \Theta_{\kappa}$ are the collection of all parameters of each layer and the kernel $\kappa$.
+		where $\theta = (\theta_{1}, \theta_{2}, \dots, \theta_{L -1}, \theta_{L}, \theta_{0}) \in \Theta = \Theta_{1} \otimes \Theta_{2} \otimes \dots \otimes \Theta_{L - 1} \otimes \Theta_{L} \otimes \Theta_{0}$ are the collection of all parameters of each layer and the kernel $\kappa$.
+
+		In order to train the multi-layered features in an end-to-end fashion, we employ \cref{alg:kernel_embedding_classifier_training}.
+With a deep architecture, the feature representations the kernel embedding network can learn are very flexible, and can work very well for structured data by employing suitable network architectures.
+
+		If we choose to employ nonlinear kernels $\kappa$, the model architecture is also wide in that an even higher dimensional feature space is implicitly defined on top of the feature space of the last network layer.
+Despite its supreme flexibility, this again prevents the model from being scalable.
+We therefore turn to the specific case where we employ a linear kernel $\kappa$ on top of the multi-layered features.
 
@@
 
-\newpage
-\section{Full Probabilistic Inference and Mode Reconstruction}
-\label{app:mode_reconstruction}
-
-	Formulated as a conditional embedding learning task in a reproducing kernel Hilbert space, the kernel embedding classifier is able to learn a discriminative model to nonparametrically infer about the distribution of discrete labels $Y$ given an example input $X$.
-In the previous section, we devised a training algorithm for learning the optimal hyperparameters for the conditional embedding corresponding to the classifier.
-Now that the conditional embedding is learned, we can perform full probabilistic inference between all the observed and hidden variables (if any) of the kernel embedding network.
-That is,
-
-	\note{Note: Not completed yet.}
-
-	\subsection{Hidden Representation Reconstruction}
-
-		\note{Note: Observed quantities are done, but hidden quantities needs experimental verification.}
+		The deep linear kernel embedding network is simply a special case at the intersection of the linear kernel embedding classifier and the deep kernel embedding network.
+From the linear KEC perspective, we simply choose $\varphi_{\theta}(x) = \varphi^{(L)}_{\theta_{L}}\big(\varphi^{(L - 1)}_{\theta_{L - 1}}(\dots\varphi^{(2)}_{\theta_{2}}(\varphi^{(1)}_{\theta_{1}}(x)))\big)$.
+From the deep kernel embedding network perspective, we simply choose $\kappa(z, z') = z^{T} z'$ to be a linear kernel.
+
+		Nevertheless, this model architecture is perhaps the most practical and powerful form of the kernel embedding classifier.
+By having a deep architecture, the classifier is still capable of learning flexible representations on structured data, while being able to scale to larger datasets due to the linear kernel at the output layer, provided that the dimensionality of the last layer is relatively small compared to the size of the dataset.
+
+		As a subclass of linear KEC, we can employ \cref{alg:linear_kernel_embedding_classifier_training} to learn the multi-layered features effectively.
+In fact, by not mapping the multi-layered features into a nonlinear kernel, the gradients for each network weight and bias are usually more pronounced, and learning is usually faster in comparison.
+
+	\subsection{Learning Objective Intuitions}
+	\label{app:learning_objective_intuitions}
+
+		The learning objective \eqref{eq:objective} for the kernel embedding classifier is composed of two terms: a training loss (or data fit) term and a model complexity (or regularisation) term.
+In this section we provide some intuition towards the relative effects of each term for two types of kernel models: a radial basis type kernel, producing a nonlinear kernel embedding classifier, and a linear kernel, producing a linear kernel embedding classifier.
+
+		Consider a typical radial basis type kernels such as the Gaussian (squared exponential) or Mat\'{e}rn kernel $k_{\theta}$.
+These types of kernels are usually placed on top of subsets of Euclidean spaces $\mathcal{X} \subseteq \mathbb{R}^{d}$ where $d$ is the dimensionality of an input $x \in \mathcal{X}$.
+Here, the hyperparameters $\theta$ usually includes length scale parameters ($1$ parameter for isotropic kernels, $d$ parameters for anisotropic kernels, or $\frac{d (d - 1)}{2}$ parameters for non-diagonal kernels) and possibly a sensitivity parameter which is simply a multiplicative constant that scales the magnitude of the kernel.
+
+		These types of kernels implicitly map the input space $\mathcal{X}$ to an uncountably infinite dimensional RKHS $\mathcal{H}_{k_{\theta}}$, making the model nonparametric.
+This means that the feature space $\mathcal{H}_{k_{\theta}}$ is already quite flexible for any $\theta \in \Theta$, since for any $\theta \in \Theta$ it has an uncountably infinite amount of feature basis to use for creating linear decision boundaries.
+As such, and it is relatively easy to find linear decision boundaries within such a high dimensional space.
+In this way, experiments show that for most datasets, most initialisations of $\theta$ already produces a very reasonable model of low training loss.
+In fact, there is often a subset of length scales and sensitivity parameters within $\Theta$ in which the training loss is relatively constant.
+
+		In these scenarios, the gradients from the training loss term is usually very small, and the gradient from the learning objective is dominated by the complexity term.
+Intuitively, the learning objective communicating the following message: ``the model is already performing quite well, or at least as best as it can, on the dataset, so let us focus on finding the simplest model that can still produce a similar performance''.
+
+		This is in contrast to the case with linear kernels $k_{\theta}(x, x') = \varphi_{\theta}(x)^{T} \varphi_{\theta}(x')$.
+In this case, the input space $\mathcal{X}$, usually but not necessarily also a subset of the Euclidean space $\mathbb{R}^{d}$, is explicitly mapped to a finite dimensional RKHS $\mathcal{H}_{k_{\theta}} = \mathcal{Z} \subseteq \mathbb{R}^{p}$ through the feature map $\varphi_{\theta} : \mathcal{X} \to \mathcal{Z}$.
+With only finitely many feature basis, the model becomes parametric, and the number of features is fixed at $p$ so that its capacity does not grow with the size of the dataset like a nonparametric model.
+
+		In \cref{app:deep_linear_kernel_embedding_network}, we focused on linear kernel embedding classifiers with deep neural network features, where the flexibility of such a narrow model comes from the deep architecture instead.
+This is in contrast to the case of radial basis type kernels which has a shallow architecture and the flexibility comes from the wide collection of implicit feature basis (uncountably many) which becomes more expressive as we observe more data.
+In this case, for most initialisations of the model parameters $\theta \in \Theta$, the model will not necessarily perform well on the training data.
+As such, the training loss is large and its gradients will be larger in magnitude, in order to drive the model towards a better model fit.
+
+		On the other hand, the complexity term is comparatively smaller.
+Recall that the model complexity is measured in the RKHS $\mathcal{H}_{k_{\theta}}$, which in this case is the space of the last layer $\mathcal{Z} \subseteq \mathbb{R}^{p}$ of the neural network.
+Earlier layers are free to learn very complicated feature representations.
+As long as the learned feature representations in the last layer is simple, the complexity term will be small.
+Since the number of features is fixed, the capacity of the model is limited, and thus the complexity term is usually not as big as the training loss term.
+In this way, the gradients from the learning objective is dominated by the training loss term.
+Intuitively, the learning objective is communicating the following message: ``the model is performing very poorly on the dataset, so let us first focus on learning representations to explain the dataset before we worry about finding the simplest model''.
 
@@
 
-	\subsection{More about the training objective}
-
-		The training objective \eqref{eq:objective} for the kernel embedding classifier is composed of two terms: a training loss (or data fit) term and a model complexity (or regularisation) term.
-In this section we provide some intuition towards the relative effects of each term for two types of kernel models: a radial basis type kernel and a linear kernel.
-
-		Consider a typical radial basis type kernels such as the Gaussian (squared exponential) or Mat\'{e}rn kernel $k_{\theta}$.
-These types of kernels are usually placed on top of subsets of Euclidean spaces $\mathcal{X} \subseteq \mathbb{R}^{d}$ where $d$ is the dimensionality of an input $x \in \mathcal{X}$.
-Here, the hyperparameters $\theta$ usually includes length scale parameters ($1$ parameter for isotropic kernels, $d$ parameters for anisotropic kernels, or $\frac{d (d - 1)}{2}$ parameters for non-diagonal kernels) and possibly a sensitivity parameter which is simply a multiplicative constant that scales the magnitude of the kernel.
-
-		These types of kernels implicitly map the input space $\mathcal{X}$ to an uncountably infinite dimensional RKHS $\mathcal{H}_{k_{\theta}}$, making the model nonparametric.
-This means that the feature space $\mathcal{H}_{k_{\theta}}$ is already quite flexible for any $\theta \in \Theta$, since for any $\theta \in \Theta$ it has an uncountably infinite amount of feature basis to use for creating linear decision boundaries.
-As such, and it is relatively easy to find linear decision boundaries within such a high dimensional space.
-In this way, experiments show that for most datasets, most initialisations of $\theta$ already produces a very reasonable model of low training loss.
-In fact, there is often a subset of length scales and sensitivity parameters within $\Theta$ in which the training loss is relatively constant.
-
-		In these scenarios, the gradients from the training loss term is usually very small, and the gradient from the training objective is dominated by the complexity term.
-Intuitively, the training objective communicating the following message: ``the model is already performing quite well, or at least as best as it can, on the dataset, so let us focus on finding the simplest model that can still produce a similar performance''.
-
-		This is in contrast to the case with linear kernels $k_{\theta}(x, x') = \varphi_{\theta}(x)^{T} \varphi_{\theta}(x')$.
-In this case, the input space $\mathcal{X}$, usually but not necessarily also a subset of the Euclidean space $\mathbb{R}^{d}$, is explicitly mapped to a finite dimensional RKHS $\mathcal{H}_{k_{\theta}} = \mathcal{Z} \subseteq \mathbb{R}^{p}$ through the feature map $\varphi_{\theta} : \mathcal{X} \to \mathcal{Z}$.
-With only finitely many feature basis, the model becomes parametric, and the number of features is fixed at $p$ so that its capacity does not grow with the size of the dataset like a nonparametric model.
-In \cref{app:linear_kernel_embedding_classifier}, we focused on linear kernel embedding classifiers with deep neural network features, where the flexibility of such a narrow model comes from the deep architecture instead.
-This is in contrast to the case of radial basis type kernels which has a shallow architecture and the flexibility comes from the wide collection of feature basis (uncountably many) which becomes more expressive as we observe more data.
-
-		In this case, for most initialisations of the model parameters $\theta \in \Theta$, the model will not necessarily perform well on the training data.
-As such, the training loss is large and its gradients will be larger in magnitude, in order to drive the model towards a better model fit.
-
-		On the other hand, the complexity term is comparatively smaller.
-Recall that the model complexity is measured in the RKHS $\mathcal{H}_{k_{\theta}}$, which in this case is the space of the last layer $\mathcal{Z} \subseteq \mathbb{R}^{p}$ of the neural network.
-Earlier layers are free to learn very complicated feature extractions.
-As long as the learned feature representations in the last layer is simple, the complexity term will be small.
-Since the number of features is fixed, the capacity of the model is limited, and thus the complexity term is usually not as big as the training loss term.
-In this way, the gradients from the training objective is dominated by the training loss term.
-Intuitively, the training objective is communicating the following message: ``the model is performing very poorly on the dataset, so let us first focus on learning representations to explain the dataset before we worry about finding the simplest model''.
-
 \end{document}

### 2017-05-16 cake.tex
Add updated cake

--- 2017-05-10 kernel_embedding_classifier.tex
@@
 % if you need to pass options to natbib, use, e.g.:
-\PassOptionsToPackage{square, authoryear, comma, sort&compress}{natbib}
-% before loading nips_2016
+% \PassOptionsToPackage{numbers, compress}{natbib}
+% before loading nips_2017
 %
 % to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{nips_2016}
-
-\usepackage[final]{nips_2016}
+% \usepackage[nonatbib]{nips_2017}
+
+\usepackage{nips_2017}
 
 % to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[final]{nips_2016}
-
-\usepackage[utf8x]{inputenc} % allow utf-8 input
+% \usepackage[final]{nips_2017}
+
+\usepackage[utf8]{inputenc} % allow utf-8 input
 \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
@@
 \usepackage[dvipsnames]{xcolor}
-
-\newcommand{\argmax}{\operatornamewithlimits{argmax}}
-\newcommand{\note}[1]{{\color{orange} #1}}
-\newcommand{\edit}[1]{{\color{forestgreen} #1}}
-
 \newtheorem{theorem}{Theorem}[section]
@@
 \newtheorem{claim}[theorem]{Claim}
-
 \usepackage{multirow}
-
 \usepackage{algorithm}
@@
 
-\title{CAKE: Classification avec Kernel Embeddings \\ with Rademacher Complexity based Risk Bounds}
+\usepackage{footnote}
+\makesavenoteenv{tabular}
+
+\newcommand{\argmax}{\operatornamewithlimits{argmax}}
+\newcommand{\note}[1]{{\color{orange} #1}}
+\newcommand{\edit}[1]{{\color{forestgreen} #1}}
+
+\title{CAKE: Classification \textit{avec} Kernel Embeddings \\ using Rademacher Complexity Bounds}
 
@@
 % author name.
-
-%\author{
-%  Kelvin Y.S. Hsu, Richard Nock, Fabio T. Ramos \\
-%  University of Sydney, Australia\\
-%  DATA61, CSIRO\\
-%  \texttt{\{Kelvin.Hsu, Richard.Nock, Fabio.Ramos\}@\{sydney.edu.au, data61.csiro.au\}} \\
-%  %% examples of more authors
-%  %% \And
-%  %% Coauthor \\
-%  %% Affiliation \\
-%  %% Address \\
-%  %% \texttt{email} \\
-%  %% \AND
-%  %% Coauthor \\
-%  %% Affiliation \\
-%  %% Address \\
-%  %% \texttt{email} \\
-%  %% \And
-%  %% Coauthor \\
-%  %% Affiliation \\
-%  %% Address \\
-%  %% \texttt{email} \\
-%  %% \And
-%  %% Coauthor \\
-%  %% Affiliation \\
-%  %% Address \\
-%  %% \texttt{email} \\
-%}
 
@@
 \begin{document}
+% \nipsfinalcopy is no longer used
 
@@
 \begin{abstract}
-	We propose learning-theoretic bounds for learning the hyperparameters of kernel embeddings in the probabilistic multiclass classification context.
+	We propose learning-theoretic bounds for hyperparameter learning of conditional kernel embeddings in the probabilistic multiclass classification context.
 Kernel embeddings are nonparametric methods to represent probability distributions directly through observed data in a reproducing kernel Hilbert space (RKHS).
-However, the problem of hyperparameter learning for kernel embeddings remains challenging, often relying on heuristics and domain specific knowledge.
-We begin by developing the kernel embedding classifier (KEC), and prove the stochastic convergence of its probabilistic predictions.
-We then prove that expected classification error can be bounded with high probability using Rademacher complexity based risk bounds.
-We use this bound to propose a scalable kernel learning algorithm for probabilistic multiclass classification.
-Classification performance is benchmarked on standard UCI datasets.
+This property forms the core of modern kernel methods, yet the problem of hyperparameter learning for kernel embeddings remains challenging, often relying on heuristics and domain expertise.
+We begin by developing the kernel embedding classifier (KEC), and prove the stochastic convergence for its probabilistic inferece.
+We then prove that its expected classification error can be bounded with high probability using Rademacher complexity based risk bounds.
+We use this bound to propose a scalable kernel learning algorithm for conditional embeddings with batch stochastic gradient descent.
 We further apply our proposed kernel learning algorithm to learn feature representations of a deep convolutional network, with improved accuracy as compared to the original network, demonstrating the generality of this approach.
@@
 
-- We address the need for a principled way of obtaining probabilistic outputs from a multiclass classifier.
-- It works in domains with not a lot of data, and we later provide a way for which it can scale
-- We address hyperparameter learning for a kernel embedding model
-- We do not rely on priors
-
-Data dependent risk bounds
-
 \section{Introduction}
@@
 	Kernel embeddings are a principled way to represent probability distributions in a nonparametric setting.
-
-	learning theoretic (be specific and mention PAC)
-	(complexity penalty terms that are not data dependent cannot be universally effective) \citep{kearns1997experimental}
+By transforming probability distributions into mean embeddings within a reproducing kernel Hilbert space (RKHS), distributions can be represented directly from data without assuming a parametric structure.
+Consequently, probabilistic inference can be carried out entirely within the RKHS in a nonparametric form, where difficult marginalisation integrals become simple linear algebra operations.
+This very general and powerful technique is core to modern kernel methods, including support vector machines \citep{scholkopf2002learning}, kernel two-sample testing \citep{gretton2007kernel}, kernel Bayesian inference  \citep{fukumizu2013kernel}, nonparametric density estimation \citep{song2008tailoring, kanagawa2014recovering}, domain-invariant component analysis \citep{muandet2013domain}, dimensionality reduction \citep{fukumizu2004dimensionality}, feature discovery via hypothesis testing \citep{jitkrittum2016interpretable}, and filtering \citep{kanagawa2016filtering}.
+The problem of estimating the kernel mean in a reproducing kernel Hilbert space (RKHS) is thus central to kernel methods.
+
+	Positive definite symmetric kernels $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ are the soul of kernel methods, where they provide a coherent sense of similarity between two elements of the same space through implicitly defining higher dimensional features.
+However, they are most often selected by design, in which kernel based learning algorithms focus only on learning the weightings on the implicit features, and not the features itself.
+That is, the kernel itself is not learned.
+Multiple kernel learning has focused on learning constructions of richer kernels from simpler ones \citep{gonen2011multiple, zien2007multiclass}, although the simpler kernels themselves are also preselected by design.
+By placing a Gaussian process prior over the function class, Gaussian process models \citep{rasmussen2006gaussian} achieve tractable marginal likelihood based learning algorithms that is able to learn the model hyperparameters, which includes the kernel parameters.
+However, this approach requires various approximations for non-Gaussian likelihoods, and does not generalise well to non-Gaussian priors.
+Within the kernel embedding framework itself, hyperparameters has been similarly difficult to tune, and its learning is usually only restricted to heuristical approaches such as cross validation.
+Recent work has introduced Gaussian process priors on mean embeddings to achieve Bayesian hyperparameter learning \citep{flaxman2016bayesian}.
+However, the learning is separate from the application domain, and the approach has yet to generalise to conditional embeddings.
+
+	In this paper, we take a learning theoretic approach to learn the hyperparameters of a conditional kernel embedding in a supervised manner.
+We first begin by proposing the kernel embedding classifier (KEC), a principled framework for inferring multiclass probabilistic outputs using conditional embeddings, and provide a proof for its stochastic convergence.
+We then employ Rademacher complexity as a data dependent model complexity measure, and prove that the expected classification risk can be bounded with high probability by the empirical risk and the trace norm of the conditional embedding.
+We use this bound to propose a learning objective that learns the balance between performance accuracy and model complexity in a way that does not rely on priors.
+Finally, we note that the learning algorithm proposed generalises to an one class setting, enabling unsupervised kernel learning on unlabeled data.
+
+	Our work also has implications in the supervised learning context.
+The kernel embedding classifier is natural in the probabilistic multiclass domain.
+On the other hand, similarly kernel based classifiers such as support vector classifiers (SVC) \citep{m2001introduction} and Gaussian process classifiers (GPC) \citep{rasmussen2006gaussian} are natural only in the binary classification domain, and require extensions to handle the multiclass scenario, such as using one-against-all, one-against-one, or decision trees on multiple independent binary classifiers \citep{aly2005survey, hsu2002comparison}.
+Moreover, SVCs are not probabilistic by nature, while GPCs are analytically intractable and must resort to posterior approximations.
+In this paper, we verify the performance and versatility of the kernel embedding classifier on standard UCI datasets.
+With its generality and flexibility, KECs can also be constructed to learn explicit feature representations, and is inherently compatible with deep neural network type architectures.
+To this end, we demonstrate that KECs can perform end-to-end learning on a convolutional neural network, while also outperforming the original network.
 
@@
 
-	Under the assumption that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$, \cite{song2009hilbert} proved that the conditional expectation of a function $g \in \mathcal{H}_{l}$ can be expressed as an inner product,  % Theorem 4
+	Under the assumption that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$, \citet[Theorem 4]{song2009hilbert} proved that the conditional expectation of a function $g \in \mathcal{H}_{l}$ can be expressed as an inner product,
 	\begin{equation}
@@
 	In this section, we formulate a kernel embedding based probabilistic classifier by casting it into the conditional embedding framework.
-
-	In the multiclass classification context, the output label space is finite and discrete, taking values only in $\mathcal{Y} = \mathbb{N}_{m} := \{1, \dots, m\}$.
+In the multiclass setting, the output label space is finite and discrete, taking values only in $\mathcal{Y} = \mathbb{N}_{m} := \{1, \dots, m\}$.
 Naturally, we first choose the Kronecker delta kernel $\delta : \mathbb{N}_{m} \times \mathbb{N}_{m} \to \{0, 1\}$ as the output kernel $l$, where labels that are the same has unit similarity and labels that are different have no similarity.
@@
 
-	We proceed to prove that the empirical decision probabilities \eqref{eq:empirical_decision_probability} converges to the true decision probabilities with more data.
+	We proceed to prove that the empirical decision probabilities \eqref{eq:empirical_decision_probability} converges to the true decision probabilities.
+In fact, the inference distribution \eqref{eq:empirical_decision_probability_vector} is equivalent to a conditional embedding.
 We direct the reader to the supplementary material for proof.
@@
 	\end{theorem}
-	Finally, to perform classification at a query point $x^{\star} \in \mathcal{X}$, we simply take the class with the highest empirical decision probability, $\hat{y}^{\star} = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x^{\star})$.
-
-	While the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ will converge to the true decision probability function  $p_{c} : \mathcal{X} \to [0, 1]$ in the limit, for finite $n$ and a fixed regulariser $\lambda > 0$, the stochasticity in the empirical estimates implies that these probabilities may not necessarily sum up to one, nor are they strictly restricted to the range $[0, 1]$.
-However, they will usually be very close to the true predicted probabilities.
-Moreover, such stochasticity also does not principally affect the classification prediction, since we simply take the argmax of the empirical decision probability vector \eqref{eq:empirical_decision_probability_vector}.
-
-	If strict, valid probabilities are required for interpretation, visualisation, or other purposes, the probabilities can be clipped at zero then normalised to one, a procedure we refer to as \textit{clip-normalisation},
+	While decision probability estimates \eqref{eq:empirical_decision_probability} do not necessarily form a normalised distribution for finite $n$, \cref{thm:probability_convergence_copy} guarantees that they approach one with increasing sample sizes.
+If normalised distributions are required for interpretation, distribution estimates \eqref{eq:empirical_decision_probability} can be clip-normalised,
 	\begin{equation}
 		\tilde{p}_{c}(x) := \frac{\max\{\hat{p}_{c}(x), 0\}}{\sum_{j = 1}^{m} \max\{\hat{p}_{j}(x), 0\}}.
-	\label{eq:probability_clip_normalise}
-	\end{equation}
-	Notice that for classification prediction, the argmax solution over the classes of the empirical decision probabilities \eqref{eq:empirical_decision_probability} and its clip-normalised version \eqref{eq:probability_clip_normalise} remain the same.
-Furthermore, since $\hat{p}_{c}(x)$ converges to true probabilities $p_{c}(x)$ according to \cref{thm:probability_convergence_copy}, the effect of clip-normalisation reduces as $n$ increases such that $\tilde{p}_{c}(x)$ becomes very close to $\hat{p}_{c}(x)$ and $p_{c}(x)$.
-
-\section{Learning with Rademacher Complexity based Risk Bounds}
+	\label{eq:empirical_decision_probability_clip_normalised}
+	\end{equation}
+	Of course, classification $\hat{y}(x) = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x) = \argmax_{c \in \mathbb{N}_{m}} \tilde{p}_{c}(x)$ remains invariant.
+\Cref{thm:probability_convergence_copy} also implies the reducing effect of clip-normalisation as with increasing sample sizes, where $\tilde{p}_{c}(x)$ approaches to both $\hat{p}_{c}(x)$ and $p_{c}(x)$.
+
+\section{Hyperparameter Learning with Rademacher Complexity Bounds}
 \label{sec:hyperparameter_learning}
 
-	The formulation of the kernel embedding classifier requires the specification of a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ over the input space $\mathcal{X}$, or rather, a class of kernels $\{k_{\theta}\}_{\theta \in \Theta}$ parametrised by the kernel parameters $\theta \in \Theta$.
-It also requires the specification of a regularisation parameter $\lambda$ for the conditional embedding as in \eqref{eq:empirical_conditional_embedding}.
-These are hyperparameters of the kernel embedding classifier which needs to be learned in order to produce a reasonable classifier model.
-While decision probability estimates \eqref{eq:empirical_decision_probability} converge to the true decision probabilities \eqref{eq:decision_probability} for any choice of positive definite kernels $k_{\theta}$ (\cref{thm:probability_convergence_copy}), for finite $n$ we would like to find the kernel from the kernel family which produces the most appropriately discriminative model to perform classification tasks.
-
-	In the kernel embedding literature, hyperparameters has been notoriously difficult to tune, and its learning is usually only restricted to heuristics or methods such as cross validation which requires pre-selecting the number of folds and the split of the folds.
-In this paper, we take a learning theoretic approach to learn the hyperparameters of the KEC, inspired by the original training procedure of support vector classifiers (SVC) as described by \cite[p.
-185]{m2001introduction}.
-Assuming a perfectly separable case, the training of a SVC begins by introducing a \textit{prediction constraint} on the training set, where the classifier is constrained to correctly classify all the available training examples.
-The strategy is to minimise the \textit{complexity} of the SVC model while ensuring perfect classification over training examples.
-The model complexity in the SVC context is measured by the VC dimension $h$ of the binary classifier, which has an upper bound $h \leq \lVert \bvec{w} \rVert^{2} R^{2} + 1$.
-Since it is difficult to compute the VC dimension explicitly, we instead minimise its upper bound, which is equivalent to and leads to the common interpretation of maximising the margin $\frac{2}{\lVert \bvec{w} \rVert}$.
-
-	Similarly, we propose to train our kernel embedding classifier with the same high level formulation: minimise the model complexity without compromising classification performance on the training data.
-Instead of employing the VC dimension as the complexity measure of our model, which is defined mainly for binary classifiers, we consider the \textit{Rademacher complexity} of the kernel embedding classifier.
-Given a function class $\mathcal{F}$ and a loss function $\mathcal{L}(y, \bvec{f}(x))$, the expected test loss $\mathbb{E}[\mathcal{L}(Y, \bvec{f}(X))]$ is bounded by the expected training loss $\frac{1}{n}\sum_{i = 1}^{n} \mathcal{L}(y_{i}, \bvec{f}(x_{i}))$ plus the Rademacher complexity and a constant with high probability, similar to the case with the VC dimension \citep{bartlett2002rademacher}.
-As such, if we can minimise the model complexity in the sense of the Rademacher complexity while maintaining a low training loss, we can optimise generalisation ability in the sense of low expected test loss.
-
-			Further more, since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:specific_expected_loss_bound_for_kec_applied} is true with probability $1 - \beta$ if we replace all the random variables $X_{i}, Y_{i}$ with the training observations $x_{i}, y_{i}$.
-
-			Therefore, in order to minimise the expected test loss, we propose the following training objective for the kernel embedding classifier,
-
-	For a predictor parametrised as $f(x; W) = W^{T} x$, \cite{yu2014large} showed that the global Rademacher complexity of such a predictor is upper-bounded in terms of its trace norm, $\sqrt{\mathrm{trace}(W^{T} W)}$.
-This was originally discussed in the context of multi-label classification, where $W \in \mathbb{R}^{d \times L}$ and $f$ produces a binary vector of length $L$ indicating the multiple labels that describes the input $x \in \mathbb{R}^{d}$.
-In the context of the kernel embedding classifier, the empirical decision probabilities \eqref{eq:empirical_decision_probability_vector} also has the same analytical form, where the input $x$ is replaced by some feature vector $\phi(x)$.
-By using the canonical feature map $\phi(x) = k(x, \cdot)$ and the reproducing property $\langle \phi(x), \phi(x') \rangle = k(x, x')$ in the RKHS, we can write \eqref{eq:empirical_decision_probability_vector} as $\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \Phi^{T} \phi(x) = W^{T} \phi(x)$, where instead of mapping input examples in $\mathbb{R}^{d}$ to output multi-label vector $\mathbb{R}^{L}$, $W^{T}$ maps features in the RKHS $\mathcal{H}_{k}$ to the a vector of multiclass probabilities in $\mathbb{R}^{m}$.
-Using the reproducing property $K = \Phi^{T} \Phi$ again, the squared trace norm for such a predictor is then $\mathrm{trace}(W^{T} W) = \mathrm{trace}(\bvec{Y}^{T} (K + n \lambda I)^{-1} K (K + n \lambda I)^{-1} \bvec{Y})$.
-We therefore propose to use this trace norm as an upper bound measure of the kernel embedding classifier model complexity,
-	\begin{equation}
-		r(\theta, \lambda) := \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} K_{\theta} (K_{\theta} + n \lambda I)^{-1} \bvec{Y}\bigg)},
-	\label{eq:trace_norm}
-	\end{equation}
-	where we use the subscript $\theta$ to make explicit the dependence on the kernel parameters. Therefore, with high probability and up to a constant term, an upper bound of the test loss is
-	\begin{equation}
-		q(\theta, \lambda) := \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}(y_{i}, \hat{\bvec{p}}_{\theta, \lambda}(x_{i})) + r(\theta, \lambda).
-	\label{eq:objective}
-	\end{equation}
-	We employ gradient based methods to train the kernel embedding classifier with this training loss and complexity bound objective.
-The gradients of the learning objective with respect to the hyperparameters is obtained using automatic differentiation.
+	Kernel embedding classifiers are equivalent to a conditional embedding with a discrete target space $\mathcal{Y}$.
+We now turn to address hyperparameter learning for the KEC, and explicitly denote the kernel parameters $\theta \in \Theta$ and regularisation parameter $\lambda \in \Lambda = \mathbb{R}_{+}$ that define the KEC model.
+Hyperparameter learning for conditional embeddings is particularly difficult compared to joint embeddings, since the kernel $\{k_{\theta} : \theta \in \Theta\}$ is to be learned jointly with a regularisation parameter $\lambda$.
+While the conditional embedding map $\hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the operator $\mathcal{U}$ that minimises the regularised least squares loss $\frac{1}{n} \sum_{i = 1}^{n} \| \psi(y_{i}) - \mathcal{U} \phi(x_{i}) \|_{\mathcal{H}_{l}}^{2} + \lambda \| \mathcal{U} \|_{HS}$ in the RKHS \citep{song2013kernel}, minimising this loss directly over $\theta \in \Theta, \lambda \in \Lambda$ for $\mathcal{U} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X}$ would trivially result in an overfitted model with $\lambda \rightarrow 0$.
+This implies that the notion of model complexity is especially important, yet the standard solutions employ either cross validation or nested loops separating $\theta$ and $\lambda$, both of which are heuristics and subject to design choices.
+
+	To this end, we propose to use a learning theoretic approach to quantify a balance between model complexity and performance accuracy.
+The Rademacher complexity \citep{bartlett2002rademacher} measures the expressiveness of a function class $F$ by its ability to shatter, or fit, noise.
+They are data-dependent measures, and are thus particularly well suited to learning tasks where generalisation ability is vital, since complexity penalties that are not data dependent cannot be universally effective \citep{kearns1997experimental}.
+
+	We begin by defining a loss function as a measure for the generalisation error.
+For decision functions of the form $\bvec{f} : \mathcal{X} \to \mathcal{A} = \mathbb{R}^{m}$ where entries of $f$ are interpreted as probabilities, we employ the cross entropy loss,
+	\begin{equation}
+		\mathcal{L}_{\epsilon}(y, \bvec{f}(x)) := - \log{ [\bvec{y}^{T} \bvec{f}(x)]_{\epsilon}^{1} } = - \log{ [f_{y}(x)]_{\epsilon}^{1} },
+	\label{eq:cross_entropy_loss_copy}
+	\end{equation}
+	to express classification risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$.
+Under this loss, we prove that the expected risk for the kernel embedding classifier $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a Rademacher complexity bound $r(\theta, \lambda)$ with high probability.
+We refer the reader to the supplementary material for detailed proof.
+
+	\begin{theorem}[Expected Risk Bound for KEC Hyperparameter Learning]
+		\label{thm:expected_risk_bound_hyperparameter_learning_copy}
+
+		For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$ used to define $\bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector}, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $\theta \in \Theta$, $\lambda \in \Lambda$, and $\epsilon \in (0, e^{-1})$ satisfies
+		\begin{equation}
+			\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e r(\theta, \lambda) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
+		\label{eq:expected_risk_bound_hyperparameter_learning_copy}
+		\end{equation}
+		where $r(\theta, \lambda) := \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} K_{\theta} (K_{\theta} + n \lambda I)^{-1} \bvec{Y}\bigg) \sup_{x \in \mathcal{X}} k_{\theta}(x, x)}$.
+	\end{theorem}
 
@@
 			\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
-			\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial r}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial r}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
+			\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial q}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial q}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
 			\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
@@
 
-	\subsection{Batch Stochastic Gradient Descent}
-	\label{sec:stochastic_gradient_descent}
-
-		With standard gradient descent, the time complexity of each training iteration is dominated by the Cholesky decomposition of the regularised gram matrix $K_{\theta} + n \lambda I$ of size $n \times n$, which has a time complexity of $O(n^{3})$.
-In order to scale the hyperparameter training of kernel embedding classifiers to large datasets, we propose to optimise the objective \eqref{eq:objective} with stochastic gradient descent.
-
-		We begin by selecting a mini-batch size $n_{b} << n$ that is much smaller than $n$.
-At each training iteration, we sample a mini-batch of size $n_{b}$ from the full dataset.
-The objective \eqref{eq:objective} and its gradients with respect to the hyperparameters are then computed only for the mini-batch.
-This stochastic gradient is then used to make hyperparameter updates in that training iteration.
-This continues until the magnitude of the stochastic gradients fall below a certain range.
-This training algorithm is presented in \cref{alg:kernel_embedding_classifier_training}.
-This implementation also generalises the gradient descent approach, where $n_{b} = n$ so that $\mathcal{I} = \mathbb{N}_{n}$ and the full dataset is used to compute the gradients.
-
-		\note{Justify with the bound after discussing with Richard}
+	In order for the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} to be non-trivial, we focus on bounded kernels in the sense that $\alpha^{2}(\theta) := \sup_{x \in \mathcal{X}} k_{\theta}(x, x) < \infty$.
+For example, Gaussian kernels $k_{\theta}(x, x') = \sigma_{f}^{2} \exp{( - \frac{1}{2}(x - x') \Sigma^{-1} (x - x') )}$ and similar stationary kernels such as the Mat\'{e}rn family with sensitivity and length scales $\theta = (\sigma_{f}, \Sigma)$ have $\alpha(\theta) = \sigma_{f}$.
+For non-stationary kernels such as the linear or polynomial kernels, the domain $\mathcal{X}$ is assumed to be compact and thus can be rescaled so that $\alpha(\theta) = 1$.
+Since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} is true with probability $1 - \beta$ when the random variables $X_{i}, Y_{i}$ are realised as the training observations $x_{i}, y_{i}$.
+We therefore employ this upper bound as the hyperparameter learning objective,
+	\begin{equation}
+		q(\theta, \lambda) := \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(y_{i}, \bvec{f}_{\theta, \lambda}(x_{i})) + 4 e r(\theta, \lambda).
+	\label{eq:learning_objective}
+	\end{equation}
+	We employ gradient based optimisers such as Gradient descent or Adam \citep{kingma2014adam}.
+Since \cref{thm:expected_risk_bound_hyperparameter_learning_copy} holds for any $n \in \mathbb{N}_{+}$ and any set of data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ from $\mathbb{P}_{X Y}$, with the trade-off of relaxing bound tightness through $\sqrt{8 \log{(2 / \beta)} / n}$, the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} also holds with high probability for a subset of the training data.
+This enables scalable hyperparameter learning through batch stochastic gradient updates, where each gradient update stochastically improves a different upper bound of the generalisation risk.
+Because this bound holds with high probability over \textit{iid} samples, through randomly selecting a batch of training examples that comes from the same distribution, the resulting stochastic gradient will improve a strict upper bound with the same high probability.
+We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:kernel_embedding_classifier_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size.
+
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width=0.32\linewidth]{figures/iris_overfitted_model.eps}
+		\includegraphics[width=0.32\linewidth]{figures/iris_balanced_model.eps}
+		\includegraphics[width=0.32\linewidth]{figures/iris_underfitted_model.eps}
+		\includegraphics[width=\linewidth]{figures/iris_rademacher_complexity_bound.eps}
+		\includegraphics[width=0.48\linewidth]{figures/iris_cross_entropy_loss.eps}
+		\includegraphics[width=0.48\linewidth]{figures/iris_accuracy.eps}
+		\caption{Rademacher complexity balanced learning of hyperparameters for an isotropic Gaussian kernel embedding classifier, using the first two attributes of the iris dataset.}
+		\label{fig:iris}
+	\end{figure}
+
+	\paragraph{Toy Example}
+
+		The first two of four total attributes of the iris dataset \citep{fisher1936use} is known to have class labels that are not only not linearly separable, but also non-separable by any means, in that the same example $x \in \mathbb{R}^{2}$ may be assigned different output labels $y \in \mathbb{N}_{3} := \{1, 2, 3\}$ as they were only separable with the two remaining attributes.
+In these difficult scenarios, the notion of model complexity is extremely important, and the success of a learning algorithm greatly depends on how it balances training performance and model complexity to avoid both underfitting and overfitting.
+
+		\Cref{fig:iris} demonstrates \cref{alg:kernel_embedding_classifier_training} with full gradient updates ($n_{b} = n$) to learn the hyperparameters of the conditional embedding of the iris dataset.
+The kernel used is isotropic Gaussian with diagonal length scales $\Sigma = \ell^{2} I_{2}$ and sensitivity $\alpha = \sigma_{f}$, so the model hyperparameters are $\theta = (\alpha, \ell)$ and the conditional embedding regularisation $\lambda$.
+We evaluate the performance of the learning algorithm on a withheld test set using 20\% of the available 150 data samples.
+Attributes are scaled into the unit range $[0, 1]$ and decision probability maps are plotted for the region $[-0.5, 1.05]^{2}$, where the red, green, and blue colour channel represents the decision probability for classes $c = 1, 2, 3$.
+We begin from two initial scenarios, one originally overfitting ($\alpha_{o} = 0.01$, $\ell_{o} = 0.035$, $\lambda_{o} = 10^{-6}$) and another underfitting ($\alpha_{u} = 1$, $\ell_{u} = 1$, $\lambda_{u} = 1$) the training data.
+Initially, both models performs sub-optimally with a test accuracy of 56.67\%.
+We see that the Rademacher complexity bound (RCB) $r(\theta, \lambda)$ appropriately measures the amount of overfitting with $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = 4.33$ and $r(\alpha_{u}, \ell_{u}), \lambda_{u}) = 0.31$.
+We then learn model hyperparameters with \cref{alg:kernel_embedding_classifier_training} for 500 iterations from both initialisations at rate $\eta = 0.01$, where both models converges to a balanced model with appropriate complexity bounds $r((\alpha_{o}, \ell_{o}) = (0.01, 0.24), \lambda_{o} = 8.62 \times 10^{-7}) = 2.23 \approx 2.14 = r((\alpha_{u}, \ell_{u}) = (5.1, 0.24), \lambda_{u} = 0.20)$ and an improved test accuracy of 73.33\%.
+In particular, the initially overfitted model learns a simpler model at the expense of lower training performance, emphasising the benefits of complexity based regularisation, without which the learning would only maximise training performance at the cost of further overfitting.
+Meanwhile, the initially underfitted model learns to trade some complexity away to improve the unflattering performance on the training set.
+In both scenarios, our learning algorithm improved performance on the test set.
+
+		Furthermore, while \cref{fig:iris} shows that the model has converged for all performance measures, including complexity bounds, decision probabilities, and accuracy or loss on both training and test sets, the learned hyperparameters $((\alpha, \ell), \lambda)$ themselves differ for different initialisations.
+For a Gaussian or similarly stationary kernel, we have that $r((\sigma_{f}, \ell), \lambda) = r((1, \ell), \lambda \sigma^{-2}_{f})$, so the bound $r$ is only interested in the quantities $\lambda \sigma^{-2}_{f}$ and $\ell$.
+Indeed, in our example above, $\lambda_{o} \alpha_{o}^{-2} = 0.0086 \approx 0.0075 = \lambda_{u} \alpha_{u}^{-2}$ and $\ell_{o} = 0.24 = \ell_{u}$ after learning.
+This illustrates that there can be non-trivial subsets of the kernel family $k_{\theta}$, $\theta \in \Theta$, and regularisations $\lambda \in \Lambda$ with the same complexity bound.
+The same can be true for other performance measures.
+Our learning algorithm does not distinguish amongst them, and any family member with an optimal bound $q(\theta, \lambda)$ is a solution.
+
+		% $ \sigma^{2}_{f} \bvec{Y}^{T} (K_{(\sigma_{f}, \ell)} + n \lambda I)^{-1} K_{(\sigma_{f}, \ell)} (K_{(\sigma_{f}, \ell)} + n \lambda I)^{-1} \bvec{Y} = \bvec{Y}^{T} (K_{(1, \ell)} + n \frac{\lambda}{\sigma^{2}_{f}} I)^{-1} K_{(1, \ell)} (K_{(1, \ell)} + n \frac{\lambda}{\sigma^{2}_{f}} I)^{-1} \bvec{Y}$.
+%	RCB from overfitted after 500 iterations: 2.2299
+%	RCB from underfitted after 500 iterations: 2.1424
+%	
+%	HYPERS from overfitted $\sigma_{f} = 0.01$, $\sigma = 0.035$, $\lambda = 10^{-6}$ to $\sigma_{f} = 0.01$, $\sigma = 0.24$, $\lambda = 8.6186 \times 10^{-7}$.
+%	
+%	$0.195949 / (5.1^2) = 0.007533602460592081 \approx 0.00861677 = 8.61677e-07 / (0.01^2)$
+%	
+%	HYPERS from underfitted $\sigma_{f} = 1$, $\sigma = 1$, $\lambda = 1$ to $\sigma_{f} = 5.1$, $\sigma = 0.24$, $\lambda = 0.1960$
+
+%	
+%	NEED TO SHOW VISUALISATIONS OF IRIS HERE AND DISCUSS TWO INITIALISATIONS: ONE OVERFITTING AND ONE UNDERFITTING, AND SHOW THAT OUR TRAINING ALGORITHM FINDS A BALANCE FROM BOTH INITIAL SETTINGS.
+%	
+%	ALSO SHOW REVERSE EMBEDDING RESULTS
+
+	\paragraph{Neural Network Kernels} DISCUSSION NOT DONE
+
+\section{Related Work}
+\label{sec:related_work}
+
+	For a linear class of predictors parametrised as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularisation to bound the Rademacher complexity, achieving tight generalisation bounds in the context of multi-label learning.
+The KEC predictor \eqref{eq:empirical_decision_probability_vector} has the same linear form in the feature space, $\bvec{f}_{\theta, \lambda}(x) = \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \Phi_{\theta}^{T} \phi_{\theta}(x) = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$, where instead of learning the operator $W^{T}$ directory, we learn hyperparameters $\theta \in \Theta, \lambda \in \Lambda$ for the empirical conditional embedding map $\mathcal{U}^{(\theta, \lambda)}_{Y | X}$ to learn the features $\phi_{\theta}(x)$.
+\cite{xu2016local} extends the trace norm regularisation approach by considering the local Rademacher complexity on a subset of the predictor class, where they instead minimise the tail sum of the predictor singular values.
+In the proof of \cref{thm:expected_risk_bound_hyperparameter_learning_copy}, $\theta \in \Theta$ and $\lambda \in \Lambda$ define subsets of $\Theta$ and $\Lambda$ where the Rademacher complexity is considered over.
+By minimising $q(\theta, \lambda)$, we shrink the subset being considered, achieving localised Rademacher complexity based feature learning without selecting parameters that define the tail sum.
+Local Rademacher complexity has also been employed for multiple kernel learning \citep{kloft2011local, cortes2013learning} to learn convex combinations of simpler kernels for a support vector machine.
+We extend its application to the probabilistic multiclass case, and use Rademacher complexity based risk bounds to learn the hyperparameters of a conditional kernel embedding.
 
 \section{Experiments}
-
-	We will also open-source the code on GitHub.
-All the core algorithms presented in this paper will be available and implemented in TensorFlow \citep{abadi2016tensorflow}, while having the same API as \texttt{scikit-learn} models so that it is straightforward to use.
+\label{sec:experiments}
+
+	We demonstrate the average performance of learning anisotropic Gaussian kernels and fully connected neural network kernels under the kernel embedding classification framework on standard UCI datasets, summarised in \cref{tab:stationary_experiments}.
+The former has a shallow but wide model architecture, while the latter has a deeper but narrower model architecture.
+
+	The Gaussian kernel is learned through both the original gradient update (GKEC) and the scalable batch stochastic gradient update (GKEC-SGD) using a tenth ($n_{b} \approx \frac{n}{10}$) of the training set each time, with sensitivity and length scales initialised to $1$.
+For neural network kernels, we randomly select two simple fully connected architectures with 16-32-8 (NNKEC-1) and 96-32 (NNKEC-2) hidden units respectively, and learn the corresponding kernel without dropout under ReLU activation.
+Weight parameters are initialised from a truncated normal distribution with standard deviation $0.1$, while biases are initialised to $0.1$, and are to be trained with full gradient updates.
+For all experiments, regularisation parameter $\lambda$ is initialised to $1$ and is learned jointly with the kernel.
+Classifiers are trained with the Adam optimiser \citep{kingma2014adam} in TensorFlow \citep{abadi2016tensorflow} with a learning rate of $\eta = 0.1$ and $\epsilon = 10^{-15}$ for learning objective $q(\theta, \lambda)$.
+Training is ran for 1000 or 10000 iterations when using full or batch stochastic gradient updates respectively, regardless of training convergence.
+All datasets are scaled so that all dimensions are in the unit range.
+Each classifier is trained on 9 out of 10 folds and tested on the remaining fold.
+The folds are shuffled over all 10 combinations to obtain the average test accuracy.
+We compare our results to other approaches using neural networks \citep[a; c]{kaya2016banknote, freire2009short}, probabilistic binary trees \citep[b]{horton1996probabilistic}, decision trees \citep[d]{zhou2004size}, and regularised discriminant analysis \citep[e]{aeberhard1992comparison}.
+These numbers are only illustrative, however, in that different authors may have used different data pre-processing, folds, optimiser, learning rate, architecture (for neural nets), and training time.
+
+	STILL HAS TO ADD CONVOLUTIONAL KERNEL MNIST STUFF WHICH ACHIEVED 99.5\% TEST ACCURACY WITH SGD
+
+	ALSO SHOW REVERSE EMBEDDING RESULTS TO OBTAIN THE CLASS MODES
+
+	DISCUSSION NOT DONE 
+%	\begin{table}[t]
+%		\begin{center}
+%			\begin{tabular}{ l | c | c }
+%				\hline
+%				\multicolumn{3}{ c }{Classification Accuracy on UCI Datasets} \\
+%				\hline
+%				\hline				
+%				Dataset \hspace{\fill} $(n, d, m)$ & Method & Test Accuracy \\
+%				\hline
+%				\hline
+%				\texttt{banknote} & Gaussian KEC & $99.93 \pm 0.22$ \\
+%				(1372, 4, 2) & Gaussian KEC (SGD 124) & $98.83 \pm 0.88$ \\
+%				& Neural KEC (16, 32, 8) & $99.49 \pm 1.03$ \\
+%				& Neural KEC (96, 32) & $99.42 \pm 0.91$ \\
+%				\hline
+%				\texttt{ecoli} & Gaussian KEC & $87.50 \pm 4.36$ \\
+%				(336, 7, 8) & Gaussian KEC (SGD 30) & $84.50 \pm 5.02$ \\
+%				& Neural KEC (16, 32, 8) & $87.49 \pm 3.24$ \\
+%				& Neural KEC (96, 32) & $86.32 \pm 5.98$ \\
+%				\hline
+%				\texttt{robot} & Gaussian KEC & \\
+%				(5456, 24, 4) & Gaussian KEC (SGD 491) & $95.45 \pm 0.86$ \\
+%				& Neural KEC (16, 32, 8) & $82.31 \pm 7.11$ \\	
+%%				\texttt{robot} \hspace{\fill} (5456, 24, 4) & Neural KEC (96, 32) & $92.25 \pm 1.39$ \\	
+%				& Neural KEC (96, 32) & $94.50 \pm 0.75$ \\
+%				\hline
+%				\texttt{segment} & Gaussian KEC & \\
+%				(2310, 19, 7) & Gaussian KEC (SGD 208) & $96.10 \pm 1.46$ \\
+%				& Neural KEC (16, 32, 8) & $94.59 \pm 1.62$ \\
+%				& Neural KEC (96, 32) & $96.71 \pm 1.06$ \\
+%				\hline
+%				\texttt{wine} & Gaussian KEC & $97.22 \pm 3.73$ \\
+%				(178, 13, 3) & Gaussian KEC (SGD 16) & $93.27 \pm 6.04$ \\
+%				& Neural KEC (16, 32, 8) & $96.11 \pm 5.00$\\
+%				& Neural KEC (96, 32) & $97.22 \pm 5.12$ \\
+%				\hline
+%				\texttt{yeast} & Gaussian KEC & $52.49 \pm 2.06$ \\
+%				(1484, 8, 10) & Gaussian KEC (SGD 134) & $60.30 \pm 4.39$ \\
+%				& Neural KEC (16, 32, 8) & $55.80 \pm 4.96$ \\
+%				& Neural KEC (96, 32) & $59.57 \pm 3.98 $ \\
+%				\hline
+%				\hline
+%			\end{tabular}
+%		\end{center}
+%		\caption{Classification accuracy of two kernel embedding classification architectures on standard UCI Datasets.
+Numbers after ``SGD'' indicates the batch size used.
+Numbers after ``Neural KEC'' indicates the size of the hidden layers, starting from the first.}
+%		\label{tab:stationary_experiments_old}
+%	\end{table}
 
 	\begin{table}[t]
-		\begin{center}
-			\begin{tabular}{ l l || c || c c || c }
-				\hline
-				\multicolumn{6}{ c }{Classification Accuracy on UCI Datasets} \\
-				\hline
-				\hline
-%				& & & \multicolumn{2}{ c }{Accuracy} & \\
-%				\hline				
-				Dataset & & Method & Train & Test & Test (Literature) \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 1372$ & CE + RC & 99.59 & 100 & Artificial Neural Network: 99.78 \\
-				\texttt{banknote} & $d = 4$ & CE & 99.59 & 100 & \citep{kaya2016banknote} \\
-				& $m = 2$ & RC & 99.59 & 100 &  \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 336$ & CE + RC & 92.05 & 91.18 & Probabilistic Binary Tree: 81.1 \\
-				\texttt{ecoli} & $d = 7$ & CE & 94.04 & 85.29 & \citep{horton1996probabilistic} \\
-				& $m = 8$ & RC & 91.05 & 88.24 &  \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 150$ & CE + RC & 97.78 & 100 & SVM: 94.67 \\
-				\texttt{iris} & $d = 4$ & CE & 97.04 & 100 & \citep{koggalage2004reducing}\\
-				& $m = 3$ & RC & 97.78 & 100 & ANN: 83.33 \citep{swain2012approach} \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 7797$ & CE + RC &   &   & \\
-				\texttt{isolet} & $d = 617$ & CE &   &   & \\
-				& $m = 26$ & RC &   &   &  \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 2310$ & CE + RC & 99.37 & 97.40 & Decision Trees \& Neural Nets: \\
-				\texttt{segment} & $d = 19$ & CE & 97.84 & 96.97 &  99.14 - 99.98 \\
-				& $m = 7$ & RC & 97.35 & 96.10 & \citep{lim2000comparison} \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 178$ & CE + RC & 100 & 100 & RDA: 100, QDA: 99.4, \\
-				\texttt{wine} & $d = 13$ & CE & 100 & 100 & LDA: 98.9, 1NN: 96.1 \\
-				& $m = 3$ & RC & 100 & 100 & \citep{aeberhard1992comparison} \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 6497$ & CE + RC & & & \\
-				\texttt{wine-quality} & $d = 12$ & CE & & & \\
-				& $m = 2$ & RC & & &  \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 1484$ & CE + RC & 67.04 & 57.72 & Probabilistic Binary Tree: 55.0 \\
-				\texttt{yeast} & $d = 8$ & CE & 68.24 & 56.38 & \citep{horton1996probabilistic} \\
-				& $m = 10$ & RC & 62.25 & 56.38 &  \\
-				\hline
-				\hline
+		\caption{Classification Accuracy (\%) of Gaussian and Neural Network KEC on UCI datasets}
+		\label{tab:stationary_experiments}
+		\centering
+		\begin{tabular}{lccccc}			
+			Dataset \hspace{\fill} $(n, d, m)$ & GKEC & GKEC-SGD & NNKEC-1 & NNKEC-2 & Others \\
+			\midrule
+			\texttt{banknote} \hspace{\fill} (1372, 4, 2) & $99.9 \pm 0.2$ & $98.8 \pm 0.9$ & $99.5 \pm 1.0$ & $99.4 \pm 0.9$ & 99.78\textsuperscript{a} \\
+			\texttt{ecoli} \hspace{\fill} (336, 7, 8) & $87.5 \pm 4.4$ & $84.5 \pm 5.0$ & $87.5 \pm 3.2$ & $86.3 \pm 6.0$ & 81.1\textsuperscript{b} \\
+			\texttt{robot} \hspace{\fill} (5456, 24, 4) & $97.8$ & $95.5 \pm 0.9$ & $82.3 \pm 7.1$ & $94.5 \pm 0.8$ & 97.59\textsuperscript{c} \\
+			\texttt{segment} \hspace{\fill} (2310, 19, 7) & $98.4 \pm 0.8$ & $96.1 \pm 1.5$ & $94.6 \pm 1.6$ & $96.7 \pm 1.1$ & 96.83\textsuperscript{d} \\
+			\texttt{waveform} \hspace{\fill} (5000, 21, 3) & $87.2$ & $83.3 \pm 1.6$ & $86.8 \pm 1.6$ & $86.7 \pm 1.6$ & 90.98\textsuperscript{d} \\
+			\texttt{wine} \hspace{\fill} (178, 13, 3) & $97.2 \pm 3.7$ & $93.3 \pm 6.0$ & $96.1 \pm 5.0$ & $97.2 \pm 5.1$ & 100\textsuperscript{e} \\
+			\texttt{yeast} \hspace{\fill} (1484, 8, 10) & $52.5 \pm 2.1$ & $60.3 \pm 4.4$ & $55.8 \pm 5.0$ & $59.6 \pm 4.0$ & 55.0\textsuperscript{b} \\
 		\end{tabular}
-		\end{center}
-		\caption{Classification Accuracy of the Kernel Embedding Classifier on standard UCI Datasets.}
-		\label{tab:experiments}
 	\end{table}
@@
 
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width=0.25\linewidth]{figures/spiral_all_final.eps}
+		\caption{.}
+		\label{fig:spiral}
+	\end{figure}
+
 \section{Conclusion}
 
-	\note{Summarise main contribution.
-Specifically, the guaranteed convergence of the kernel embedding classifier in both decision probability and information entropy, the Rademacher complexity based hyperparameter training scheme, the stochastic gradient descent version thereof which allows scalable training, the application of such flexible training methods to train deep convolutional features, and the fully probabilistic inference on both inputs and outputs.
-Focus the point of the paper as that this is a new and elegant formulation of a fully probabilistic classifier (not just in the outputs, but even in the inputs) with complexity bound based training.
-Being formulated as type of kernel conditional embedding learning, all the nice properties from the Hilbert space embedding world can be imported into this framework.
-In practice, even though the mathematical theory of kernel embeddings can be tricky, the resulting algorithms are very elegant and simple, so that implementation is quick and easy.
-Being very general, there should be a lot of things we can do in the future to improve it or build upon it.}
-
-	\textbf{Future Work}: \note{(Not that polished)}
-
-	\begin{itemize}
-		\item \textbf{Hyperparameter Training through Local Rademacher Complexity.} In parallel with the work of \cite{xu2016local}, we can derive an upper bound for the \textit{local Rademacher complexity} of our kernel embedding classifier.
-In contrast to the global Rademacher complexity, the local Rademacher complexity of a model produces a sharper generalization error bound and a faster convergence rate.
-Specifically, for our classifier, it is upper bounded by the tail sum of the sorted eigenvalues of $B^{T} (K + n \lambda I)^{-1} K (K + n \lambda I)^{-1} B$.
-The complication is that there is an extra design choice to be made: from which eigenvalue should the tail sum start.
-Preliminary experiments that we have done so far shows that this choice affects the training a lot, and thus more work is needed to theorise how this choice should be done, and if it really improves classification performance consistently at the end of the day.
-
-		\item \textbf{Multiple Kernel Learning and Shallow-Deep Kernels.} With kernel methods, newer and more flexible kernel classes can always be formed by convex combinations of simpler positive definite kernels.
-We can explore kernel and hyperparameter learning for these architectures under the kernel embedding classification framework that we developed in this paper.
-
-		\textbf{Multiple Kernel Learning}.
-In summary, multiple kernel learning is traditionally interested in forming a new kernel $k(x, x') := \sum_{i = 1}^{p} \alpha_{i} k_{i}(x, x')$ from simpler kernels $k_{i}(x, x')$ by finding the optimal coefficient vector $\{\alpha_{i}\}_{i = 1}^{p}$ with respect to its learning task under convexity constraints.
-While this convex optimisation problem is quite tractable, each kernel component $k_{i}$ stays fixed, so that it is up to the practitioners to choose and tune each kernel component a-priori.
-With the kernel embedding classification framework, hyperparameter training is very general, and makes no restrictions on where the trainable parameters must appear (with the trade-off being that the optimisation may become non-convex).
-As such, we can construct newer kernels through $k(x, x'; \theta) := \sum_{i = 1}^{p} \alpha_{i} k_{i}(x, x'; \theta_{i})$ and generalise the multiple kernel learning problem to one that finds the optimal coefficient vector $\{\alpha_{i}\}_{i = 1}^{p}$ and kernel parameters $\{\theta_{i}\}_{i = 1}^{p}$.
-Of course, the regularisation parameter $\lambda$ is jointly learned at the same time.
-
-		\textbf{Shallow-Deep Kernels}.
-Similarly, another way of convexly combining kernels is through a simple tensor multiplication, $k([x, z]^{T}, [x', z']^{T}; \theta_{\mathcal{X}}, \theta_{\mathcal{Z}}) := k_{\mathcal{X}}(x, x'; \theta_{\mathcal{X}}) k_{\mathcal{Z}}(z, z'; \theta_{\mathcal{Z}})$.
-In this scenario, we can let $x \in \mathcal{X}$ to be the original unaltered example inputs, while $z = f(x; w) \in \mathcal{Z}$ be the output of the last hidden layer of a neural network, where we use $w$ to collectively denote all the weight and bias parameters of the neural network.
-In this way, $k_{\mathcal{X}}$ is a shallow kernel allowing a direct connection from input to output, while $k_{\mathcal{Z}}$ is a deep kernel performing multiple layers of feature extraction from the input before it is connected to the output.
-Again, because hyperparameter training is very general in the kernel embedding classification framework, it should be possible to jointly learn the kernel hyperparameters $\theta_{\mathcal{X}}, \theta_{\mathcal{Z}}$, the neural network weights and biases $w$, and the regularisation parameter $\lambda$.
-
-		\item \textbf{Connection to other kernel models.} It should not be too surprising if we can find many connections or even equivalences to other kernel techniques.
-For example, if we look at the form of our decision probability estimator, it is also the same as the mean prediction of a Gaussian process regression, except we replace the real-valued targets in the regression case with the one-hot encoded class targets for our classification task.
-Of course, the main difference thereafter is how we train the two models.
-We turned to complexity based training partly because, unlike a Gaussian process, it is very difficult to find the marginal likelihood for a kernel embedding, and this has worked out well.
-However, future work can look into the direction of actually finding a way to compute or approximate the marginal likelihood for the kernel embedding classifier, making the link between Gaussian processes and kernel embeddings even stronger.
-
-		Another simpler connection may be the k-nearest-neighbour classifier.
-For any stationary and radially symmetric kernel like the Gaussian and Matern kernels, shorter length scales usually produces a nearest-neighbour effect on the inference of kernel embedding classifiers.
-Of course, this is suboptimal, and the complexity based training developed in this paper would know better to not learn such a length scale.
-However, this link would illustrate the purpose and effectiveness of a complexity based training scheme for kernel methods.
-
-		\item \textbf{Sampling and Generative Models.} While the kernel embedding classifier is trained as a discriminative model, at its core it is simply just a condition embedding of $\mathbb{P}_{Y | X}$.
-As such, we can do full probabilistic inference entirely in reproducing kernel Hilbert spaces and obtain the Hilbert space embeddings of $\mathbb{P}_{X | Y}$, similar to what we have touched upon in \cref{sec:mode_reconstruction}, or even simply of the marginals $\mathbb{P}_{X}$ and $\mathbb{P}_{Y}$.
-If we can recover these distributions as densities ($\mathbb{P}_{Y}$ would correspond to a probability mass function over a finite and discrete space $\mathbb{N}_{m}$ which is identical to the mean embedding already, and so this step would be trivial for $\mathbb{P}_{Y}$), then we would be able to model our data in a fully generative manner.
-In fact, in \cref{sec:mode_reconstruction} we have have already done so indirectly through reversing the embedding.
-Of course, this would require us to solve the pre-image problem of kernel embeddings, for which no general methodology exists yet besides a few heuristics with various assumptions.
-Nevertheless, assuming we can recover the densities well enough, we can then generate samples from those distributions.
-Alternatively, if we can instead sample from those distributions \textit{without} finding the pre-image, but by directly using the mean embeddings instead, that would make the kernel embedding classifier very useful as a generative modelling tool.
-
-		\item \textbf{Target Label Kernel.} In this paper, we proposed to place a Kronecker delta kernel $l = \delta$ over the label space $\mathcal{Y} = \mathbb{N}_{m}$ as it is the simplest kernel over a discrete and finite domain.
-However, it is possible to place other kernels over the label space.
-A simple kernel is to have a `generalised Kronecker delta kernel' that has unit similarity when labels are the same, but a small, positive yet non-zero similarity when labels are different.
-If we set these cross similarity to be the same across all non-identical pairs of labels, then it is straight forward to show that the inference algorithm we developed in this paper stays the same.
-However, if we allow them to vary amongst each other as kernel parameters (between the range $(0, 1)$, in order to stay positive definite), then we suspect that these cross similarity coefficients would act as correlation factors between classes.
-The training algorithm we developed here does not prevent the target label kernel to have its own hyperparameters.
-As such, we should be able to learn the correlation effects between the classes effectively using the same training scheme.
-We suspect that this would make the empirical decision probabilities converge to a valid probability distribution faster.
-However, we also suspect that the training may become even more non-convex and optimisation to become more difficult.
-
-		These factors may even give rise to new interpretable insights in terms of how different classes may be more related to each other.
-For example, in an image recognition task of animals, it may learn that, the class `horse' and 'pony' are much more similar than `horse' and `elephant' from the input features, and start to use the output correlations to focus on inferring about them as a group instead.
-		\end{itemize}
+	\note{Summarise main contribution.}
+
+	Contrary to parametric models, nonlinear kernels produce nonparametric classifiers, and thus its model capacity grows with increasing data.
+Within a large enough family of kernels $k_{\theta}$, the kernel embedding classifier always has the capacity to shatter the training data and produce zero training error.
+This is precisely the quality Rademacher complexity measures.
+Given that it has such capabilities, we instead focus on learning the simplest model, so that it can generalise well to unseen data.
+By jointly minimising the training risk and the Rademacher complexity bound, we are effectively removing unnecessarily complex models while maintaining good generalisation performance.
+Without the Rademacher complexity bound $r(\theta, \lambda)$, the classifier can easily overfit by adapting its model capacity to the training data closely.
+In short, while parametric models have limited capacity and thus trying to learn to perform well on a training set to its best ability is a good indicator to test performance, nonparametric models has infinite capacity and need to learn not to exploit this capacity on training data and instead learn the simplest pattern it can to be able to infer about new test instances.
 
@@
 
-	The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref{eq:probability_clip_normalise}, at the query point $x \in \mathcal{X}$,
+	The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref{eq:empirical_decision_probability_clip_normalised}, at the query point $x \in \mathcal{X}$,
 	\begin{equation}
@@
 
+		Therefore, $\hat{\bvec{p}}(x) \equiv \hat{\mu}_{Y | X = x}$.
+
 		\begin{proof}
@@
 		where we decompose $\bvec{k}_{\theta}(x) = \Phi_{\theta}^{T} \phi_{\theta}(x)$ by the reproducing property.
+By \cref{thm:empirical_probability_is_embedding}, $\bvec{f}_{\theta, \lambda}(x) = \hat{\bvec{p}}_{\theta, \lambda}(x) = \hat{\mu}^{(\theta, \lambda)}_{Y | X = x} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$.
+Therefore, we have that $\hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \equiv W_{\theta, \lambda}^{T}$.
+Throughout this paper, inner products are defined in the Hilbert-Schmidt sense, which induces the Hilbert-Schmidt norm $\| \cdot \|_{HS}$ and generalises the Frobenius inner product with induced norm $\| \cdot \|_{\mathrm{tr}}$ for finite dimensional operators.
+Nevertheless, while they refer to the same quantity, we will use the standard notations $ \| \hat{\mathcal{U}}^{\theta, \lambda}_{Y | X} \|_{HS}$ as per the literature in Hilbert space embeddings and $\| W_{\theta, \lambda} \|_{\mathrm{tr}}$ as per the literature for linear classifiers.
 
@@
 
+			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
 Suppose that $k_{\theta}$ is a family of positive definite stationary kernels.
 That is, $k_{\theta} (x, x') = \tilde{k}_{\theta}( \| x - x' \| )$ for some real-valued function $\tilde{k} : [0, \infty) \to [0, \infty)$.
-Further suppose there exists $\tilde{\theta} \in \Theta$ such that that $k_{\theta}(0, 0) \leq k_{\tilde{\theta}}(0, 0)$ for all $\theta \in \Theta$.
-For any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of kernel embedding classifiers $F_{n}(\Theta, \Lambda)$ defined over $\theta \in \Theta, \lambda \in \Lambda$ is bounded by
-
-			\begin{equation}
-				\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) \leq 2 \rho \sqrt{k_{\tilde{\theta}}(0, 0)}.
+Select $\tilde{\theta} \in \Theta$ and define $\Theta(\tilde{\theta})$ such that $k_{\theta}(0, 0) \leq k_{\tilde{\theta}}(0, 0)$ for all $\theta \in \Theta(\tilde{\theta})$.
+For any $\tilde{\theta} \in \Theta$ and set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the resulting class of kernel embedding classifiers $F_{n}(\Theta(\tilde{\theta}), \Lambda)$ defined over $\theta \in \Theta(\tilde{\theta}), \lambda \in \Lambda$ is bounded by
+
+			\begin{equation}
+				\mathcal{R}_{n}(F_{n}(\Theta(\tilde{\theta}), \Lambda)) \leq 2 \rho \sqrt{k_{\tilde{\theta}}(0, 0)}.
 			\end{equation}
@@
 		\end{corollary}
+
+		\Cref{thm:rademacher_complexity_stationary_kernels_bound} motivates the choice $\alpha^{2}(\tilde{\theta}) = k_{\tilde{\theta}}(0, 0) = \sigma_{f}^{2}$ for stationary radial basis type kernels such as the Gaussian or Mat\'{e}rn kernels, where $\sigma_{f}$ is the sensitivity \citep{rasmussen2006gaussian} of the stationary kernel, which we employ in \cref{alg:kernel_embedding_classifier_training} when the kernel is stationary.
+
+%		Another class of kernels that is both expressive and scalable are those composed from feed forward neural networks. 
+%		
+%		\begin{corollary}[Rademacher Complexity Bound for Neural Network Kernels]
+%			\label{thm:rademacher_complexity_neural_kernels_bound}
+%			
+%			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
+Denote $\theta = \{W_{j}, b_{j}\}_{j = 1}^{l}$ for the kernel parameters of the neural network kernel $k_{\theta}(x, x') := \varphi_{\theta}(x)^{T} \varphi_{\theta}(x')$ defined from the $l$-multilayered neural network $\varphi_{\theta}(x) := \varphi^{\theta}_{l}(\varphi^{\theta}_{l - 1}(\dots \varphi^{\theta}_{1}(x)))$.
+Let $\varphi^{\theta}_{j}(z) = \varphi^{\theta}_{j}( z ; W_{j}, b_{j}) = \sigma(W_{j} z + b_{j})$ be the $j^{\mathrm{th}}$ multi-valued perceptron layer with an element wise rectified linear unit (ReLU) activation $\sigma(\cdot) = \max \{ \cdot, 0 \}$ and appropriately sized weights $W_{j}$, biases $b_{j}$, and input $z$ from the previous hidden layer.
+Without loss of generality, suppose that $x \in \mathcal{X} = [-1, 1]^{d}$.
+Select $\tilde{\theta} \in \Theta$ and define $\Theta(\tilde{\theta})$ such that $\| W_{j} \|_{\mathrm{tr}} \leq \| \tilde{W}_{j} \|_{\mathrm{tr}}$ and $\| b_{j} \| \leq \| \tilde{b}_{j} \|$ , $j \in \mathbb{N}_{l}$, for all $\theta = \{W_{j}, b_{j}\}_{j = 1}^{l} \in \Theta(\tilde{\theta})$.
+For any $\tilde{\theta} = \{\tilde{W}_{j}, \tilde{b}_{j}\}_{j = 1}^{l} \in \Theta$ and set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the resulting class of the kernel embedding classifiers $F_{n}(\Theta(\tilde{\theta}), \Lambda)$ defined over $\theta \in \Theta(\tilde{\theta}), \lambda \in \Lambda$ is bounded by
+%			
+%			\begin{equation}
+%				\mathcal{R}_{n}(F_{n}(\Theta(\tilde{\theta}), \Lambda)) \leq 2 \rho D^{\tilde{\theta}}_{l}(D^{\tilde{\theta}}_{l - 1}( \dots D^{\tilde{\theta}}_{1}(\sqrt{d}))),
+%			\end{equation}
+%			
+%			where $D^{\tilde{\theta}}_{j}(a) := a \| \tilde{W}_{j} \|_{\mathrm{tr}} + \| \tilde{b}_{j} \|$, .
+%			
+%			\begin{proof}
+%				Let $z^{\theta}_{j}(x) := \varphi^{\theta}_{j}(\varphi^{\theta}_{j - 1}(\dots \varphi^{\theta}_{1}(x)))$ be the $j^{\mathrm{th}}$ hidden layer so that $z^{\theta}_{j}(x) = \varphi^{\theta}_{j}(z^{\theta}_{j - 1}(x)) = \sigma(W_{j} z^{\theta}_{j - 1}(x) + b_{j})$ with $z^{\theta}_{0}(x) = x$ for all $j \in \mathbb{N}_{l}$.
+At the last layer, we have $\varphi_{\theta}(x) = z_{l}(x)$.
+For any layer $j \in \mathbb{N}_{l}$,
+%			
+%				\begin{equation}
+%					\begin{aligned}
+%						\| z^{\theta}_{j}(x) \| &= \| \sigma(W_{j} z^{\theta}_{j - 1}(x) + b_{j}) \| \\
+%						&\leq \| W_{j} z^{\theta}_{j - 1}(x) + b_{j} \| \\
+%						&\leq \| W_{j} z^{\theta}_{j - 1}(x) \| + \| b_{j} \| \\
+%						&\leq \| W_{j} \|_{\mathrm{tr}} \| z^{\theta}_{j - 1}(x) \| + \| b_{j} \| \\
+%						&=: D^{\theta}_{j}(\| z^{\theta}_{j - 1}(x) \|). \\
+%					\end{aligned}
+%				\end{equation}
+%				
+%				This recursive relationship can be rolled out explicitly to bound the kernel,
+%
+%				\begin{equation}
+%					\begin{aligned}
+%						\sqrt{k_{\theta}(x, x)} &= \| \varphi_{\theta}(x) \| \\
+%						&= \| z^{\theta}_{l}(x) \| \\
+%						&\leq D^{\theta}_{j}(\| z^{\theta}_{j - 1}(x) \|) \\
+%						&\leq D^{\theta}_{l}(D^{\theta}_{l - 1}( \dots D^{\theta}_{1}( \| x \| ))) \\
+%						&\leq D^{\theta}_{l}(D^{\theta}_{l - 1}( \dots D^{\theta}_{1}( \sqrt{d} ))).
+%					\end{aligned}
+%				\end{equation}
+%
+%				Since $\| W_{j} \|_{\mathrm{tr}} \leq \| \tilde{W}_{j} \|_{\mathrm{tr}}$ and $\| b_{j} \| \leq \| \tilde{b}_{j} \|$ , $j \in \mathbb{N}_{l}$, for all $\theta = \{W_{j}, b_{j}\}_{j = 1}^{l} \in \Theta(\tilde{\theta})$, we have $D^{\theta}_{j}(a) := a \| W_{j} \|_{\mathrm{tr}} + \| b_{j} \| \leq a \| \tilde{W}_{j} \|_{\mathrm{tr}} + \| \tilde{b}_{j} \| =: D^{\tilde{\theta}}_{j}(a)$ for $a \geq 0$.
+Hence, $\sqrt{k_{\theta}(x, x)} \leq D^{\tilde{\theta}}_{l}(D^{\tilde{\theta}}_{l - 1}( \dots D^{\tilde{\theta}}_{1}(\sqrt{d})))$ for all $\theta \in \Theta(\tilde{\theta})$ and $x \in \mathcal{X} = [-1, 1]^{d}$, and we choose $\alpha = D^{\tilde{\theta}}_{l}(D^{\tilde{\theta}}_{l - 1}( \dots D^{\tilde{\theta}}_{1}(\sqrt{d})))$ in \cref{thm:rademacher_complexity_bound}.
+%				
+%			\end{proof}
+%		\end{corollary}
 
@@
 
-		We will refer to \eqref{eq:normalised_cross_entropy_loss} as the normalised cross entropy loss \footnote{Of course, the above normalisation only ensures that the loss function attains a maximum of one, but can still be negative if $\hat{p}_{y}(x)$ higher than $1$.
-We can enforce this requirement by clipping the loss function at zero through $\max\{\cdot, 0\}$.
-However, for brevity, we will avoid explicitly writing this clipping operation, as it does not principally affect our subsequent analysis.
-It should nevertheless be understood that all losses discussed in this section are clipped from below at zero or, equivalently, the probability estimates $\hat{p}_{y}(x)$ are clipped from above at one.}.
-We then further define the centred normalised cross entropy loss,
+		We will refer to \eqref{eq:normalised_cross_entropy_loss} as the normalised cross entropy loss. We then further define the centred normalised cross entropy loss,
 
@@
 In contrast, the three kernel embedding classifier variants to be introduced in this section form other combinations of model architecture in both depth and width.
+Of course, this characterisation of architecture is not mutually exclusive.
+For example, a polynomial kernel can be seen as a nonlinear kernel where higher order polynomial features are implicitly defined, or as a linear kernel on explicit polynomial features.
 We summarise those architectures in \cref{tab:kernel_embedding_classifier_variants}.
@@
 				\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
-				\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial r}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial r}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
+				\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial q}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial q}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
 				\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
@@
 
-		The learning objective \eqref{eq:objective} for the kernel embedding classifier is composed of two terms: a training loss (or data fit) term and a model complexity (or regularisation) term.
+		The learning objective \eqref{eq:learning_objective} for the kernel embedding classifier is composed of two terms: a training loss (or data fit) term and a model complexity (or regularisation) term.
 In this section we provide some intuition towards the relative effects of each term for two types of kernel models: a radial basis type kernel, producing a nonlinear kernel embedding classifier, and a linear kernel, producing a linear kernel embedding classifier.

### 2017-05-16 cake.tex
Update cake

@@
 This property forms the core of modern kernel methods, yet the problem of hyperparameter learning for kernel embeddings remains challenging, often relying on heuristics and domain expertise.
-We begin by developing the kernel embedding classifier (KEC), and prove the stochastic convergence for its probabilistic inferece.
+We begin by developing the kernel embedding classifier (KEC), and prove its stochastic convergence for probabilistic inference.
 We then prove that its expected classification error can be bounded with high probability using Rademacher complexity based risk bounds.
-We use this bound to propose a scalable kernel learning algorithm for conditional embeddings with batch stochastic gradient descent.
-We further apply our proposed kernel learning algorithm to learn feature representations of a deep convolutional network, with improved accuracy as compared to the original network, demonstrating the generality of this approach.
+We use this bound to propose a scalable hyperparameter learning algorithm for conditional embeddings with batch stochastic gradient descent.
+We apply our learning algorithm to standard UCI datasets, as well as to learn feature representations of a convolutional neural network with improved accuracy, demonstrating the generality of this approach.
 \end{abstract}
@@
 	where $K := \{k(x_{i}, x_{j})\}_{i = 1, j = 1}^{n, n}$, $\Phi := \begin{bmatrix} \phi(x_{1}) & \dots & \phi(x_{n}) \end{bmatrix}$, $\Psi := \begin{bmatrix} \psi(y_{1}) & \dots & \psi(y_{n}) \end{bmatrix}$, $\phi(x) := k(x, \cdot)$, $\psi(y) := l(y, \cdot)$, and $\lambda$ is the regularisation parameter for the conditional operator \citep{song2013kernel}.
-We then define the empirical conditional embedding by $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$, which stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \cite[Theorem 6]{song2009hilbert}.
+The empirical conditional embedding defined by $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$ then stochastically converges to the conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \cite[Theorem 6]{song2009hilbert}.
 This allows us to approximate the conditional expectation \eqref{eq:conditional_expectation} with $\langle \hat{\mu}_{Y | X = x}, g \rangle$ instead,
@@
 	\end{equation}
-	where $\bvec{g} := \{g(y_{i})\}_{i = 1}^{n}$ and $\bvec{k}(x) := \{k(x_{i}, x\}_{i = 1}^{n}$, knowing that it would converge to the true expectation as $n$ increases for sufficiently small $\lambda$.
+	where $\bvec{g} := \{g(y_{i})\}_{i = 1}^{n}$ and $\bvec{k}(x) := \{k(x_{i}, x\}_{i = 1}^{n}$.
 
@@
 	Kernel embedding classifiers are equivalent to a conditional embedding with a discrete target space $\mathcal{Y}$.
-We now turn to address hyperparameter learning for the KEC, and explicitly denote the kernel parameters $\theta \in \Theta$ and regularisation parameter $\lambda \in \Lambda = \mathbb{R}_{+}$ that define the KEC model.
-Hyperparameter learning for conditional embeddings is particularly difficult compared to joint embeddings, since the kernel $\{k_{\theta} : \theta \in \Theta\}$ is to be learned jointly with a regularisation parameter $\lambda$.
+Hyperparameter learning for conditional embeddings is particularly difficult compared to joint embeddings, since the kernel $\{k_{\theta} : \theta \in \Theta\}$ is to be learned jointly with a regularisation parameter $\lambda \in \Lambda = \mathbb{R}_{+}$.
 While the conditional embedding map $\hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the operator $\mathcal{U}$ that minimises the regularised least squares loss $\frac{1}{n} \sum_{i = 1}^{n} \| \psi(y_{i}) - \mathcal{U} \phi(x_{i}) \|_{\mathcal{H}_{l}}^{2} + \lambda \| \mathcal{U} \|_{HS}$ in the RKHS \citep{song2013kernel}, minimising this loss directly over $\theta \in \Theta, \lambda \in \Lambda$ for $\mathcal{U} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X}$ would trivially result in an overfitted model with $\lambda \rightarrow 0$.
@@
 
-	To this end, we propose to use a learning theoretic approach to quantify a balance between model complexity and performance accuracy.
+	To this end, we propose to use a learning theoretic approach to balance model complexity and data fit.
 The Rademacher complexity \citep{bartlett2002rademacher} measures the expressiveness of a function class $F$ by its ability to shatter, or fit, noise.
@@
 
-	We begin by defining a loss function as a measure for the generalisation error.
-For decision functions of the form $\bvec{f} : \mathcal{X} \to \mathcal{A} = \mathbb{R}^{m}$ where entries of $f$ are interpreted as probabilities, we employ the cross entropy loss,
+	We begin by defining a loss function as a measure for performance.
+For decision functions of the form $\bvec{f} : \mathcal{X} \to \mathcal{A} = \mathbb{R}^{m}$ whose entries are probability estimates, we employ the cross entropy loss,
 	\begin{equation}
@@
 	\end{equation}
-	to express classification risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$.
+	to express classification risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$.
 Under this loss, we prove that the expected risk for the kernel embedding classifier $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a Rademacher complexity bound $r(\theta, \lambda)$ with high probability.
-We refer the reader to the supplementary material for detailed proof.
+%We refer the reader to the supplementary material for detailed proof.
 
@@
 	In order for the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} to be non-trivial, we focus on bounded kernels in the sense that $\alpha^{2}(\theta) := \sup_{x \in \mathcal{X}} k_{\theta}(x, x) < \infty$.
-For example, Gaussian kernels $k_{\theta}(x, x') = \sigma_{f}^{2} \exp{( - \frac{1}{2}(x - x') \Sigma^{-1} (x - x') )}$ and similar stationary kernels such as the Mat\'{e}rn family with sensitivity and length scales $\theta = (\sigma_{f}, \Sigma)$ have $\alpha(\theta) = \sigma_{f}$.
-For non-stationary kernels such as the linear or polynomial kernels, the domain $\mathcal{X}$ is assumed to be compact and thus can be rescaled so that $\alpha(\theta) = 1$.
+Gaussian kernels $k_{\theta}(x, x') = \sigma_{f}^{2} \exp{( - \frac{1}{2}(x - x') \Sigma^{-1} (x - x') )}$ and similar stationary kernels such as the Mat\'{e}rn family with sensitivity and length scales $\theta = (\sigma_{f}, \Sigma)$, for example, have $\alpha(\theta) = \sigma_{f}$.
 Since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} is true with probability $1 - \beta$ when the random variables $X_{i}, Y_{i}$ are realised as the training observations $x_{i}, y_{i}$.
-We therefore employ this upper bound as the hyperparameter learning objective,
+We therefore employ this upper bound as the learning objective,
 	\begin{equation}
@@
 
-		\Cref{fig:iris} demonstrates \cref{alg:kernel_embedding_classifier_training} with full gradient updates ($n_{b} = n$) to learn the hyperparameters of the conditional embedding of the iris dataset.
+		\Cref{fig:iris} demonstrates \cref{alg:kernel_embedding_classifier_training} with full gradient updates ($n_{b} = n$) to learn the hyperparameters of the conditional embedding of the iris dataset using only the first two attributes.
 The kernel used is isotropic Gaussian with diagonal length scales $\Sigma = \ell^{2} I_{2}$ and sensitivity $\alpha = \sigma_{f}$, so the model hyperparameters are $\theta = (\alpha, \ell)$ and the conditional embedding regularisation $\lambda$.
@@
 
-	\paragraph{Neural Network Kernels} DISCUSSION NOT DONE
+	\paragraph{Neural Network Kernels} Our learning algorithm is general and can learn the hyperparameters of any conditional embedding with discrete target space for any family of positive definite kernels $k_{\theta}$ over $\theta \in \Theta$ and $\lambda \in \Lambda$.
+One particularly useful class of kernels are neural network kernels, in which the kernel is formed from explicit features that come from (usually but not necessarily the last layer of) a neural network.
+These kernels benefit in both scalability and expressibility.
+For large datasets, the $n \times n$ Cholesky decomposition for full gradient update in \cref{alg:kernel_embedding_classifier_training} can be replaced by a $p \times p$ matrix that is independent of the size of $n$ by the Woodbury matrix inversion identity \citep{higham2002accuracy}.
+This allows scalability for $n >> p$ without using stochastic gradient updates so that the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} can be as tight as possible for a given training set of size $n$.
+Neural networks are by construction compositional, and thus latent representations of deeper networks undergo more transformations to generates a smaller (not infinitely many) collection of more expressive nonlinear features.
+That is, typical nonlinear kernels define implicit high dimensional features and thus has a shallow but wide model architecture.
+In contrast, neural network kernels define explicit lower dimensional features through multiple layers of abstraction, and thus has a deeper but narrower model architecture.
+We direct the reader to the supplementary material for a detailed discussion of the various kernel embedding classifier architectures.
+The feature transformations are typically defined by weights and biases of each hidden layer, which define the parameters $\theta \in \Theta$ of a neural network kernel and are thus trainable under our learning algorithm.
 
@@
 By minimising $q(\theta, \lambda)$, we shrink the subset being considered, achieving localised Rademacher complexity based feature learning without selecting parameters that define the tail sum.
-Local Rademacher complexity has also been employed for multiple kernel learning \citep{kloft2011local, cortes2013learning} to learn convex combinations of simpler kernels for a support vector machine.
-We extend its application to the probabilistic multiclass case, and use Rademacher complexity based risk bounds to learn the hyperparameters of a conditional kernel embedding.
+Local Rademacher complexity has also been employed for multiple kernel learning \citep{kloft2011local, cortes2013learning} to learn convex combinations of simpler preselected kernels for a support vector machine.
+We extend its application to the probabilistic multiclass case, and use Rademacher complexity bounds to learn any general kernel for a conditional embedding.
 
@@
 \label{sec:experiments}
-
-	We demonstrate the average performance of learning anisotropic Gaussian kernels and fully connected neural network kernels under the kernel embedding classification framework on standard UCI datasets, summarised in \cref{tab:stationary_experiments}.
-The former has a shallow but wide model architecture, while the latter has a deeper but narrower model architecture.
-
-	The Gaussian kernel is learned through both the original gradient update (GKEC) and the scalable batch stochastic gradient update (GKEC-SGD) using a tenth ($n_{b} \approx \frac{n}{10}$) of the training set each time, with sensitivity and length scales initialised to $1$.
-For neural network kernels, we randomly select two simple fully connected architectures with 16-32-8 (NNKEC-1) and 96-32 (NNKEC-2) hidden units respectively, and learn the corresponding kernel without dropout under ReLU activation.
-Weight parameters are initialised from a truncated normal distribution with standard deviation $0.1$, while biases are initialised to $0.1$, and are to be trained with full gradient updates.
-For all experiments, regularisation parameter $\lambda$ is initialised to $1$ and is learned jointly with the kernel.
-Classifiers are trained with the Adam optimiser \citep{kingma2014adam} in TensorFlow \citep{abadi2016tensorflow} with a learning rate of $\eta = 0.1$ and $\epsilon = 10^{-15}$ for learning objective $q(\theta, \lambda)$.
-Training is ran for 1000 or 10000 iterations when using full or batch stochastic gradient updates respectively, regardless of training convergence.
-All datasets are scaled so that all dimensions are in the unit range.
-Each classifier is trained on 9 out of 10 folds and tested on the remaining fold.
-The folds are shuffled over all 10 combinations to obtain the average test accuracy.
-We compare our results to other approaches using neural networks \citep[a; c]{kaya2016banknote, freire2009short}, probabilistic binary trees \citep[b]{horton1996probabilistic}, decision trees \citep[d]{zhou2004size}, and regularised discriminant analysis \citep[e]{aeberhard1992comparison}.
-These numbers are only illustrative, however, in that different authors may have used different data pre-processing, folds, optimiser, learning rate, architecture (for neural nets), and training time.
-
-	STILL HAS TO ADD CONVOLUTIONAL KERNEL MNIST STUFF WHICH ACHIEVED 99.5\% TEST ACCURACY WITH SGD
-
-	ALSO SHOW REVERSE EMBEDDING RESULTS TO OBTAIN THE CLASS MODES
-
-	DISCUSSION NOT DONE 
-%	\begin{table}[t]
-%		\begin{center}
-%			\begin{tabular}{ l | c | c }
-%				\hline
-%				\multicolumn{3}{ c }{Classification Accuracy on UCI Datasets} \\
-%				\hline
-%				\hline				
-%				Dataset \hspace{\fill} $(n, d, m)$ & Method & Test Accuracy \\
-%				\hline
-%				\hline
-%				\texttt{banknote} & Gaussian KEC & $99.93 \pm 0.22$ \\
-%				(1372, 4, 2) & Gaussian KEC (SGD 124) & $98.83 \pm 0.88$ \\
-%				& Neural KEC (16, 32, 8) & $99.49 \pm 1.03$ \\
-%				& Neural KEC (96, 32) & $99.42 \pm 0.91$ \\
-%				\hline
-%				\texttt{ecoli} & Gaussian KEC & $87.50 \pm 4.36$ \\
-%				(336, 7, 8) & Gaussian KEC (SGD 30) & $84.50 \pm 5.02$ \\
-%				& Neural KEC (16, 32, 8) & $87.49 \pm 3.24$ \\
-%				& Neural KEC (96, 32) & $86.32 \pm 5.98$ \\
-%				\hline
-%				\texttt{robot} & Gaussian KEC & \\
-%				(5456, 24, 4) & Gaussian KEC (SGD 491) & $95.45 \pm 0.86$ \\
-%				& Neural KEC (16, 32, 8) & $82.31 \pm 7.11$ \\	
-%%				\texttt{robot} \hspace{\fill} (5456, 24, 4) & Neural KEC (96, 32) & $92.25 \pm 1.39$ \\	
-%				& Neural KEC (96, 32) & $94.50 \pm 0.75$ \\
-%				\hline
-%				\texttt{segment} & Gaussian KEC & \\
-%				(2310, 19, 7) & Gaussian KEC (SGD 208) & $96.10 \pm 1.46$ \\
-%				& Neural KEC (16, 32, 8) & $94.59 \pm 1.62$ \\
-%				& Neural KEC (96, 32) & $96.71 \pm 1.06$ \\
-%				\hline
-%				\texttt{wine} & Gaussian KEC & $97.22 \pm 3.73$ \\
-%				(178, 13, 3) & Gaussian KEC (SGD 16) & $93.27 \pm 6.04$ \\
-%				& Neural KEC (16, 32, 8) & $96.11 \pm 5.00$\\
-%				& Neural KEC (96, 32) & $97.22 \pm 5.12$ \\
-%				\hline
-%				\texttt{yeast} & Gaussian KEC & $52.49 \pm 2.06$ \\
-%				(1484, 8, 10) & Gaussian KEC (SGD 134) & $60.30 \pm 4.39$ \\
-%				& Neural KEC (16, 32, 8) & $55.80 \pm 4.96$ \\
-%				& Neural KEC (96, 32) & $59.57 \pm 3.98 $ \\
-%				\hline
-%				\hline
-%			\end{tabular}
-%		\end{center}
-%		\caption{Classification accuracy of two kernel embedding classification architectures on standard UCI Datasets.
-Numbers after ``SGD'' indicates the batch size used.
-Numbers after ``Neural KEC'' indicates the size of the hidden layers, starting from the first.}
-%		\label{tab:stationary_experiments_old}
-%	\end{table}
 
@@
 
+	We demonstrate the average performance of learning anisotropic Gaussian kernels and fully connected neural network kernels under the kernel embedding classification framework on standard UCI datasets, summarised in \cref{tab:stationary_experiments}.
+The former has a shallow but wide model architecture, while the latter has a deeper but narrower model architecture.
+
+	The Gaussian kernel is learned using both full gradient update (GKEC) and the scalable batch stochastic gradient update (GKEC-SGD) using a tenth ($n_{b} \approx \frac{n}{10}$) of the training set each time, with sensitivity and length scales initialised to $1$.
+For neural network kernels, we randomly select two simple fully connected architectures with 16-32-8 (NNKEC-1) and 96-32 (NNKEC-2) hidden units respectively, and learn the corresponding kernel without dropout under ReLU activation.
+Weight parameters are initialised from a truncated normal distribution with standard deviation $0.1$, while biases are initialised to $0.1$, and are to be trained with full gradient updates.
+For all experiments, regularisation parameter $\lambda$ is initialised to $1$ and is learned jointly with the kernel.
+Classifiers are trained with the Adam optimiser \citep{kingma2014adam} in TensorFlow \citep{abadi2016tensorflow} with a learning rate of $\eta = 0.1$ and $\epsilon = 10^{-15}$ under the learning objective $q(\theta, \lambda)$.
+Training is ran for 1000 or 10000 iterations when using full or batch stochastic gradient updates respectively, regardless of training convergence.
+All datasets are scaled so that all attributes are in the unit range.
+Each classifier is trained on 9 out of 10 folds and tested on the remaining fold.
+The folds are shuffled over all 10 combinations to obtain the average test accuracy.
+We compare our results to other approaches using neural networks \citep[a; c]{kaya2016banknote, freire2009short}, probabilistic binary trees \citep[b]{horton1996probabilistic}, decision trees \citep[d]{zhou2004size}, and regularised discriminant analysis \citep[e]{aeberhard1992comparison}.
+These numbers are only illustrative, however, in that different authors may have used different data pre-processing, test folds, optimiser, learning rate, architecture (for neural nets), and training time.
+\Cref{tab:stationary_experiments} shows that our learning algorithm achieves similar performance to other approaches without any special tuning or heuristics by simply placing a conditional embedding on training data and applying a complexity bound based learning algorithm.
+The SGD approach for Gaussian kernels performs similarly to the full gradient approach, verifying the claim of \cref{thm:expected_risk_bound_hyperparameter_learning_copy} for any $n$.
+For neural network kernels, we did not attempt to choose an optimal architecture for any dataset.
+The learning algorithm is to train the same simple untrained network for different datasets under only 1000 iterations, and still generates comparable performance.
+
+	We also demonstrate
+
+	83.7\% with only 500 data points
+
+	STILL HAS TO ADD CONVOLUTIONAL KERNEL MNIST STUFF WHICH ACHIEVED 99.5\% TEST ACCURACY WITH SGD
+
+	ALSO SHOW REVERSE EMBEDDING RESULTS TO OBTAIN THE CLASS MODES
+
+	DISCUSSION NOT DONE
+
 	\begin{figure}[t]
@@
 
-	\begin{figure}[t]
-		\centering
-		\includegraphics[width=0.25\linewidth]{figures/spiral_all_final.eps}
-		\caption{.}
-		\label{fig:spiral}
-	\end{figure}
-
+%	\begin{figure}[t]
+%		\centering
+%		\includegraphics[width=0.25\linewidth]{figures/spiral_all_final.eps}
+%		\caption{.}
+%		\label{fig:spiral}
+%	\end{figure}
+%	
 \section{Conclusion}
@@
 
-\section{Information Entropy}
-\label{app:information_entropy}
-
-	The kernel embedding classifier provides decision probabilities instead of just a single label prediction.
-Such a probabilistic classifier allows us to quantify the uncertainty of its predictions for any given example $x \in \mathcal{X}$ through the information entropy \citep{shannon1951prediction, jaynes1957information}.
-This is ideal for detecting the decision boundaries of the classifier and areas of low data density.
-
-	We present two main approaches for inferring the information entropy from the classifier.
-Specifically, we would like to infer estimates for $h(x) := \mathbb{H}[Y | X = x] = - \sum_{c = 1}^{m} p_{c}(x) \log{p_{c}(x)} $, the information entropy of the possible labels $Y$ for a given example $X = x$.
-
-	The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref{eq:empirical_decision_probability_clip_normalised}, at the query point $x \in \mathcal{X}$,
-	\begin{equation}
-		\tilde{h}(x) := - \sum_{c = 1}^{m} \tilde{p}_{c}(x) \log{\tilde{p}_{c}(x)}.
-	\label{eq:entropy_clip_normalise}
-	\end{equation}
-	We call \eqref{eq:entropy_clip_normalise} the \textit{clip-normalised information entropy}.
-Since $\tilde{p}_{c}(x)$ converges pointwise to $p_{c}(x)$ with increasing data, $\tilde{h}(x)$ also converges pointwise to $h(x)$.
-
-	Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information \footnote{Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$.},
-	\begin{equation}
-	\begin{aligned}
-		\mathbb{H}[Y | X = x] &= - \sum_{c = 1}^{m} \mathbb{P}[Y = c| X = x] \log{\mathbb{P}[Y = c | X = x]} \\
-		&= \mathbb{E}[- \log{\mathbb{P}[Y | X = x]} | X = x] \\
-		&= \mathbb{E}[u_{x}(Y) | X = x],
-	\end{aligned}
-	\end{equation}
-	where $u_{x}(y) := - \log{\mathbb{P}[Y = y | X = x]}$ is the \textit{information} (in nats) we would gain when we discover that example $x$ actually has label $y$.
-If $u_{x} : \mathbb{N}_{m} \to \mathbb{R}$ is in the RKHS $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by $\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle$.
-This is the basis of our second approach.
-
-	Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$.
-We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the RKHS.
-Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref{eq:empirical_conditional_expectation} and estimate $h(x)$ by
-	\begin{equation}
-		\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle = \bvec{u}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x).
-	\end{equation}
-	Unfortunately, $u_{x}$ is not known exactly, since $\mathbb{P}[Y = y | X = x]$ is not known exactly.
-Instead, since $\hat{p}_{c}(x)$ is a consistent estimate for $\mathbb{P}[Y = c | X = x]$ by \cref{thm:probability_convergence}, we propose to replace $u_{x}(y)$ with the negative log of $\hat{p}_{y}(x)$.
-However, we cannot simply take the log of this estimator, as $\hat{p}_{y}(x)$ may produce non-positive estimates to the prediction probabilities.
-The straight forward way to mitigate this problem is to clip $\hat{p}_{y}(x)$ from the bottom by a very small number, before taking the log.
-However, experiments show that this produces non-smooth estimates over $\mathcal{X}$ and the degree of smoothness varies drastically between different choices of that small number (see \cref{app:design_choices}).
-Instead, in virtue of the fact that $\lim_{p \to 0} - p \log{p} = 0$ even though $\lim_{p \to 0} - \log{p} = \infty$, we simply define the information estimate $\hat{u}_{x}(y)$ as zero if the empirical decision probability is non-positive,
-	\begin{equation}
-		\hat{u}_{x}(y) := \begin{cases}
-		- \log{\hat{p}_{y}(x)} & \mathrm{if } \quad \hat{p}_{y}(x) > 0 \\
-		0 & \mathrm{otherwise}. \end{cases}
-	\label{eq:empirical_information}
-	\end{equation}
-	It remains to show that $\hat{u}_{x} \in \mathcal{H}_{\delta}$.
-Indeed, the identity $\hat{u}_{x} = \sum_{c = 1}^{m} \hat{u}_{x}(c) \delta(c, \cdot)$ holds and thus $\hat{u}_{x}$ is in the span of the kernel canonical features.
-We then arrive at the following estimate for $h(x)$,
-	\begin{equation}
-		\hat{h}(x) := \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle = \hat{\bvec{u}}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x),
-		\label{eq:empirical_information_entropy}
-	\end{equation}
-	where $\hat{\bvec{u}}_{x} := \{\hat{u}_{x}(y_{i})\}_{i = 1}^{n}$.
-Similar to the case with decision probabilities \eqref{eq:decision_probability}, the information entropy estimate \eqref{eq:empirical_information_entropy} is not guaranteed to be non-negative.
-However, in practice these negative values are close to zero.
-Furthermore, negative estimated information entropy implies that the model is very confident about its prediction, and it suffices to simply clip the entropy at zero if strict information entropy is required (see \cref{app:design_choices}).
-We give the proof of convergence of \eqref{eq:empirical_information_entropy} in \cref{app:convergence_theorems}.
-	\begin{theorem}[Uniform Convergence of Empirical Information Entropy Function]
-		\label{thm:entropy_convergence_copy}
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical information entropy function $\hat{h} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_information_entropy} converges uniformly to the true information entropy function $h : \mathcal{X} \to [0, \infty)$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-	\end{theorem}
-
-\section{Convergence Theorems}
+\section{Convergence Theorems for Kernel Embedding Classifiers}
 \label{app:convergence_theorems}
@@
 
-	In \cref{app:information_entropy}, we proposed an estimator for the information entropy $h(x)$ for a prediction at $x \in \mathcal{X}$.
-Since this estimator is now based on the inner product between the empirical conditional embedding and another empirically estimate function, instead of between the empirical conditional embedding and a known function, it is not immediately clear that such an estimator converges.
+	\subsection{Information Entropy of Kernel Embedding Classifiers}
+	\label{app:information_entropy}
+
+		The kernel embedding classifier provides decision probabilities instead of just a single label prediction.
+Such a probabilistic classifier allows us to quantify the uncertainty of its predictions for any given example $x \in \mathcal{X}$ through the information entropy \citep{shannon1951prediction, jaynes1957information}.
+This is ideal for detecting the decision boundaries of the classifier and areas of low data density.
+
+		We present two main approaches for inferring the information entropy from the classifier.
+Specifically, we would like to infer estimates for $h(x) := \mathbb{H}[Y | X = x] = - \sum_{c = 1}^{m} p_{c}(x) \log{p_{c}(x)} $, the information entropy of the possible labels $Y$ for a given example $X = x$.
+
+		The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref{eq:empirical_decision_probability_clip_normalised}, at the query point $x \in \mathcal{X}$,
+		\begin{equation}
+		\tilde{h}(x) := - \sum_{c = 1}^{m} \tilde{p}_{c}(x) \log{\tilde{p}_{c}(x)}.
+		\label{eq:entropy_clip_normalise}
+		\end{equation}
+		We call \eqref{eq:entropy_clip_normalise} the \textit{clip-normalised information entropy}.
+Since $\tilde{p}_{c}(x)$ converges pointwise to $p_{c}(x)$ with increasing data, $\tilde{h}(x)$ also converges pointwise to $h(x)$.
+
+		Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information \footnote{Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$.},
+		\begin{equation}
+		\begin{aligned}
+		\mathbb{H}[Y | X = x] &= - \sum_{c = 1}^{m} \mathbb{P}[Y = c| X = x] \log{\mathbb{P}[Y = c | X = x]} \\
+		&= \mathbb{E}[- \log{\mathbb{P}[Y | X = x]} | X = x] \\
+		&= \mathbb{E}[u_{x}(Y) | X = x],
+		\end{aligned}
+		\end{equation}
+		where $u_{x}(y) := - \log{\mathbb{P}[Y = y | X = x]}$ is the \textit{information} (in nats) we would gain when we discover that example $x$ actually has label $y$.
+If $u_{x} : \mathbb{N}_{m} \to \mathbb{R}$ is in the RKHS $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by $\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle$.
+This is the basis of our second approach.
+
+		Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$.
+We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the RKHS.
+Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref{eq:empirical_conditional_expectation} and estimate $h(x)$ by
+		\begin{equation}
+		\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle = \bvec{u}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x).
+		\end{equation}
+		Unfortunately, $u_{x}$ is not known exactly, since $\mathbb{P}[Y = y | X = x]$ is not known exactly.
+Instead, since $\hat{p}_{c}(x)$ is a consistent estimate for $\mathbb{P}[Y = c | X = x]$ by \cref{thm:probability_convergence}, we propose to replace $u_{x}(y)$ with the negative log of $\hat{p}_{y}(x)$.
+However, we cannot simply take the log of this estimator, as $\hat{p}_{y}(x)$ may produce non-positive estimates to the prediction probabilities.
+The straight forward way to mitigate this problem is to clip $\hat{p}_{y}(x)$ from the bottom by a very small number, before taking the log.
+However, experiments show that this produces non-smooth estimates over $\mathcal{X}$ and the degree of smoothness varies drastically between different choices of that small number (see \cref{app:design_choices}).
+Instead, in virtue of the fact that $\lim_{p \to 0} - p \log{p} = 0$ even though $\lim_{p \to 0} - \log{p} = \infty$, we simply define the information estimate $\hat{u}_{x}(y)$ as zero if the empirical decision probability is non-positive,
+		\begin{equation}
+		\hat{u}_{x}(y) := \begin{cases}
+		- \log{\hat{p}_{y}(x)} & \mathrm{if } \quad \hat{p}_{y}(x) > 0 \\
+		0 & \mathrm{otherwise}. \end{cases}
+		\label{eq:empirical_information}
+		\end{equation}
+		It remains to show that $\hat{u}_{x} \in \mathcal{H}_{\delta}$.
+Indeed, the identity $\hat{u}_{x} = \sum_{c = 1}^{m} \hat{u}_{x}(c) \delta(c, \cdot)$ holds and thus $\hat{u}_{x}$ is in the span of the kernel canonical features.
+We then arrive at the following estimate for $h(x)$,
+		\begin{equation}
+		\hat{h}(x) := \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle = \hat{\bvec{u}}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x),
+		\label{eq:empirical_information_entropy}
+		\end{equation}
+		where $\hat{\bvec{u}}_{x} := \{\hat{u}_{x}(y_{i})\}_{i = 1}^{n}$.
+Similar to the case with decision probabilities \eqref{eq:decision_probability}, the information entropy estimate \eqref{eq:empirical_information_entropy} is not guaranteed to be non-negative.
+However, in practice these negative values are close to zero.
+Furthermore, negative estimated information entropy implies that the model is very confident about its prediction, and it suffices to simply clip the entropy at zero if strict information entropy is required.
+
+		Since this estimator is now based on the inner product between the empirical conditional embedding and another empirically estimate function, instead of between the empirical conditional embedding and a known function like the decision probability estimate, it is not immediately clear that such an estimator converges.
 Nevertheless, intuition tells us that the inner product between two converging quantities should converge.
@@
 \newpage
-\section{Learning Theoretic Bounds for the Kernel Embedding Classifiers}
+\section{Learning Theoretic Bounds for Kernel Embedding Classifiers}
 \label{app:learning_theoretic_bounds}
@@
 \newpage
-\section{Special Cases of the Kernel Embedding Classifier}
+\section{Special Cases of Kernel Embedding Classifiers}
 \label{app:special_cases}
@@
 
-\newpage
-\section{Design Choices and More Discussion}
-\label{app:design_choices}
-
-	In this section we discuss the various design choices we make in formulating the kernel embedding classifier.
-
-	\subsection{Decision Probabilities: Why clip-normalise and not softmax-normalise or softplus-normalise?}
-
-		For \eqref{eq:probability_clip_normalise}...
-
-		The simple reason is that it works better.
+%\newpage
+%\section{Design Choices and More Discussion}
+%\label{app:design_choices}
+%
+%	In this section we discuss the various design choices we make in formulating the kernel embedding classifier.
+%
+%	\subsection{Decision Probabilities: Why clip-normalise and not softmax-normalise or softplus-normalise?}
+%	
+%		For \eqref{eq:probability_clip_normalise}...
+%		
+%		The simple reason is that it works better.
 The more theoretical reason is that our raw probability estimates usually produces predictions with low cross entropy loss.
@@
 When normalising after this, because the unlikely classes has taken up some probabilities, the class with high probabilities will have their high probabilities slightly reduces, making the cross entropy loss slightly higher and the predictions less confident.
-
-	\subsection{Information Entropy: Why define information gain to be zero despite being infinitely surprised?}
-
-		For \eqref{eq:empirical_information}...
-
-		\note{\textbf{Unpolished.}} This is really for numerical and experimental reasons.
+%		
+%	\subsection{Information Entropy: Why define information gain to be zero despite being infinitely surprised?}
+%	
+%		For \eqref{eq:empirical_information}...
+%		
+%		\note{\textbf{Unpolished.}} This is really for numerical and experimental reasons.
 The information entropy map obtained this way are just simply much smoother and intuitive.
@@
 Instead, defining the information gain to zero despite being infinitely surprised gave us very smooth estimates that is very close to both the map we expect and the map we obtain from computing the information entropy directly from the clip-normalised decision probabilities.
-
-	\subsection{Information Entropy: Why clip from below at zero?}
-
-		For \eqref{eq:empirical_information_entropy}...
-
-		\note{\textbf{Unpolished.}} Similar to the reason for clip-normalising decision probabilities, if the inference algorithm has produces an information entropy that is slightly less than zero, this just means that it is very confident at those regions.
+%		
+%	\subsection{Information Entropy: Why clip from below at zero?}
+%	
+%		For \eqref{eq:empirical_information_entropy}...
+%		
+%		\note{\textbf{Unpolished.}} Similar to the reason for clip-normalising decision probabilities, if the inference algorithm has produces an information entropy that is slightly less than zero, this just means that it is very confident at those regions.
 As such, in the limit, we expect that this would converge back to zero.
 Therefore, for finite data, we clip it from below at zero to indicate what the current data suggests the true information entropy should be when we have infinite data.
-
-	\subsection{Cross Entropy Loss: Why use the raw decision probabilities?}
+%		
+%	\subsection{Cross Entropy Loss: Why use the raw decision probabilities?}
 

### 2017-05-17 cake.tex
Immediate edit after comment

@@
 
-\usepackage{footnote}
-\makesavenoteenv{tabular}
+%\usepackage{footnote}
+%\makesavenoteenv{tabular}
 
@@
 Kernel embeddings are nonparametric methods to represent probability distributions directly through observed data in a reproducing kernel Hilbert space (RKHS).
-This property forms the core of modern kernel methods, yet the problem of hyperparameter learning for kernel embeddings remains challenging, often relying on heuristics and domain expertise.
+This property forms the core of modern kernel methods, yet hyperparameter learning for kernel embeddings remains challenging, often relying on heuristics and domain expertise.
 We begin by developing the kernel embedding classifier (KEC), and prove its stochastic convergence for probabilistic inference.
@@
 
-	Kernel embeddings are a principled way to represent probability distributions in a nonparametric setting.
-By transforming probability distributions into mean embeddings within a reproducing kernel Hilbert space (RKHS), distributions can be represented directly from data without assuming a parametric structure.
-Consequently, probabilistic inference can be carried out entirely within the RKHS in a nonparametric form, where difficult marginalisation integrals become simple linear algebra operations.
+	Kernel embeddings are principled methods to represent probability distributions in a nonparametric setting.
+By transforming distributions into mean embeddings within a reproducing kernel Hilbert space (RKHS), distributions can be represented directly from data without assuming a parametric structure \citep{song2013kernel}.
+Consequently, probabilistic inference can be carried out entirely within the RKHS nonparametrically, where difficult marginalisation integrals become simple linear algebra \citep{muandet2016kernel}.
 This very general and powerful technique is core to modern kernel methods, including support vector machines \citep{scholkopf2002learning}, kernel two-sample testing \citep{gretton2007kernel}, kernel Bayesian inference  \citep{fukumizu2013kernel}, nonparametric density estimation \citep{song2008tailoring, kanagawa2014recovering}, domain-invariant component analysis \citep{muandet2013domain}, dimensionality reduction \citep{fukumizu2004dimensionality}, feature discovery via hypothesis testing \citep{jitkrittum2016interpretable}, and filtering \citep{kanagawa2016filtering}.
@@
 However, this approach requires various approximations for non-Gaussian likelihoods, and does not generalise well to non-Gaussian priors.
-Within the kernel embedding framework itself, hyperparameters has been similarly difficult to tune, and its learning is usually only restricted to heuristical approaches such as cross validation.
+Within the kernel embedding framework itself, hyperparameters have been similarly difficult to tune, and its learning is usually only restricted to heuristical approaches such as cross validation.
 Recent work has introduced Gaussian process priors on mean embeddings to achieve Bayesian hyperparameter learning \citep{flaxman2016bayesian}.
@@
 	In this paper, we take a learning theoretic approach to learn the hyperparameters of a conditional kernel embedding in a supervised manner.
-We first begin by proposing the kernel embedding classifier (KEC), a principled framework for inferring multiclass probabilistic outputs using conditional embeddings, and provide a proof for its stochastic convergence.
-We then employ Rademacher complexity as a data dependent model complexity measure, and prove that the expected classification risk can be bounded with high probability by the empirical risk and the trace norm of the conditional embedding.
-We use this bound to propose a learning objective that learns the balance between performance accuracy and model complexity in a way that does not rely on priors.
-Finally, we note that the learning algorithm proposed generalises to an one class setting, enabling unsupervised kernel learning on unlabeled data.
+We begin by proposing the kernel embedding classifier (KEC), a principled framework for inferring multiclass probabilistic outputs using conditional embeddings, and provide a proof for its stochastic convergence.
+We then employ Rademacher complexity as a data dependent model complexity measure, and prove that expected classification risk can be bounded by empirical risk and conditional embedding trace norm with high probability.
+We use this bound to propose a learning objective that learns the balance between data fit and model complexity in a way that does not rely on priors.
 
@@
 
-	To construct a conditional embedding map $\mathcal{U}_{Y | X}$ corresponding to the distribution $\mathbb{P}_{Y | X}$ where $X : \Omega \to \mathcal{X}$ and $Y: \Omega \to \mathcal{Y}$ are measurable random variables, we choose a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ for the input space $\mathcal{X}$ and another kernel $l : \mathcal{Y} \times \mathcal{Y} \to \mathbb{R}$ for the output space $\mathcal{Y}$.
+	To construct a conditional embedding map $\mathcal{U}_{Y | X}$ corresponding to the distribution $\mathbb{P}_{Y | X}$, where $X : \Omega \to \mathcal{X}$ and $Y: \Omega \to \mathcal{Y}$ are measurable random variables, we choose a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ for the input space $\mathcal{X}$ and another kernel $l : \mathcal{Y} \times \mathcal{Y} \to \mathbb{R}$ for the output space $\mathcal{Y}$.
 These kernels $k$ and $l$ each describe how similarity is measured within each of their respective domains $\mathcal{X}$ and $\mathcal{Y}$, and are symmetric and positive definite such that they uniquely define the RKHS $\mathcal{H}_{k}$ and $\mathcal{H}_{l}$.
-Such a conditional embedding map is then defined by
-	\begin{equation}
-		\mathcal{U}_{Y | X} := C_{YX} C_{XX}^{-1},
-	\label{eq:conditional_embedding}
-	\end{equation}
-	where $C_{YX} := \mathbb{E}[l(Y, \cdot) \otimes k(X, \cdot)]$ and $C_{XX} := \mathbb{E}[k(X, \cdot) \otimes k(X, \cdot)]$ \citep{song2009hilbert}.
+We then define $\mathcal{U}_{Y | X} := C_{YX} C_{XX}^{-1}$ where $C_{YX} := \mathbb{E}[l(Y, \cdot) \otimes k(X, \cdot)]$ and $C_{XX} := \mathbb{E}[k(X, \cdot) \otimes k(X, \cdot)]$ \citep{song2009hilbert}.
 The conditional embedding map can be seen as an operator map from $\mathcal{H}_{k}$ to $\mathcal{H}_{l}$.
@@
 
-	Under the assumption that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$, \citet[Theorem 4]{song2009hilbert} proved that the conditional expectation of a function $g \in \mathcal{H}_{l}$ can be expressed as an inner product,
-	\begin{equation}
-		\mathbb{E}[g(Y) | X = x] = \langle \mu_{Y | X = x}, g \rangle.
-	\label{eq:conditional_expectation}
-	\end{equation}
+	Under the assumption that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$, \citet[Theorem 4]{song2009hilbert} proved that the conditional expectation of a function $g \in \mathcal{H}_{l}$ can be expressed as an inner product, $\mathbb{E}[g(Y) | X = x] = \langle \mu_{Y | X = x}, g \rangle$.
 While the assumptions that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$ and $k(x, \cdot) \in \mathrm{image}(C_{XX})$ holds for finite input domains $\mathcal{X}$ for characteristic kernels $k$, it is not necessarily true when $\mathcal{X}$ is a continuous domain \citep{fukumizu2004dimensionality}, which is the scenario for many classification problems.
-In this case, $C_{YX} C_{XX}^{-1}$ becomes only an approximation to $\mathcal{U}_{Y | X}$, and we instead regularise the inverse and use $C_{YX} (C_{XX} + \lambda I)^{-1}$, which also serves to avoid overfitting \citep[p.
-13]{song2013kernel}.
+In this case, $C_{YX} C_{XX}^{-1}$ becomes only an approximation to $\mathcal{U}_{Y | X}$, and we instead regularise the inverse and use $C_{YX} (C_{XX} + \lambda I)^{-1}$, which also serves to avoid overfitting \citep{song2013kernel}.
 
 	On top of this, in practice we do not have access to the distribution $\mathbb{P}_{X Y}$ to analytically derive the conditional embedding.
-Instead, we have a finite collection of data points $\{x_{i}, y_{i}\} \in \mathcal{X} \times \mathcal{Y}$, $i \in \mathbb{N}_{n} := \{1, \dots, n\}$, for which the conditional embedding map $\mathcal{U}_{Y | X}$ can be estimated by
+Instead, we have a finite collection of observations $\{x_{i}, y_{i}\} \in \mathcal{X} \times \mathcal{Y}$, $i \in \mathbb{N}_{n} := \{1, \dots, n\}$, for which the conditional embedding map $\mathcal{U}_{Y | X}$ can be estimated by
 	\begin{equation}
@@
 	\end{equation}
-	where $K := \{k(x_{i}, x_{j})\}_{i = 1, j = 1}^{n, n}$, $\Phi := \begin{bmatrix} \phi(x_{1}) & \dots & \phi(x_{n}) \end{bmatrix}$, $\Psi := \begin{bmatrix} \psi(y_{1}) & \dots & \psi(y_{n}) \end{bmatrix}$, $\phi(x) := k(x, \cdot)$, $\psi(y) := l(y, \cdot)$, and $\lambda$ is the regularisation parameter for the conditional operator \citep{song2013kernel}.
-The empirical conditional embedding defined by $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$ then stochastically converges to the conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \cite[Theorem 6]{song2009hilbert}.
-This allows us to approximate the conditional expectation \eqref{eq:conditional_expectation} with $\langle \hat{\mu}_{Y | X = x}, g \rangle$ instead,
+	where $K := \{k(x_{i}, x_{j})\}_{i = 1, j = 1}^{n, n}$, $\Phi := \begin{bmatrix} \phi(x_{1}) & \dots & \phi(x_{n}) \end{bmatrix}$, $\Psi := \begin{bmatrix} \psi(y_{1}) & \dots & \psi(y_{n}) \end{bmatrix}$, $\phi(x) := k(x, \cdot)$, and $\psi(y) := l(y, \cdot)$ \citep{song2013kernel}.
+The empirical conditional embedding $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$ then stochastically converges to the conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot) \in \mathrm{image}(C_{XX})$ \cite[Theorem 6]{song2009hilbert}.
+This allows us to approximate the conditional expectation with $\langle \hat{\mu}_{Y | X = x}, g \rangle$ instead,
 	\begin{equation}
@@
 	\end{equation}
-	where $\bvec{g} := \{g(y_{i})\}_{i = 1}^{n}$ and $\bvec{k}(x) := \{k(x_{i}, x\}_{i = 1}^{n}$.
+	where $\bvec{g} := \{g(y_{i})\}_{i = 1}^{n}$ and $\bvec{k}(x) := \{k(x_{i}, x)\}_{i = 1}^{n}$.
 
@@
 Naturally, we first choose the Kronecker delta kernel $\delta : \mathbb{N}_{m} \times \mathbb{N}_{m} \to \{0, 1\}$ as the output kernel $l$, where labels that are the same has unit similarity and labels that are different have no similarity.
-That is, for all pairs of labels $y_{i}, y_{j} \in \mathcal{Y}$,
-	\begin{equation}
-		\delta(y_{i}, y_{j}) := \begin{cases}
-		1 & \mathrm{if } \quad y_{i} = y_{j}, \\
-		0 & \mathrm{otherwise}.
-		\end{cases}
-	\end{equation}
+That is, for all pairs of labels $y_{i}, y_{j} \in \mathcal{Y}$, $\delta(y_{i}, y_{j}) = 1$ only if $y_{i} = y_{j}$ and is $0$ otherwise.
 As $\delta$ is an integrally strictly positive definite kernel on $\mathbb{N}_{m}$, it is therefore characteristic \citep[Theorem 7]{sriperumbudur2010hilbert}.
-As such, by definition of characteristic kernels, $\delta$ uniquely defines a RKHS $\mathcal{H}_{\delta}$ \citep{fukumizu2004dimensionality}.
-Notice that this kernel has no parameters, so that the model hyperparameters only come from the kernel of the input space and the regularisation parameter $\lambda$.
-
-	Recall that the RKHS induced by a positive definite kernel is the closure of the span of its kernel induced features \citep{xu2009refinement}, so that $\mathcal{H}_{l} = \overline{\mathrm{span}\{l(y, \cdot) : y \in \mathcal{Y}\}}$.
-For $\mathcal{Y} = \mathbb{N}_{m}$ and $l = \delta$, this means that any real-valued function $g : \mathbb{N}_{m} \to \mathbb{R}$ that is bounded on its discrete domain $\mathbb{N}_{m}$ is in the RKHS of $\delta$, because we can always write $g = \sum_{y = 1}^{m} g(y) \delta(y, \cdot) \in \mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}$.
-
+As such, by definition of characteristic kernels \citep{fukumizu2004dimensionality}, $\delta$ uniquely defines a RKHS  $\mathcal{H}_{\delta} = \overline{\mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}}$, which is the closure of the span of its kernel induced features \citep{xu2009refinement}.
+For $\mathcal{Y} = \mathbb{N}_{m}$, this means that any real-valued function $g : \mathbb{N}_{m} \to \mathbb{R}$ that is bounded on its discrete domain $\mathbb{N}_{m}$ is in the RKHS of $\delta$, because we can always write $g = \sum_{y = 1}^{m} g(y) \delta(y, \cdot) \in \mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}$.
 In particular, indicator functions on $\mathbb{N}_{m}$ are in the RKHS $\mathcal{H}_{\delta}$, since
@@
 
-	While such properties does not becessarily hold for continuous domains in general, this convenient property in the case of a discrete domain $\mathcal{Y}$ with a Kronecker delta kernel $\delta$ is what allows consistent estimations of decision probabilities used in multiclass classification, which we turn to next.
+	While such properties does not necessarily hold for continuous domains in general, this convenient property in the case of a discrete domain $\mathcal{Y}$ with a Kronecker delta kernel $\delta$ is what allows consistent estimations of decision probabilities used in multiclass classification, which we turn to next.
 
@@
 In fact, the inference distribution \eqref{eq:empirical_decision_probability_vector} is equivalent to a conditional embedding.
-We direct the reader to the supplementary material for proof.
 	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
@@
 		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+See appendix A for proof and other convergence results.
 	\end{theorem}
 	While decision probability estimates \eqref{eq:empirical_decision_probability} do not necessarily form a normalised distribution for finite $n$, \cref{thm:probability_convergence_copy} guarantees that they approach one with increasing sample sizes.
-If normalised distributions are required for interpretation, distribution estimates \eqref{eq:empirical_decision_probability} can be clip-normalised,
+When normalised distributions are required, distribution estimates \eqref{eq:empirical_decision_probability} can be clip-normalised,
 	\begin{equation}
@@
 		\begin{equation}
-			\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e r(\theta, \lambda) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
+			\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e \; r(\theta, \lambda) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
 		\label{eq:expected_risk_bound_hyperparameter_learning_copy}
@@
 
+	We refer the read to appendix B for proof.
+In order for the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} to be non-trivial, we focus on bounded kernels in the sense that $\alpha^{2}(\theta) := \sup_{x \in \mathcal{X}} k_{\theta}(x, x) < \infty$.
+Gaussian kernels $k_{\theta}(x, x') = \sigma_{f}^{2} \exp{( - \frac{1}{2}(x - x') \Sigma^{-1} (x - x') )}$ and similar stationary kernels (e.g.
+Mat\'{e}rn) with sensitivity and length scales $\theta = (\sigma_{f}, \Sigma)$, for example, have $\alpha(\theta) = \sigma_{f}$.
+Since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} is true with probability $1 - \beta$ when the random variables $X_{i}, Y_{i}$ are realised as the training observations $x_{i}, y_{i}$.
+We therefore employ this upper bound as the learning objective,
+	\begin{equation}
+		q(\theta, \lambda) := \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(y_{i}, \bvec{f}_{\theta, \lambda}(x_{i})) + 4 e \; r(\theta, \lambda).
+	\label{eq:learning_objective}
+	\end{equation}
+	We employ gradient based optimisers such as Gradient descent or Adam \citep{kingma2014adam}.
+Since \cref{thm:expected_risk_bound_hyperparameter_learning_copy} holds for any $n \in \mathbb{N}_{+}$ and any set of data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ from $\mathbb{P}_{X Y}$, with the trade-off of relaxing bound tightness through $\sqrt{8 \log{(2 / \beta)} / n}$, the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} also holds with high probability for a subset of the training data.
+This enables scalable hyperparameter learning through batch stochastic gradient updates, where each gradient update stochastically improves a different upper bound of the generalisation risk.
+Because this bound holds with high probability over \textit{iid} samples, through randomly selecting a batch of training examples that comes from the same distribution, the resulting stochastic gradient will improve a strict upper bound with the same high probability.
+We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:kernel_embedding_classifier_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size.
+The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is performed only once after learning instead of once every learning iteration, and can be avoided by using kernel herding \citep{chen2010super} or other kernel data reduction technique to select subsets to estimate the already learned embedding.
+All further inference steps take $O(n^{2})$ time for back substitution.
+
 	\begin{algorithm}[tb]
-		\caption{KEC Hyperparameter Learning with Batch Stochastic Gradient Descent}
+		\caption{KEC Hyperparameter Learning with Batch Stochastic Gradient Updates}
 		\label{alg:kernel_embedding_classifier_training}
@@
 
-	In order for the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} to be non-trivial, we focus on bounded kernels in the sense that $\alpha^{2}(\theta) := \sup_{x \in \mathcal{X}} k_{\theta}(x, x) < \infty$.
-Gaussian kernels $k_{\theta}(x, x') = \sigma_{f}^{2} \exp{( - \frac{1}{2}(x - x') \Sigma^{-1} (x - x') )}$ and similar stationary kernels such as the Mat\'{e}rn family with sensitivity and length scales $\theta = (\sigma_{f}, \Sigma)$, for example, have $\alpha(\theta) = \sigma_{f}$.
-Since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} is true with probability $1 - \beta$ when the random variables $X_{i}, Y_{i}$ are realised as the training observations $x_{i}, y_{i}$.
-We therefore employ this upper bound as the learning objective,
-	\begin{equation}
-		q(\theta, \lambda) := \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(y_{i}, \bvec{f}_{\theta, \lambda}(x_{i})) + 4 e r(\theta, \lambda).
-	\label{eq:learning_objective}
-	\end{equation}
-	We employ gradient based optimisers such as Gradient descent or Adam \citep{kingma2014adam}.
-Since \cref{thm:expected_risk_bound_hyperparameter_learning_copy} holds for any $n \in \mathbb{N}_{+}$ and any set of data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ from $\mathbb{P}_{X Y}$, with the trade-off of relaxing bound tightness through $\sqrt{8 \log{(2 / \beta)} / n}$, the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} also holds with high probability for a subset of the training data.
-This enables scalable hyperparameter learning through batch stochastic gradient updates, where each gradient update stochastically improves a different upper bound of the generalisation risk.
-Because this bound holds with high probability over \textit{iid} samples, through randomly selecting a batch of training examples that comes from the same distribution, the resulting stochastic gradient will improve a strict upper bound with the same high probability.
-We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:kernel_embedding_classifier_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size.
+	% , is general for any conditional embedding with discrete target space given any family of positive definite kernels $k_{\theta}$ over $\theta \in \Theta$ and $\lambda \in \Lambda$
+	Our learning algorithm does not restrict the way the kernel $k_{\theta}$ is constructed from its parameters $\theta \in \Theta$.
+One particularly useful class of kernels are linear kernels with neural network features, in which the kernel $k(x, x') = \langle \varphi(x), \varphi(x') \rangle$ is constructed from neural networks $\varphi : \mathcal{X} \to \mathbb{R}^{p}$ explicitly.
+Neural networks are typically defined by weights and biases of its hidden layers, which collectively define the parameters of the constructed kernel, and are thus trainable under our learning algorithm.
+These kernels benefit in both scalability and expressibility.
+For large datasets, the $n \times n$ Cholesky decomposition required for full gradient updates in \cref{alg:kernel_embedding_classifier_training} can be transformed into a $p \times p$ decomposition by the Woodbury matrix inversion identity \citep{higham2002accuracy}.
+This allows scalability for $n >> p$ without using stochastic gradient updates so that the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} can be as tight as possible for a given $n$.
+Neural networks are by construction compositional, and thus latent representations of deeper networks undergo more transformations to generate a smaller and explicit collection of more expressive nonlinear features, leading to a deeper but narrower model architecture.
+This is in contrast to the potentially infinitely many implicit features from nonlinear kernels, which in turn define a shallower but wider model architecture.
+We direct the reader to appendix C for detailed discussion on the various kernel embedding classifier architectures.
+
+\section{Related Work}
+\label{sec:related_work}
+
+	For a linear class of predictors parametrised as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularisation to bound the Rademacher complexity, achieving tight generalisation bounds in the context of multi-label learning.
+The KEC predictor \eqref{eq:empirical_decision_probability_vector} has the same linear form in the feature space, $\bvec{f}_{\theta, \lambda}(x) = \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \Phi_{\theta}^{T} \phi_{\theta}(x) = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$, where instead of learning the operator $W^{T}$ directory, we learn hyperparameters $\theta \in \Theta, \lambda \in \Lambda$ for the empirical conditional embedding map $\mathcal{U}^{(\theta, \lambda)}_{Y | X}$ to learn the features $\phi_{\theta}(x)$.
+\cite{xu2016local} extends the trace norm regularisation approach by considering the local Rademacher complexity on a subset of the predictor class, where they instead minimise the tail sum of the predictor singular values.
+In the proof of \cref{thm:expected_risk_bound_hyperparameter_learning_copy}, $\theta \in \Theta$ and $\lambda \in \Lambda$ define subsets of $\Theta$ and $\Lambda$ where the Rademacher complexity is considered over.
+By minimising $q(\theta, \lambda)$, we shrink the subset being considered, achieving localised Rademacher complexity based feature learning without selecting parameters that define the tail sum.
+Local Rademacher complexity has also been employed for multiple kernel learning \citep{kloft2011local, cortes2013learning} to learn convex combinations of simpler preselected kernels for a support vector machine.
+We extend its application to the probabilistic multiclass case, and use Rademacher complexity bounds to learn any general kernel for a conditional embedding.
+
+\section{Experiments}
+\label{sec:experiments}
+
+	\paragraph{Toy Example}
 
@@
 
-	\paragraph{Toy Example}
-
 		The first two of four total attributes of the iris dataset \citep{fisher1936use} is known to have class labels that are not only not linearly separable, but also non-separable by any means, in that the same example $x \in \mathbb{R}^{2}$ may be assigned different output labels $y \in \mathbb{N}_{3} := \{1, 2, 3\}$ as they were only separable with the two remaining attributes.
@@
 
-		\Cref{fig:iris} demonstrates \cref{alg:kernel_embedding_classifier_training} with full gradient updates ($n_{b} = n$) to learn the hyperparameters of the conditional embedding of the iris dataset using only the first two attributes.
-The kernel used is isotropic Gaussian with diagonal length scales $\Sigma = \ell^{2} I_{2}$ and sensitivity $\alpha = \sigma_{f}$, so the model hyperparameters are $\theta = (\alpha, \ell)$ and the conditional embedding regularisation $\lambda$.
+		\Cref{fig:iris} demonstrates \cref{alg:kernel_embedding_classifier_training} with full gradient updates ($n_{b} = n$) to learn hyperparameters of the conditional embedding on the two attribute iris dataset.
+The kernel used is isotropic Gaussian with diagonal length scales $\Sigma = \ell^{2} I_{2}$ and sensitivity $\alpha = \sigma_{f}$, so the hyperparameters are $\theta = (\alpha, \ell)$ and $\lambda$.
 We evaluate the performance of the learning algorithm on a withheld test set using 20\% of the available 150 data samples.
-Attributes are scaled into the unit range $[0, 1]$ and decision probability maps are plotted for the region $[-0.5, 1.05]^{2}$, where the red, green, and blue colour channel represents the decision probability for classes $c = 1, 2, 3$.
+Attributes are scaled into the unit range $[0, 1]$ and decision probability maps are plotted for the region $[-0.5, 1.05]^{2}$, where the red, green, and blue colour channel represents the clip-normalised decision probability for classes $c = 1, 2, 3$.
 We begin from two initial scenarios, one originally overfitting ($\alpha_{o} = 0.01$, $\ell_{o} = 0.035$, $\lambda_{o} = 10^{-6}$) and another underfitting ($\alpha_{u} = 1$, $\ell_{u} = 1$, $\lambda_{u} = 1$) the training data.
@@
 
-		% $ \sigma^{2}_{f} \bvec{Y}^{T} (K_{(\sigma_{f}, \ell)} + n \lambda I)^{-1} K_{(\sigma_{f}, \ell)} (K_{(\sigma_{f}, \ell)} + n \lambda I)^{-1} \bvec{Y} = \bvec{Y}^{T} (K_{(1, \ell)} + n \frac{\lambda}{\sigma^{2}_{f}} I)^{-1} K_{(1, \ell)} (K_{(1, \ell)} + n \frac{\lambda}{\sigma^{2}_{f}} I)^{-1} \bvec{Y}$.
-%	RCB from overfitted after 500 iterations: 2.2299
-%	RCB from underfitted after 500 iterations: 2.1424
-%	
-%	HYPERS from overfitted $\sigma_{f} = 0.01$, $\sigma = 0.035$, $\lambda = 10^{-6}$ to $\sigma_{f} = 0.01$, $\sigma = 0.24$, $\lambda = 8.6186 \times 10^{-7}$.
-%	
-%	$0.195949 / (5.1^2) = 0.007533602460592081 \approx 0.00861677 = 8.61677e-07 / (0.01^2)$
-%	
-%	HYPERS from underfitted $\sigma_{f} = 1$, $\sigma = 1$, $\lambda = 1$ to $\sigma_{f} = 5.1$, $\sigma = 0.24$, $\lambda = 0.1960$
-
-%	
-%	NEED TO SHOW VISUALISATIONS OF IRIS HERE AND DISCUSS TWO INITIALISATIONS: ONE OVERFITTING AND ONE UNDERFITTING, AND SHOW THAT OUR TRAINING ALGORITHM FINDS A BALANCE FROM BOTH INITIAL SETTINGS.
-%	
-%	ALSO SHOW REVERSE EMBEDDING RESULTS
-
-	\paragraph{Neural Network Kernels} Our learning algorithm is general and can learn the hyperparameters of any conditional embedding with discrete target space for any family of positive definite kernels $k_{\theta}$ over $\theta \in \Theta$ and $\lambda \in \Lambda$.
-One particularly useful class of kernels are neural network kernels, in which the kernel is formed from explicit features that come from (usually but not necessarily the last layer of) a neural network.
-These kernels benefit in both scalability and expressibility.
-For large datasets, the $n \times n$ Cholesky decomposition for full gradient update in \cref{alg:kernel_embedding_classifier_training} can be replaced by a $p \times p$ matrix that is independent of the size of $n$ by the Woodbury matrix inversion identity \citep{higham2002accuracy}.
-This allows scalability for $n >> p$ without using stochastic gradient updates so that the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} can be as tight as possible for a given training set of size $n$.
-Neural networks are by construction compositional, and thus latent representations of deeper networks undergo more transformations to generates a smaller (not infinitely many) collection of more expressive nonlinear features.
-That is, typical nonlinear kernels define implicit high dimensional features and thus has a shallow but wide model architecture.
-In contrast, neural network kernels define explicit lower dimensional features through multiple layers of abstraction, and thus has a deeper but narrower model architecture.
-We direct the reader to the supplementary material for a detailed discussion of the various kernel embedding classifier architectures.
-The feature transformations are typically defined by weights and biases of each hidden layer, which define the parameters $\theta \in \Theta$ of a neural network kernel and are thus trainable under our learning algorithm.
-
-\section{Related Work}
-\label{sec:related_work}
-
-	For a linear class of predictors parametrised as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularisation to bound the Rademacher complexity, achieving tight generalisation bounds in the context of multi-label learning.
-The KEC predictor \eqref{eq:empirical_decision_probability_vector} has the same linear form in the feature space, $\bvec{f}_{\theta, \lambda}(x) = \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \Phi_{\theta}^{T} \phi_{\theta}(x) = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$, where instead of learning the operator $W^{T}$ directory, we learn hyperparameters $\theta \in \Theta, \lambda \in \Lambda$ for the empirical conditional embedding map $\mathcal{U}^{(\theta, \lambda)}_{Y | X}$ to learn the features $\phi_{\theta}(x)$.
-\cite{xu2016local} extends the trace norm regularisation approach by considering the local Rademacher complexity on a subset of the predictor class, where they instead minimise the tail sum of the predictor singular values.
-In the proof of \cref{thm:expected_risk_bound_hyperparameter_learning_copy}, $\theta \in \Theta$ and $\lambda \in \Lambda$ define subsets of $\Theta$ and $\Lambda$ where the Rademacher complexity is considered over.
-By minimising $q(\theta, \lambda)$, we shrink the subset being considered, achieving localised Rademacher complexity based feature learning without selecting parameters that define the tail sum.
-Local Rademacher complexity has also been employed for multiple kernel learning \citep{kloft2011local, cortes2013learning} to learn convex combinations of simpler preselected kernels for a support vector machine.
-We extend its application to the probabilistic multiclass case, and use Rademacher complexity bounds to learn any general kernel for a conditional embedding.
-
-\section{Experiments}
-\label{sec:experiments}
+	\paragraph{UCI Datasets}
 
@@
 				\texttt{ecoli} \hspace{\fill} (336, 7, 8) & $87.5 \pm 4.4$ & $84.5 \pm 5.0$ & $87.5 \pm 3.2$ & $86.3 \pm 6.0$ & 81.1\textsuperscript{b} \\
-			\texttt{robot} \hspace{\fill} (5456, 24, 4) & $97.8$ & $95.5 \pm 0.9$ & $82.3 \pm 7.1$ & $94.5 \pm 0.8$ & 97.59\textsuperscript{c} \\
+				\texttt{robot} \hspace{\fill} (5456, 24, 4) & $96.7 \pm 0.9$ & $95.5 \pm 0.9$ & $82.3 \pm 7.1$ & $94.5 \pm 0.8$ & 97.59\textsuperscript{c} \\
 				\texttt{segment} \hspace{\fill} (2310, 19, 7) & $98.4 \pm 0.8$ & $96.1 \pm 1.5$ & $94.6 \pm 1.6$ & $96.7 \pm 1.1$ & 96.83\textsuperscript{d} \\
-			\texttt{waveform} \hspace{\fill} (5000, 21, 3) & $87.2$ & $83.3 \pm 1.6$ & $86.8 \pm 1.6$ & $86.7 \pm 1.6$ & 90.98\textsuperscript{d} \\
 				\texttt{wine} \hspace{\fill} (178, 13, 3) & $97.2 \pm 3.7$ & $93.3 \pm 6.0$ & $96.1 \pm 5.0$ & $97.2 \pm 5.1$ & 100\textsuperscript{e} \\
@@
 
+	\paragraph{MNIST}
+
 		We also demonstrate
@@
 
-	ALSO SHOW REVERSE EMBEDDING RESULTS TO OBTAIN THE CLASS MODES
-
 		DISCUSSION NOT DONE
 
-	\begin{figure}[t]
-		\centering
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_50.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_100.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_250.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_500.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_750.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_1000.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_1500.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_2000.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_5000.eps}
-		\includegraphics[width=\linewidth]{figures/test_performance.eps}
-		\caption{Training the kernel embedding classifier on the MNIST digits dataset with an anisotropic Gaussian kernel. Top: Learned length scales for each pixel; Bottom: Performance on the test set.}
-		\label{fig:pixel_relevance}
-	\end{figure}
+%	\begin{figure}[t]
+%		\centering
+%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_50.eps}
+%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_100.eps}
+%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_250.eps}
+%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_500.eps}
+%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_750.eps}
+%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_1000.eps}
+%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_1500.eps}
+%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_2000.eps}
+%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_5000.eps}
+%		\includegraphics[width=\linewidth]{figures/test_performance.eps}
+%		\caption{Training the kernel embedding classifier on the MNIST digits dataset with an anisotropic Gaussian kernel. Top: Learned length scales for each pixel; Bottom: Performance on the test set.}
+%		\label{fig:pixel_relevance}
+%	\end{figure}
 
@@
 	\note{Summarise main contribution.}
+
+	FUTURE WORK: REVERSE EMBEDDING, SEMI-SUPERVISED LEARNING, ONE CLASS LEARNING, REGRESSION
 
@@
 
-\small
+%		\item \textbf{Sampling and Generative Models.} While the kernel embedding classifier is trained as a discriminative model, at its core it is simply just a condition embedding of $\mathbb{P}_{Y | X}$.
+As such, we can do full probabilistic inference entirely in reproducing kernel Hilbert spaces and obtain the Hilbert space embeddings of $\mathbb{P}_{X | Y}$, similar to what we have touched upon in \cref{sec:mode_reconstruction}, or even simply of the marginals $\mathbb{P}_{X}$ and $\mathbb{P}_{Y}$.
+If we can recover these distributions as densities ($\mathbb{P}_{Y}$ would correspond to a probability mass function over a finite and discrete space $\mathbb{N}_{m}$ which is identical to the mean embedding already, and so this step would be trivial for $\mathbb{P}_{Y}$), then we would be able to model our data in a fully generative manner.
+In fact, in \cref{sec:mode_reconstruction} we have have already done so indirectly through reversing the embedding.
+Of course, this would require us to solve the pre-image problem of kernel embeddings, for which no general methodology exists yet besides a few heuristics with various assumptions.
+Nevertheless, assuming we can recover the densities well enough, we can then generate samples from those distributions.
+Alternatively, if we can instead sample from those distributions \textit{without} finding the pre-image, but by directly using the mean embeddings instead, that would make the kernel embedding classifier very useful as a generative modelling tool.
+%		
+%		\item \textbf{Target Label Kernel.} In this paper, we proposed to place a Kronecker delta kernel $l = \delta$ over the label space $\mathcal{Y} = \mathbb{N}_{m}$ as it is the simplest kernel over a discrete and finite domain.
+However, it is possible to place other kernels over the label space.
+A simple kernel is to have a `generalised Kronecker delta kernel' that has unit similarity when labels are the same, but a small, positive yet non-zero similarity when labels are different.
+If we set these cross similarity to be the same across all non-identical pairs of labels, then it is straight forward to show that the inference algorithm we developed in this paper stays the same.
+However, if we allow them to vary amongst each other as kernel parameters (between the range $(0, 1)$, in order to stay positive definite), then we suspect that these cross similarity coefficients would act as correlation factors between classes.
+The training algorithm we developed here does not prevent the target label kernel to have its own hyperparameters.
+As such, we should be able to learn the correlation effects between the classes effectively using the same training scheme.
+We suspect that this would make the empirical decision probabilities converge to a valid probability distribution faster.
+However, we also suspect that the training may become even more non-convex and optimisation to become more difficult.
+%		
+%		These factors may even give rise to new interpretable insights in terms of how different classes may be more related to each other.
+For example, in an image recognition task of animals, it may learn that, the class `horse' and 'pony' are much more similar than `horse' and `elephant' from the input features, and start to use the output correlations to focus on inferring about them as a group instead.
+
 \bibliographystyle{apalike}
@@
 		\begin{algorithm}[tb]
-			\caption{Linear KEC Hyperparameter Learning with Batch Stochastic Gradient Descent}
+			\caption{Linear KEC Hyperparameter Learning with Batch Stochastic Gradient Updates}
 			\label{alg:linear_kernel_embedding_classifier_training}

### 2017-05-18 cake.tex
Revision for paper and appendix

@@
 \usepackage{algorithmic}
-
-%\usepackage{footnote}
-%\makesavenoteenv{tabular}
-
 \newcommand{\argmax}{\operatornamewithlimits{argmax}}
-\newcommand{\note}[1]{{\color{orange} #1}}
-\newcommand{\edit}[1]{{\color{forestgreen} #1}}
 
@@
 \author{
-	Kelvin Y.S. Hsu \\
-	University of Sydney, Australia\\
-	DATA61, CSIRO\\
-	\texttt{Kelvin.Hsu@\{sydney.edu.au, data61.csiro.au\}} \\
-	%% examples of more authors
-	\And
-	Richard Nock \\
-	Australian National University, Australia\\
-	University of Sydney, Australia\\
-	DATA61, CSIRO\\
-	\texttt{Richard.Nock@data61.csiro.au} \\
-	\And
-	Fabio T. Ramos \\
-	University of Sydney, Australia\\
-	DATA61, CSIRO\\
-	\texttt{Fabio.Ramos@\{sydney.edu.au, data61.csiro.au\}} \\
-	%% \texttt{email} \\
-	%% \AND
-	%% Coauthor \\
-	%% Affiliation \\
-	%% Address \\
-	%% \texttt{email} \\
-	%% \And
-	%% Coauthor \\
-	%% Affiliation \\
-	%% Address \\
-	%% \texttt{email} \\
-	%% \And
-	%% Coauthor \\
-	%% Affiliation \\
-	%% Address \\
-	%% \texttt{email} \\
 }
@@
 \begin{document}
-% \nipsfinalcopy is no longer used
 
@@
 We begin by developing the kernel embedding classifier (KEC), and prove its stochastic convergence for probabilistic inference.
-We then prove that its expected classification error can be bounded with high probability using Rademacher complexity based risk bounds.
+We then prove that its expected classification error can be bounded with high probability using Rademacher complexity bounds.
 We use this bound to propose a scalable hyperparameter learning algorithm for conditional embeddings with batch stochastic gradient descent.
@@
 By transforming distributions into mean embeddings within a reproducing kernel Hilbert space (RKHS), distributions can be represented directly from data without assuming a parametric structure \citep{song2013kernel}.
-Consequently, probabilistic inference can be carried out entirely within the RKHS nonparametrically, where difficult marginalisation integrals become simple linear algebra \citep{muandet2016kernel}.
+Consequently, nonparametric probabilistic inference can be carried out entirely within the RKHS, where difficult marginalisation integrals become simple linear algebra \citep{muandet2016kernel}.
 This very general and powerful technique is core to modern kernel methods, including support vector machines \citep{scholkopf2002learning}, kernel two-sample testing \citep{gretton2007kernel}, kernel Bayesian inference  \citep{fukumizu2013kernel}, nonparametric density estimation \citep{song2008tailoring, kanagawa2014recovering}, domain-invariant component analysis \citep{muandet2013domain}, dimensionality reduction \citep{fukumizu2004dimensionality}, feature discovery via hypothesis testing \citep{jitkrittum2016interpretable}, and filtering \citep{kanagawa2016filtering}.
@@
 	To construct a conditional embedding map $\mathcal{U}_{Y | X}$ corresponding to the distribution $\mathbb{P}_{Y | X}$, where $X : \Omega \to \mathcal{X}$ and $Y: \Omega \to \mathcal{Y}$ are measurable random variables, we choose a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ for the input space $\mathcal{X}$ and another kernel $l : \mathcal{Y} \times \mathcal{Y} \to \mathbb{R}$ for the output space $\mathcal{Y}$.
-These kernels $k$ and $l$ each describe how similarity is measured within each of their respective domains $\mathcal{X}$ and $\mathcal{Y}$, and are symmetric and positive definite such that they uniquely define the RKHS $\mathcal{H}_{k}$ and $\mathcal{H}_{l}$.
+These kernels $k$ and $l$ each describe how similarity is measured within their respective domains $\mathcal{X}$ and $\mathcal{Y}$, and are symmetric and positive definite such that they uniquely define the RKHS $\mathcal{H}_{k}$ and $\mathcal{H}_{l}$.
 We then define $\mathcal{U}_{Y | X} := C_{YX} C_{XX}^{-1}$ where $C_{YX} := \mathbb{E}[l(Y, \cdot) \otimes k(X, \cdot)]$ and $C_{XX} := \mathbb{E}[k(X, \cdot) \otimes k(X, \cdot)]$ \citep{song2009hilbert}.
@@
 	\end{equation}
-	That is, indicator functions $\mathbb{1}_{c} = \delta(c, \cdot)$, $c \in \mathbb{N}_{m}$ are simply the canonical kernel features of $\mathcal{H}_{\delta}$.
-
-	While such properties does not necessarily hold for continuous domains in general, this convenient property in the case of a discrete domain $\mathcal{Y}$ with a Kronecker delta kernel $\delta$ is what allows consistent estimations of decision probabilities used in multiclass classification, which we turn to next.
+	That is, indicator functions $\mathbb{1}_{c} = \delta(c, \cdot)$, $c \in \mathbb{N}_{m}$, are simply the canonical kernel features of $\mathcal{H}_{\delta}$.
+Such properties do not necessarily hold for continuous domains in general.
+This convenient property in the case of a discrete domain $\mathcal{Y}$ with a Kronecker delta kernel $\delta$ is what allows consistent estimations of decision probabilities used in multiclass classification, which we turn to next.
 
@@
 	where $\bvec{Y} := \begin{bmatrix} \bvec{1}_{1} & \bvec{1}_{2} & \cdots & \bvec{1}_{m} \end{bmatrix} \in \{0, 1\}^{n \times m}$ is simply the one hot encoded labels $\{y_{i}\}_{i = 1}^{n}$.
-
-	We proceed to prove that the empirical decision probabilities \eqref{eq:empirical_decision_probability} converges to the true decision probabilities.
-In fact, the inference distribution \eqref{eq:empirical_decision_probability_vector} is equivalent to a conditional embedding.
+The kernel embedding classifier is thus the multi-valued decision function $\bvec{f}(x)$ \eqref{eq:empirical_decision_probability_vector}.
+We proceed to prove that empirical decision probabilities \eqref{eq:empirical_decision_probability} converge to the true decision probabilities.
+In fact, the inference distribution \eqref{eq:empirical_decision_probability_vector} is equivalent to the empirical conditional embedding.
 	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
@@
 	\end{theorem}
-	While decision probability estimates \eqref{eq:empirical_decision_probability} do not necessarily form a normalised distribution for finite $n$, \cref{thm:probability_convergence_copy} guarantees that they approach one with increasing sample sizes.
+	While decision probability estimates \eqref{eq:empirical_decision_probability} do not necessarily form a normalised distribution for finite $n$, \cref{thm:probability_convergence_copy} guarantees that they approach one with increasing sample size.
 When normalised distributions are required, distribution estimates \eqref{eq:empirical_decision_probability} can be clip-normalised,
@@
 
-	Kernel embedding classifiers are equivalent to a conditional embedding with a discrete target space $\mathcal{Y}$.
-Hyperparameter learning for conditional embeddings is particularly difficult compared to joint embeddings, since the kernel $\{k_{\theta} : \theta \in \Theta\}$ is to be learned jointly with a regularisation parameter $\lambda \in \Lambda = \mathbb{R}_{+}$.
+	Kernel embedding classifiers \eqref{eq:empirical_decision_probability} are equivalent to a conditional embedding with a discrete target space $\mathcal{Y}$.
+Hyperparameter learning for conditional embeddings is particularly difficult compared to joint embeddings, since the kernel $k_{\theta}$ with parameters $\theta \in \Theta$ is to be learned jointly with a regularisation parameter $\lambda \in \Lambda = \mathbb{R}_{+}$.
 While the conditional embedding map $\hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the operator $\mathcal{U}$ that minimises the regularised least squares loss $\frac{1}{n} \sum_{i = 1}^{n} \| \psi(y_{i}) - \mathcal{U} \phi(x_{i}) \|_{\mathcal{H}_{l}}^{2} + \lambda \| \mathcal{U} \|_{HS}$ in the RKHS \citep{song2013kernel}, minimising this loss directly over $\theta \in \Theta, \lambda \in \Lambda$ for $\mathcal{U} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X}$ would trivially result in an overfitted model with $\lambda \rightarrow 0$.
@@
 Under this loss, we prove that the expected risk for the kernel embedding classifier $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a Rademacher complexity bound $r(\theta, \lambda)$ with high probability.
-%We refer the reader to the supplementary material for detailed proof.
 
@@
 
-	We refer the read to appendix B for proof.
+	We refer the reader to appendix B for proof.
 In order for the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} to be non-trivial, we focus on bounded kernels in the sense that $\alpha^{2}(\theta) := \sup_{x \in \mathcal{X}} k_{\theta}(x, x) < \infty$.
@@
 
-	% , is general for any conditional embedding with discrete target space given any family of positive definite kernels $k_{\theta}$ over $\theta \in \Theta$ and $\lambda \in \Lambda$
 	Our learning algorithm does not restrict the way the kernel $k_{\theta}$ is constructed from its parameters $\theta \in \Theta$.
-One particularly useful class of kernels are linear kernels with neural network features, in which the kernel $k(x, x') = \langle \varphi(x), \varphi(x') \rangle$ is constructed from neural networks $\varphi : \mathcal{X} \to \mathbb{R}^{p}$ explicitly.
+One particularly useful class of kernels are those with explicit neural network features, in which the kernel $k(x, x') = \langle \varphi(x), \varphi(x') \rangle$ is constructed from neural networks $\varphi : \mathcal{X} \to \mathbb{R}^{p}$ explicitly.
 Neural networks are typically defined by weights and biases of its hidden layers, which collectively define the parameters of the constructed kernel, and are thus trainable under our learning algorithm.
@@
 We see that the Rademacher complexity bound (RCB) $r(\theta, \lambda)$ appropriately measures the amount of overfitting with $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = 4.33$ and $r(\alpha_{u}, \ell_{u}), \lambda_{u}) = 0.31$.
-We then learn model hyperparameters with \cref{alg:kernel_embedding_classifier_training} for 500 iterations from both initialisations at rate $\eta = 0.01$, where both models converges to a balanced model with appropriate complexity bounds $r((\alpha_{o}, \ell_{o}) = (0.01, 0.24), \lambda_{o} = 8.62 \times 10^{-7}) = 2.23 \approx 2.14 = r((\alpha_{u}, \ell_{u}) = (5.1, 0.24), \lambda_{u} = 0.20)$ and an improved test accuracy of 73.33\%.
+We then learn model hyperparameters with \cref{alg:kernel_embedding_classifier_training} for 500 iterations from both initialisations at rate $\eta = 0.01$, where both models converges to a balanced model with appropriate complexity bounds $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = r((0.01, 0.24), 8.62 \times 10^{-7}) = 2.23 \approx 2.14 = r((\alpha_{u}, \ell_{u}), \lambda_{u}) = r((5.1, 0.24), 0.20)$ and an improved test accuracy of 73.33\%.
 In particular, the initially overfitted model learns a simpler model at the expense of lower training performance, emphasising the benefits of complexity based regularisation, without which the learning would only maximise training performance at the cost of further overfitting.
@@
 		Furthermore, while \cref{fig:iris} shows that the model has converged for all performance measures, including complexity bounds, decision probabilities, and accuracy or loss on both training and test sets, the learned hyperparameters $((\alpha, \ell), \lambda)$ themselves differ for different initialisations.
-For a Gaussian or similarly stationary kernel, we have that $r((\sigma_{f}, \ell), \lambda) = r((1, \ell), \lambda \sigma^{-2}_{f})$, so the bound $r$ is only interested in the quantities $\lambda \sigma^{-2}_{f}$ and $\ell$.
+For a Gaussian kernel, we have that $r((\sigma_{f}, \ell), \lambda) = r((1, \ell), \lambda \sigma^{-2}_{f})$ for $\alpha(\theta) = \sigma_{f}$, so the bound $r$ is only interested in the quantities $\lambda \sigma^{-2}_{f}$ and $\ell$.
 Indeed, in our example above, $\lambda_{o} \alpha_{o}^{-2} = 0.0086 \approx 0.0075 = \lambda_{u} \alpha_{u}^{-2}$ and $\ell_{o} = 0.24 = \ell_{u}$ after learning.
@@
 		\begin{table}[t]
-			\caption{Classification Accuracy (\%) of Gaussian and Neural Network KEC on UCI datasets}
+			\caption{Classification Accuracy (\%) of Kernel Embedding Classifiers on UCI datasets}
 			\label{tab:stationary_experiments}
@@
 
-		We demonstrate the average performance of learning anisotropic Gaussian kernels and fully connected neural network kernels under the kernel embedding classification framework on standard UCI datasets, summarised in \cref{tab:stationary_experiments}.
+		We demonstrate the average performance of learning anisotropic Gaussian kernels and kernels with explicit neural network features on standard UCI datasets \citep{merz1998uci}, summarised in \cref{tab:stationary_experiments}.
 The former has a shallow but wide model architecture, while the latter has a deeper but narrower model architecture.
 
-		The Gaussian kernel is learned using both full gradient update (GKEC) and the scalable batch stochastic gradient update (GKEC-SGD) using a tenth ($n_{b} \approx \frac{n}{10}$) of the training set each time, with sensitivity and length scales initialised to $1$.
-For neural network kernels, we randomly select two simple fully connected architectures with 16-32-8 (NNKEC-1) and 96-32 (NNKEC-2) hidden units respectively, and learn the corresponding kernel without dropout under ReLU activation.
-Weight parameters are initialised from a truncated normal distribution with standard deviation $0.1$, while biases are initialised to $0.1$, and are to be trained with full gradient updates.
+		The Gaussian kernel is learned with both full (GKEC) and batch stochastic gradient updates (GKEC-SGD) using a tenth ($n_{b} \approx \frac{n}{10}$) of the training set each training iteration, with sensitivity and length scales initialised to $1$.
+For explicit kernels with neural network features, we randomly select two simple fully connected architectures with 16-32-8 (NNKEC-1) and 96-32 (NNKEC-2) hidden units respectively, and learn the corresponding kernel without dropout under ReLU activation.
+Biases are initialised to $0.1$ while weight parameters are initialised from a truncated normal distribution with standard deviation $0.1$, and are to be trained with full gradient updates.
 For all experiments, regularisation parameter $\lambda$ is initialised to $1$ and is learned jointly with the kernel.
 Classifiers are trained with the Adam optimiser \citep{kingma2014adam} in TensorFlow \citep{abadi2016tensorflow} with a learning rate of $\eta = 0.1$ and $\epsilon = 10^{-15}$ under the learning objective $q(\theta, \lambda)$.
-Training is ran for 1000 or 10000 iterations when using full or batch stochastic gradient updates respectively, regardless of training convergence.
+Training is ran for 1000 or 10000 iterations when using full or batch gradient updates respectively, regardless of training convergence.
 All datasets are scaled so that all attributes are in the unit range.
-Each classifier is trained on 9 out of 10 folds and tested on the remaining fold.
-The folds are shuffled over all 10 combinations to obtain the average test accuracy.
+Each classifier is trained on 9 out of 10 folds and tested on the remaining fold, which are shuffled over all 10 combinations to obtain the average test accuracy.
 We compare our results to other approaches using neural networks \citep[a; c]{kaya2016banknote, freire2009short}, probabilistic binary trees \citep[b]{horton1996probabilistic}, decision trees \citep[d]{zhou2004size}, and regularised discriminant analysis \citep[e]{aeberhard1992comparison}.
-These numbers are only illustrative, however, in that different authors may have used different data pre-processing, test folds, optimiser, learning rate, architecture (for neural nets), and training time.
-\Cref{tab:stationary_experiments} shows that our learning algorithm achieves similar performance to other approaches without any special tuning or heuristics by simply placing a conditional embedding on training data and applying a complexity bound based learning algorithm.
-The SGD approach for Gaussian kernels performs similarly to the full gradient approach, verifying the claim of \cref{thm:expected_risk_bound_hyperparameter_learning_copy} for any $n$.
-For neural network kernels, we did not attempt to choose an optimal architecture for any dataset.
+However, these approaches may have used different data pre-processing, test folds, optimiser, learning rate, architecture (for neural nets), and training time.
+Comparisons are thus only illustrative.
+\Cref{tab:stationary_experiments} shows that our learning algorithm achieves similar performance to other approaches without any special tuning or heuristics, but by simply placing a conditional embedding on training data and applying a complexity bound based learning algorithm.
+The SGD approach for Gaussian kernels performs similarly to the full gradient approach, verifying the claim of \cref{thm:expected_risk_bound_hyperparameter_learning_copy} for $n = n_{b}$.
+For neural network features, we did not attempt to choose an optimal architecture for each dataset.
 The learning algorithm is to train the same simple untrained network for different datasets under only 1000 iterations, and still generates comparable performance.
@@
 
-		83.7\% with only 500 data points
+%		83.7\% with only 500 data points
 
@@
 %
+
+	- original convolutional neural network uses 1e-2 learning rate as well under cross entropy loss so we use the same learning rate
+	- we also use sgd batches of 6000 for that network
+	- for 10000 iterations, we obtain 99.5+, they get 99.2
+	- unlike the uci examples, this time we use a architecture that aligns more with the specific dataset, and thus achieves outstanding performance
+	- we initialise regularisation parameter to 10
+
 \section{Conclusion}
-
-	\note{Summarise main contribution.}
 
@@
 
+\newpage
 \bibliographystyle{apalike}
@@
 
-	In this section we provide a few theorems, lemmas, and derivations which proves the convergence properties of estimators derived from our kernel embedding classifier.
+	In this section we provide theorems, lemmas, and derivations for the convergence properties of the kernel embedding classifier.
 
@@
 However, one should keep in mind that $\hat{f}$ is estimated using the dataset $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ and is thus random over the possible data observation events $\omega \in \Omega$.
-We would like to provide a sense of the stochastic convergence of $\hat{f}$ to $f$ by providing an upper bound of their absolute pointwise difference $| \hat{f}(x) - f(x) |$ which we know convergences to zero at some stochastic rate.
-Since the kernel embedding classifier is based on conditional embeddings, this upper bound will be provided by the RKHS norm of the error between empirical and true conditional embeddings.
+We would like to provide a sense of the stochastic convergence of $\hat{f}$ to $f$ by providing an upper bound of their absolute pointwise difference $| \hat{f}(x) - f(x) |$, and show that such an upper bound converges to zero at some stochastic rate.
+Since the kernel embedding classifier is based on conditional embeddings (and, as we will show, is equivalent to a conditional embedding), this upper bound will be provided by the RKHS norm of the error between empirical and true conditional embeddings.
 Specifically, the empirical conditional embedding stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \cite[Theorem 6]{song2009hilbert}.
 That is,
-
 	\begin{equation}
@@
 	\end{equation}
-
 	\begin{theorem}[Pointwise and Uniform Convergence of Estimators based on Conditional Embeddings]
@@
 		Suppose that $k(x, \cdot)$ is in the image of $C_{XX}$ and that there exists $0 \leq \gamma(x) < \infty$ such that for some estimator function $\hat{f} : \mathcal{X} \to \mathbb{R}$ and target function  $f : \mathcal{X} \to \mathbb{R}$,
-
 		\begin{equation}
@@
 		\end{equation}
-
 		then the estimator $\hat{f}$ converges pointwise to the target $f$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
@@
 			Suppose that there exists $0 \leq \gamma(x) < \infty$ such that \eqref{eq:estimator_error_bound} is satisfied.
-Note that this statement holds for all possible datasets represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$.
-Thus, for any constant $C$, the implication statement $\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C \implies | \hat{f}(x) - f(x) | \leq C \gamma(x)$ holds for all possible data observation events $\omega \in \Omega$.
+That is, the inequality \eqref{eq:estimator_error_bound} holds for all possible data observations $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$.
+For any constant $C$, the implication statement $\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C \implies | \hat{f}(x) - f(x) | \leq C \gamma(x)$ holds for all possible observation events $\omega \in \Omega$.
 Writing this explicitly in event space translates this to a probability statement,
-
 			\begin{equation}
@@
 			\end{equation}
-
 			Since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is valid.
 By letting $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ in \eqref{eq:probability_statement}, we immediately have that the probability inequality in statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is also true if we replace $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|$ with $| \hat{f}(x) - f(x) |$ and $M_{\epsilon}$ with $\gamma(x) M_{\epsilon}$,
-
 			\begin{equation}
@@
 			\end{equation}
-
 			where we employed statement \eqref{eq:probability_statement} between the third and fourth line for $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
 Therefore, since $M_{\epsilon}$ is arbitrary, define $\tilde{M}_{\epsilon}(x) := \gamma(x) M_{\epsilon}$ so that, with the above result, the statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} implies the following,
-
 			\begin{equation}
@@
 			\end{equation}
-
 			In other words, the function $\hat{f}$ stochastically converges pointwise to $f$ with a rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
@@
 		\begin{proof}
+
 			Consider the pointwise absolute difference between the decision probability and its empirical estimate,
-
 			\begin{equation}
@@
 			\end{equation}
-
-			where the last inequality follows from the Cauchy–Schwarz inequality in a Hilbert space.
+			where the last inequality follows from the Cauchy Schwarz inequality in a Hilbert space.
 
 			From \eqref{eq:indicator_function}, since $\mathbb{1}_{c} = \delta(c, \cdot)$ and using the fact that $\delta$ is a reproducing kernel, we have that for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-
 			\begin{equation}
@@
 			\end{equation}
-
 			Therefore, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, $\hat{p}_{c}$ converges uniformly to $p_{c}$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
@@
 This immediately implies that inner products in this space are simply the usual dot products in a Euclidean space, since
-
 	\begin{equation}
@@
 	\end{equation}
-
 	Consequently, the RKHS norm for bounded functions $g \in \mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of its vector representation $\bvec{g}$,
-
 	\begin{equation}
@@
 	\end{equation}
-
 	A special and convenient result that arises due to this discrete and finite label space is that the decision probabilities and its empirical estimate are simply the conditional embeddings and its empirical estimate.
 
-	\begin{claim}[Decision Probabilities are Conditional Embeddings]
+	\begin{lemma}[Decision Probabilities are Conditional Embeddings]
 	\label{thm:probability_is_embedding}
@@
 		The decision probability for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,
-
 		\begin{equation}
@@
 		\end{equation}
-
-		\begin{proof} Since indicator functions are the canonical features of the label RKHS $\mathcal{H}_{\delta}$, we employ the fact that expectations of indicator functions are probabilities to prove this claim,
-
+		Therefore, $\bvec{p}(x) \equiv \mu_{Y | X = x}$.
+
+		\begin{proof}
+
+			Since indicator functions are the canonical features of the label RKHS $\mathcal{H}_{\delta}$, we employ the fact that expectations of indicator functions are probabilities to prove this claim,
 			\begin{equation}
@@
 				=& \mathbb{E}[\mathbb{1}_{c}(Y) | X = x] = \mathbb{P}[Y \in \{c\} | X = x] \\
-				=& \mathbb{P}[Y = c | X = x] := p_{c}(x).
+				=& \mathbb{P}[Y = c | X = x] =: p_{c}(x).
 			\end{aligned}
@@
 
-	\end{claim}
-
-	\begin{claim}[Empirical Decision Probabilities are Empirical Conditional Embeddings]
+	\end{lemma}
+
+	\begin{lemma}[Empirical Decision Probabilities are Empirical Conditional Embeddings]
 	\label{thm:empirical_probability_is_embedding}
@@
 		The empirical decision probability \eqref{eq:empirical_decision_probability} for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the empirical conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,
-
 		\begin{equation}
@@
 		\end{equation}
-
 		Therefore, $\hat{\bvec{p}}(x) \equiv \hat{\mu}_{Y | X = x}$.
@@
 			Let the canonical feature maps of $\mathcal{X}$ and $\mathcal{Y}$ be $\phi(x) = k(x, \cdot)$ and $\psi(y) = l(y, \cdot) = \delta(y, \cdot)$, then the empirical conditional embedding is defined by
-
-			\begin{equation}
-				\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} \phi(x)
-			\end{equation}
-
+			\begin{equation}
+				\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} \phi(x).
+			\end{equation}
 			By the reproducing property, the evaluation of $\hat{\mu}_{Y | X = x} \in \mathcal{H}_{l}$ is given by a dot product,
-
 			\begin{equation}
@@
 			\end{equation}
-
 			where $\bvec{l}_{c} := \{l(y_{i}, c)\}_{i = 1}^{n}$ and $\bvec{k}_{x} := \{k(x_{i}, x)\}_{i = 1}^{n}$.
 While the notation $\bvec{l}_{c}$ is usually avoided due do its similarity to $\bvec{1}_{c}$, in this context they happen to represent equal quantities,
-
 			\begin{equation}
@@
 			\end{equation}
-
 			The claim then immediately follows by the definition of our decision probability estimator,
-
 			\begin{equation}
@@
 
-	\end{claim}
+	\end{lemma}
+
+	\Cref{thm:empirical_probability_is_embedding} shows that the decision function $\bvec{f}(x)$ \eqref{eq:empirical_decision_probability_vector} of a kernel embedding classifier is no more than the empirical conditional embedding estimated from the data.
 
@@
 
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability vector function $\hat{\bvec{p}} : \mathcal{X} \to \mathbb{R}^{m}$ \eqref{eq:empirical_decision_probability_vector} converges uniformly to the true decision probability vector function $\bvec{p} : \mathcal{X} \to [0, 1]^{m}$ in the $\ell_{2}$-norm, where $\bvec{p}(x) := \{p_{c}(x)\}_{c = 1}^{m}$, at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability vector function $\hat{\bvec{p}} : \mathcal{X} \to \mathbb{R}^{m}$ \eqref{eq:empirical_decision_probability_vector} converges uniformly to the true decision probability vector function $\bvec{p} : \mathcal{X} \to [0, 1]^{m}$ in the $\ell_{1}$-norm and $\ell_{2}$-norm, where $\bvec{p}(x) := \{p_{c}(x)\}_{c = 1}^{m}$, at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
 
@@
 More formally, from \eqref{eq:decision_probability_error_upper_bound} and \eqref{eq:indicator_rkhs_norm}, the $\ell_{1}$-norm of the difference can be bounded,
-
 			\begin{equation}
@@
 			\end{equation}
-
 			Therefore, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = m$ independent of $x \in \mathcal{X}$, we have uniform convergence in $\ell_{1}$ where we replace all instances of $| \hat{f}(x) - f(x) |$ in the proof of \cref{thm:pointwise_uniform_convergence} with ${\lVert \hat{\bvec{p}}(x) - \bvec{p}(x) \rVert}_{\ell_{1}}$.
 
-			For convergence in $\ell_{2}$, we show that the $\ell_{2}$-norm of the difference between the true and empirical decision probability vector functions is the same as the RKHS norm of the difference between the true and empirical conditional embedding, which converges to zero at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $x \in \mathcal{X}$ and $c \in \mathcal{Y} = \mathbb{N}_{m}$ \citep{song2009hilbert}.
+			For convergence in $\ell_{2}$, we show that the $\ell_{2}$-norm of the difference between the true and empirical decision probability vector functions is the same as the RKHS norm of the difference between the true and empirical conditional embedding, which converges to zero at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $x \in \mathcal{X}$ and $c \in \mathcal{Y} = \mathbb{N}_{m}$ by \eqref{eq:empirical_conditional_embedding_stochastic_convergence}.
 To this end, we use \cref{thm:probability_is_embedding} and \cref{thm:empirical_probability_is_embedding} and write
-
 			\begin{equation}
@@
 			\end{equation}
-
 			where the last equality comes from \eqref{eq:rkhs_norm_is_l2_norm} and the fact that the empirical and true conditional embeddings are bounded functions in the RKHS.
@@
 
-		Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information \footnote{Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$.},
+		Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information,
 		\begin{equation}
@@
 		where $u_{x}(y) := - \log{\mathbb{P}[Y = y | X = x]}$ is the \textit{information} (in nats) we would gain when we discover that example $x$ actually has label $y$.
+Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$.
 If $u_{x} : \mathbb{N}_{m} \to \mathbb{R}$ is in the RKHS $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by $\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle$.
@@
 		Unfortunately, $u_{x}$ is not known exactly, since $\mathbb{P}[Y = y | X = x]$ is not known exactly.
-Instead, since $\hat{p}_{c}(x)$ is a consistent estimate for $\mathbb{P}[Y = c | X = x]$ by \cref{thm:probability_convergence}, we propose to replace $u_{x}(y)$ with the negative log of $\hat{p}_{y}(x)$.
+Instead, since $\hat{p}_{c}(x)$ is a consistent estimate for $\mathbb{P}[Y = c | X = x]$ by \cref{thm:probability_convergence}, we propose to replace $u_{x}(y)$ with the information of $\hat{p}_{y}(x)$.
 However, we cannot simply take the log of this estimator, as $\hat{p}_{y}(x)$ may produce non-positive estimates to the prediction probabilities.
 The straight forward way to mitigate this problem is to clip $\hat{p}_{y}(x)$ from the bottom by a very small number, before taking the log.
-However, experiments show that this produces non-smooth estimates over $\mathcal{X}$ and the degree of smoothness varies drastically between different choices of that small number (see \cref{app:design_choices}).
+However, experiments show that this produces non-smooth estimates over $\mathcal{X}$ and the degree of smoothness varies drastically between different choices of that small number.
 Instead, in virtue of the fact that $\lim_{p \to 0} - p \log{p} = 0$ even though $\lim_{p \to 0} - \log{p} = \infty$, we simply define the information estimate $\hat{u}_{x}(y)$ as zero if the empirical decision probability is non-positive,
@@
 				Consider the pointwise absolute difference between the empirical and true information entropy,
-
 				\begin{equation}
@@
 				\end{equation}
-
-				where the we used the triangle inequality and Cauchy–Schwarz inequality in a Hilbert space respectively.
-
-				Now, since $l = \delta$ is bounded, so is $\hat{\mu}_{Y | X = x}(c) = \sum_{i = 1}^{n} w_{i} \delta(y_{i}, c)$ for some embedding weights $w_{i}$ and all $c \in \mathbb{N}_{m}$, and thus its RKHS norm is finite for all $n \in \mathbb{N}_{n}$.
+				where the we used the triangle inequality and Cauchy Schwarz inequality in a Hilbert space respectively.
+Since $l = \delta$ is bounded, so is $\hat{\mu}_{Y | X = x}(c) = \sum_{i = 1}^{n} w_{i} \delta(y_{i}, c)$ for some embedding weights $w_{i}$ and all $c \in \mathbb{N}_{m}$, and thus its RKHS norm is finite for all $n \in \mathbb{N}_{n}$.
 Similarly, assuming that $p_{c}(x)$ is never exactly zero, $u_{x}(c)$ is also finite for all $c \in \mathbb{N}_{m}$ and thus so is its RKHS norm.
-We already know that $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$ stochastically converges to zero at the rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ \citep[Theorem 6]{song2009hilbert}.
+We already know that $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$ stochastically converges to zero at the rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ \eqref{eq:empirical_conditional_embedding_stochastic_convergence}.
 Thus, it remains to bound $\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}}$ by a multiple of $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$.
@@
 				To this end, we first use \cref{thm:probability_is_embedding} and \cref{thm:empirical_probability_is_embedding} and to express the theoretical and empirical information as the negative log of the embedding, so that it is explicitly written as a function of $c \in \mathcal{Y}$ in $\mathcal{H}_{\delta}$ indexed by $x \in \mathcal{X}$,
-
 				\begin{equation}
@@
 				\end{equation}
-
 				Since $\log$ is a concave function, we have the property that $\log{a} - \log{b} \leq \frac{1}{b} (a - b)$.
 This allows us to bound $| \hat{u}_{x}(c) - u_{x}(c) |$ by $| \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |$ for all $c \in \mathbb{N}_{m}$,
-
 				\begin{equation}
@@
 						&\leq \frac{1}{| \mu_{Y | X = x}(c) |} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) | \\
-					&= \alpha_{x} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |,
-				\end{aligned}
-				\end{equation}
-
-				where we define $\alpha_{x} := \max_{c \in \mathbb{N}_{m}} \frac{1}{| \mu_{Y | X = x}(c) |}$.
+						&\leq \alpha_{x} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |,
+					\end{aligned}
+				\end{equation}
+				where we define $\alpha_{x} := \max_{c \in \mathbb{N}_{m}} \frac{1}{| \mu_{Y | X = x}(c) |}$, which is well defined as the conditional embedding is bounded.
 Since the RKHS norm of bounded functions in $\mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of their vector representations \eqref{eq:rkhs_norm_is_l2_norm}, we have
-
 				\begin{equation}
@@
 				\end{equation}
-
 				Therefore, $\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}} \leq \alpha_{x} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$, and \eqref{eq:information_entropy_bound} becomes
-
 				\begin{equation}
@@
 				\end{equation}
-
 				Hence, with $\gamma(x) = \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| u_{x} \|_{\mathcal{H}_{\delta}}$, \cref{thm:pointwise_uniform_convergence} implies that $\hat{h}$ converges pointwise to $h$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
@@
 
-	In this section we derive the Rademacher complexity bound of the kernel embedding classifier, and show that it can be used in conjunction with the training loss to bound the expected risk with high probability.
+	In this section we derive Rademacher complexity bounds for kernel embedding classifiers, and show that it can be used in conjunction with cross entropy loss to bound the expected risk with high probability.
 
@@
 
-		\begin{theorem}[Rademacher Complexity Bound for the Kernel Embedding Classifier]
+		\begin{theorem}[Rademacher Complexity Bound for Kernel Embedding Classifiers]
 		\label{thm:rademacher_complexity_bound}
@@
 			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
-Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}} = k_{\theta}(x, x) \leq \alpha^{2}$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
+Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$, $\alpha > 0$, is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
 For any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of kernel embedding classifiers $F_{n}(\Theta, \Lambda)$ \eqref{eq:predictor_class} defined over $\theta \in \Theta, \lambda \in \Lambda$ is bounded by
@@
 
-				where $\sigma_{i}$ are \textit{iid} Rademacher random variables, taking values in $\{-1, 1\}$ with equal probability, and $X_{i}$ are \textit{iid} random variables from the same distribution $\mathbb{P}_{X}$ of our training data.
+				where $\sigma_{i}$ are \textit{iid} Rademacher random variables, taking values in $\{-1, 1\}$ with equal probability, and $X_{i}$ are \textit{iid} random variables from the same distribution $\mathbb{P}_{X}$ as our training data.
 We further define $\bm{\sigma} := \{\sigma_{i}\}_{i = 1}^{n}$.
@@
 
-		\Cref{thm:rademacher_complexity_stationary_kernels_bound} motivates the choice $\alpha^{2}(\tilde{\theta}) = k_{\tilde{\theta}}(0, 0) = \sigma_{f}^{2}$ for stationary radial basis type kernels such as the Gaussian or Mat\'{e}rn kernels, where $\sigma_{f}$ is the sensitivity \citep{rasmussen2006gaussian} of the stationary kernel, which we employ in \cref{alg:kernel_embedding_classifier_training} when the kernel is stationary.
+		\Cref{thm:rademacher_complexity_stationary_kernels_bound} motivates the choice $\alpha^{2}(\theta) = k_{\theta}(0, 0) = \sigma_{f}^{2}$ for stationary radial basis type kernels such as the Gaussian or Mat\'{e}rn kernels, where $\sigma_{f}$ is the sensitivity \citep{rasmussen2006gaussian} of the stationary kernel, which we employ in \cref{alg:kernel_embedding_classifier_training} when the kernel is stationary.
 
@@
 
-		In order to quantify the performance of the kernel embedding classifier, we specify a loss function $\mathcal{L} : \mathcal{Y} \times \mathcal{A} \to [0, \infty)$, where $\mathcal{L}(y, f(x))$ measures the loss of a decision function $f : \mathcal{X} \to \mathcal{A}$ on a paired example $x \in \mathcal{X}$ and $y \in \mathcal{Y}$.
+		In order to quantify the performance of the kernel embedding classifier, we specify a loss function $\mathcal{L} : \mathcal{Y} \times \mathcal{A} \to [0, \infty)$, where $\mathcal{L}(y, f(x))$ measures the loss of a decision function $f : \mathcal{X} \to \mathcal{A}$ on a paired example $x \in \mathcal{X}$ and label $y \in \mathcal{Y}$.
 In the kernel embedding classification context, the decision function is $\bvec{f}_{\theta, \lambda} : \mathcal{X} \to \mathbb{R}^{m}$, with $\mathcal{A} = \mathbb{R}^{m}$ and $\mathcal{Y} = \mathbb{N}_{m}$.
@@
 			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
-Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}} = k_{\theta}(x, x) \leq \alpha^{2}$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
+Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$, $\alpha > 0$, is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
 For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
@@
 			\begin{proof}
-				The claim is a direct consequence of \cref{thm:rademacher_complexity_bound} and \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss}.
+				From \cref{thm:rademacher_complexity_bound}, we have $\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) \leq 2 \alpha \rho$.
+Further, from \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss}, we have $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 2 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$.
+These are both deterministic inequalities, leading to $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 4 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \alpha \rho$.
+We then apply this inequality to \cref{thm:expected_normalised_cross_entropy_loss_bound}, which proves the claim.
+
 			\end{proof}
@@
 The second term is a model complexity or regularisation term, which measures how complicated the model is.
-In this case, the model complexity is measured by the Rademacher complexity, which captures the expressiveness of the function class by quantifying how well the function class is able to shatter pure noise.
+In this case, the model complexity is measured by the Rademacher complexity, which captures the expressiveness of the function class by quantifying how well the function class is able to shatter noise.
 The third term is a statistical constant which plays no specific role to the function class.
@@
 
-		Therefore, we propose to choose $\epsilon = e^{-1}$, and then replace replace $\mathcal{L}_{e^{-1}}$ with $\mathcal{L}_{\epsilon}$ for some new generic $\epsilon \in (0, e^{-1})$ much smaller than $e^{-1}$.
+		Therefore, we propose to choose $\epsilon = e^{-1}$, and then replace replace $\mathcal{L}_{e^{-1}}$ with $\mathcal{L}_{\epsilon}$ for some new generic $\epsilon \in (0, e^{-1})$ much smaller than $e^{-1}$ on the training loss terms.
 In this way, we still maintain an upper bound for the training loss term.
-While this bound would not necessarily be tight for high training losses, the gradients from the high training loss would drive the system to a lower training loss, where the bound would become tight again.
+While this bound would not necessarily be tight for high training losses, the gradients from the high training loss would drive the system to a lower training loss, where the bound would become tight again as equality holds in \eqref{eq:loss_inequality} whenever $f_{y}(x) \geq e^{-1}$.
 
@@
 			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
-Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}} = k_{\theta}(x, x) \leq \alpha^{2}$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
+Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
 For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
@@
 			\begin{proof}
-				The claim is a direct consequence of applying \cref{thm:expected_loss_bound_for_kec} with $\epsilon = e^{-1}$, and using \eqref{eq:loss_inequality} to further bound each of the cross entropy loss terms that has a clip factor $\epsilon = e^{-1}$ with the corresponding cross entropy loss term that has a generic clip factor $\epsilon \in (0, e^{-1})$ again.
 
@@
 
-		Clearly, this subset is non-empty, since $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ it itself an element of this subset.
+		Clearly, this subset is non-empty, since $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ is itself an element of this subset.
 Note that $\alpha : \Theta \to \mathbb{R}_{+}$ must necessarily exist as the kernel family $k_{\theta}$ is assumed to be bounded over the domain $\mathcal{X}$.
@@
 
-		Thus, we can assert that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ is bounded for all $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, and that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}} = k_{\theta}(x, x) \leq \alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$ is bounded in RKHS norm for all $x \in \mathcal{X}, (\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$.
+		Thus, we can assert that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ is bounded for all $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, and that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$ is bounded in RKHS norm for all $x \in \mathcal{X}, (\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$.
 By \cref{thm:specific_expected_loss_bound_for_kec}, we can now claim the following.
@@
 			\begin{proof}
-				This result is a direct consequence of applying \cref{thm:specific_expected_loss_bound_for_kec} with the choice of $\rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ and $\alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$.
-The inequality \eqref{eq:specific_expected_loss_bound_for_kec} then only holds for a subset of kernel parameter and regularisation $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ as defined by \eqref{eq:hyperparameter_subset_definition}.
+				We first apply \cref{thm:specific_expected_loss_bound_for_kec} with the choice of $\rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ and $\alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$.
+The inequality \eqref{eq:specific_expected_loss_bound_for_kec} then only holds for a subset of kernel parameters and regularisations $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ as defined by \eqref{eq:hyperparameter_subset_definition}.
 			\end{proof}
@@
 			\begin{proof}
-				This result is a direct consequence of applying \cref{thm:general_expected_risk_bound_hyperparameter_learning} with the choice of $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
+				We first apply \cref{thm:general_expected_risk_bound_hyperparameter_learning} with the choice of $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
 We then replace the notation $\tilde{\theta} \rightarrow \theta$ and $\tilde{\lambda} \rightarrow \lambda$ back to avoid cluttered notation.
@@
 	For a kernel embedding classifier, the modelling lies in the choice of the kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ over the input space $\mathcal{X}$.
-The only requirement for the kernel $k$ is that it is symmetric and positive definite.
-In some cases, positive semi-definite kernels also suffice.
-There are no other requirements, and thus we may construct richer and more expressive kernel families in any way we prefer, subject to those requirements.
-Once such a kernel family is constructed, the kernel parameters $\theta$, as well as the regularisation parameter $\lambda$, can be learned effectively using the training algorithm described in \cref{sec:hyperparameter_learning}.
+The only requirement for the kernel $k$ is that it is symmetric and positive definite, and thus we may construct richer and more expressive kernel families in any way subject to such requirements.
+Once such a kernel family is constructed, the kernel parameters $\theta$, as well as the regularisation parameter $\lambda$, can be learned effectively using the learning algorithm described in \cref{sec:hyperparameter_learning}.
 
@@
 We can then construct the kernel family by incorporating such structural representations into the kernel.
-Even better, we can construct the kernel family so that it is capable or learning such structural representations by itself.
+Even better, we can construct the kernel family so that it is capable or learning such structural representations by itself, by parametrising such representations into the kernel.
 
@@
 This construction allows the incorporation of trainable domain specific structures and enables scalability to larger datasets.
-We first begin by introducing the linear kernel embedding classifier (Linear KEC) in \cref{app:linear_kernel_embedding_classifier}, where explicit feature maps can be learned while enabling scalability to larger datasets.
-We then construct the deep nonlinear kernel embedding network (Deep Nonlinear KEN) in \cref{app:deep_kernel_embeddings}, where the kernel family is formed from multiple layers of learned representations before a simpler yet potentially nonlinear kernel encodes their similarity for inference.
-Finally, we marry both constructions into the deep linear kernel embedding network (Deep Linear KEN) in \cref{app:deep_linear_kernel_embedding_network}, which provides a scalable and more applicable version of the deep kernel embedding network by placing a linear kernel on the last layer of the network.
+We first begin by introducing the explicit kernel embedding classifier in \cref{app:explicit_kernel_embedding_classifier}, where explicit feature maps can be learned while enabling scalability to larger datasets.
+We then construct the kernel embedding network (KEN) in \cref{app:kernel_embedding_network}, where the kernel family is formed from multiple layers of learned representations before a simpler kernel encodes their similarity for inference.
+Finally, we marry both constructions into the explicit kernel embedding network in \cref{app:explicit_kernel_embedding_network}, which provides a scalable and more applicable version of the deep kernel embedding network by placing a linear kernel on the network features.
 
@@
 				\hline
-					Nonlinear KEC & Wide & Shallow & Low & High & High or Low $d$, Low $n$ \\
-					Linear KEC & Narrow & Shallow & High & Low & Low $d$, High $n$ \\
-					Deep Nonlinear KEN &  Wide & Deep & Low & High & Structured $d$, Low $n$ \\
-					Deep Linear KEN & Narrow & Deep & High & High & Structured $d$, High $n$ \\ 
+				Implicit KEC & Wide & Shallow & Low & High & High or Low $d$, Low $n$ \\
+				Explicit KEC & Narrow & Shallow & High & Low & Low $d$, High $n$ \\
+				Implicit KEN &  Wide & Deep & Low & High & Structured $d$, Low $n$ \\
+				Explicit KEN & Narrow & Deep & High & High & Structured $d$, High $n$ \\ 
 			\end{tabular}
@@
 
-	\subsection{Linear Kernel Embedding Classifier}
-	\label{app:linear_kernel_embedding_classifier}
+	\subsection{Explicit Kernel Embedding Classifier}
+	\label{app:explicit_kernel_embedding_classifier}
 
@@
 
-		However, this elegant property is also the very reason that prevents kernel-based methods from scaling to larger datasets, as the size of such a matrix grows very quickly by $O(n^{2})$ as the dataset grows.
+		However, this elegant property is also the very reason that prevents kernel-based methods from scaling to larger datasets, as the size of such a gram matrix grows very quickly by $O(n^{2})$.
 Many kernel-based methods also require the inversion of a regularised gram matrix, which has a time complexity of $O(n^{3})$, and cannot be easily parallelised like standard matrix multiplications.
@@
 
-		In order to scale to big datasets, instead of placing a kernel over the input space directly and let it implicitly define the feature space, we explicitly define a finite dimensional feature space $\mathcal{Z} \subseteq \mathbb{R}^{p}$ of dimension $p$, where $p < n$, and place a linear kernel over it.
+		In order to scale to big datasets, instead of placing a kernel over the input space directly and let it implicitly define the feature space, we explicitly define a finite dimensional feature space $\mathcal{Z} \subseteq \mathbb{R}^{p}$ of lower dimension $p$, where $p < n$, and place a linear kernel over it.
 That is, we specify a family of explicit features maps $\varphi_{\theta} : \mathcal{X} \to \mathcal{Z}$, and place a linear kernel on top of these explicit features,
@@
 
-		By explicitly defining a finite dimensional feature space, the matrix to be inverted during both learning and inference in the kernel embedding classifier can be reduced from size $n \times n$ to size $p \times p$ by using the Woodbury matrix identity.
+		By explicitly defining a finite dimensional feature space, the matrix to be inverted during both learning and inference in the kernel embedding classifier can be reduced from size $n \times n$ to size $p \times p$ by using the Woodbury matrix inversion identity \citep{higham2002accuracy}.
 We use this identity to modify \cref{alg:kernel_embedding_classifier_training} to \cref{alg:linear_kernel_embedding_classifier_training} to exploit this computational speed up.
 
-%		\note{Choose each batch to be greater than the dimensionality of the last layer to avoid numerical instability with Cholesky Decomposition as the upper bound is not tight for small $n$ and the gradients may send it off to some unstable region instead}
-
 		However, with a fixed and finite amount of feature basis, the model becomes parametric and its flexibility is compromised.
-In other words, the model is narrow in the number of feature representations, and also shallow in the number of transformations used to define each feature.
+In other words, the model is narrow in the number of feature representations.
 We therefore turn to multi-layered feature compositions, where the flexibility of a model comes from the deep architecture instead of implicit high dimensional features.
@@
 		\begin{algorithm}[tb]
-			\caption{Linear KEC Hyperparameter Learning with Batch Stochastic Gradient Updates}
+			\caption{Explicit KEC Hyperparameter Learning with Batch Stochastic Gradient Updates}
 			\label{alg:linear_kernel_embedding_classifier_training}
@@
 
-	\subsection{Deep Kernel Embedding Network}
-	\label{app:deep_kernel_embeddings}
+	\subsection{Kernel Embedding Network}
+	\label{app:kernel_embedding_network}
 
@@
 For example, in image recognition, pixel dimensions are spatially correlated: nearby pixels are more related, and ordering between the pixel dimensions matter.
-One would expect that convolutional features \citep{lecun1998gradient} would be natural in this domain and provide a performance boost to our classifier should it be included.
+One would expect convolutional features \citep{lecun1998gradient} to be natural in this domain, and provide a performance boost to our classifier should it be included.
 In this way, we can often benefit by including domain specific structures and features into our model.
 
-		In this section, we focus on constructing kernels for which inputs $x, x' \in \mathcal{X}$ is to undergo various stages of feature transformations before such it is passed into a simpler kernel $\kappa$ which captures the similarity between the representations.
+		In this section, we focus on constructing kernels for which inputs $x, x' \in \mathcal{X}$ is to undergo various stages of feature transformations before such it is passed into a simpler kernel $\kappa$ that captures the similarity between the representations.
 Specifically, we pay particular attention to feature transformations in the form of a perceptron, so that the cumulative stages of feature transformation become the (feed-forward) multi-layer perceptron that is familiar within the neural network literature.
-Although our approach can generalise to other architectures, such as recurrent neural networks, we omit such consideration for simplicity.
 
@@
 
-		For example, in a typical multi-layer perceptron context, each layer can be written as $\varphi^{(j)}_{\theta_{j}}(x) = \sigma(W_{j} x + b_{j})$, where $W$ and $b$ are the weight and bias parameters of the layer, and $\sigma$ is an element-wise activation function, typically the rectified linear unit (ReLU) or the sigmoid.
+		For example, in a typical multi-layer perceptron context, each layer can be written as $\varphi^{(j)}_{\theta_{j}}(x) = \sigma(W_{j} x + b_{j})$, where $W_{j}$ and $b_{j}$ are the weight and bias parameters of the layer, and $\sigma$ is an element-wise activation function, typically the rectified linear unit (ReLU) or the sigmoid.
 In this case, the layer is parametrised by $\theta_{j} = \{W_{j}, b_{j}\}$.
-The setup for a feed-forward convolutional neural network is also very similar.
 
@@
 
-		In order to train the multi-layered features in an end-to-end fashion, we employ \cref{alg:kernel_embedding_classifier_training}.
+		In order to train the multi-layered representations in an end-to-end fashion, we employ \cref{alg:kernel_embedding_classifier_training}.
 With a deep architecture, the feature representations the kernel embedding network can learn are very flexible, and can work very well for structured data by employing suitable network architectures.
@@
 
-	\subsection{Deep Linear Kernel Embedding Network}
-	\label{app:deep_linear_kernel_embedding_network}
-
-		The deep linear kernel embedding network is simply a special case at the intersection of the linear kernel embedding classifier and the deep kernel embedding network.
-From the linear KEC perspective, we simply choose $\varphi_{\theta}(x) = \varphi^{(L)}_{\theta_{L}}\big(\varphi^{(L - 1)}_{\theta_{L - 1}}(\dots\varphi^{(2)}_{\theta_{2}}(\varphi^{(1)}_{\theta_{1}}(x)))\big)$.
-From the deep kernel embedding network perspective, we simply choose $\kappa(z, z') = z^{T} z'$ to be a linear kernel.
-
-		Nevertheless, this model architecture is perhaps the most practical and powerful form of the kernel embedding classifier.
+	\subsection{Explicit Kernel Embedding Network}
+	\label{app:explicit_kernel_embedding_network}
+
+		The explicit kernel embedding network is simply a special case at the intersection of the explicit kernel embedding classifier and the kernel embedding network.
+From the explicit KEC perspective, we simply choose $\varphi_{\theta}(x) = \varphi^{(L)}_{\theta_{L}}\big(\varphi^{(L - 1)}_{\theta_{L - 1}}(\dots\varphi^{(2)}_{\theta_{2}}(\varphi^{(1)}_{\theta_{1}}(x)))\big)$.
+From the KEN perspective, we simply choose $\kappa(z, z') = z^{T} z'$ to be a linear kernel.
+
+		This model architecture is a very practical and powerful form of the kernel embedding classifier.
 By having a deep architecture, the classifier is still capable of learning flexible representations on structured data, while being able to scale to larger datasets due to the linear kernel at the output layer, provided that the dimensionality of the last layer is relatively small compared to the size of the dataset.
 
-		As a subclass of linear KEC, we can employ \cref{alg:linear_kernel_embedding_classifier_training} to learn the multi-layered features effectively.
+		As a subclass of explicit KEC, we can employ \cref{alg:linear_kernel_embedding_classifier_training} to learn the multi-layered features effectively.
 In fact, by not mapping the multi-layered features into a nonlinear kernel, the gradients for each network weight and bias are usually more pronounced, and learning is usually faster in comparison.
-
-	\subsection{Learning Objective Intuitions}
-	\label{app:learning_objective_intuitions}
-
-		The learning objective \eqref{eq:learning_objective} for the kernel embedding classifier is composed of two terms: a training loss (or data fit) term and a model complexity (or regularisation) term.
-In this section we provide some intuition towards the relative effects of each term for two types of kernel models: a radial basis type kernel, producing a nonlinear kernel embedding classifier, and a linear kernel, producing a linear kernel embedding classifier.
-
-		Consider a typical radial basis type kernels such as the Gaussian (squared exponential) or Mat\'{e}rn kernel $k_{\theta}$.
-These types of kernels are usually placed on top of subsets of Euclidean spaces $\mathcal{X} \subseteq \mathbb{R}^{d}$ where $d$ is the dimensionality of an input $x \in \mathcal{X}$.
-Here, the hyperparameters $\theta$ usually includes length scale parameters ($1$ parameter for isotropic kernels, $d$ parameters for anisotropic kernels, or $\frac{d (d - 1)}{2}$ parameters for non-diagonal kernels) and possibly a sensitivity parameter which is simply a multiplicative constant that scales the magnitude of the kernel.
-
-		These types of kernels implicitly map the input space $\mathcal{X}$ to an uncountably infinite dimensional RKHS $\mathcal{H}_{k_{\theta}}$, making the model nonparametric.
-This means that the feature space $\mathcal{H}_{k_{\theta}}$ is already quite flexible for any $\theta \in \Theta$, since for any $\theta \in \Theta$ it has an uncountably infinite amount of feature basis to use for creating linear decision boundaries.
-As such, and it is relatively easy to find linear decision boundaries within such a high dimensional space.
-In this way, experiments show that for most datasets, most initialisations of $\theta$ already produces a very reasonable model of low training loss.
-In fact, there is often a subset of length scales and sensitivity parameters within $\Theta$ in which the training loss is relatively constant.
-
-		In these scenarios, the gradients from the training loss term is usually very small, and the gradient from the learning objective is dominated by the complexity term.
-Intuitively, the learning objective communicating the following message: ``the model is already performing quite well, or at least as best as it can, on the dataset, so let us focus on finding the simplest model that can still produce a similar performance''.
-
-		This is in contrast to the case with linear kernels $k_{\theta}(x, x') = \varphi_{\theta}(x)^{T} \varphi_{\theta}(x')$.
-In this case, the input space $\mathcal{X}$, usually but not necessarily also a subset of the Euclidean space $\mathbb{R}^{d}$, is explicitly mapped to a finite dimensional RKHS $\mathcal{H}_{k_{\theta}} = \mathcal{Z} \subseteq \mathbb{R}^{p}$ through the feature map $\varphi_{\theta} : \mathcal{X} \to \mathcal{Z}$.
-With only finitely many feature basis, the model becomes parametric, and the number of features is fixed at $p$ so that its capacity does not grow with the size of the dataset like a nonparametric model.
-
-		In \cref{app:deep_linear_kernel_embedding_network}, we focused on linear kernel embedding classifiers with deep neural network features, where the flexibility of such a narrow model comes from the deep architecture instead.
-This is in contrast to the case of radial basis type kernels which has a shallow architecture and the flexibility comes from the wide collection of implicit feature basis (uncountably many) which becomes more expressive as we observe more data.
-In this case, for most initialisations of the model parameters $\theta \in \Theta$, the model will not necessarily perform well on the training data.
-As such, the training loss is large and its gradients will be larger in magnitude, in order to drive the model towards a better model fit.
-
-		On the other hand, the complexity term is comparatively smaller.
-Recall that the model complexity is measured in the RKHS $\mathcal{H}_{k_{\theta}}$, which in this case is the space of the last layer $\mathcal{Z} \subseteq \mathbb{R}^{p}$ of the neural network.
-Earlier layers are free to learn very complicated feature representations.
-As long as the learned feature representations in the last layer is simple, the complexity term will be small.
-Since the number of features is fixed, the capacity of the model is limited, and thus the complexity term is usually not as big as the training loss term.
-In this way, the gradients from the learning objective is dominated by the training loss term.
-Intuitively, the learning objective is communicating the following message: ``the model is performing very poorly on the dataset, so let us first focus on learning representations to explain the dataset before we worry about finding the simplest model''.
+This approach was used to train the neural network features in our experiments.
 
 %\newpage
-%\section{Design Choices and More Discussion}
-%\label{app:design_choices}
-%
-%	In this section we discuss the various design choices we make in formulating the kernel embedding classifier.
-%
-%	\subsection{Decision Probabilities: Why clip-normalise and not softmax-normalise or softplus-normalise?}
-%	
-%		For \eqref{eq:probability_clip_normalise}...
-%		
-%		The simple reason is that it works better.
-The more theoretical reason is that our raw probability estimates usually produces predictions with low cross entropy loss.
-This means that it assigns high probability for the correct class and low probability to other classes.
-Because the decision probability estimates are not guaranteed to be strictly positive, the lower probabilities for those other classes can sometimes be slightly negative, and clip-normalisation would simply make them zero, as that would be closer to what the kernel embedding classifier is trying to express: it is so unlikely it has even assigned it negative probabilities, so it might as well be zero.
-When normalising after clipping, the zeroed-out probabilities do not come into play and the high probabilities get to keep their high values.
-Softmax and softplus operations would instead assign small positive probabilities to those slightly negative instances.
-When normalising after this, because the unlikely classes has taken up some probabilities, the class with high probabilities will have their high probabilities slightly reduces, making the cross entropy loss slightly higher and the predictions less confident.
-%		
-%	\subsection{Information Entropy: Why define information gain to be zero despite being infinitely surprised?}
-%	
-%		For \eqref{eq:empirical_information}...
-%		
-%		\note{\textbf{Unpolished.}} This is really for numerical and experimental reasons.
-The information entropy map obtained this way are just simply much smoother and intuitive.
-The alternative is to first clip the raw probability predictions at some very small tolerance, such as $\epsilon = 10^{-15}$, before we pass it through the log, as what is done in many information or entropy based computations, such as the cross entropy computation implemented in \texttt{scipy}.
-When we tried this, we saw that this produces an unnecessarily non-smooth estimate of the information entropy map.
-Furthermore, by adjusting the tolerance $\epsilon$ slightly to other small numbers, such as $10^{-10}$ or $10^{-20}$, the information entropy map changes in where the non-smoothness occurs and in what magnitude.
-This was simply too ugly for us to accept.
-Instead, defining the information gain to zero despite being infinitely surprised gave us very smooth estimates that is very close to both the map we expect and the map we obtain from computing the information entropy directly from the clip-normalised decision probabilities.
-%		
-%	\subsection{Information Entropy: Why clip from below at zero?}
-%	
-%		For \eqref{eq:empirical_information_entropy}...
-%		
-%		\note{\textbf{Unpolished.}} Similar to the reason for clip-normalising decision probabilities, if the inference algorithm has produces an information entropy that is slightly less than zero, this just means that it is very confident at those regions.
-As such, in the limit, we expect that this would converge back to zero.
-Therefore, for finite data, we clip it from below at zero to indicate what the current data suggests the true information entropy should be when we have infinite data.
-%		
-%	\subsection{Cross Entropy Loss: Why use the raw decision probabilities?}
+%\bibliographystyle{apalike}
+%\bibliography{kernel_embedding}
 

### 2017-05-19 cake.tex
Complete Draft

@@
 
-% The \author macro works with any number of authors. There are two
-% commands used to separate the names and addresses of multiple
-% authors: \And and \AND.
-%
-% Using \And between authors leaves it to LaTeX to determine where to
-% break the lines. Using \AND forces a line break at that point. So,
-% if LaTeX puts 3 of 4 authors names on the first line, and the last
-% on the second line, try using \AND instead of \And before the third
-% author name.
-
 \author{
@@
 	\end{equation}
-	That is, indicator functions $\mathbb{1}_{c} = \delta(c, \cdot)$, $c \in \mathbb{N}_{m}$, are simply the canonical kernel features of $\mathcal{H}_{\delta}$.
+	That is, indicator functions $\mathbb{1}_{c} = \delta(c, \cdot)$, $c \in \mathbb{N}_{m}$, are simply the canonical kernel induced features of $\mathcal{H}_{\delta}$.
 Such properties do not necessarily hold for continuous domains in general.
@@
 	Our learning algorithm does not restrict the way the kernel $k_{\theta}$ is constructed from its parameters $\theta \in \Theta$.
-One particularly useful class of kernels are those with explicit neural network features, in which the kernel $k(x, x') = \langle \varphi(x), \varphi(x') \rangle$ is constructed from neural networks $\varphi : \mathcal{X} \to \mathbb{R}^{p}$ explicitly.
+One particularly useful class of kernel embedding classifiers are those where the input kernel $k(x, x') = \langle \varphi(x), \varphi(x') \rangle$ is constructed from neural networks $\varphi : \mathcal{X} \to \mathbb{R}^{p}$ explicitly.
+We refer to these types of kernel embedding classifiers as kernel embedding networks (KEN).
 Neural networks are typically defined by weights and biases of its hidden layers, which collectively define the parameters of the constructed kernel, and are thus trainable under our learning algorithm.
@@
 This allows scalability for $n >> p$ without using stochastic gradient updates so that the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} can be as tight as possible for a given $n$.
-Neural networks are by construction compositional, and thus latent representations of deeper networks undergo more transformations to generate a smaller and explicit collection of more expressive nonlinear features, leading to a deeper but narrower model architecture.
+Neural networks are by construction compositional, and thus latent representations of deeper networks undergo more transformations to generate a smaller and explicit collection of expressive nonlinear features, leading to a deeper but narrower model architecture.
 This is in contrast to the potentially infinitely many implicit features from nonlinear kernels, which in turn define a shallower but wider model architecture.
-We direct the reader to appendix C for detailed discussion on the various kernel embedding classifier architectures.
+We direct the reader to appendix C for detailed discussion on the various kernel embedding classifier architectures and their implementation as compared to \cref{alg:kernel_embedding_classifier_training}.
 
@@
 We evaluate the performance of the learning algorithm on a withheld test set using 20\% of the available 150 data samples.
-Attributes are scaled into the unit range $[0, 1]$ and decision probability maps are plotted for the region $[-0.5, 1.05]^{2}$, where the red, green, and blue colour channel represents the clip-normalised decision probability for classes $c = 1, 2, 3$.
+Attributes are scaled into the unit range $[0, 1]$ and decision probability maps are plotted for the region $[-0.5, 1.05]^{2}$, where the red, green, and blue colour channels represent the clip-normalised decision probability \eqref{eq:empirical_decision_probability_clip_normalised} for classes $c = 1, 2, 3$.
 We begin from two initial scenarios, one originally overfitting ($\alpha_{o} = 0.01$, $\ell_{o} = 0.035$, $\lambda_{o} = 10^{-6}$) and another underfitting ($\alpha_{u} = 1$, $\ell_{u} = 1$, $\lambda_{u} = 1$) the training data.
 Initially, both models performs sub-optimally with a test accuracy of 56.67\%.
-We see that the Rademacher complexity bound (RCB) $r(\theta, \lambda)$ appropriately measures the amount of overfitting with $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = 4.33$ and $r(\alpha_{u}, \ell_{u}), \lambda_{u}) = 0.31$.
+We see that the Rademacher complexity bound (RCB) $r(\theta, \lambda)$ appropriately measures the amount of overfitting with $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = 4.33$ and $r((\alpha_{u}, \ell_{u}), \lambda_{u}) = 0.31$.
 We then learn model hyperparameters with \cref{alg:kernel_embedding_classifier_training} for 500 iterations from both initialisations at rate $\eta = 0.01$, where both models converges to a balanced model with appropriate complexity bounds $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = r((0.01, 0.24), 8.62 \times 10^{-7}) = 2.23 \approx 2.14 = r((\alpha_{u}, \ell_{u}), \lambda_{u}) = r((5.1, 0.24), 0.20)$ and an improved test accuracy of 73.33\%.
@@
 
-		Furthermore, while \cref{fig:iris} shows that the model has converged for all performance measures, including complexity bounds, decision probabilities, and accuracy or loss on both training and test sets, the learned hyperparameters $((\alpha, \ell), \lambda)$ themselves differ for different initialisations.
-For a Gaussian kernel, we have that $r((\sigma_{f}, \ell), \lambda) = r((1, \ell), \lambda \sigma^{-2}_{f})$ for $\alpha(\theta) = \sigma_{f}$, so the bound $r$ is only interested in the quantities $\lambda \sigma^{-2}_{f}$ and $\ell$.
-Indeed, in our example above, $\lambda_{o} \alpha_{o}^{-2} = 0.0086 \approx 0.0075 = \lambda_{u} \alpha_{u}^{-2}$ and $\ell_{o} = 0.24 = \ell_{u}$ after learning.
-This illustrates that there can be non-trivial subsets of the kernel family $k_{\theta}$, $\theta \in \Theta$, and regularisations $\lambda \in \Lambda$ with the same complexity bound.
-The same can be true for other performance measures.
-Our learning algorithm does not distinguish amongst them, and any family member with an optimal bound $q(\theta, \lambda)$ is a solution.
-
 	\paragraph{UCI Datasets}
@@
 			\caption{Classification Accuracy (\%) of Kernel Embedding Classifiers on UCI datasets}
-			\label{tab:stationary_experiments}
+			\label{tab:uci_experiments}
 			\centering
 			\begin{tabular}{lccccc}			
-				Dataset \hspace{\fill} $(n, d, m)$ & GKEC & GKEC-SGD & NNKEC-1 & NNKEC-2 & Others \\
+				Dataset \hspace{\fill} $(n, d, m)$ & GKEC & GKEC-SGD & KEN-1 & KEN-2 & Others \\
 				\midrule
@@
 
-		We demonstrate the average performance of learning anisotropic Gaussian kernels and kernels with explicit neural network features on standard UCI datasets \citep{merz1998uci}, summarised in \cref{tab:stationary_experiments}.
+		We demonstrate the average performance of learning anisotropic Gaussian kernels and kernels with explicit neural network features on standard UCI datasets \citep{merz1998uci}, summarised in \cref{tab:uci_experiments}.
 The former has a shallow but wide model architecture, while the latter has a deeper but narrower model architecture.
-
 The Gaussian kernel is learned with both full (GKEC) and batch stochastic gradient updates (GKEC-SGD) using a tenth ($n_{b} \approx \frac{n}{10}$) of the training set each training iteration, with sensitivity and length scales initialised to $1$.
-For explicit kernels with neural network features, we randomly select two simple fully connected architectures with 16-32-8 (NNKEC-1) and 96-32 (NNKEC-2) hidden units respectively, and learn the corresponding kernel without dropout under ReLU activation.
-Biases are initialised to $0.1$ while weight parameters are initialised from a truncated normal distribution with standard deviation $0.1$, and are to be trained with full gradient updates.
-For all experiments, regularisation parameter $\lambda$ is initialised to $1$ and is learned jointly with the kernel.
-Classifiers are trained with the Adam optimiser \citep{kingma2014adam} in TensorFlow \citep{abadi2016tensorflow} with a learning rate of $\eta = 0.1$ and $\epsilon = 10^{-15}$ under the learning objective $q(\theta, \lambda)$.
-Training is ran for 1000 or 10000 iterations when using full or batch gradient updates respectively, regardless of training convergence.
-All datasets are scaled so that all attributes are in the unit range.
-Each classifier is trained on 9 out of 10 folds and tested on the remaining fold, which are shuffled over all 10 combinations to obtain the average test accuracy.
+For neural network induced kernels, we randomly select two simple fully connected architectures with 16-32-8 (KEN-1) and 96-32 (KEN-2) hidden units respectively, and learn the conditional embedding without dropout under ReLU activation.
+Biases and standard deviations of zero mean truncated normal distributed weights are initialised to $0.1$, and are to be trained with full gradient updates.
+For all experiments, $\lambda$ is initialised to $1$ and is learned jointly with the kernel.
+Classifiers are trained with the Adam optimiser \citep{kingma2014adam} in TensorFlow \citep{abadi2016tensorflow} with rate $\eta = 0.1$ and $\epsilon = 10^{-15}$ under the learning objective $q(\theta, \lambda)$ \eqref{eq:learning_objective}.
+Classifiers are trained for 1000 or 10000 iterations when using full or batch gradient updates respectively, regardless of convergence.
+All attributes are scaled to the unit range.
+Each classifier is trained on 9 out of 10 folds and tested on the remaining fold, which are shuffled over all 10 combinations to obtain the test accuracy average and deviation.
 We compare our results to other approaches using neural networks \citep[a; c]{kaya2016banknote, freire2009short}, probabilistic binary trees \citep[b]{horton1996probabilistic}, decision trees \citep[d]{zhou2004size}, and regularised discriminant analysis \citep[e]{aeberhard1992comparison}.
-However, these approaches may have used different data pre-processing, test folds, optimiser, learning rate, architecture (for neural nets), and training time.
-Comparisons are thus only illustrative.
-\Cref{tab:stationary_experiments} shows that our learning algorithm achieves similar performance to other approaches without any special tuning or heuristics, but by simply placing a conditional embedding on training data and applying a complexity bound based learning algorithm.
-The SGD approach for Gaussian kernels performs similarly to the full gradient approach, verifying the claim of \cref{thm:expected_risk_bound_hyperparameter_learning_copy} for $n = n_{b}$.
+\Cref{tab:uci_experiments} shows that our learning algorithm achieves similar performance without any special tuning or heuristics, but by simply placing a conditional embedding on training data and applying a complexity bound based learning algorithm.
+The SGD approach for Gaussian kernels performs similarly to the full gradient approach, supporting \cref{thm:expected_risk_bound_hyperparameter_learning_copy} for $n = n_{b}$.
 For neural network features, we did not attempt to choose an optimal architecture for each dataset.
@@
 
-	\paragraph{MNIST}
-
-		We also demonstrate
-
-%		83.7\% with only 500 data points
-
-		STILL HAS TO ADD CONVOLUTIONAL KERNEL MNIST STUFF WHICH ACHIEVED 99.5\% TEST ACCURACY WITH SGD
-
-		DISCUSSION NOT DONE
-
-%	\begin{figure}[t]
-%		\centering
-%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_50.eps}
-%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_100.eps}
-%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_250.eps}
-%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_500.eps}
-%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_750.eps}
-%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_1000.eps}
-%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_1500.eps}
-%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_2000.eps}
-%		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_5000.eps}
-%		\includegraphics[width=\linewidth]{figures/test_performance.eps}
-%		\caption{Training the kernel embedding classifier on the MNIST digits dataset with an anisotropic Gaussian kernel. Top: Learned length scales for each pixel; Bottom: Performance on the test set.}
-%		\label{fig:pixel_relevance}
-%	\end{figure}
-
-%	\begin{figure}[t]
-%		\centering
-%		\includegraphics[width=0.25\linewidth]{figures/spiral_all_final.eps}
-%		\caption{.}
-%		\label{fig:spiral}
-%	\end{figure}
-%
-
-	- original convolutional neural network uses 1e-2 learning rate as well under cross entropy loss so we use the same learning rate
-	- we also use sgd batches of 6000 for that network
-	- for 10000 iterations, we obtain 99.5+, they get 99.2
-	- unlike the uci examples, this time we use a architecture that aligns more with the specific dataset, and thus achieves outstanding performance
-	- we initialise regularisation parameter to 10
+	\paragraph{MNIST by learning pixel length scales}
+
+		We apply \cref{alg:kernel_embedding_classifier_training} to learn anisotropic length scales of Gaussian kernels on pixels of the MNIST digits dataset \citep{lecun1998gradient}.
+We first demonstrate the test performance of KECs as the training set increases in size, verifying \cref{thm:probability_convergence_copy} in that decision probabilities converge to the true and thus test distribution as $n$ increases.
+In the top left plot of \cref{fig:mnist_experiments}, we train on datasets of varying sizes, from 50 to 5000 samples, and benchmark performance on the standard test set of 10000 examples.
+All hyperparameters are initialised to 1 before training.
+For each $n$, we see that KECs outperform SVCs, since SVCs are unable to learn the length scales of the Gaussian kernel.
+This also shows that KECs perform very well with small datasets even when $n < d$.
+The MNIST dataset has $d = 28^{2} = 784$ pixel dimensions, yet with only $n = 50, 150, 250$ training samples, the KEC achieves a test accuracy of 45.7\%, 70.09\%, and 79.37\% respectively, compared to 18.13\%, 37.43\%, and 53.81\% from SVCs.
+We also compare training under the learning objective with and without the Rademacher complexity bound.
+For small $n$ below 750 samples, the latter outperforms the former (e.g.
+86.69\% and 86.96\% for $n = 500$), while for large $n$ the former outperforms the latter (e.g.
+96.05\% and 95.3\% for $n= 5000$).
+This verifies that complexity based regularisation becomes especially important when data size grows, where overfitting starts to hurt generalisation performance.
+Our bound is also tighter with larger $n$, so that generalisation performance improves with more data.
+The images at the bottom of \cref{fig:mnist_experiments} show the pixel length scales learned through batch stochastic gradient updates ($n_{b} = 1200$) on all available training images of the digits indicated, demonstrating the most discriminative regions for classification.
+In particular, the most discriminative regions are usually around the edges of the digits, subject to slight intraclass translations.
+
+	\paragraph{MNIST by learning convolutional features}
+
+		\begin{figure}[t]
+			\centering 
+			\includegraphics[width=0.49\linewidth]{figures/gaussian_mnist_test_performance_short.eps}
+			\includegraphics[width=0.49\linewidth]{figures/deep_mnist_test_performance_short.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_01_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_068_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_12_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_14_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_23_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_38_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_479_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_56_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_0123456789_batch_1200.eps}
+			\caption{Top: Test accuracy and cross entropy loss by learning Gaussian kernels (left) and deep convolutional features (right). Bottom: Learned pixel length scales under Gaussian kernels.}
+			\label{fig:mnist_experiments}
+		\end{figure}
+
+		We now apply our learning algorithm to train convolutional neural networks (CNN) on the MNIST dataset.
+We employ an example architecture from the TensorFlow tutorial on deep MNIST classification \citep{abadi2016tensorflow}.
+This ReLU activated architecture uses two convolutional layers, each with max pooling, followed by a fully connected layer with a drop out probability of 0.5.
+The original network then employs a final softmax regressor on the last hidden layer for classification.
+The kernel embedding network instead employs a linear kernel on the last hidden layer to construct the conditional embedding.
+We then train both networks from the same initialisation with stochastic gradient updates using 6000 images at a time for 800 epochs, with learning rate $\eta = 0.01$.
+All biases and standard deviations of zero mean truncated normal distributed weights are initialised to 0.1.
+The convolutional features of the kernel embedding network are trained jointly with the regularisation parameter, initialised to $\lambda = 10$, under our proposed learning objective \eqref{eq:learning_objective}, while the original CNN is trained under its usual cross entropy loss.
+The fully connected layer is trained with a drop out probability of 0.5 for both cases to allow direct comparison.
+The top right plot in \cref{fig:mnist_experiments} shows that the KEN learns convolutional features at a much faster rate, maintaining a higher test accuracy at all times.
+After 800 epochs, our convolutional KEN reaches a test accuracy of 99.48\%, compared to 99.26\% from the original CNN.
+This demonstrates that our learning algorithm can perform end-to-end learning with convolutional features from scratch, by placing a conditional embedding on a neural network.
+The resulting classifier can outperform the original neural network in both convergence rate and accuracy.
 
@@
 
-	FUTURE WORK: REVERSE EMBEDDING, SEMI-SUPERVISED LEARNING, ONE CLASS LEARNING, REGRESSION
-
-	Contrary to parametric models, nonlinear kernels produce nonparametric classifiers, and thus its model capacity grows with increasing data.
-Within a large enough family of kernels $k_{\theta}$, the kernel embedding classifier always has the capacity to shatter the training data and produce zero training error.
-This is precisely the quality Rademacher complexity measures.
-Given that it has such capabilities, we instead focus on learning the simplest model, so that it can generalise well to unseen data.
-By jointly minimising the training risk and the Rademacher complexity bound, we are effectively removing unnecessarily complex models while maintaining good generalisation performance.
-Without the Rademacher complexity bound $r(\theta, \lambda)$, the classifier can easily overfit by adapting its model capacity to the training data closely.
-In short, while parametric models have limited capacity and thus trying to learn to perform well on a training set to its best ability is a good indicator to test performance, nonparametric models has infinite capacity and need to learn not to exploit this capacity on training data and instead learn the simplest pattern it can to be able to infer about new test instances.
-
-%		\item \textbf{Sampling and Generative Models.} While the kernel embedding classifier is trained as a discriminative model, at its core it is simply just a condition embedding of $\mathbb{P}_{Y | X}$.
-As such, we can do full probabilistic inference entirely in reproducing kernel Hilbert spaces and obtain the Hilbert space embeddings of $\mathbb{P}_{X | Y}$, similar to what we have touched upon in \cref{sec:mode_reconstruction}, or even simply of the marginals $\mathbb{P}_{X}$ and $\mathbb{P}_{Y}$.
-If we can recover these distributions as densities ($\mathbb{P}_{Y}$ would correspond to a probability mass function over a finite and discrete space $\mathbb{N}_{m}$ which is identical to the mean embedding already, and so this step would be trivial for $\mathbb{P}_{Y}$), then we would be able to model our data in a fully generative manner.
-In fact, in \cref{sec:mode_reconstruction} we have have already done so indirectly through reversing the embedding.
-Of course, this would require us to solve the pre-image problem of kernel embeddings, for which no general methodology exists yet besides a few heuristics with various assumptions.
-Nevertheless, assuming we can recover the densities well enough, we can then generate samples from those distributions.
-Alternatively, if we can instead sample from those distributions \textit{without} finding the pre-image, but by directly using the mean embeddings instead, that would make the kernel embedding classifier very useful as a generative modelling tool.
-%		
-%		\item \textbf{Target Label Kernel.} In this paper, we proposed to place a Kronecker delta kernel $l = \delta$ over the label space $\mathcal{Y} = \mathbb{N}_{m}$ as it is the simplest kernel over a discrete and finite domain.
-However, it is possible to place other kernels over the label space.
-A simple kernel is to have a `generalised Kronecker delta kernel' that has unit similarity when labels are the same, but a small, positive yet non-zero similarity when labels are different.
-If we set these cross similarity to be the same across all non-identical pairs of labels, then it is straight forward to show that the inference algorithm we developed in this paper stays the same.
-However, if we allow them to vary amongst each other as kernel parameters (between the range $(0, 1)$, in order to stay positive definite), then we suspect that these cross similarity coefficients would act as correlation factors between classes.
-The training algorithm we developed here does not prevent the target label kernel to have its own hyperparameters.
-As such, we should be able to learn the correlation effects between the classes effectively using the same training scheme.
-We suspect that this would make the empirical decision probabilities converge to a valid probability distribution faster.
-However, we also suspect that the training may become even more non-convex and optimisation to become more difficult.
-%		
-%		These factors may even give rise to new interpretable insights in terms of how different classes may be more related to each other.
-For example, in an image recognition task of animals, it may learn that, the class `horse' and 'pony' are much more similar than `horse' and `elephant' from the input features, and start to use the output correlations to focus on inferring about them as a group instead.
+	We propose a hyperparameter learning framework for conditional embeddings when the target is discrete.
+This naturally results in a nonparametric probabilistic multiclass classifier whose convergence properties can be guaranteed.
+Because nonparametric models have infinite capacity and can potentially overfit, we propose learning-theoretic bounds to regularise the conditional embedding in a way that minimises expected classification risk.
+The resulting bound justifies the use of stochastic gradient updates for hyperparameter learning, which we verify experimentally on standard UCI datasets.
+The kernel embedding classifier is also inherently flexible in architecture, and in particular can perform end-to-end learning on a neural network, which we demonstrate on UCI datasets and MNIST digits, where it outperforms the original convolutional neural network in the latter.
+
+	As kernel embedding classifiers are simply learned conditional embeddings, this framework can incorporated and extended in many ways into techniques that requires appropriately trained embeddings.
+In particular, nonparametric probabilistic inference can be carried out in the RKHS to obtain joint and reverse conditional embeddings, where mode decoding, density recovery, and sampling techniques can lead to effective generative models now that hyperparameters are learned.
+This line of probabilistic inference can potentially lead to Bayesian extensions to our framework.
+We also envision a semi-supervised and one class extension to the KEC framework that can relax supervision in training.
+Moreover, instead of a Kronecker delta kernel, target label kernels with non-zero and potentially trainable similarities between distinct labels may capture label correlations better than our original framework.
+Finally, our framework and algorithm is simple, and developments in creating deeper connections and relationships with other kernel based models can be fruitful.
 
@@
 
-			%		Consequently, $| \hat{p}_{c}(x) - p_{c}(x) | \leq \big\| \hat{\mu}_{Y | X = x}^{(n)} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}}$ for all $x \in \mathcal{X}$, where the right hand side of which approaches zero stochastically at rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, so that $\hat{p}_{c}$ converges pointwise to $p_{c}$ at least at this rate.
-The convergence rate does not depend on $x \in \mathcal{X}$, so this (stochastic) convergence is pointwise uniform.
-
-%			Consequently, for all $x \in \mathcal{X}$ and $c \in \mathcal{Y}$, we have 
-%			
-%			\begin{equation}
-%				| \hat{p}_{c}(x) - p_{c}(x) | \leq \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}}.
-%			\label{eq:uniform_convergence}
-%			\end{equation}
-%			
-%			This is true for all possible datasets represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$.
-Thus, for any constant $C$, the implication statement $\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C \implies | \hat{p}_{c}(x) - p_{c}(x) | \leq C$ holds for all possible data observation events $\omega \in \Omega$.
-Writing this explicitly in event space translates this to a probability statement,
-%			
-%			\begin{equation}
-%			\begin{aligned}
-%			\{\omega \in \Omega : \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C\} &\subseteq \{\omega \in \Omega : | \hat{p}_{c}(x) - p_{c}(x) | \leq C\} \\
-%			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C\Big] &\leq \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | \leq C \Big].
-%			\label{eq:probability_statement}
-%			\end{aligned}
-%			\end{equation}
-%			
-%			Since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is valid.
-By letting $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ in \eqref{eq:probability_statement}, we immediately have that the probability inequality in statement \eqref{eq:probability_statement} is also true if we replace $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|$ with $| \hat{p}_{c}(x) - p_{c}(x) |$, % the RKHS norm between the empirical and true embeddings to the absolute difference between the empirical decision probability and the true decision probability,
-%			
-%			\begin{equation}
-%			\begin{aligned}
-%			\mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
-%			\implies 1 - \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
-%			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
-%			\implies \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
-%			\implies 1 - \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
-%			\implies \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon.
-%			\end{aligned}	
-%			\end{equation}
-%			
-%			In other words, the function $\hat{p}_{c}$ stochastically converges pointwise to $p_{c} := \mathbb{P}[Y = c | X = \cdot]$ with a rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-The convergence rate does not depend on $x \in \mathcal{X}$ nor $c \in \mathbb{N}_{m}$, so this stochastic convergence is pointwise uniform in its domain $\mathcal{X}$ across all label classes.
-
 		\end{proof}
@@
 
-%		Another class of kernels that is both expressive and scalable are those composed from feed forward neural networks. 
-%		
-%		\begin{corollary}[Rademacher Complexity Bound for Neural Network Kernels]
-%			\label{thm:rademacher_complexity_neural_kernels_bound}
-%			
-%			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
-Denote $\theta = \{W_{j}, b_{j}\}_{j = 1}^{l}$ for the kernel parameters of the neural network kernel $k_{\theta}(x, x') := \varphi_{\theta}(x)^{T} \varphi_{\theta}(x')$ defined from the $l$-multilayered neural network $\varphi_{\theta}(x) := \varphi^{\theta}_{l}(\varphi^{\theta}_{l - 1}(\dots \varphi^{\theta}_{1}(x)))$.
-Let $\varphi^{\theta}_{j}(z) = \varphi^{\theta}_{j}( z ; W_{j}, b_{j}) = \sigma(W_{j} z + b_{j})$ be the $j^{\mathrm{th}}$ multi-valued perceptron layer with an element wise rectified linear unit (ReLU) activation $\sigma(\cdot) = \max \{ \cdot, 0 \}$ and appropriately sized weights $W_{j}$, biases $b_{j}$, and input $z$ from the previous hidden layer.
-Without loss of generality, suppose that $x \in \mathcal{X} = [-1, 1]^{d}$.
-Select $\tilde{\theta} \in \Theta$ and define $\Theta(\tilde{\theta})$ such that $\| W_{j} \|_{\mathrm{tr}} \leq \| \tilde{W}_{j} \|_{\mathrm{tr}}$ and $\| b_{j} \| \leq \| \tilde{b}_{j} \|$ , $j \in \mathbb{N}_{l}$, for all $\theta = \{W_{j}, b_{j}\}_{j = 1}^{l} \in \Theta(\tilde{\theta})$.
-For any $\tilde{\theta} = \{\tilde{W}_{j}, \tilde{b}_{j}\}_{j = 1}^{l} \in \Theta$ and set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the resulting class of the kernel embedding classifiers $F_{n}(\Theta(\tilde{\theta}), \Lambda)$ defined over $\theta \in \Theta(\tilde{\theta}), \lambda \in \Lambda$ is bounded by
-%			
-%			\begin{equation}
-%				\mathcal{R}_{n}(F_{n}(\Theta(\tilde{\theta}), \Lambda)) \leq 2 \rho D^{\tilde{\theta}}_{l}(D^{\tilde{\theta}}_{l - 1}( \dots D^{\tilde{\theta}}_{1}(\sqrt{d}))),
-%			\end{equation}
-%			
-%			where $D^{\tilde{\theta}}_{j}(a) := a \| \tilde{W}_{j} \|_{\mathrm{tr}} + \| \tilde{b}_{j} \|$, .
-%			
-%			\begin{proof}
-%				Let $z^{\theta}_{j}(x) := \varphi^{\theta}_{j}(\varphi^{\theta}_{j - 1}(\dots \varphi^{\theta}_{1}(x)))$ be the $j^{\mathrm{th}}$ hidden layer so that $z^{\theta}_{j}(x) = \varphi^{\theta}_{j}(z^{\theta}_{j - 1}(x)) = \sigma(W_{j} z^{\theta}_{j - 1}(x) + b_{j})$ with $z^{\theta}_{0}(x) = x$ for all $j \in \mathbb{N}_{l}$.
-At the last layer, we have $\varphi_{\theta}(x) = z_{l}(x)$.
-For any layer $j \in \mathbb{N}_{l}$,
-%			
-%				\begin{equation}
-%					\begin{aligned}
-%						\| z^{\theta}_{j}(x) \| &= \| \sigma(W_{j} z^{\theta}_{j - 1}(x) + b_{j}) \| \\
-%						&\leq \| W_{j} z^{\theta}_{j - 1}(x) + b_{j} \| \\
-%						&\leq \| W_{j} z^{\theta}_{j - 1}(x) \| + \| b_{j} \| \\
-%						&\leq \| W_{j} \|_{\mathrm{tr}} \| z^{\theta}_{j - 1}(x) \| + \| b_{j} \| \\
-%						&=: D^{\theta}_{j}(\| z^{\theta}_{j - 1}(x) \|). \\
-%					\end{aligned}
-%				\end{equation}
-%				
-%				This recursive relationship can be rolled out explicitly to bound the kernel,
-%
-%				\begin{equation}
-%					\begin{aligned}
-%						\sqrt{k_{\theta}(x, x)} &= \| \varphi_{\theta}(x) \| \\
-%						&= \| z^{\theta}_{l}(x) \| \\
-%						&\leq D^{\theta}_{j}(\| z^{\theta}_{j - 1}(x) \|) \\
-%						&\leq D^{\theta}_{l}(D^{\theta}_{l - 1}( \dots D^{\theta}_{1}( \| x \| ))) \\
-%						&\leq D^{\theta}_{l}(D^{\theta}_{l - 1}( \dots D^{\theta}_{1}( \sqrt{d} ))).
-%					\end{aligned}
-%				\end{equation}
-%
-%				Since $\| W_{j} \|_{\mathrm{tr}} \leq \| \tilde{W}_{j} \|_{\mathrm{tr}}$ and $\| b_{j} \| \leq \| \tilde{b}_{j} \|$ , $j \in \mathbb{N}_{l}$, for all $\theta = \{W_{j}, b_{j}\}_{j = 1}^{l} \in \Theta(\tilde{\theta})$, we have $D^{\theta}_{j}(a) := a \| W_{j} \|_{\mathrm{tr}} + \| b_{j} \| \leq a \| \tilde{W}_{j} \|_{\mathrm{tr}} + \| \tilde{b}_{j} \| =: D^{\tilde{\theta}}_{j}(a)$ for $a \geq 0$.
-Hence, $\sqrt{k_{\theta}(x, x)} \leq D^{\tilde{\theta}}_{l}(D^{\tilde{\theta}}_{l - 1}( \dots D^{\tilde{\theta}}_{1}(\sqrt{d})))$ for all $\theta \in \Theta(\tilde{\theta})$ and $x \in \mathcal{X} = [-1, 1]^{d}$, and we choose $\alpha = D^{\tilde{\theta}}_{l}(D^{\tilde{\theta}}_{l - 1}( \dots D^{\tilde{\theta}}_{1}(\sqrt{d})))$ in \cref{thm:rademacher_complexity_bound}.
-%				
-%			\end{proof}
-%		\end{corollary}
-
 	\subsection{Expected Risk Bounds}
@@
 Since, like the expected loss, the training loss term is always in the unit range $[0, 1]$, we focus on understanding the tightness of the bound contributed from the complexity term.
-
-%		Consider a clipped cross entropy loss with a very small clipping factor, $0 < \epsilon << 1$.
-In this scenario, $M_{\epsilon} = - \log{\epsilon}$ would be very large, shooting up to infinity exponentially quickly as $\epsilon$ gets smaller, and the coefficient on the training loss term would then be very small.
-On the other hand, $\epsilon \log{\frac{1}{\epsilon}}$ would be very small, so that the coefficient on the complexity term would then be very large.
-In other words, as $\epsilon$ gets smaller, the training loss term becomes exponentially smaller while the complexity term becomes exponentially larger.
-This raises a major concern.
-The first concern is that the bound unlikely to be tight due to the exploding coefficient on the complexity term.
-Since we will likely be using some sort of gradient-based optimisation to minimise this upper bound, the second concern is that the gradient contribution coming from the training objective is vastly diminished while the gradient contribution from the complexity term is vastly amplified, potentially causing an imbalance in the optimisation to bias towards simpler models that do not perform well on the training data.
-%		
-%		A large clipping factor $\epsilon$ near one also raises similar concerns.
-The coefficient on the complexity term also explodes.
-Meanwhile, although the coefficient on the training loss is now larger, the loss is constant (at one) for probability estimates under $\epsilon$ and approaches the zero-one loss, for which the gradients are zero for most scenarios of the
-%
 
@@
 		\end{equation}
-
-%		In fact, the inequality $\mathcal{L}_{\epsilon_{1}}(y, f(x)) \leq \mathcal{L}_{\epsilon_{2}}(y, f(x))$ holds in general for all $\epsilon_{1} \leq \epsilon_{2}, x \in \mathcal{X}, y \in \mathcal{Y}$.
 
@@
 	\begin{table}[h]
-		\begin{center}
-			\begin{tabular}{ l || c c c c c}
+		\caption{Properties of Kernel Embedding Classifier Architectures}
+		\label{tab:kernel_embedding_classifier_variants}
+		\centering
+		\begin{tabular}{lccccc}
 			KEC Variant & Width & Depth & Scalability & Flexibility & Typical Datasets  \\
-				\hline
+			\midrule
 			Implicit KEC & Wide & Shallow & Low & High & High or Low $d$, Low $n$ \\
@@
 		\end{tabular}
-		\end{center}
-		\caption{Properties of kernel embedding classifier architectures}
-		\label{tab:kernel_embedding_classifier_variants}
 	\end{table}
@@
 		By explicitly defining a finite dimensional feature space, the matrix to be inverted during both learning and inference in the kernel embedding classifier can be reduced from size $n \times n$ to size $p \times p$ by using the Woodbury matrix inversion identity \citep{higham2002accuracy}.
-We use this identity to modify \cref{alg:kernel_embedding_classifier_training} to \cref{alg:linear_kernel_embedding_classifier_training} to exploit this computational speed up.
+We use this identity to modify \cref{alg:kernel_embedding_classifier_training} to \cref{alg:explicit_kernel_embedding_classifier_training} to exploit this computational speed up.
 
@@
 			\caption{Explicit KEC Hyperparameter Learning with Batch Stochastic Gradient Updates}
-			\label{alg:linear_kernel_embedding_classifier_training}
+			\label{alg:explicit_kernel_embedding_classifier_training}
 			\begin{algorithmic}[1]
@@
 
-		As a subclass of explicit KEC, we can employ \cref{alg:linear_kernel_embedding_classifier_training} to learn the multi-layered features effectively.
+		As a subclass of explicit KEC, we can employ \cref{alg:explicit_kernel_embedding_classifier_training} to learn the multi-layered features effectively.
 In fact, by not mapping the multi-layered features into a nonlinear kernel, the gradients for each network weight and bias are usually more pronounced, and learning is usually faster in comparison.

### 2017-05-19 cake.tex
Separate main paper and supplementary material and fixed capital letters in references

@@
 \newcommand{\argmax}{\operatornamewithlimits{argmax}}
+
+%\usepackage{varioref}
+%\usepackage{xr-hyper}
+%\externaldocument[cake_appendix]{cake_appendix}
 
@@
 		\begin{table}[t]
-			\caption{Classification Accuracy (\%) of Kernel Embedding Classifiers on UCI datasets}
+			\caption{Classification accuracy (\%) of kernel embedding classifiers on UCI datasets}
 			\label{tab:uci_experiments}
@@
 
-		We demonstrate the average performance of learning anisotropic Gaussian kernels and kernels with explicit neural network features on standard UCI datasets \citep{merz1998uci}, summarised in \cref{tab:uci_experiments}.
+		We demonstrate the average performance of learning anisotropic Gaussian kernels and kernels with explicit neural network features on standard UCI datasets \citep{bache2013uci}, summarised in \cref{tab:uci_experiments}.
 The former has a shallow but wide model architecture, while the latter has a deeper but narrower model architecture.
@@
 
-\newpage
-\appendix
-
-\section{Convergence Theorems for Kernel Embedding Classifiers}
-\label{app:convergence_theorems}
-
-	In this section we provide theorems, lemmas, and derivations for the convergence properties of the kernel embedding classifier.
-
-	We consider the case in which a dataset, represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$, is collected in a \textit{iid} fashion from some distribution $\mathbb{P}_{X Y}$.
+%\newpage
+%\appendix
+%	
+%\section{Convergence Theorems for Kernel Embedding Classifiers}
+%\label{app:convergence_theorems}
+%
+%	In this section we provide theorems, lemmas, and derivations for the convergence properties of the kernel embedding classifier.
+%	
+%	We consider the case in which a dataset, represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$, is collected in a \textit{iid} fashion from some distribution $\mathbb{P}_{X Y}$.
 That is $\{X_{i}, Y_{i}\} \sim \mathbb{P}_{X Y}$ for all $i \in \mathbb{N}_{n}$ and each observed sample is independent from each other.
@@
 That is,
-	\begin{equation}
-		\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists M_{\epsilon} > 0 \quad s.t.
+%	\begin{equation}
+%		\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists M_{\epsilon} > 0 \quad s.t.
 \quad \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
-	\label{eq:empirical_conditional_embedding_stochastic_convergence}
-	\end{equation}
-	\begin{theorem}[Pointwise and Uniform Convergence of Estimators based on Conditional Embeddings]
-		\label{thm:pointwise_uniform_convergence}
-		Suppose that $k(x, \cdot)$ is in the image of $C_{XX}$ and that there exists $0 \leq \gamma(x) < \infty$ such that for some estimator function $\hat{f} : \mathcal{X} \to \mathbb{R}$ and target function  $f : \mathcal{X} \to \mathbb{R}$,
-		\begin{equation}
-			| \hat{f}(x) - f(x) | \leq \gamma(x) \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}}, \forall x \in \mathcal{X},
-		\label{eq:estimator_error_bound}
-		\end{equation}
-		then the estimator $\hat{f}$ converges pointwise to the target $f$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+%	\label{eq:empirical_conditional_embedding_stochastic_convergence}
+%	\end{equation}
+%	\begin{theorem}[Pointwise and Uniform Convergence of Estimators based on Conditional Embeddings]
+%		\label{thm:pointwise_uniform_convergence}
+%		Suppose that $k(x, \cdot)$ is in the image of $C_{XX}$ and that there exists $0 \leq \gamma(x) < \infty$ such that for some estimator function $\hat{f} : \mathcal{X} \to \mathbb{R}$ and target function  $f : \mathcal{X} \to \mathbb{R}$,
+%		\begin{equation}
+%			| \hat{f}(x) - f(x) | \leq \gamma(x) \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}}, \forall x \in \mathcal{X},
+%		\label{eq:estimator_error_bound}
+%		\end{equation}
+%		then the estimator $\hat{f}$ converges pointwise to the target $f$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
 Further, if $\gamma(x) = \gamma$ is independent of $x \in \mathcal{X}$, then this convergence is uniform.
-
-		\begin{proof}
-
-			Suppose that there exists $0 \leq \gamma(x) < \infty$ such that \eqref{eq:estimator_error_bound} is satisfied.
+%		
+%		\begin{proof}
+%			
+%			Suppose that there exists $0 \leq \gamma(x) < \infty$ such that \eqref{eq:estimator_error_bound} is satisfied.
 That is, the inequality \eqref{eq:estimator_error_bound} holds for all possible data observations $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$.
@@
 Writing this explicitly in event space translates this to a probability statement,
-			\begin{equation}
-			\begin{aligned}
-				\{\omega \in \Omega : \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq C\} &\subseteq \{\omega \in \Omega : | \hat{f}(x) - f(x) | \leq C \gamma(x)\} \\
-				\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq C\Big] &\leq \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq C \gamma(x) \Big].
-			\label{eq:probability_statement}
-			\end{aligned}
-			\end{equation}
-			Since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is valid.
+%			\begin{equation}
+%			\begin{aligned}
+%				\{\omega \in \Omega : \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq C\} &\subseteq \{\omega \in \Omega : | \hat{f}(x) - f(x) | \leq C \gamma(x)\} \\
+%				\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq C\Big] &\leq \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq C \gamma(x) \Big].
+%			\label{eq:probability_statement}
+%			\end{aligned}
+%			\end{equation}
+%			Since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is valid.
 By letting $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ in \eqref{eq:probability_statement}, we immediately have that the probability inequality in statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is also true if we replace $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|$ with $| \hat{f}(x) - f(x) |$ and $M_{\epsilon}$ with $\gamma(x) M_{\epsilon}$,
-			\begin{equation}
-			\begin{aligned}
-			\mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
-			\implies 1 - \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
-			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
-			\implies \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
-			\implies 1 - \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
-			\implies \mathbb{P}\Big[| \hat{f}(x) - f(x) | > \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon.
-			\end{aligned}	
-			\end{equation}
-			where we employed statement \eqref{eq:probability_statement} between the third and fourth line for $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+%			\begin{equation}
+%			\begin{aligned}
+%			\mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
+%			\implies 1 - \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
+%			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
+%			\implies \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
+%			\implies 1 - \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
+%			\implies \mathbb{P}\Big[| \hat{f}(x) - f(x) | > \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon.
+%			\end{aligned}	
+%			\end{equation}
+%			where we employed statement \eqref{eq:probability_statement} between the third and fourth line for $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
 Therefore, since $M_{\epsilon}$ is arbitrary, define $\tilde{M}_{\epsilon}(x) := \gamma(x) M_{\epsilon}$ so that, with the above result, the statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} implies the following,
-			\begin{equation}
-				\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists \tilde{M}_{\epsilon}(x) > 0 \quad s.t.
+%			\begin{equation}
+%				\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists \tilde{M}_{\epsilon}(x) > 0 \quad s.t.
 \quad \mathbb{P}\Big[\big| \hat{f}(x) - f(x) \big| > \tilde{M}_{\epsilon}(x) \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
-			\end{equation}
-			In other words, the function $\hat{f}$ stochastically converges pointwise to $f$ with a rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+%			\end{equation}
+%			In other words, the function $\hat{f}$ stochastically converges pointwise to $f$ with a rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
 The convergence is pointwise as the constant $\tilde{M}_{\epsilon}(x)$ may be different for each point $x \in \mathcal{X}$.
 If $\gamma(x) = \gamma$ such that $\tilde{M}_{\epsilon}(x) = \tilde{M}_{\epsilon}$ does not depend on $x \in \mathcal{X}$, then this stochastic convergence is uniform in its domain $\mathcal{X}$.
-		\end{proof}
-
-	\end{theorem}
-
-	With \cref{thm:pointwise_uniform_convergence}, we can now show the convergence of various estimators based on the conditional embedding, as long as we can show that their estimator error is upper bounded by a multiple of the conditional embedding error in the RKHS norm.
+%		\end{proof}
+%
+%	\end{theorem}
+%	
+%	With \cref{thm:pointwise_uniform_convergence}, we can now show the convergence of various estimators based on the conditional embedding, as long as we can show that their estimator error is upper bounded by a multiple of the conditional embedding error in the RKHS norm.
 As such, we turn to the convergence of the empirical decision probability function \eqref{eq:empirical_decision_probability} below.
-
-	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
-		\label{thm:probability_convergence}
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-
-		\begin{proof}
-
-			Consider the pointwise absolute difference between the decision probability and its empirical estimate,
-			\begin{equation}
-				\begin{aligned}
-					| \hat{p}_{c}(x) - p_{c}(x) | &= | \langle \hat{\mu}_{Y | X = x}, \mathbb{1}_{c} \rangle - \langle \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
-					&= | \langle \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
-					&\leq \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}},
-				\label{eq:decision_probability_error_upper_bound}
-				\end{aligned}
-			\end{equation}
-			where the last inequality follows from the Cauchy Schwarz inequality in a Hilbert space.
-
-			From \eqref{eq:indicator_function}, since $\mathbb{1}_{c} = \delta(c, \cdot)$ and using the fact that $\delta$ is a reproducing kernel, we have that for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-			\begin{equation}
-				\begin{aligned}
-					\big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}}^{2} = \langle \mathbb{1}_{c}, \mathbb{1}_{c} \rangle = \langle \delta(c, \cdot), \delta(c, \cdot) \rangle = \delta(c, c) = 1.
-				\label{eq:indicator_rkhs_norm}
-				\end{aligned}
-			\end{equation}
-			Therefore, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, $\hat{p}_{c}$ converges uniformly to $p_{c}$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-
-		\end{proof}
-	\end{theorem}
-
-	The above proof is for uniform convergence over all $x \in \mathcal{X}$ at the stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+%
+%	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
+%		\label{thm:probability_convergence}
+%		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+%		
+%		\begin{proof}
+%
+%			Consider the pointwise absolute difference between the decision probability and its empirical estimate,
+%			\begin{equation}
+%				\begin{aligned}
+%					| \hat{p}_{c}(x) - p_{c}(x) | &= | \langle \hat{\mu}_{Y | X = x}, \mathbb{1}_{c} \rangle - \langle \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
+%					&= | \langle \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
+%					&\leq \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}},
+%				\label{eq:decision_probability_error_upper_bound}
+%				\end{aligned}
+%			\end{equation}
+%			where the last inequality follows from the Cauchy Schwarz inequality in a Hilbert space.
+%			
+%			From \eqref{eq:indicator_function}, since $\mathbb{1}_{c} = \delta(c, \cdot)$ and using the fact that $\delta$ is a reproducing kernel, we have that for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+%			\begin{equation}
+%				\begin{aligned}
+%					\big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}}^{2} = \langle \mathbb{1}_{c}, \mathbb{1}_{c} \rangle = \langle \delta(c, \cdot), \delta(c, \cdot) \rangle = \delta(c, c) = 1.
+%				\label{eq:indicator_rkhs_norm}
+%				\end{aligned}
+%			\end{equation}
+%			Therefore, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, $\hat{p}_{c}$ converges uniformly to $p_{c}$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+%			
+%		\end{proof}
+%	\end{theorem}
+%	
+%	The above proof is for uniform convergence over all $x \in \mathcal{X}$ at the stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
 Intuitively, however, for stationary zero-centred kernels like the Gaussian kernel, the convergence rate may be higher at regions of high data density, since the kernel effects, being centred around the training data, are stronger at these regions.
 The worse case convergence rate described here in the theorem would be a tight lower bound for regions in $\mathcal{X}$ with lower data density, where the kernel effects have decayed and most empirical probabilities are smaller and further from summing up to one.
-
-	Because the label space $\mathcal{Y} = \mathbb{N}_{m}$ is discrete and finite, \textit{bounded} functions $g \in \mathcal{H}_{\delta}$ in the RKHS are actually equivalent to their vector representations $\bvec{g} := \{g(c)\}_{c = 1}^{m}$, because one can always write $g = \sum_{c = 1}^{m} g(c) \delta(c, \cdot)$.
+%	
+%	Because the label space $\mathcal{Y} = \mathbb{N}_{m}$ is discrete and finite, \textit{bounded} functions $g \in \mathcal{H}_{\delta}$ in the RKHS are actually equivalent to their vector representations $\bvec{g} := \{g(c)\}_{c = 1}^{m}$, because one can always write $g = \sum_{c = 1}^{m} g(c) \delta(c, \cdot)$.
 This immediately implies that inner products in this space are simply the usual dot products in a Euclidean space, since
-	\begin{equation}
-		\begin{aligned}
-			\langle g_{1}, g_{2} \rangle_{\mathcal{H}_{\delta}} &= \bigg\langle \sum_{c = 1}^{m} g_{1}(c) \delta(c, \cdot), \sum_{c' = 1}^{m} g_{2}(c') \delta(c', \cdot)  \bigg\rangle_{\mathcal{H}_{\delta}} \\
-			&= \sum_{c = 1}^{m} \sum_{c' = 1}^{m} g_{1}(c) g_{2}(c') \langle \delta(c, \cdot), \delta(c', \cdot) \rangle_{\mathcal{H}_{\delta}} \\
-			&= \sum_{c = 1}^{m} g_{1}(c) g_{2}(c) \\
-			&= \bvec{g}_{1} \cdot \bvec{g}_{2}.
-		\end{aligned}
-	\end{equation}
-	Consequently, the RKHS norm for bounded functions $g \in \mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of its vector representation $\bvec{g}$,
-	\begin{equation}
-	\lVert g \rVert_{\mathcal{H}_{\delta}} = \lVert \bvec{g} \rVert_{\ell_{2}}.
-	\label{eq:rkhs_norm_is_l2_norm}
-	\end{equation}
-	A special and convenient result that arises due to this discrete and finite label space is that the decision probabilities and its empirical estimate are simply the conditional embeddings and its empirical estimate.
-
-	\begin{lemma}[Decision Probabilities are Conditional Embeddings]
-	\label{thm:probability_is_embedding}
-
-		The decision probability for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,
-		\begin{equation}
-			p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mu_{Y | X = x}(c).
-		\end{equation}
-		Therefore, $\bvec{p}(x) \equiv \mu_{Y | X = x}$.
-
-		\begin{proof}
-
-			Since indicator functions are the canonical features of the label RKHS $\mathcal{H}_{\delta}$, we employ the fact that expectations of indicator functions are probabilities to prove this claim,
-			\begin{equation}
-			\begin{aligned}
-				\mu_{Y | X = x}(c) :=& \mathbb{E}[l(Y, c) | X = x ]= \mathbb{E}[\delta(Y, c) | X = x] \\
-				=& \mathbb{E}[\mathbb{1}_{c}(Y) | X = x] = \mathbb{P}[Y \in \{c\} | X = x] \\
-				=& \mathbb{P}[Y = c | X = x] =: p_{c}(x).
-			\end{aligned}
-			\end{equation}
-		\end{proof}
-
-	\end{lemma}
-
-	\begin{lemma}[Empirical Decision Probabilities are Empirical Conditional Embeddings]
-	\label{thm:empirical_probability_is_embedding}
-
-		The empirical decision probability \eqref{eq:empirical_decision_probability} for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the empirical conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,
-		\begin{equation}
-			\hat{p}_{c}(x) = \hat{\mu}_{Y | X = x}(c).
-		\end{equation}
-		Therefore, $\hat{\bvec{p}}(x) \equiv \hat{\mu}_{Y | X = x}$.
-
-		\begin{proof}
-
-			Let the canonical feature maps of $\mathcal{X}$ and $\mathcal{Y}$ be $\phi(x) = k(x, \cdot)$ and $\psi(y) = l(y, \cdot) = \delta(y, \cdot)$, then the empirical conditional embedding is defined by
-			\begin{equation}
-				\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} \phi(x).
-			\end{equation}
-			By the reproducing property, the evaluation of $\hat{\mu}_{Y | X = x} \in \mathcal{H}_{l}$ is given by a dot product,
-			\begin{equation}
-				\begin{aligned}
-					\hat{\mu}_{Y | X = x}(c) &= \langle l(c, \cdot), \hat{\mu}_{Y | X = x} \rangle \\
-					&= \langle \psi(c), \hat{\mu}_{Y | X = x} \rangle \\
-					&= \psi(c)^{T} \hat{\mu}_{Y | X = x} \\
-					&= \psi(c)^{T} \hat{\mathcal{U}}_{Y | X} \phi(x) \\
-					&= \psi(c)^{T} \Psi (K + n \lambda I)^{-1} \Phi^{T} \phi(x) \\
-					&= \bvec{l}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x), \\
-				\end{aligned}
-			\end{equation}
-			where $\bvec{l}_{c} := \{l(y_{i}, c)\}_{i = 1}^{n}$ and $\bvec{k}_{x} := \{k(x_{i}, x)\}_{i = 1}^{n}$.
+%	\begin{equation}
+%		\begin{aligned}
+%			\langle g_{1}, g_{2} \rangle_{\mathcal{H}_{\delta}} &= \bigg\langle \sum_{c = 1}^{m} g_{1}(c) \delta(c, \cdot), \sum_{c' = 1}^{m} g_{2}(c') \delta(c', \cdot)  \bigg\rangle_{\mathcal{H}_{\delta}} \\
+%			&= \sum_{c = 1}^{m} \sum_{c' = 1}^{m} g_{1}(c) g_{2}(c') \langle \delta(c, \cdot), \delta(c', \cdot) \rangle_{\mathcal{H}_{\delta}} \\
+%			&= \sum_{c = 1}^{m} g_{1}(c) g_{2}(c) \\
+%			&= \bvec{g}_{1} \cdot \bvec{g}_{2}.
+%		\end{aligned}
+%	\end{equation}
+%	Consequently, the RKHS norm for bounded functions $g \in \mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of its vector representation $\bvec{g}$,
+%	\begin{equation}
+%	\lVert g \rVert_{\mathcal{H}_{\delta}} = \lVert \bvec{g} \rVert_{\ell_{2}}.
+%	\label{eq:rkhs_norm_is_l2_norm}
+%	\end{equation}
+%	A special and convenient result that arises due to this discrete and finite label space is that the decision probabilities and its empirical estimate are simply the conditional embeddings and its empirical estimate.
+%	
+%	\begin{lemma}[Decision Probabilities are Conditional Embeddings]
+%	\label{thm:probability_is_embedding}
+%	
+%		The decision probability for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,
+%		\begin{equation}
+%			p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mu_{Y | X = x}(c).
+%		\end{equation}
+%		Therefore, $\bvec{p}(x) \equiv \mu_{Y | X = x}$.
+%		
+%		\begin{proof} 
+%		
+%			Since indicator functions are the canonical features of the label RKHS $\mathcal{H}_{\delta}$, we employ the fact that expectations of indicator functions are probabilities to prove this claim,
+%			\begin{equation}
+%			\begin{aligned}
+%				\mu_{Y | X = x}(c) :=& \mathbb{E}[l(Y, c) | X = x ]= \mathbb{E}[\delta(Y, c) | X = x] \\
+%				=& \mathbb{E}[\mathbb{1}_{c}(Y) | X = x] = \mathbb{P}[Y \in \{c\} | X = x] \\
+%				=& \mathbb{P}[Y = c | X = x] =: p_{c}(x).
+%			\end{aligned}
+%			\end{equation}
+%		\end{proof}
+%
+%	\end{lemma}
+%	
+%	\begin{lemma}[Empirical Decision Probabilities are Empirical Conditional Embeddings]
+%	\label{thm:empirical_probability_is_embedding}
+%	
+%		The empirical decision probability \eqref{eq:empirical_decision_probability} for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the empirical conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,
+%		\begin{equation}
+%			\hat{p}_{c}(x) = \hat{\mu}_{Y | X = x}(c).
+%		\end{equation}
+%		Therefore, $\hat{\bvec{p}}(x) \equiv \hat{\mu}_{Y | X = x}$.
+%				
+%		\begin{proof}
+%			
+%			Let the canonical feature maps of $\mathcal{X}$ and $\mathcal{Y}$ be $\phi(x) = k(x, \cdot)$ and $\psi(y) = l(y, \cdot) = \delta(y, \cdot)$, then the empirical conditional embedding is defined by
+%			\begin{equation}
+%				\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} \phi(x).
+%			\end{equation}
+%			By the reproducing property, the evaluation of $\hat{\mu}_{Y | X = x} \in \mathcal{H}_{l}$ is given by a dot product,
+%			\begin{equation}
+%				\begin{aligned}
+%					\hat{\mu}_{Y | X = x}(c) &= \langle l(c, \cdot), \hat{\mu}_{Y | X = x} \rangle \\
+%					&= \langle \psi(c), \hat{\mu}_{Y | X = x} \rangle \\
+%					&= \psi(c)^{T} \hat{\mu}_{Y | X = x} \\
+%					&= \psi(c)^{T} \hat{\mathcal{U}}_{Y | X} \phi(x) \\
+%					&= \psi(c)^{T} \Psi (K + n \lambda I)^{-1} \Phi^{T} \phi(x) \\
+%					&= \bvec{l}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x), \\
+%				\end{aligned}
+%			\end{equation}
+%			where $\bvec{l}_{c} := \{l(y_{i}, c)\}_{i = 1}^{n}$ and $\bvec{k}_{x} := \{k(x_{i}, x)\}_{i = 1}^{n}$.
 While the notation $\bvec{l}_{c}$ is usually avoided due do its similarity to $\bvec{1}_{c}$, in this context they happen to represent equal quantities,
-			\begin{equation}
-				\bvec{l}_{c} := \{l(y_{i}, c)\}_{i = 1}^{n} = \{\delta(y_{i}, c)\}_{i = 1}^{n} = \{\mathbb{1}_{c}(y_{i})\}_{i = 1}^{n} =: \bvec{1}_{c}.
-			\end{equation}
-			The claim then immediately follows by the definition of our decision probability estimator,
-			\begin{equation}
-				\hat{\mu}_{Y | X = x}(c) = \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x) =: \hat{p}_{c}(x).
-			\end{equation}
-		\end{proof}
-
-	\end{lemma}
-
-	\Cref{thm:empirical_probability_is_embedding} shows that the decision function $\bvec{f}(x)$ \eqref{eq:empirical_decision_probability_vector} of a kernel embedding classifier is no more than the empirical conditional embedding estimated from the data.
-
-	Since we have identified the equivalence of decision probabilities and the conditional embedding, we can now also show that the empirical decision probability vector also converges to the true decision probability vector.
-
-	\begin{lemma}[Uniform Convergence of Empirical Decision Probability Vector Function in $\ell_{1}$ and $\ell_{2}$]
-	\label{thm:probability_vector_convergence}
-
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability vector function $\hat{\bvec{p}} : \mathcal{X} \to \mathbb{R}^{m}$ \eqref{eq:empirical_decision_probability_vector} converges uniformly to the true decision probability vector function $\bvec{p} : \mathcal{X} \to [0, 1]^{m}$ in the $\ell_{1}$-norm and $\ell_{2}$-norm, where $\bvec{p}(x) := \{p_{c}(x)\}_{c = 1}^{m}$, at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-
-		\begin{proof}
-			For convergence in $\ell_{1}$, we simply extend \cref{thm:probability_convergence}, which proved that each entry of $\hat{\bvec{p}}(x)$ converges pointwise uniformly at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ to the corresponding entry of $\bvec{p}(x)$.
+%			\begin{equation}
+%				\bvec{l}_{c} := \{l(y_{i}, c)\}_{i = 1}^{n} = \{\delta(y_{i}, c)\}_{i = 1}^{n} = \{\mathbb{1}_{c}(y_{i})\}_{i = 1}^{n} =: \bvec{1}_{c}.
+%			\end{equation}
+%			The claim then immediately follows by the definition of our decision probability estimator,
+%			\begin{equation}
+%				\hat{\mu}_{Y | X = x}(c) = \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x) =: \hat{p}_{c}(x).
+%			\end{equation}
+%		\end{proof}
+%		
+%	\end{lemma}
+%	
+%	\Cref{thm:empirical_probability_is_embedding} shows that the decision function $\bvec{f}(x)$ \eqref{eq:empirical_decision_probability_vector} of a kernel embedding classifier is no more than the empirical conditional embedding estimated from the data.
+%
+%	Since we have identified the equivalence of decision probabilities and the conditional embedding, we can now also show that the empirical decision probability vector also converges to the true decision probability vector.
+%
+%	\begin{lemma}[Uniform Convergence of Empirical Decision Probability Vector Function in $\ell_{1}$ and $\ell_{2}$]
+%	\label{thm:probability_vector_convergence} 
+%	
+%		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability vector function $\hat{\bvec{p}} : \mathcal{X} \to \mathbb{R}^{m}$ \eqref{eq:empirical_decision_probability_vector} converges uniformly to the true decision probability vector function $\bvec{p} : \mathcal{X} \to [0, 1]^{m}$ in the $\ell_{1}$-norm and $\ell_{2}$-norm, where $\bvec{p}(x) := \{p_{c}(x)\}_{c = 1}^{m}$, at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+%		
+%		\begin{proof}
+%			For convergence in $\ell_{1}$, we simply extend \cref{thm:probability_convergence}, which proved that each entry of $\hat{\bvec{p}}(x)$ converges pointwise uniformly at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ to the corresponding entry of $\bvec{p}(x)$.
 Since each entry converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the entire vector.
 More formally, from \eqref{eq:decision_probability_error_upper_bound} and \eqref{eq:indicator_rkhs_norm}, the $\ell_{1}$-norm of the difference can be bounded,
-			\begin{equation}
-				\begin{aligned}
-					{\lVert \hat{\bvec{p}}(x) - \bvec{p}(x) \rVert}_{\ell_{1}} :=& \sum_{c = 1}^{m} | \hat{p}_{c}(x) - p_{c}(x) | \\
-					\leq& \sum_{c = 1}^{m} \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \\
-					=& m \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}}
-				\end{aligned}
-			\end{equation}
-			Therefore, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = m$ independent of $x \in \mathcal{X}$, we have uniform convergence in $\ell_{1}$ where we replace all instances of $| \hat{f}(x) - f(x) |$ in the proof of \cref{thm:pointwise_uniform_convergence} with ${\lVert \hat{\bvec{p}}(x) - \bvec{p}(x) \rVert}_{\ell_{1}}$.
-
-			For convergence in $\ell_{2}$, we show that the $\ell_{2}$-norm of the difference between the true and empirical decision probability vector functions is the same as the RKHS norm of the difference between the true and empirical conditional embedding, which converges to zero at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $x \in \mathcal{X}$ and $c \in \mathcal{Y} = \mathbb{N}_{m}$ by \eqref{eq:empirical_conditional_embedding_stochastic_convergence}.
+%			\begin{equation}
+%				\begin{aligned}
+%					{\lVert \hat{\bvec{p}}(x) - \bvec{p}(x) \rVert}_{\ell_{1}} :=& \sum_{c = 1}^{m} | \hat{p}_{c}(x) - p_{c}(x) | \\
+%					\leq& \sum_{c = 1}^{m} \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \\
+%					=& m \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}}
+%				\end{aligned}
+%			\end{equation}
+%			Therefore, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = m$ independent of $x \in \mathcal{X}$, we have uniform convergence in $\ell_{1}$ where we replace all instances of $| \hat{f}(x) - f(x) |$ in the proof of \cref{thm:pointwise_uniform_convergence} with ${\lVert \hat{\bvec{p}}(x) - \bvec{p}(x) \rVert}_{\ell_{1}}$.
+%			
+%			For convergence in $\ell_{2}$, we show that the $\ell_{2}$-norm of the difference between the true and empirical decision probability vector functions is the same as the RKHS norm of the difference between the true and empirical conditional embedding, which converges to zero at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $x \in \mathcal{X}$ and $c \in \mathcal{Y} = \mathbb{N}_{m}$ by \eqref{eq:empirical_conditional_embedding_stochastic_convergence}.
 To this end, we use \cref{thm:probability_is_embedding} and \cref{thm:empirical_probability_is_embedding} and write
-			\begin{equation}
-				\begin{aligned}
-					{\lVert \hat{\bvec{p}}(x)  - \bvec{p}(x) \rVert}_{\ell_{2}} &= {\lVert \{ \hat{p}_{c}(x) \}_{c = 1}^{m} - \{ p_{c}(x) \}_{c = 1}^{m} \rVert}_{\ell_{2}} \\
-					&= {\lVert \{ \hat{p}_{c}(x) - p_{c}(x) \}_{c = 1}^{m} \rVert}_{\ell_{2}} \\
-					&= {\lVert \{ \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c)\}_{c = 1}^{m} \rVert}_{\ell_{2}} \\
-					&= \| \hat{\bm{\mu}}_{Y | X = x} - \bm{\mu}_{Y | X = x}  \|_{\ell_{2}} \\
-					&= {\lVert \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}\rVert}_{\mathcal{H}_{\delta}},
-				\end{aligned}
-			\end{equation}
-			where the last equality comes from \eqref{eq:rkhs_norm_is_l2_norm} and the fact that the empirical and true conditional embeddings are bounded functions in the RKHS.
+%			\begin{equation}
+%				\begin{aligned}
+%					{\lVert \hat{\bvec{p}}(x)  - \bvec{p}(x) \rVert}_{\ell_{2}} &= {\lVert \{ \hat{p}_{c}(x) \}_{c = 1}^{m} - \{ p_{c}(x) \}_{c = 1}^{m} \rVert}_{\ell_{2}} \\
+%					&= {\lVert \{ \hat{p}_{c}(x) - p_{c}(x) \}_{c = 1}^{m} \rVert}_{\ell_{2}} \\
+%					&= {\lVert \{ \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c)\}_{c = 1}^{m} \rVert}_{\ell_{2}} \\
+%					&= \| \hat{\bm{\mu}}_{Y | X = x} - \bm{\mu}_{Y | X = x}  \|_{\ell_{2}} \\
+%					&= {\lVert \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}\rVert}_{\mathcal{H}_{\delta}},
+%				\end{aligned}
+%			\end{equation}
+%			where the last equality comes from \eqref{eq:rkhs_norm_is_l2_norm} and the fact that the empirical and true conditional embeddings are bounded functions in the RKHS.
 Again, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, we have uniform convergence in $\ell_{2}$.
-		\end{proof}
-	\end{lemma}
-
-	\subsection{Information Entropy of Kernel Embedding Classifiers}
-	\label{app:information_entropy}
-
-		The kernel embedding classifier provides decision probabilities instead of just a single label prediction.
+%		\end{proof}
+%	\end{lemma}
+%		
+%	\subsection{Information Entropy of Kernel Embedding Classifiers}
+%	\label{app:information_entropy}
+%	
+%		The kernel embedding classifier provides decision probabilities instead of just a single label prediction.
 Such a probabilistic classifier allows us to quantify the uncertainty of its predictions for any given example $x \in \mathcal{X}$ through the information entropy \citep{shannon1951prediction, jaynes1957information}.
 This is ideal for detecting the decision boundaries of the classifier and areas of low data density.
-
-		We present two main approaches for inferring the information entropy from the classifier.
+%		
+%		We present two main approaches for inferring the information entropy from the classifier.
 Specifically, we would like to infer estimates for $h(x) := \mathbb{H}[Y | X = x] = - \sum_{c = 1}^{m} p_{c}(x) \log{p_{c}(x)} $, the information entropy of the possible labels $Y$ for a given example $X = x$.
-
-		The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref{eq:empirical_decision_probability_clip_normalised}, at the query point $x \in \mathcal{X}$,
-		\begin{equation}
-			\tilde{h}(x) := - \sum_{c = 1}^{m} \tilde{p}_{c}(x) \log{\tilde{p}_{c}(x)}.
-		\label{eq:entropy_clip_normalise}
-		\end{equation}
-		We call \eqref{eq:entropy_clip_normalise} the \textit{clip-normalised information entropy}.
+%		
+%		The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref{eq:empirical_decision_probability_clip_normalised}, at the query point $x \in \mathcal{X}$,
+%		\begin{equation}
+%			\tilde{h}(x) := - \sum_{c = 1}^{m} \tilde{p}_{c}(x) \log{\tilde{p}_{c}(x)}.
+%		\label{eq:entropy_clip_normalise}
+%		\end{equation}
+%		We call \eqref{eq:entropy_clip_normalise} the \textit{clip-normalised information entropy}.
 Since $\tilde{p}_{c}(x)$ converges pointwise to $p_{c}(x)$ with increasing data, $\tilde{h}(x)$ also converges pointwise to $h(x)$.
-
-		Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information,
-		\begin{equation}
-			\begin{aligned}
-				\mathbb{H}[Y | X = x] &= - \sum_{c = 1}^{m} \mathbb{P}[Y = c| X = x] \log{\mathbb{P}[Y = c | X = x]} \\
-				&= \mathbb{E}[- \log{\mathbb{P}[Y | X = x]} | X = x] \\
-				&= \mathbb{E}[u_{x}(Y) | X = x],
-			\end{aligned}
-		\end{equation}
-		where $u_{x}(y) := - \log{\mathbb{P}[Y = y | X = x]}$ is the \textit{information} (in nats) we would gain when we discover that example $x$ actually has label $y$.
+%		
+%		Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information,
+%		\begin{equation}
+%			\begin{aligned}
+%				\mathbb{H}[Y | X = x] &= - \sum_{c = 1}^{m} \mathbb{P}[Y = c| X = x] \log{\mathbb{P}[Y = c | X = x]} \\
+%				&= \mathbb{E}[- \log{\mathbb{P}[Y | X = x]} | X = x] \\
+%				&= \mathbb{E}[u_{x}(Y) | X = x],
+%			\end{aligned}
+%		\end{equation}
+%		where $u_{x}(y) := - \log{\mathbb{P}[Y = y | X = x]}$ is the \textit{information} (in nats) we would gain when we discover that example $x$ actually has label $y$.
 Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$.
@@
 This is the basis of our second approach.
-
-		Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$.
+%		
+%		Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$.
 We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the RKHS.
 Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref{eq:empirical_conditional_expectation} and estimate $h(x)$ by
-		\begin{equation}
-			\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle = \bvec{u}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x).
-		\end{equation}
-		Unfortunately, $u_{x}$ is not known exactly, since $\mathbb{P}[Y = y | X = x]$ is not known exactly.
+%		\begin{equation}
+%			\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle = \bvec{u}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x).
+%		\end{equation}
+%		Unfortunately, $u_{x}$ is not known exactly, since $\mathbb{P}[Y = y | X = x]$ is not known exactly.
 Instead, since $\hat{p}_{c}(x)$ is a consistent estimate for $\mathbb{P}[Y = c | X = x]$ by \cref{thm:probability_convergence}, we propose to replace $u_{x}(y)$ with the information of $\hat{p}_{y}(x)$.
@@
 Instead, in virtue of the fact that $\lim_{p \to 0} - p \log{p} = 0$ even though $\lim_{p \to 0} - \log{p} = \infty$, we simply define the information estimate $\hat{u}_{x}(y)$ as zero if the empirical decision probability is non-positive,
-		\begin{equation}
-			\hat{u}_{x}(y) := \begin{cases}
-				- \log{\hat{p}_{y}(x)} & \mathrm{if } \quad \hat{p}_{y}(x) > 0 \\
-				0 & \mathrm{otherwise}. \end{cases}
-			\label{eq:empirical_information}
-		\end{equation}
-		It remains to show that $\hat{u}_{x} \in \mathcal{H}_{\delta}$.
+%		\begin{equation}
+%			\hat{u}_{x}(y) := \begin{cases}
+%				- \log{\hat{p}_{y}(x)} & \mathrm{if } \quad \hat{p}_{y}(x) > 0 \\
+%				0 & \mathrm{otherwise}. \end{cases}
+%			\label{eq:empirical_information}
+%		\end{equation}
+%		It remains to show that $\hat{u}_{x} \in \mathcal{H}_{\delta}$.
 Indeed, the identity $\hat{u}_{x} = \sum_{c = 1}^{m} \hat{u}_{x}(c) \delta(c, \cdot)$ holds and thus $\hat{u}_{x}$ is in the span of the kernel canonical features.
 We then arrive at the following estimate for $h(x)$,
-		\begin{equation}
-			\hat{h}(x) := \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle = \hat{\bvec{u}}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x),
-		\label{eq:empirical_information_entropy}
-		\end{equation}
-		where $\hat{\bvec{u}}_{x} := \{\hat{u}_{x}(y_{i})\}_{i = 1}^{n}$.
+%		\begin{equation}
+%			\hat{h}(x) := \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle = \hat{\bvec{u}}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x),
+%		\label{eq:empirical_information_entropy}
+%		\end{equation}
+%		where $\hat{\bvec{u}}_{x} := \{\hat{u}_{x}(y_{i})\}_{i = 1}^{n}$.
 Similar to the case with decision probabilities \eqref{eq:decision_probability}, the information entropy estimate \eqref{eq:empirical_information_entropy} is not guaranteed to be non-negative.
@@
 Furthermore, negative estimated information entropy implies that the model is very confident about its prediction, and it suffices to simply clip the entropy at zero if strict information entropy is required.
-
-		Since this estimator is now based on the inner product between the empirical conditional embedding and another empirically estimate function, instead of between the empirical conditional embedding and a known function like the decision probability estimate, it is not immediately clear that such an estimator converges.
+%		
+%		Since this estimator is now based on the inner product between the empirical conditional embedding and another empirically estimate function, instead of between the empirical conditional embedding and a known function like the decision probability estimate, it is not immediately clear that such an estimator converges.
 Nevertheless, intuition tells us that the inner product between two converging quantities should converge.
 We proceed to show that this intuition is correct.
-
-		\begin{theorem}[Convergence of Empirical Information Entropy Function]
-			\label{thm:entropy_convergence}
-			Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical information entropy function $\hat{h} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_information_entropy} converges pointwise to the true information entropy function $h : \mathcal{X} \to [0, \infty)$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-
-			\begin{proof}
-				Since we are interested in the asymptotic properties of our estimators when $n \to \infty$, and we have proved that the empirical decision probabilities converges to the true probabilities (\cref{thm:probability_convergence}), the condition $\hat{p}_{c}(x) > 0$ holds for large $n$ such that we simply have $\hat{u}_{x}(c) = - \log{\hat{p}_{c}(x)}$.
+%		
+%		\begin{theorem}[Convergence of Empirical Information Entropy Function]
+%			\label{thm:entropy_convergence}
+%			Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical information entropy function $\hat{h} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_information_entropy} converges pointwise to the true information entropy function $h : \mathcal{X} \to [0, \infty)$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+%			
+%			\begin{proof}
+%				Since we are interested in the asymptotic properties of our estimators when $n \to \infty$, and we have proved that the empirical decision probabilities converges to the true probabilities (\cref{thm:probability_convergence}), the condition $\hat{p}_{c}(x) > 0$ holds for large $n$ such that we simply have $\hat{u}_{x}(c) = - \log{\hat{p}_{c}(x)}$.
 That is, the effects of clipping for the information estimate \eqref{eq:empirical_information} vanishes.
-
-				Consider the pointwise absolute difference between the empirical and true information entropy,
-				\begin{equation}
-					\begin{aligned}
-						| \hat{h}(x) - h(x) | &= | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
-						&= | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} + \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
-						&\leq | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | + | \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
-						&= | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} - u_{x} \rangle_{\mathcal{H}_{\delta}} | + | \langle \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
-						&\leq \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}} + \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| u_{x} \|_{\mathcal{H}_{\delta}},
-					\label{eq:information_entropy_bound}
-					\end{aligned}
-				\end{equation}
-				where the we used the triangle inequality and Cauchy Schwarz inequality in a Hilbert space respectively.
+%				
+%				Consider the pointwise absolute difference between the empirical and true information entropy,
+%				\begin{equation}
+%					\begin{aligned}
+%						| \hat{h}(x) - h(x) | &= | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
+%						&= | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} + \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
+%						&\leq | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | + | \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
+%						&= | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} - u_{x} \rangle_{\mathcal{H}_{\delta}} | + | \langle \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
+%						&\leq \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}} + \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| u_{x} \|_{\mathcal{H}_{\delta}},
+%					\label{eq:information_entropy_bound}
+%					\end{aligned}
+%				\end{equation}
+%				where the we used the triangle inequality and Cauchy Schwarz inequality in a Hilbert space respectively.
 Since $l = \delta$ is bounded, so is $\hat{\mu}_{Y | X = x}(c) = \sum_{i = 1}^{n} w_{i} \delta(y_{i}, c)$ for some embedding weights $w_{i}$ and all $c \in \mathbb{N}_{m}$, and thus its RKHS norm is finite for all $n \in \mathbb{N}_{n}$.
@@
 Thus, it remains to bound $\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}}$ by a multiple of $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$.
-
-				To this end, we first use \cref{thm:probability_is_embedding} and \cref{thm:empirical_probability_is_embedding} and to express the theoretical and empirical information as the negative log of the embedding, so that it is explicitly written as a function of $c \in \mathcal{Y}$ in $\mathcal{H}_{\delta}$ indexed by $x \in \mathcal{X}$,
-				\begin{equation}
-					\begin{aligned}
-						u_{x}(c) &= - \log{p_{c}(x)} = -\log{\mu_{Y | X = x}(c)}, \\
-						\hat{u}_{x}(c) &= - \log{\hat{p}_{c}(x)} = -\log{\hat{\mu}_{Y | X = x}(c)}. \\
-					\end{aligned}
-				\end{equation}
-				Since $\log$ is a concave function, we have the property that $\log{a} - \log{b} \leq \frac{1}{b} (a - b)$.
+%				
+%				To this end, we first use \cref{thm:probability_is_embedding} and \cref{thm:empirical_probability_is_embedding} and to express the theoretical and empirical information as the negative log of the embedding, so that it is explicitly written as a function of $c \in \mathcal{Y}$ in $\mathcal{H}_{\delta}$ indexed by $x \in \mathcal{X}$,
+%				\begin{equation}
+%					\begin{aligned}
+%						u_{x}(c) &= - \log{p_{c}(x)} = -\log{\mu_{Y | X = x}(c)}, \\
+%						\hat{u}_{x}(c) &= - \log{\hat{p}_{c}(x)} = -\log{\hat{\mu}_{Y | X = x}(c)}. \\
+%					\end{aligned}
+%				\end{equation}
+%				Since $\log$ is a concave function, we have the property that $\log{a} - \log{b} \leq \frac{1}{b} (a - b)$.
 This allows us to bound $| \hat{u}_{x}(c) - u_{x}(c) |$ by $| \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |$ for all $c \in \mathbb{N}_{m}$,
-				\begin{equation}
-					\begin{aligned}
-						| \hat{u}_{x}(c) - u_{x}(c) | &= | \log{\hat{\mu}_{Y | X = x}(c)} - \log{\mu_{Y | X = x}(c)} | \\
-						&\leq \frac{1}{| \mu_{Y | X = x}(c) |} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) | \\
-						&\leq \alpha_{x} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |,
-					\end{aligned}
-				\end{equation}
-				where we define $\alpha_{x} := \max_{c \in \mathbb{N}_{m}} \frac{1}{| \mu_{Y | X = x}(c) |}$, which is well defined as the conditional embedding is bounded.
+%				\begin{equation}
+%					\begin{aligned}
+%						| \hat{u}_{x}(c) - u_{x}(c) | &= | \log{\hat{\mu}_{Y | X = x}(c)} - \log{\mu_{Y | X = x}(c)} | \\
+%						&\leq \frac{1}{| \mu_{Y | X = x}(c) |} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) | \\
+%						&\leq \alpha_{x} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |,
+%					\end{aligned}
+%				\end{equation}
+%				where we define $\alpha_{x} := \max_{c \in \mathbb{N}_{m}} \frac{1}{| \mu_{Y | X = x}(c) |}$, which is well defined as the conditional embedding is bounded.
 Since the RKHS norm of bounded functions in $\mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of their vector representations \eqref{eq:rkhs_norm_is_l2_norm}, we have
-				\begin{equation}
-					\begin{aligned}
-						\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}}^{2} &= \| \hat{\bvec{u}}_{x} - \bvec{u}_{x} \|_{\ell_{2}}^{2} \\
-						&= \sum_{c = 1}^{m} | \hat{u}_{x}(c) - u_{x}(c) |^{2} \\
-						&\leq \sum_{c = 1}^{m} \alpha_{x}^{2} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |^{2} \\
-						&\leq \alpha_{x}^{2} \sum_{c = 1}^{m} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |^{2} \\
-						&\leq \alpha_{x}^{2} \| \hat{\bm{\mu}}_{Y | X = x} - \bm{\mu}_{Y | X = x}  \|_{\ell_{2}}^{2} \\
-						&\leq \alpha_{x}^{2} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}^{2}. \\
-					\end{aligned}
-				\end{equation}
-				Therefore, $\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}} \leq \alpha_{x} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$, and \eqref{eq:information_entropy_bound} becomes
-				\begin{equation}
-					\begin{aligned}
-						| \hat{h}(x) - h(x) | &\leq \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}} + \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| u_{x} \|_{\mathcal{H}_{\delta}} \\
-						&= \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| u_{x} \|_{\mathcal{H}_{\delta}} \\
-						&= ( \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| u_{x} \|_{\mathcal{H}_{\delta}} ) \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}. \\
-					\end{aligned}
-				\end{equation}
-				Hence, with $\gamma(x) = \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| u_{x} \|_{\mathcal{H}_{\delta}}$, \cref{thm:pointwise_uniform_convergence} implies that $\hat{h}$ converges pointwise to $h$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-			\end{proof}
-		\end{theorem}
-
-\newpage
-\section{Learning Theoretic Bounds for Kernel Embedding Classifiers}
-\label{app:learning_theoretic_bounds}
-
-	In this section we derive Rademacher complexity bounds for kernel embedding classifiers, and show that it can be used in conjunction with cross entropy loss to bound the expected risk with high probability.
-
-	\subsection{Rademacher Complexity Bounds}
-	\label{app:rademacher_complexity_theorems}
-
-		Suppose a set of training data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ is drawn from $\mathbb{P}_{X Y}$ in an \textit{iid} fashion.
+%				\begin{equation}
+%					\begin{aligned}
+%						\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}}^{2} &= \| \hat{\bvec{u}}_{x} - \bvec{u}_{x} \|_{\ell_{2}}^{2} \\
+%						&= \sum_{c = 1}^{m} | \hat{u}_{x}(c) - u_{x}(c) |^{2} \\
+%						&\leq \sum_{c = 1}^{m} \alpha_{x}^{2} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |^{2} \\
+%						&\leq \alpha_{x}^{2} \sum_{c = 1}^{m} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |^{2} \\
+%						&\leq \alpha_{x}^{2} \| \hat{\bm{\mu}}_{Y | X = x} - \bm{\mu}_{Y | X = x}  \|_{\ell_{2}}^{2} \\
+%						&\leq \alpha_{x}^{2} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}^{2}. \\
+%					\end{aligned}
+%				\end{equation}
+%				Therefore, $\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}} \leq \alpha_{x} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$, and \eqref{eq:information_entropy_bound} becomes
+%				\begin{equation}
+%					\begin{aligned}
+%						| \hat{h}(x) - h(x) | &\leq \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}} + \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| u_{x} \|_{\mathcal{H}_{\delta}} \\
+%						&= \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| u_{x} \|_{\mathcal{H}_{\delta}} \\
+%						&= ( \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| u_{x} \|_{\mathcal{H}_{\delta}} ) \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}. \\
+%					\end{aligned}
+%				\end{equation}
+%				Hence, with $\gamma(x) = \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| u_{x} \|_{\mathcal{H}_{\delta}}$, \cref{thm:pointwise_uniform_convergence} implies that $\hat{h}$ converges pointwise to $h$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+%			\end{proof}
+%		\end{theorem}
+%	
+%\newpage
+%\section{Learning Theoretic Bounds for Kernel Embedding Classifiers}
+%\label{app:learning_theoretic_bounds}
+%
+%	In this section we derive Rademacher complexity bounds for kernel embedding classifiers, and show that it can be used in conjunction with cross entropy loss to bound the expected risk with high probability.
+%		
+%	\subsection{Rademacher Complexity Bounds}
+%	\label{app:rademacher_complexity_theorems}
+%
+%		Suppose a set of training data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ is drawn from $\mathbb{P}_{X Y}$ in an \textit{iid} fashion.
 We denote the one hot encoded target labels of $\{y_{i}\}_{i = 1}^{n}$ by $\bvec{y}_{i} := \{\mathbb{1}_{c}(y_{i})\}_{c = 1}^{m} \in \{0, 1\}^{m}$ and $\bvec{Y} := \begin{bmatrix} \bvec{y}_{1} & \bvec{y}_{2} & \cdots & \bvec{y}_{n} \end{bmatrix}^{T} \in \{0, 1\}^{n \times m}$.
@@
 The kernel embedding classifier has a predictor form $\hat{\bvec{p}}(x) = \bvec{f}_{\theta, \lambda}(x)$ \eqref{eq:empirical_decision_probability_vector} defined by
-
-		\begin{equation}
-			\bvec{f}_{\theta, \lambda}(x) := \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \bvec{k}_{\theta}(x),
-		\label{eq:predictor}
-		\end{equation}
-
-		where each entry of the predictor $\bvec{f}_{\theta, \lambda}(x)$ is the decision probability estimate for $p_{c}(x)$.
+%	
+%		\begin{equation}
+%			\bvec{f}_{\theta, \lambda}(x) := \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \bvec{k}_{\theta}(x),
+%		\label{eq:predictor}
+%		\end{equation}
+%		
+%		where each entry of the predictor $\bvec{f}_{\theta, \lambda}(x)$ is the decision probability estimate for $p_{c}(x)$.
 This defines the function class of the predictor over the kernel family and a set of regularisation parameters for any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$,
-
-		\begin{equation}
-			F_{n}(\Theta, \Lambda) := \{ \bvec{f}_{\theta, \lambda}(x) : \theta \in \Theta, \lambda \in \Lambda \}.
-		\label{eq:predictor_class}
-		\end{equation}
-
-		The predictor form \eqref{eq:predictor} is linear in the reproducing kernel Hilbert space $\mathcal{H}_{k_{\theta}}$ induced by $k_{\theta}$ in the sense that
-
-		\begin{equation}
-			\begin{aligned}
-				\bvec{f}_{\theta, \lambda}(x) &:= W_{\theta, \lambda}^{T} \phi_{\theta}(x), \\
-				W_{\theta, \lambda} &:= \Phi_{\theta} (K_{\theta} + n \lambda I)^{-1} \bvec{Y},
-			\end{aligned}
-		\label{eq:linear_predictor}
-		\end{equation}
-
-		where we decompose $\bvec{k}_{\theta}(x) = \Phi_{\theta}^{T} \phi_{\theta}(x)$ by the reproducing property.
+%		
+%		\begin{equation}
+%			F_{n}(\Theta, \Lambda) := \{ \bvec{f}_{\theta, \lambda}(x) : \theta \in \Theta, \lambda \in \Lambda \}.
+%		\label{eq:predictor_class}
+%		\end{equation}
+%		
+%		The predictor form \eqref{eq:predictor} is linear in the reproducing kernel Hilbert space $\mathcal{H}_{k_{\theta}}$ induced by $k_{\theta}$ in the sense that
+%		
+%		\begin{equation}
+%			\begin{aligned}
+%				\bvec{f}_{\theta, \lambda}(x) &:= W_{\theta, \lambda}^{T} \phi_{\theta}(x), \\
+%				W_{\theta, \lambda} &:= \Phi_{\theta} (K_{\theta} + n \lambda I)^{-1} \bvec{Y},
+%			\end{aligned}
+%		\label{eq:linear_predictor}
+%		\end{equation}
+%		
+%		where we decompose $\bvec{k}_{\theta}(x) = \Phi_{\theta}^{T} \phi_{\theta}(x)$ by the reproducing property.
 By \cref{thm:empirical_probability_is_embedding}, $\bvec{f}_{\theta, \lambda}(x) = \hat{\bvec{p}}_{\theta, \lambda}(x) = \hat{\mu}^{(\theta, \lambda)}_{Y | X = x} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$.
@@
 Nevertheless, while they refer to the same quantity, we will use the standard notations $ \| \hat{\mathcal{U}}^{\theta, \lambda}_{Y | X} \|_{HS}$ as per the literature in Hilbert space embeddings and $\| W_{\theta, \lambda} \|_{\mathrm{tr}}$ as per the literature for linear classifiers.
-
-		\begin{theorem}[Rademacher Complexity Bound for Kernel Embedding Classifiers]
-		\label{thm:rademacher_complexity_bound}
-
-			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
+%
+%		\begin{theorem}[Rademacher Complexity Bound for Kernel Embedding Classifiers]
+%		\label{thm:rademacher_complexity_bound}
+%		
+%			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
 Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$, $\alpha > 0$, is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
 For any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of kernel embedding classifiers $F_{n}(\Theta, \Lambda)$ \eqref{eq:predictor_class} defined over $\theta \in \Theta, \lambda \in \Lambda$ is bounded by
-
-			\begin{equation}
-				\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) \leq 2 \alpha \rho.
-			\label{eq:rademacher_complexity_bound}
-			\end{equation}
-
-			\begin{proof}
-
-				The Rademacher complexity \citep[Definition 2]{bartlett2002rademacher} of the function class $F_{n}(\Theta, \Lambda)$ is
-
-				\begin{equation}
-					\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) := \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \frac{2}{n} \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg] = \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg],
-				\end{equation}
-
-				where $\sigma_{i}$ are \textit{iid} Rademacher random variables, taking values in $\{-1, 1\}$ with equal probability, and $X_{i}$ are \textit{iid} random variables from the same distribution $\mathbb{P}_{X}$ as our training data.
+%				
+%			\begin{equation}
+%				\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) \leq 2 \alpha \rho.
+%			\label{eq:rademacher_complexity_bound}
+%			\end{equation}
+%	
+%			\begin{proof}
+%			
+%				The Rademacher complexity \citep[Definition 2]{bartlett2002rademacher} of the function class $F_{n}(\Theta, \Lambda)$ is 
+%				
+%				\begin{equation}
+%					\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) := \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \frac{2}{n} \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg] = \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg],
+%				\end{equation}
+%				
+%				where $\sigma_{i}$ are \textit{iid} Rademacher random variables, taking values in $\{-1, 1\}$ with equal probability, and $X_{i}$ are \textit{iid} random variables from the same distribution $\mathbb{P}_{X}$ as our training data.
 We further define $\bm{\sigma} := \{\sigma_{i}\}_{i = 1}^{n}$.
-
-				We first bound the term inside the suprenum using the Cauchy Schwarz inequality,
-
-				\begin{equation}
-					\begin{aligned}
-						\Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\| &= \Big\| \sum_{i = 1}^{n} \sigma_{i} W_{\theta, \lambda}^{T} \phi_{\theta}(X_{i}) \Big\| \\
-						&= \Big\| W_{\theta, \lambda}^{T} \bm{\Phi}_{\theta} \bm{\sigma} \Big\| \\
-						&\leq \| W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \bm{\sigma} \| \\
-						&\leq \| W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta}^{T} \|_{\mathrm{tr}} \| \bm{\sigma} \| \\
-						&= \| W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} \| \bm{\sigma} \|,
-					\end{aligned}
-				\end{equation}
-
-				where we define the random operator $\bm{\Phi}_{\theta} := \begin{bmatrix} \phi(X_{1}) & \phi(X_{2}) & \cdots & \phi(X_{n}) \end{bmatrix}$.
+%				
+%				We first bound the term inside the suprenum using the Cauchy Schwarz inequality,
+%				
+%				\begin{equation}
+%					\begin{aligned}
+%						\Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\| &= \Big\| \sum_{i = 1}^{n} \sigma_{i} W_{\theta, \lambda}^{T} \phi_{\theta}(X_{i}) \Big\| \\
+%						&= \Big\| W_{\theta, \lambda}^{T} \bm{\Phi}_{\theta} \bm{\sigma} \Big\| \\
+%						&\leq \| W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \bm{\sigma} \| \\
+%						&\leq \| W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta}^{T} \|_{\mathrm{tr}} \| \bm{\sigma} \| \\
+%						&= \| W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} \| \bm{\sigma} \|,
+%					\end{aligned}
+%				\end{equation}
+%				
+%				where we define the random operator $\bm{\Phi}_{\theta} := \begin{bmatrix} \phi(X_{1}) & \phi(X_{2}) & \cdots & \phi(X_{n}) \end{bmatrix}$.
 Note that this is distinct from $\Phi_{\theta}$, whose columns are the canonical RKHS features at the training observations and is not random.
@@
 We can then also compute the trace norm of the other random component $\bm{\Phi}_{\theta}$,
-
-				\begin{equation}
-					\begin{aligned}
-						\| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} :=& \sqrt{\mathrm{trace}(\bm{\Phi}_{\theta}^{T} \bm{\Phi}_{\theta})} \\
-						=& \sqrt{\mathrm{trace}(\bvec{K}_{\theta})} \\
-						=& \sqrt{\sum_{i = 1}^{n} k_{\theta}(X_{i}, X_{i})} \\
-						=& \sqrt{n} \sqrt{ \frac{1}{n} \sum_{i = 1}^{n} k_{\theta}(X_{i}, X_{i})} \\
-						\leq& \sqrt{n} \sqrt{ \frac{1}{n} \sum_{i = 1}^{n} \alpha^{2}} \\
-						=& \sqrt{n} \alpha,
-					\end{aligned}
-				\end{equation}
-
-				where the inequality comes from the assertion that $k_{\theta}(x, x) \leq \alpha^{2}$ for all $x \in \mathcal{X}, \theta \in \Theta$.
+%				
+%				\begin{equation}
+%					\begin{aligned}
+%						\| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} :=& \sqrt{\mathrm{trace}(\bm{\Phi}_{\theta}^{T} \bm{\Phi}_{\theta})} \\
+%						=& \sqrt{\mathrm{trace}(\bvec{K}_{\theta})} \\
+%						=& \sqrt{\sum_{i = 1}^{n} k_{\theta}(X_{i}, X_{i})} \\
+%						=& \sqrt{n} \sqrt{ \frac{1}{n} \sum_{i = 1}^{n} k_{\theta}(X_{i}, X_{i})} \\
+%						\leq& \sqrt{n} \sqrt{ \frac{1}{n} \sum_{i = 1}^{n} \alpha^{2}} \\
+%						=& \sqrt{n} \alpha,
+%					\end{aligned}
+%				\end{equation}
+%				
+%				where the inequality comes from the assertion that $k_{\theta}(x, x) \leq \alpha^{2}$ for all $x \in \mathcal{X}, \theta \in \Theta$.
 This bounds all the random components in the expectation by a constant, so that later the expectation can vanish.
-
-				Using the assertion that $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ for all $\theta \in \Theta, \lambda \in \Lambda$, we can now bound Rademacher complexity,
-
-				\begin{equation}
-					\begin{aligned}
-						\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) &= \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg] \\
-						&\leq \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} \| \bm{\sigma} \| \bigg] \\
-						&= \frac{2}{n} \sqrt{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} \bigg] \\
-						&\leq \frac{2}{n} \sqrt{n} \sqrt{n} \alpha \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \bigg] \\
-						&\leq 2 \alpha \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \bigg] \\
-						&= 2 \alpha \sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \\
-						&\leq 2 \alpha \rho.
-					\end{aligned}
-				\end{equation}
-			\end{proof}
-		\end{theorem}
-
-		\Cref{thm:rademacher_complexity_bound} provides a generic Rademacher complexity bound for any type of kernel embedding classifier with a bounded positive definite kernel and bounded trace norm.
+%				
+%				Using the assertion that $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ for all $\theta \in \Theta, \lambda \in \Lambda$, we can now bound Rademacher complexity,
+%				
+%				\begin{equation}
+%					\begin{aligned}
+%						\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) &= \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg] \\
+%						&\leq \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} \| \bm{\sigma} \| \bigg] \\
+%						&= \frac{2}{n} \sqrt{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} \bigg] \\
+%						&\leq \frac{2}{n} \sqrt{n} \sqrt{n} \alpha \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \bigg] \\
+%						&\leq 2 \alpha \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \bigg] \\
+%						&= 2 \alpha \sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \\
+%						&\leq 2 \alpha \rho.
+%					\end{aligned}
+%				\end{equation}
+%			\end{proof}
+%		\end{theorem}
+%	
+%		\Cref{thm:rademacher_complexity_bound} provides a generic Rademacher complexity bound for any type of kernel embedding classifier with a bounded positive definite kernel and bounded trace norm.
 One of the most widely used kernels in practice are the family of stationary kernels.
 We provide a more specific bound for the case of stationary kernels below.
-
-		\begin{corollary}[Rademacher Complexity Bound for Stationary Kernels]
-		\label{thm:rademacher_complexity_stationary_kernels_bound}
-
-			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
+%		
+%		\begin{corollary}[Rademacher Complexity Bound for Stationary Kernels]
+%		\label{thm:rademacher_complexity_stationary_kernels_bound}
+%	
+%			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
 Suppose that $k_{\theta}$ is a family of positive definite stationary kernels.
@@
 For any $\tilde{\theta} \in \Theta$ and set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the resulting class of kernel embedding classifiers $F_{n}(\Theta(\tilde{\theta}), \Lambda)$ defined over $\theta \in \Theta(\tilde{\theta}), \lambda \in \Lambda$ is bounded by
-
-			\begin{equation}
-				\mathcal{R}_{n}(F_{n}(\Theta(\tilde{\theta}), \Lambda)) \leq 2 \rho \sqrt{k_{\tilde{\theta}}(0, 0)}.
-			\end{equation}
-
-			\begin{proof}
-
-				Observe that $k_{\tilde{\theta}}(0, 0)$ is an upper bound for $k_{\theta}(x, x)$ for all $x \in \mathcal{X}$ and $\theta \in \Theta$,
-
-				\begin{equation}
-					\begin{aligned}
-						k_{\theta}(x, x) = \tilde{k}_{\theta}( \| x - x \| ) = \tilde{k}_{\theta}( \| 0 \| ) = k_{\theta}(0, 0) \leq k_{\tilde{\theta}}(0, 0),
-					\end{aligned}
-				\end{equation}
-
-				We simply choose $\alpha^{2} = k_{\tilde{\theta}}(0, 0)$ in \cref{thm:rademacher_complexity_bound}.
-			\end{proof}
-
-		\end{corollary}
-
-		\Cref{thm:rademacher_complexity_stationary_kernels_bound} motivates the choice $\alpha^{2}(\theta) = k_{\theta}(0, 0) = \sigma_{f}^{2}$ for stationary radial basis type kernels such as the Gaussian or Mat\'{e}rn kernels, where $\sigma_{f}$ is the sensitivity \citep{rasmussen2006gaussian} of the stationary kernel, which we employ in \cref{alg:kernel_embedding_classifier_training} when the kernel is stationary.
-
-	\subsection{Expected Risk Bounds}
-	\label{app:expected_risk_bounds}
-
-		In order to quantify the performance of the kernel embedding classifier, we specify a loss function $\mathcal{L} : \mathcal{Y} \times \mathcal{A} \to [0, \infty)$, where $\mathcal{L}(y, f(x))$ measures the loss of a decision function $f : \mathcal{X} \to \mathcal{A}$ on a paired example $x \in \mathcal{X}$ and label $y \in \mathcal{Y}$.
+%		
+%			\begin{equation}
+%				\mathcal{R}_{n}(F_{n}(\Theta(\tilde{\theta}), \Lambda)) \leq 2 \rho \sqrt{k_{\tilde{\theta}}(0, 0)}.
+%			\end{equation}
+%			
+%			\begin{proof}
+%				
+%				Observe that $k_{\tilde{\theta}}(0, 0)$ is an upper bound for $k_{\theta}(x, x)$ for all $x \in \mathcal{X}$ and $\theta \in \Theta$,
+%				
+%				\begin{equation}
+%					\begin{aligned}
+%						k_{\theta}(x, x) = \tilde{k}_{\theta}( \| x - x \| ) = \tilde{k}_{\theta}( \| 0 \| ) = k_{\theta}(0, 0) \leq k_{\tilde{\theta}}(0, 0),
+%					\end{aligned}
+%				\end{equation}
+%				
+%				We simply choose $\alpha^{2} = k_{\tilde{\theta}}(0, 0)$ in \cref{thm:rademacher_complexity_bound}.
+%			\end{proof}
+%		
+%		\end{corollary}
+%	
+%		\Cref{thm:rademacher_complexity_stationary_kernels_bound} motivates the choice $\alpha^{2}(\theta) = k_{\theta}(0, 0) = \sigma_{f}^{2}$ for stationary radial basis type kernels such as the Gaussian or Mat\'{e}rn kernels, where $\sigma_{f}$ is the sensitivity \citep{rasmussen2006gaussian} of the stationary kernel, which we employ in \cref{alg:kernel_embedding_classifier_training} when the kernel is stationary.
+%
+%	\subsection{Expected Risk Bounds}
+%	\label{app:expected_risk_bounds}
+%	
+%		In order to quantify the performance of the kernel embedding classifier, we specify a loss function $\mathcal{L} : \mathcal{Y} \times \mathcal{A} \to [0, \infty)$, where $\mathcal{L}(y, f(x))$ measures the loss of a decision function $f : \mathcal{X} \to \mathcal{A}$ on a paired example $x \in \mathcal{X}$ and label $y \in \mathcal{Y}$.
 In the kernel embedding classification context, the decision function is $\bvec{f}_{\theta, \lambda} : \mathcal{X} \to \mathbb{R}^{m}$, with $\mathcal{A} = \mathbb{R}^{m}$ and $\mathcal{Y} = \mathbb{N}_{m}$.
 The loss function is to capture the desire for $\bvec{y}^{T} \bvec{f}_{\theta, \lambda}(x) = \bvec{f}_{y}^{(\theta, \lambda)}(x)$ to be high for all likely test points $x \in \mathcal{X}$ and $y \in \mathcal{Y}$.
-
-		A suitable choice of the loss function in the probabilistic multiclass classification context is the cross entropy loss,
-
-		\begin{equation}
-			\mathcal{L}(y, \bvec{f}(x)) := - \log{\bvec{y}^{T} \bvec{f}(x)} = - \log{f_{y}(x)},
-		\end{equation}
-
-		where $\bvec{f}(x)$ are the inferred decision probability estimates of each class for the example $x \in \mathcal{X}$.
+%		
+%		A suitable choice of the loss function in the probabilistic multiclass classification context is the cross entropy loss,
+%		
+%		\begin{equation}
+%			\mathcal{L}(y, \bvec{f}(x)) := - \log{\bvec{y}^{T} \bvec{f}(x)} = - \log{f_{y}(x)},
+%		\end{equation}
+%		
+%		where $\bvec{f}(x)$ are the inferred decision probability estimates of each class for the example $x \in \mathcal{X}$.
 Since logarithms explode at zero, in practice the probability estimate is often clipped from below at a predetermined threshold $\epsilon \in (0, 1)$.
@@
 Consequently, with the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$, we define the effective cross entropy loss as
-
-		\begin{equation}
-			\mathcal{L}_{\epsilon}(y, \bvec{f}(x)) := - \log{ [\bvec{y}^{T} \bvec{f}(x)]_{\epsilon}^{1} } = - \log{ [f_{y}(x)]_{\epsilon}^{1} },
-		\label{eq:cross_entropy_loss}
-		\end{equation}
-
-		In this way, our cross entropy loss \eqref{eq:cross_entropy_loss} is both bounded and positive.
+%		
+%		\begin{equation}
+%			\mathcal{L}_{\epsilon}(y, \bvec{f}(x)) := - \log{ [\bvec{y}^{T} \bvec{f}(x)]_{\epsilon}^{1} } = - \log{ [f_{y}(x)]_{\epsilon}^{1} },
+%		\label{eq:cross_entropy_loss}
+%		\end{equation}
+%		
+%		In this way, our cross entropy loss \eqref{eq:cross_entropy_loss} is both bounded and positive.
 In our subsequent analysis, we require that our loss function has an image in $[0, 1]$.
 To do this, we simply rescale the loss function by dividing it by its largest value,
-
-		\begin{equation}
-			\begin{aligned}
-				\bar{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) &:= \frac{1}{M_{\epsilon}} \mathcal{L}_{\epsilon}(y, \bvec{f}(x)) = - \frac{1}{M_{\epsilon}} \log{ [f_{y}(x)]_{\epsilon}^{1} }, \\
-				M_{\epsilon} &:= - \log{\epsilon}.
-			\end{aligned}
-		\label{eq:normalised_cross_entropy_loss}
-		\end{equation}
-
-		We will refer to \eqref{eq:normalised_cross_entropy_loss} as the normalised cross entropy loss. We then further define the centred normalised cross entropy loss,
-
-		\begin{equation}
-			\tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) := \bar{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) - \bar{\mathcal{L}}_{\epsilon}(y, \bvec{0}) = - \frac{1}{M_{\epsilon}} \log{ [f_{y}(x)]_{\epsilon}^{1} } - 1.
-		\label{eq:centred_normalised_cross_entropy_loss}
-		\end{equation}
-
-		With the normalised cross entropy loss \eqref{eq:normalised_cross_entropy_loss} as our loss function, we now employ Theorem 8 of \cite{bartlett2002rademacher} for this loss and provide a bound for the expected normalised cross entropy loss for an unseen test example.
-
-		\begin{lemma}[Expected Risk Bound]
-		\label{thm:expected_normalised_cross_entropy_loss_bound}
-			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
-
-			\begin{equation}
-				\frac{1}{M_{\epsilon}} \mathbb{E}[\mathcal{L}_{\epsilon}(Y, f(X))] \leq \frac{1}{n M_{\epsilon}} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + \mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}}.
-			\label{eq:expected_loss_bound}
-			\end{equation}
-
-			\begin{proof}
-				Since $\bar{\mathcal{L}}_{\epsilon} : \mathcal{Y} \times \mathcal{A} \to [0, 1]$ has a unit range and dominates itself, $\bar{\mathcal{L}}_{\epsilon}(y, f(x)) \leq \bar{\mathcal{L}}_{\epsilon}(y, f(x))$, the result follows directly from Theorem 8 of \cite{bartlett2002rademacher}.
+%		
+%		\begin{equation}
+%			\begin{aligned}
+%				\bar{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) &:= \frac{1}{M_{\epsilon}} \mathcal{L}_{\epsilon}(y, \bvec{f}(x)) = - \frac{1}{M_{\epsilon}} \log{ [f_{y}(x)]_{\epsilon}^{1} }, \\
+%				M_{\epsilon} &:= - \log{\epsilon}.
+%			\end{aligned}
+%		\label{eq:normalised_cross_entropy_loss}
+%		\end{equation}
+%		
+%		We will refer to \eqref{eq:normalised_cross_entropy_loss} as the normalised cross entropy loss. We then further define the centred normalised cross entropy loss,
+%		
+%		\begin{equation}
+%			\tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) := \bar{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) - \bar{\mathcal{L}}_{\epsilon}(y, \bvec{0}) = - \frac{1}{M_{\epsilon}} \log{ [f_{y}(x)]_{\epsilon}^{1} } - 1.
+%		\label{eq:centred_normalised_cross_entropy_loss}
+%		\end{equation}
+%		
+%		With the normalised cross entropy loss \eqref{eq:normalised_cross_entropy_loss} as our loss function, we now employ Theorem 8 of \cite{bartlett2002rademacher} for this loss and provide a bound for the expected normalised cross entropy loss for an unseen test example.
+%		
+%		\begin{lemma}[Expected Risk Bound]
+%		\label{thm:expected_normalised_cross_entropy_loss_bound}
+%			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
+%			
+%			\begin{equation}
+%				\frac{1}{M_{\epsilon}} \mathbb{E}[\mathcal{L}_{\epsilon}(Y, f(X))] \leq \frac{1}{n M_{\epsilon}} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + \mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}}.
+%			\label{eq:expected_loss_bound}
+%			\end{equation}
+%			
+%			\begin{proof}
+%				Since $\bar{\mathcal{L}}_{\epsilon} : \mathcal{Y} \times \mathcal{A} \to [0, 1]$ has a unit range and dominates itself, $\bar{\mathcal{L}}_{\epsilon}(y, f(x)) \leq \bar{\mathcal{L}}_{\epsilon}(y, f(x))$, the result follows directly from Theorem 8 of \cite{bartlett2002rademacher}.
 We then use the definition \eqref{eq:normalised_cross_entropy_loss} for the normalised cross entropy loss.
-			\end{proof}
-		\end{lemma}
-
-		Equivalently, by definition \eqref{eq:predictor_class}, this result holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
+%			\end{proof}
+%		\end{lemma}
+%		
+%		Equivalently, by definition \eqref{eq:predictor_class}, this result holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
 The bound \eqref{eq:expected_loss_bound} involves the Rademacher complexity $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda))$ of the centred normalised cross entropy loss applied onto the class of functions $F_{n}(\Theta, \Lambda)$, and not just the Rademacher complexity $\mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$ of the class of functions $F_{n}(\Theta, \Lambda)$ itself.
@@
 We now proceed to bound the former with the latter, so that the former is also bounded by the bound on the latter \eqref{eq:rademacher_complexity_bound}.
-
-		\begin{lemma}[Rademacher Complexity Bound with Cross Entropy Loss]
-		\label{thm:rademacher_complexity_bound_with_cross_entropy_loss}
-
-			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of cross entropy loss applied onto the kernel embedding classifier is bounded by
-
-			\begin{equation}
-				\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 2 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \mathcal{R}_{n}(F_{n}(\Theta, \Lambda)),
-			\label{eq:composed_rademacher_complexity_bound}
-			\end{equation}
-
-			where $\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda) := \{(x, y) \mapsto \tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}_{\theta, \lambda}(x)) : \theta \in \Theta, \lambda \in \Lambda\}$.
-
-			\begin{proof}
-				Let $\tilde{\psi}(z) := - \frac{1}{M_{\epsilon}} \log{[z]_{\epsilon}^{1}} - 1$ so that $\tilde{\psi} : \mathbb{R} \to \mathbb{R}$ satisfies $\tilde{\psi}(0) = 0$.
+%		
+%		\begin{lemma}[Rademacher Complexity Bound with Cross Entropy Loss]
+%		\label{thm:rademacher_complexity_bound_with_cross_entropy_loss}
+%		
+%			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of cross entropy loss applied onto the kernel embedding classifier is bounded by
+%			
+%			\begin{equation}
+%				\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 2 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \mathcal{R}_{n}(F_{n}(\Theta, \Lambda)),
+%			\label{eq:composed_rademacher_complexity_bound}
+%			\end{equation}
+%			
+%			where $\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda) := \{(x, y) \mapsto \tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}_{\theta, \lambda}(x)) : \theta \in \Theta, \lambda \in \Lambda\}$.
+%			
+%			\begin{proof}
+%				Let $\tilde{\psi}(z) := - \frac{1}{M_{\epsilon}} \log{[z]_{\epsilon}^{1}} - 1$ so that $\tilde{\psi} : \mathbb{R} \to \mathbb{R}$ satisfies $\tilde{\psi}(0) = 0$.
 Then, the centered normalised cross entropy loss can be written as $\tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) = \tilde{\psi}(f_{y}(x))$.
@@
 We proceed to show that $\tilde{\psi}$ is Lipschitz by showing that the suprenum of its absolute derivative over all piecewise regions is finite, and thus infer its Lipschitz constant.
-
-				The real-valued function $\tilde{\psi}$ can be split into three piecewise regions over the real domain,
-
-				\begin{equation}
-					\tilde{\psi}(z) = \begin{cases}
-						0, \qquad &z \in (-\infty, \epsilon], \\
-						- \frac{1}{M_{\epsilon}}\log{z} - 1, \qquad & z \in (\epsilon, 1), \\
-						-1, & z \in [1, \infty).
-					\end{cases}
-				\end{equation}
-
-				The derivative over the regions $z \in (-\infty, \epsilon]$ and $z \in [1, \infty)$ is thus $0$ and the local Lipschitz constant over that region is thus $0$. We then focus on the other region,
-
-				\begin{equation}
-					\begin{aligned}
-						\sup_{z \in (\epsilon, 1)} | \tilde{\psi}'(z) | = \sup_{z \in (\epsilon, 1)} \bigg| - \frac{1}{z M_{\epsilon}} \bigg| = \sup_{z \in (\epsilon, 1)} \frac{1}{z M_{\epsilon}} = \frac{1}{\epsilon M_{\epsilon}} = \frac{1}{\epsilon \log{\frac{1}{\epsilon}}}.
-					\end{aligned}
-				\end{equation}
-
-				Thus, $\tilde{\psi}$ is Lipschitz with a Lipschitz constant of $L_{\tilde{\psi}} = \frac{1}{\epsilon \log{\frac{1}{\epsilon}}}$.
-
-				For a given general loss function $\mathcal{L}$, \citet[Corollary 3.17]{ledoux2013probability} proved that if there exists a Lipschitz real-valued function $\psi : \mathbb{R} \to \mathbb{R}$, $\psi(0) = 0$, with constant $L_{\psi}$ such that $\mathcal{L}(y, f(x)) = \psi(f_{y}(x))$, then $\mathcal{R}_{n}(\mathcal{L} \circ F) \leq 2 L_{\psi} \mathcal{R}_{n}(F)$ for any class of functions $F$.
+%				
+%				The real-valued function $\tilde{\psi}$ can be split into three piecewise regions over the real domain,
+%				
+%				\begin{equation}
+%					\tilde{\psi}(z) = \begin{cases}
+%						0, \qquad &z \in (-\infty, \epsilon], \\
+%						- \frac{1}{M_{\epsilon}}\log{z} - 1, \qquad & z \in (\epsilon, 1), \\
+%						-1, & z \in [1, \infty).
+%					\end{cases}
+%				\end{equation}
+%				
+%				The derivative over the regions $z \in (-\infty, \epsilon]$ and $z \in [1, \infty)$ is thus $0$ and the local Lipschitz constant over that region is thus $0$. We then focus on the other region,
+%				
+%				\begin{equation}
+%					\begin{aligned}
+%						\sup_{z \in (\epsilon, 1)} | \tilde{\psi}'(z) | = \sup_{z \in (\epsilon, 1)} \bigg| - \frac{1}{z M_{\epsilon}} \bigg| = \sup_{z \in (\epsilon, 1)} \frac{1}{z M_{\epsilon}} = \frac{1}{\epsilon M_{\epsilon}} = \frac{1}{\epsilon \log{\frac{1}{\epsilon}}}.
+%					\end{aligned}
+%				\end{equation}
+%				
+%				Thus, $\tilde{\psi}$ is Lipschitz with a Lipschitz constant of $L_{\tilde{\psi}} = \frac{1}{\epsilon \log{\frac{1}{\epsilon}}}$.
+%				
+%				For a given general loss function $\mathcal{L}$, \citet[Corollary 3.17]{ledoux2013probability} proved that if there exists a Lipschitz real-valued function $\psi : \mathbb{R} \to \mathbb{R}$, $\psi(0) = 0$, with constant $L_{\psi}$ such that $\mathcal{L}(y, f(x)) = \psi(f_{y}(x))$, then $\mathcal{R}_{n}(\mathcal{L} \circ F) \leq 2 L_{\psi} \mathcal{R}_{n}(F)$ for any class of functions $F$.
 This result is also described in \citet[Theorem 12.4]{bartlett2002rademacher}.
-
-				Applying this result to our loss function with $\mathcal{L} = \tilde{\mathcal{L}}_{\epsilon}$ with $\psi = \tilde{\psi}$ and $F = F_{n}(\Theta, \Lambda)$, we have $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 2 L_{\tilde{\psi}} \mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$, which proves the claim.
-			\end{proof}
-		\end{lemma}
-
-		The bound \eqref{eq:composed_rademacher_complexity_bound} in \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss} will be the bridge that relates the expected cross entropy loss over our function class to the Rademacher complexity of our function class.
+%				
+%				Applying this result to our loss function with $\mathcal{L} = \tilde{\mathcal{L}}_{\epsilon}$ with $\psi = \tilde{\psi}$ and $F = F_{n}(\Theta, \Lambda)$, we have $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 2 L_{\tilde{\psi}} \mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$, which proves the claim.
+%			\end{proof}
+%		\end{lemma}
+%		
+%		The bound \eqref{eq:composed_rademacher_complexity_bound} in \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss} will be the bridge that relates the expected cross entropy loss over our function class to the Rademacher complexity of our function class.
 We now proceed to state the main theorem which forms the backbone of our learning algorithm for the kernel embedding classifier.
-
-		\begin{lemma}[General Expected Risk Bound for the Kernel Embedding Classifier]
-			\label{thm:expected_loss_bound_for_kec}
-
-			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
+%		
+%		\begin{lemma}[General Expected Risk Bound for the Kernel Embedding Classifier]
+%			\label{thm:expected_loss_bound_for_kec}
+%			
+%			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
 Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$, $\alpha > 0$, is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
 For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
-
-			\begin{equation}
-				\frac{1}{M_{\epsilon}} \mathbb{E}[\mathcal{L}_{\epsilon}(Y, f(X))] \leq \frac{1}{n M_{\epsilon}} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
-			\label{eq:expected_loss_bound_for_kec}
-			\end{equation}
-
-			for any $\epsilon \in (0, 1)$. Equivalently, the bound \eqref{eq:expected_loss_bound_for_kec} holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
-
-			\begin{proof}
-				From \cref{thm:rademacher_complexity_bound}, we have $\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) \leq 2 \alpha \rho$.
+%			
+%			\begin{equation}
+%				\frac{1}{M_{\epsilon}} \mathbb{E}[\mathcal{L}_{\epsilon}(Y, f(X))] \leq \frac{1}{n M_{\epsilon}} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
+%			\label{eq:expected_loss_bound_for_kec}
+%			\end{equation}
+%			
+%			for any $\epsilon \in (0, 1)$. Equivalently, the bound \eqref{eq:expected_loss_bound_for_kec} holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
+%	
+%			\begin{proof}
+%				From \cref{thm:rademacher_complexity_bound}, we have $\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) \leq 2 \alpha \rho$.
 Further, from \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss}, we have $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 2 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$.
@@
 We then apply this inequality to \cref{thm:expected_normalised_cross_entropy_loss_bound}, which proves the claim.
-
-			\end{proof}
-		\end{lemma}
-
-		Similar to many learning theoretic bounds, the expected risk bound \eqref{eq:expected_loss_bound_for_kec} is composed of three qualitatively different terms.
+%
+%			\end{proof}
+%		\end{lemma}
+%
+%		Similar to many learning theoretic bounds, the expected risk bound \eqref{eq:expected_loss_bound_for_kec} is composed of three qualitatively different terms.
 The first term is a training loss or data fit term, which is a measure of how poorly the decision function $f$ is performing on a given training dataset.
@@
 The third term is a statistical constant which plays no specific role to the function class.
-
-		We will eventually be minimising the first two terms over some class of functions $f \in F_{n}(\Theta, \Lambda)$ with some approach, as a proxy to minimising the actual expected risk.
+%		
+%		We will eventually be minimising the first two terms over some class of functions $f \in F_{n}(\Theta, \Lambda)$ with some approach, as a proxy to minimising the actual expected risk.
 It would be fruitful to develop an intuition for the tightness of the bound from the contributions of the training loss term and the model complexity term.
 Since, like the expected loss, the training loss term is always in the unit range $[0, 1]$, we focus on understanding the tightness of the bound contributed from the complexity term.
-
-		Consider a clipped cross entropy loss with either a very small clipping factor $\epsilon \approx 0$, or a very large clipping factor $\epsilon \approx 1$.
+%		
+%		Consider a clipped cross entropy loss with either a very small clipping factor $\epsilon \approx 0$, or a very large clipping factor $\epsilon \approx 1$.
 In this scenario, $\epsilon \log{\frac{1}{\epsilon}}$ would be very small, so that the coefficient on the complexity term would then be very large, regardless of what the complexity bound factors $\alpha$ and $\rho$ are.
 As a result, intuitively, this bound is unlikely to be tight due to the large coefficient on the complexity term.
-
-		Consequently, it would then be natural to consider a middle-ground choice of the cross entropy loss where this bound is the most tight by varying $\epsilon \in (0, 1)$.
+%		
+%		Consequently, it would then be natural to consider a middle-ground choice of the cross entropy loss where this bound is the most tight by varying $\epsilon \in (0, 1)$.
 Since $\epsilon \log{\frac{1}{\epsilon}}$ is maximised at $\epsilon = \frac{1}{e}$ for a maximal value of $\frac{1}{e}$, such a choice in the clipping factor would indeed yield the tightest bound for the complexity bound in terms of the bounding slack of the result stated in \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss}.
-
-		This is great news for the complexity term.
+%		 
+%		This is great news for the complexity term.
 What about the the training loss term?
@@
 In other words, by using a slightly larger clipping factor than usual, we have seemingly lost the faster convergence properties from using a cross entropy loss.
-
-		Nevertheless, observe that for such a clipping factor $\epsilon = e^{-1}$, the normalisation constant becomes $M_{e^{-1}} = - \log{\frac{1}{e}} = 1$, so that it is effectively removed.
+%		
+%		Nevertheless, observe that for such a clipping factor $\epsilon = e^{-1}$, the normalisation constant becomes $M_{e^{-1}} = - \log{\frac{1}{e}} = 1$, so that it is effectively removed.
 Furthermore, we also have the following simple upper bound for the cross entropy loss clipped at $\epsilon = e^{-1}$,
-
-		\begin{equation}
-			\bar{\mathcal{L}}_{e^{-1}}(y, f(x)) = \mathcal{L}_{e^{-1}}(y, f(x)) \leq \mathcal{L}_{\epsilon}(y, f(x)) \quad \forall \epsilon \in (0, e^{-1}), x \in \mathcal{X}, y \in \mathcal{Y}.
-		\label{eq:loss_inequality}
-		\end{equation}
-
-		To see why inequality \eqref{eq:loss_inequality} holds, note that $[f_{y}(x)]_{\epsilon}^{1} \leq [f_{y}(x)]_{e^{-1}}^{1}$ holds for all $\epsilon \in (0, e^{-1}), x \in \mathcal{X}, y \in \mathcal{Y}$.
+%		
+%		\begin{equation}
+%			\bar{\mathcal{L}}_{e^{-1}}(y, f(x)) = \mathcal{L}_{e^{-1}}(y, f(x)) \leq \mathcal{L}_{\epsilon}(y, f(x)) \quad \forall \epsilon \in (0, e^{-1}), x \in \mathcal{X}, y \in \mathcal{Y}.
+%		\label{eq:loss_inequality}
+%		\end{equation}
+%		
+%		To see why inequality \eqref{eq:loss_inequality} holds, note that $[f_{y}(x)]_{\epsilon}^{1} \leq [f_{y}(x)]_{e^{-1}}^{1}$ holds for all $\epsilon \in (0, e^{-1}), x \in \mathcal{X}, y \in \mathcal{Y}$.
 Applying negative log to both sides yields the inequality from definition \eqref{eq:cross_entropy_loss}.
-
-		Therefore, we propose to choose $\epsilon = e^{-1}$, and then replace replace $\mathcal{L}_{e^{-1}}$ with $\mathcal{L}_{\epsilon}$ for some new generic $\epsilon \in (0, e^{-1})$ much smaller than $e^{-1}$ on the training loss terms.
+%
+%		Therefore, we propose to choose $\epsilon = e^{-1}$, and then replace replace $\mathcal{L}_{e^{-1}}$ with $\mathcal{L}_{\epsilon}$ for some new generic $\epsilon \in (0, e^{-1})$ much smaller than $e^{-1}$ on the training loss terms.
 In this way, we still maintain an upper bound for the training loss term.
 While this bound would not necessarily be tight for high training losses, the gradients from the high training loss would drive the system to a lower training loss, where the bound would become tight again as equality holds in \eqref{eq:loss_inequality} whenever $f_{y}(x) \geq e^{-1}$.
-
-		The above intuition motivates the result in the following theorem.
-
-		\begin{theorem}[Specific Expected Risk Bound for the Kernel Embedding Classifier]
-			\label{thm:specific_expected_loss_bound_for_kec}
-
-			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
+%		
+%		The above intuition motivates the result in the following theorem.
+%	
+%		\begin{theorem}[Specific Expected Risk Bound for the Kernel Embedding Classifier]
+%			\label{thm:specific_expected_loss_bound_for_kec}
+%			
+%			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
 Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
 For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
-
-			\begin{equation}
-			\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 e \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
-			\label{eq:specific_expected_loss_bound_for_kec}
-			\end{equation}
-
-			for any $\epsilon \in (0, e^{-1})$.
+%			
+%			\begin{equation}
+%			\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 e \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
+%			\label{eq:specific_expected_loss_bound_for_kec}
+%			\end{equation}
+%			
+%			for any $\epsilon \in (0, e^{-1})$.
 Equivalently, the bound \eqref{eq:specific_expected_loss_bound_for_kec} holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
-
-			\begin{proof}
-
-				We first apply \cref{thm:expected_loss_bound_for_kec} with $\epsilon = e^{-1}$,
-
-				\begin{equation}
-					\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{e^{-1}}(Y_{i}, f(X_{i})) + 4 e \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}}.
-				\end{equation}
-
-				For any $\epsilon \in (0, e^{-1})$, the inequality $\mathcal{L}_{e^{-1}}(Y_{i}, f(X_{i})) \leq \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i}))$ holds almost surely (a.s.) due to the deterministic inequality \eqref{eq:loss_inequality}.
+%			
+%			\begin{proof}
+%				
+%				We first apply \cref{thm:expected_loss_bound_for_kec} with $\epsilon = e^{-1}$,
+%				
+%				\begin{equation}
+%					\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{e^{-1}}(Y_{i}, f(X_{i})) + 4 e \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}}.
+%				\end{equation}
+%				
+%				For any $\epsilon \in (0, e^{-1})$, the inequality $\mathcal{L}_{e^{-1}}(Y_{i}, f(X_{i})) \leq \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i}))$ holds almost surely (a.s.) due to the deterministic inequality \eqref{eq:loss_inequality}.
 These sets of inequalities together proves the claim.
-			\end{proof}
-		\end{theorem}
-
-	\subsection{Expected Risk Bounds for Hyperparameter Learning}
-	\label{app:expected_risk_bounds_for_hyperparameter_learning}
-
-		We are now ready to use the result of \cref{thm:specific_expected_loss_bound_for_kec} to derive a specific expected risk bound for a given choice of hyperparameters $\theta \in \Theta$ and $\lambda \in \Lambda$ of the kernel embedding classifier, and not just for a general set of hyperparameters.
+%			\end{proof}
+%		\end{theorem}
+%
+%	\subsection{Expected Risk Bounds for Hyperparameter Learning}
+%	\label{app:expected_risk_bounds_for_hyperparameter_learning}
+%	
+%		We are now ready to use the result of \cref{thm:specific_expected_loss_bound_for_kec} to derive a specific expected risk bound for a given choice of hyperparameters $\theta \in \Theta$ and $\lambda \in \Lambda$ of the kernel embedding classifier, and not just for a general set of hyperparameters.
 We focus on kernels $k_{\theta}$ that are bounded over the domain $\mathcal{X}$ in the sense that for each $\theta \in \Theta$, $k_{\theta}(x, x) < \infty$ for all $x \in \mathcal{X}$.
-
-		For some kernel parameters $\tilde{\theta} \in \Theta$ and regularisation parameter $\tilde{\lambda} \in \Lambda$, we construct a subset of hyperparameters (kernel parameters and regularisation parameters) $\Xi(\tilde{\theta}, \tilde{\lambda}) \subseteq \Theta \times \Lambda$ such that
-
-		\begin{equation}
-			\Xi(\tilde{\theta}, \tilde{\lambda}) := \{ (\theta, \lambda) \in \Theta \times \Lambda : \| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}, \; k_{\theta}(x, x) \leq \alpha^{2}(\tilde{\theta}) := \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x) \} \\
-			\label{eq:hyperparameter_subset_definition}
-		\end{equation}
-
-		Clearly, this subset is non-empty, since $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ is itself an element of this subset.
+%		
+%		For some kernel parameters $\tilde{\theta} \in \Theta$ and regularisation parameter $\tilde{\lambda} \in \Lambda$, we construct a subset of hyperparameters (kernel parameters and regularisation parameters) $\Xi(\tilde{\theta}, \tilde{\lambda}) \subseteq \Theta \times \Lambda$ such that
+%
+%		\begin{equation}
+%			\Xi(\tilde{\theta}, \tilde{\lambda}) := \{ (\theta, \lambda) \in \Theta \times \Lambda : \| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}, \; k_{\theta}(x, x) \leq \alpha^{2}(\tilde{\theta}) := \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x) \} \\
+%			\label{eq:hyperparameter_subset_definition}
+%		\end{equation}
+%		
+%		Clearly, this subset is non-empty, since $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ is itself an element of this subset.
 Note that $\alpha : \Theta \to \mathbb{R}_{+}$ must necessarily exist as the kernel family $k_{\theta}$ is assumed to be bounded over the domain $\mathcal{X}$.
 The class of kernel embedding classifiers over this subset of hyperparameters is
-
-		\begin{equation}
-			F_{n}(\Xi(\tilde{\theta}, \tilde{\lambda})) := \{\bvec{f}_{\theta, \lambda}(x) : (\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda}) \}.
-		\end{equation}
-
-		Thus, we can assert that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ is bounded for all $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, and that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$ is bounded in RKHS norm for all $x \in \mathcal{X}, (\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$.
+%		
+%		\begin{equation}
+%			F_{n}(\Xi(\tilde{\theta}, \tilde{\lambda})) := \{\bvec{f}_{\theta, \lambda}(x) : (\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda}) \}.
+%		\end{equation}
+%		
+%		Thus, we can assert that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ is bounded for all $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, and that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$ is bounded in RKHS norm for all $x \in \mathcal{X}, (\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$.
 By \cref{thm:specific_expected_loss_bound_for_kec}, we can now claim the following.
-
-		\begin{lemma}[General Expected Risk Bound for KEC Hyperparameter Learning]
-			\label{thm:general_expected_risk_bound_hyperparameter_learning}
-
-			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ satisfies
-
-			\begin{equation}
-				\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e \sqrt{\sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)} \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}} + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
-			\label{eq:general_expected_risk_bound_hyperparameter_learning}
-			\end{equation}
-
-			for every $\epsilon \in (0, e^{-1})$, where
-
-			\begin{equation}
-				\begin{aligned}
-					\bvec{f}_{\theta, \lambda}(x) :=& \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \bvec{k}_{\theta}(x), \\
-					\| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}} =& \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\tilde{\theta}} + n \tilde{\lambda} I)^{-1} K_{\tilde{\theta}} (K_{\tilde{\theta}} + n \tilde{\lambda} I)^{-1} \bvec{Y}\bigg)}.
-				\end{aligned}
-			\end{equation}
-
-			\begin{proof}
-				We first apply \cref{thm:specific_expected_loss_bound_for_kec} with the choice of $\rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ and $\alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$.
+%
+%		\begin{lemma}[General Expected Risk Bound for KEC Hyperparameter Learning]
+%			\label{thm:general_expected_risk_bound_hyperparameter_learning}
+%			
+%			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ satisfies
+%			
+%			\begin{equation}
+%				\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e \sqrt{\sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)} \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}} + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
+%			\label{eq:general_expected_risk_bound_hyperparameter_learning}
+%			\end{equation}
+%			
+%			for every $\epsilon \in (0, e^{-1})$, where 
+%			
+%			\begin{equation}
+%				\begin{aligned}
+%					\bvec{f}_{\theta, \lambda}(x) :=& \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \bvec{k}_{\theta}(x), \\
+%					\| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}} =& \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\tilde{\theta}} + n \tilde{\lambda} I)^{-1} K_{\tilde{\theta}} (K_{\tilde{\theta}} + n \tilde{\lambda} I)^{-1} \bvec{Y}\bigg)}.
+%				\end{aligned}
+%			\end{equation}
+%			
+%			\begin{proof}
+%				We first apply \cref{thm:specific_expected_loss_bound_for_kec} with the choice of $\rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ and $\alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$.
 The inequality \eqref{eq:specific_expected_loss_bound_for_kec} then only holds for a subset of kernel parameters and regularisations $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ as defined by \eqref{eq:hyperparameter_subset_definition}.
-			\end{proof}
-		\end{lemma}
-
-		Since inequality \eqref{eq:general_expected_risk_bound_hyperparameter_learning} holds for any $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ and we know that $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, we choose $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
+%			\end{proof}
+%		\end{lemma}
+%		
+%		Since inequality \eqref{eq:general_expected_risk_bound_hyperparameter_learning} holds for any $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ and we know that $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, we choose $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
 We now arrive at our final result from which we can bound the expected risk for a specific choice of hyperparameters $\theta \in \Theta$ and $\lambda \in \Lambda$.
-
-		\begin{theorem}[Expected Risk Bound for KEC Hyperparameter Learning]
-			\label{thm:expected_risk_bound_hyperparameter_learning}
-
-			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $\theta \in \Theta$ and $\lambda \in \Lambda$ satisfies
-
-			\begin{equation}
-				\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e r(\theta, \lambda) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
-			\label{eq:expected_risk_bound_hyperparameter_learning}
-			\end{equation}
-
-			for every $\epsilon \in (0, e^{-1})$, where
-
-			\begin{equation}
-				\begin{aligned}
-					\bvec{f}_{\theta, \lambda}(x) &:= \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \bvec{k}_{\theta}(x), \\
-					r(\theta, \lambda) &:= \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} K_{\theta} (K_{\theta} + n \lambda I)^{-1} \bvec{Y}\bigg) \sup_{x \in \mathcal{X}} k_{\theta}(x, x)}.
-				\end{aligned}
-			\end{equation}
-
-			\begin{proof}
-				We first apply \cref{thm:general_expected_risk_bound_hyperparameter_learning} with the choice of $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
+%		
+%		\begin{theorem}[Expected Risk Bound for KEC Hyperparameter Learning]
+%			\label{thm:expected_risk_bound_hyperparameter_learning}
+%			
+%			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $\theta \in \Theta$ and $\lambda \in \Lambda$ satisfies
+%			
+%			\begin{equation}
+%				\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e r(\theta, \lambda) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
+%			\label{eq:expected_risk_bound_hyperparameter_learning}
+%			\end{equation}
+%			
+%			for every $\epsilon \in (0, e^{-1})$, where 
+%			
+%			\begin{equation}
+%				\begin{aligned}
+%					\bvec{f}_{\theta, \lambda}(x) &:= \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \bvec{k}_{\theta}(x), \\
+%					r(\theta, \lambda) &:= \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} K_{\theta} (K_{\theta} + n \lambda I)^{-1} \bvec{Y}\bigg) \sup_{x \in \mathcal{X}} k_{\theta}(x, x)}.
+%				\end{aligned}
+%			\end{equation}
+%			
+%			\begin{proof}
+%				We first apply \cref{thm:general_expected_risk_bound_hyperparameter_learning} with the choice of $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
 We then replace the notation $\tilde{\theta} \rightarrow \theta$ and $\tilde{\lambda} \rightarrow \lambda$ back to avoid cluttered notation.
 Note that this should not be confused with the general $\theta$ and $\lambda$ from earlier theorems.
-			\end{proof}
-		\end{theorem}
-
-\newpage
-\section{Special Cases of Kernel Embedding Classifiers}
-\label{app:special_cases}
-
-	For a kernel embedding classifier, the modelling lies in the choice of the kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ over the input space $\mathcal{X}$.
+%			\end{proof}
+%		\end{theorem}
+%		
+%\newpage
+%\section{Special Cases of Kernel Embedding Classifiers}
+%\label{app:special_cases}
+%
+%	For a kernel embedding classifier, the modelling lies in the choice of the kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ over the input space $\mathcal{X}$.
 The only requirement for the kernel $k$ is that it is symmetric and positive definite, and thus we may construct richer and more expressive kernel families in any way subject to such requirements.
 Once such a kernel family is constructed, the kernel parameters $\theta$, as well as the regularisation parameter $\lambda$, can be learned effectively using the learning algorithm described in \cref{sec:hyperparameter_learning}.
-
-	One way to construct richer and more expressive kernels is to compose them from simpler kernels.
+%	
+%	One way to construct richer and more expressive kernels is to compose them from simpler kernels.
 For example, we can construct new kernels through convex combinations or products of multiple simpler kernels \citep{genton2001classes}.
@@
 Even better, we can construct the kernel family so that it is capable or learning such structural representations by itself, by parametrising such representations into the kernel.
-
-	In this section, we focus on special cases of the kernel embedding classifier where the kernel family is constructed through explicit feature maps.
+%	
+%	In this section, we focus on special cases of the kernel embedding classifier where the kernel family is constructed through explicit feature maps.
 This construction allows the incorporation of trainable domain specific structures and enables scalability to larger datasets.
@@
 Finally, we marry both constructions into the explicit kernel embedding network in \cref{app:explicit_kernel_embedding_network}, which provides a scalable and more applicable version of the deep kernel embedding network by placing a linear kernel on the network features.
-
-	In essence, we can categorise the kernel embedding classifier using two properties: the model width and the model depth.
+%
+%	In essence, we can categorise the kernel embedding classifier using two properties: the model width and the model depth.
 The model width represents the dimensionality of the feature space used to construct the linear decision boundaries.
@@
 We summarise those architectures in \cref{tab:kernel_embedding_classifier_variants}.
-
-	\begin{table}[h]
-		\caption{Properties of Kernel Embedding Classifier Architectures}
-		\label{tab:kernel_embedding_classifier_variants}
-		\centering
-		\begin{tabular}{lccccc}
-			KEC Variant & Width & Depth & Scalability & Flexibility & Typical Datasets  \\
-			\midrule
-			Implicit KEC & Wide & Shallow & Low & High & High or Low $d$, Low $n$ \\
-			Explicit KEC & Narrow & Shallow & High & Low & Low $d$, High $n$ \\
-			Implicit KEN &  Wide & Deep & Low & High & Structured $d$, Low $n$ \\
-			Explicit KEN & Narrow & Deep & High & High & Structured $d$, High $n$ \\ 
-		\end{tabular}
-	\end{table}
-
-	\subsection{Explicit Kernel Embedding Classifier}
-	\label{app:explicit_kernel_embedding_classifier}
-
-		The advantage of using a kernel-based classifier is that the kernel $k$ allows us to express nonlinearities in a simple way.
+%
+%	\begin{table}[h]
+%		\caption{Properties of Kernel Embedding Classifier Architectures}
+%		\label{tab:kernel_embedding_classifier_variants}
+%		\centering
+%		\begin{tabular}{lccccc}
+%			KEC Variant & Width & Depth & Scalability & Flexibility & Typical Datasets  \\
+%			\midrule
+%			Implicit KEC & Wide & Shallow & Low & High & High or Low $d$, Low $n$ \\
+%			Explicit KEC & Narrow & Shallow & High & Low & Low $d$, High $n$ \\
+%			Implicit KEN &  Wide & Deep & Low & High & Structured $d$, Low $n$ \\
+%			Explicit KEN & Narrow & Deep & High & High & Structured $d$, High $n$ \\ 
+%		\end{tabular}
+%	\end{table}
+%			
+%	\subsection{Explicit Kernel Embedding Classifier}
+%	\label{app:explicit_kernel_embedding_classifier}
+%	
+%		The advantage of using a kernel-based classifier is that the kernel $k$ allows us to express nonlinearities in a simple way.
 It does this by implicitly mapping the input space $\mathcal{X}$ to a high dimensional feature space $\mathcal{H}_{k}$ of non-linear basis functions such that decision boundaries become linear in that space.
@@
 In this way, the capacity of the model grows with the size of the dataset, which makes kernel methods nonparametric and very flexible, as it can adapt to the complexity of a dataset even with relatively simple kernels.
-
-		However, this elegant property is also the very reason that prevents kernel-based methods from scaling to larger datasets, as the size of such a gram matrix grows very quickly by $O(n^{2})$.
+%		
+%		However, this elegant property is also the very reason that prevents kernel-based methods from scaling to larger datasets, as the size of such a gram matrix grows very quickly by $O(n^{2})$.
 Many kernel-based methods also require the inversion of a regularised gram matrix, which has a time complexity of $O(n^{3})$, and cannot be easily parallelised like standard matrix multiplications.
 As such, inference on datasets beyond tens of thousands of observations quickly becomes impractical to perform with kernel-based techniques.
-
-		In order to scale to big datasets, instead of placing a kernel over the input space directly and let it implicitly define the feature space, we explicitly define a finite dimensional feature space $\mathcal{Z} \subseteq \mathbb{R}^{p}$ of lower dimension $p$, where $p < n$, and place a linear kernel over it.
+%		
+%		In order to scale to big datasets, instead of placing a kernel over the input space directly and let it implicitly define the feature space, we explicitly define a finite dimensional feature space $\mathcal{Z} \subseteq \mathbb{R}^{p}$ of lower dimension $p$, where $p < n$, and place a linear kernel over it.
 That is, we specify a family of explicit features maps $\varphi_{\theta} : \mathcal{X} \to \mathcal{Z}$, and place a linear kernel on top of these explicit features,
-
-		\begin{equation}
-			k_{\theta}(x, x') = \varphi_{\theta}(x)^{T} \varphi_{\theta}(x').
-		\end{equation}
-
-		By explicitly defining a finite dimensional feature space, the matrix to be inverted during both learning and inference in the kernel embedding classifier can be reduced from size $n \times n$ to size $p \times p$ by using the Woodbury matrix inversion identity \citep{higham2002accuracy}.
+%		
+%		\begin{equation}
+%			k_{\theta}(x, x') = \varphi_{\theta}(x)^{T} \varphi_{\theta}(x').
+%		\end{equation}
+%		
+%		By explicitly defining a finite dimensional feature space, the matrix to be inverted during both learning and inference in the kernel embedding classifier can be reduced from size $n \times n$ to size $p \times p$ by using the Woodbury matrix inversion identity \citep{higham2002accuracy}.
 We use this identity to modify \cref{alg:kernel_embedding_classifier_training} to \cref{alg:explicit_kernel_embedding_classifier_training} to exploit this computational speed up.
-
-		However, with a fixed and finite amount of feature basis, the model becomes parametric and its flexibility is compromised.
+%		
+%		However, with a fixed and finite amount of feature basis, the model becomes parametric and its flexibility is compromised.
 In other words, the model is narrow in the number of feature representations.
 We therefore turn to multi-layered feature compositions, where the flexibility of a model comes from the deep architecture instead of implicit high dimensional features.
-
-		\begin{algorithm}[tb]
-			\caption{Explicit KEC Hyperparameter Learning with Batch Stochastic Gradient Updates}
-			\label{alg:explicit_kernel_embedding_classifier_training}
-			\begin{algorithmic}[1]
-				\STATE {\bfseries Input:} feature family $\varphi_{\theta} : \mathcal{X} \to \mathcal{Z} \subseteq \mathbb{R}^{p}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial feature parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
-				\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
-				\REPEAT
-				\STATE Sample the next batch batch $\mathcal{I} \subseteq \mathbb{N}_{n}$, $| \mathcal{I} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I} = \mathbb{N}_{n}$)
-				\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
-				\STATE $Z_{\theta} \leftarrow \{\varphi_{\theta}(x_{i}) : i \in \mathcal{I}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times p}$
-				\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(Z_{\theta}^{T} Z_{\theta} + n_{b} \lambda I_{p}) \hspace{\fill} \in \mathbb{R}^{p \times p}$
-				\STATE $W_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Z_{\theta}^{T} Y) \hspace{\fill} \in \mathbb{R}^{p \times m}$
-				\STATE $P_{\theta, \lambda} \leftarrow Z_{\theta} W_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-				\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \alpha(\theta) \sqrt{\sum_{c = 1}^{m} \sum_{j = 1}^{p} (W_{\theta, \lambda})_{j, c}^{2}}$
-				\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
-				\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial q}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial q}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
-				\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
-			\end{algorithmic}
-		\end{algorithm}
-
-	\subsection{Kernel Embedding Network}
-	\label{app:kernel_embedding_network}
-
-		For many application domains, there are natural structures in the data.
+%
+%		\begin{algorithm}[tb]
+%			\caption{Explicit KEC Hyperparameter Learning with Batch Stochastic Gradient Updates}
+%			\label{alg:explicit_kernel_embedding_classifier_training}
+%			\begin{algorithmic}[1]
+%				\STATE {\bfseries Input:} feature family $\varphi_{\theta} : \mathcal{X} \to \mathcal{Z} \subseteq \mathbb{R}^{p}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial feature parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
+%				\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
+%				\REPEAT
+%				\STATE Sample the next batch batch $\mathcal{I} \subseteq \mathbb{N}_{n}$, $| \mathcal{I} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I} = \mathbb{N}_{n}$)
+%				\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
+%				\STATE $Z_{\theta} \leftarrow \{\varphi_{\theta}(x_{i}) : i \in \mathcal{I}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times p}$
+%				\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(Z_{\theta}^{T} Z_{\theta} + n_{b} \lambda I_{p}) \hspace{\fill} \in \mathbb{R}^{p \times p}$
+%				\STATE $W_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Z_{\theta}^{T} Y) \hspace{\fill} \in \mathbb{R}^{p \times m}$
+%				\STATE $P_{\theta, \lambda} \leftarrow Z_{\theta} W_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
+%				\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \alpha(\theta) \sqrt{\sum_{c = 1}^{m} \sum_{j = 1}^{p} (W_{\theta, \lambda})_{j, c}^{2}}$
+%				\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
+%				\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial q}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial q}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
+%				\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
+%			\end{algorithmic}
+%		\end{algorithm}
+%
+%	\subsection{Kernel Embedding Network}
+%	\label{app:kernel_embedding_network}
+%	
+%		For many application domains, there are natural structures in the data.
 For example, in image recognition, pixel dimensions are spatially correlated: nearby pixels are more related, and ordering between the pixel dimensions matter.
@@
 In this way, we can often benefit by including domain specific structures and features into our model.
-
-		In this section, we focus on constructing kernels for which inputs $x, x' \in \mathcal{X}$ is to undergo various stages of feature transformations before such it is passed into a simpler kernel $\kappa$ that captures the similarity between the representations.
+%
+%		In this section, we focus on constructing kernels for which inputs $x, x' \in \mathcal{X}$ is to undergo various stages of feature transformations before such it is passed into a simpler kernel $\kappa$ that captures the similarity between the representations.
 Specifically, we pay particular attention to feature transformations in the form of a perceptron, so that the cumulative stages of feature transformation become the (feed-forward) multi-layer perceptron that is familiar within the neural network literature.
-
-		Formally, let $\mathcal{F}_{0} := \mathcal{X}$ be the original input space.
+%	
+%		Formally, let $\mathcal{F}_{0} := \mathcal{X}$ be the original input space.
 The $j^{\mathrm{th}}$ layer of the network $\varphi^{(j)}_{\theta_{j}} : \mathcal{F}_{j - 1} \to \mathcal{F}_{j}, j = 1, 2, \dots, L$ is to transform features from the previous layer to features in the current layer, where $L$ is the total number of such feature transformation layers, and $\theta_{j} \in \Theta_{j}$ parametrises each of those transformations.
-
-		For example, in a typical multi-layer perceptron context, each layer can be written as $\varphi^{(j)}_{\theta_{j}}(x) = \sigma(W_{j} x + b_{j})$, where $W_{j}$ and $b_{j}$ are the weight and bias parameters of the layer, and $\sigma$ is an element-wise activation function, typically the rectified linear unit (ReLU) or the sigmoid.
+%		
+%		For example, in a typical multi-layer perceptron context, each layer can be written as $\varphi^{(j)}_{\theta_{j}}(x) = \sigma(W_{j} x + b_{j})$, where $W_{j}$ and $b_{j}$ are the weight and bias parameters of the layer, and $\sigma$ is an element-wise activation function, typically the rectified linear unit (ReLU) or the sigmoid.
 In this case, the layer is parametrised by $\theta_{j} = \{W_{j}, b_{j}\}$.
-
-		Let $\kappa_{\theta_{0}} : \mathcal{F}_{p} \times \mathcal{F}_{p} \to \mathbb{R}$ be parametrised by $\theta_{0} \in \Theta_{0}$. We will construct our kernel network $k$ by
-
-		\begin{equation}
-			k_{\theta}(x, x') := \kappa_{\theta_{0}}\Bigg( \varphi^{(L)}_{\theta_{L}}\bigg(\varphi^{(L - 1)}_{\theta_{L - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x)\big)\Big)\bigg), \varphi^{(L)}_{\theta_{L}}\bigg(\varphi^{(L - 1)}_{\theta_{L - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x')\big)\Big)\bigg) \Bigg)
-		\label{eq:deep_kernel_embedding_network}
-		\end{equation}
-
-		where $\theta = (\theta_{1}, \theta_{2}, \dots, \theta_{L -1}, \theta_{L}, \theta_{0}) \in \Theta = \Theta_{1} \otimes \Theta_{2} \otimes \dots \otimes \Theta_{L - 1} \otimes \Theta_{L} \otimes \Theta_{0}$ are the collection of all parameters of each layer and the kernel $\kappa$.
-
-		In order to train the multi-layered representations in an end-to-end fashion, we employ \cref{alg:kernel_embedding_classifier_training}.
+%		
+%		Let $\kappa_{\theta_{0}} : \mathcal{F}_{p} \times \mathcal{F}_{p} \to \mathbb{R}$ be parametrised by $\theta_{0} \in \Theta_{0}$. We will construct our kernel network $k$ by
+%		
+%		\begin{equation}
+%			k_{\theta}(x, x') := \kappa_{\theta_{0}}\Bigg( \varphi^{(L)}_{\theta_{L}}\bigg(\varphi^{(L - 1)}_{\theta_{L - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x)\big)\Big)\bigg), \varphi^{(L)}_{\theta_{L}}\bigg(\varphi^{(L - 1)}_{\theta_{L - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x')\big)\Big)\bigg) \Bigg)
+%		\label{eq:deep_kernel_embedding_network}
+%		\end{equation}
+%		
+%		where $\theta = (\theta_{1}, \theta_{2}, \dots, \theta_{L -1}, \theta_{L}, \theta_{0}) \in \Theta = \Theta_{1} \otimes \Theta_{2} \otimes \dots \otimes \Theta_{L - 1} \otimes \Theta_{L} \otimes \Theta_{0}$ are the collection of all parameters of each layer and the kernel $\kappa$.
+%		
+%		In order to train the multi-layered representations in an end-to-end fashion, we employ \cref{alg:kernel_embedding_classifier_training}.
 With a deep architecture, the feature representations the kernel embedding network can learn are very flexible, and can work very well for structured data by employing suitable network architectures.
-
-		If we choose to employ nonlinear kernels $\kappa$, the model architecture is also wide in that an even higher dimensional feature space is implicitly defined on top of the feature space of the last network layer.
+%		
+%		If we choose to employ nonlinear kernels $\kappa$, the model architecture is also wide in that an even higher dimensional feature space is implicitly defined on top of the feature space of the last network layer.
 Despite its supreme flexibility, this again prevents the model from being scalable.
 We therefore turn to the specific case where we employ a linear kernel $\kappa$ on top of the multi-layered features.
-
-	\subsection{Explicit Kernel Embedding Network}
-	\label{app:explicit_kernel_embedding_network}
-
-		The explicit kernel embedding network is simply a special case at the intersection of the explicit kernel embedding classifier and the kernel embedding network.
+%
+%	\subsection{Explicit Kernel Embedding Network}
+%	\label{app:explicit_kernel_embedding_network}
+%
+%		The explicit kernel embedding network is simply a special case at the intersection of the explicit kernel embedding classifier and the kernel embedding network.
 From the explicit KEC perspective, we simply choose $\varphi_{\theta}(x) = \varphi^{(L)}_{\theta_{L}}\big(\varphi^{(L - 1)}_{\theta_{L - 1}}(\dots\varphi^{(2)}_{\theta_{2}}(\varphi^{(1)}_{\theta_{1}}(x)))\big)$.
 From the KEN perspective, we simply choose $\kappa(z, z') = z^{T} z'$ to be a linear kernel.
-
-		This model architecture is a very practical and powerful form of the kernel embedding classifier.
+%		
+%		This model architecture is a very practical and powerful form of the kernel embedding classifier.
 By having a deep architecture, the classifier is still capable of learning flexible representations on structured data, while being able to scale to larger datasets due to the linear kernel at the output layer, provided that the dimensionality of the last layer is relatively small compared to the size of the dataset.
-
-		As a subclass of explicit KEC, we can employ \cref{alg:explicit_kernel_embedding_classifier_training} to learn the multi-layered features effectively.
+%		
+%		As a subclass of explicit KEC, we can employ \cref{alg:explicit_kernel_embedding_classifier_training} to learn the multi-layered features effectively.
 In fact, by not mapping the multi-layered features into a nonlinear kernel, the gradients for each network weight and bias are usually more pronounced, and learning is usually faster in comparison.

### 2017-05-19 cake.tex
Final Version

--- 2017-05-19 cake.tex
@@
 While the conditional embedding map $\hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the operator $\mathcal{U}$ that minimises the regularised least squares loss $\frac{1}{n} \sum_{i = 1}^{n} \| \psi(y_{i}) - \mathcal{U} \phi(x_{i}) \|_{\mathcal{H}_{l}}^{2} + \lambda \| \mathcal{U} \|_{HS}$ in the RKHS \citep{song2013kernel}, minimising this loss directly over $\theta \in \Theta, \lambda \in \Lambda$ for $\mathcal{U} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X}$ would trivially result in an overfitted model with $\lambda \rightarrow 0$.
-This implies that the notion of model complexity is especially important, yet the standard solutions employ either cross validation or nested loops separating $\theta$ and $\lambda$, both of which are heuristics and subject to design choices.
+This implies that the notion of model complexity is especially important, yet current standard solutions often employ either cross validation or nested optimisation separating $\theta$ and $\lambda$, both of which are heuristics and subject to design choices.
 
@@
 We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:kernel_embedding_classifier_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size.
-The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is performed only once after learning instead of once every learning iteration, and can be avoided by using kernel herding \citep{chen2010super} or other kernel data reduction technique to select subsets to estimate the already learned embedding.
+The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is performed only once after learning instead of once every learning iteration, and can be avoided by using kernel herding \citep{chen2010super} or other kernel data reduction technique to select data subsets that can estimate the already learned embedding.
 All further inference steps take $O(n^{2})$ time for back substitution.
@@
 			\STATE $P_{\theta, \lambda} \leftarrow K_{\theta} V_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-			\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
+			\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
 			\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
@@
 One particularly useful class of kernel embedding classifiers are those where the input kernel $k(x, x') = \langle \varphi(x), \varphi(x') \rangle$ is constructed from neural networks $\varphi : \mathcal{X} \to \mathbb{R}^{p}$ explicitly.
-We refer to these types of kernel embedding classifiers as kernel embedding networks (KEN).
+We refer to kernel embedding classifiers constructed this way as kernel embedding networks (KEN).
 Neural networks are typically defined by weights and biases of its hidden layers, which collectively define the parameters of the constructed kernel, and are thus trainable under our learning algorithm.
@@
 	For a linear class of predictors parametrised as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularisation to bound the Rademacher complexity, achieving tight generalisation bounds in the context of multi-label learning.
-The KEC predictor \eqref{eq:empirical_decision_probability_vector} has the same linear form in the feature space, $\bvec{f}_{\theta, \lambda}(x) = \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \Phi_{\theta}^{T} \phi_{\theta}(x) = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$, where instead of learning the operator $W^{T}$ directory, we learn hyperparameters $\theta \in \Theta, \lambda \in \Lambda$ for the empirical conditional embedding map $\mathcal{U}^{(\theta, \lambda)}_{Y | X}$ to learn the features $\phi_{\theta}(x)$.
+The KEC predictor \eqref{eq:empirical_decision_probability_vector} has the same linear form in the feature space, $\bvec{f}_{\theta, \lambda}(x) = \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \Phi_{\theta}^{T} \phi_{\theta}(x) = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$, where instead of learning the operator $W^{T}$ directory, we learn hyperparameters $\theta \in \Theta, \lambda \in \Lambda$ for the empirical conditional embedding map $\mathcal{U}^{(\theta, \lambda)}_{Y | X}$ and thus also the features $\phi_{\theta}(x)$.
 \cite{xu2016local} extends the trace norm regularisation approach by considering the local Rademacher complexity on a subset of the predictor class, where they instead minimise the tail sum of the predictor singular values.
@@
 Classifiers are trained with the Adam optimiser \citep{kingma2014adam} in TensorFlow \citep{abadi2016tensorflow} with rate $\eta = 0.1$ and $\epsilon = 10^{-15}$ under the learning objective $q(\theta, \lambda)$ \eqref{eq:learning_objective}.
-Classifiers are trained for 1000 or 10000 iterations when using full or batch gradient updates respectively, regardless of convergence.
+Training is ran for 1000 or 10000 iterations when using full or batch gradient updates respectively, regardless of convergence.
 All attributes are scaled to the unit range.
@@
 The fully connected layer is trained with a drop out probability of 0.5 for both cases to allow direct comparison.
-The top right plot in \cref{fig:mnist_experiments} shows that the KEN learns convolutional features at a much faster rate, maintaining a higher test accuracy at all times.
-After 800 epochs, our convolutional KEN reaches a test accuracy of 99.48\%, compared to 99.26\% from the original CNN.
-This demonstrates that our learning algorithm can perform end-to-end learning with convolutional features from scratch, by placing a conditional embedding on a neural network.
+The top right plot in \cref{fig:mnist_experiments} shows that kernel embedding networks learn convolutional features at a much faster rate, maintaining a higher test accuracy at all epochs.
+After 800 epochs, our convolutional kernel embedding network reaches a test accuracy of 99.48\%, compared to 99.26\% from the original CNN.
+This demonstrates that our learning algorithm can perform end-to-end learning with convolutional features from scratch, by simply placing a conditional embedding on a neural network.
 The resulting classifier can outperform the original neural network in both convergence rate and accuracy.
@@
 
-	As kernel embedding classifiers are simply learned conditional embeddings, this framework can incorporated and extended in many ways into techniques that requires appropriately trained embeddings.
+	As kernel embedding classifiers are simply trainable conditional embeddings, this framework can incorporated and extended in many ways into techniques that requires appropriately learned kernel embeddings.
 In particular, nonparametric probabilistic inference can be carried out in the RKHS to obtain joint and reverse conditional embeddings, where mode decoding, density recovery, and sampling techniques can lead to effective generative models now that hyperparameters are learned.
-This line of probabilistic inference can potentially lead to Bayesian extensions to our framework.
+This line of approach can potentially lead to Bayesian extensions to our framework.
 We also envision a semi-supervised and one class extension to the KEC framework that can relax supervision in training.
 Moreover, instead of a Kronecker delta kernel, target label kernels with non-zero and potentially trainable similarities between distinct labels may capture label correlations better than our original framework.
-Finally, our framework and algorithm is simple, and developments in creating deeper connections and relationships with other kernel based models can be fruitful.
+Finally, our framework and algorithm is simple, and developments in establishing deeper connections and relationships with other kernel based models can be fruitful.
 
@@
 
-\newpage
-\appendix
-
-\section{Convergence Theorems for Kernel Embedding Classifiers}
-\label{app:convergence_theorems}
-
-	In this section we provide theorems, lemmas, and derivations for the convergence properties of the kernel embedding classifier.
-
-	We consider the case in which a dataset, represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$, is collected in a \textit{iid} fashion from some distribution $\mathbb{P}_{X Y}$.
-That is $\{X_{i}, Y_{i}\} \sim \mathbb{P}_{X Y}$ for all $i \in \mathbb{N}_{n}$ and each observed sample is independent from each other.
-Suppose we have an estimator function $\hat{f}^{(n)} : \mathcal{X} \to \mathbb{R}$ which is to estimate some target function  $f : \mathcal{X} \to \mathbb{R}$, usually but not necessarily derived from $\mathbb{P}_{Y |X }$, empirically using the collected dataset $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of size $n \in \mathbb{N}_{+}$.
-Here, we use the superscript $(n)$ to denote the estimator's dependence on the dataset.
-From this point on, we drop this superscript to avoid cluttered notation.
-However, one should keep in mind that $\hat{f}$ is estimated using the dataset $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ and is thus random over the possible data observation events $\omega \in \Omega$.
-We would like to provide a sense of the stochastic convergence of $\hat{f}$ to $f$ by providing an upper bound of their absolute pointwise difference $| \hat{f}(x) - f(x) |$, and show that such an upper bound converges to zero at some stochastic rate.
-Since the kernel embedding classifier is based on conditional embeddings (and, as we will show, is equivalent to a conditional embedding), this upper bound will be provided by the RKHS norm of the error between empirical and true conditional embeddings.
-Specifically, the empirical conditional embedding stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \cite[Theorem 6]{song2009hilbert}.
-That is,
-	\begin{equation}
-		\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists M_{\epsilon} > 0 \quad s.t.
-\quad \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
-	\label{eq:empirical_conditional_embedding_stochastic_convergence}
-	\end{equation}
-	\begin{theorem}[Pointwise and Uniform Convergence of Estimators based on Conditional Embeddings]
-		\label{thm:pointwise_uniform_convergence}
-		Suppose that $k(x, \cdot)$ is in the image of $C_{XX}$ and that there exists $0 \leq \gamma(x) < \infty$ such that for some estimator function $\hat{f} : \mathcal{X} \to \mathbb{R}$ and target function  $f : \mathcal{X} \to \mathbb{R}$,
-		\begin{equation}
-			| \hat{f}(x) - f(x) | \leq \gamma(x) \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}}, \forall x \in \mathcal{X},
-		\label{eq:estimator_error_bound}
-		\end{equation}
-		then the estimator $\hat{f}$ converges pointwise to the target $f$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-Further, if $\gamma(x) = \gamma$ is independent of $x \in \mathcal{X}$, then this convergence is uniform.
-
-		\begin{proof}
-
-			Suppose that there exists $0 \leq \gamma(x) < \infty$ such that \eqref{eq:estimator_error_bound} is satisfied.
-That is, the inequality \eqref{eq:estimator_error_bound} holds for all possible data observations $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$.
-For any constant $C$, the implication statement $\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C \implies | \hat{f}(x) - f(x) | \leq C \gamma(x)$ holds for all possible observation events $\omega \in \Omega$.
-Writing this explicitly in event space translates this to a probability statement,
-			\begin{equation}
-			\begin{aligned}
-				\{\omega \in \Omega : \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq C\} &\subseteq \{\omega \in \Omega : | \hat{f}(x) - f(x) | \leq C \gamma(x)\} \\
-				\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq C\Big] &\leq \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq C \gamma(x) \Big].
-			\label{eq:probability_statement}
-			\end{aligned}
-			\end{equation}
-			Since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is valid.
-By letting $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ in \eqref{eq:probability_statement}, we immediately have that the probability inequality in statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is also true if we replace $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|$ with $| \hat{f}(x) - f(x) |$ and $M_{\epsilon}$ with $\gamma(x) M_{\epsilon}$,
-			\begin{equation}
-			\begin{aligned}
-			\mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
-			\implies 1 - \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
-			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
-			\implies \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
-			\implies 1 - \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
-			\implies \mathbb{P}\Big[| \hat{f}(x) - f(x) | > \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon.
-			\end{aligned}	
-			\end{equation}
-			where we employed statement \eqref{eq:probability_statement} between the third and fourth line for $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-Therefore, since $M_{\epsilon}$ is arbitrary, define $\tilde{M}_{\epsilon}(x) := \gamma(x) M_{\epsilon}$ so that, with the above result, the statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} implies the following,
-			\begin{equation}
-				\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists \tilde{M}_{\epsilon}(x) > 0 \quad s.t.
-\quad \mathbb{P}\Big[\big| \hat{f}(x) - f(x) \big| > \tilde{M}_{\epsilon}(x) \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
-			\end{equation}
-			In other words, the function $\hat{f}$ stochastically converges pointwise to $f$ with a rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-The convergence is pointwise as the constant $\tilde{M}_{\epsilon}(x)$ may be different for each point $x \in \mathcal{X}$.
-If $\gamma(x) = \gamma$ such that $\tilde{M}_{\epsilon}(x) = \tilde{M}_{\epsilon}$ does not depend on $x \in \mathcal{X}$, then this stochastic convergence is uniform in its domain $\mathcal{X}$.
-		\end{proof}
-
-	\end{theorem}
-
-	With \cref{thm:pointwise_uniform_convergence}, we can now show the convergence of various estimators based on the conditional embedding, as long as we can show that their estimator error is upper bounded by a multiple of the conditional embedding error in the RKHS norm.
-As such, we turn to the convergence of the empirical decision probability function \eqref{eq:empirical_decision_probability} below.
-
-	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
-		\label{thm:probability_convergence}
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-
-		\begin{proof}
-
-			Consider the pointwise absolute difference between the decision probability and its empirical estimate,
-			\begin{equation}
-				\begin{aligned}
-					| \hat{p}_{c}(x) - p_{c}(x) | &= | \langle \hat{\mu}_{Y | X = x}, \mathbb{1}_{c} \rangle - \langle \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
-					&= | \langle \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
-					&\leq \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}},
-				\label{eq:decision_probability_error_upper_bound}
-				\end{aligned}
-			\end{equation}
-			where the last inequality follows from the Cauchy Schwarz inequality in a Hilbert space.
-
-			From \eqref{eq:indicator_function}, since $\mathbb{1}_{c} = \delta(c, \cdot)$ and using the fact that $\delta$ is a reproducing kernel, we have that for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-			\begin{equation}
-				\begin{aligned}
-					\big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}}^{2} = \langle \mathbb{1}_{c}, \mathbb{1}_{c} \rangle = \langle \delta(c, \cdot), \delta(c, \cdot) \rangle = \delta(c, c) = 1.
-				\label{eq:indicator_rkhs_norm}
-				\end{aligned}
-			\end{equation}
-			Therefore, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, $\hat{p}_{c}$ converges uniformly to $p_{c}$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-
-		\end{proof}
-	\end{theorem}
-
-	The above proof is for uniform convergence over all $x \in \mathcal{X}$ at the stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-Intuitively, however, for stationary zero-centred kernels like the Gaussian kernel, the convergence rate may be higher at regions of high data density, since the kernel effects, being centred around the training data, are stronger at these regions.
-The worse case convergence rate described here in the theorem would be a tight lower bound for regions in $\mathcal{X}$ with lower data density, where the kernel effects have decayed and most empirical probabilities are smaller and further from summing up to one.
-
-	Because the label space $\mathcal{Y} = \mathbb{N}_{m}$ is discrete and finite, \textit{bounded} functions $g \in \mathcal{H}_{\delta}$ in the RKHS are actually equivalent to their vector representations $\bvec{g} := \{g(c)\}_{c = 1}^{m}$, because one can always write $g = \sum_{c = 1}^{m} g(c) \delta(c, \cdot)$.
-This immediately implies that inner products in this space are simply the usual dot products in a Euclidean space, since
-	\begin{equation}
-		\begin{aligned}
-			\langle g_{1}, g_{2} \rangle_{\mathcal{H}_{\delta}} &= \bigg\langle \sum_{c = 1}^{m} g_{1}(c) \delta(c, \cdot), \sum_{c' = 1}^{m} g_{2}(c') \delta(c', \cdot)  \bigg\rangle_{\mathcal{H}_{\delta}} \\
-			&= \sum_{c = 1}^{m} \sum_{c' = 1}^{m} g_{1}(c) g_{2}(c') \langle \delta(c, \cdot), \delta(c', \cdot) \rangle_{\mathcal{H}_{\delta}} \\
-			&= \sum_{c = 1}^{m} g_{1}(c) g_{2}(c) \\
-			&= \bvec{g}_{1} \cdot \bvec{g}_{2}.
-		\end{aligned}
-	\end{equation}
-	Consequently, the RKHS norm for bounded functions $g \in \mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of its vector representation $\bvec{g}$,
-	\begin{equation}
-	\lVert g \rVert_{\mathcal{H}_{\delta}} = \lVert \bvec{g} \rVert_{\ell_{2}}.
-	\label{eq:rkhs_norm_is_l2_norm}
-	\end{equation}
-	A special and convenient result that arises due to this discrete and finite label space is that the decision probabilities and its empirical estimate are simply the conditional embeddings and its empirical estimate.
-
-	\begin{lemma}[Decision Probabilities are Conditional Embeddings]
-	\label{thm:probability_is_embedding}
-
-		The decision probability for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,
-		\begin{equation}
-			p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mu_{Y | X = x}(c).
-		\end{equation}
-		Therefore, $\bvec{p}(x) \equiv \mu_{Y | X = x}$.
-
-		\begin{proof}
-
-			Since indicator functions are the canonical features of the label RKHS $\mathcal{H}_{\delta}$, we employ the fact that expectations of indicator functions are probabilities to prove this claim,
-			\begin{equation}
-			\begin{aligned}
-				\mu_{Y | X = x}(c) :=& \mathbb{E}[l(Y, c) | X = x ]= \mathbb{E}[\delta(Y, c) | X = x] \\
-				=& \mathbb{E}[\mathbb{1}_{c}(Y) | X = x] = \mathbb{P}[Y \in \{c\} | X = x] \\
-				=& \mathbb{P}[Y = c | X = x] =: p_{c}(x).
-			\end{aligned}
-			\end{equation}
-		\end{proof}
-
-	\end{lemma}
-
-	\begin{lemma}[Empirical Decision Probabilities are Empirical Conditional Embeddings]
-	\label{thm:empirical_probability_is_embedding}
-
-		The empirical decision probability \eqref{eq:empirical_decision_probability} for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the empirical conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,
-		\begin{equation}
-			\hat{p}_{c}(x) = \hat{\mu}_{Y | X = x}(c).
-		\end{equation}
-		Therefore, $\hat{\bvec{p}}(x) \equiv \hat{\mu}_{Y | X = x}$.
-
-		\begin{proof}
-
-			Let the canonical feature maps of $\mathcal{X}$ and $\mathcal{Y}$ be $\phi(x) = k(x, \cdot)$ and $\psi(y) = l(y, \cdot) = \delta(y, \cdot)$, then the empirical conditional embedding is defined by
-			\begin{equation}
-				\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} \phi(x).
-			\end{equation}
-			By the reproducing property, the evaluation of $\hat{\mu}_{Y | X = x} \in \mathcal{H}_{l}$ is given by a dot product,
-			\begin{equation}
-				\begin{aligned}
-					\hat{\mu}_{Y | X = x}(c) &= \langle l(c, \cdot), \hat{\mu}_{Y | X = x} \rangle \\
-					&= \langle \psi(c), \hat{\mu}_{Y | X = x} \rangle \\
-					&= \psi(c)^{T} \hat{\mu}_{Y | X = x} \\
-					&= \psi(c)^{T} \hat{\mathcal{U}}_{Y | X} \phi(x) \\
-					&= \psi(c)^{T} \Psi (K + n \lambda I)^{-1} \Phi^{T} \phi(x) \\
-					&= \bvec{l}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x), \\
-				\end{aligned}
-			\end{equation}
-			where $\bvec{l}_{c} := \{l(y_{i}, c)\}_{i = 1}^{n}$ and $\bvec{k}_{x} := \{k(x_{i}, x)\}_{i = 1}^{n}$.
-While the notation $\bvec{l}_{c}$ is usually avoided due do its similarity to $\bvec{1}_{c}$, in this context they happen to represent equal quantities,
-			\begin{equation}
-				\bvec{l}_{c} := \{l(y_{i}, c)\}_{i = 1}^{n} = \{\delta(y_{i}, c)\}_{i = 1}^{n} = \{\mathbb{1}_{c}(y_{i})\}_{i = 1}^{n} =: \bvec{1}_{c}.
-			\end{equation}
-			The claim then immediately follows by the definition of our decision probability estimator,
-			\begin{equation}
-				\hat{\mu}_{Y | X = x}(c) = \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x) =: \hat{p}_{c}(x).
-			\end{equation}
-		\end{proof}
-
-	\end{lemma}
-
-	\Cref{thm:empirical_probability_is_embedding} shows that the decision function $\bvec{f}(x)$ \eqref{eq:empirical_decision_probability_vector} of a kernel embedding classifier is no more than the empirical conditional embedding estimated from the data.
-
-	Since we have identified the equivalence of decision probabilities and the conditional embedding, we can now also show that the empirical decision probability vector also converges to the true decision probability vector.
-
-	\begin{lemma}[Uniform Convergence of Empirical Decision Probability Vector Function in $\ell_{1}$ and $\ell_{2}$]
-	\label{thm:probability_vector_convergence}
-
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability vector function $\hat{\bvec{p}} : \mathcal{X} \to \mathbb{R}^{m}$ \eqref{eq:empirical_decision_probability_vector} converges uniformly to the true decision probability vector function $\bvec{p} : \mathcal{X} \to [0, 1]^{m}$ in the $\ell_{1}$-norm and $\ell_{2}$-norm, where $\bvec{p}(x) := \{p_{c}(x)\}_{c = 1}^{m}$, at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-
-		\begin{proof}
-			For convergence in $\ell_{1}$, we simply extend \cref{thm:probability_convergence}, which proved that each entry of $\hat{\bvec{p}}(x)$ converges pointwise uniformly at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ to the corresponding entry of $\bvec{p}(x)$.
-Since each entry converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the entire vector.
-More formally, from \eqref{eq:decision_probability_error_upper_bound} and \eqref{eq:indicator_rkhs_norm}, the $\ell_{1}$-norm of the difference can be bounded,
-			\begin{equation}
-				\begin{aligned}
-					{\lVert \hat{\bvec{p}}(x) - \bvec{p}(x) \rVert}_{\ell_{1}} :=& \sum_{c = 1}^{m} | \hat{p}_{c}(x) - p_{c}(x) | \\
-					\leq& \sum_{c = 1}^{m} \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \\
-					=& m \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}}
-				\end{aligned}
-			\end{equation}
-			Therefore, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = m$ independent of $x \in \mathcal{X}$, we have uniform convergence in $\ell_{1}$ where we replace all instances of $| \hat{f}(x) - f(x) |$ in the proof of \cref{thm:pointwise_uniform_convergence} with ${\lVert \hat{\bvec{p}}(x) - \bvec{p}(x) \rVert}_{\ell_{1}}$.
-
-			For convergence in $\ell_{2}$, we show that the $\ell_{2}$-norm of the difference between the true and empirical decision probability vector functions is the same as the RKHS norm of the difference between the true and empirical conditional embedding, which converges to zero at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $x \in \mathcal{X}$ and $c \in \mathcal{Y} = \mathbb{N}_{m}$ by \eqref{eq:empirical_conditional_embedding_stochastic_convergence}.
-To this end, we use \cref{thm:probability_is_embedding} and \cref{thm:empirical_probability_is_embedding} and write
-			\begin{equation}
-				\begin{aligned}
-					{\lVert \hat{\bvec{p}}(x)  - \bvec{p}(x) \rVert}_{\ell_{2}} &= {\lVert \{ \hat{p}_{c}(x) \}_{c = 1}^{m} - \{ p_{c}(x) \}_{c = 1}^{m} \rVert}_{\ell_{2}} \\
-					&= {\lVert \{ \hat{p}_{c}(x) - p_{c}(x) \}_{c = 1}^{m} \rVert}_{\ell_{2}} \\
-					&= {\lVert \{ \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c)\}_{c = 1}^{m} \rVert}_{\ell_{2}} \\
-					&= \| \hat{\bm{\mu}}_{Y | X = x} - \bm{\mu}_{Y | X = x}  \|_{\ell_{2}} \\
-					&= {\lVert \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}\rVert}_{\mathcal{H}_{\delta}},
-				\end{aligned}
-			\end{equation}
-			where the last equality comes from \eqref{eq:rkhs_norm_is_l2_norm} and the fact that the empirical and true conditional embeddings are bounded functions in the RKHS.
-Again, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, we have uniform convergence in $\ell_{2}$.
-		\end{proof}
-	\end{lemma}
-
-	\subsection{Information Entropy of Kernel Embedding Classifiers}
-	\label{app:information_entropy}
-
-		The kernel embedding classifier provides decision probabilities instead of just a single label prediction.
-Such a probabilistic classifier allows us to quantify the uncertainty of its predictions for any given example $x \in \mathcal{X}$ through the information entropy \citep{shannon1951prediction, jaynes1957information}.
-This is ideal for detecting the decision boundaries of the classifier and areas of low data density.
-
-		We present two main approaches for inferring the information entropy from the classifier.
-Specifically, we would like to infer estimates for $h(x) := \mathbb{H}[Y | X = x] = - \sum_{c = 1}^{m} p_{c}(x) \log{p_{c}(x)} $, the information entropy of the possible labels $Y$ for a given example $X = x$.
-
-		The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref{eq:empirical_decision_probability_clip_normalised}, at the query point $x \in \mathcal{X}$,
-		\begin{equation}
-			\tilde{h}(x) := - \sum_{c = 1}^{m} \tilde{p}_{c}(x) \log{\tilde{p}_{c}(x)}.
-		\label{eq:entropy_clip_normalise}
-		\end{equation}
-		We call \eqref{eq:entropy_clip_normalise} the \textit{clip-normalised information entropy}.
-Since $\tilde{p}_{c}(x)$ converges pointwise to $p_{c}(x)$ with increasing data, $\tilde{h}(x)$ also converges pointwise to $h(x)$.
-
-		Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information,
-		\begin{equation}
-			\begin{aligned}
-				\mathbb{H}[Y | X = x] &= - \sum_{c = 1}^{m} \mathbb{P}[Y = c| X = x] \log{\mathbb{P}[Y = c | X = x]} \\
-				&= \mathbb{E}[- \log{\mathbb{P}[Y | X = x]} | X = x] \\
-				&= \mathbb{E}[u_{x}(Y) | X = x],
-			\end{aligned}
-		\end{equation}
-		where $u_{x}(y) := - \log{\mathbb{P}[Y = y | X = x]}$ is the \textit{information} (in nats) we would gain when we discover that example $x$ actually has label $y$.
-Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$.
-If $u_{x} : \mathbb{N}_{m} \to \mathbb{R}$ is in the RKHS $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by $\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle$.
-This is the basis of our second approach.
-
-		Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$.
-We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the RKHS.
-Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref{eq:empirical_conditional_expectation} and estimate $h(x)$ by
-		\begin{equation}
-			\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle = \bvec{u}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x).
-		\end{equation}
-		Unfortunately, $u_{x}$ is not known exactly, since $\mathbb{P}[Y = y | X = x]$ is not known exactly.
-Instead, since $\hat{p}_{c}(x)$ is a consistent estimate for $\mathbb{P}[Y = c | X = x]$ by \cref{thm:probability_convergence}, we propose to replace $u_{x}(y)$ with the information of $\hat{p}_{y}(x)$.
-However, we cannot simply take the log of this estimator, as $\hat{p}_{y}(x)$ may produce non-positive estimates to the prediction probabilities.
-The straight forward way to mitigate this problem is to clip $\hat{p}_{y}(x)$ from the bottom by a very small number, before taking the log.
-However, experiments show that this produces non-smooth estimates over $\mathcal{X}$ and the degree of smoothness varies drastically between different choices of that small number.
-Instead, in virtue of the fact that $\lim_{p \to 0} - p \log{p} = 0$ even though $\lim_{p \to 0} - \log{p} = \infty$, we simply define the information estimate $\hat{u}_{x}(y)$ as zero if the empirical decision probability is non-positive,
-		\begin{equation}
-			\hat{u}_{x}(y) := \begin{cases}
-				- \log{\hat{p}_{y}(x)} & \mathrm{if } \quad \hat{p}_{y}(x) > 0 \\
-				0 & \mathrm{otherwise}. \end{cases}
-			\label{eq:empirical_information}
-		\end{equation}
-		It remains to show that $\hat{u}_{x} \in \mathcal{H}_{\delta}$.
-Indeed, the identity $\hat{u}_{x} = \sum_{c = 1}^{m} \hat{u}_{x}(c) \delta(c, \cdot)$ holds and thus $\hat{u}_{x}$ is in the span of the kernel canonical features.
-We then arrive at the following estimate for $h(x)$,
-		\begin{equation}
-			\hat{h}(x) := \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle = \hat{\bvec{u}}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x),
-		\label{eq:empirical_information_entropy}
-		\end{equation}
-		where $\hat{\bvec{u}}_{x} := \{\hat{u}_{x}(y_{i})\}_{i = 1}^{n}$.
-Similar to the case with decision probabilities \eqref{eq:decision_probability}, the information entropy estimate \eqref{eq:empirical_information_entropy} is not guaranteed to be non-negative.
-However, in practice these negative values are close to zero.
-Furthermore, negative estimated information entropy implies that the model is very confident about its prediction, and it suffices to simply clip the entropy at zero if strict information entropy is required.
-
-		Since this estimator is now based on the inner product between the empirical conditional embedding and another empirically estimate function, instead of between the empirical conditional embedding and a known function like the decision probability estimate, it is not immediately clear that such an estimator converges.
-Nevertheless, intuition tells us that the inner product between two converging quantities should converge.
-We proceed to show that this intuition is correct.
-
-		\begin{theorem}[Convergence of Empirical Information Entropy Function]
-			\label{thm:entropy_convergence}
-			Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical information entropy function $\hat{h} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_information_entropy} converges pointwise to the true information entropy function $h : \mathcal{X} \to [0, \infty)$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-
-			\begin{proof}
-				Since we are interested in the asymptotic properties of our estimators when $n \to \infty$, and we have proved that the empirical decision probabilities converges to the true probabilities (\cref{thm:probability_convergence}), the condition $\hat{p}_{c}(x) > 0$ holds for large $n$ such that we simply have $\hat{u}_{x}(c) = - \log{\hat{p}_{c}(x)}$.
-That is, the effects of clipping for the information estimate \eqref{eq:empirical_information} vanishes.
-
-				Consider the pointwise absolute difference between the empirical and true information entropy,
-				\begin{equation}
-					\begin{aligned}
-						| \hat{h}(x) - h(x) | &= | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
-						&= | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} + \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
-						&\leq | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | + | \langle \hat{\mu}_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} - \langle \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
-						&= | \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} - u_{x} \rangle_{\mathcal{H}_{\delta}} | + | \langle \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}, u_{x} \rangle_{\mathcal{H}_{\delta}} | \\
-						&\leq \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}} + \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| u_{x} \|_{\mathcal{H}_{\delta}},
-					\label{eq:information_entropy_bound}
-					\end{aligned}
-				\end{equation}
-				where the we used the triangle inequality and Cauchy Schwarz inequality in a Hilbert space respectively.
-Since $l = \delta$ is bounded, so is $\hat{\mu}_{Y | X = x}(c) = \sum_{i = 1}^{n} w_{i} \delta(y_{i}, c)$ for some embedding weights $w_{i}$ and all $c \in \mathbb{N}_{m}$, and thus its RKHS norm is finite for all $n \in \mathbb{N}_{n}$.
-Similarly, assuming that $p_{c}(x)$ is never exactly zero, $u_{x}(c)$ is also finite for all $c \in \mathbb{N}_{m}$ and thus so is its RKHS norm.
-We already know that $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$ stochastically converges to zero at the rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ \eqref{eq:empirical_conditional_embedding_stochastic_convergence}.
-Thus, it remains to bound $\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}}$ by a multiple of $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$.
-
-				To this end, we first use \cref{thm:probability_is_embedding} and \cref{thm:empirical_probability_is_embedding} and to express the theoretical and empirical information as the negative log of the embedding, so that it is explicitly written as a function of $c \in \mathcal{Y}$ in $\mathcal{H}_{\delta}$ indexed by $x \in \mathcal{X}$,
-				\begin{equation}
-					\begin{aligned}
-						u_{x}(c) &= - \log{p_{c}(x)} = -\log{\mu_{Y | X = x}(c)}, \\
-						\hat{u}_{x}(c) &= - \log{\hat{p}_{c}(x)} = -\log{\hat{\mu}_{Y | X = x}(c)}. \\
-					\end{aligned}
-				\end{equation}
-				Since $\log$ is a concave function, we have the property that $\log{a} - \log{b} \leq \frac{1}{b} (a - b)$.
-This allows us to bound $| \hat{u}_{x}(c) - u_{x}(c) |$ by $| \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |$ for all $c \in \mathbb{N}_{m}$,
-				\begin{equation}
-					\begin{aligned}
-						| \hat{u}_{x}(c) - u_{x}(c) | &= | \log{\hat{\mu}_{Y | X = x}(c)} - \log{\mu_{Y | X = x}(c)} | \\
-						&\leq \frac{1}{| \mu_{Y | X = x}(c) |} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) | \\
-						&\leq \alpha_{x} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |,
-					\end{aligned}
-				\end{equation}
-				where we define $\alpha_{x} := \max_{c \in \mathbb{N}_{m}} \frac{1}{| \mu_{Y | X = x}(c) |}$, which is well defined as the conditional embedding is bounded.
-Since the RKHS norm of bounded functions in $\mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of their vector representations \eqref{eq:rkhs_norm_is_l2_norm}, we have
-				\begin{equation}
-					\begin{aligned}
-						\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}}^{2} &= \| \hat{\bvec{u}}_{x} - \bvec{u}_{x} \|_{\ell_{2}}^{2} \\
-						&= \sum_{c = 1}^{m} | \hat{u}_{x}(c) - u_{x}(c) |^{2} \\
-						&\leq \sum_{c = 1}^{m} \alpha_{x}^{2} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |^{2} \\
-						&\leq \alpha_{x}^{2} \sum_{c = 1}^{m} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |^{2} \\
-						&\leq \alpha_{x}^{2} \| \hat{\bm{\mu}}_{Y | X = x} - \bm{\mu}_{Y | X = x}  \|_{\ell_{2}}^{2} \\
-						&\leq \alpha_{x}^{2} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}^{2}. \\
-					\end{aligned}
-				\end{equation}
-				Therefore, $\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}} \leq \alpha_{x} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$, and \eqref{eq:information_entropy_bound} becomes
-				\begin{equation}
-					\begin{aligned}
-						| \hat{h}(x) - h(x) | &\leq \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}} + \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| u_{x} \|_{\mathcal{H}_{\delta}} \\
-						&= \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}} \| u_{x} \|_{\mathcal{H}_{\delta}} \\
-						&= ( \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| u_{x} \|_{\mathcal{H}_{\delta}} ) \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}. \\
-					\end{aligned}
-				\end{equation}
-				Hence, with $\gamma(x) = \alpha_{x} \| \hat{\mu}_{Y | X = x} \|_{\mathcal{H}_{\delta}} + \| u_{x} \|_{\mathcal{H}_{\delta}}$, \cref{thm:pointwise_uniform_convergence} implies that $\hat{h}$ converges pointwise to $h$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-			\end{proof}
-		\end{theorem}
-
-\newpage
-\section{Learning Theoretic Bounds for Kernel Embedding Classifiers}
-\label{app:learning_theoretic_bounds}
-
-	In this section we derive Rademacher complexity bounds for kernel embedding classifiers, and show that it can be used in conjunction with cross entropy loss to bound the expected risk with high probability.
-
-	\subsection{Rademacher Complexity Bounds}
-	\label{app:rademacher_complexity_theorems}
-
-		Suppose a set of training data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ is drawn from $\mathbb{P}_{X Y}$ in an \textit{iid} fashion.
-We denote the one hot encoded target labels of $\{y_{i}\}_{i = 1}^{n}$ by $\bvec{y}_{i} := \{\mathbb{1}_{c}(y_{i})\}_{c = 1}^{m} \in \{0, 1\}^{m}$ and $\bvec{Y} := \begin{bmatrix} \bvec{y}_{1} & \bvec{y}_{2} & \cdots & \bvec{y}_{n} \end{bmatrix}^{T} \in \{0, 1\}^{n \times m}$.
-Similarly, let $\bvec{y} \in \{0, 1\}^{m}$ denote the one hot encoded target labels for a generic label $y \in \mathcal{Y}$.
-Let $k_{\theta} : \mathcal{X} \times \mathcal{X} \to [0, \infty)$ be a family of positive definite kernels indexed by $\theta \in \Theta$.
-As before, we define the shorthand notation for the gram matrices $K_{\theta} := \{k_{\theta}(x_{i}, x_{j}) : i \in \mathbb{N}_{n}, j \in \mathbb{N}_{n}\}$ and $\bvec{k}_{\theta}(x) := \{k_{\theta}(x_{i}, x) : i \in \mathbb{N}_{n}\}$, and $\lambda$ denotes the regularisation parameter of the conditional embedding \eqref{eq:empirical_conditional_embedding}.
-The kernel embedding classifier has a predictor form $\hat{\bvec{p}}(x) = \bvec{f}_{\theta, \lambda}(x)$ \eqref{eq:empirical_decision_probability_vector} defined by
-
-		\begin{equation}
-			\bvec{f}_{\theta, \lambda}(x) := \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \bvec{k}_{\theta}(x),
-		\label{eq:predictor}
-		\end{equation}
-
-		where each entry of the predictor $\bvec{f}_{\theta, \lambda}(x)$ is the decision probability estimate for $p_{c}(x)$.
-This defines the function class of the predictor over the kernel family and a set of regularisation parameters for any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$,
-
-		\begin{equation}
-			F_{n}(\Theta, \Lambda) := \{ \bvec{f}_{\theta, \lambda}(x) : \theta \in \Theta, \lambda \in \Lambda \}.
-		\label{eq:predictor_class}
-		\end{equation}
-
-		The predictor form \eqref{eq:predictor} is linear in the reproducing kernel Hilbert space $\mathcal{H}_{k_{\theta}}$ induced by $k_{\theta}$ in the sense that
-
-		\begin{equation}
-			\begin{aligned}
-				\bvec{f}_{\theta, \lambda}(x) &:= W_{\theta, \lambda}^{T} \phi_{\theta}(x), \\
-				W_{\theta, \lambda} &:= \Phi_{\theta} (K_{\theta} + n \lambda I)^{-1} \bvec{Y},
-			\end{aligned}
-		\label{eq:linear_predictor}
-		\end{equation}
-
-		where we decompose $\bvec{k}_{\theta}(x) = \Phi_{\theta}^{T} \phi_{\theta}(x)$ by the reproducing property.
-By \cref{thm:empirical_probability_is_embedding}, $\bvec{f}_{\theta, \lambda}(x) = \hat{\bvec{p}}_{\theta, \lambda}(x) = \hat{\mu}^{(\theta, \lambda)}_{Y | X = x} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$.
-Therefore, we have that $\hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \equiv W_{\theta, \lambda}^{T}$.
-Throughout this paper, inner products are defined in the Hilbert-Schmidt sense, which induces the Hilbert-Schmidt norm $\| \cdot \|_{HS}$ and generalises the Frobenius inner product with induced norm $\| \cdot \|_{\mathrm{tr}}$ for finite dimensional operators.
-Nevertheless, while they refer to the same quantity, we will use the standard notations $ \| \hat{\mathcal{U}}^{\theta, \lambda}_{Y | X} \|_{HS}$ as per the literature in Hilbert space embeddings and $\| W_{\theta, \lambda} \|_{\mathrm{tr}}$ as per the literature for linear classifiers.
-
-		\begin{theorem}[Rademacher Complexity Bound for Kernel Embedding Classifiers]
-		\label{thm:rademacher_complexity_bound}
-
-			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
-Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$, $\alpha > 0$, is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
-For any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of kernel embedding classifiers $F_{n}(\Theta, \Lambda)$ \eqref{eq:predictor_class} defined over $\theta \in \Theta, \lambda \in \Lambda$ is bounded by
-
-			\begin{equation}
-				\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) \leq 2 \alpha \rho.
-			\label{eq:rademacher_complexity_bound}
-			\end{equation}
-
-			\begin{proof}
-
-				The Rademacher complexity \citep[Definition 2]{bartlett2002rademacher} of the function class $F_{n}(\Theta, \Lambda)$ is
-
-				\begin{equation}
-					\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) := \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \frac{2}{n} \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg] = \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg],
-				\end{equation}
-
-				where $\sigma_{i}$ are \textit{iid} Rademacher random variables, taking values in $\{-1, 1\}$ with equal probability, and $X_{i}$ are \textit{iid} random variables from the same distribution $\mathbb{P}_{X}$ as our training data.
-We further define $\bm{\sigma} := \{\sigma_{i}\}_{i = 1}^{n}$.
-
-				We first bound the term inside the suprenum using the Cauchy Schwarz inequality,
-
-				\begin{equation}
-					\begin{aligned}
-						\Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\| &= \Big\| \sum_{i = 1}^{n} \sigma_{i} W_{\theta, \lambda}^{T} \phi_{\theta}(X_{i}) \Big\| \\
-						&= \Big\| W_{\theta, \lambda}^{T} \bm{\Phi}_{\theta} \bm{\sigma} \Big\| \\
-						&\leq \| W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \bm{\sigma} \| \\
-						&\leq \| W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta}^{T} \|_{\mathrm{tr}} \| \bm{\sigma} \| \\
-						&= \| W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} \| \bm{\sigma} \|,
-					\end{aligned}
-				\end{equation}
-
-				where we define the random operator $\bm{\Phi}_{\theta} := \begin{bmatrix} \phi(X_{1}) & \phi(X_{2}) & \cdots & \phi(X_{n}) \end{bmatrix}$.
-Note that this is distinct from $\Phi_{\theta}$, whose columns are the canonical RKHS features at the training observations and is not random.
-Now, random or not, $\bm{\sigma} := \{\sigma_{i}\}_{i = 1}^{n}$ is just a collection of values that are either $-1$ or $1$, so its norm is simply $\| \bm{\sigma} \| = \sqrt{n}$.
-We can then also compute the trace norm of the other random component $\bm{\Phi}_{\theta}$,
-
-				\begin{equation}
-					\begin{aligned}
-						\| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} :=& \sqrt{\mathrm{trace}(\bm{\Phi}_{\theta}^{T} \bm{\Phi}_{\theta})} \\
-						=& \sqrt{\mathrm{trace}(\bvec{K}_{\theta})} \\
-						=& \sqrt{\sum_{i = 1}^{n} k_{\theta}(X_{i}, X_{i})} \\
-						=& \sqrt{n} \sqrt{ \frac{1}{n} \sum_{i = 1}^{n} k_{\theta}(X_{i}, X_{i})} \\
-						\leq& \sqrt{n} \sqrt{ \frac{1}{n} \sum_{i = 1}^{n} \alpha^{2}} \\
-						=& \sqrt{n} \alpha,
-					\end{aligned}
-				\end{equation}
-
-				where the inequality comes from the assertion that $k_{\theta}(x, x) \leq \alpha^{2}$ for all $x \in \mathcal{X}, \theta \in \Theta$.
-This bounds all the random components in the expectation by a constant, so that later the expectation can vanish.
-
-				Using the assertion that $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ for all $\theta \in \Theta, \lambda \in \Lambda$, we can now bound Rademacher complexity,
-
-				\begin{equation}
-					\begin{aligned}
-						\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) &= \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg] \\
-						&\leq \frac{2}{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} \| \bm{\sigma} \| \bigg] \\
-						&= \frac{2}{n} \sqrt{n} \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \| \| \bm{\Phi}_{\theta} \|_{\mathrm{tr}} \bigg] \\
-						&\leq \frac{2}{n} \sqrt{n} \sqrt{n} \alpha \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \bigg] \\
-						&\leq 2 \alpha \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \bigg] \\
-						&= 2 \alpha \sup_{\theta \in \Theta, \lambda \in \Lambda} \|  W_{\theta, \lambda} \|_{\mathrm{tr}} \\
-						&\leq 2 \alpha \rho.
-					\end{aligned}
-				\end{equation}
-			\end{proof}
-		\end{theorem}
-
-		\Cref{thm:rademacher_complexity_bound} provides a generic Rademacher complexity bound for any type of kernel embedding classifier with a bounded positive definite kernel and bounded trace norm.
-One of the most widely used kernels in practice are the family of stationary kernels.
-We provide a more specific bound for the case of stationary kernels below.
-
-		\begin{corollary}[Rademacher Complexity Bound for Stationary Kernels]
-		\label{thm:rademacher_complexity_stationary_kernels_bound}
-
-			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
-Suppose that $k_{\theta}$ is a family of positive definite stationary kernels.
-That is, $k_{\theta} (x, x') = \tilde{k}_{\theta}( \| x - x' \| )$ for some real-valued function $\tilde{k} : [0, \infty) \to [0, \infty)$.
-Select $\tilde{\theta} \in \Theta$ and define $\Theta(\tilde{\theta})$ such that $k_{\theta}(0, 0) \leq k_{\tilde{\theta}}(0, 0)$ for all $\theta \in \Theta(\tilde{\theta})$.
-For any $\tilde{\theta} \in \Theta$ and set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the resulting class of kernel embedding classifiers $F_{n}(\Theta(\tilde{\theta}), \Lambda)$ defined over $\theta \in \Theta(\tilde{\theta}), \lambda \in \Lambda$ is bounded by
-
-			\begin{equation}
-				\mathcal{R}_{n}(F_{n}(\Theta(\tilde{\theta}), \Lambda)) \leq 2 \rho \sqrt{k_{\tilde{\theta}}(0, 0)}.
-			\end{equation}
-
-			\begin{proof}
-
-				Observe that $k_{\tilde{\theta}}(0, 0)$ is an upper bound for $k_{\theta}(x, x)$ for all $x \in \mathcal{X}$ and $\theta \in \Theta$,
-
-				\begin{equation}
-					\begin{aligned}
-						k_{\theta}(x, x) = \tilde{k}_{\theta}( \| x - x \| ) = \tilde{k}_{\theta}( \| 0 \| ) = k_{\theta}(0, 0) \leq k_{\tilde{\theta}}(0, 0),
-					\end{aligned}
-				\end{equation}
-
-				We simply choose $\alpha^{2} = k_{\tilde{\theta}}(0, 0)$ in \cref{thm:rademacher_complexity_bound}.
-			\end{proof}
-
-		\end{corollary}
-
-		\Cref{thm:rademacher_complexity_stationary_kernels_bound} motivates the choice $\alpha^{2}(\theta) = k_{\theta}(0, 0) = \sigma_{f}^{2}$ for stationary radial basis type kernels such as the Gaussian or Mat\'{e}rn kernels, where $\sigma_{f}$ is the sensitivity \citep{rasmussen2006gaussian} of the stationary kernel, which we employ in \cref{alg:kernel_embedding_classifier_training} when the kernel is stationary.
-
-	\subsection{Expected Risk Bounds}
-	\label{app:expected_risk_bounds}
-
-		In order to quantify the performance of the kernel embedding classifier, we specify a loss function $\mathcal{L} : \mathcal{Y} \times \mathcal{A} \to [0, \infty)$, where $\mathcal{L}(y, f(x))$ measures the loss of a decision function $f : \mathcal{X} \to \mathcal{A}$ on a paired example $x \in \mathcal{X}$ and label $y \in \mathcal{Y}$.
-In the kernel embedding classification context, the decision function is $\bvec{f}_{\theta, \lambda} : \mathcal{X} \to \mathbb{R}^{m}$, with $\mathcal{A} = \mathbb{R}^{m}$ and $\mathcal{Y} = \mathbb{N}_{m}$.
-The loss function is to capture the desire for $\bvec{y}^{T} \bvec{f}_{\theta, \lambda}(x) = \bvec{f}_{y}^{(\theta, \lambda)}(x)$ to be high for all likely test points $x \in \mathcal{X}$ and $y \in \mathcal{Y}$.
-
-		A suitable choice of the loss function in the probabilistic multiclass classification context is the cross entropy loss,
-
-		\begin{equation}
-			\mathcal{L}(y, \bvec{f}(x)) := - \log{\bvec{y}^{T} \bvec{f}(x)} = - \log{f_{y}(x)},
-		\end{equation}
-
-		where $\bvec{f}(x)$ are the inferred decision probability estimates of each class for the example $x \in \mathcal{X}$.
-Since logarithms explode at zero, in practice the probability estimate is often clipped from below at a predetermined threshold $\epsilon \in (0, 1)$.
-Furthermore, it is also convenient to clip the probability estimate from above at one to avoid negative losses, as further reward for high prediction probabilities are not necessary.
-In other words, assigning a probability estimate greater than one to the correct label is really just correctly assigning a probability estimate of one but with slight approximation error.
-Consequently, with the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$, we define the effective cross entropy loss as
-
-		\begin{equation}
-			\mathcal{L}_{\epsilon}(y, \bvec{f}(x)) := - \log{ [\bvec{y}^{T} \bvec{f}(x)]_{\epsilon}^{1} } = - \log{ [f_{y}(x)]_{\epsilon}^{1} },
-		\label{eq:cross_entropy_loss}
-		\end{equation}
-
-		In this way, our cross entropy loss \eqref{eq:cross_entropy_loss} is both bounded and positive.
-In our subsequent analysis, we require that our loss function has an image in $[0, 1]$.
-To do this, we simply rescale the loss function by dividing it by its largest value,
-
-		\begin{equation}
-			\begin{aligned}
-				\bar{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) &:= \frac{1}{M_{\epsilon}} \mathcal{L}_{\epsilon}(y, \bvec{f}(x)) = - \frac{1}{M_{\epsilon}} \log{ [f_{y}(x)]_{\epsilon}^{1} }, \\
-				M_{\epsilon} &:= - \log{\epsilon}.
-			\end{aligned}
-		\label{eq:normalised_cross_entropy_loss}
-		\end{equation}
-
-		We will refer to \eqref{eq:normalised_cross_entropy_loss} as the normalised cross entropy loss. We then further define the centred normalised cross entropy loss,
-
-		\begin{equation}
-			\tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) := \bar{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) - \bar{\mathcal{L}}_{\epsilon}(y, \bvec{0}) = - \frac{1}{M_{\epsilon}} \log{ [f_{y}(x)]_{\epsilon}^{1} } - 1.
-		\label{eq:centred_normalised_cross_entropy_loss}
-		\end{equation}
-
-		With the normalised cross entropy loss \eqref{eq:normalised_cross_entropy_loss} as our loss function, we now employ Theorem 8 of \cite{bartlett2002rademacher} for this loss and provide a bound for the expected normalised cross entropy loss for an unseen test example.
-
-		\begin{lemma}[Expected Risk Bound]
-		\label{thm:expected_normalised_cross_entropy_loss_bound}
-			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
-
-			\begin{equation}
-				\frac{1}{M_{\epsilon}} \mathbb{E}[\mathcal{L}_{\epsilon}(Y, f(X))] \leq \frac{1}{n M_{\epsilon}} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + \mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}}.
-			\label{eq:expected_loss_bound}
-			\end{equation}
-
-			\begin{proof}
-				Since $\bar{\mathcal{L}}_{\epsilon} : \mathcal{Y} \times \mathcal{A} \to [0, 1]$ has a unit range and dominates itself, $\bar{\mathcal{L}}_{\epsilon}(y, f(x)) \leq \bar{\mathcal{L}}_{\epsilon}(y, f(x))$, the result follows directly from Theorem 8 of \cite{bartlett2002rademacher}.
-We then use the definition \eqref{eq:normalised_cross_entropy_loss} for the normalised cross entropy loss.
-			\end{proof}
-		\end{lemma}
-
-		Equivalently, by definition \eqref{eq:predictor_class}, this result holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
-The bound \eqref{eq:expected_loss_bound} involves the Rademacher complexity $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda))$ of the centred normalised cross entropy loss applied onto the class of functions $F_{n}(\Theta, \Lambda)$, and not just the Rademacher complexity $\mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$ of the class of functions $F_{n}(\Theta, \Lambda)$ itself.
-In \cref{thm:rademacher_complexity_bound}, we have bounded the latter.
-We now proceed to bound the former with the latter, so that the former is also bounded by the bound on the latter \eqref{eq:rademacher_complexity_bound}.
-
-		\begin{lemma}[Rademacher Complexity Bound with Cross Entropy Loss]
-		\label{thm:rademacher_complexity_bound_with_cross_entropy_loss}
-
-			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of cross entropy loss applied onto the kernel embedding classifier is bounded by
-
-			\begin{equation}
-				\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 2 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \mathcal{R}_{n}(F_{n}(\Theta, \Lambda)),
-			\label{eq:composed_rademacher_complexity_bound}
-			\end{equation}
-
-			where $\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda) := \{(x, y) \mapsto \tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}_{\theta, \lambda}(x)) : \theta \in \Theta, \lambda \in \Lambda\}$.
-
-			\begin{proof}
-				Let $\tilde{\psi}(z) := - \frac{1}{M_{\epsilon}} \log{[z]_{\epsilon}^{1}} - 1$ so that $\tilde{\psi} : \mathbb{R} \to \mathbb{R}$ satisfies $\tilde{\psi}(0) = 0$.
-Then, the centered normalised cross entropy loss can be written as $\tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) = \tilde{\psi}(f_{y}(x))$.
-In particular, $\tilde{\psi}(z)$ is piecewise differentiable.
-We proceed to show that $\tilde{\psi}$ is Lipschitz by showing that the suprenum of its absolute derivative over all piecewise regions is finite, and thus infer its Lipschitz constant.
-
-				The real-valued function $\tilde{\psi}$ can be split into three piecewise regions over the real domain,
-
-				\begin{equation}
-					\tilde{\psi}(z) = \begin{cases}
-						0, \qquad &z \in (-\infty, \epsilon], \\
-						- \frac{1}{M_{\epsilon}}\log{z} - 1, \qquad & z \in (\epsilon, 1), \\
-						-1, & z \in [1, \infty).
-					\end{cases}
-				\end{equation}
-
-				The derivative over the regions $z \in (-\infty, \epsilon]$ and $z \in [1, \infty)$ is thus $0$ and the local Lipschitz constant over that region is thus $0$. We then focus on the other region,
-
-				\begin{equation}
-					\begin{aligned}
-						\sup_{z \in (\epsilon, 1)} | \tilde{\psi}'(z) | = \sup_{z \in (\epsilon, 1)} \bigg| - \frac{1}{z M_{\epsilon}} \bigg| = \sup_{z \in (\epsilon, 1)} \frac{1}{z M_{\epsilon}} = \frac{1}{\epsilon M_{\epsilon}} = \frac{1}{\epsilon \log{\frac{1}{\epsilon}}}.
-					\end{aligned}
-				\end{equation}
-
-				Thus, $\tilde{\psi}$ is Lipschitz with a Lipschitz constant of $L_{\tilde{\psi}} = \frac{1}{\epsilon \log{\frac{1}{\epsilon}}}$.
-
-				For a given general loss function $\mathcal{L}$, \citet[Corollary 3.17]{ledoux2013probability} proved that if there exists a Lipschitz real-valued function $\psi : \mathbb{R} \to \mathbb{R}$, $\psi(0) = 0$, with constant $L_{\psi}$ such that $\mathcal{L}(y, f(x)) = \psi(f_{y}(x))$, then $\mathcal{R}_{n}(\mathcal{L} \circ F) \leq 2 L_{\psi} \mathcal{R}_{n}(F)$ for any class of functions $F$.
-This result is also described in \citet[Theorem 12.4]{bartlett2002rademacher}.
-
-				Applying this result to our loss function with $\mathcal{L} = \tilde{\mathcal{L}}_{\epsilon}$ with $\psi = \tilde{\psi}$ and $F = F_{n}(\Theta, \Lambda)$, we have $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 2 L_{\tilde{\psi}} \mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$, which proves the claim.
-			\end{proof}
-		\end{lemma}
-
-		The bound \eqref{eq:composed_rademacher_complexity_bound} in \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss} will be the bridge that relates the expected cross entropy loss over our function class to the Rademacher complexity of our function class.
-We now proceed to state the main theorem which forms the backbone of our learning algorithm for the kernel embedding classifier.
-
-		\begin{lemma}[General Expected Risk Bound for the Kernel Embedding Classifier]
-			\label{thm:expected_loss_bound_for_kec}
-
-			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
-Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$, $\alpha > 0$, is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
-For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
-
-			\begin{equation}
-				\frac{1}{M_{\epsilon}} \mathbb{E}[\mathcal{L}_{\epsilon}(Y, f(X))] \leq \frac{1}{n M_{\epsilon}} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
-			\label{eq:expected_loss_bound_for_kec}
-			\end{equation}
-
-			for any $\epsilon \in (0, 1)$. Equivalently, the bound \eqref{eq:expected_loss_bound_for_kec} holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
-
-			\begin{proof}
-				From \cref{thm:rademacher_complexity_bound}, we have $\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) \leq 2 \alpha \rho$.
-Further, from \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss}, we have $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 2 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$.
-These are both deterministic inequalities, leading to $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 4 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \alpha \rho$.
-We then apply this inequality to \cref{thm:expected_normalised_cross_entropy_loss_bound}, which proves the claim.
-
-			\end{proof}
-		\end{lemma}
-
-		Similar to many learning theoretic bounds, the expected risk bound \eqref{eq:expected_loss_bound_for_kec} is composed of three qualitatively different terms.
-The first term is a training loss or data fit term, which is a measure of how poorly the decision function $f$ is performing on a given training dataset.
-The second term is a model complexity or regularisation term, which measures how complicated the model is.
-In this case, the model complexity is measured by the Rademacher complexity, which captures the expressiveness of the function class by quantifying how well the function class is able to shatter noise.
-The third term is a statistical constant which plays no specific role to the function class.
-
-		We will eventually be minimising the first two terms over some class of functions $f \in F_{n}(\Theta, \Lambda)$ with some approach, as a proxy to minimising the actual expected risk.
-It would be fruitful to develop an intuition for the tightness of the bound from the contributions of the training loss term and the model complexity term.
-Since, like the expected loss, the training loss term is always in the unit range $[0, 1]$, we focus on understanding the tightness of the bound contributed from the complexity term.
-
-		Consider a clipped cross entropy loss with either a very small clipping factor $\epsilon \approx 0$, or a very large clipping factor $\epsilon \approx 1$.
-In this scenario, $\epsilon \log{\frac{1}{\epsilon}}$ would be very small, so that the coefficient on the complexity term would then be very large, regardless of what the complexity bound factors $\alpha$ and $\rho$ are.
-As a result, intuitively, this bound is unlikely to be tight due to the large coefficient on the complexity term.
-
-		Consequently, it would then be natural to consider a middle-ground choice of the cross entropy loss where this bound is the most tight by varying $\epsilon \in (0, 1)$.
-Since $\epsilon \log{\frac{1}{\epsilon}}$ is maximised at $\epsilon = \frac{1}{e}$ for a maximal value of $\frac{1}{e}$, such a choice in the clipping factor would indeed yield the tightest bound for the complexity bound in terms of the bounding slack of the result stated in \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss}.
-
-		This is great news for the complexity term.
-What about the the training loss term?
-Intuition tells us that, with a clipping factor of $\epsilon = e^{-1}$ that is slightly more than a third of the way into the interval $(0, 1)$ from zero, the classifier is not being penalised as strongly for assigning probabilities smaller than $e^{-1}$ to observed classes as compared to very small values of $\epsilon$.
-Furthermore, beyond the clipping point, assigning even lower probabilities to the observations does not result in a higher loss.
-In practice, the cross entropy loss is renowned for its rapidly growing penalty as the probability assignment gets lower, which is advantageous when using a gradient based optimisation scheme.
-In this case, the gradients are large in magnitude and the classifier can adjust and fix these assignment errors relatively quickly.
-In other words, by using a slightly larger clipping factor than usual, we have seemingly lost the faster convergence properties from using a cross entropy loss.
-
-		Nevertheless, observe that for such a clipping factor $\epsilon = e^{-1}$, the normalisation constant becomes $M_{e^{-1}} = - \log{\frac{1}{e}} = 1$, so that it is effectively removed.
-Furthermore, we also have the following simple upper bound for the cross entropy loss clipped at $\epsilon = e^{-1}$,
-
-		\begin{equation}
-			\bar{\mathcal{L}}_{e^{-1}}(y, f(x)) = \mathcal{L}_{e^{-1}}(y, f(x)) \leq \mathcal{L}_{\epsilon}(y, f(x)) \quad \forall \epsilon \in (0, e^{-1}), x \in \mathcal{X}, y \in \mathcal{Y}.
-		\label{eq:loss_inequality}
-		\end{equation}
-
-		To see why inequality \eqref{eq:loss_inequality} holds, note that $[f_{y}(x)]_{\epsilon}^{1} \leq [f_{y}(x)]_{e^{-1}}^{1}$ holds for all $\epsilon \in (0, e^{-1}), x \in \mathcal{X}, y \in \mathcal{Y}$.
-Applying negative log to both sides yields the inequality from definition \eqref{eq:cross_entropy_loss}.
-
-		Therefore, we propose to choose $\epsilon = e^{-1}$, and then replace replace $\mathcal{L}_{e^{-1}}$ with $\mathcal{L}_{\epsilon}$ for some new generic $\epsilon \in (0, e^{-1})$ much smaller than $e^{-1}$ on the training loss terms.
-In this way, we still maintain an upper bound for the training loss term.
-While this bound would not necessarily be tight for high training losses, the gradients from the high training loss would drive the system to a lower training loss, where the bound would become tight again as equality holds in \eqref{eq:loss_inequality} whenever $f_{y}(x) \geq e^{-1}$.
-
-		The above intuition motivates the result in the following theorem.
-
-		\begin{theorem}[Specific Expected Risk Bound for the Kernel Embedding Classifier]
-			\label{thm:specific_expected_loss_bound_for_kec}
-
-			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
-Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
-For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
-
-			\begin{equation}
-			\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 e \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
-			\label{eq:specific_expected_loss_bound_for_kec}
-			\end{equation}
-
-			for any $\epsilon \in (0, e^{-1})$.
-Equivalently, the bound \eqref{eq:specific_expected_loss_bound_for_kec} holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
-
-			\begin{proof}
-
-				We first apply \cref{thm:expected_loss_bound_for_kec} with $\epsilon = e^{-1}$,
-
-				\begin{equation}
-					\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{e^{-1}}(Y_{i}, f(X_{i})) + 4 e \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}}.
-				\end{equation}
-
-				For any $\epsilon \in (0, e^{-1})$, the inequality $\mathcal{L}_{e^{-1}}(Y_{i}, f(X_{i})) \leq \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i}))$ holds almost surely (a.s.) due to the deterministic inequality \eqref{eq:loss_inequality}.
-These sets of inequalities together proves the claim.
-			\end{proof}
-		\end{theorem}
-
-	\subsection{Expected Risk Bounds for Hyperparameter Learning}
-	\label{app:expected_risk_bounds_for_hyperparameter_learning}
-
-		We are now ready to use the result of \cref{thm:specific_expected_loss_bound_for_kec} to derive a specific expected risk bound for a given choice of hyperparameters $\theta \in \Theta$ and $\lambda \in \Lambda$ of the kernel embedding classifier, and not just for a general set of hyperparameters.
-We focus on kernels $k_{\theta}$ that are bounded over the domain $\mathcal{X}$ in the sense that for each $\theta \in \Theta$, $k_{\theta}(x, x) < \infty$ for all $x \in \mathcal{X}$.
-
-		For some kernel parameters $\tilde{\theta} \in \Theta$ and regularisation parameter $\tilde{\lambda} \in \Lambda$, we construct a subset of hyperparameters (kernel parameters and regularisation parameters) $\Xi(\tilde{\theta}, \tilde{\lambda}) \subseteq \Theta \times \Lambda$ such that
-
-		\begin{equation}
-			\Xi(\tilde{\theta}, \tilde{\lambda}) := \{ (\theta, \lambda) \in \Theta \times \Lambda : \| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}, \; k_{\theta}(x, x) \leq \alpha^{2}(\tilde{\theta}) := \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x) \} \\
-			\label{eq:hyperparameter_subset_definition}
-		\end{equation}
-
-		Clearly, this subset is non-empty, since $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ is itself an element of this subset.
-Note that $\alpha : \Theta \to \mathbb{R}_{+}$ must necessarily exist as the kernel family $k_{\theta}$ is assumed to be bounded over the domain $\mathcal{X}$.
-The class of kernel embedding classifiers over this subset of hyperparameters is
-
-		\begin{equation}
-			F_{n}(\Xi(\tilde{\theta}, \tilde{\lambda})) := \{\bvec{f}_{\theta, \lambda}(x) : (\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda}) \}.
-		\end{equation}
-
-		Thus, we can assert that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ is bounded for all $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, and that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$ is bounded in RKHS norm for all $x \in \mathcal{X}, (\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$.
-By \cref{thm:specific_expected_loss_bound_for_kec}, we can now claim the following.
-
-		\begin{lemma}[General Expected Risk Bound for KEC Hyperparameter Learning]
-			\label{thm:general_expected_risk_bound_hyperparameter_learning}
-
-			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ satisfies
-
-			\begin{equation}
-				\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e \sqrt{\sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)} \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}} + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
-			\label{eq:general_expected_risk_bound_hyperparameter_learning}
-			\end{equation}
-
-			for every $\epsilon \in (0, e^{-1})$, where
-
-			\begin{equation}
-				\begin{aligned}
-					\bvec{f}_{\theta, \lambda}(x) :=& \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \bvec{k}_{\theta}(x), \\
-					\| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}} =& \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\tilde{\theta}} + n \tilde{\lambda} I)^{-1} K_{\tilde{\theta}} (K_{\tilde{\theta}} + n \tilde{\lambda} I)^{-1} \bvec{Y}\bigg)}.
-				\end{aligned}
-			\end{equation}
-
-			\begin{proof}
-				We first apply \cref{thm:specific_expected_loss_bound_for_kec} with the choice of $\rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ and $\alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$.
-The inequality \eqref{eq:specific_expected_loss_bound_for_kec} then only holds for a subset of kernel parameters and regularisations $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ as defined by \eqref{eq:hyperparameter_subset_definition}.
-			\end{proof}
-		\end{lemma}
-
-		Since inequality \eqref{eq:general_expected_risk_bound_hyperparameter_learning} holds for any $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ and we know that $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, we choose $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
-We now arrive at our final result from which we can bound the expected risk for a specific choice of hyperparameters $\theta \in \Theta$ and $\lambda \in \Lambda$.
-
-		\begin{theorem}[Expected Risk Bound for KEC Hyperparameter Learning]
-			\label{thm:expected_risk_bound_hyperparameter_learning}
-
-			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $\theta \in \Theta$ and $\lambda \in \Lambda$ satisfies
-
-			\begin{equation}
-				\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e r(\theta, \lambda) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
-			\label{eq:expected_risk_bound_hyperparameter_learning}
-			\end{equation}
-
-			for every $\epsilon \in (0, e^{-1})$, where
-
-			\begin{equation}
-				\begin{aligned}
-					\bvec{f}_{\theta, \lambda}(x) &:= \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \bvec{k}_{\theta}(x), \\
-					r(\theta, \lambda) &:= \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} K_{\theta} (K_{\theta} + n \lambda I)^{-1} \bvec{Y}\bigg) \sup_{x \in \mathcal{X}} k_{\theta}(x, x)}.
-				\end{aligned}
-			\end{equation}
-
-			\begin{proof}
-				We first apply \cref{thm:general_expected_risk_bound_hyperparameter_learning} with the choice of $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
-We then replace the notation $\tilde{\theta} \rightarrow \theta$ and $\tilde{\lambda} \rightarrow \lambda$ back to avoid cluttered notation.
-Note that this should not be confused with the general $\theta$ and $\lambda$ from earlier theorems.
-			\end{proof}
-		\end{theorem}
-
-\newpage
-\section{Special Cases of Kernel Embedding Classifiers}
-\label{app:special_cases}
-
-	For a kernel embedding classifier, the modelling lies in the choice of the kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ over the input space $\mathcal{X}$.
-The only requirement for the kernel $k$ is that it is symmetric and positive definite, and thus we may construct richer and more expressive kernel families in any way subject to such requirements.
-Once such a kernel family is constructed, the kernel parameters $\theta$, as well as the regularisation parameter $\lambda$, can be learned effectively using the learning algorithm described in \cref{sec:hyperparameter_learning}.
-
-	One way to construct richer and more expressive kernels is to compose them from simpler kernels.
-For example, we can construct new kernels through convex combinations or products of multiple simpler kernels \citep{genton2001classes}.
-Any new parameters, such as coefficients for linear combinations of simpler kernels, can be included into the kernel parameters $\theta$ and learned in the same way as before.
-Alternatively, there may be domain specific structures or representations within the data that can be exploited.
-We can then construct the kernel family by incorporating such structural representations into the kernel.
-Even better, we can construct the kernel family so that it is capable or learning such structural representations by itself, by parametrising such representations into the kernel.
-
-	In this section, we focus on special cases of the kernel embedding classifier where the kernel family is constructed through explicit feature maps.
-This construction allows the incorporation of trainable domain specific structures and enables scalability to larger datasets.
-We first begin by introducing the explicit kernel embedding classifier in \cref{app:explicit_kernel_embedding_classifier}, where explicit feature maps can be learned while enabling scalability to larger datasets.
-We then construct the kernel embedding network (KEN) in \cref{app:kernel_embedding_network}, where the kernel family is formed from multiple layers of learned representations before a simpler kernel encodes their similarity for inference.
-Finally, we marry both constructions into the explicit kernel embedding network in \cref{app:explicit_kernel_embedding_network}, which provides a scalable and more applicable version of the deep kernel embedding network by placing a linear kernel on the network features.
-
-	In essence, we can categorise the kernel embedding classifier using two properties: the model width and the model depth.
-The model width represents the dimensionality of the feature space used to construct the linear decision boundaries.
-The model depth represents the number of transformations used to map examples from the input space to the feature space.
-By implicitly defining a high dimensional feature space through simple transformations, typical nonlinear kernels produces classifiers that have a shallow but wide architecture.
-In contrast, the three kernel embedding classifier variants to be introduced in this section form other combinations of model architecture in both depth and width.
-Of course, this characterisation of architecture is not mutually exclusive.
-For example, a polynomial kernel can be seen as a nonlinear kernel where higher order polynomial features are implicitly defined, or as a linear kernel on explicit polynomial features.
-We summarise those architectures in \cref{tab:kernel_embedding_classifier_variants}.
-
-	\begin{table}[h]
-		\caption{Properties of Kernel Embedding Classifier Architectures}
-		\label{tab:kernel_embedding_classifier_variants}
-		\centering
-		\begin{tabular}{lccccc}
-			KEC Variant & Width & Depth & Scalability & Flexibility & Typical Datasets  \\
-			\midrule
-			Implicit KEC & Wide & Shallow & Low & High & High or Low $d$, Low $n$ \\
-			Explicit KEC & Narrow & Shallow & High & Low & Low $d$, High $n$ \\
-			Implicit KEN &  Wide & Deep & Low & High & Structured $d$, Low $n$ \\
-			Explicit KEN & Narrow & Deep & High & High & Structured $d$, High $n$ \\ 
-		\end{tabular}
-	\end{table}
-
-	\subsection{Explicit Kernel Embedding Classifier}
-	\label{app:explicit_kernel_embedding_classifier}
-
-		The advantage of using a kernel-based classifier is that the kernel $k$ allows us to express nonlinearities in a simple way.
-It does this by implicitly mapping the input space $\mathcal{X}$ to a high dimensional feature space $\mathcal{H}_{k}$ of non-linear basis functions such that decision boundaries become linear in that space.
-For many kernels, such as the Gaussian kernel defined over the Euclidean space, the feature space $\mathcal{H}_{k}$ has dimensionality that is uncountably infinite.
-Nevertheless, by virtue of the Representer Theorem \citep{kimeldorf1971some}, the resulting decision functions can be represented by a finite linear combination of kernels centred at the training data, and the kernel embedding classifier is no exception.
-This elegant and convenient result enables exact inference to be performed while only requiring a finite kernel gram matrix of the size of the dataset ($n \times n$) to be computed.
-In this way, the capacity of the model grows with the size of the dataset, which makes kernel methods nonparametric and very flexible, as it can adapt to the complexity of a dataset even with relatively simple kernels.
-
-		However, this elegant property is also the very reason that prevents kernel-based methods from scaling to larger datasets, as the size of such a gram matrix grows very quickly by $O(n^{2})$.
-Many kernel-based methods also require the inversion of a regularised gram matrix, which has a time complexity of $O(n^{3})$, and cannot be easily parallelised like standard matrix multiplications.
-As such, inference on datasets beyond tens of thousands of observations quickly becomes impractical to perform with kernel-based techniques.
-
-		In order to scale to big datasets, instead of placing a kernel over the input space directly and let it implicitly define the feature space, we explicitly define a finite dimensional feature space $\mathcal{Z} \subseteq \mathbb{R}^{p}$ of lower dimension $p$, where $p < n$, and place a linear kernel over it.
-That is, we specify a family of explicit features maps $\varphi_{\theta} : \mathcal{X} \to \mathcal{Z}$, and place a linear kernel on top of these explicit features,
-
-		\begin{equation}
-			k_{\theta}(x, x') = \varphi_{\theta}(x)^{T} \varphi_{\theta}(x').
-		\end{equation}
-
-		By explicitly defining a finite dimensional feature space, the matrix to be inverted during both learning and inference in the kernel embedding classifier can be reduced from size $n \times n$ to size $p \times p$ by using the Woodbury matrix inversion identity \citep{higham2002accuracy}.
-We use this identity to modify \cref{alg:kernel_embedding_classifier_training} to \cref{alg:explicit_kernel_embedding_classifier_training} to exploit this computational speed up.
-
-		However, with a fixed and finite amount of feature basis, the model becomes parametric and its flexibility is compromised.
-In other words, the model is narrow in the number of feature representations.
-We therefore turn to multi-layered feature compositions, where the flexibility of a model comes from the deep architecture instead of implicit high dimensional features.
-
-		\begin{algorithm}[tb]
-			\caption{Explicit KEC Hyperparameter Learning with Batch Stochastic Gradient Updates}
-			\label{alg:explicit_kernel_embedding_classifier_training}
-			\begin{algorithmic}[1]
-				\STATE {\bfseries Input:} feature family $\varphi_{\theta} : \mathcal{X} \to \mathcal{Z} \subseteq \mathbb{R}^{p}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial feature parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
-				\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
-				\REPEAT
-				\STATE Sample the next batch batch $\mathcal{I} \subseteq \mathbb{N}_{n}$, $| \mathcal{I} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I} = \mathbb{N}_{n}$)
-				\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
-				\STATE $Z_{\theta} \leftarrow \{\varphi_{\theta}(x_{i}) : i \in \mathcal{I}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times p}$
-				\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(Z_{\theta}^{T} Z_{\theta} + n_{b} \lambda I_{p}) \hspace{\fill} \in \mathbb{R}^{p \times p}$
-				\STATE $W_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Z_{\theta}^{T} Y) \hspace{\fill} \in \mathbb{R}^{p \times m}$
-				\STATE $P_{\theta, \lambda} \leftarrow Z_{\theta} W_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-				\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \alpha(\theta) \sqrt{\sum_{c = 1}^{m} \sum_{j = 1}^{p} (W_{\theta, \lambda})_{j, c}^{2}}$
-				\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
-				\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial q}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial q}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
-				\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
-			\end{algorithmic}
-		\end{algorithm}
-
-	\subsection{Kernel Embedding Network}
-	\label{app:kernel_embedding_network}
-
-		For many application domains, there are natural structures in the data.
-For example, in image recognition, pixel dimensions are spatially correlated: nearby pixels are more related, and ordering between the pixel dimensions matter.
-One would expect convolutional features \citep{lecun1998gradient} to be natural in this domain, and provide a performance boost to our classifier should it be included.
-In this way, we can often benefit by including domain specific structures and features into our model.
-
-		In this section, we focus on constructing kernels for which inputs $x, x' \in \mathcal{X}$ is to undergo various stages of feature transformations before such it is passed into a simpler kernel $\kappa$ that captures the similarity between the representations.
-Specifically, we pay particular attention to feature transformations in the form of a perceptron, so that the cumulative stages of feature transformation become the (feed-forward) multi-layer perceptron that is familiar within the neural network literature.
-
-		Formally, let $\mathcal{F}_{0} := \mathcal{X}$ be the original input space.
-The $j^{\mathrm{th}}$ layer of the network $\varphi^{(j)}_{\theta_{j}} : \mathcal{F}_{j - 1} \to \mathcal{F}_{j}, j = 1, 2, \dots, L$ is to transform features from the previous layer to features in the current layer, where $L$ is the total number of such feature transformation layers, and $\theta_{j} \in \Theta_{j}$ parametrises each of those transformations.
-
-		For example, in a typical multi-layer perceptron context, each layer can be written as $\varphi^{(j)}_{\theta_{j}}(x) = \sigma(W_{j} x + b_{j})$, where $W_{j}$ and $b_{j}$ are the weight and bias parameters of the layer, and $\sigma$ is an element-wise activation function, typically the rectified linear unit (ReLU) or the sigmoid.
-In this case, the layer is parametrised by $\theta_{j} = \{W_{j}, b_{j}\}$.
-
-		Let $\kappa_{\theta_{0}} : \mathcal{F}_{p} \times \mathcal{F}_{p} \to \mathbb{R}$ be parametrised by $\theta_{0} \in \Theta_{0}$. We will construct our kernel network $k$ by
-
-		\begin{equation}
-			k_{\theta}(x, x') := \kappa_{\theta_{0}}\Bigg( \varphi^{(L)}_{\theta_{L}}\bigg(\varphi^{(L - 1)}_{\theta_{L - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x)\big)\Big)\bigg), \varphi^{(L)}_{\theta_{L}}\bigg(\varphi^{(L - 1)}_{\theta_{L - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x')\big)\Big)\bigg) \Bigg)
-		\label{eq:deep_kernel_embedding_network}
-		\end{equation}
-
-		where $\theta = (\theta_{1}, \theta_{2}, \dots, \theta_{L -1}, \theta_{L}, \theta_{0}) \in \Theta = \Theta_{1} \otimes \Theta_{2} \otimes \dots \otimes \Theta_{L - 1} \otimes \Theta_{L} \otimes \Theta_{0}$ are the collection of all parameters of each layer and the kernel $\kappa$.
-
-		In order to train the multi-layered representations in an end-to-end fashion, we employ \cref{alg:kernel_embedding_classifier_training}.
-With a deep architecture, the feature representations the kernel embedding network can learn are very flexible, and can work very well for structured data by employing suitable network architectures.
-
-		If we choose to employ nonlinear kernels $\kappa$, the model architecture is also wide in that an even higher dimensional feature space is implicitly defined on top of the feature space of the last network layer.
-Despite its supreme flexibility, this again prevents the model from being scalable.
-We therefore turn to the specific case where we employ a linear kernel $\kappa$ on top of the multi-layered features.
-
-	\subsection{Explicit Kernel Embedding Network}
-	\label{app:explicit_kernel_embedding_network}
-
-		The explicit kernel embedding network is simply a special case at the intersection of the explicit kernel embedding classifier and the kernel embedding network.
-From the explicit KEC perspective, we simply choose $\varphi_{\theta}(x) = \varphi^{(L)}_{\theta_{L}}\big(\varphi^{(L - 1)}_{\theta_{L - 1}}(\dots\varphi^{(2)}_{\theta_{2}}(\varphi^{(1)}_{\theta_{1}}(x)))\big)$.
-From the KEN perspective, we simply choose $\kappa(z, z') = z^{T} z'$ to be a linear kernel.
-
-		This model architecture is a very practical and powerful form of the kernel embedding classifier.
-By having a deep architecture, the classifier is still capable of learning flexible representations on structured data, while being able to scale to larger datasets due to the linear kernel at the output layer, provided that the dimensionality of the last layer is relatively small compared to the size of the dataset.
-
-		As a subclass of explicit KEC, we can employ \cref{alg:explicit_kernel_embedding_classifier_training} to learn the multi-layered features effectively.
-In fact, by not mapping the multi-layered features into a nonlinear kernel, the gradients for each network weight and bias are usually more pronounced, and learning is usually faster in comparison.
-This approach was used to train the neural network features in our experiments.
-
-%\newpage
-%\bibliographystyle{apalike}
-%\bibliography{kernel_embedding}
-
 \end{document}

### 2017-05-19 cake_appendix.tex
Final Version

--- 2017-05-10 kernel_embedding_classifier.tex
@@
 % if you need to pass options to natbib, use, e.g.:
-\PassOptionsToPackage{square, authoryear, comma, sort&compress}{natbib}
-% before loading nips_2016
+% \PassOptionsToPackage{numbers, compress}{natbib}
+% before loading nips_2017
 %
 % to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{nips_2016}
-
-\usepackage[final]{nips_2016}
+% \usepackage[nonatbib]{nips_2017}
+
+\usepackage{nips_2017}
 
 % to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[final]{nips_2016}
-
-\usepackage[utf8x]{inputenc} % allow utf-8 input
+% \usepackage[final]{nips_2017}
+
+% My Packages
+\usepackage[nokeyprefix]{refstyle}
+\usepackage{varioref}
+\usepackage{xr-hyper}
+\externaldocument[cake]{cake}
+% End My Packages
+
+\usepackage[utf8]{inputenc} % allow utf-8 input
 \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
@@
 \newtheorem{claim}[theorem]{Claim}
-
 \usepackage{multirow}
-
 \usepackage{algorithm}
 \usepackage{algorithmic}
-
-\title{CAKE: Classification avec Kernel Embeddings \\ with Rademacher Complexity based Risk Bounds}
-
-% The \author macro works with any number of authors. There are two
-% commands used to separate the names and addresses of multiple
-% authors: \And and \AND.
-%
-% Using \And between authors leaves it to LaTeX to determine where to
-% break the lines. Using \AND forces a line break at that point. So,
-% if LaTeX puts 3 of 4 authors names on the first line, and the last
-% on the second line, try using \AND instead of \And before the third
-% author name.
-
-%\author{
-%  Kelvin Y.S. Hsu, Richard Nock, Fabio T. Ramos \\
-%  University of Sydney, Australia\\
-%  DATA61, CSIRO\\
-%  \texttt{\{Kelvin.Hsu, Richard.Nock, Fabio.Ramos\}@\{sydney.edu.au, data61.csiro.au\}} \\
-%  %% examples of more authors
-%  %% \And
-%  %% Coauthor \\
-%  %% Affiliation \\
-%  %% Address \\
-%  %% \texttt{email} \\
-%  %% \AND
-%  %% Coauthor \\
-%  %% Affiliation \\
-%  %% Address \\
-%  %% \texttt{email} \\
-%  %% \And
-%  %% Coauthor \\
-%  %% Affiliation \\
-%  %% Address \\
-%  %% \texttt{email} \\
-%  %% \And
-%  %% Coauthor \\
-%  %% Affiliation \\
-%  %% Address \\
-%  %% \texttt{email} \\
-%}
+\newcommand{\argmax}{\operatornamewithlimits{argmax}}
+\numberwithin{equation}{section}
+\numberwithin{table}{section}
+\numberwithin{algorithm}{section}
+
+% End My Packages
+
+\title{CAKE: Classification \textit{avec} Kernel Embeddings \\ using Rademacher Complexity Bounds: \\ Supplementary Material}
 
 \author{
-	Kelvin Y.S. Hsu \\
-	University of Sydney, Australia\\
-	DATA61, CSIRO\\
-	\texttt{Kelvin.Hsu@\{sydney.edu.au, data61.csiro.au\}} \\
-	%% examples of more authors
-	\And
-	Richard Nock \\
-	Australian National University, Australia\\
-	University of Sydney, Australia\\
-	DATA61, CSIRO\\
-	\texttt{Richard.Nock@data61.csiro.au} \\
-	\And
-	Fabio T. Ramos \\
-	University of Sydney, Australia\\
-	DATA61, CSIRO\\
-	\texttt{Fabio.Ramos@\{sydney.edu.au, data61.csiro.au\}} \\
-	%% \texttt{email} \\
-	%% \AND
-	%% Coauthor \\
-	%% Affiliation \\
-	%% Address \\
-	%% \texttt{email} \\
-	%% \And
-	%% Coauthor \\
-	%% Affiliation \\
-	%% Address \\
-	%% \texttt{email} \\
-	%% \And
-	%% Coauthor \\
-	%% Affiliation \\
-	%% Address \\
-	%% \texttt{email} \\
 }
@@
 
-\begin{abstract}
-	We propose learning-theoretic bounds for learning the hyperparameters of kernel embeddings in the probabilistic multiclass classification context.
-Kernel embeddings are nonparametric methods to represent probability distributions directly through observed data in a reproducing kernel Hilbert space (RKHS).
-However, the problem of hyperparameter learning for kernel embeddings remains challenging, often relying on heuristics and domain specific knowledge.
-We begin by developing the kernel embedding classifier (KEC), and prove the stochastic convergence of its probabilistic predictions.
-We then prove that expected classification error can be bounded with high probability using Rademacher complexity based risk bounds.
-We use this bound to propose a scalable kernel learning algorithm for probabilistic multiclass classification.
-Classification performance is benchmarked on standard UCI datasets.
-We further apply our proposed kernel learning algorithm to learn feature representations of a deep convolutional network, with improved accuracy as compared to the original network, demonstrating the generality of this approach.
-\end{abstract}
-
-- We address the need for a principled way of obtaining probabilistic outputs from a multiclass classifier.
-- It works in domains with not a lot of data, and we later provide a way for which it can scale
-- We address hyperparameter learning for a kernel embedding model
-- We do not rely on priors
-
-Data dependent risk bounds
-
-\section{Introduction}
-\label{sec:introduction}
-
-	Kernel embeddings are a principled way to represent probability distributions in a nonparametric setting.
-
-	learning theoretic (be specific and mention PAC)
-	(complexity penalty terms that are not data dependent cannot be universally effective) \citep{kearns1997experimental}
-
-\section{Hilbert Space Embeddings of Conditional Probability Distributions}
-\label{sec:background}
-
-	We begin by providing an overview of Hilbert space embeddings, where probability distributions are represented by mean embeddings in a reproducing kernel Hilbert space (RKHS) through positive definite kernels.
-Specifically, in the supervised learning context for which we are primarily interested in, we focus on conditional distributions and its representations in the RKHS.
-
-	To construct a conditional embedding map $\mathcal{U}_{Y | X}$ corresponding to the distribution $\mathbb{P}_{Y | X}$ where $X : \Omega \to \mathcal{X}$ and $Y: \Omega \to \mathcal{Y}$ are measurable random variables, we choose a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ for the input space $\mathcal{X}$ and another kernel $l : \mathcal{Y} \times \mathcal{Y} \to \mathbb{R}$ for the output space $\mathcal{Y}$.
-These kernels $k$ and $l$ each describe how similarity is measured within each of their respective domains $\mathcal{X}$ and $\mathcal{Y}$, and are symmetric and positive definite such that they uniquely define the RKHS $\mathcal{H}_{k}$ and $\mathcal{H}_{l}$.
-Such a conditional embedding map is then defined by
-	\begin{equation}
-		\mathcal{U}_{Y | X} := C_{YX} C_{XX}^{-1},
-	\label{eq:conditional_embedding}
-	\end{equation}
-	where $C_{YX} := \mathbb{E}[l(Y, \cdot) \otimes k(X, \cdot)]$ and $C_{XX} := \mathbb{E}[k(X, \cdot) \otimes k(X, \cdot)]$ \citep{song2009hilbert}.
-The conditional embedding map can be seen as an operator map from $\mathcal{H}_{k}$ to $\mathcal{H}_{l}$.
-In this sense, it sweeps out a family of conditional embeddings $\mu_{Y | X = x}$ in $\mathcal{H}_{l}$, each indexed by the input variable $x$, via the property $\mu_{Y | X = x} := \mathbb{E}[l(Y, \cdot) | X = x] = \mathcal{U}_{Y | X} k(x, \cdot)$.
-
-	Under the assumption that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$, \cite{song2009hilbert} proved that the conditional expectation of a function $g \in \mathcal{H}_{l}$ can be expressed as an inner product,  % Theorem 4
-	\begin{equation}
-		\mathbb{E}[g(Y) | X = x] = \langle \mu_{Y | X = x}, g \rangle.
-	\label{eq:conditional_expectation}
-	\end{equation}
-	While the assumptions that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$ and $k(x, \cdot) \in \mathrm{image}(C_{XX})$ holds for finite input domains $\mathcal{X}$ for characteristic kernels $k$, it is not necessarily true when $\mathcal{X}$ is a continuous domain \citep{fukumizu2004dimensionality}, which is the scenario for many classification problems.
-In this case, $C_{YX} C_{XX}^{-1}$ becomes only an approximation to $\mathcal{U}_{Y | X}$, and we instead regularise the inverse and use $C_{YX} (C_{XX} + \lambda I)^{-1}$, which also serves to avoid overfitting \citep[p.
-13]{song2013kernel}.
-
-	On top of this, in practice we do not have access to the distribution $\mathbb{P}_{X Y}$ to analytically derive the conditional embedding.
-Instead, we have a finite collection of data points $\{x_{i}, y_{i}\} \in \mathcal{X} \times \mathcal{Y}$, $i \in \mathbb{N}_{n} := \{1, \dots, n\}$, for which the conditional embedding map $\mathcal{U}_{Y | X}$ can be estimated by
-	\begin{equation}
-		\hat{\mathcal{U}}_{Y | X} = \Psi (K + n \lambda I)^{-1} \Phi^{T},
-	\label{eq:empirical_conditional_embedding}
-	\end{equation}
-	where $K := \{k(x_{i}, x_{j})\}_{i = 1, j = 1}^{n, n}$, $\Phi := \begin{bmatrix} \phi(x_{1}) & \dots & \phi(x_{n}) \end{bmatrix}$, $\Psi := \begin{bmatrix} \psi(y_{1}) & \dots & \psi(y_{n}) \end{bmatrix}$, $\phi(x) := k(x, \cdot)$, $\psi(y) := l(y, \cdot)$, and $\lambda$ is the regularisation parameter for the conditional operator \citep{song2013kernel}.
-We then define the empirical conditional embedding by $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$, which stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \cite[Theorem 6]{song2009hilbert}.
-This allows us to approximate the conditional expectation \eqref{eq:conditional_expectation} with $\langle \hat{\mu}_{Y | X = x}, g \rangle$ instead,
-	\begin{equation}
-		\mathbb{E}[g(Y) | X = x] \approx \langle \hat{\mu}_{Y | X = x}, g \rangle = \bvec{g}^{T} (K + n \lambda I)^{-1} \bvec{k}(x),
-	\label{eq:empirical_conditional_expectation}
-	\end{equation}
-	where $\bvec{g} := \{g(y_{i})\}_{i = 1}^{n}$ and $\bvec{k}(x) := \{k(x_{i}, x\}_{i = 1}^{n}$, knowing that it would converge to the true expectation as $n$ increases for sufficiently small $\lambda$.
-
-\section{Kernel Embedding Classifier}
-\label{sec:kernel_embedding_classifier}
-
-	In this section, we formulate a kernel embedding based probabilistic classifier by casting it into the conditional embedding framework.
-
-	In the multiclass classification context, the output label space is finite and discrete, taking values only in $\mathcal{Y} = \mathbb{N}_{m} := \{1, \dots, m\}$.
-Naturally, we first choose the Kronecker delta kernel $\delta : \mathbb{N}_{m} \times \mathbb{N}_{m} \to \{0, 1\}$ as the output kernel $l$, where labels that are the same has unit similarity and labels that are different have no similarity.
-That is, for all pairs of labels $y_{i}, y_{j} \in \mathcal{Y}$,
-	\begin{equation}
-		\delta(y_{i}, y_{j}) := \begin{cases}
-		1 & \mathrm{if } \quad y_{i} = y_{j}, \\
-		0 & \mathrm{otherwise}.
-		\end{cases}
-	\end{equation}
-	As $\delta$ is an integrally strictly positive definite kernel on $\mathbb{N}_{m}$, it is therefore characteristic \citep[Theorem 7]{sriperumbudur2010hilbert}.
-As such, by definition of characteristic kernels, $\delta$ uniquely defines a RKHS $\mathcal{H}_{\delta}$ \citep{fukumizu2004dimensionality}.
-Notice that this kernel has no parameters, so that the model hyperparameters only come from the kernel of the input space and the regularisation parameter $\lambda$.
-
-	Recall that the RKHS induced by a positive definite kernel is the closure of the span of its kernel induced features \citep{xu2009refinement}, so that $\mathcal{H}_{l} = \overline{\mathrm{span}\{l(y, \cdot) : y \in \mathcal{Y}\}}$.
-For $\mathcal{Y} = \mathbb{N}_{m}$ and $l = \delta$, this means that any real-valued function $g : \mathbb{N}_{m} \to \mathbb{R}$ that is bounded on its discrete domain $\mathbb{N}_{m}$ is in the RKHS of $\delta$, because we can always write $g = \sum_{y = 1}^{m} g(y) \delta(y, \cdot) \in \mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}$.
-
-	In particular, indicator functions on $\mathbb{N}_{m}$ are in the RKHS $\mathcal{H}_{\delta}$, since
-	\begin{equation}
-		\mathbb{1}_{c}(y) := \mathbb{1}_{\{c\}}(y) := \begin{cases}
-		1 & \mathrm{if } \quad y \in \{c\} \\
-		0 & \mathrm{otherwise}
-		\end{cases} = \delta(c, y).
-	\label{eq:indicator_function}
-	\end{equation}
-	That is, indicator functions $\mathbb{1}_{c} = \delta(c, \cdot)$, $c \in \mathbb{N}_{m}$ are simply the canonical kernel features of $\mathcal{H}_{\delta}$.
-
-	While such properties does not becessarily hold for continuous domains in general, this convenient property in the case of a discrete domain $\mathcal{Y}$ with a Kronecker delta kernel $\delta$ is what allows consistent estimations of decision probabilities used in multiclass classification, which we turn to next.
-
-	Let $p_{c}(x) := \mathbb{P}[Y = c | X = x]$ be the \textit{decision probability function} for class $c \in \mathbb{N}_{m}$, which is the probability of the class label $Y$ being $c$ when the example $X$ is $x$.
-We begin by writing this probability as an expectation of indicator functions,
-	\begin{equation}
-		p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mathbb{P}[Y \in \{c\} | X = x] = \mathbb{E}[\mathbb{1}_{c}(Y) | X = x].
-	\label{eq:decision_probability}
-	\end{equation}	
-	With $\mathbb{1}_{c} \in \mathcal{H}_{\delta}$, we let $g = \mathbb{1}_{c}$ in \eqref{eq:empirical_conditional_expectation} and $\bvec{1}_{c} := \{\mathbb{1}_{c}(y_{i})\}_{i = 1}^{n}$ to estimate the right hand side of \eqref{eq:decision_probability} by
-	\begin{equation}
-		\hat{p}_{c}(x) = f_{c}(x) := \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x).
-	\label{eq:empirical_decision_probability}
-	\end{equation}
-	Therefore, the vector of empirical decision probability functions over the classes $c \in \mathbb{N}_{m}$ is
-	\begin{equation}
-		\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \bvec{k}(x) \in \mathbb{R}^{m},
-	\label{eq:empirical_decision_probability_vector}
-	\end{equation}
-	where $\bvec{Y} := \begin{bmatrix} \bvec{1}_{1} & \bvec{1}_{2} & \cdots & \bvec{1}_{m} \end{bmatrix} \in \{0, 1\}^{n \times m}$ is simply the one hot encoded labels $\{y_{i}\}_{i = 1}^{n}$.
-
-	We proceed to prove that the empirical decision probabilities \eqref{eq:empirical_decision_probability} converges to the true decision probabilities with more data.
-We direct the reader to the supplementary material for proof.
-	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
-		\label{thm:probability_convergence_copy}
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-	\end{theorem}
-	Finally, to perform classification at a query point $x^{\star} \in \mathcal{X}$, we simply take the class with the highest empirical decision probability, $\hat{y}^{\star} = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x^{\star})$.
-
-	While the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ will converge to the true decision probability function  $p_{c} : \mathcal{X} \to [0, 1]$ in the limit, for finite $n$ and a fixed regulariser $\lambda > 0$, the stochasticity in the empirical estimates implies that these probabilities may not necessarily sum up to one, nor are they strictly restricted to the range $[0, 1]$.
-However, they will usually be very close to the true predicted probabilities.
-Moreover, such stochasticity also does not principally affect the classification prediction, since we simply take the argmax of the empirical decision probability vector \eqref{eq:empirical_decision_probability_vector}.
-
-	If strict, valid probabilities are required for interpretation, visualisation, or other purposes, the probabilities can be clipped at zero then normalised to one, a procedure we refer to as \textit{clip-normalisation},
-	\begin{equation}
-		\tilde{p}_{c}(x) := \frac{\max\{\hat{p}_{c}(x), 0\}}{\sum_{j = 1}^{m} \max\{\hat{p}_{j}(x), 0\}}.
-	\label{eq:probability_clip_normalise}
-	\end{equation}
-	Notice that for classification prediction, the argmax solution over the classes of the empirical decision probabilities \eqref{eq:empirical_decision_probability} and its clip-normalised version \eqref{eq:probability_clip_normalise} remain the same.
-Furthermore, since $\hat{p}_{c}(x)$ converges to true probabilities $p_{c}(x)$ according to \cref{thm:probability_convergence_copy}, the effect of clip-normalisation reduces as $n$ increases such that $\tilde{p}_{c}(x)$ becomes very close to $\hat{p}_{c}(x)$ and $p_{c}(x)$.
-
-\section{Learning with Rademacher Complexity based Risk Bounds}
-\label{sec:hyperparameter_learning}
-
-	The formulation of the kernel embedding classifier requires the specification of a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ over the input space $\mathcal{X}$, or rather, a class of kernels $\{k_{\theta}\}_{\theta \in \Theta}$ parametrised by the kernel parameters $\theta \in \Theta$.
-It also requires the specification of a regularisation parameter $\lambda$ for the conditional embedding as in \eqref{eq:empirical_conditional_embedding}.
-These are hyperparameters of the kernel embedding classifier which needs to be learned in order to produce a reasonable classifier model.
-While decision probability estimates \eqref{eq:empirical_decision_probability} converge to the true decision probabilities \eqref{eq:decision_probability} for any choice of positive definite kernels $k_{\theta}$ (\cref{thm:probability_convergence_copy}), for finite $n$ we would like to find the kernel from the kernel family which produces the most appropriately discriminative model to perform classification tasks.
-
-	In the kernel embedding literature, hyperparameters has been notoriously difficult to tune, and its learning is usually only restricted to heuristics or methods such as cross validation which requires pre-selecting the number of folds and the split of the folds.
-In this paper, we take a learning theoretic approach to learn the hyperparameters of the KEC, inspired by the original training procedure of support vector classifiers (SVC) as described by \cite[p.
-185]{m2001introduction}.
-Assuming a perfectly separable case, the training of a SVC begins by introducing a \textit{prediction constraint} on the training set, where the classifier is constrained to correctly classify all the available training examples.
-The strategy is to minimise the \textit{complexity} of the SVC model while ensuring perfect classification over training examples.
-The model complexity in the SVC context is measured by the VC dimension $h$ of the binary classifier, which has an upper bound $h \leq \lVert \bvec{w} \rVert^{2} R^{2} + 1$.
-Since it is difficult to compute the VC dimension explicitly, we instead minimise its upper bound, which is equivalent to and leads to the common interpretation of maximising the margin $\frac{2}{\lVert \bvec{w} \rVert}$.
-
-	Similarly, we propose to train our kernel embedding classifier with the same high level formulation: minimise the model complexity without compromising classification performance on the training data.
-Instead of employing the VC dimension as the complexity measure of our model, which is defined mainly for binary classifiers, we consider the \textit{Rademacher complexity} of the kernel embedding classifier.
-Given a function class $\mathcal{F}$ and a loss function $\mathcal{L}(y, \bvec{f}(x))$, the expected test loss $\mathbb{E}[\mathcal{L}(Y, \bvec{f}(X))]$ is bounded by the expected training loss $\frac{1}{n}\sum_{i = 1}^{n} \mathcal{L}(y_{i}, \bvec{f}(x_{i}))$ plus the Rademacher complexity and a constant with high probability, similar to the case with the VC dimension \citep{bartlett2002rademacher}.
-As such, if we can minimise the model complexity in the sense of the Rademacher complexity while maintaining a low training loss, we can optimise generalisation ability in the sense of low expected test loss.
-
-			Further more, since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:specific_expected_loss_bound_for_kec_applied} is true with probability $1 - \beta$ if we replace all the random variables $X_{i}, Y_{i}$ with the training observations $x_{i}, y_{i}$.
-
-			Therefore, in order to minimise the expected test loss, we propose the following training objective for the kernel embedding classifier,
-
-	For a predictor parametrised as $f(x; W) = W^{T} x$, \cite{yu2014large} showed that the global Rademacher complexity of such a predictor is upper-bounded in terms of its trace norm, $\sqrt{\mathrm{trace}(W^{T} W)}$.
-This was originally discussed in the context of multi-label classification, where $W \in \mathbb{R}^{d \times L}$ and $f$ produces a binary vector of length $L$ indicating the multiple labels that describes the input $x \in \mathbb{R}^{d}$.
-In the context of the kernel embedding classifier, the empirical decision probabilities \eqref{eq:empirical_decision_probability_vector} also has the same analytical form, where the input $x$ is replaced by some feature vector $\phi(x)$.
-By using the canonical feature map $\phi(x) = k(x, \cdot)$ and the reproducing property $\langle \phi(x), \phi(x') \rangle = k(x, x')$ in the RKHS, we can write \eqref{eq:empirical_decision_probability_vector} as $\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \Phi^{T} \phi(x) = W^{T} \phi(x)$, where instead of mapping input examples in $\mathbb{R}^{d}$ to output multi-label vector $\mathbb{R}^{L}$, $W^{T}$ maps features in the RKHS $\mathcal{H}_{k}$ to the a vector of multiclass probabilities in $\mathbb{R}^{m}$.
-Using the reproducing property $K = \Phi^{T} \Phi$ again, the squared trace norm for such a predictor is then $\mathrm{trace}(W^{T} W) = \mathrm{trace}(\bvec{Y}^{T} (K + n \lambda I)^{-1} K (K + n \lambda I)^{-1} \bvec{Y})$.
-We therefore propose to use this trace norm as an upper bound measure of the kernel embedding classifier model complexity,
-	\begin{equation}
-		r(\theta, \lambda) := \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} K_{\theta} (K_{\theta} + n \lambda I)^{-1} \bvec{Y}\bigg)},
-	\label{eq:trace_norm}
-	\end{equation}
-	where we use the subscript $\theta$ to make explicit the dependence on the kernel parameters. Therefore, with high probability and up to a constant term, an upper bound of the test loss is
-	\begin{equation}
-		q(\theta, \lambda) := \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}(y_{i}, \hat{\bvec{p}}_{\theta, \lambda}(x_{i})) + r(\theta, \lambda).
-	\label{eq:objective}
-	\end{equation}
-	We employ gradient based methods to train the kernel embedding classifier with this training loss and complexity bound objective.
-The gradients of the learning objective with respect to the hyperparameters is obtained using automatic differentiation.
-
-	\begin{algorithm}[tb]
-		\caption{KEC Hyperparameter Learning with Batch Stochastic Gradient Descent}
-		\label{alg:kernel_embedding_classifier_training}
-		\begin{algorithmic}[1]
-			\STATE {\bfseries Input:} kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial kernel parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
-			\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
-			\REPEAT
-			\STATE Sample the next batch $\mathcal{I} \subseteq \mathbb{N}_{n}$, $| \mathcal{I} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I} = \mathbb{N}_{n}$)
-			\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
-			\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathcal{I}, j \in \mathcal{I}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
-			\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n_{b} \lambda I_{n_{b}}) \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
-			\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Y) \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-			\STATE $P_{\theta, \lambda} \leftarrow K_{\theta} V_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-			\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
-			\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
-			\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial r}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial r}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
-			\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
-		\end{algorithmic}
-	\end{algorithm}
-
-	\subsection{Batch Stochastic Gradient Descent}
-	\label{sec:stochastic_gradient_descent}
-
-		With standard gradient descent, the time complexity of each training iteration is dominated by the Cholesky decomposition of the regularised gram matrix $K_{\theta} + n \lambda I$ of size $n \times n$, which has a time complexity of $O(n^{3})$.
-In order to scale the hyperparameter training of kernel embedding classifiers to large datasets, we propose to optimise the objective \eqref{eq:objective} with stochastic gradient descent.
-
-		We begin by selecting a mini-batch size $n_{b} << n$ that is much smaller than $n$.
-At each training iteration, we sample a mini-batch of size $n_{b}$ from the full dataset.
-The objective \eqref{eq:objective} and its gradients with respect to the hyperparameters are then computed only for the mini-batch.
-This stochastic gradient is then used to make hyperparameter updates in that training iteration.
-This continues until the magnitude of the stochastic gradients fall below a certain range.
-This training algorithm is presented in \cref{alg:kernel_embedding_classifier_training}.
-This implementation also generalises the gradient descent approach, where $n_{b} = n$ so that $\mathcal{I} = \mathbb{N}_{n}$ and the full dataset is used to compute the gradients.
-
-		\note{Justify with the bound after discussing with Richard}
-
-\section{Experiments}
-
-	We will also open-source the code on GitHub.
-All the core algorithms presented in this paper will be available and implemented in TensorFlow \citep{abadi2016tensorflow}, while having the same API as \texttt{scikit-learn} models so that it is straightforward to use.
-
-	\begin{table}[t]
-		\begin{center}
-			\begin{tabular}{ l l || c || c c || c }
-				\hline
-				\multicolumn{6}{ c }{Classification Accuracy on UCI Datasets} \\
-				\hline
-				\hline
-%				& & & \multicolumn{2}{ c }{Accuracy} & \\
-%				\hline				
-				Dataset & & Method & Train & Test & Test (Literature) \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 1372$ & CE + RC & 99.59 & 100 & Artificial Neural Network: 99.78 \\
-				\texttt{banknote} & $d = 4$ & CE & 99.59 & 100 & \citep{kaya2016banknote} \\
-				& $m = 2$ & RC & 99.59 & 100 &  \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 336$ & CE + RC & 92.05 & 91.18 & Probabilistic Binary Tree: 81.1 \\
-				\texttt{ecoli} & $d = 7$ & CE & 94.04 & 85.29 & \citep{horton1996probabilistic} \\
-				& $m = 8$ & RC & 91.05 & 88.24 &  \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 150$ & CE + RC & 97.78 & 100 & SVM: 94.67 \\
-				\texttt{iris} & $d = 4$ & CE & 97.04 & 100 & \citep{koggalage2004reducing}\\
-				& $m = 3$ & RC & 97.78 & 100 & ANN: 83.33 \citep{swain2012approach} \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 7797$ & CE + RC &   &   & \\
-				\texttt{isolet} & $d = 617$ & CE &   &   & \\
-				& $m = 26$ & RC &   &   &  \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 2310$ & CE + RC & 99.37 & 97.40 & Decision Trees \& Neural Nets: \\
-				\texttt{segment} & $d = 19$ & CE & 97.84 & 96.97 &  99.14 - 99.98 \\
-				& $m = 7$ & RC & 97.35 & 96.10 & \citep{lim2000comparison} \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 178$ & CE + RC & 100 & 100 & RDA: 100, QDA: 99.4, \\
-				\texttt{wine} & $d = 13$ & CE & 100 & 100 & LDA: 98.9, 1NN: 96.1 \\
-				& $m = 3$ & RC & 100 & 100 & \citep{aeberhard1992comparison} \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 6497$ & CE + RC & & & \\
-				\texttt{wine-quality} & $d = 12$ & CE & & & \\
-				& $m = 2$ & RC & & &  \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 1484$ & CE + RC & 67.04 & 57.72 & Probabilistic Binary Tree: 55.0 \\
-				\texttt{yeast} & $d = 8$ & CE & 68.24 & 56.38 & \citep{horton1996probabilistic} \\
-				& $m = 10$ & RC & 62.25 & 56.38 &  \\
-				\hline
-				\hline
-			\end{tabular}
-		\end{center}
-		\caption{Classification Accuracy of the Kernel Embedding Classifier on standard UCI Datasets.}
-		\label{tab:experiments}
-	\end{table}
-
-	\begin{figure}[t]
-		\centering
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_50.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_100.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_250.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_500.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_750.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_1000.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_1500.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_2000.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_5000.eps}
-		\includegraphics[width=\linewidth]{figures/test_performance.eps}
-		\caption{Training the kernel embedding classifier on the MNIST digits dataset with an anisotropic Gaussian kernel. Top: Learned length scales for each pixel; Bottom: Performance on the test set.}
-		\label{fig:pixel_relevance}
-	\end{figure}
-
-\section{Conclusion}
-
-	\note{Summarise main contribution.
-Specifically, the guaranteed convergence of the kernel embedding classifier in both decision probability and information entropy, the Rademacher complexity based hyperparameter training scheme, the stochastic gradient descent version thereof which allows scalable training, the application of such flexible training methods to train deep convolutional features, and the fully probabilistic inference on both inputs and outputs.
-Focus the point of the paper as that this is a new and elegant formulation of a fully probabilistic classifier (not just in the outputs, but even in the inputs) with complexity bound based training.
-Being formulated as type of kernel conditional embedding learning, all the nice properties from the Hilbert space embedding world can be imported into this framework.
-In practice, even though the mathematical theory of kernel embeddings can be tricky, the resulting algorithms are very elegant and simple, so that implementation is quick and easy.
-Being very general, there should be a lot of things we can do in the future to improve it or build upon it.}
-
-	\textbf{Future Work}: \note{(Not that polished)}
-
-	\begin{itemize}
-		\item \textbf{Hyperparameter Training through Local Rademacher Complexity.} In parallel with the work of \cite{xu2016local}, we can derive an upper bound for the \textit{local Rademacher complexity} of our kernel embedding classifier.
-In contrast to the global Rademacher complexity, the local Rademacher complexity of a model produces a sharper generalization error bound and a faster convergence rate.
-Specifically, for our classifier, it is upper bounded by the tail sum of the sorted eigenvalues of $B^{T} (K + n \lambda I)^{-1} K (K + n \lambda I)^{-1} B$.
-The complication is that there is an extra design choice to be made: from which eigenvalue should the tail sum start.
-Preliminary experiments that we have done so far shows that this choice affects the training a lot, and thus more work is needed to theorise how this choice should be done, and if it really improves classification performance consistently at the end of the day.
-
-		\item \textbf{Multiple Kernel Learning and Shallow-Deep Kernels.} With kernel methods, newer and more flexible kernel classes can always be formed by convex combinations of simpler positive definite kernels.
-We can explore kernel and hyperparameter learning for these architectures under the kernel embedding classification framework that we developed in this paper.
-
-		\textbf{Multiple Kernel Learning}.
-In summary, multiple kernel learning is traditionally interested in forming a new kernel $k(x, x') := \sum_{i = 1}^{p} \alpha_{i} k_{i}(x, x')$ from simpler kernels $k_{i}(x, x')$ by finding the optimal coefficient vector $\{\alpha_{i}\}_{i = 1}^{p}$ with respect to its learning task under convexity constraints.
-While this convex optimisation problem is quite tractable, each kernel component $k_{i}$ stays fixed, so that it is up to the practitioners to choose and tune each kernel component a-priori.
-With the kernel embedding classification framework, hyperparameter training is very general, and makes no restrictions on where the trainable parameters must appear (with the trade-off being that the optimisation may become non-convex).
-As such, we can construct newer kernels through $k(x, x'; \theta) := \sum_{i = 1}^{p} \alpha_{i} k_{i}(x, x'; \theta_{i})$ and generalise the multiple kernel learning problem to one that finds the optimal coefficient vector $\{\alpha_{i}\}_{i = 1}^{p}$ and kernel parameters $\{\theta_{i}\}_{i = 1}^{p}$.
-Of course, the regularisation parameter $\lambda$ is jointly learned at the same time.
-
-		\textbf{Shallow-Deep Kernels}.
-Similarly, another way of convexly combining kernels is through a simple tensor multiplication, $k([x, z]^{T}, [x', z']^{T}; \theta_{\mathcal{X}}, \theta_{\mathcal{Z}}) := k_{\mathcal{X}}(x, x'; \theta_{\mathcal{X}}) k_{\mathcal{Z}}(z, z'; \theta_{\mathcal{Z}})$.
-In this scenario, we can let $x \in \mathcal{X}$ to be the original unaltered example inputs, while $z = f(x; w) \in \mathcal{Z}$ be the output of the last hidden layer of a neural network, where we use $w$ to collectively denote all the weight and bias parameters of the neural network.
-In this way, $k_{\mathcal{X}}$ is a shallow kernel allowing a direct connection from input to output, while $k_{\mathcal{Z}}$ is a deep kernel performing multiple layers of feature extraction from the input before it is connected to the output.
-Again, because hyperparameter training is very general in the kernel embedding classification framework, it should be possible to jointly learn the kernel hyperparameters $\theta_{\mathcal{X}}, \theta_{\mathcal{Z}}$, the neural network weights and biases $w$, and the regularisation parameter $\lambda$.
-
-		\item \textbf{Connection to other kernel models.} It should not be too surprising if we can find many connections or even equivalences to other kernel techniques.
-For example, if we look at the form of our decision probability estimator, it is also the same as the mean prediction of a Gaussian process regression, except we replace the real-valued targets in the regression case with the one-hot encoded class targets for our classification task.
-Of course, the main difference thereafter is how we train the two models.
-We turned to complexity based training partly because, unlike a Gaussian process, it is very difficult to find the marginal likelihood for a kernel embedding, and this has worked out well.
-However, future work can look into the direction of actually finding a way to compute or approximate the marginal likelihood for the kernel embedding classifier, making the link between Gaussian processes and kernel embeddings even stronger.
-
-		Another simpler connection may be the k-nearest-neighbour classifier.
-For any stationary and radially symmetric kernel like the Gaussian and Matern kernels, shorter length scales usually produces a nearest-neighbour effect on the inference of kernel embedding classifiers.
-Of course, this is suboptimal, and the complexity based training developed in this paper would know better to not learn such a length scale.
-However, this link would illustrate the purpose and effectiveness of a complexity based training scheme for kernel methods.
-
-		\item \textbf{Sampling and Generative Models.} While the kernel embedding classifier is trained as a discriminative model, at its core it is simply just a condition embedding of $\mathbb{P}_{Y | X}$.
-As such, we can do full probabilistic inference entirely in reproducing kernel Hilbert spaces and obtain the Hilbert space embeddings of $\mathbb{P}_{X | Y}$, similar to what we have touched upon in \cref{sec:mode_reconstruction}, or even simply of the marginals $\mathbb{P}_{X}$ and $\mathbb{P}_{Y}$.
-If we can recover these distributions as densities ($\mathbb{P}_{Y}$ would correspond to a probability mass function over a finite and discrete space $\mathbb{N}_{m}$ which is identical to the mean embedding already, and so this step would be trivial for $\mathbb{P}_{Y}$), then we would be able to model our data in a fully generative manner.
-In fact, in \cref{sec:mode_reconstruction} we have have already done so indirectly through reversing the embedding.
-Of course, this would require us to solve the pre-image problem of kernel embeddings, for which no general methodology exists yet besides a few heuristics with various assumptions.
-Nevertheless, assuming we can recover the densities well enough, we can then generate samples from those distributions.
-Alternatively, if we can instead sample from those distributions \textit{without} finding the pre-image, but by directly using the mean embeddings instead, that would make the kernel embedding classifier very useful as a generative modelling tool.
-
-		\item \textbf{Target Label Kernel.} In this paper, we proposed to place a Kronecker delta kernel $l = \delta$ over the label space $\mathcal{Y} = \mathbb{N}_{m}$ as it is the simplest kernel over a discrete and finite domain.
-However, it is possible to place other kernels over the label space.
-A simple kernel is to have a `generalised Kronecker delta kernel' that has unit similarity when labels are the same, but a small, positive yet non-zero similarity when labels are different.
-If we set these cross similarity to be the same across all non-identical pairs of labels, then it is straight forward to show that the inference algorithm we developed in this paper stays the same.
-However, if we allow them to vary amongst each other as kernel parameters (between the range $(0, 1)$, in order to stay positive definite), then we suspect that these cross similarity coefficients would act as correlation factors between classes.
-The training algorithm we developed here does not prevent the target label kernel to have its own hyperparameters.
-As such, we should be able to learn the correlation effects between the classes effectively using the same training scheme.
-We suspect that this would make the empirical decision probabilities converge to a valid probability distribution faster.
-However, we also suspect that the training may become even more non-convex and optimisation to become more difficult.
-
-		These factors may even give rise to new interpretable insights in terms of how different classes may be more related to each other.
-For example, in an image recognition task of animals, it may learn that, the class `horse' and 'pony' are much more similar than `horse' and `elephant' from the input features, and start to use the output correlations to focus on inferring about them as a group instead.
-		\end{itemize}
-
-\small
-\bibliographystyle{apalike}
-\bibliography{kernel_embedding}
-
-\newpage
 	\appendix
 
-\section{Information Entropy}
-\label{app:information_entropy}
-
-	The kernel embedding classifier provides decision probabilities instead of just a single label prediction.
-Such a probabilistic classifier allows us to quantify the uncertainty of its predictions for any given example $x \in \mathcal{X}$ through the information entropy \citep{shannon1951prediction, jaynes1957information}.
-This is ideal for detecting the decision boundaries of the classifier and areas of low data density.
-
-	We present two main approaches for inferring the information entropy from the classifier.
-Specifically, we would like to infer estimates for $h(x) := \mathbb{H}[Y | X = x] = - \sum_{c = 1}^{m} p_{c}(x) \log{p_{c}(x)} $, the information entropy of the possible labels $Y$ for a given example $X = x$.
-
-	The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref{eq:probability_clip_normalise}, at the query point $x \in \mathcal{X}$,
-	\begin{equation}
-		\tilde{h}(x) := - \sum_{c = 1}^{m} \tilde{p}_{c}(x) \log{\tilde{p}_{c}(x)}.
-	\label{eq:entropy_clip_normalise}
-	\end{equation}
-	We call \eqref{eq:entropy_clip_normalise} the \textit{clip-normalised information entropy}.
-Since $\tilde{p}_{c}(x)$ converges pointwise to $p_{c}(x)$ with increasing data, $\tilde{h}(x)$ also converges pointwise to $h(x)$.
-
-	Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information \footnote{Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$.},
-	\begin{equation}
-	\begin{aligned}
-		\mathbb{H}[Y | X = x] &= - \sum_{c = 1}^{m} \mathbb{P}[Y = c| X = x] \log{\mathbb{P}[Y = c | X = x]} \\
-		&= \mathbb{E}[- \log{\mathbb{P}[Y | X = x]} | X = x] \\
-		&= \mathbb{E}[u_{x}(Y) | X = x],
-	\end{aligned}
-	\end{equation}
-	where $u_{x}(y) := - \log{\mathbb{P}[Y = y | X = x]}$ is the \textit{information} (in nats) we would gain when we discover that example $x$ actually has label $y$.
-If $u_{x} : \mathbb{N}_{m} \to \mathbb{R}$ is in the RKHS $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by $\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle$.
-This is the basis of our second approach.
-
-	Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$.
-We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the RKHS.
-Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref{eq:empirical_conditional_expectation} and estimate $h(x)$ by
-	\begin{equation}
-		\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle = \bvec{u}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x).
-	\end{equation}
-	Unfortunately, $u_{x}$ is not known exactly, since $\mathbb{P}[Y = y | X = x]$ is not known exactly.
-Instead, since $\hat{p}_{c}(x)$ is a consistent estimate for $\mathbb{P}[Y = c | X = x]$ by \cref{thm:probability_convergence}, we propose to replace $u_{x}(y)$ with the negative log of $\hat{p}_{y}(x)$.
-However, we cannot simply take the log of this estimator, as $\hat{p}_{y}(x)$ may produce non-positive estimates to the prediction probabilities.
-The straight forward way to mitigate this problem is to clip $\hat{p}_{y}(x)$ from the bottom by a very small number, before taking the log.
-However, experiments show that this produces non-smooth estimates over $\mathcal{X}$ and the degree of smoothness varies drastically between different choices of that small number (see \cref{app:design_choices}).
-Instead, in virtue of the fact that $\lim_{p \to 0} - p \log{p} = 0$ even though $\lim_{p \to 0} - \log{p} = \infty$, we simply define the information estimate $\hat{u}_{x}(y)$ as zero if the empirical decision probability is non-positive,
-	\begin{equation}
-		\hat{u}_{x}(y) := \begin{cases}
-		- \log{\hat{p}_{y}(x)} & \mathrm{if } \quad \hat{p}_{y}(x) > 0 \\
-		0 & \mathrm{otherwise}. \end{cases}
-	\label{eq:empirical_information}
-	\end{equation}
-	It remains to show that $\hat{u}_{x} \in \mathcal{H}_{\delta}$.
-Indeed, the identity $\hat{u}_{x} = \sum_{c = 1}^{m} \hat{u}_{x}(c) \delta(c, \cdot)$ holds and thus $\hat{u}_{x}$ is in the span of the kernel canonical features.
-We then arrive at the following estimate for $h(x)$,
-	\begin{equation}
-		\hat{h}(x) := \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle = \hat{\bvec{u}}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x),
-		\label{eq:empirical_information_entropy}
-	\end{equation}
-	where $\hat{\bvec{u}}_{x} := \{\hat{u}_{x}(y_{i})\}_{i = 1}^{n}$.
-Similar to the case with decision probabilities \eqref{eq:decision_probability}, the information entropy estimate \eqref{eq:empirical_information_entropy} is not guaranteed to be non-negative.
-However, in practice these negative values are close to zero.
-Furthermore, negative estimated information entropy implies that the model is very confident about its prediction, and it suffices to simply clip the entropy at zero if strict information entropy is required (see \cref{app:design_choices}).
-We give the proof of convergence of \eqref{eq:empirical_information_entropy} in \cref{app:convergence_theorems}.
-	\begin{theorem}[Uniform Convergence of Empirical Information Entropy Function]
-		\label{thm:entropy_convergence_copy}
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical information entropy function $\hat{h} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_information_entropy} converges uniformly to the true information entropy function $h : \mathcal{X} \to [0, \infty)$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-	\end{theorem}
-
-\section{Convergence Theorems}
+	\section{Convergence Theorems for Kernel Embedding Classifiers}
 	\label{app:convergence_theorems}
 
-	In this section we provide a few theorems, lemmas, and derivations which proves the convergence properties of estimators derived from our kernel embedding classifier.
+	In this section we provide theorems and derivations that establish convergence properties of kernel embedding classifiers.
 
@@
 
-			Suppose that there exists $0 \leq \gamma(x) < \infty$ such that \eqref{eq:estimator_error_bound} is satisfied.
-Note that this statement holds for all possible datasets represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$.
-Thus, for any constant $C$, the implication statement $\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C \implies | \hat{f}(x) - f(x) | \leq C \gamma(x)$ holds for all possible data observation events $\omega \in \Omega$.
+			Suppose that there exists $0 \leq \gamma(x) < \infty$ such that \eqref[name = ]{eq:estimator_error_bound} is satisfied.
+That is, the inequality \eqref[name = ]{eq:estimator_error_bound} holds for all possible data observations $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$.
+For any constant $C$, the implication statement $\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C \implies | \hat{f}(x) - f(x) | \leq C \gamma(x)$ holds for all possible observation events $\omega \in \Omega$.
 Writing this explicitly in event space translates this to a probability statement,
-
 			\begin{equation}
@@
 			\end{equation}
-
-			Since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is valid.
-By letting $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ in \eqref{eq:probability_statement}, we immediately have that the probability inequality in statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is also true if we replace $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|$ with $| \hat{f}(x) - f(x) |$ and $M_{\epsilon}$ with $\gamma(x) M_{\epsilon}$,
-
+			Since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, statement \eqref[name = ]{eq:empirical_conditional_embedding_stochastic_convergence} is valid.
+By letting $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ in \eqref[name = ]{eq:probability_statement}, we immediately have that the probability inequality in statement \eqref[name = ]{eq:empirical_conditional_embedding_stochastic_convergence} is also true if we replace $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|$ with $| \hat{f}(x) - f(x) |$ and $M_{\epsilon}$ with $\gamma(x) M_{\epsilon}$,
 			\begin{equation}
@@
 			\end{equation}
-
-			where we employed statement \eqref{eq:probability_statement} between the third and fourth line for $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-Therefore, since $M_{\epsilon}$ is arbitrary, define $\tilde{M}_{\epsilon}(x) := \gamma(x) M_{\epsilon}$ so that, with the above result, the statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} implies the following,
-
+			where we employed statement \eqref[name = ]{eq:probability_statement} between the third and fourth line for $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+Therefore, since $M_{\epsilon}$ is arbitrary, define $\tilde{M}_{\epsilon}(x) := \gamma(x) M_{\epsilon}$ so that, with the above result, the statement \eqref[name = ]{eq:empirical_conditional_embedding_stochastic_convergence} implies the following,
 			\begin{equation}
@@
 	With \cref{thm:pointwise_uniform_convergence}, we can now show the convergence of various estimators based on the conditional embedding, as long as we can show that their estimator error is upper bounded by a multiple of the conditional embedding error in the RKHS norm.
-As such, we turn to the convergence of the empirical decision probability function \eqref{eq:empirical_decision_probability} below.
+As such, we turn to the convergence of the empirical decision probability function \eqref[name= , xr=cake]{eq:empirical_decision_probability} below.
 
@@
 		\label{thm:probability_convergence}
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-
-		\begin{proof}
+		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref[name= , xr=cake]{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref[name= , xr=cake]{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+
+		\begin{proof}
+
 			Consider the pointwise absolute difference between the decision probability and its empirical estimate,			
-
 			\begin{equation}
@@
 
-			where the last inequality follows from the Cauchy–Schwarz inequality in a Hilbert space.
-
-			From \eqref{eq:indicator_function}, since $\mathbb{1}_{c} = \delta(c, \cdot)$ and using the fact that $\delta$ is a reproducing kernel, we have that for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-
+			where the last inequality follows from the Cauchy Schwarz inequality in a Hilbert space.
+
+			From \eqref[name = , xr=cake]{eq:indicator_function}, since $\mathbb{1}_{c} = \delta(c, \cdot)$ and using the fact that $\delta$ is a reproducing kernel, we have that for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
 			\begin{equation}
@@
 			Therefore, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, $\hat{p}_{c}$ converges uniformly to $p_{c}$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-
-			%		Consequently, $| \hat{p}_{c}(x) - p_{c}(x) | \leq \big\| \hat{\mu}_{Y | X = x}^{(n)} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}}$ for all $x \in \mathcal{X}$, where the right hand side of which approaches zero stochastically at rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, so that $\hat{p}_{c}$ converges pointwise to $p_{c}$ at least at this rate.
-The convergence rate does not depend on $x \in \mathcal{X}$, so this (stochastic) convergence is pointwise uniform.
-
-%			Consequently, for all $x \in \mathcal{X}$ and $c \in \mathcal{Y}$, we have 
-%			
-%			\begin{equation}
-%				| \hat{p}_{c}(x) - p_{c}(x) | \leq \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}}.
-%			\label{eq:uniform_convergence}
-%			\end{equation}
-%			
-%			This is true for all possible datasets represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$.
-Thus, for any constant $C$, the implication statement $\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C \implies | \hat{p}_{c}(x) - p_{c}(x) | \leq C$ holds for all possible data observation events $\omega \in \Omega$.
-Writing this explicitly in event space translates this to a probability statement,
-%			
-%			\begin{equation}
-%			\begin{aligned}
-%			\{\omega \in \Omega : \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C\} &\subseteq \{\omega \in \Omega : | \hat{p}_{c}(x) - p_{c}(x) | \leq C\} \\
-%			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C\Big] &\leq \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | \leq C \Big].
-%			\label{eq:probability_statement}
-%			\end{aligned}
-%			\end{equation}
-%			
-%			Since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is valid.
-By letting $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ in \eqref{eq:probability_statement}, we immediately have that the probability inequality in statement \eqref{eq:probability_statement} is also true if we replace $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|$ with $| \hat{p}_{c}(x) - p_{c}(x) |$, % the RKHS norm between the empirical and true embeddings to the absolute difference between the empirical decision probability and the true decision probability,
-%			
-%			\begin{equation}
-%			\begin{aligned}
-%			\mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
-%			\implies 1 - \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
-%			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
-%			\implies \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
-%			\implies 1 - \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
-%			\implies \mathbb{P}\Big[| \hat{p}_{c}(x) - p_{c}(x) | > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon.
-%			\end{aligned}	
-%			\end{equation}
-%			
-%			In other words, the function $\hat{p}_{c}$ stochastically converges pointwise to $p_{c} := \mathbb{P}[Y = c | X = \cdot]$ with a rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-The convergence rate does not depend on $x \in \mathcal{X}$ nor $c \in \mathbb{N}_{m}$, so this stochastic convergence is pointwise uniform in its domain $\mathcal{X}$ across all label classes.
 
@@
 
-	\begin{claim}[Decision Probabilities are Conditional Embeddings]
+	\begin{lemma}[Decision Probabilities are Conditional Embeddings]
 	\label{thm:probability_is_embedding}
@@
 
-		\begin{proof} Since indicator functions are the canonical features of the label RKHS $\mathcal{H}_{\delta}$, we employ the fact that expectations of indicator functions are probabilities to prove this claim,
+		Therefore, $\bvec{p}(x) \equiv \mu_{Y | X = x}$.
+
+		\begin{proof}
+
+			Since indicator functions are the canonical features of the label RKHS $\mathcal{H}_{\delta}$, we employ the fact that expectations of indicator functions are probabilities to prove this claim,
 
@@
 					=& \mathbb{E}[\mathbb{1}_{c}(Y) | X = x] = \mathbb{P}[Y \in \{c\} | X = x] \\
-				=& \mathbb{P}[Y = c | X = x] := p_{c}(x).
-			\end{aligned}
-			\end{equation}
-		\end{proof}
-
-	\end{claim}
-
-	\begin{claim}[Empirical Decision Probabilities are Empirical Conditional Embeddings]
+					=& \mathbb{P}[Y = c | X = x] =: p_{c}(x).
+				\end{aligned}
+			\end{equation}
+
+		\end{proof}
+
+	\end{lemma}
+
+	\begin{lemma}[Empirical Decision Probabilities are Empirical Conditional Embeddings]
 	\label{thm:empirical_probability_is_embedding}
 
-		The empirical decision probability \eqref{eq:empirical_decision_probability} for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the empirical conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,
+		The empirical decision probability \eqref[name = , xr=cake]{eq:empirical_decision_probability} for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the empirical conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,
 
@@
 			\begin{equation}
-				\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} \phi(x)
+				\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} \phi(x).
 			\end{equation}
@@
 			\end{equation}
-		\end{proof}
-
-	\end{claim}
+
+		\end{proof}
+
+	\end{lemma}
+
+	\Cref{thm:empirical_probability_is_embedding} shows that the decision function $\bvec{f}(x)$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} of a kernel embedding classifier is no more than the empirical conditional embedding estimated from the data.
 
@@
 
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability vector function $\hat{\bvec{p}} : \mathcal{X} \to \mathbb{R}^{m}$ \eqref{eq:empirical_decision_probability_vector} converges uniformly to the true decision probability vector function $\bvec{p} : \mathcal{X} \to [0, 1]^{m}$ in the $\ell_{2}$-norm, where $\bvec{p}(x) := \{p_{c}(x)\}_{c = 1}^{m}$, at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability vector function $\hat{\bvec{p}} : \mathcal{X} \to \mathbb{R}^{m}$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} converges uniformly to the true decision probability vector function $\bvec{p} : \mathcal{X} \to [0, 1]^{m}$ in the $\ell_{1}$-norm and $\ell_{2}$-norm, where $\bvec{p}(x) := \{p_{c}(x)\}_{c = 1}^{m}$, at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
 
@@
 Since each entry converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the entire vector.
-More formally, from \eqref{eq:decision_probability_error_upper_bound} and \eqref{eq:indicator_rkhs_norm}, the $\ell_{1}$-norm of the difference can be bounded,
+More formally, from \eqref[name = ]{eq:decision_probability_error_upper_bound} and \eqref[name = ]{eq:indicator_rkhs_norm}, the $\ell_{1}$-norm of the difference can be bounded,
 
@@
 
-			For convergence in $\ell_{2}$, we show that the $\ell_{2}$-norm of the difference between the true and empirical decision probability vector functions is the same as the RKHS norm of the difference between the true and empirical conditional embedding, which converges to zero at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $x \in \mathcal{X}$ and $c \in \mathcal{Y} = \mathbb{N}_{m}$ \citep{song2009hilbert}.
+			For convergence in $\ell_{2}$, we show that the $\ell_{2}$-norm of the difference between the true and empirical decision probability vector functions is the same as the RKHS norm of the difference between the true and empirical conditional embedding, which converges to zero at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $x \in \mathcal{X}$ and $c \in \mathcal{Y} = \mathbb{N}_{m}$ by \eqref[name = ]{eq:empirical_conditional_embedding_stochastic_convergence}.
 To this end, we use \cref{thm:probability_is_embedding} and \cref{thm:empirical_probability_is_embedding} and write
@@
 
-			where the last equality comes from \eqref{eq:rkhs_norm_is_l2_norm} and the fact that the empirical and true conditional embeddings are bounded functions in the RKHS.
+			where the last equality comes from \eqref[name = ]{eq:rkhs_norm_is_l2_norm} and the fact that the empirical and true conditional embeddings are bounded functions in the RKHS.
 Again, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, we have uniform convergence in $\ell_{2}$.
@@
 
-	In \cref{app:information_entropy}, we proposed an estimator for the information entropy $h(x)$ for a prediction at $x \in \mathcal{X}$.
-Since this estimator is now based on the inner product between the empirical conditional embedding and another empirically estimate function, instead of between the empirical conditional embedding and a known function, it is not immediately clear that such an estimator converges.
+	\subsection{Information Entropy of Kernel Embedding Classifiers}
+	\label{app:information_entropy}
+
+		The kernel embedding classifier provides decision probabilities instead of just a single label prediction.
+Such a probabilistic classifier allows us to quantify the uncertainty of its predictions for any given example $x \in \mathcal{X}$ through the information entropy \citep{shannon1951prediction, jaynes1957information}.
+This is ideal for detecting the decision boundaries of the classifier and areas of low data density.
+
+		We present two main approaches for inferring the information entropy from the classifier.
+Specifically, we would like to infer estimates for $h(x) := \mathbb{H}[Y | X = x] = - \sum_{c = 1}^{m} p_{c}(x) \log{p_{c}(x)} $, the information entropy of the possible labels $Y$ for a given example $X = x$.
+
+		The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref[name = , xr=cake]{eq:empirical_decision_probability_clip_normalised}, at the query point $x \in \mathcal{X}$,
+
+		\begin{equation}
+			\tilde{h}(x) := - \sum_{c = 1}^{m} \tilde{p}_{c}(x) \log{\tilde{p}_{c}(x)}.
+		\label{eq:entropy_clip_normalise}
+		\end{equation}
+
+		We call \eqref[name = ]{eq:entropy_clip_normalise} the \textit{clip-normalised information entropy}.
+Since $\tilde{p}_{c}(x)$ converges pointwise to $p_{c}(x)$ with increasing data, $\tilde{h}(x)$ also converges pointwise to $h(x)$.
+
+		Just as decision probabilities can be expressed as an expectation of indicator functions, information entropy can be expressed as expected information,
+		\begin{equation}
+			\begin{aligned}
+				\mathbb{H}[Y | X = x] &= - \sum_{c = 1}^{m} \mathbb{P}[Y = c| X = x] \log{\mathbb{P}[Y = c | X = x]} \\
+				&= \mathbb{E}[- \log{\mathbb{P}[Y | X = x]} | X = x] \\
+				&= \mathbb{E}[u_{x}(Y) | X = x],
+			\end{aligned}
+		\end{equation}
+		where $u_{x}(y) := - \log{\mathbb{P}[Y = y | X = x]}$ is the \textit{information} (in nats) we would gain when we discover that example $x$ actually has label $y$.
+Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$.
+If $u_{x} : \mathbb{N}_{m} \to \mathbb{R}$ is in the RKHS $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by $\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle$.
+This is the basis of our second approach.
+
+		Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$.
+We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the RKHS.
+Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref[name = , xr=cake]{eq:empirical_conditional_expectation} and estimate $h(x)$ by
+
+		\begin{equation}
+			\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle = \bvec{u}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x).
+		\end{equation}
+
+		Unfortunately, $u_{x}$ is not known exactly, since $\mathbb{P}[Y = y | X = x]$ is not known exactly.
+Instead, since $\hat{p}_{c}(x)$ is a consistent estimate for $\mathbb{P}[Y = c | X = x]$ by \cref{thm:probability_convergence}, we propose to replace $u_{x}(y)$ with the information of $\hat{p}_{y}(x)$.
+However, we cannot simply take the log of this estimator, as $\hat{p}_{y}(x)$ may produce non-positive estimates to the prediction probabilities.
+The straight forward way to mitigate this problem is to clip $\hat{p}_{y}(x)$ from the bottom by a very small number, before taking the log.
+However, experiments show that this produces non-smooth estimates over $\mathcal{X}$ and the degree of smoothness varies drastically between different choices of that small number.
+Instead, in virtue of the fact that $\lim_{p \to 0} - p \log{p} = 0$ even though $\lim_{p \to 0} - \log{p} = \infty$, we simply define the information estimate $\hat{u}_{x}(y)$ as zero if the empirical decision probability is non-positive,
+
+		\begin{equation}
+			\hat{u}_{x}(y) := \begin{cases}
+				- \log{\hat{p}_{y}(x)} & \mathrm{if } \quad \hat{p}_{y}(x) > 0 \\
+				0 & \mathrm{otherwise}. \end{cases}
+			\label{eq:empirical_information}
+		\end{equation}
+
+		It remains to show that $\hat{u}_{x} \in \mathcal{H}_{\delta}$.
+Indeed, the identity $\hat{u}_{x} = \sum_{c = 1}^{m} \hat{u}_{x}(c) \delta(c, \cdot)$ holds and thus $\hat{u}_{x}$ is in the span of the kernel canonical features.
+We then arrive at the following estimate for $h(x)$,
+
+		\begin{equation}
+			\hat{h}(x) := \langle \hat{\mu}_{Y | X = x}, \hat{u}_{x} \rangle = \hat{\bvec{u}}_{x}^{T} (K + n \lambda I)^{-1} \bvec{k}(x),
+		\label{eq:empirical_information_entropy}
+		\end{equation}
+
+		where $\hat{\bvec{u}}_{x} := \{\hat{u}_{x}(y_{i})\}_{i = 1}^{n}$.
+Similar to the case with decision probabilities \eqref[name = , xr=cake]{eq:decision_probability}, the information entropy estimate \eqref[name = ]{eq:empirical_information_entropy} is not guaranteed to be non-negative.
+However, in practice these negative values are close to zero.
+Furthermore, negative estimated information entropy implies that the model is very confident about its prediction, and it suffices to simply clip the entropy at zero if strict information entropy is required.
+
+		Since this estimator is now based on the inner product between the empirical conditional embedding and another empirically estimate function, instead of between the empirical conditional embedding and a known function like the decision probability estimate, it is not immediately clear that such an estimator converges.
 Nevertheless, intuition tells us that the inner product between two converging quantities should converge.
@@
 			\label{thm:entropy_convergence}
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical information entropy function $\hat{h} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_information_entropy} converges pointwise to the true information entropy function $h : \mathcal{X} \to [0, \infty)$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
+			Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical information entropy function $\hat{h} : \mathcal{X} \to \mathbb{R}$ \eqref[name = ]{eq:empirical_information_entropy} converges pointwise to the true information entropy function $h : \mathcal{X} \to [0, \infty)$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
 
@@
 				Since we are interested in the asymptotic properties of our estimators when $n \to \infty$, and we have proved that the empirical decision probabilities converges to the true probabilities (\cref{thm:probability_convergence}), the condition $\hat{p}_{c}(x) > 0$ holds for large $n$ such that we simply have $\hat{u}_{x}(c) = - \log{\hat{p}_{c}(x)}$.
-That is, the effects of clipping for the information estimate \eqref{eq:empirical_information} vanishes.
+That is, the effects of clipping for the information estimate \eqref[name = ]{eq:empirical_information} vanishes.
 
@@
 
-			where the we used the triangle inequality and Cauchy–Schwarz inequality in a Hilbert space respectively.
-
-			Now, since $l = \delta$ is bounded, so is $\hat{\mu}_{Y | X = x}(c) = \sum_{i = 1}^{n} w_{i} \delta(y_{i}, c)$ for some embedding weights $w_{i}$ and all $c \in \mathbb{N}_{m}$, and thus its RKHS norm is finite for all $n \in \mathbb{N}_{n}$.
+				where the we used the triangle inequality and Cauchy Schwarz inequality in a Hilbert space respectively.
+Since $l = \delta$ is bounded, so is $\hat{\mu}_{Y | X = x}(c) = \sum_{i = 1}^{n} w_{i} \delta(y_{i}, c)$ for some embedding weights $w_{i}$ and all $c \in \mathbb{N}_{m}$, and thus its RKHS norm is finite for all $n \in \mathbb{N}_{n}$.
 Similarly, assuming that $p_{c}(x)$ is never exactly zero, $u_{x}(c)$ is also finite for all $c \in \mathbb{N}_{m}$ and thus so is its RKHS norm.
-We already know that $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$ stochastically converges to zero at the rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ \citep[Theorem 6]{song2009hilbert}.
+We already know that $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$ stochastically converges to zero at the rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ \eqref[name = ]{eq:empirical_conditional_embedding_stochastic_convergence}.
 Thus, it remains to bound $\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}}$ by a multiple of $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$.
@@
 						&\leq \frac{1}{| \mu_{Y | X = x}(c) |} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) | \\
-				&= \alpha_{x} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |,
-			\end{aligned}
-			\end{equation}
-
-			where we define $\alpha_{x} := \max_{c \in \mathbb{N}_{m}} \frac{1}{| \mu_{Y | X = x}(c) |}$.
-Since the RKHS norm of bounded functions in $\mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of their vector representations \eqref{eq:rkhs_norm_is_l2_norm}, we have
+						&\leq \alpha_{x} | \hat{\mu}_{Y | X = x}(c) - \mu_{Y | X = x}(c) |,
+					\end{aligned}
+				\end{equation}
+
+				where we define $\alpha_{x} := \max_{c \in \mathbb{N}_{m}} \frac{1}{| \mu_{Y | X = x}(c) |}$, which is well defined as the conditional embedding is bounded.
+Since the RKHS norm of bounded functions in $\mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of their vector representations \eqref[name = ]{eq:rkhs_norm_is_l2_norm}, we have
 
@@
 
-			Therefore, $\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}} \leq \alpha_{x} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$, and \eqref{eq:information_entropy_bound} becomes
+				Therefore, $\| \hat{u}_{x} - u_{x} \|_{\mathcal{H}_{\delta}} \leq \alpha_{x} \| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$, and \eqref[name = ]{eq:information_entropy_bound} becomes
 
@@
 \newpage
-\section{Learning Theoretic Bounds for the Kernel Embedding Classifiers}
+\section{Learning Theoretic Bounds for Kernel Embedding Classifiers}
 \label{app:learning_theoretic_bounds}
 
-	In this section we derive the Rademacher complexity bound of the kernel embedding classifier, and show that it can be used in conjunction with the training loss to bound the expected risk with high probability.
+	In this section we derive Rademacher complexity bounds for kernel embedding classifiers, and show that it can be used in conjunction with cross entropy loss to bound the expected risk with high probability.
 
@@
 Let $k_{\theta} : \mathcal{X} \times \mathcal{X} \to [0, \infty)$ be a family of positive definite kernels indexed by $\theta \in \Theta$.
-As before, we define the shorthand notation for the gram matrices $K_{\theta} := \{k_{\theta}(x_{i}, x_{j}) : i \in \mathbb{N}_{n}, j \in \mathbb{N}_{n}\}$ and $\bvec{k}_{\theta}(x) := \{k_{\theta}(x_{i}, x) : i \in \mathbb{N}_{n}\}$, and $\lambda$ denotes the regularisation parameter of the conditional embedding \eqref{eq:empirical_conditional_embedding}.
-The kernel embedding classifier has a predictor form $\hat{\bvec{p}}(x) = \bvec{f}_{\theta, \lambda}(x)$ \eqref{eq:empirical_decision_probability_vector} defined by
+As before, we define the shorthand notation for the gram matrices $K_{\theta} := \{k_{\theta}(x_{i}, x_{j}) : i \in \mathbb{N}_{n}, j \in \mathbb{N}_{n}\}$ and $\bvec{k}_{\theta}(x) := \{k_{\theta}(x_{i}, x) : i \in \mathbb{N}_{n}\}$, and $\lambda$ denotes the regularisation parameter of the conditional embedding \eqref[name = , xr=cake]{eq:empirical_conditional_embedding}.
+The kernel embedding classifier has a predictor form $\hat{\bvec{p}}(x) = \bvec{f}_{\theta, \lambda}(x)$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} defined by
 
@@
 
-		The predictor form \eqref{eq:predictor} is linear in the reproducing kernel Hilbert space $\mathcal{H}_{k_{\theta}}$ induced by $k_{\theta}$ in the sense that
+		The predictor form \eqref[name = ]{eq:predictor} is linear in the reproducing kernel Hilbert space $\mathcal{H}_{k_{\theta}}$ induced by $k_{\theta}$ in the sense that
 
@@
 		where we decompose $\bvec{k}_{\theta}(x) = \Phi_{\theta}^{T} \phi_{\theta}(x)$ by the reproducing property.
-
-		\begin{theorem}[Rademacher Complexity Bound for the Kernel Embedding Classifier]
+By \cref{thm:empirical_probability_is_embedding}, $\bvec{f}_{\theta, \lambda}(x) = \hat{\bvec{p}}_{\theta, \lambda}(x) = \hat{\mu}^{(\theta, \lambda)}_{Y | X = x} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$.
+Therefore, we have that $\hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \equiv W_{\theta, \lambda}^{T}$.
+Throughout this paper, inner products are defined in the Hilbert-Schmidt sense, which induces the Hilbert-Schmidt norm $\| \cdot \|_{HS}$ and generalises the Frobenius inner product with induced norm $\| \cdot \|_{\mathrm{tr}}$ for finite dimensional operators.
+Nevertheless, while they refer to the same quantity, we will use the standard notations $ \| \hat{\mathcal{U}}^{\theta, \lambda}_{Y | X} \|_{HS}$ as per the literature in Hilbert space embeddings and $\| W_{\theta, \lambda} \|_{\mathrm{tr}}$ as per the literature for linear classifiers.
+
+		\begin{theorem}[Rademacher Complexity Bound for Kernel Embedding Classifiers]
 		\label{thm:rademacher_complexity_bound}
@@
 			Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
-Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}} = k_{\theta}(x, x) \leq \alpha^{2}$ is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
-For any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of kernel embedding classifiers $F_{n}(\Theta, \Lambda)$ \eqref{eq:predictor_class} defined over $\theta \in \Theta, \lambda \in \Lambda$ is bounded by
+Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$, $\alpha > 0$, is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
+For any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of kernel embedding classifiers $F_{n}(\Theta, \Lambda)$ \eqref[name = ]{eq:predictor_class} defined over $\theta \in \Theta, \lambda \in \Lambda$ is bounded by
 
@@
 		\end{corollary}
+
+		\Cref{thm:rademacher_complexity_stationary_kernels_bound} motivates the choice $\alpha^{2}(\theta) = k_{\theta}(0, 0) = \sigma_{f}^{2}$ for stationary radial basis type kernels such as the Gaussian or Mat\'{e}rn kernels, where $\sigma_{f}$ is the sensitivity \citep{rasmussen2006gaussian} of the stationary kernel, which we employ in our learning algorithm when the kernel is stationary.
 
@@
 
-		In this way, our cross entropy loss \eqref{eq:cross_entropy_loss} is both bounded and positive.
+		In this way, our cross entropy loss \eqref[name = ]{eq:cross_entropy_loss} is both bounded and positive.
 In our subsequent analysis, we require that our loss function has an image in $[0, 1]$.
@@
 
-		We will refer to \eqref{eq:normalised_cross_entropy_loss} as the normalised cross entropy loss \footnote{Of course, the above normalisation only ensures that the loss function attains a maximum of one, but can still be negative if $\hat{p}_{y}(x)$ higher than $1$.
-We can enforce this requirement by clipping the loss function at zero through $\max\{\cdot, 0\}$.
-However, for brevity, we will avoid explicitly writing this clipping operation, as it does not principally affect our subsequent analysis.
-It should nevertheless be understood that all losses discussed in this section are clipped from below at zero or, equivalently, the probability estimates $\hat{p}_{y}(x)$ are clipped from above at one.}.
-We then further define the centred normalised cross entropy loss,
+		We will refer to \eqref[name = ]{eq:normalised_cross_entropy_loss} as the normalised cross entropy loss. We then further define the centred normalised cross entropy loss,
 
@@
 
-		With the normalised cross entropy loss \eqref{eq:normalised_cross_entropy_loss} as our loss function, we now employ Theorem 8 of \cite{bartlett2002rademacher} for this loss and provide a bound for the expected normalised cross entropy loss for an unseen test example.
+		With the normalised cross entropy loss \eqref[name = ]{eq:normalised_cross_entropy_loss} as our loss function, we now employ Theorem 8 of \cite{bartlett2002rademacher} for this loss and provide a bound for the expected normalised cross entropy loss for an unseen test example.
 
@@
 				Since $\bar{\mathcal{L}}_{\epsilon} : \mathcal{Y} \times \mathcal{A} \to [0, 1]$ has a unit range and dominates itself, $\bar{\mathcal{L}}_{\epsilon}(y, f(x)) \leq \bar{\mathcal{L}}_{\epsilon}(y, f(x))$, the result follows directly from Theorem 8 of \cite{bartlett2002rademacher}.
-We then use the definition \eqref{eq:normalised_cross_entropy_loss} for the normalised cross entropy loss.
+We then use the definition \eqref[name = ]{eq:normalised_cross_entropy_loss} for the normalised cross entropy loss.
 			\end{proof}
@@
 
-		Equivalently, by definition \eqref{eq:predictor_class}, this result holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
-The bound \eqref{eq:expected_loss_bound} involves the Rademacher complexity $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda))$ of the centred normalised cross entropy loss applied onto the class of functions $F_{n}(\Theta, \Lambda)$, and not just the Rademacher complexity $\mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$ of the class of functions $F_{n}(\Theta, \Lambda)$ itself.
+		Equivalently, by definition \eqref[name = ]{eq:predictor_class}, this result holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
+The bound \eqref[name = ]{eq:expected_loss_bound} involves the Rademacher complexity $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda))$ of the centred normalised cross entropy loss applied onto the class of functions $F_{n}(\Theta, \Lambda)$, and not just the Rademacher complexity $\mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$ of the class of functions $F_{n}(\Theta, \Lambda)$ itself.
 In \cref{thm:rademacher_complexity_bound}, we have bounded the latter.
-We now proceed to bound the former with the latter, so that the former is also bounded by the bound on the latter \eqref{eq:rademacher_complexity_bound}.
+We now proceed to bound the former with the latter, so that the former is also bounded by the bound on the latter \eqref[name = ]{eq:rademacher_complexity_bound}.
 
@@
 
-		The bound \eqref{eq:composed_rademacher_complexity_bound} in \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss} will be the bridge that relates the expected cross entropy loss over our function class to the Rademacher complexity of our function class.
+		The bound \eqref[name = ]{eq:composed_rademacher_complexity_bound} in \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss} will be the bridge that relates the expected cross entropy loss over our function class to the Rademacher complexity of our function class.
 We now proceed to state the main theorem which forms the backbone of our learning algorithm for the kernel embedding classifier.
@@
 
-			for any $\epsilon \in (0, 1)$. Equivalently, the bound \eqref{eq:expected_loss_bound_for_kec} holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
-
-			\begin{proof}
-				The claim is a direct consequence of \cref{thm:rademacher_complexity_bound} and \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss}.
+			for any $\epsilon \in (0, 1)$.
+Equivalently, the bound \eqref[name = ]{eq:expected_loss_bound_for_kec} holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
+
+			\begin{proof}
+				From \cref{thm:rademacher_complexity_bound}, we have $\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) \leq 2 \alpha \rho$.
+Further, from \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss}, we have $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 2 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$.
+These are both deterministic inequalities, leading to $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 4 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \alpha \rho$.
+We then apply this inequality to \cref{thm:expected_normalised_cross_entropy_loss_bound}, which proves the claim.
+
 			\end{proof}
@@
 
-		Similar to many learning theoretic bounds, the expected risk bound \eqref{eq:expected_loss_bound_for_kec} is composed of three qualitatively different terms.
+		Similar to many learning theoretic bounds, the expected risk bound \eqref[name = ]{eq:expected_loss_bound_for_kec} is composed of three qualitatively different terms.
 The first term is a training loss or data fit term, which is a measure of how poorly the decision function $f$ is performing on a given training dataset.
 The second term is a model complexity or regularisation term, which measures how complicated the model is.
-In this case, the model complexity is measured by the Rademacher complexity, which captures the expressiveness of the function class by quantifying how well the function class is able to shatter pure noise.
+In this case, the model complexity is measured by the Rademacher complexity, which captures the expressiveness of the function class by quantifying how well the function class is able to shatter noise.
 The third term is a statistical constant which plays no specific role to the function class.
@@
 
-%		Consider a clipped cross entropy loss with a very small clipping factor, $0 < \epsilon << 1$.
-In this scenario, $M_{\epsilon} = - \log{\epsilon}$ would be very large, shooting up to infinity exponentially quickly as $\epsilon$ gets smaller, and the coefficient on the training loss term would then be very small.
-On the other hand, $\epsilon \log{\frac{1}{\epsilon}}$ would be very small, so that the coefficient on the complexity term would then be very large.
-In other words, as $\epsilon$ gets smaller, the training loss term becomes exponentially smaller while the complexity term becomes exponentially larger.
-This raises a major concern.
-The first concern is that the bound unlikely to be tight due to the exploding coefficient on the complexity term.
-Since we will likely be using some sort of gradient-based optimisation to minimise this upper bound, the second concern is that the gradient contribution coming from the training objective is vastly diminished while the gradient contribution from the complexity term is vastly amplified, potentially causing an imbalance in the optimisation to bias towards simpler models that do not perform well on the training data.
-%		
-%		A large clipping factor $\epsilon$ near one also raises similar concerns.
-The coefficient on the complexity term also explodes.
-Meanwhile, although the coefficient on the training loss is now larger, the loss is constant (at one) for probability estimates under $\epsilon$ and approaches the zero-one loss, for which the gradients are zero for most scenarios of the
-%
-
 		Consider a clipped cross entropy loss with either a very small clipping factor $\epsilon \approx 0$, or a very large clipping factor $\epsilon \approx 1$.
@@
 		This is great news for the complexity term.
-What about the the training loss term?
+What about the training loss term?
 Intuition tells us that, with a clipping factor of $\epsilon = e^{-1}$ that is slightly more than a third of the way into the interval $(0, 1)$ from zero, the classifier is not being penalised as strongly for assigning probabilities smaller than $e^{-1}$ to observed classes as compared to very small values of $\epsilon$.
@@
 
-%		In fact, the inequality $\mathcal{L}_{\epsilon_{1}}(y, f(x)) \leq \mathcal{L}_{\epsilon_{2}}(y, f(x))$ holds in general for all $\epsilon_{1} \leq \epsilon_{2}, x \in \mathcal{X}, y \in \mathcal{Y}$.
-
-		To see why inequality \eqref{eq:loss_inequality} holds, note that $[f_{y}(x)]_{\epsilon}^{1} \leq [f_{y}(x)]_{e^{-1}}^{1}$ holds for all $\epsilon \in (0, e^{-1}), x \in \mathcal{X}, y \in \mathcal{Y}$.
-Applying negative log to both sides yields the inequality from definition \eqref{eq:cross_entropy_loss}.
-
-		Therefore, we propose to choose $\epsilon = e^{-1}$, and then replace replace $\mathcal{L}_{e^{-1}}$ with $\mathcal{L}_{\epsilon}$ for some new generic $\epsilon \in (0, e^{-1})$ much smaller than $e^{-1}$.
+		To see why inequality \eqref[name = ]{eq:loss_inequality} holds, note that $[f_{y}(x)]_{\epsilon}^{1} \leq [f_{y}(x)]_{e^{-1}}^{1}$ holds for all $\epsilon \in (0, e^{-1}), x \in \mathcal{X}, y \in \mathcal{Y}$.
+Applying negative log to both sides yields the inequality from definition \eqref[name = ]{eq:cross_entropy_loss}.
+
+		Therefore, we propose to choose $\epsilon = e^{-1}$, and then replace replace $\mathcal{L}_{e^{-1}}$ with $\mathcal{L}_{\epsilon}$ for some new generic $\epsilon \in (0, e^{-1})$ much smaller than $e^{-1}$ on the training loss terms.
 In this way, we still maintain an upper bound for the training loss term.
-While this bound would not necessarily be tight for high training losses, the gradients from the high training loss would drive the system to a lower training loss, where the bound would become tight again.
+While this bound would not necessarily be tight for high training losses, the gradients from the high training loss would drive the system to a lower training loss, where the bound would become tight again as equality holds in \eqref[name = ]{eq:loss_inequality} whenever $f_{y}(x) \geq e^{-1}$.
 
@@
 			\begin{equation}
-			\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 e \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
+			\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 e \; \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
 			\label{eq:specific_expected_loss_bound_for_kec}
@@
 			for any $\epsilon \in (0, e^{-1})$.
-Equivalently, the bound \eqref{eq:specific_expected_loss_bound_for_kec} holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
-
-			\begin{proof}
-				The claim is a direct consequence of applying \cref{thm:expected_loss_bound_for_kec} with $\epsilon = e^{-1}$, and using \eqref{eq:loss_inequality} to further bound each of the cross entropy loss terms that has a clip factor $\epsilon = e^{-1}$ with the corresponding cross entropy loss term that has a generic clip factor $\epsilon \in (0, e^{-1})$ again.
+Equivalently, the bound \eqref[name = ]{eq:specific_expected_loss_bound_for_kec} holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
+
+			\begin{proof}
 
@@
 				\begin{equation}
-					\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{e^{-1}}(Y_{i}, f(X_{i})) + 4 e \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}}.
-				\end{equation}
-
-				For any $\epsilon \in (0, e^{-1})$, the inequality $\mathcal{L}_{e^{-1}}(Y_{i}, f(X_{i})) \leq \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i}))$ holds almost surely (a.s.) due to the deterministic inequality \eqref{eq:loss_inequality}.
+					\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{e^{-1}}(Y_{i}, f(X_{i})) + 4 e \; \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}}.
+				\end{equation}
+
+				For any $\epsilon \in (0, e^{-1})$, the inequality $\mathcal{L}_{e^{-1}}(Y_{i}, f(X_{i})) \leq \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i}))$ holds almost surely (a.s.) due to the deterministic inequality \eqref[name = ]{eq:loss_inequality}.
 These sets of inequalities together proves the claim.
@@
 		\begin{equation}
-			\Xi(\tilde{\theta}, \tilde{\lambda}) := \{ (\theta, \lambda) \in \Theta \times \Lambda : \| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}, \; k_{\theta}(x, x) \leq \alpha^{2}(\tilde{\theta}) := \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x) \} \\
+			\Xi(\tilde{\theta}, \tilde{\lambda}) := \{ (\theta, \lambda) \in \Theta \times \Lambda : \| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}, \; \sup_{x \in \mathcal{X}} k_{\theta}(x, x) \leq \alpha^{2}(\tilde{\theta}) := \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x) \}.
+\\
 			\label{eq:hyperparameter_subset_definition}
@@
 			\begin{proof}
-				This result is a direct consequence of applying \cref{thm:specific_expected_loss_bound_for_kec} with the choice of $\rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ and $\alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$.
-The inequality \eqref{eq:specific_expected_loss_bound_for_kec} then only holds for a subset of kernel parameter and regularisation $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ as defined by \eqref{eq:hyperparameter_subset_definition}.
+				We first apply \cref{thm:specific_expected_loss_bound_for_kec} with the choice of $\rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ and $\alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$.
+The inequality \eqref[name = ]{eq:specific_expected_loss_bound_for_kec} then only holds for a subset of kernel parameters and regularisations $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ as defined by \eqref[name = ]{eq:hyperparameter_subset_definition}.
 			\end{proof}
@@
 
-		Since inequality \eqref{eq:general_expected_risk_bound_hyperparameter_learning} holds for any $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ and we know that $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, we choose $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
+		Since inequality \eqref[name = ]{eq:general_expected_risk_bound_hyperparameter_learning} holds for any $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ and we know that $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, we choose $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
 We now arrive at our final result from which we can bound the expected risk for a specific choice of hyperparameters $\theta \in \Theta$ and $\lambda \in \Lambda$.
@@
 			\begin{equation}
-				\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e r(\theta, \lambda) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
+				\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e \; r(\theta, \lambda) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
 			\label{eq:expected_risk_bound_hyperparameter_learning}
@@
 	For a kernel embedding classifier, the modelling lies in the choice of the kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ over the input space $\mathcal{X}$.
-The only requirement for the kernel $k$ is that it is symmetric and positive definite.
-In some cases, positive semi-definite kernels also suffice.
-There are no other requirements, and thus we may construct richer and more expressive kernel families in any way we prefer, subject to those requirements.
-Once such a kernel family is constructed, the kernel parameters $\theta$, as well as the regularisation parameter $\lambda$, can be learned effectively using the training algorithm described in \cref{sec:hyperparameter_learning}.
+The only requirement for the kernel $k$ is that it is symmetric and positive definite, and thus we may construct richer and more expressive kernel families in any way subject to such requirements.
+Once such a kernel family is constructed, the kernel parameters $\theta$, as well as the regularisation parameter $\lambda$, can be learned effectively using algorithm 1.
 
@@
 	\begin{table}[h]
-			\begin{center}
-				\begin{tabular}{ l || c c c c c}
-					KEC Variant & Width & Depth & Scalability & Flexibility & Typical Datasets  \\
-					\hline
-					Nonlinear KEC & Wide & Shallow & Low & High & High or Low $d$, Low $n$ \\
-					Linear KEC & Narrow & Shallow & High & Low & Low $d$, High $n$ \\
-					Deep Nonlinear KEN &  Wide & Deep & Low & High & Structured $d$, Low $n$ \\
-					Deep Linear KEN & Narrow & Deep & High & High & Structured $d$, High $n$ \\ 
-				\end{tabular}
-			\end{center}
 		\caption{Properties of kernel embedding classifier architectures}
 		\label{tab:kernel_embedding_classifier_variants}
+		\centering
+		\begin{tabular}{lccccc}
+			KEC Variant & Width & Depth & Scalability & Flexibility & Typical Datasets  \\
+			\midrule
+			Implicit KEC & Wide & Shallow & Low & High & High or Low $d$, Low $n$ \\
+			Explicit KEC & Narrow & Shallow & High & Low & Low $d$, High $n$ \\
+			Implicit KEN &  Wide & Deep & Low & High & Structured $d$, Low $n$ \\
+			Explicit KEN & Narrow & Deep & High & High & Structured $d$, High $n$ \\ 
+		\end{tabular}
 	\end{table}
 
-	\subsection{Linear Kernel Embedding Classifier}
-	\label{app:linear_kernel_embedding_classifier}
+	\subsection{Explicit Kernel Embedding Classifier}
+	\label{app:explicit_kernel_embedding_classifier}
 
@@
 
-		By explicitly defining a finite dimensional feature space, the matrix to be inverted during both learning and inference in the kernel embedding classifier can be reduced from size $n \times n$ to size $p \times p$ by using the Woodbury matrix identity.
-We use this identity to modify \cref{alg:kernel_embedding_classifier_training} to \cref{alg:linear_kernel_embedding_classifier_training} to exploit this computational speed up.
-
-%		\note{Choose each batch to be greater than the dimensionality of the last layer to avoid numerical instability with Cholesky Decomposition as the upper bound is not tight for small $n$ and the gradients may send it off to some unstable region instead}
+		By explicitly defining a finite dimensional feature space, the matrix to be inverted during both learning and inference in the kernel embedding classifier can be reduced from size $n \times n$ to size $p \times p$ by using the Woodbury matrix inversion identity \citep{higham2002accuracy}.
+We use this identity to modify algorithm 1 to \cref{alg:explicit_kernel_embedding_classifier_training} to exploit this computational speed up.
 
 		However, with a fixed and finite amount of feature basis, the model becomes parametric and its flexibility is compromised.
-In other words, the model is narrow in the number of feature representations, and also shallow in the number of transformations used to define each feature.
+In other words, the model is narrow in the number of feature representations.
 We therefore turn to multi-layered feature compositions, where the flexibility of a model comes from the deep architecture instead of implicit high dimensional features.
@@
 		\begin{algorithm}[tb]
-			\caption{Linear KEC Hyperparameter Learning with Batch Stochastic Gradient Descent}
-			\label{alg:linear_kernel_embedding_classifier_training}
+			\caption{Explicit KEC Hyperparameter Learning with Batch Stochastic Gradient Updates}
+			\label{alg:explicit_kernel_embedding_classifier_training}
 			\begin{algorithmic}[1]
@@
 				\STATE $P_{\theta, \lambda} \leftarrow Z_{\theta} W_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-				\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \alpha(\theta) \sqrt{\sum_{c = 1}^{m} \sum_{j = 1}^{p} (W_{\theta, \lambda})_{j, c}^{2}}$
+				\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; \alpha(\theta) \sqrt{\sum_{c = 1}^{m} \sum_{j = 1}^{p} (W_{\theta, \lambda})_{j, c}^{2}}$
 				\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
-				\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial r}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial r}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
+				\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial q}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial q}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
 				\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
@@
 
-		In order to train the multi-layered features in an end-to-end fashion, we employ \cref{alg:kernel_embedding_classifier_training}.
+		In order to train the multi-layered representations in an end-to-end fashion, we employ algorithm 1.
 With a deep architecture, the feature representations the kernel embedding network can learn are very flexible, and can work very well for structured data by employing suitable network architectures.
@@
 
-	\subsection{Deep Linear Kernel Embedding Network}
-	\label{app:deep_linear_kernel_embedding_network}
-
-		The deep linear kernel embedding network is simply a special case at the intersection of the linear kernel embedding classifier and the deep kernel embedding network.
-From the linear KEC perspective, we simply choose $\varphi_{\theta}(x) = \varphi^{(L)}_{\theta_{L}}\big(\varphi^{(L - 1)}_{\theta_{L - 1}}(\dots\varphi^{(2)}_{\theta_{2}}(\varphi^{(1)}_{\theta_{1}}(x)))\big)$.
-From the deep kernel embedding network perspective, we simply choose $\kappa(z, z') = z^{T} z'$ to be a linear kernel.
-
-		Nevertheless, this model architecture is perhaps the most practical and powerful form of the kernel embedding classifier.
+	\subsection{Explicit Kernel Embedding Network}
+	\label{app:explicit_kernel_embedding_network}
+
+		The explicit kernel embedding network is simply a special case at the intersection of the explicit kernel embedding classifier and the kernel embedding network.
+From the explicit KEC perspective, we simply choose $\varphi_{\theta}(x) = \varphi^{(L)}_{\theta_{L}}\big(\varphi^{(L - 1)}_{\theta_{L - 1}}(\dots\varphi^{(2)}_{\theta_{2}}(\varphi^{(1)}_{\theta_{1}}(x)))\big)$.
+From the KEN perspective, we simply choose $\kappa(z, z') = z^{T} z'$ to be a linear kernel.
+
+		This model architecture is a very practical and powerful form of the kernel embedding classifier.
 By having a deep architecture, the classifier is still capable of learning flexible representations on structured data, while being able to scale to larger datasets due to the linear kernel at the output layer, provided that the dimensionality of the last layer is relatively small compared to the size of the dataset.
 
-		As a subclass of linear KEC, we can employ \cref{alg:linear_kernel_embedding_classifier_training} to learn the multi-layered features effectively.
+		As a subclass of explicit KEC, we can employ \cref{alg:explicit_kernel_embedding_classifier_training} to learn the multi-layered features effectively.
 In fact, by not mapping the multi-layered features into a nonlinear kernel, the gradients for each network weight and bias are usually more pronounced, and learning is usually faster in comparison.
-
-	\subsection{Learning Objective Intuitions}
-	\label{app:learning_objective_intuitions}
-
-		The learning objective \eqref{eq:objective} for the kernel embedding classifier is composed of two terms: a training loss (or data fit) term and a model complexity (or regularisation) term.
-In this section we provide some intuition towards the relative effects of each term for two types of kernel models: a radial basis type kernel, producing a nonlinear kernel embedding classifier, and a linear kernel, producing a linear kernel embedding classifier.
-
-		Consider a typical radial basis type kernels such as the Gaussian (squared exponential) or Mat\'{e}rn kernel $k_{\theta}$.
-These types of kernels are usually placed on top of subsets of Euclidean spaces $\mathcal{X} \subseteq \mathbb{R}^{d}$ where $d$ is the dimensionality of an input $x \in \mathcal{X}$.
-Here, the hyperparameters $\theta$ usually includes length scale parameters ($1$ parameter for isotropic kernels, $d$ parameters for anisotropic kernels, or $\frac{d (d - 1)}{2}$ parameters for non-diagonal kernels) and possibly a sensitivity parameter which is simply a multiplicative constant that scales the magnitude of the kernel.
-
-		These types of kernels implicitly map the input space $\mathcal{X}$ to an uncountably infinite dimensional RKHS $\mathcal{H}_{k_{\theta}}$, making the model nonparametric.
-This means that the feature space $\mathcal{H}_{k_{\theta}}$ is already quite flexible for any $\theta \in \Theta$, since for any $\theta \in \Theta$ it has an uncountably infinite amount of feature basis to use for creating linear decision boundaries.
-As such, and it is relatively easy to find linear decision boundaries within such a high dimensional space.
-In this way, experiments show that for most datasets, most initialisations of $\theta$ already produces a very reasonable model of low training loss.
-In fact, there is often a subset of length scales and sensitivity parameters within $\Theta$ in which the training loss is relatively constant.
-
-		In these scenarios, the gradients from the training loss term is usually very small, and the gradient from the learning objective is dominated by the complexity term.
-Intuitively, the learning objective communicating the following message: ``the model is already performing quite well, or at least as best as it can, on the dataset, so let us focus on finding the simplest model that can still produce a similar performance''.
-
-		This is in contrast to the case with linear kernels $k_{\theta}(x, x') = \varphi_{\theta}(x)^{T} \varphi_{\theta}(x')$.
-In this case, the input space $\mathcal{X}$, usually but not necessarily also a subset of the Euclidean space $\mathbb{R}^{d}$, is explicitly mapped to a finite dimensional RKHS $\mathcal{H}_{k_{\theta}} = \mathcal{Z} \subseteq \mathbb{R}^{p}$ through the feature map $\varphi_{\theta} : \mathcal{X} \to \mathcal{Z}$.
-With only finitely many feature basis, the model becomes parametric, and the number of features is fixed at $p$ so that its capacity does not grow with the size of the dataset like a nonparametric model.
-
-		In \cref{app:deep_linear_kernel_embedding_network}, we focused on linear kernel embedding classifiers with deep neural network features, where the flexibility of such a narrow model comes from the deep architecture instead.
-This is in contrast to the case of radial basis type kernels which has a shallow architecture and the flexibility comes from the wide collection of implicit feature basis (uncountably many) which becomes more expressive as we observe more data.
-In this case, for most initialisations of the model parameters $\theta \in \Theta$, the model will not necessarily perform well on the training data.
-As such, the training loss is large and its gradients will be larger in magnitude, in order to drive the model towards a better model fit.
-
-		On the other hand, the complexity term is comparatively smaller.
-Recall that the model complexity is measured in the RKHS $\mathcal{H}_{k_{\theta}}$, which in this case is the space of the last layer $\mathcal{Z} \subseteq \mathbb{R}^{p}$ of the neural network.
-Earlier layers are free to learn very complicated feature representations.
-As long as the learned feature representations in the last layer is simple, the complexity term will be small.
-Since the number of features is fixed, the capacity of the model is limited, and thus the complexity term is usually not as big as the training loss term.
-In this way, the gradients from the learning objective is dominated by the training loss term.
-Intuitively, the learning objective is communicating the following message: ``the model is performing very poorly on the dataset, so let us first focus on learning representations to explain the dataset before we worry about finding the simplest model''.
+This approach was used to train the neural network features in our experiments.
 
 \newpage
-\section{Design Choices and More Discussion}
-\label{app:design_choices}
-
-	In this section we discuss the various design choices we make in formulating the kernel embedding classifier.
-
-	\subsection{Decision Probabilities: Why clip-normalise and not softmax-normalise or softplus-normalise?}
-
-		For \eqref{eq:probability_clip_normalise}...
-
-		The simple reason is that it works better.
-The more theoretical reason is that our raw probability estimates usually produces predictions with low cross entropy loss.
-This means that it assigns high probability for the correct class and low probability to other classes.
-Because the decision probability estimates are not guaranteed to be strictly positive, the lower probabilities for those other classes can sometimes be slightly negative, and clip-normalisation would simply make them zero, as that would be closer to what the kernel embedding classifier is trying to express: it is so unlikely it has even assigned it negative probabilities, so it might as well be zero.
-When normalising after clipping, the zeroed-out probabilities do not come into play and the high probabilities get to keep their high values.
-Softmax and softplus operations would instead assign small positive probabilities to those slightly negative instances.
-When normalising after this, because the unlikely classes has taken up some probabilities, the class with high probabilities will have their high probabilities slightly reduces, making the cross entropy loss slightly higher and the predictions less confident.
-
-	\subsection{Information Entropy: Why define information gain to be zero despite being infinitely surprised?}
-
-		For \eqref{eq:empirical_information}...
-
-		\note{\textbf{Unpolished.}} This is really for numerical and experimental reasons.
-The information entropy map obtained this way are just simply much smoother and intuitive.
-The alternative is to first clip the raw probability predictions at some very small tolerance, such as $\epsilon = 10^{-15}$, before we pass it through the log, as what is done in many information or entropy based computations, such as the cross entropy computation implemented in \texttt{scipy}.
-When we tried this, we saw that this produces an unnecessarily non-smooth estimate of the information entropy map.
-Furthermore, by adjusting the tolerance $\epsilon$ slightly to other small numbers, such as $10^{-10}$ or $10^{-20}$, the information entropy map changes in where the non-smoothness occurs and in what magnitude.
-This was simply too ugly for us to accept.
-Instead, defining the information gain to zero despite being infinitely surprised gave us very smooth estimates that is very close to both the map we expect and the map we obtain from computing the information entropy directly from the clip-normalised decision probabilities.
-
-	\subsection{Information Entropy: Why clip from below at zero?}
-
-		For \eqref{eq:empirical_information_entropy}...
-
-		\note{\textbf{Unpolished.}} Similar to the reason for clip-normalising decision probabilities, if the inference algorithm has produces an information entropy that is slightly less than zero, this just means that it is very confident at those regions.
-As such, in the limit, we expect that this would converge back to zero.
-Therefore, for finite data, we clip it from below at zero to indicate what the current data suggests the true information entropy should be when we have infinite data.
-
-	\subsection{Cross Entropy Loss: Why use the raw decision probabilities?}
+\bibliographystyle{apalike}
+\bibliography{kernel_embedding}
 

### 2017-05-23 cake.tex
Fix typo in pseudocode

@@
 			\REPEAT
-			\STATE Sample the next batch $\mathcal{I} \subseteq \mathbb{N}_{n}$, $| \mathcal{I} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I} = \mathbb{N}_{n}$)
-			\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
-			\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathcal{I}, j \in \mathcal{I}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
+			\STATE Sample the next batch $\mathcal{I}_{b} \subseteq \mathbb{N}_{n}$, $| \mathcal{I}_{b} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I}_{b} = \mathbb{N}_{n}$)
+			\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}_{b}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
+			\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathcal{I}_{b}, j \in \mathcal{I}_{b}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
 			\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n_{b} \lambda I_{n_{b}}) \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
@@
 			\STATE $P_{\theta, \lambda} \leftarrow K_{\theta} V_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-			\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
+			\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n_{b}} \sum_{i \in \mathcal{I}_{b}} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
 			\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)

### 2017-05-23 cake_appendix.tex
Fix typo in pseudocode

@@
 				\REPEAT
-				\STATE Sample the next batch batch $\mathcal{I} \subseteq \mathbb{N}_{n}$, $| \mathcal{I} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I} = \mathbb{N}_{n}$)
-				\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
-				\STATE $Z_{\theta} \leftarrow \{\varphi_{\theta}(x_{i}) : i \in \mathcal{I}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times p}$
+				\STATE Sample the next batch $\mathcal{I}_{b} \subseteq \mathbb{N}_{n}$, $| \mathcal{I}_{b} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I}_{b} = \mathbb{N}_{n}$)
+				\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}_{b}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
+				\STATE $Z_{\theta} \leftarrow \{\varphi_{\theta}(x_{i}) : i \in \mathcal{I}_{b}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times p}$
 				\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(Z_{\theta}^{T} Z_{\theta} + n_{b} \lambda I_{p}) \hspace{\fill} \in \mathbb{R}^{p \times p}$
@@
 				\STATE $P_{\theta, \lambda} \leftarrow Z_{\theta} W_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-				\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; \alpha(\theta) \sqrt{\sum_{c = 1}^{m} \sum_{j = 1}^{p} (W_{\theta, \lambda})_{j, c}^{2}}$
+				\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n_{b}} \sum_{i \in \mathcal{I}_{b}} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; \alpha(\theta) \sqrt{\sum_{c = 1}^{m} \sum_{j = 1}^{p} (W_{\theta, \lambda})_{j, c}^{2}}$
 				\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)

### 2017-06-05 cake.tex
Minor changes

@@
 	Under the assumption that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$, \citet[Theorem 4]{song2009hilbert} proved that the conditional expectation of a function $g \in \mathcal{H}_{l}$ can be expressed as an inner product, $\mathbb{E}[g(Y) | X = x] = \langle \mu_{Y | X = x}, g \rangle$.
-While the assumptions that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$ and $k(x, \cdot) \in \mathrm{image}(C_{XX})$ holds for finite input domains $\mathcal{X}$ for characteristic kernels $k$, it is not necessarily true when $\mathcal{X}$ is a continuous domain \citep{fukumizu2004dimensionality}, which is the scenario for many classification problems.
+While the assumptions that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$ and $k(x, \cdot) \in \mathrm{image}(C_{XX})$ hold for finite input domains $\mathcal{X}$ and characteristic kernels $k$, it is not necessarily true when $\mathcal{X}$ is a continuous domain \citep{fukumizu2004dimensionality}, which is the scenario for many classification problems.
 In this case, $C_{YX} C_{XX}^{-1}$ becomes only an approximation to $\mathcal{U}_{Y | X}$, and we instead regularise the inverse and use $C_{YX} (C_{XX} + \lambda I)^{-1}$, which also serves to avoid overfitting \citep{song2013kernel}.
@@
 In the multiclass setting, the output label space is finite and discrete, taking values only in $\mathcal{Y} = \mathbb{N}_{m} := \{1, \dots, m\}$.
-Naturally, we first choose the Kronecker delta kernel $\delta : \mathbb{N}_{m} \times \mathbb{N}_{m} \to \{0, 1\}$ as the output kernel $l$, where labels that are the same has unit similarity and labels that are different have no similarity.
+Naturally, we first choose the Kronecker delta kernel $\delta : \mathbb{N}_{m} \times \mathbb{N}_{m} \to \{0, 1\}$ as the output kernel $l$, where labels that are the same have unit similarity and labels that are different have no similarity.
 That is, for all pairs of labels $y_{i}, y_{j} \in \mathcal{Y}$, $\delta(y_{i}, y_{j}) = 1$ only if $y_{i} = y_{j}$ and is $0$ otherwise.
@@
 			\STATE $P_{\theta, \lambda} \leftarrow K_{\theta} V_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-			\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n_{b}} \sum_{i \in \mathcal{I}_{b}} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
+			\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n_{b}} \sum_{i = 1}^{n_{b}} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
 			\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
@@
 	Our learning algorithm does not restrict the way the kernel $k_{\theta}$ is constructed from its parameters $\theta \in \Theta$.
-One particularly useful class of kernel embedding classifiers are those where the input kernel $k(x, x') = \langle \varphi(x), \varphi(x') \rangle$ is constructed from neural networks $\varphi : \mathcal{X} \to \mathbb{R}^{p}$ explicitly.
+One particularly useful class of kernel embedding classifiers are those where the input kernel $k_{\theta}(x, x') = \langle \varphi_{\theta}(x), \varphi_{\theta}(x') \rangle$ is constructed from neural networks $\varphi_{\theta} : \mathcal{X} \to \mathbb{R}^{p}$ explicitly.
 We refer to kernel embedding classifiers constructed this way as kernel embedding networks (KEN).
-Neural networks are typically defined by weights and biases of its hidden layers, which collectively define the parameters of the constructed kernel, and are thus trainable under our learning algorithm.
+Neural networks are typically defined by weights and biases of its hidden layers, which collectively define the parameters $\theta$ of the constructed kernel, and are thus trainable under our learning algorithm.
 These kernels benefit in both scalability and expressibility.
@@
 The kernel embedding network instead employs a linear kernel on the last hidden layer to construct the conditional embedding.
-We then train both networks from the same initialisation with stochastic gradient updates using 6000 images at a time for 800 epochs, with learning rate $\eta = 0.01$.
+We then train both networks from the same initialisation with stochastic gradient updates using $n_{b} = 6000$ images at a time for 800 epochs, with learning rate $\eta = 0.01$.
 All biases and standard deviations of zero mean truncated normal distributed weights are initialised to 0.1.

### 2017-07-09 cake.tex
Review first half of paper

@@
 That is, the kernel itself is not learned.
-Multiple kernel learning has focused on learning constructions of richer kernels from simpler ones \citep{gonen2011multiple, zien2007multiclass}, although the simpler kernels themselves are also preselected by design.
+Multiple kernel learning has focused on learning constructions of richer kernels from simpler ones \citep{gonen2011multiple, zien2007multiclass}, although the simpler kernels themselves are usually fixed a-priori.
 By placing a Gaussian process prior over the function class, Gaussian process models \citep{rasmussen2006gaussian} achieve tractable marginal likelihood based learning algorithms that is able to learn the model hyperparameters, which includes the kernel parameters.
@@
 Recent work has introduced Gaussian process priors on mean embeddings to achieve Bayesian hyperparameter learning \citep{flaxman2016bayesian}.
-However, the learning is separate from the application domain, and the approach has yet to generalise to conditional embeddings.
+However, the approach has yet to generalise to conditional embeddings for supervised learning.
 
@@
 We begin by proposing the kernel embedding classifier (KEC), a principled framework for inferring multiclass probabilistic outputs using conditional embeddings, and provide a proof for its stochastic convergence.
-We then employ Rademacher complexity as a data dependent model complexity measure, and prove that expected classification risk can be bounded by empirical risk and conditional embedding trace norm with high probability.
+We then employ Rademacher complexity as a data dependent model complexity measure, and prove that expected classification risk can be bounded by a combination of empirical risk and conditional embedding norm with high probability.
 We use this bound to propose a learning objective that learns the balance between data fit and model complexity in a way that does not rely on priors.
@@
 We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:kernel_embedding_classifier_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size.
-The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is performed only once after learning instead of once every learning iteration, and can be avoided by using kernel herding \citep{chen2010super} or other kernel data reduction technique to select data subsets that can estimate the already learned embedding.
+The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is performed only once after learning instead of once every learning iteration, and can be avoided by using kernel herding \citep{chen2010super} or random Fourier features \citep{rahimi2008random} to estimate the already learned embedding.
 All further inference steps take $O(n^{2})$ time for back substitution.

### 2017-08-01 cake.tex
Before NIPS review

@@
 
-		We demonstrate the average performance of learning anisotropic Gaussian kernels and kernels with explicit neural network features on standard UCI datasets \citep{bache2013uci}, summarised in \cref{tab:uci_experiments}.
+		We demonstrate the average performance of learning anisotropic Gaussian kernels and kernels constructed from neural networks on standard UCI datasets \citep{bache2013uci}, summarised in \cref{tab:uci_experiments}.
 The former has a shallow but wide model architecture, while the latter has a deeper but narrower model architecture.
 The Gaussian kernel is learned with both full (GKEC) and batch stochastic gradient updates (GKEC-SGD) using a tenth ($n_{b} \approx \frac{n}{10}$) of the training set each training iteration, with sensitivity and length scales initialised to $1$.
-For neural network induced kernels, we randomly select two simple fully connected architectures with 16-32-8 (KEN-1) and 96-32 (KEN-2) hidden units respectively, and learn the conditional embedding without dropout under ReLU activation.
+For kernel embedding networks, we randomly select two simple fully connected architectures with 16-32-8 (KEN-1) and 96-32 (KEN-2) hidden units respectively, and learn the conditional embedding without dropout under ReLU activation.
 Biases and standard deviations of zero mean truncated normal distributed weights are initialised to $0.1$, and are to be trained with full gradient updates.
@@
 Classifiers are trained with the Adam optimiser \citep{kingma2014adam} in TensorFlow \citep{abadi2016tensorflow} with rate $\eta = 0.1$ and $\epsilon = 10^{-15}$ under the learning objective $q(\theta, \lambda)$ \eqref{eq:learning_objective}.
-Training is ran for 1000 or 10000 iterations when using full or batch gradient updates respectively, regardless of convergence.
+Training is ran for 1000 epochs, regardless of convergence, for direct comparison.
 All attributes are scaled to the unit range.
@@
 \Cref{tab:uci_experiments} shows that our learning algorithm achieves similar performance without any special tuning or heuristics, but by simply placing a conditional embedding on training data and applying a complexity bound based learning algorithm.
-The SGD approach for Gaussian kernels performs similarly to the full gradient approach, supporting \cref{thm:expected_risk_bound_hyperparameter_learning_copy} for $n = n_{b}$.
-For neural network features, we did not attempt to choose an optimal architecture for each dataset.
+The stochastic gradient approach for Gaussian kernels performs similarly to the full gradient approach, supporting \cref{thm:expected_risk_bound_hyperparameter_learning_copy} for $n = n_{b}$.
+For kernel embedding networks, we did not attempt to choose an optimal architecture for each dataset.
 The learning algorithm is to train the same simple untrained network for different datasets under only 1000 iterations, and still generates comparable performance.

### 2017-09-19 old/fabio_quick_edit_1.tex
Add folder 'old'

--- 2017-05-10 kernel_embedding_classifier.tex
@@
 % if you need to pass options to natbib, use, e.g.:
-\PassOptionsToPackage{square, authoryear, comma, sort&compress}{natbib}
-% before loading nips_2016
+\PassOptionsToPackage{numbers, compress}{natbib}
+% before loading nips_2017
 %
 % to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{nips_2016}
-
-\usepackage[final]{nips_2016}
+% \usepackage[nonatbib]{nips_2017}
+
+\usepackage{nips_2017}
 
 % to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[final]{nips_2016}
-
-\usepackage[utf8x]{inputenc} % allow utf-8 input
+% \usepackage[final]{nips_2017}
+
+\usepackage[utf8]{inputenc} % allow utf-8 input
 \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
@@
 \newtheorem{claim}[theorem]{Claim}
-
 \usepackage{multirow}
-
 \usepackage{algorithm}
 \usepackage{algorithmic}
+
+\newcommand{\argmax}{\operatornamewithlimits{argmax}}
+\newcommand{\note}[1]{{\color{orange} #1}}
+\newcommand{\edit}[1]{{\color{forestgreen} #1}}
 
@@
 	\end{theorem}
-	Finally, to perform classification at a query point $x^{\star} \in \mathcal{X}$, we simply take the class with the highest empirical decision probability, $\hat{y}^{\star} = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x^{\star})$.
-
-	While the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ will converge to the true decision probability function  $p_{c} : \mathcal{X} \to [0, 1]$ in the limit, for finite $n$ and a fixed regulariser $\lambda > 0$, the stochasticity in the empirical estimates implies that these probabilities may not necessarily sum up to one, nor are they strictly restricted to the range $[0, 1]$.
-However, they will usually be very close to the true predicted probabilities.
-Moreover, such stochasticity also does not principally affect the classification prediction, since we simply take the argmax of the empirical decision probability vector \eqref{eq:empirical_decision_probability_vector}.
-
-	If strict, valid probabilities are required for interpretation, visualisation, or other purposes, the probabilities can be clipped at zero then normalised to one, a procedure we refer to as \textit{clip-normalisation},
+	While decision probability estimates \eqref{eq:empirical_decision_probability} do not necessarily form a normalised distribution for finite $n$, \cref{thm:probability_convergence_copy} guarantees that they approach one with increasing sample sizes.
+If normalised distributions are required for interpretation, distribution estimates \eqref{eq:empirical_decision_probability} can be clip-normalised,
 	\begin{equation}
 		\tilde{p}_{c}(x) := \frac{\max\{\hat{p}_{c}(x), 0\}}{\sum_{j = 1}^{m} \max\{\hat{p}_{j}(x), 0\}}.
-	\label{eq:probability_clip_normalise}
-	\end{equation}
-	Notice that for classification prediction, the argmax solution over the classes of the empirical decision probabilities \eqref{eq:empirical_decision_probability} and its clip-normalised version \eqref{eq:probability_clip_normalise} remain the same.
-Furthermore, since $\hat{p}_{c}(x)$ converges to true probabilities $p_{c}(x)$ according to \cref{thm:probability_convergence_copy}, the effect of clip-normalisation reduces as $n$ increases such that $\tilde{p}_{c}(x)$ becomes very close to $\hat{p}_{c}(x)$ and $p_{c}(x)$.
-
-\section{Learning with Rademacher Complexity based Risk Bounds}
+	\label{eq:empirical_decision_probability_clip_normalised}
+	\end{equation}
+	Of course, classification $\hat{y}(x) = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x) = \argmax_{c \in \mathbb{N}_{m}} \tilde{p}_{c}(x)$ remains invariant.
+\Cref{thm:probability_convergence_copy} also implies the reducing effect of clip-normalisation as with increasing sample sizes, where $\tilde{p}_{c}(x)$ approaches to both $\hat{p}_{c}(x)$ and $p_{c}(x)$.
+
+\section{Hyperparameter Learning with Rademacher Complexity Bounds}
 \label{sec:hyperparameter_learning}
 
-	The formulation of the kernel embedding classifier requires the specification of a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ over the input space $\mathcal{X}$, or rather, a class of kernels $\{k_{\theta}\}_{\theta \in \Theta}$ parametrised by the kernel parameters $\theta \in \Theta$.
-It also requires the specification of a regularisation parameter $\lambda$ for the conditional embedding as in \eqref{eq:empirical_conditional_embedding}.
-These are hyperparameters of the kernel embedding classifier which needs to be learned in order to produce a reasonable classifier model.
-While decision probability estimates \eqref{eq:empirical_decision_probability} converge to the true decision probabilities \eqref{eq:decision_probability} for any choice of positive definite kernels $k_{\theta}$ (\cref{thm:probability_convergence_copy}), for finite $n$ we would like to find the kernel from the kernel family which produces the most appropriately discriminative model to perform classification tasks.
-
-	In the kernel embedding literature, hyperparameters has been notoriously difficult to tune, and its learning is usually only restricted to heuristics or methods such as cross validation which requires pre-selecting the number of folds and the split of the folds.
-In this paper, we take a learning theoretic approach to learn the hyperparameters of the KEC, inspired by the original training procedure of support vector classifiers (SVC) as described by \cite[p.
-185]{m2001introduction}.
-Assuming a perfectly separable case, the training of a SVC begins by introducing a \textit{prediction constraint} on the training set, where the classifier is constrained to correctly classify all the available training examples.
-The strategy is to minimise the \textit{complexity} of the SVC model while ensuring perfect classification over training examples.
-The model complexity in the SVC context is measured by the VC dimension $h$ of the binary classifier, which has an upper bound $h \leq \lVert \bvec{w} \rVert^{2} R^{2} + 1$.
-Since it is difficult to compute the VC dimension explicitly, we instead minimise its upper bound, which is equivalent to and leads to the common interpretation of maximising the margin $\frac{2}{\lVert \bvec{w} \rVert}$.
-
-	Similarly, we propose to train our kernel embedding classifier with the same high level formulation: minimise the model complexity without compromising classification performance on the training data.
-Instead of employing the VC dimension as the complexity measure of our model, which is defined mainly for binary classifiers, we consider the \textit{Rademacher complexity} of the kernel embedding classifier.
-Given a function class $\mathcal{F}$ and a loss function $\mathcal{L}(y, \bvec{f}(x))$, the expected test loss $\mathbb{E}[\mathcal{L}(Y, \bvec{f}(X))]$ is bounded by the expected training loss $\frac{1}{n}\sum_{i = 1}^{n} \mathcal{L}(y_{i}, \bvec{f}(x_{i}))$ plus the Rademacher complexity and a constant with high probability, similar to the case with the VC dimension \citep{bartlett2002rademacher}.
-As such, if we can minimise the model complexity in the sense of the Rademacher complexity while maintaining a low training loss, we can optimise generalisation ability in the sense of low expected test loss.
-
-			Further more, since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:specific_expected_loss_bound_for_kec_applied} is true with probability $1 - \beta$ if we replace all the random variables $X_{i}, Y_{i}$ with the training observations $x_{i}, y_{i}$.
-
-			Therefore, in order to minimise the expected test loss, we propose the following training objective for the kernel embedding classifier,
-
-	For a predictor parametrised as $f(x; W) = W^{T} x$, \cite{yu2014large} showed that the global Rademacher complexity of such a predictor is upper-bounded in terms of its trace norm, $\sqrt{\mathrm{trace}(W^{T} W)}$.
-This was originally discussed in the context of multi-label classification, where $W \in \mathbb{R}^{d \times L}$ and $f$ produces a binary vector of length $L$ indicating the multiple labels that describes the input $x \in \mathbb{R}^{d}$.
-In the context of the kernel embedding classifier, the empirical decision probabilities \eqref{eq:empirical_decision_probability_vector} also has the same analytical form, where the input $x$ is replaced by some feature vector $\phi(x)$.
-By using the canonical feature map $\phi(x) = k(x, \cdot)$ and the reproducing property $\langle \phi(x), \phi(x') \rangle = k(x, x')$ in the RKHS, we can write \eqref{eq:empirical_decision_probability_vector} as $\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \Phi^{T} \phi(x) = W^{T} \phi(x)$, where instead of mapping input examples in $\mathbb{R}^{d}$ to output multi-label vector $\mathbb{R}^{L}$, $W^{T}$ maps features in the RKHS $\mathcal{H}_{k}$ to the a vector of multiclass probabilities in $\mathbb{R}^{m}$.
-Using the reproducing property $K = \Phi^{T} \Phi$ again, the squared trace norm for such a predictor is then $\mathrm{trace}(W^{T} W) = \mathrm{trace}(\bvec{Y}^{T} (K + n \lambda I)^{-1} K (K + n \lambda I)^{-1} \bvec{Y})$.
-We therefore propose to use this trace norm as an upper bound measure of the kernel embedding classifier model complexity,
-	\begin{equation}
-		r(\theta, \lambda) := \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} K_{\theta} (K_{\theta} + n \lambda I)^{-1} \bvec{Y}\bigg)},
-	\label{eq:trace_norm}
-	\end{equation}
-	where we use the subscript $\theta$ to make explicit the dependence on the kernel parameters. Therefore, with high probability and up to a constant term, an upper bound of the test loss is
-	\begin{equation}
-		q(\theta, \lambda) := \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}(y_{i}, \hat{\bvec{p}}_{\theta, \lambda}(x_{i})) + r(\theta, \lambda).
-	\label{eq:objective}
-	\end{equation}
-	We employ gradient based methods to train the kernel embedding classifier with this training loss and complexity bound objective.
-The gradients of the learning objective with respect to the hyperparameters is obtained using automatic differentiation.
+	Kernel embedding classifiers are equivalent to a conditional embedding with a discrete target space $\mathcal{Y}$.
+We now turn to address hyperparameter learning for the KEC, and explicitly denote the kernel parameters $\theta \in \Theta$ and regularisation parameter $\lambda \in \Lambda = \mathbb{R}_{+}$ that define the KEC model.
+Hyperparameter learning for conditional embeddings is particularly difficult compared to joint embeddings, since the kernel $\{k_{\theta} : \theta \in \Theta\}$ is to be learned jointly with a regularisation parameter $\lambda$.
+While the conditional embedding map $\hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the operator $\mathcal{U}$ that minimises the regularised least squares loss $\frac{1}{n} \sum_{i = 1}^{n} \| \psi(y_{i}) - \mathcal{U} \phi(x_{i}) \|_{\mathcal{H}_{l}}^{2} + \lambda \| \mathcal{U} \|_{HS}$ in the RKHS \citep{song2013kernel}, minimising this loss directly over $\theta \in \Theta, \lambda \in \Lambda$ for $\mathcal{U} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X}$ would trivially result in an overfitted model with $\lambda \rightarrow 0$.
+This implies that the notion of model complexity is especially important.
+Nevertheless, current standard solutions employ either cross validation or nested loops separating $\theta$ and $\lambda$, both of which are heuristics and subject to design choices.
+
+	To this end, we propose to use a learning theoretic approach to quantify a balance between model complexity and performance accuracy.
+The Rademacher complexity \citep{bartlett2002rademacher} measures the expressiveness of a function class $F$ by its ability to shatter, or fit, noise.
+They are data-dependent measures, and are thus particularly well suited to learning tasks where generalisation ability is vital, since complexity penalties that are not data dependent cannot be universally effective \citep{kearns1997experimental}.
+
+	We begin by defining a loss function as a measure for the generalisation error.
+For decision functions of the form $\bvec{f} : \mathcal{X} \to \mathcal{A} = \mathbb{R}^{m}$ where entries of $f$ are interpreted as probabilities, we employ the cross entropy loss,
+	\begin{equation}
+		\mathcal{L}_{\epsilon}(y, \bvec{f}(x)) := - \log{ [\bvec{y}^{T} \bvec{f}(x)]_{\epsilon}^{1} } = - \log{ [f_{y}(x)]_{\epsilon}^{1} },
+	\label{eq:cross_entropy_loss_copy}
+	\end{equation}
+	to express classification risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$.
+Under this loss, we prove that the expected risk for the kernel embedding classifier $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a Rademacher complexity bound $r(\theta, \lambda)$ with high probability.
+We refer the reader to the supplementary material for detailed proof.
+
+	\begin{theorem}[Expected Risk Bound for KEC Hyperparameter Learning]
+		\label{thm:expected_risk_bound_hyperparameter_learning_copy}
+
+		For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$ used to define $\bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector}, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $\theta \in \Theta$, $\lambda \in \Lambda$, and $\epsilon \in (0, e^{-1})$ satisfies
+		\begin{equation}
+			\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e r(\theta, \lambda) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
+		\label{eq:expected_risk_bound_hyperparameter_learning_copy}
+		\end{equation}
+		where $r(\theta, \lambda) := \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} K_{\theta} (K_{\theta} + n \lambda I)^{-1} \bvec{Y}\bigg) \sup_{x \in \mathcal{X}} k_{\theta}(x, x)}$.
+	\end{theorem}
 
@@
 
-	\subsection{Batch Stochastic Gradient Descent}
-	\label{sec:stochastic_gradient_descent}
-
-		With standard gradient descent, the time complexity of each training iteration is dominated by the Cholesky decomposition of the regularised gram matrix $K_{\theta} + n \lambda I$ of size $n \times n$, which has a time complexity of $O(n^{3})$.
-In order to scale the hyperparameter training of kernel embedding classifiers to large datasets, we propose to optimise the objective \eqref{eq:objective} with stochastic gradient descent.
-
-		We begin by selecting a mini-batch size $n_{b} << n$ that is much smaller than $n$.
-At each training iteration, we sample a mini-batch of size $n_{b}$ from the full dataset.
-The objective \eqref{eq:objective} and its gradients with respect to the hyperparameters are then computed only for the mini-batch.
-This stochastic gradient is then used to make hyperparameter updates in that training iteration.
-This continues until the magnitude of the stochastic gradients fall below a certain range.
-This training algorithm is presented in \cref{alg:kernel_embedding_classifier_training}.
-This implementation also generalises the gradient descent approach, where $n_{b} = n$ so that $\mathcal{I} = \mathbb{N}_{n}$ and the full dataset is used to compute the gradients.
-
-		\note{Justify with the bound after discussing with Richard}
+	In order for the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} to be non-trivial, we focus on bounded kernels in the sense that $\alpha^{2}(\theta) := \sup_{x \in \mathcal{X}} k_{\theta}(x, x) < \infty$.
+For example, Gaussian kernels $k_{\theta}(x, x') = \sigma_{f}^{2} \exp{( - \frac{1}{2}(x - x') \Sigma^{-1} (x - x') )}$ and similar stationary kernels such as the Mat\'{e}rn family with sensitivity and length scales $\theta = (\sigma_{f}, \Sigma)$ have $\alpha(\theta) = \sigma_{f}$.
+For non-stationary kernels such as the linear or polynomial kernels, the domain $\mathcal{X}$ is assumed to be compact and thus can be rescaled so that $\alpha(\theta) = 1$.
+Since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} is true with probability $1 - \beta$ when the random variables $X_{i}, Y_{i}$ are realised as the training observations $x_{i}, y_{i}$.
+We therefore employ this upper bound as the hyperparameter learning objective,
+	\begin{equation}
+		q(\theta, \lambda) := \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(y_{i}, \bvec{f}_{\theta, \lambda}(x_{i})) + 4 e r(\theta, \lambda).
+	\label{eq:learning_objective}
+	\end{equation}
+	We employ gradient based optimisers such as Gradient descent or Adam \citep{kingma2014adam}.
+Since \cref{thm:expected_risk_bound_hyperparameter_learning_copy} holds for any $n \in \mathbb{N}_{+}$ and any set of training data $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with the trade-off of relaxing the bound tightness through $\sqrt{8 \log{(2 / \beta)} / n}$, the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} also holds with high probability for a batch subset of the training data.
+This enables scalable kernel learning through batch stochastic gradient updates, where each gradient update stochastically attempts to minimise a different upper bound of the generalisation risk.
+Because this upper bound holds with high probability over \textit{iid} samples, through randomly selecting the \textit{iid} samples used to compute the upper bound, with the same high probability the resulting stochastic gradient will attempt to minimise a strict upper bound.
+We present this scalable kernel learning via batch stochastic gradient updates in \cref{alg:kernel_embedding_classifier_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size.
+
+	NEED TO SHOW VISUALISATIONS OF SPIRAL HERE AND DISCUSS TWO INITIALISATIONS: ONE OVERFITTING AND ONE UNDERFITTING, AND SHOW THAT OUR TRAINING ALGORITHM FINDS A BALANCE FROM BOTH INITIAL SETTINGS.
+
+	ALSO SHOW REVERSE EMBEDDING RESULTS
+
+	\textbf{Neural Network Kernels.} DISCUSSION NOT DONE
+
+\section{Related Work}
+\label{sec:related_work}
+
+	For a linear class of predictors parametrised as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularisation to bound the Rademacher complexity, achieving tight generalisation bounds in the context of multi-label learning.
+The KEC predictor \eqref{eq:empirical_decision_probability_vector} has the same linear form in the feature space, $\bvec{f}_{\theta, \lambda}(x) = \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \Phi_{\theta}^{T} \phi_{\theta}(x) = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$, where instead of learning the operator $W^{T}$ directory, we learn hyperparameters $\theta \in \Theta, \lambda \in \Lambda$ for the empirical conditional embedding map $\mathcal{U}^{(\theta, \lambda)}_{Y | X}$ to learn the features $\phi_{\theta}(x)$.
+\cite{xu2016local} extends the trace norm regularisation approach by considering the local Rademacher complexity on a subset of the predictor class, where they instead minimise the tail sum of the predictor singular values.
+In the proof of \cref{thm:expected_risk_bound_hyperparameter_learning_copy}, $\theta \in \Theta$ and $\lambda \in \Lambda$ define subsets of $\Theta$ and $\Lambda$ where the Rademacher complexity is considered over.
+By minimising $q(\theta, \lambda)$, we shrink the subset being considered, achieving localised Rademacher complexity based feature learning without selecting parameters that define the tail sum.
+Local Rademacher complexity has also been employed for multiple kernel learning \citep{kloft2011local, cortes2013learning} to learn convex combinations of simpler kernels for a support vector machine.
+We extend its application to the probabilistic multiclass case, and use Rademacher complexity based risk bounds to learn the hyperparameters of a conditional kernel embedding.
+
+	DISCUSSION NOT DONE
 
 \section{Experiments}
-
-	We will also open-source the code on GitHub.
-All the core algorithms presented in this paper will be available and implemented in TensorFlow \citep{abadi2016tensorflow}, while having the same API as \texttt{scikit-learn} models so that it is straightforward to use.
+\label{sec:experiments}
+
+	We demonstrate the average performance of learning anisotropic Gaussian kernels and fully connected neural network kernels under the kernel embedding classification framework on standard UCI datasets, summarised in \cref{tab:stationary_experiments}.
+The former has a shallow but wide model architecture, while the latter has a deeper but narrower model architecture.
+
+	The Gaussian kernel is learned through both the original gradient update (GKEC) and the scalable batch stochastic gradient update (GKEC-SGD) using a tenth ($n_{b} \approx \frac{n}{10}$) of the training set each time, with sensitivity and length scales initialised to $1$.
+For neural network kernels, we randomly select two simple fully connected architectures with 16-32-8 (NNKEC-1) and 96-32 (NNKEC-2) hidden units respectively, and learn the corresponding kernel without dropout under ReLU activation.
+Weight parameters are initialised from a truncated normal distribution with standard deviation $0.1$, while biases are initialised to $0.1$, and are to be trained with full gradient updates.
+For all experiments, regularisation parameter $\lambda$ is initialised to $1$ and is learned jointly with the kernel.
+Classifiers are trained with the Adam optimiser \citep{kingma2014adam} in TensorFlow \citep{abadi2016tensorflow} with a learning rate of $\eta = 0.1$ and $\epsilon = 10^{-15}$ for learning objective $q(\theta, \lambda)$.
+Training is ran for 1000 or 10000 iterations when using full or batch stochastic gradient updates respectively, regardless of training convergence.
+All datasets are scaled so that all dimensions are in the unit range.
+Each classifier is trained on 9 out of 10 folds and tested on the remaining fold.
+The folds are shuffled over all 10 combinations to obtain the average test accuracy.
+We also provide typical performance on the dataset using other approaches.
+See supplementary material for details.
+These numbers are only illustrative, however, in that other work may have used different data pre-processing, folds, or longer training time.
+
+	- \texttt{banknote}: ANN: 99.78 \citep{kaya2016banknote} \\
+	- \texttt{ecoli}: Probabilistic Binary Tree: 81.1 \citep{horton1996probabilistic} \\
+	- \texttt{robot}: ANN: 97.6 \citep{freire2009short} \\
+	- \texttt{segment}: Decision Trees \& Neural Nets: 99.14 - 99.98 \citep{lim2000comparison} \\
+	- \texttt{wine}: RDA: 100, QDA: 99.4, LDA: 98.9, 1NN: 96.1 \citep{aeberhard1992comparison} \\
+	- \texttt{yeast}: Probabilistic Binary Tree: 55.0 \citep{horton1996probabilistic} \\
+
+	STILL HAS TO ADD CONVOLUTIONAL KERNEL MNIST STUFF WHICH ACHIEVED 99.5\% TEST ACCURACY WITH SGD
+
+	ALSO SHOW REVERSE EMBEDDING RESULTS TO OBTAIN THE CLASS MODES
+
+	DISCUSSION NOT DONE 
+%	\begin{table}[t]
+%		\begin{center}
+%			\begin{tabular}{ l | c | c }
+%				\hline
+%				\multicolumn{3}{ c }{Classification Accuracy on UCI Datasets} \\
+%				\hline
+%				\hline				
+%				Dataset \hspace{\fill} $(n, d, m)$ & Method & Test Accuracy \\
+%				\hline
+%				\hline
+%				\texttt{banknote} & Gaussian KEC & $99.93 \pm 0.22$ \\
+%				(1372, 4, 2) & Gaussian KEC (SGD 124) & $98.83 \pm 0.88$ \\
+%				& Neural KEC (16, 32, 8) & $99.49 \pm 1.03$ \\
+%				& Neural KEC (96, 32) & $99.42 \pm 0.91$ \\
+%				\hline
+%				\texttt{ecoli} & Gaussian KEC & $87.50 \pm 4.36$ \\
+%				(336, 7, 8) & Gaussian KEC (SGD 30) & $84.50 \pm 5.02$ \\
+%				& Neural KEC (16, 32, 8) & $87.49 \pm 3.24$ \\
+%				& Neural KEC (96, 32) & $86.32 \pm 5.98$ \\
+%				\hline
+%				\texttt{robot} & Gaussian KEC & \\
+%				(5456, 24, 4) & Gaussian KEC (SGD 491) & $95.45 \pm 0.86$ \\
+%				& Neural KEC (16, 32, 8) & $82.31 \pm 7.11$ \\	
+%%				\texttt{robot} \hspace{\fill} (5456, 24, 4) & Neural KEC (96, 32) & $92.25 \pm 1.39$ \\	
+%				& Neural KEC (96, 32) & $94.50 \pm 0.75$ \\
+%				\hline
+%				\texttt{segment} & Gaussian KEC & \\
+%				(2310, 19, 7) & Gaussian KEC (SGD 208) & $96.10 \pm 1.46$ \\
+%				& Neural KEC (16, 32, 8) & $94.59 \pm 1.62$ \\
+%				& Neural KEC (96, 32) & $96.71 \pm 1.06$ \\
+%				\hline
+%				\texttt{wine} & Gaussian KEC & $97.22 \pm 3.73$ \\
+%				(178, 13, 3) & Gaussian KEC (SGD 16) & $93.27 \pm 6.04$ \\
+%				& Neural KEC (16, 32, 8) & $96.11 \pm 5.00$\\
+%				& Neural KEC (96, 32) & $97.22 \pm 5.12$ \\
+%				\hline
+%				\texttt{yeast} & Gaussian KEC & $52.49 \pm 2.06$ \\
+%				(1484, 8, 10) & Gaussian KEC (SGD 134) & $60.30 \pm 4.39$ \\
+%				& Neural KEC (16, 32, 8) & $55.80 \pm 4.96$ \\
+%				& Neural KEC (96, 32) & $59.57 \pm 3.98 $ \\
+%				\hline
+%				\hline
+%			\end{tabular}
+%		\end{center}
+%		\caption{Classification accuracy of two kernel embedding classification architectures on standard UCI Datasets.
+Numbers after ``SGD'' indicates the batch size used.
+Numbers after ``Neural KEC'' indicates the size of the hidden layers, starting from the first.}
+%		\label{tab:stationary_experiments_old}
+%	\end{table}
 
 	\begin{table}[t]
-		\begin{center}
-			\begin{tabular}{ l l || c || c c || c }
-				\hline
-				\multicolumn{6}{ c }{Classification Accuracy on UCI Datasets} \\
-				\hline
-				\hline
-%				& & & \multicolumn{2}{ c }{Accuracy} & \\
-%				\hline				
-				Dataset & & Method & Train & Test & Test (Literature) \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 1372$ & CE + RC & 99.59 & 100 & Artificial Neural Network: 99.78 \\
-				\texttt{banknote} & $d = 4$ & CE & 99.59 & 100 & \citep{kaya2016banknote} \\
-				& $m = 2$ & RC & 99.59 & 100 &  \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 336$ & CE + RC & 92.05 & 91.18 & Probabilistic Binary Tree: 81.1 \\
-				\texttt{ecoli} & $d = 7$ & CE & 94.04 & 85.29 & \citep{horton1996probabilistic} \\
-				& $m = 8$ & RC & 91.05 & 88.24 &  \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 150$ & CE + RC & 97.78 & 100 & SVM: 94.67 \\
-				\texttt{iris} & $d = 4$ & CE & 97.04 & 100 & \citep{koggalage2004reducing}\\
-				& $m = 3$ & RC & 97.78 & 100 & ANN: 83.33 \citep{swain2012approach} \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 7797$ & CE + RC &   &   & \\
-				\texttt{isolet} & $d = 617$ & CE &   &   & \\
-				& $m = 26$ & RC &   &   &  \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 2310$ & CE + RC & 99.37 & 97.40 & Decision Trees \& Neural Nets: \\
-				\texttt{segment} & $d = 19$ & CE & 97.84 & 96.97 &  99.14 - 99.98 \\
-				& $m = 7$ & RC & 97.35 & 96.10 & \citep{lim2000comparison} \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 178$ & CE + RC & 100 & 100 & RDA: 100, QDA: 99.4, \\
-				\texttt{wine} & $d = 13$ & CE & 100 & 100 & LDA: 98.9, 1NN: 96.1 \\
-				& $m = 3$ & RC & 100 & 100 & \citep{aeberhard1992comparison} \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 6497$ & CE + RC & & & \\
-				\texttt{wine-quality} & $d = 12$ & CE & & & \\
-				& $m = 2$ & RC & & &  \\
-				\hline
-				\hline
-				\multirow{6}{*}{}
-				& $n = 1484$ & CE + RC & 67.04 & 57.72 & Probabilistic Binary Tree: 55.0 \\
-				\texttt{yeast} & $d = 8$ & CE & 68.24 & 56.38 & \citep{horton1996probabilistic} \\
-				& $m = 10$ & RC & 62.25 & 56.38 &  \\
-				\hline
-				\hline
+		\caption{Classification accuracy of Gaussian and Neural Network KEC on UCI datasets}
+		\label{tab:stationary_experiments}
+		\centering
+		\begin{tabular}{lccccc}			
+			Dataset \hspace{\fill} $(n, d, m)$ & GKEC & GKEC-SGD & NNKEC-1 & NNKEC-2 & Others \\
+			\midrule
+			\texttt{banknote} \hspace{\fill} (1372, 4, 2) & $99.9 \pm 0.2$ & $98.8 \pm 0.9$ & $99.5 \pm 1.0$ & $99.4 \pm 0.9$ & 99.78 \\
+			\texttt{ecoli} \hspace{\fill} (336, 7, 8) & $87.5 \pm 4.4$ & $84.5 \pm 5.0$ & $87.5 \pm 3.2$ & $86.3 \pm 6.0$ & 81.1 \\
+			\texttt{robot} \hspace{\fill} (5456, 24, 4) & $97.8$ & $95.5 \pm 0.9$ & $82.3 \pm 7.1$ & $94.5 \pm 0.8$ & 97.59 \\
+			\texttt{segment} \hspace{\fill} (2310, 19, 7) & $98.4 \pm 0.8$ & $96.1 \pm 1.5$ & $94.6 \pm 1.6$ & $96.7 \pm 1.1$ & 99.14 \\
+			\texttt{wine} \hspace{\fill} (178, 13, 3) & $97.2 \pm 3.7$ & $93.3 \pm 6.0$ & $96.1 \pm 5.0$ & $97.2 \pm 5.1$ & 98.9 \\
+			\texttt{yeast} \hspace{\fill} (1484, 8, 10) & $52.5 \pm 2.1$ & $60.3 \pm 4.4$ & $55.8 \pm 5.0$ & $59.6 \pm 4.0$ & 55.0 \\
 		\end{tabular}
-		\end{center}
-		\caption{Classification Accuracy of the Kernel Embedding Classifier on standard UCI Datasets.}
-		\label{tab:experiments}
 	\end{table}

### 2017-09-19 old/kernel_embedding_classifier.tex
Add folder 'old'

--- 2017-05-10 kernel_embedding_classifier.tex
@@
 \begin{abstract}
+
 	We propose learning-theoretic bounds for learning the hyperparameters of kernel embeddings in the probabilistic multiclass classification context.
@@
 
+\section{Introduction}
+\label{sec:introduction}
+
+	Kernel embeddings are a principled way to represent probability distributions in a nonparametric setting.
+They transform probability distributions into mean embeddings within a reproducing kernel Hilbert space (RKHS), and represent embeddings directly from data without assuming a parametric form.
+
+	Within the kernel embedding framework, hyperparameters has been notoriously difficult to tune, and its learning is usually only restricted to heuristics or methods such as cross validation which requires pre-selecting the number of folds and the split of the folds.
+In this paper, we take a learning theoretic approach to learn the hyperparameters of a conditional kernel embedding in a supervised manner.
+
+	learning theoretic (be specific and mention PAC)
+	(complexity penalty terms that are not data dependent cannot be universally effective) \citep{kearns1997experimental}
+
 - We address the need for a principled way of obtaining probabilistic outputs from a multiclass classifier.
@@
 Data dependent risk bounds
-
-\section{Introduction}
-\label{sec:introduction}
-
-	Kernel embeddings are a principled way to represent probability distributions in a nonparametric setting.
-
-	learning theoretic (be specific and mention PAC)
-	(complexity penalty terms that are not data dependent cannot be universally effective) \citep{kearns1997experimental}
 
@@
 
-	In the kernel embedding literature, hyperparameters has been notoriously difficult to tune, and its learning is usually only restricted to heuristics or methods such as cross validation which requires pre-selecting the number of folds and the split of the folds.
-In this paper, we take a learning theoretic approach to learn the hyperparameters of the KEC, inspired by the original training procedure of support vector classifiers (SVC) as described by \cite[p.
+	inspired by the original training procedure of support vector classifiers (SVC) as described by \cite[p.
 185]{m2001introduction}.

### 2017-09-19 reviews/reviews_response.txt
Add folder 'reviews'

Reviewer 1: Clear rejection, The reviewer is confident but not absolutely certain that the evaluation is correct

Summary

The paper applies conditional mean embeddings to multi-class classification and provides rates of convergence under restrictive assumptions and a result about Rademacher complexities.

Review

It appears to me that the authors apply essentially ridge-regression to a classification task and interpret the probability of the regressor as the probability that covariate x falls into class i. Theorem 3.1 is then not surprising and, in fact, standard results for ridge regression should give stronger results than what the authors get (in particular, the condition k(x,cdot) in the image of C_XX should be unnecessary and optimal schedules for lambda are known depending on the eigenvalue decay of the kernel). There exists also a close relation to vector-valued RKHSs and corresponding regression. Furthermore, the use of Rademacher complexities is common in regression and it seems to me that the authors completely ignored the link to standard ridge regression. At the very least there should be lengthy paragraph explaining why this differs from ridge regression and why standard results can’t be applied, but the word “ridge” doesn’t even appear in the paper.

I can’t see much novelty in the paper given the vast ridge regression literature and in my opinion the authors need to compare their results to what is known about ridge regression or explain why ridge regression results are not applicable in this setting.

Detailed Comments

Section 2

Be more precise about the objects. C_XX and C_YX as defined are elements in the tensor space. For U_{Y|X} you identify these with linear operators, i.e. there is an isomorphic and (I guess) isometric map between the tensor element and the linear operators. A line explaining how properties of the kernel translate into properties of these operators might also be helpful, e.g. when are the operators compact.
You define U_{Y|X} as C_YX C_XX^-1 but are then later talking about approximating U_{Y|X} by C_{YX}C_{XX}^-1. You should define U_{Y|X} without referring to C_{YX} etc. and then explain that in certain cases they coincide and in other cases they only approximate U_{Y|X}.

- Yes, C_{XX} and C_{YX} are tensors. We agree and would definitely like to expand on the details more. However, being a background section, most of the definitions and descriptions are provided by the papers cited, specifically, Song et. al. (2009).
- Yes, ideally U_{Y|X} should be defined without referring to C_{YX} and C_{XX}. More precisely, U_{Y|X} is defined as the operator U such that \mu_{Y | X = x} = U k(x, \cdot), and the definition we used is then really a direct consequence that can be derived. However, because C_{YX}C_{XX}^-1 is the unique solution to the operator U described here, it is common to simply use this as the definition instead, as seen in Definition 3 in Song et. al. (2009).

Section 3
H_delta can be identified with R^m and the Euclidean norm

- Yes, that is exactly right, which makes the mathematics very convenient

P(Y=y|X=x) needs a clarification. Is X a finite space? Or do you have some form of density assumption (not sure how this would look like)?

- The beauty here is that there are little restrictions to the input space X, as long as you can define a kernel k over that space. There are no density assumptions. The only catch is for the next section, since we use (batch stochastic) gradient descent to learn the kernel hyperparameters with our proposed objective, we require that the kernel to be differentiable with respect to the hyperparameters. This was implicit and not stated explicitly. We will state this explicitly in our next iteration of the paper.

Reviewer 2: Ok but not good enough - rejection, The reviewer is confident but not absolutely certain that the evaluation is correct

This paper deals with supervised classification within the framework of kernel embeddings of probability distributions. Specifically, the authors propose a kernel embedding classifier based on the Hilbert space embedding of conditional distributions. They also provide a risk bound using the notion of Rademacher complexity. This bound was used to derive a way to learn the hyperparameter of the kernel function. Experiments to assess the performance of the proposed classifier on a toy example, UCI data sets and MNIST are provided.

The subject matter of the paper is of importance, since the proper modeling of the kernel hyperparameter is crucial for kernel methods and in particular for the kernel embedding of probability distribution. Unfortunately the contribution of the paper compared to what is known in the literature is not clear. My foremost concerns are the following:

1) Section 3 describes the proposed Kernel embedding classifier. This is exactly kernel ridge regression (or regularized least squares classification). The connection between the kernel embedding of conditional distribution and ridge regression was established in [Grunewalder & al., Conditional mean embeddings as regressors. ICML 2012]. They showed the connection between the two formalisms using the framework of vector-valued function learning. Eq. 6 can be seen as a particular case of this framework.

- Grunewalder et. al. showed that the conditional embedding is the solution to a vector-valued ridged regression problem. Since eq. 6 is indeed a conditional embedding, it is thus also the solution to a particular vector-valued ridged regression problem. This is not the contribution of our Section 3. Our contribution is to simply establish that as this particular condition embedding, eq. 6., is a consistent estimate of the decision probabilities. Furthermore, instead of using cross validation to learn the hyperparameters like they do in Grunewalder et. al., we use a Rademacher complexity based bound to perform the learning.

2) In Section 4, it will be more easy to follow and understand the results by adding more materials about the bound of the Rademacher complexity which will allow the result of Theorem 4.1. The excess risk bound for learning with trace norm regularization was studied in [Maurer & Pontil, COLT 2013]. Contribution of this section compared to this work should be clearly mentioned.

- This is all stated in the appendix

3) The question of the kernel choice over a class of kernels (such as Gaussian kernels parameterized by their bandwidth) in the framework of RKHS embedding of distribution was studied in [Sriperumbudur & al., Kernel choice and classifiability for RKHS embeddings of probability distributions. NIPS 2009]. Multiple kernel learning with kernel embedding was also considered in [Gretton & al., Optimal kernel choice for large-scale two sample tests. NIPS 2012]. The authors should add more information about previous work on this topic so that their results can be understood with respect to previous studies.

Reviewer 3: Ok but not good enough - rejection, The reviewer is confident but not absolutely certain that the evaluation is correct

== A summary of the review ==

In my opinion, the theoretical contributions are not good enough:

i) The connection to conditional mean embeddings seems to be rather superficial. This is because the proposed estimator can be easily derived from the fact that the conditional expectation of a class indicator provides a conditional class probability.

ii) Theoretical results in Theorems 3.1 and 4.1 are not strong enough, as I explain below.

Also the experiments are not thorough enough, as mentioned below. From these reasons, I do not think that this paper is good enough for this NIPS, while the proposed method looks promising.

== Detailed comments ==

- Theorem 3.1:

The assumption that $k(x,\cdot)$ is included in the image of the covariance operator is too strong. This is because it essentially requires that the delta function is in the RKHS: this is always invalid, if the kernel is continuous. Maybe it would be better not to rely on the result by Song et al. (2009). Instead you may use the results obtained in the following papers (or other better results by Le Song):

Grunewalder et al, "Conditional mean embeddings as regressors", 
ICML 2012

A Caponnetto, E De Vito 
"Optimal rates for the regularized least-squares algorithm" 
Foundations of Computational Mathematics 7 (3), 331-368, 2007

- Theorem 4.1:

I understand that this result gives a motivation for using Eq.(10) as an objective of hyper-parameter learning. But Theorem 4.1 does not guarantee that the resulting estimate (i.e. with learned hyper-parameters) converges to the best estimator in the hypothesis class (as the sample size goes to infinity). In this sense, Theorem 4.1 is not a strong theoretical contribution.

- Algorithm 1:

Are the gradients of Eq.(10) obtainable? It seems that the loss function in Eq.(8) is not differentiable, as it involves clipping.

- Experiments:

i) In Table 1, does "Others" mean that the best performance among the other competitors is reported? Or did you take these results from the cited papers?

ii) There should be comparisons with existing kernel learning methods such as multiple kernel learning. Also it would be possible to compare with support vector classifiers with hyper-parameters chosen via cross-validation.

iii) The sizes of training data in the experiments are relatively small. It is questionable whether the proposed can be applied to large scale problems.

### 2017-10-02 AISTATS2018/cake_aistats2018.tex
Revised abstract and introduction

--- 2017-08-01 cake.tex
@@
-\documentclass{article}
+\documentclass[twoside]{article}
+\usepackage{aistats2018}
+% If your paper is accepted, change the options for the package
+% aistats2018 as follows:
+%
+%\usepackage[accepted]{aistats2018}
+%
+% This option will print headings for the title of your paper and
+% headings for the authors names, plus a copyright note at the end of
+% the first column of the first page.
 
-% if you need to pass options to natbib, use, e.g.:
-% \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading nips_2017
-%
-% to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{nips_2017}
+\bibliographystyle{apalike}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography
+\usepackage[square, authoryear, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
 
-\usepackage{nips_2017}
-
-% to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[final]{nips_2017}
-
+\usepackage{glossaries}
+\usepackage{acronym}
 \usepackage[utf8]{inputenc} % allow utf-8 input
@@
 
+\newacronym{CME}{CME}{conditional mean embedding}
+\newacronym{MCE}{MCE}{multiclass conditional embedding}
+\newacronym{CEN}{CEN}{conditional embedding network}
+\newacronym{RKHS}{RKHS}{reproducing kernel Hilbert space}
+\newacronym{SVM}{SVM}{support vector machine}
+\newacronym{SVC}{SVC}{support vector classifier}
+\newacronym{GP}{GP}{Gaussian process}
+\newacronym{GPs}{GPs}{Gaussian processes}
+\newacronym{GPC}{GPC}{Gaussian process classifier}
+\newacronym{KRR}{KRR}{kernel ridged regression}
+\newacronym{RLSC}{RLSC}{regularized least squares classification}
+\newacronym{ERM}{ERM}{empirical risk minimization}
+
 %\usepackage{varioref}
@@
 
-\title{CAKE: Classification \textit{avec} Kernel Embeddings \\ using Rademacher Complexity Bounds}
-
-\author{
-}
-
 \begin{document}
 
-\maketitle
+	\twocolumn[
+
+	\aistatstitle{Hyperparameter Learning for Multiclass Conditional Embeddings \\ with Rademacher Complexity Bounds}
+
+	\aistatsauthor{ Anonymous Author 1 \And Anonymous Author 2 \And Anonymous Author 3 }
+
+	\aistatsaddress{ Unknown Institution 1 \And Unknown Institution 2 \And Unknown Institution 3 } ]
 
 	\begin{abstract}
-	We propose learning-theoretic bounds for hyperparameter learning of conditional kernel embeddings in the probabilistic multiclass classification context.
+
+		% The goal is to motivate the problem here and outline our contribution in response 
+		How can we design a scalable learning objective for learning kernel hyperparameters of conditional mean embeddings?
+Conditional mean embeddings are nonparametric models that encodes conditional distributions in a reproducing kernel Hilbert space (RKHS) directly through observed data, resulting in a flexible and powerful framework for probabilistic inference.
+However, their performance is greatly dependent on the choice of kernel hyperparameters and regularization, yet current approaches for hyperparameter tuning predominantly rely on cross validation and distance based heuristics.
+For conditional mean embeddings with multiclass targets but arbitrary inputs, we propose a hyperparameter learning framework based on Rademacher complexity bounds to prevent overfitting by balancing datafit against model complexity.
+The approach only requires batch updates, allowing scalable kernel learning without kernel approximations.
+Experiments demonstrate that our framework outperforms standard cross validation and heuristics, and can be further extended to incorporate and learn neural network weights with improved accuracy.
+
+		%	We benchmark our learning algorithm with standard UCI datasets, as well as to learn features of a convolutional neural network with improved accuracy, demonstrating the generality of this approach.
+
+		%	ORIGINAL:
+		%	We propose learning-theoretic bounds for hyperparameter learning of conditional kernel embeddings for estimating multiclass probabilities.
 Kernel embeddings are nonparametric methods to represent probability distributions directly through observed data in a reproducing kernel Hilbert space (RKHS).
-This property forms the core of modern kernel methods, yet hyperparameter learning for kernel embeddings remains challenging, often relying on heuristics and domain expertise.
-We begin by developing the kernel embedding classifier (KEC), and prove its stochastic convergence for probabilistic inference.
+We consider an estimator for multiclass probabilities based on the conditional embedding, with proven stochastic convergence.
 We then prove that its expected classification error can be bounded with high probability using Rademacher complexity bounds.
@@
 
-	Kernel embeddings are principled methods to represent probability distributions in a nonparametric setting.
+	% Can still motivate with standard KE
+
+	% How does it compare with cross val? Note that cross val can't exactly scale
+
+	% Cross validation, whose performance varies largely with the folds chosen.
+It also requires multiple models to be fitted during learning, increasing the computational demand.
+The computational demand is at least $O(n^3)$ and can be $O(n^4)$ in the extreme case of leave-one-out cross validation.
+
+	% Median length heuristic, while faster, often produces ill-fitted models, as it is unable to leverage the supervision from labels, and its appication are restricted to length scale type parameters.
+
+	% Can we formulate a learning objective that resembles the marginal likelihood for conditional mean embeddings?
+
+	% Paragraph: Introducing nonparametric kernel based models, and CME is one of them
+
+	% Paragraph: Immediately start by motivating why conditional mean embeddings and kernel embeddings are useful in general
+
+	\Glspl{CME} are attractive because they encode conditional expectations in a \gls{RKHS}, bypassing the need for a parametrised density \citep{song2013kernel}.
+They are part of a broader class of models known as kernel embeddings, where nonparametric probabilistic inference can be carried out entirely within the \gls{RKHS} because difficult marginalization integrals become simple linear algebra \citep{muandet2016kernel}.
+This very general framework is core to modern kernel probabilistic methods, including kernel two-sample testing \citep{gretton2007kernel}, kernel Bayesian inference  \citep{fukumizu2013kernel}, nonparametric density estimation \citep{song2008tailoring, kanagawa2014recovering}, domain-invariant component analysis \citep{muandet2013domain}, dimensionality reduction \citep{fukumizu2004dimensionality}, feature discovery \citep{jitkrittum2016interpretable}, and state space filtering \citep{kanagawa2016filtering}.
+
+	% Paragraph: What are MCEs? Why do MCEs matter?
+
+	% % In this paper, we focus on a rarely investigated form of the CME...
+	\Glspl{MCE} are \glspl{CME} with discrete targets but arbitrary inputs, where on top of conditional expectations we can further infer conditional probabilities.
+As such, they are widely applicable to probabilistic inference in multiclass settings and learning probabilistic mappings between arbitrary inputs and a discrete set of actions or outcomes.
+Unlike \glspl{SVM} \citep{scholkopf2002learning}, \glspl{GPC} \citep{rasmussen2006gaussian}, and multiclass \glspl{RLSC} \citep{rifkin2003regularized, pahikkala2012unsupervised}, \Glspl{MCE} do not require fitting separate binary classifiers for each class or each pair of classes for a final multiclass prediction.
+Instead, a single conditional embedding is sufficient for producing consistent probabilistic estimates from \glspl{MCE}.
+
+	% Paragraph: Why do we want to learn their hyperparameters?
+
+	Nevertheless, like most kernel based models, their performance is highly dependent on the hyperparameters chosen.
+In these settings, the model selection process usually begins by selecting a kernel, whose parameters become part of the model hyperparameters, which may further include noise or regularisation parameters.
+Given a set of hyperparameters, training boils down to solving either a convex optimization problem, e.g.
+\glspl{SVM}, or a linear set of equations, e.g.
+\glspl{GPC}, \glspl{RLSC}, and \glspl{CME}.
+Unfortunately, kernel hyperparameter tuning is not straight forward, and various forms of cross validation \citep{song2013kernel} or heuristics such as the median length heuristic \citep{muandet2016kernel} remain as the primary approaches for this task.
+
+	% Paragraph: Success story of GPs to motivate what we want
+
+	One notable success story in this domain are \gls{GPs} \citep{rasmussen2006gaussian}, which has long enjoyed the well celebrated marginal likelihood for continuous hyperparameter learning.
+The marginal likelihood arises naturally from the Bayesian formulation of the model, and exhibits certain desirable properties -- in particular, the ability to automatically balance between data fit and model complexity.
+On the other hand, \glspl{CME} are not necessarily Bayesian, and hence they do not benefit from a natural marginal likelihood formulation, yet such a balance is critical when generalising the model beyond unseen examples.
+
+	% Paragraph: Contribution
+
+	Can we formulate a learning objective for \glspl{MCE} that resembles the marginal likelihood of \gls{GPs} to balance data fit and model complexity?
+In this paper, we present such a learning objective as our main contribution.
+In particular, we 1) derive a measure of model complexity for a specific \gls{MCE} based on the Rademacher complexity of a relevant class of \glspl{MCE}, 2) formulate a novel learning objective based on this complexity measure to achieve the balance between data fit and model complexity, and 3) propose a scalable hyperparameter learning algorithm under this objective using batch updates.
+We show that this learning objective produces \glspl{MCE} that generalises better than that learned from cross validation, \gls{ERM}, and median length heuristics on standard benchmarks, and apply such an algorithm to incorporate and learn neural network weights with improved accuracy on the MNIST dataset.
+Finally, we also discuss some variations to the \glspl{MCE} model.
+
+		% Contributions:
+		% - Derived an upper bound for the expected risk?
+		% - Show proof of shrinkage?
+		% - 
+		% - Proposed a scalable learning objective for learning kernel hyperparameters and regularization of the conditional mean embedding
+		% - Proposed a scalable inference framework using neural networks
+
+	\gls{KRR} \citep{friedman2001elements}
+
+	- Difference between both \citep{rifkin2003regularized} and \citep{pahikkala2012unsupervised} is the loss function used and natural multiclass formulation and what we are optimising over (not the weights directly but the hyperparameter of the weights).
+	- 
+	%	Kernel embeddings are principled methods to represent probability distributions in a nonparametric setting \citep{song2013kernel}.
 By transforming distributions into mean embeddings within a reproducing kernel Hilbert space (RKHS), distributions can be represented directly from data without assuming a parametric structure \citep{song2013kernel}.
-Consequently, nonparametric probabilistic inference can be carried out entirely within the RKHS, where difficult marginalisation integrals become simple linear algebra \citep{muandet2016kernel}.
-This very general and powerful technique is core to modern kernel methods, including support vector machines \citep{scholkopf2002learning}, kernel two-sample testing \citep{gretton2007kernel}, kernel Bayesian inference  \citep{fukumizu2013kernel}, nonparametric density estimation \citep{song2008tailoring, kanagawa2014recovering}, domain-invariant component analysis \citep{muandet2013domain}, dimensionality reduction \citep{fukumizu2004dimensionality}, feature discovery via hypothesis testing \citep{jitkrittum2016interpretable}, and filtering \citep{kanagawa2016filtering}.
+Consequently, nonparametric probabilistic inference can be carried out entirely within the RKHS, where difficult marginalization integrals become simple linear algebra \citep{muandet2016kernel}.
+
+	%	This very general and powerful technique is core to modern kernel methods, including support vector machines \citep{scholkopf2002learning}, kernel two-sample testing \citep{gretton2007kernel}, kernel Bayesian inference  \citep{fukumizu2013kernel}, nonparametric density estimation \citep{song2008tailoring, kanagawa2014recovering}, domain-invariant component analysis \citep{muandet2013domain}, dimensionality reduction \citep{fukumizu2004dimensionality}, feature discovery via hypothesis testing \citep{jitkrittum2016interpretable}, and filtering \citep{kanagawa2016filtering}.
 The problem of estimating the kernel mean in a reproducing kernel Hilbert space (RKHS) is thus central to kernel methods.
-
-	Positive definite symmetric kernels $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ are the soul of kernel methods, where they provide a coherent sense of similarity between two elements of the same space through implicitly defining higher dimensional features.
+	%	
+	%	Positive definite symmetric kernels $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ are the soul of kernel methods, where they provide a coherent sense of similarity between two elements of the same space through implicitly defining higher dimensional features.
 However, they are most often selected by design, in which kernel based learning algorithms focus only on learning the weightings on the implicit features, and not the features itself.
@@
 However, the approach has yet to generalise to conditional embeddings for supervised learning.
-
-	In this paper, we take a learning theoretic approach to learn the hyperparameters of a conditional kernel embedding in a supervised manner.
-We begin by proposing the kernel embedding classifier (KEC), a principled framework for inferring multiclass probabilistic outputs using conditional embeddings, and provide a proof for its stochastic convergence.
+	%	
+	%	In this paper, we take a learning theoretic approach to learn the hyperparameters of a conditional kernel embedding in a supervised manner.
+We begin by proposing the \gls{MCE} (\gls{MCE}), a principled framework for inferring multiclass probabilistic outputs using conditional embeddings, and provide a proof for its stochastic convergence.
 We then employ Rademacher complexity as a data dependent model complexity measure, and prove that expected classification risk can be bounded by a combination of empirical risk and conditional embedding norm with high probability.
 We use this bound to propose a learning objective that learns the balance between data fit and model complexity in a way that does not rely on priors.
-
-	Our work also has implications in the supervised learning context.
-The kernel embedding classifier is natural in the probabilistic multiclass domain.
+	%	
+	%	Our work also has implications in the supervised learning context.
+The \gls{MCE} is natural in the probabilistic multiclass domain.
 On the other hand, similarly kernel based classifiers such as support vector classifiers (SVC) \citep{m2001introduction} and Gaussian process classifiers (GPC) \citep{rasmussen2006gaussian} are natural only in the binary classification domain, and require extensions to handle the multiclass scenario, such as using one-against-all, one-against-one, or decision trees on multiple independent binary classifiers \citep{aly2005survey, hsu2002comparison}.
 Moreover, SVCs are not probabilistic by nature, while GPCs are analytically intractable and must resort to posterior approximations.
-In this paper, we verify the performance and versatility of the kernel embedding classifier on standard UCI datasets.
-With its generality and flexibility, KECs can also be constructed to learn explicit feature representations, and is inherently compatible with deep neural network type architectures.
-To this end, we demonstrate that KECs can perform end-to-end learning on a convolutional neural network, while also outperforming the original network.
+In this paper, we verify the performance and versatility of the \gls{MCE} on standard UCI datasets.
+With its generality and flexibility, \gls{MCE}s can also be constructed to learn explicit feature representations, and is inherently compatible with deep neural network type architectures.
+To this end, we demonstrate that \gls{MCE}s can perform end-to-end learning on a convolutional neural network, while also outperforming the original network.
+
+	\citep{wilson2016stochastic}
+
+	Do a related work section? And then...
+
+	In the remainder of this paper, \cref{sec:background} provides the relevant background in \glspl{CME} and Rademacher complexities, \cref{sec:kernel_embedding_classifier} introduces the \gls{MCE}, \cref{sec:hyperparameter_learning} outlines our approach and algorithm, and \cref{sec:experiments} presents the experiments.
 
@@
 
-\section{Kernel Embedding Classifier}
+	\section{Multiclass Conditional Embeddings}
 	\label{sec:kernel_embedding_classifier}
@@
 	\begin{equation}
-		p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mathbb{P}[Y \in \{c\} | X = x] = \mathbb{E}[\mathbb{1}_{c}(Y) | X = x].
+	p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mathbb{E}[\mathbb{1}_{c}(Y) | X = x].
 	\label{eq:decision_probability}
@@
 	where $\bvec{Y} := \begin{bmatrix} \bvec{1}_{1} & \bvec{1}_{2} & \cdots & \bvec{1}_{m} \end{bmatrix} \in \{0, 1\}^{n \times m}$ is simply the one hot encoded labels $\{y_{i}\}_{i = 1}^{n}$.
-The kernel embedding classifier is thus the multi-valued decision function $\bvec{f}(x)$ \eqref{eq:empirical_decision_probability_vector}.
+The \gls{MCE} is thus the multi-valued decision function $\bvec{f}(x)$ \eqref{eq:empirical_decision_probability_vector}.
 We proceed to prove that empirical decision probabilities \eqref{eq:empirical_decision_probability} converge to the true decision probabilities.
@@
 	\end{theorem}
+
+	Note that the kernel image assumption is on the input kernel not the output kernel, which is a Kronecker delta in this case.
+Furthermore, this assumption can be relaxed in practice due to \citep{song2009hilbert} by adding a regularisation parameter.
+
 	While decision probability estimates \eqref{eq:empirical_decision_probability} do not necessarily form a normalised distribution for finite $n$, \cref{thm:probability_convergence_copy} guarantees that they approach one with increasing sample size.
@@
 
-	Kernel embedding classifiers \eqref{eq:empirical_decision_probability} are equivalent to a conditional embedding with a discrete target space $\mathcal{Y}$.
+	\gls{MCE}s \eqref{eq:empirical_decision_probability} are equivalent to a conditional embedding with a discrete target space $\mathcal{Y}$.
 Hyperparameter learning for conditional embeddings is particularly difficult compared to joint embeddings, since the kernel $k_{\theta}$ with parameters $\theta \in \Theta$ is to be learned jointly with a regularisation parameter $\lambda \in \Lambda = \mathbb{R}_{+}$.
@@
 	to express classification risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$.
-Under this loss, we prove that the expected risk for the kernel embedding classifier $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a Rademacher complexity bound $r(\theta, \lambda)$ with high probability.
+Under this loss, we prove that the expected risk for the \gls{MCE} $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a Rademacher complexity bound $r(\theta, \lambda)$ with high probability.
 
-	\begin{theorem}[Expected Risk Bound for KEC Hyperparameter Learning]
+	\begin{theorem}[Expected Risk Bound for \gls{MCE} Hyperparameter Learning]
 		\label{thm:expected_risk_bound_hyperparameter_learning_copy}
@@
 		\begin{equation}
-			\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e \; r(\theta, \lambda) + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
+		\begin{aligned}
+		&\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \\
+		&\leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e \; r(\theta, \lambda) + \sqrt{\frac{8}{n} \log{\frac{2}{\beta}}},
 		\label{eq:expected_risk_bound_hyperparameter_learning_copy}
+		\end{aligned}
 		\end{equation}
-		where $r(\theta, \lambda) := \sqrt{\mathrm{trace}\bigg(\bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} K_{\theta} (K_{\theta} + n \lambda I)^{-1} \bvec{Y}\bigg) \sup_{x \in \mathcal{X}} k_{\theta}(x, x)}$.
+		where $r(\theta, \lambda) := \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda}) \sup_{x \in \mathcal{X}} k_{\theta}(x, x)}$ and $V_{\theta, \lambda} := (K_{\theta} + n \lambda I)^{-1} \bvec{Y}$.
 	\end{theorem}
@@
 
-	\begin{algorithm}[tb]
-		\caption{KEC Hyperparameter Learning with Batch Stochastic Gradient Updates}
+	\begin{algorithm*}[tb]
+		\caption{\gls{MCE} Hyperparameter Learning with Batch Stochastic Gradient Updates}
 		\label{alg:kernel_embedding_classifier_training}
@@
 		\end{algorithmic}
-	\end{algorithm}
+	\end{algorithm*}
 
 	Our learning algorithm does not restrict the way the kernel $k_{\theta}$ is constructed from its parameters $\theta \in \Theta$.
-One particularly useful class of kernel embedding classifiers are those where the input kernel $k_{\theta}(x, x') = \langle \varphi_{\theta}(x), \varphi_{\theta}(x') \rangle$ is constructed from neural networks $\varphi_{\theta} : \mathcal{X} \to \mathbb{R}^{p}$ explicitly.
-We refer to kernel embedding classifiers constructed this way as kernel embedding networks (KEN).
+One particularly useful class of \gls{MCE}s are those where the input kernel $k_{\theta}(x, x') = \langle \varphi_{\theta}(x), \varphi_{\theta}(x') \rangle$ is constructed from neural networks $\varphi_{\theta} : \mathcal{X} \to \mathbb{R}^{p}$ explicitly.
+We refer to \gls{MCE}s constructed this way as kernel embedding networks (KEN).
 Neural networks are typically defined by weights and biases of its hidden layers, which collectively define the parameters $\theta$ of the constructed kernel, and are thus trainable under our learning algorithm.
@@
 This is in contrast to the potentially infinitely many implicit features from nonlinear kernels, which in turn define a shallower but wider model architecture.
-We direct the reader to appendix C for detailed discussion on the various kernel embedding classifier architectures and their implementation as compared to \cref{alg:kernel_embedding_classifier_training}.
+We direct the reader to appendix C for detailed discussion on the various \gls{MCE} architectures and their implementation as compared to \cref{alg:kernel_embedding_classifier_training}.
+
+	\section{Variations}
+
+	- CEN and different variations
+	- Linear kernels on top of neural network features would be positive definition but not characteristic.
+However it is often faster to train and the results can be good given a good network architecture
+	% Remember the idea about running datafit section on a validation set
+	- Using a validation batch
+	- Talk about the scaling of the complexity term helps
 
@@
 	For a linear class of predictors parametrised as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularisation to bound the Rademacher complexity, achieving tight generalisation bounds in the context of multi-label learning.
-The KEC predictor \eqref{eq:empirical_decision_probability_vector} has the same linear form in the feature space, $\bvec{f}_{\theta, \lambda}(x) = \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \Phi_{\theta}^{T} \phi_{\theta}(x) = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$, where instead of learning the operator $W^{T}$ directory, we learn hyperparameters $\theta \in \Theta, \lambda \in \Lambda$ for the empirical conditional embedding map $\mathcal{U}^{(\theta, \lambda)}_{Y | X}$ and thus also the features $\phi_{\theta}(x)$.
+The \gls{MCE} predictor \eqref{eq:empirical_decision_probability_vector} has the same linear form in the feature space, $\bvec{f}_{\theta, \lambda}(x) = \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \Phi_{\theta}^{T} \phi_{\theta}(x) = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$, where instead of learning the operator $W^{T}$ directory, we learn hyperparameters $\theta \in \Theta, \lambda \in \Lambda$ for the empirical conditional embedding map $\mathcal{U}^{(\theta, \lambda)}_{Y | X}$ and thus also the features $\phi_{\theta}(x)$.
 \cite{xu2016local} extends the trace norm regularisation approach by considering the local Rademacher complexity on a subset of the predictor class, where they instead minimise the tail sum of the predictor singular values.
@@
 
-		\begin{figure}[t]
+	\begin{figure*}[t]
 		\centering
@@
 		\includegraphics[width=0.48\linewidth]{figures/iris_accuracy.eps}
-			\caption{Rademacher complexity balanced learning of hyperparameters for an isotropic Gaussian kernel embedding classifier, using the first two attributes of the iris dataset.}
+		\caption{Rademacher complexity balanced learning of hyperparameters for an isotropic Gaussian \gls{MCE}, using the first two attributes of the iris dataset.}
 		\label{fig:iris}
-		\end{figure}
+	\end{figure*}
 
@@
 
-		\begin{table}[t]
-			\caption{Classification accuracy (\%) of kernel embedding classifiers on UCI datasets}
+	%	\begin{table*}[t]
+	%		\caption{Classification accuracy (\%) on UCI datasets}
+	%		\label{tab:uci_experiments}
+	%		\centering
+	%		\begin{tabular}{lcccccccc}	
+	%			Dataset \hspace{\fill} $(n, d, m)$ & G\gls{MCE} & G\gls{MCE}-SGD & KEN-1 & KEN-2 & ERM & CV & MED & Others \\
+	%			\midrule
+	%			\texttt{banknote} \hspace{\fill} (1372, 4, 2) & $\mathbf{99.9 \pm 0.2}$ & $98.8 \pm 0.9$ & $99.5 \pm 1.0$ & $99.4 \pm 0.9$ & $\mathbf{99.9 \pm 0.2}$ & $\mathbf{99.9 \pm 0.2}$ & $92.0 \pm 4.3$ & 99.78\textsuperscript{a} \\
+	%			\texttt{ecoli} \hspace{\fill} (336, 7, 8) & $\mathbf{87.5 \pm 4.4}$ & $84.5 \pm 5.0$ & $\mathbf{87.5 \pm 3.2}$ & $86.3 \pm 6.0$ & $72.1 \pm 20.5$ & $73.8 \pm 23.8$ & $42.1 \pm 47.7$ & 81.1\textsuperscript{b} \\
+	%			\texttt{robot} \hspace{\fill} (5456, 24, 4) & $\mathbf{96.7 \pm 0.9}$ & $95.5 \pm 0.9$ & $82.3 \pm 7.1$ & $94.5 \pm 0.8$ & $91.0 \pm 3.7$ & $90.9 \pm 3.4$ & $81.1 \pm 6.2$ & 97.59\textsuperscript{c} \\
+	%			\texttt{segment} \hspace{\fill} (2310, 19, 7) & $\mathbf{98.4 \pm 0.8}$ & $96.1 \pm 1.5$ & $94.6 \pm 1.6$ & $96.7 \pm 1.1$ & $98.1 \pm 1.1$ & $98.3 \pm 1.3$ & $27.3 \pm 26.4$ & 96.83\textsuperscript{d} \\
+	%			\texttt{wine} \hspace{\fill} (178, 13, 3) & $\mathbf{97.2 \pm 3.7}$ & $93.3 \pm 6.0$ & $96.1 \pm 5.0$ & $97.2 \pm 5.1$ & $93.9 \pm 5.2$ & $93.3 \pm 7.4$ & $93.3 \pm 7.8$ & 100\textsuperscript{e} \\
+	%			\texttt{yeast} \hspace{\fill} (1484, 8, 10) & $52.5 \pm 2.1$ & $\mathbf{60.3 \pm 4.4}$ & $55.8 \pm 5.0$ & $59.6 \pm 4.0$ & $45.9 \pm 6.4$ & $58.0 \pm 5.8$ & $31.2 \pm 14.1$ & 55.0\textsuperscript{b} \\
+	%		\end{tabular}
+	%	\end{table*}
+
+	\begin{table*}[t]
+		\caption{Test accuracy (\%) on UCI datasets}
 		\label{tab:uci_experiments}
 		\centering
-			\begin{tabular}{lccccc}			
-				Dataset \hspace{\fill} $(n, d, m)$ & GKEC & GKEC-SGD & KEN-1 & KEN-2 & Others \\
+		\begin{tabular}{lcccccccc}	
+			Dataset & G\gls{MCE} & G\gls{MCE}-SGD & KEN-1 & KEN-2 & ERM & CV & MED & Others \\
 			\midrule
-				\texttt{banknote} \hspace{\fill} (1372, 4, 2) & $99.9 \pm 0.2$ & $98.8 \pm 0.9$ & $99.5 \pm 1.0$ & $99.4 \pm 0.9$ & 99.78\textsuperscript{a} \\
-				\texttt{ecoli} \hspace{\fill} (336, 7, 8) & $87.5 \pm 4.4$ & $84.5 \pm 5.0$ & $87.5 \pm 3.2$ & $86.3 \pm 6.0$ & 81.1\textsuperscript{b} \\
-				\texttt{robot} \hspace{\fill} (5456, 24, 4) & $96.7 \pm 0.9$ & $95.5 \pm 0.9$ & $82.3 \pm 7.1$ & $94.5 \pm 0.8$ & 97.59\textsuperscript{c} \\
-				\texttt{segment} \hspace{\fill} (2310, 19, 7) & $98.4 \pm 0.8$ & $96.1 \pm 1.5$ & $94.6 \pm 1.6$ & $96.7 \pm 1.1$ & 96.83\textsuperscript{d} \\
-				\texttt{wine} \hspace{\fill} (178, 13, 3) & $97.2 \pm 3.7$ & $93.3 \pm 6.0$ & $96.1 \pm 5.0$ & $97.2 \pm 5.1$ & 100\textsuperscript{e} \\
-				\texttt{yeast} \hspace{\fill} (1484, 8, 10) & $52.5 \pm 2.1$ & $60.3 \pm 4.4$ & $55.8 \pm 5.0$ & $59.6 \pm 4.0$ & 55.0\textsuperscript{b} \\
+			\texttt{banknote} & $\mathbf{99.9 \pm 0.2}$ & $98.8 \pm 0.9$ & $99.5 \pm 1.0$ & $99.4 \pm 0.9$ & $\mathbf{99.9 \pm 0.2}$ & $\mathbf{99.9 \pm 0.2}$ & $92.0 \pm 4.3$ & 99.78\textsuperscript{a} \\
+			\texttt{ecoli} & $\mathbf{87.5 \pm 4.4}$ & $84.5 \pm 5.0$ & $\mathbf{87.5 \pm 3.2}$ & $86.3 \pm 6.0$ & $72.1 \pm 20.5$ & $73.8 \pm 23.8$ & $42.1 \pm 47.7$ & 81.1\textsuperscript{b} \\
+			\texttt{robot} & $\mathbf{96.7 \pm 0.9}$ & $95.5 \pm 0.9$ & $82.3 \pm 7.1$ & $94.5 \pm 0.8$ & $91.0 \pm 3.7$ & $90.9 \pm 3.4$ & $81.1 \pm 6.2$ & 97.59\textsuperscript{c} \\
+			\texttt{segment} & $\mathbf{98.4 \pm 0.8}$ & $96.1 \pm 1.5$ & $94.6 \pm 1.6$ & $96.7 \pm 1.1$ & $98.1 \pm 1.1$ & $98.3 \pm 1.3$ & $27.3 \pm 26.4$ & 96.83\textsuperscript{d} \\
+			\texttt{wine} & $\mathbf{97.2 \pm 3.7}$ & $93.3 \pm 6.0$ & $96.1 \pm 5.0$ & $97.2 \pm 5.1$ & $93.9 \pm 5.2$ & $93.3 \pm 7.4$ & $93.3 \pm 7.8$ & 100\textsuperscript{e} \\
+			\texttt{yeast} & $52.5 \pm 2.1$ & $\mathbf{60.3 \pm 4.4}$ & $55.8 \pm 5.0$ & $59.6 \pm 4.0$ & $45.9 \pm 6.4$ & $58.0 \pm 5.8$ & $31.2 \pm 14.1$ & 55.0\textsuperscript{b} \\
 		\end{tabular}
-		\end{table}
+	\end{table*}
 
@@
 The former has a shallow but wide model architecture, while the latter has a deeper but narrower model architecture.
-The Gaussian kernel is learned with both full (GKEC) and batch stochastic gradient updates (GKEC-SGD) using a tenth ($n_{b} \approx \frac{n}{10}$) of the training set each training iteration, with sensitivity and length scales initialised to $1$.
+The Gaussian kernel is learned with both full (G\gls{MCE}) and batch stochastic gradient updates (G\gls{MCE}-SGD) using a tenth ($n_{b} \approx \frac{n}{10}$) of the training set each training iteration, with sensitivity and length scales initialised to $1$.
 For kernel embedding networks, we randomly select two simple fully connected architectures with 16-32-8 (KEN-1) and 96-32 (KEN-2) hidden units respectively, and learn the conditional embedding without dropout under ReLU activation.
@@
 	We apply \cref{alg:kernel_embedding_classifier_training} to learn anisotropic length scales of Gaussian kernels on pixels of the MNIST digits dataset \citep{lecun1998gradient}.
-We first demonstrate the test performance of KECs as the training set increases in size, verifying \cref{thm:probability_convergence_copy} in that decision probabilities converge to the true and thus test distribution as $n$ increases.
+We first demonstrate the test performance of \gls{MCE}s as the training set increases in size, verifying \cref{thm:probability_convergence_copy} in that decision probabilities converge to the true and thus test distribution as $n$ increases.
 In the top left plot of \cref{fig:mnist_experiments}, we train on datasets of varying sizes, from 50 to 5000 samples, and benchmark performance on the standard test set of 10000 examples.
 All hyperparameters are initialised to 1 before training.
-For each $n$, we see that KECs outperform SVCs, since SVCs are unable to learn the length scales of the Gaussian kernel.
-This also shows that KECs perform very well with small datasets even when $n < d$.
-The MNIST dataset has $d = 28^{2} = 784$ pixel dimensions, yet with only $n = 50, 150, 250$ training samples, the KEC achieves a test accuracy of 45.7\%, 70.09\%, and 79.37\% respectively, compared to 18.13\%, 37.43\%, and 53.81\% from SVCs.
+For each $n$, we see that \gls{MCE}s outperform SVCs, since SVCs are unable to learn the length scales of the Gaussian kernel.
+This also shows that \gls{MCE}s perform very well with small datasets even when $n < d$.
+The MNIST dataset has $d = 28^{2} = 784$ pixel dimensions, yet with only $n = 50, 150, 250$ training samples, the \gls{MCE} achieves a test accuracy of 45.7\%, 70.09\%, and 79.37\% respectively, compared to 18.13\%, 37.43\%, and 53.81\% from SVCs.
 We also compare training under the learning objective with and without the Rademacher complexity bound.
@@
 
-		\begin{figure}[t]
+	\begin{figure*}[t]
 		\centering 
@@
 		\label{fig:mnist_experiments}
-		\end{figure}
+	\end{figure*}
 
@@
 The resulting bound justifies the use of stochastic gradient updates for hyperparameter learning, which we verify experimentally on standard UCI datasets.
-The kernel embedding classifier is also inherently flexible in architecture, and in particular can perform end-to-end learning on a neural network, which we demonstrate on UCI datasets and MNIST digits, where it outperforms the original convolutional neural network in the latter.
+The \gls{MCE} is also inherently flexible in architecture, and in particular can perform end-to-end learning on a neural network, which we demonstrate on UCI datasets and MNIST digits, where it outperforms the original convolutional neural network in the latter.
 
-	As kernel embedding classifiers are simply trainable conditional embeddings, this framework can incorporated and extended in many ways into techniques that requires appropriately learned kernel embeddings.
+	As \gls{MCE}s are simply trainable conditional embeddings, this framework can incorporated and extended in many ways into techniques that requires appropriately learned kernel embeddings.
 In particular, nonparametric probabilistic inference can be carried out in the RKHS to obtain joint and reverse conditional embeddings, where mode decoding, density recovery, and sampling techniques can lead to effective generative models now that hyperparameters are learned.
 This line of approach can potentially lead to Bayesian extensions to our framework.
-We also envision a semi-supervised and one class extension to the KEC framework that can relax supervision in training.
+We also envision a semi-supervised and one class extension to the \gls{MCE} framework that can relax supervision in training.
 Moreover, instead of a Kronecker delta kernel, target label kernels with non-zero and potentially trainable similarities between distinct labels may capture label correlations better than our original framework.
@@
 	\newpage
+	\bibliography{kernel_embedding}
 	\bibliographystyle{apalike}
-\bibliography{kernel_embedding}
 

### 2017-10-07 AISTATS2018/cake_aistats2018.tex
Almost done with background, editted MCE section, about to change hyperparameter learning section

@@
 \newacronym{GPC}{GPC}{Gaussian process classifier}
-\newacronym{KRR}{KRR}{kernel ridged regression}
+\newacronym{KRR}{KRR}{kernel ridged regressor}
 \newacronym{RLSC}{RLSC}{regularized least squares classification}
 \newacronym{ERM}{ERM}{empirical risk minimization}
+\newacronym{MMD}{MMD}{maximum mean discrepancy}
 
@@
 
-		% The goal is to motivate the problem here and outline our contribution in response 
+		% The goal is to motivate the problem here and outline our contribution
 		How can we design a scalable learning objective for learning kernel hyperparameters of conditional mean embeddings?
-Conditional mean embeddings are nonparametric models that encodes conditional distributions in a reproducing kernel Hilbert space (RKHS) directly through observed data, resulting in a flexible and powerful framework for probabilistic inference.
+Conditional mean embeddings are nonparametric models that encodes conditional distributions in a reproducing kernel Hilbert space directly through observed data, resulting in a flexible and powerful framework for probabilistic inference.
 However, their performance is greatly dependent on the choice of kernel hyperparameters and regularization, yet current approaches for hyperparameter tuning predominantly rely on cross validation and distance based heuristics.
@@
 The approach only requires batch updates, allowing scalable kernel learning without kernel approximations.
-Experiments demonstrate that our framework outperforms standard cross validation and heuristics, and can be further extended to incorporate and learn neural network weights with improved accuracy.
+Experiments demonstrate that our framework outperforms standard cross validation and heuristics, and can be further extended to incorporate and learn neural network weights to improve generalization.
 
-		%	We benchmark our learning algorithm with standard UCI datasets, as well as to learn features of a convolutional neural network with improved accuracy, demonstrating the generality of this approach.
-
-		%	ORIGINAL:
+		% % % Original:
 		%	We propose learning-theoretic bounds for hyperparameter learning of conditional kernel embeddings for estimating multiclass probabilities.
@@
 
-	% Can we formulate a learning objective that resembles the marginal likelihood for conditional mean embeddings?
-
-	% Paragraph: Introducing nonparametric kernel based models, and CME is one of them
-
 		% Paragraph: Immediately start by motivating why conditional mean embeddings and kernel embeddings are useful in general
 
-	\Glspl{CME} are attractive because they encode conditional expectations in a \gls{RKHS}, bypassing the need for a parametrised density \citep{song2013kernel}.
+		\Glspl{CME} are attractive because they encode conditional expectations in a \gls{RKHS}, bypassing the need for a parametrized distribution \citep{song2013kernel}.
 They are part of a broader class of models known as kernel embeddings, where nonparametric probabilistic inference can be carried out entirely within the \gls{RKHS} because difficult marginalization integrals become simple linear algebra \citep{muandet2016kernel}.
@@
 		\Glspl{MCE} are \glspl{CME} with discrete targets but arbitrary inputs, where on top of conditional expectations we can further infer conditional probabilities.
-As such, they are widely applicable to probabilistic inference in multiclass settings and learning probabilistic mappings between arbitrary inputs and a discrete set of actions or outcomes.
-Unlike \glspl{SVM} \citep{scholkopf2002learning}, \glspl{GPC} \citep{rasmussen2006gaussian}, and multiclass \glspl{RLSC} \citep{rifkin2003regularized, pahikkala2012unsupervised}, \Glspl{MCE} do not require fitting separate binary classifiers for each class or each pair of classes for a final multiclass prediction.
-Instead, a single conditional embedding is sufficient for producing consistent probabilistic estimates from \glspl{MCE}.
+As such, they are widely applicable to probabilistic inference in multiclass settings and learning probabilistic representations between arbitrary inputs and a discrete set of actions or outcomes.
+Unlike \glspl{SVM} \citep{scholkopf2002learning}, \glspl{GPC} \citep{rasmussen2006gaussian}, and multiclass \glspl{RLSC} \citep{rifkin2003regularized, pahikkala2012unsupervised}, \Glspl{MCE} do not require separately fitting binary classifiers for each class or each pair of classes for a final multiclass prediction.
+Instead, a single conditional embedding is sufficient for producing consistent multiclass probabilistic estimates.
 
@@
 		Nevertheless, like most kernel based models, their performance is highly dependent on the hyperparameters chosen.
-In these settings, the model selection process usually begins by selecting a kernel, whose parameters become part of the model hyperparameters, which may further include noise or regularisation parameters.
+In these settings, the model selection process usually begins by selecting a kernel, whose parameters become part of the model hyperparameters, which may further include noise or regularization parameters.
 Given a set of hyperparameters, training boils down to solving either a convex optimization problem, e.g.
-\glspl{SVM}, or a linear set of equations, e.g.
+\glspl{SVM}, or a set of linear equations, e.g.
 \glspl{GPC}, \glspl{RLSC}, and \glspl{CME}.
-Unfortunately, kernel hyperparameter tuning is not straight forward, and various forms of cross validation \citep{song2013kernel} or heuristics such as the median length heuristic \citep{muandet2016kernel} remain as the primary approaches for this task.
+Unfortunately, hyperparameter tuning is not straight forward, and various forms of cross validation \citep{song2013kernel} or heuristics such as the median length heuristic \citep{damien2017asymptotic, muandet2016kernel} remain as the primary approaches for this task.
 
@@
 
-	One notable success story in this domain are \gls{GPs} \citep{rasmussen2006gaussian}, which has long enjoyed the well celebrated marginal likelihood for continuous hyperparameter learning.
+		One notable success story in this domain are \gls{GPs} \citep{rasmussen2006gaussian}, which has long enjoyed the well celebrated marginal likelihood for hyperparameter learning.
 The marginal likelihood arises naturally from the Bayesian formulation of the model, and exhibits certain desirable properties -- in particular, the ability to automatically balance between data fit and model complexity.
-On the other hand, \glspl{CME} are not necessarily Bayesian, and hence they do not benefit from a natural marginal likelihood formulation, yet such a balance is critical when generalising the model beyond unseen examples.
+On the other hand, \glspl{CME} are not necessarily Bayesian, and hence they do not benefit from a natural marginal likelihood formulation, yet such a balance is critical when generalizing the model beyond unseen examples.
 
@@
 In this paper, we present such a learning objective as our main contribution.
-In particular, we 1) derive a measure of model complexity for a specific \gls{MCE} based on the Rademacher complexity of a relevant class of \glspl{MCE}, 2) formulate a novel learning objective based on this complexity measure to achieve the balance between data fit and model complexity, and 3) propose a scalable hyperparameter learning algorithm under this objective using batch updates.
-We show that this learning objective produces \glspl{MCE} that generalises better than that learned from cross validation, \gls{ERM}, and median length heuristics on standard benchmarks, and apply such an algorithm to incorporate and learn neural network weights with improved accuracy on the MNIST dataset.
-Finally, we also discuss some variations to the \glspl{MCE} model.
+In particular, we 1) derive a measure of model complexity for a specific \gls{MCE} based on the Rademacher complexity of a relevant class of \glspl{MCE}, 2) formulate a novel learning objective based on this complexity measure to control expected generalization risk by balancing data fit against model complexity, and 3) propose a scalable hyperparameter learning algorithm under this objective using batch updates.
+We show that this learning objective produces \glspl{MCE} that generalizes better than that learned from cross validation, \gls{ERM}, and median length heuristics on standard benchmarks, and apply such an algorithm to incorporate and learn neural network weights to improve generalization accuracy on the MNIST dataset.
+% Finally, we also discuss some variations to the \gls{MCE} model.
 
@@
 
-	\gls{KRR} \citep{friedman2001elements}
-
-	- Difference between both \citep{rifkin2003regularized} and \citep{pahikkala2012unsupervised} is the loss function used and natural multiclass formulation and what we are optimising over (not the weights directly but the hyperparameter of the weights).
-	- 
+		% % % Original:
 		%	Kernel embeddings are principled methods to represent probability distributions in a nonparametric setting \citep{song2013kernel}.
@@
 Consequently, nonparametric probabilistic inference can be carried out entirely within the RKHS, where difficult marginalization integrals become simple linear algebra \citep{muandet2016kernel}.
+--COVERED
 
@@
 The problem of estimating the kernel mean in a reproducing kernel Hilbert space (RKHS) is thus central to kernel methods.
+-- COVERED
 		%	
@@
 However, the approach has yet to generalise to conditional embeddings for supervised learning.
+-- TALK ABOUT THIS IN RELATED WORK
 		%	
@@
 We use this bound to propose a learning objective that learns the balance between data fit and model complexity in a way that does not rely on priors.
+-- COVERED, but could use some phrases here like "does not rely on priors"
 		%	
@@
 
-	\citep{wilson2016stochastic}
-
-	Do a related work section? And then...
-
-	In the remainder of this paper, \cref{sec:background} provides the relevant background in \glspl{CME} and Rademacher complexities, \cref{sec:kernel_embedding_classifier} introduces the \gls{MCE}, \cref{sec:hyperparameter_learning} outlines our approach and algorithm, and \cref{sec:experiments} presents the experiments.
-
-	\section{Hilbert Space Embeddings of Conditional Probability Distributions}
+	\section{Background and Related Work}
 	\label{sec:background}
 
-	We begin by providing an overview of Hilbert space embeddings, where probability distributions are represented by mean embeddings in a reproducing kernel Hilbert space (RKHS) through positive definite kernels.
+		\subsection{Conditional Mean Embeddings}
+
+%			We begin by providing an overview of Hilbert space embeddings, where probability distributions are represented by mean embeddings in a reproducing kernel Hilbert space (RKHS) through positive definite kernels.
 Specifically, in the supervised learning context for which we are primarily interested in, we focus on conditional distributions and its representations in the RKHS.
 
-	To construct a conditional embedding map $\mathcal{U}_{Y | X}$ corresponding to the distribution $\mathbb{P}_{Y | X}$, where $X : \Omega \to \mathcal{X}$ and $Y: \Omega \to \mathcal{Y}$ are measurable random variables, we choose a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ for the input space $\mathcal{X}$ and another kernel $l : \mathcal{Y} \times \mathcal{Y} \to \mathbb{R}$ for the output space $\mathcal{Y}$.
-These kernels $k$ and $l$ each describe how similarity is measured within their respective domains $\mathcal{X}$ and $\mathcal{Y}$, and are symmetric and positive definite such that they uniquely define the RKHS $\mathcal{H}_{k}$ and $\mathcal{H}_{l}$.
-We then define $\mathcal{U}_{Y | X} := C_{YX} C_{XX}^{-1}$ where $C_{YX} := \mathbb{E}[l(Y, \cdot) \otimes k(X, \cdot)]$ and $C_{XX} := \mathbb{E}[k(X, \cdot) \otimes k(X, \cdot)]$ \citep{song2009hilbert}.
-The conditional embedding map can be seen as an operator map from $\mathcal{H}_{k}$ to $\mathcal{H}_{l}$.
-In this sense, it sweeps out a family of conditional embeddings $\mu_{Y | X = x}$ in $\mathcal{H}_{l}$, each indexed by the input variable $x$, via the property $\mu_{Y | X = x} := \mathbb{E}[l(Y, \cdot) | X = x] = \mathcal{U}_{Y | X} k(x, \cdot)$.
+			To construct a conditional embedding operator $\mathcal{U}_{Y | X}$ corresponding to the distribution $\mathbb{P}_{Y | X}$, where $X : \Omega \to \mathcal{X}$ and $Y: \Omega \to \mathcal{Y}$ are measurable random variables, we first choose a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ for the input space $\mathcal{X}$ and another kernel $l : \mathcal{Y} \times \mathcal{Y} \to \mathbb{R}$ for the output space $\mathcal{Y}$.
+These kernels $k$ and $l$ each describe how similarity is measured within their respective domains $\mathcal{X}$ and $\mathcal{Y}$, and are symmetric positive definite such that they uniquely define the \gls{RKHS} $\mathcal{H}_{k}$ and $\mathcal{H}_{l}$.
+The conditional embedding operator $\mathcal{U}_{Y | X}$ is then the operator $\mathcal{U} : \mathcal{H}_{k} \to \mathcal{H}_{l}$ for which $\mu_{Y | X = x} = \mathcal{U} k(x, \cdot)$, where $\mu_{Y | X = x} := \mathbb{E}[l(Y, \cdot) | X = x]$ is the \gls{CME} \citep{song2009hilbert}.
+In this sense, it sweeps out a family of conditional embeddings $\mu_{Y | X = x}$ in $\mathcal{H}_{l}$, each indexed by the input variable $x \in \mathcal{X}$.
+We then define cross covariance operators $C_{YX} := \mathbb{E}[l(Y, \cdot) \otimes k(X, \cdot)] : \mathcal{H}_{k} \to \mathcal{H}_{l}$ and $C_{XX} := \mathbb{E}[k(X, \cdot) \otimes k(X, \cdot)] : \mathcal{H}_{k} \to \mathcal{H}_{k}$.
+Alternatively, they can be seen as elements within the tensor product space $C_{YX} \in \mathcal{H}_{l} \otimes \mathcal{H}_{k}$ and $C_{XX} \in \mathcal{H}_{k} \otimes \mathcal{H}_{k}$.
 
-	Under the assumption that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$, \citet[Theorem 4]{song2009hilbert} proved that the conditional expectation of a function $g \in \mathcal{H}_{l}$ can be expressed as an inner product, $\mathbb{E}[g(Y) | X = x] = \langle \mu_{Y | X = x}, g \rangle$.
-While the assumptions that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$ and $k(x, \cdot) \in \mathrm{image}(C_{XX})$ hold for finite input domains $\mathcal{X}$ and characteristic kernels $k$, it is not necessarily true when $\mathcal{X}$ is a continuous domain \citep{fukumizu2004dimensionality}, which is the scenario for many classification problems.
-In this case, $C_{YX} C_{XX}^{-1}$ becomes only an approximation to $\mathcal{U}_{Y | X}$, and we instead regularise the inverse and use $C_{YX} (C_{XX} + \lambda I)^{-1}$, which also serves to avoid overfitting \citep{song2013kernel}.
+			Under the assumption that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, it can be shown that $\mathcal{U}_{Y | X} = C_{YX} C_{XX}^{-1}$.
+While this assumption is satisfied for finite domains $\mathcal{X}$ with a characteristic kernel $k$, it does not necessarily hold when $\mathcal{X}$ is a continuous domain \citep{fukumizu2004dimensionality}, which is the case for many classification problems.
+In this case, $C_{YX} C_{XX}^{-1}$ becomes only an approximation to $\mathcal{U}_{Y | X}$, and we instead regularize the inversion and use $\mathcal{U}_{Y | X} = C_{YX} (C_{XX} + \lambda I)^{-1}$, which also serves to avoid overfitting \citep{song2013kernel}.
+\glspl{CME} are useful as for probabilistic inference as conditional expectations of a function $g \in \mathcal{H}_{l}$ can be expressed as inner products, $\mathbb{E}[g(Y) | X = x] = \langle \mu_{Y | X = x}, g \rangle$, provided $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$, \citet[Theorem 4]{song2009hilbert}.
 
-	On top of this, in practice we do not have access to the distribution $\mathbb{P}_{X Y}$ to analytically derive the conditional embedding.
-Instead, we have a finite collection of observations $\{x_{i}, y_{i}\} \in \mathcal{X} \times \mathcal{Y}$, $i \in \mathbb{N}_{n} := \{1, \dots, n\}$, for which the conditional embedding map $\mathcal{U}_{Y | X}$ can be estimated by
+			Furthermore, as both $C_{YX}$ and $C_{XX}$ are defined in terms of expectations of kernels, we can replace them with their empirical estimates to derive a nonparametric estimate for $\mathcal{U}_{Y | X}$ based on finite collection of observations $\{x_{i}, y_{i}\} \in \mathcal{X} \times \mathcal{Y}$, $i \in \mathbb{N}_{n} := \{1, \dots, n\}$,
 			\begin{equation}
@@
 			\end{equation}
-	where $K := \{k(x_{i}, x_{j})\}_{i = 1, j = 1}^{n, n}$, $\Phi := \begin{bmatrix} \phi(x_{1}) & \dots & \phi(x_{n}) \end{bmatrix}$, $\Psi := \begin{bmatrix} \psi(y_{1}) & \dots & \psi(y_{n}) \end{bmatrix}$, $\phi(x) := k(x, \cdot)$, and $\psi(y) := l(y, \cdot)$ \citep{song2013kernel}.
-The empirical conditional embedding $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$ then stochastically converges to the conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot) \in \mathrm{image}(C_{XX})$ \cite[Theorem 6]{song2009hilbert}.
+			where $K_{ij} := k(x_{i}, x_{j})$, $\Phi := \begin{bmatrix} \phi(x_{1}) & \dots & \phi(x_{n}) \end{bmatrix}$, $\Psi := \begin{bmatrix} \psi(y_{1}) & \dots & \psi(y_{n}) \end{bmatrix}$, $\phi(x) := k(x, \cdot)$, and $\psi(y) := l(y, \cdot)$ \citep{song2013kernel}.
+The empirical conditional embedding defined by $\hat{\mu}_{Y | X = x} := \hat{\mathcal{U}}_{Y | X} k(x, \cdot)$ then stochastically converges to the conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot) \in \mathrm{image}(C_{XX})$ \cite[Theorem 6]{song2009hilbert}.
 This allows us to approximate the conditional expectation with $\langle \hat{\mu}_{Y | X = x}, g \rangle$ instead,
@@
 
+		\subsection{Hyperparameter Learning}
+
+			Hyperparameter learning for conditional embeddings is particularly difficult compared to marginal or joint embeddings, since the kernel $k_{\theta}$ with parameters $\theta \in \Theta$ is to be learned jointly with a regularization parameter $\lambda \in \Lambda = \mathbb{R}_{+}$.
+\cite{lever2012conditional} showed that $\mathcal{U} = \hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the solution to the regularized least squares problem in the RKHS from $k(x, \cdot) \in \mathcal{H}_{k}$ to $l(y, \cdot) \mathcal{H}_{l}$,
+			\begin{equation}
+				\hat{\mathcal{E}}_{n, \lambda}[\mathcal{U}] = \frac{1}{n} \sum_{i = 1}^{n} \big\| l(y_{i}, \cdot) - \mathcal{U} k(x_{i}, \cdot) \big\|_{\mathcal{H}_{l}}^{2} + \lambda \| \mathcal{U} \|_{HS}.
+			\label{eq:lever_objective}
+			\end{equation}
+			Minimizing this objective directly over $\theta \in \Theta, \lambda \in \Lambda$ for $\mathcal{U} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X}$ and $k = k_{\theta}$ would result in an overfitted model with small $\lambda$.
+This illustrates that the notion of model complexity during learning is especially important to ensure good generalization.
+\cite{lever2012conditional} proposes to hold out a validation set $\{k(x_{t_{j}}, \cdot), l(y_{t_{j}}, \cdot)\}_{j = 1}^{J}$ and minimize $\frac{1}{J} \sum_{j = 1}^{J} \big\| l(y_{t_{j}}, \cdot) - \hat{\mathcal{U}}_{Y | X} k(x_{t_{j}}, \cdot) \big\|_{\mathcal{H}_{l}}^{2}$ where $\hat{\mathcal{U}}_{Y | X}$ is estimated from the remaining training set using \eqref{eq:empirical_conditional_embedding}.
+This could also be repeated over multiple folds for cross validation.
+\cite{song2013kernel} also uses this cross validation approach, but includes $\lambda \| \mathcal{U} \|_{HS}$ in the minimization.
+This approach improves generalization of \glspl{CME} to unseen examples.
+However, they require the selection for the split and number of folds, and are not optimized for any particular prediction task.
+By fitting a separate model for each fold during learning, they also incur a large computational cost of $O(J n^{3})$ for $J$ folds, and becomes prohibitive with large datasets.
+
+			When cross validation is too expensive, for many stationary kernels, the length scale parameter can be set by the median heuristic \citep{muandet2016kernel} via $\ell = \mathrm{median}_{i, j}(\| x_{i} - x_{j} \|_{2})$.
+However, they are restricted to length scale parameters only and cannot be used to set other hyperparameters, including $\lambda$.
+In the setting of two sample testing, \cite{gretton2012optimal} also notes that they can possibly lead to poor performance.
+In the context of \glspl{CME}, they also do not take into account of labeled information.
+\cite{flaxman2016bayesian} proposed a Bayesian learning framework for marginal embeddings via inducing points, though it is unclear how this can be extended to include \glspl{CME}.
+\cite{fukumizu2009kernel} also investigated the choice of kernel bandwidth for stationary kernels in the setting of binary classification and two sample testing using the \gls{MMD}, but has yet to generalize to \glspl{CME} or multiclass settings.
+
+		\subsection{Rademacher Complexity}
+
+			The Rademacher complexity \citep{bartlett2002rademacher} measures the expressiveness of a function class $F$ by its ability to shatter, or fit, noise.
+They are data-dependent measures, and are thus particularly well suited to learning tasks where generalisation ability is vital, since complexity penalties that are not data dependent cannot be universally effective \citep{kearns1997experimental}.
+
+	%		For a linear class of predictors parametrised as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularisation to bound the Rademacher complexity, achieving tight generalisation bounds in the context of multi-label learning.
+The \gls{MCE} predictor \eqref{eq:empirical_decision_probability_vector} has the same linear form in the feature space, $\bvec{f}_{\theta, \lambda}(x) = \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \Phi_{\theta}^{T} \phi_{\theta}(x) = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$, where instead of learning the operator $W^{T}$ directory, we learn hyperparameters $\theta \in \Theta, \lambda \in \Lambda$ for the empirical conditional embedding map $\mathcal{U}^{(\theta, \lambda)}_{Y | X}$ and thus also the features $\phi_{\theta}(x)$.
+\cite{xu2016local} extends the trace norm regularisation approach by considering the local Rademacher complexity on a subset of the predictor class, where they instead minimise the tail sum of the predictor singular values.
+In the proof of \cref{thm:expected_risk_bound_hyperparameter_learning_copy}, $\theta \in \Theta$ and $\lambda \in \Lambda$ define subsets of $\Theta$ and $\Lambda$ where the Rademacher complexity is considered over.
+By minimising $q(\theta, \lambda)$, we shrink the subset being considered, achieving localised Rademacher complexity based feature learning without selecting parameters that define the tail sum.
+Local Rademacher complexity has also been employed for multiple kernel learning \citep{kloft2011local, cortes2013learning} to learn convex combinations of simpler preselected kernels for a support vector machine.
+We extend its application to the probabilistic multiclass case, and use Rademacher complexity bounds to learn any general kernel for a conditional embedding.
+
+	- Difference between both \citep{rifkin2003regularized} and \citep{pahikkala2012unsupervised} is the loss function used and natural multiclass formulation and what we are optimising over (not the weights directly but the hyperparameter of the weights).
+	- Two problems: Hyperparam learning and pre-image
+	- By restricting it to discrete, pre-image is fine
+	- Then we propose hyperparam learning?
+
+	%From my literature review last year, the two primary challenges I identified within the kernel embeddings community are:
+	%
+	%- Hyperparameter Learning: How can we learn the hyperparameters of kernel embeddings in a principled manner that improves generlisation? And,
+	%- Pre-Image: How can we get back the distribution in probability space after we have embedded them into the Hilbert space?
+	%
+	%These problems have been heavily investigated for marginal embeddings. In January, by restricting the target of a conditional embedding to be discrete.
+
 	\section{Multiclass Conditional Embeddings}
-	\label{sec:kernel_embedding_classifier}
+	\label{sec:multiclass_conditional_embedding}
 
-	In this section, we formulate a kernel embedding based probabilistic classifier by casting it into the conditional embedding framework.
 		In the multiclass setting, the output label space is finite and discrete, taking values only in $\mathcal{Y} = \mathbb{N}_{m} := \{1, \dots, m\}$.
-Naturally, we first choose the Kronecker delta kernel $\delta : \mathbb{N}_{m} \times \mathbb{N}_{m} \to \{0, 1\}$ as the output kernel $l$, where labels that are the same have unit similarity and labels that are different have no similarity.
+Naturally, we choose the Kronecker delta kernel $\delta : \mathbb{N}_{m} \times \mathbb{N}_{m} \to \{0, 1\}$ as the output kernel $l$, where labels that are the same have unit similarity and labels that are different have no similarity.
 That is, for all pairs of labels $y_{i}, y_{j} \in \mathcal{Y}$, $\delta(y_{i}, y_{j}) = 1$ only if $y_{i} = y_{j}$ and is $0$ otherwise.
@@
 		\end{equation}
-	That is, indicator functions $\mathbb{1}_{c} = \delta(c, \cdot)$, $c \in \mathbb{N}_{m}$, are simply the canonical kernel induced features of $\mathcal{H}_{\delta}$.
+		That is, indicator functions $\mathbb{1}_{c} = \delta(c, \cdot)$, $c \in \mathbb{N}_{m}$, are simply the canonical features of $\mathcal{H}_{\delta}$.
 Such properties do not necessarily hold for continuous domains in general.
-This convenient property in the case of a discrete domain $\mathcal{Y}$ with a Kronecker delta kernel $\delta$ is what allows consistent estimations of decision probabilities used in multiclass classification, which we turn to next.
+This convenient property in the case of a discrete domain $\mathcal{Y}$ with a Kronecker delta kernel $\delta$ is what allows consistent estimations of decision probabilities in multiclass settings.
+In fact, $\mathcal{H}_{\delta}$ can be identified with $\mathbb{R}^{m}$.
+Note that there are no restrictions on the domain $\mathcal{X}$ as long as a kernel $k$ can be defined on it.
 
@@
 The \gls{MCE} is thus the multi-valued decision function $\bvec{f}(x)$ \eqref{eq:empirical_decision_probability_vector}.
+In fact, each row of the \gls{MCE} is a \gls{KRR} \citep{friedman2001elements} on $\{0, 1\}$-targets.
 We proceed to prove that empirical decision probabilities \eqref{eq:empirical_decision_probability} converge to the true decision probabilities.
@@
 
-	Note that the kernel image assumption is on the input kernel not the output kernel, which is a Kronecker delta in this case.
-Furthermore, this assumption can be relaxed in practice due to \citep{song2009hilbert} by adding a regularisation parameter.
+		In particular, the assumption that $k(x, \cdot) \in \mathrm{image}(C_{XX})$ is on the input kernel $k$ not the output kernel $l$, which is a Kronecker delta $l = \delta$ for \glspl{MCE}.
+In practice, this assumption can be relaxed through introducing the regularization parameter $\lambda$ as in \eqref{eq:empirical_conditional_embedding} \citep{song2009hilbert}.
 
-	While decision probability estimates \eqref{eq:empirical_decision_probability} do not necessarily form a normalised distribution for finite $n$, \cref{thm:probability_convergence_copy} guarantees that they approach one with increasing sample size.
-When normalised distributions are required, distribution estimates \eqref{eq:empirical_decision_probability} can be clip-normalised,
+		While decision probability estimates \eqref{eq:empirical_decision_probability} do not necessarily form a normalized distribution for finite $n$, \cref{thm:probability_convergence_copy} guarantees that they approach one with increasing sample size.
+When normalized distributions are required, distribution estimates \eqref{eq:empirical_decision_probability} can be clip-normalized,
 		\begin{equation}
@@
 	\label{sec:hyperparameter_learning}
-
-	\gls{MCE}s \eqref{eq:empirical_decision_probability} are equivalent to a conditional embedding with a discrete target space $\mathcal{Y}$.
-Hyperparameter learning for conditional embeddings is particularly difficult compared to joint embeddings, since the kernel $k_{\theta}$ with parameters $\theta \in \Theta$ is to be learned jointly with a regularisation parameter $\lambda \in \Lambda = \mathbb{R}_{+}$.
-While the conditional embedding map $\hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the operator $\mathcal{U}$ that minimises the regularised least squares loss $\frac{1}{n} \sum_{i = 1}^{n} \| \psi(y_{i}) - \mathcal{U} \phi(x_{i}) \|_{\mathcal{H}_{l}}^{2} + \lambda \| \mathcal{U} \|_{HS}$ in the RKHS \citep{song2013kernel}, minimising this loss directly over $\theta \in \Theta, \lambda \in \Lambda$ for $\mathcal{U} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X}$ would trivially result in an overfitted model with $\lambda \rightarrow 0$.
-This implies that the notion of model complexity is especially important, yet current standard solutions often employ either cross validation or nested optimisation separating $\theta$ and $\lambda$, both of which are heuristics and subject to design choices.
-
-	To this end, we propose to use a learning theoretic approach to balance model complexity and data fit.
-The Rademacher complexity \citep{bartlett2002rademacher} measures the expressiveness of a function class $F$ by its ability to shatter, or fit, noise.
-They are data-dependent measures, and are thus particularly well suited to learning tasks where generalisation ability is vital, since complexity penalties that are not data dependent cannot be universally effective \citep{kearns1997experimental}.
 
@@
 Because this bound holds with high probability over \textit{iid} samples, through randomly selecting a batch of training examples that comes from the same distribution, the resulting stochastic gradient will improve a strict upper bound with the same high probability.
-We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:kernel_embedding_classifier_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size.
+We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:multiclass_conditional_embedding_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size.
 The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is performed only once after learning instead of once every learning iteration, and can be avoided by using kernel herding \citep{chen2010super} or random Fourier features \citep{rahimi2008random} to estimate the already learned embedding.
@@
 			\caption{\gls{MCE} Hyperparameter Learning with Batch Stochastic Gradient Updates}
-		\label{alg:kernel_embedding_classifier_training}
+			\label{alg:multiclass_conditional_embedding_training}
 			\begin{algorithmic}[1]
@@
 These kernels benefit in both scalability and expressibility.
-For large datasets, the $n \times n$ Cholesky decomposition required for full gradient updates in \cref{alg:kernel_embedding_classifier_training} can be transformed into a $p \times p$ decomposition by the Woodbury matrix inversion identity \citep{higham2002accuracy}.
+For large datasets, the $n \times n$ Cholesky decomposition required for full gradient updates in \cref{alg:multiclass_conditional_embedding_training} can be transformed into a $p \times p$ decomposition by the Woodbury matrix inversion identity \citep{higham2002accuracy}.
 This allows scalability for $n >> p$ without using stochastic gradient updates so that the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} can be as tight as possible for a given $n$.
@@
 This is in contrast to the potentially infinitely many implicit features from nonlinear kernels, which in turn define a shallower but wider model architecture.
-We direct the reader to appendix C for detailed discussion on the various \gls{MCE} architectures and their implementation as compared to \cref{alg:kernel_embedding_classifier_training}.
+We direct the reader to appendix C for detailed discussion on the various \gls{MCE} architectures and their implementation as compared to \cref{alg:multiclass_conditional_embedding_training}.
 
 	\section{Variations}
+
+	\citep{wilson2016stochastic}
 
@@
 	- Talk about the scaling of the complexity term helps
-
-	\section{Related Work}
-	\label{sec:related_work}
-
-	For a linear class of predictors parametrised as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularisation to bound the Rademacher complexity, achieving tight generalisation bounds in the context of multi-label learning.
-The \gls{MCE} predictor \eqref{eq:empirical_decision_probability_vector} has the same linear form in the feature space, $\bvec{f}_{\theta, \lambda}(x) = \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \Phi_{\theta}^{T} \phi_{\theta}(x) = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$, where instead of learning the operator $W^{T}$ directory, we learn hyperparameters $\theta \in \Theta, \lambda \in \Lambda$ for the empirical conditional embedding map $\mathcal{U}^{(\theta, \lambda)}_{Y | X}$ and thus also the features $\phi_{\theta}(x)$.
-\cite{xu2016local} extends the trace norm regularisation approach by considering the local Rademacher complexity on a subset of the predictor class, where they instead minimise the tail sum of the predictor singular values.
-In the proof of \cref{thm:expected_risk_bound_hyperparameter_learning_copy}, $\theta \in \Theta$ and $\lambda \in \Lambda$ define subsets of $\Theta$ and $\Lambda$ where the Rademacher complexity is considered over.
-By minimising $q(\theta, \lambda)$, we shrink the subset being considered, achieving localised Rademacher complexity based feature learning without selecting parameters that define the tail sum.
-Local Rademacher complexity has also been employed for multiple kernel learning \citep{kloft2011local, cortes2013learning} to learn convex combinations of simpler preselected kernels for a support vector machine.
-We extend its application to the probabilistic multiclass case, and use Rademacher complexity bounds to learn any general kernel for a conditional embedding.
 
@@
 		\includegraphics[width=0.32\linewidth]{figures/iris_underfitted_model.eps}
-		\includegraphics[width=\linewidth]{figures/iris_rademacher_complexity_bound.eps}
-		\includegraphics[width=0.48\linewidth]{figures/iris_cross_entropy_loss.eps}
+		\includegraphics[width=0.48\linewidth]{figures/iris_rademacher_complexity_bound_lower_legend.eps}
+%		\includegraphics[width=0.48\linewidth]{figures/iris_cross_entropy_loss.eps}
 		\includegraphics[width=0.48\linewidth]{figures/iris_accuracy.eps}
@@
 
-	\Cref{fig:iris} demonstrates \cref{alg:kernel_embedding_classifier_training} with full gradient updates ($n_{b} = n$) to learn hyperparameters of the conditional embedding on the two attribute iris dataset.
+	\Cref{fig:iris} demonstrates \cref{alg:multiclass_conditional_embedding_training} with full gradient updates ($n_{b} = n$) to learn hyperparameters of the conditional embedding on the two attribute iris dataset.
 The kernel used is isotropic Gaussian with diagonal length scales $\Sigma = \ell^{2} I_{2}$ and sensitivity $\alpha = \sigma_{f}$, so the hyperparameters are $\theta = (\alpha, \ell)$ and $\lambda$.
@@
 We see that the Rademacher complexity bound (RCB) $r(\theta, \lambda)$ appropriately measures the amount of overfitting with $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = 4.33$ and $r((\alpha_{u}, \ell_{u}), \lambda_{u}) = 0.31$.
-We then learn model hyperparameters with \cref{alg:kernel_embedding_classifier_training} for 500 iterations from both initialisations at rate $\eta = 0.01$, where both models converges to a balanced model with appropriate complexity bounds $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = r((0.01, 0.24), 8.62 \times 10^{-7}) = 2.23 \approx 2.14 = r((\alpha_{u}, \ell_{u}), \lambda_{u}) = r((5.1, 0.24), 0.20)$ and an improved test accuracy of 73.33\%.
+We then learn model hyperparameters with \cref{alg:multiclass_conditional_embedding_training} for 500 iterations from both initialisations at rate $\eta = 0.01$, where both models converges to a balanced model with appropriate complexity bounds $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = r((0.01, 0.24), 8.62 \times 10^{-7}) = 2.23 \approx 2.14 = r((\alpha_{u}, \ell_{u}), \lambda_{u}) = r((5.1, 0.24), 0.20)$ and an improved test accuracy of 73.33\%.
 In particular, the initially overfitted model learns a simpler model at the expense of lower training performance, emphasising the benefits of complexity based regularisation, without which the learning would only maximise training performance at the cost of further overfitting.
@@
 In both scenarios, our learning algorithm improved performance on the test set.
+
+	\gls{CEN}
 
@@
 		\begin{tabular}{lcccccccc}	
-			Dataset & G\gls{MCE} & G\gls{MCE}-SGD & KEN-1 & KEN-2 & ERM & CV & MED & Others \\
+			Dataset & G\gls{MCE} & G\gls{MCE}-SGD & \gls{CEN}-1 & \gls{CEN}-2 & ERM & CV & MED & Others \\
 			\midrule
@@
 
-	We apply \cref{alg:kernel_embedding_classifier_training} to learn anisotropic length scales of Gaussian kernels on pixels of the MNIST digits dataset \citep{lecun1998gradient}.
+	We apply \cref{alg:multiclass_conditional_embedding_training} to learn anisotropic length scales of Gaussian kernels on pixels of the MNIST digits dataset \citep{lecun1998gradient}.
 We first demonstrate the test performance of \gls{MCE}s as the training set increases in size, verifying \cref{thm:probability_convergence_copy} in that decision probabilities converge to the true and thus test distribution as $n$ increases.
@@
 
-	As \gls{MCE}s are simply trainable conditional embeddings, this framework can incorporated and extended in many ways into techniques that requires appropriately learned kernel embeddings.
+	As \glspl{MCE} are simply trainable conditional embeddings, this framework can incorporated and extended in many ways into techniques that requires appropriately learned kernel embeddings.
 In particular, nonparametric probabilistic inference can be carried out in the RKHS to obtain joint and reverse conditional embeddings, where mode decoding, density recovery, and sampling techniques can lead to effective generative models now that hyperparameters are learned.

### 2017-10-08 AISTATS2018/cake_aistats2018.tex
Edited experiments, conclusion, and most sections. The only thing left is background on RC and the lead up to the RCB main theorem from the appendix. Also need to update appendix

@@
 \newacronym{MMD}{MMD}{maximum mean discrepancy}
+\newacronym{RCB}{RCB}{Rademacher complexity bound}
+\newacronym{OVA}{OVA}{one versus all}
+\newacronym{CNN}{CNN}{convolutional neural network}
 
@@
 			Hyperparameter learning for conditional embeddings is particularly difficult compared to marginal or joint embeddings, since the kernel $k_{\theta}$ with parameters $\theta \in \Theta$ is to be learned jointly with a regularization parameter $\lambda \in \Lambda = \mathbb{R}_{+}$.
-\cite{lever2012conditional} showed that $\mathcal{U} = \hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the solution to the regularized least squares problem in the RKHS from $k(x, \cdot) \in \mathcal{H}_{k}$ to $l(y, \cdot) \mathcal{H}_{l}$,
+\cite{lever2012conditional} showed that $\mathcal{U} = \hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the solution to the regularized least squares problem in the RKHS from $k(x, \cdot) \in \mathcal{H}_{k}$ to $l(y, \cdot) \in \mathcal{H}_{l}$,
 			\begin{equation}
@@
 			When cross validation is too expensive, for many stationary kernels, the length scale parameter can be set by the median heuristic \citep{muandet2016kernel} via $\ell = \mathrm{median}_{i, j}(\| x_{i} - x_{j} \|_{2})$.
-However, they are restricted to length scale parameters only and cannot be used to set other hyperparameters, including $\lambda$.
+However, they are restricted to length scale parameters only and cannot be used to set other hyperparameters, such as $\lambda$.
 In the setting of two sample testing, \cite{gretton2012optimal} also notes that they can possibly lead to poor performance.
@@
 The \gls{MCE} is thus the multi-valued decision function $\bvec{f}(x)$ \eqref{eq:empirical_decision_probability_vector}.
-In fact, each row of the \gls{MCE} is a \gls{KRR} \citep{friedman2001elements} on $\{0, 1\}$-targets.
-We proceed to prove that empirical decision probabilities \eqref{eq:empirical_decision_probability} converge to the true decision probabilities.
-In fact, the inference distribution \eqref{eq:empirical_decision_probability_vector} is equivalent to the empirical conditional embedding.
+In fact, each row of the \gls{MCE} is a \gls{KRR} \citep{friedman2001elements} on binary $\{0, 1\}$-targets.
+As empirical embeddings converges, so do the empirical decision probabilities \eqref{eq:empirical_decision_probability}.
 		\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
@@
 
-		We begin by defining a loss function as a measure for performance.
+		In order to design a hyperparameter learning algorithm that maximizes generalization performance, we begin by defining a loss function as a measure for performance.
 For decision functions of the form $\bvec{f} : \mathcal{X} \to \mathcal{A} = \mathbb{R}^{m}$ whose entries are probability estimates, we employ the cross entropy loss,
@@
 		\end{equation}
-		to express classification risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$.
-Under this loss, we prove that the expected risk for the \gls{MCE} $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a Rademacher complexity bound $r(\theta, \lambda)$ with high probability.
+		to express risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$.
+Under this loss, we prove that the expected risk for the \gls{MCE} $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a \gls{RCB} $r(\theta, \lambda)$ with high probability.
 
@@
 
+	\section{Extensions}
+
 		Our learning algorithm does not restrict the way the kernel $k_{\theta}$ is constructed from its parameters $\theta \in \Theta$.
-One particularly useful class of \gls{MCE}s are those where the input kernel $k_{\theta}(x, x') = \langle \varphi_{\theta}(x), \varphi_{\theta}(x') \rangle$ is constructed from neural networks $\varphi_{\theta} : \mathcal{X} \to \mathbb{R}^{p}$ explicitly.
-We refer to \gls{MCE}s constructed this way as kernel embedding networks (KEN).
-Neural networks are typically defined by weights and biases of its hidden layers, which collectively define the parameters $\theta$ of the constructed kernel, and are thus trainable under our learning algorithm.
+One particularly useful class of \glspl{MCE} are those where the input kernel $k_{\theta}(x, x') = \langle \varphi_{\theta}(x), \varphi_{\theta}(x') \rangle$ is constructed from neural networks $\varphi_{\theta} : \mathcal{X} \to \mathbb{R}^{p}$ explicitly.
+We refer to \glspl{MCE} constructed this way as \glspl{CEN}.
+Similar to the spirit of \cite{wilson2016stochastic} where the neural network weights and biases are learned jointly under the \gls{GP} marginal likelihood objective, \glspl{CEN} also learn network weights and biases under \eqref{eq:learning_objective}.
 These kernels benefit in both scalability and expressibility.
-For large datasets, the $n \times n$ Cholesky decomposition required for full gradient updates in \cref{alg:multiclass_conditional_embedding_training} can be transformed into a $p \times p$ decomposition by the Woodbury matrix inversion identity \citep{higham2002accuracy}.
+For large datasets, the $n \times n$ Cholesky decomposition required for full gradient updates in \cref{alg:multiclass_conditional_embedding_training} can be transformed into a $p \times p$ decomposition by the Woodbury matrix inversion identity \citep{higham2002accuracy}, reducing the time complexity to $O(p^{3} + np^{2})$.
 This allows scalability for $n >> p$ without using stochastic gradient updates so that the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} can be as tight as possible for a given $n$.
+For inference, standard map reduce methods can be used.
 Neural networks are by construction compositional, and thus latent representations of deeper networks undergo more transformations to generate a smaller and explicit collection of expressive nonlinear features, leading to a deeper but narrower model architecture.
@@
 
-	\section{Variations}
-
-	\citep{wilson2016stochastic}
-
-	- CEN and different variations
-	- Linear kernels on top of neural network features would be positive definition but not characteristic.
-However it is often faster to train and the results can be good given a good network architecture
-	% Remember the idea about running datafit section on a validation set
-	- Using a validation batch
-	- Talk about the scaling of the complexity term helps
+		While we simply replaced instantiated $X_{i}$, $Y_{i}$ to be the training observations in \cref{thm:expected_risk_bound_hyperparameter_learning_copy} to obtain \cref{alg:multiclass_conditional_embedding_training}, this does not have to be the case for batch updates.
+Instead, in each learning iteration, we could further split the batch into two sub-batches - one for training and one for validation.
+The training batch is used to form the \gls{MCE} $\bvec{f}_{\theta, \lambda}$ and \gls{RCB} $r(\theta, \lambda)$, while we evaluate the \gls{MCE} on the validation batch,
+		\begin{equation}
+		q^{V}(\theta, \lambda) := \frac{1}{n_{V}} \sum_{i = 1}^{n_{V}} \mathcal{L}_{\epsilon}(y^{V}_{i}, \bvec{f}^{T}_{\theta, \lambda}(x^{V}_{i})) + \tau \; r^{T}(\theta, \lambda),
+		\label{eq:validation_learning_objective}
+		\end{equation}
+		where $(T)$ and $(V)$ denotes training and validation.
+Note that in contrast to standard cross validation, not all data is required for each update due to the presence of the \gls{RCB}.
+Furthermore, although the multiplier on the \gls{RCB} is $4 e$, in practice one can often obtain a tighter bound with a smaller multiplier.
+As such, generalization performance can improve if we uses a multiplier $\tau < 4 e$.
+In practice, these two extensions work well together.
+Intuitively, by introducing a validation batch to measure empirical data fit, a smaller weight on the complexity penalty is required.
 
@@
 
-	\Cref{fig:iris} demonstrates \cref{alg:multiclass_conditional_embedding_training} with full gradient updates ($n_{b} = n$) to learn hyperparameters of the conditional embedding on the two attribute iris dataset.
+		\Cref{fig:iris} demonstrates \cref{alg:multiclass_conditional_embedding_training} with full gradient updates ($n_{b} = n$) to learn hyperparameters of the \gls{MCE} on the two attribute iris dataset.
 The kernel used is isotropic Gaussian with diagonal length scales $\Sigma = \ell^{2} I_{2}$ and sensitivity $\alpha = \sigma_{f}$, so the hyperparameters are $\theta = (\alpha, \ell)$ and $\lambda$.
 We evaluate the performance of the learning algorithm on a withheld test set using 20\% of the available 150 data samples.
-Attributes are scaled into the unit range $[0, 1]$ and decision probability maps are plotted for the region $[-0.5, 1.05]^{2}$, where the red, green, and blue colour channels represent the clip-normalised decision probability \eqref{eq:empirical_decision_probability_clip_normalised} for classes $c = 1, 2, 3$.
+Attributes are scaled into the unit range $[0, 1]$ and decision probability maps are plotted for the region $[-0.5, 1.05]^{2}$, where the red, green, and blue colour channels represent the clip-normalized decision probability \eqref{eq:empirical_decision_probability_clip_normalised} for classes $c = 1, 2, 3$.
 We begin from two initial scenarios, one originally overfitting ($\alpha_{o} = 0.01$, $\ell_{o} = 0.035$, $\lambda_{o} = 10^{-6}$) and another underfitting ($\alpha_{u} = 1$, $\ell_{u} = 1$, $\lambda_{u} = 1$) the training data.
 Initially, both models performs sub-optimally with a test accuracy of 56.67\%.
-We see that the Rademacher complexity bound (RCB) $r(\theta, \lambda)$ appropriately measures the amount of overfitting with $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = 4.33$ and $r((\alpha_{u}, \ell_{u}), \lambda_{u}) = 0.31$.
-We then learn model hyperparameters with \cref{alg:multiclass_conditional_embedding_training} for 500 iterations from both initialisations at rate $\eta = 0.01$, where both models converges to a balanced model with appropriate complexity bounds $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = r((0.01, 0.24), 8.62 \times 10^{-7}) = 2.23 \approx 2.14 = r((\alpha_{u}, \ell_{u}), \lambda_{u}) = r((5.1, 0.24), 0.20)$ and an improved test accuracy of 73.33\%.
-In particular, the initially overfitted model learns a simpler model at the expense of lower training performance, emphasising the benefits of complexity based regularisation, without which the learning would only maximise training performance at the cost of further overfitting.
-Meanwhile, the initially underfitted model learns to trade some complexity away to improve the unflattering performance on the training set.
+We see that the \gls{RCB} $r(\theta, \lambda)$ appropriately measures the amount of overfitting with $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = 4.33$ and $r((\alpha_{u}, \ell_{u}), \lambda_{u}) = 0.31$.
+We then learn hyperparameters with \cref{alg:multiclass_conditional_embedding_training} for 500 iterations from both initializations at rate $\eta = 0.01$, where both models converges to a balanced model with appropriate \glspl{RCB} $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = r((0.01, 0.24), 8.62 \times 10^{-7}) = 2.23 \approx 2.14 = r((\alpha_{u}, \ell_{u}), \lambda_{u}) = r((5.1, 0.24), 0.20)$ and an improved test accuracy of 73.33\%.
+In particular, the initially overfitted model learns a simpler model at the expense of lower training performance, emphasizing the benefits of complexity based regularization, without which the learning would only maximize training performance at the cost of further overfitting.
+Meanwhile, the initially underfitted model learns to increase complexity to improve the unflattering performance on the training set.
 In both scenarios, our learning algorithm improved performance on the test set.
-
-	\gls{CEN}
 
@@
 
-	We demonstrate the average performance of learning anisotropic Gaussian kernels and kernels constructed from neural networks on standard UCI datasets \citep{bache2013uci}, summarised in \cref{tab:uci_experiments}.
+		We demonstrate the average performance of learning anisotropic Gaussian kernels and kernels constructed from neural networks on standard UCI datasets \citep{bache2013uci}, summarized in \cref{tab:uci_experiments}.
 The former has a shallow but wide model architecture, while the latter has a deeper but narrower model architecture.
-The Gaussian kernel is learned with both full (G\gls{MCE}) and batch stochastic gradient updates (G\gls{MCE}-SGD) using a tenth ($n_{b} \approx \frac{n}{10}$) of the training set each training iteration, with sensitivity and length scales initialised to $1$.
-For kernel embedding networks, we randomly select two simple fully connected architectures with 16-32-8 (KEN-1) and 96-32 (KEN-2) hidden units respectively, and learn the conditional embedding without dropout under ReLU activation.
-Biases and standard deviations of zero mean truncated normal distributed weights are initialised to $0.1$, and are to be trained with full gradient updates.
-For all experiments, $\lambda$ is initialised to $1$ and is learned jointly with the kernel.
-Classifiers are trained with the Adam optimiser \citep{kingma2014adam} in TensorFlow \citep{abadi2016tensorflow} with rate $\eta = 0.1$ and $\epsilon = 10^{-15}$ under the learning objective $q(\theta, \lambda)$ \eqref{eq:learning_objective}.
-Training is ran for 1000 epochs, regardless of convergence, for direct comparison.
+The Gaussian kernel is learned with both full (G\gls{MCE}) and batch stochastic gradient updates (G\gls{MCE}-SGD) using a tenth ($n_{b} \approx \frac{n}{10}$) of the training set each training iteration, with sensitivity and length scales initialized to $1$.
+For \glspl{CEN}, we randomly select two simple fully connected architectures with 16-32-8 (\gls{CEN}-1) and 96-32 (\gls{CEN}-2) hidden units respectively, and learn the conditional embedding without dropout under ReLU activation.
+Biases and standard deviations of zero mean truncated normal distributed weights are initialized to $0.1$, and are to be learned with full gradient updates.
+For all experiments, $\lambda$ is initialized to $1$ and is learned jointly with the kernel.
+Optimization is performed with the Adam optimizer \citep{kingma2014adam} in TensorFlow \citep{abadi2016tensorflow} with rate $\eta = 0.1$ and $\epsilon = 10^{-15}$ under the learning objective $q(\theta, \lambda)$ \eqref{eq:learning_objective}.
+Learning is ran for 1000 epochs, regardless of convergence, for direct comparison.
 All attributes are scaled to the unit range.
-Each classifier is trained on 9 out of 10 folds and tested on the remaining fold, which are shuffled over all 10 combinations to obtain the test accuracy average and deviation.
-We compare our results to other approaches using neural networks \citep[a; c]{kaya2016banknote, freire2009short}, probabilistic binary trees \citep[b]{horton1996probabilistic}, decision trees \citep[d]{zhou2004size}, and regularised discriminant analysis \citep[e]{aeberhard1992comparison}.
-\Cref{tab:uci_experiments} shows that our learning algorithm achieves similar performance without any special tuning or heuristics, but by simply placing a conditional embedding on training data and applying a complexity bound based learning algorithm.
+Each model is trained on 9 out of 10 folds and tested on the remaining fold, which are shuffled over all 10 combinations to obtain the test accuracy average and deviation.
+We compare our results to \glspl{MCE} whose hyperparameters are tuned by \gls{ERM}, cross validation (CV), and the median heuristic (MED), as well as to other approaches using neural networks \citep[a; c]{kaya2016banknote, freire2009short}, probabilistic binary trees \citep[b]{horton1996probabilistic}, decision trees \citep[d]{zhou2004size}, and regularised discriminant analysis \citep[e]{aeberhard1992comparison}.
+\Cref{tab:uci_experiments} shows that our learning algorithm outperforms other hyperparameter tuning algorithms, and performs similarly to competing methods.
+Our method achieves this without any special tuning or heuristics, but by simply placing a conditional embedding on training data and applying a complexity bound based learning algorithm.
 The stochastic gradient approach for Gaussian kernels performs similarly to the full gradient approach, supporting \cref{thm:expected_risk_bound_hyperparameter_learning_copy} for $n = n_{b}$.
-For kernel embedding networks, we did not attempt to choose an optimal architecture for each dataset.
-The learning algorithm is to train the same simple untrained network for different datasets under only 1000 iterations, and still generates comparable performance.
+For \glspl{CEN}, we did not attempt to choose an optimal architecture for each dataset.
+The learning algorithm is to train the same simple untrained network for different datasets under only 1000 epochs, and still generates comparable performance.
 
@@
 		We apply \cref{alg:multiclass_conditional_embedding_training} to learn anisotropic length scales of Gaussian kernels on pixels of the MNIST digits dataset \citep{lecun1998gradient}.
-We first demonstrate the test performance of \gls{MCE}s as the training set increases in size, verifying \cref{thm:probability_convergence_copy} in that decision probabilities converge to the true and thus test distribution as $n$ increases.
-In the top left plot of \cref{fig:mnist_experiments}, we train on datasets of varying sizes, from 50 to 5000 samples, and benchmark performance on the standard test set of 10000 examples.
-All hyperparameters are initialised to 1 before training.
-For each $n$, we see that \gls{MCE}s outperform SVCs, since SVCs are unable to learn the length scales of the Gaussian kernel.
-This also shows that \gls{MCE}s perform very well with small datasets even when $n < d$.
-The MNIST dataset has $d = 28^{2} = 784$ pixel dimensions, yet with only $n = 50, 150, 250$ training samples, the \gls{MCE} achieves a test accuracy of 45.7\%, 70.09\%, and 79.37\% respectively, compared to 18.13\%, 37.43\%, and 53.81\% from SVCs.
-We also compare training under the learning objective with and without the Rademacher complexity bound.
+In the top left plot of \cref{fig:mnist_experiments}, we train on datasets of varying sizes, from 50 to 5000 images, and benchmark performance on the standard test set of 10000 images.
+All hyperparameters are initialized to 1 before learning.
+We train both \glspl{SVC} and \glspl{GPC} under the \gls{OVA} scheme, and use a Laplace approximation for the \gls{GPC} posterior.
+In all cases, \glspl{MCE} outperform \glspl{SVC}, as standard \gls{SVC} training cannot learn hyperparameters unless expensive cross validation is performed.
+\glspl{MCE} also outperform \glspl{GPC} as more data becomes available.
+Under the \gls{OVA} scheme, a set of kernel hyperparameters are learned to distinguish each class against the rest, while for our algorithm learns a consistent set of hyperparameters for all classes.
+Consequently, for 5000 data points, the computational time required for hyperparameter learning of standard \glspl{GPC} is on the order of days, while \cref{alg:multiclass_conditional_embedding_training} is on the order of hours even without batch updates.
+We also compare hyperparameter learning with and without the \gls{RCB}.
 For small $n$ below 750 samples, the latter outperforms the former (e.g.
@@
 96.05\% and 95.3\% for $n= 5000$).
-This verifies that complexity based regularisation becomes especially important when data size grows, where overfitting starts to hurt generalisation performance.
-Our bound is also tighter with larger $n$, so that generalisation performance improves with more data.
-The images at the bottom of \cref{fig:mnist_experiments} show the pixel length scales learned through batch stochastic gradient updates ($n_{b} = 1200$) on all available training images of the digits indicated, demonstrating the most discriminative regions for classification.
-In particular, the most discriminative regions are usually around the edges of the digits, subject to slight intraclass translations.
+This verifies that complexity based regularization becomes especially important as data size grows, when overfitting starts to hurt generalization performance.
+Our bound is also tighter with larger $n$, so that generalization performance improves with more data.
+The images at the bottom of \cref{fig:mnist_experiments} show the pixel length scales learned through batch stochastic gradient updates ($n_{b} = 1200$) on all available training images of different groups of digits, demonstrating the most discriminative regions for classification.
+%In particular, the most discriminative regions are usually around the edges of the digits, subject to slight intraclass translations.
+
+		% % % Removed sentences
+		% We first demonstrate the test performance of \glspl{MCE} as the training set increases in size, verifying \cref{thm:probability_convergence_copy} in that decision probabilities converge to the true and thus test distribution as $n$ increases.
+		% The MNIST dataset has $d = 28^{2} = 784$ pixel dimensions, yet with only $n = 50, 150, 250$ training samples, the \gls{MCE} achieves a test accuracy of 45.7\%, 70.09\%, and 79.37\% respectively, compared to 18.13\%, 37.43\%, and 53.81\% from SVCs.
 
@@
 			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_0123456789_batch_1200.eps}
-		\caption{Top: Test accuracy and cross entropy loss by learning Gaussian kernels (left) and deep convolutional features (right). Bottom: Learned pixel length scales under Gaussian kernels.}
+			\caption{Top: Test accuracy by learning Gaussian kernels (left) and deep convolutional features (right). Bottom: Learned pixel length scales under anistropic Gaussian (ARD) kernels.}
 			\label{fig:mnist_experiments}
@@
 
-	We now apply our learning algorithm to train convolutional neural networks (CNN) on the MNIST dataset.
+		We now apply our learning algorithm to train \gls{CNN} on the MNIST dataset.
 We employ an example architecture from the TensorFlow tutorial on deep MNIST classification \citep{abadi2016tensorflow}.
@@
 The original network then employs a final softmax regressor on the last hidden layer for classification.
-The kernel embedding network instead employs a linear kernel on the last hidden layer to construct the conditional embedding.
-We then train both networks from the same initialisation with stochastic gradient updates using $n_{b} = 6000$ images at a time for 800 epochs, with learning rate $\eta = 0.01$.
-All biases and standard deviations of zero mean truncated normal distributed weights are initialised to 0.1.
-The convolutional features of the kernel embedding network are trained jointly with the regularisation parameter, initialised to $\lambda = 10$, under our proposed learning objective \eqref{eq:learning_objective}, while the original CNN is trained under its usual cross entropy loss.
+The \gls{CEN} instead employs a linear kernel on the last hidden layer to construct the conditional embedding.
+We then train both networks from the same initialization with batch updates using $n_{b} = 6000$ images at a time for 800 epochs, with learning rate $\eta = 0.01$.
+All biases and standard deviations of zero mean truncated normal distributed weights are initialized to 0.1.
+The network weights and biases of the \gls{CEN} are learned jointly with the regularization parameter, initialized to $\lambda = 10$, under our learning objective \eqref{eq:learning_objective}, while the original \gls{CNN} is trained under its usual cross entropy loss.
 The fully connected layer is trained with a drop out probability of 0.5 for both cases to allow direct comparison.
-The top right plot in \cref{fig:mnist_experiments} shows that kernel embedding networks learn convolutional features at a much faster rate, maintaining a higher test accuracy at all epochs.
-After 800 epochs, our convolutional kernel embedding network reaches a test accuracy of 99.48\%, compared to 99.26\% from the original CNN.
-This demonstrates that our learning algorithm can perform end-to-end learning with convolutional features from scratch, by simply placing a conditional embedding on a neural network.
-The resulting classifier can outperform the original neural network in both convergence rate and accuracy.
+The top right plot in \cref{fig:mnist_experiments} shows that \glspl{CEN} learns at a much faster rate, maintaining a higher test accuracy at all epochs.
+After 800 epochs, \gls{CEN} reaches a test accuracy of 99.48\%, compared to 99.26\% from the original \gls{CNN}.
+This demonstrates that our learning algorithm can perform end-to-end learning with \glspl{CNN} from scratch, by simply replacing the softmax layer with an \gls{MCE}.
+The resulting \gls{CEN} can outperform the original \gls{CNN} in both convergence rate and accuracy.
 
@@
 
-	We propose a hyperparameter learning framework for conditional embeddings when the target is discrete.
-This naturally results in a nonparametric probabilistic multiclass classifier whose convergence properties can be guaranteed.
-Because nonparametric models have infinite capacity and can potentially overfit, we propose learning-theoretic bounds to regularise the conditional embedding in a way that minimises expected classification risk.
-The resulting bound justifies the use of stochastic gradient updates for hyperparameter learning, which we verify experimentally on standard UCI datasets.
-The \gls{MCE} is also inherently flexible in architecture, and in particular can perform end-to-end learning on a neural network, which we demonstrate on UCI datasets and MNIST digits, where it outperforms the original convolutional neural network in the latter.
+		We propose a scalable hyperparameter learning framework for \glspl{MCE}.
+Because nonparametric models have infinite capacity and can potentially overfit, we derive learning-theoretic bounds to regularize the \gls{MCE} in a way that minimizes expected generalization risk.
+The resulting bound justifies the use of stochastic gradient updates for hyperparameter learning, which we verify experimentally.
+Our algorithm does not impose restrictions to the form of the positive definite kernel, and in particular can perform end-to-end learning on a neural network by replacing the softmax layer with a \gls{MCE}, which we demonstrate on UCI datasets and MNIST digits, where it outperforms the original convolutional neural network in the latter.
 
-	As \glspl{MCE} are simply trainable conditional embeddings, this framework can incorporated and extended in many ways into techniques that requires appropriately learned kernel embeddings.
-In particular, nonparametric probabilistic inference can be carried out in the RKHS to obtain joint and reverse conditional embeddings, where mode decoding, density recovery, and sampling techniques can lead to effective generative models now that hyperparameters are learned.
+		This framework can incorporated and extended in many ways into techniques that requires appropriately learned conditional embeddings.
+In particular, nonparametric probabilistic inference can be carried out in the \gls{RKHS} to obtain joint and reverse conditional embeddings, where mode decoding, density recovery, and sampling techniques can lead to effective generative models now that hyperparameters are learned.
 This line of approach can potentially lead to Bayesian extensions to our framework.
 We also envision a semi-supervised and one class extension to the \gls{MCE} framework that can relax supervision in training.
-Moreover, instead of a Kronecker delta kernel, target label kernels with non-zero and potentially trainable similarities between distinct labels may capture label correlations better than our original framework.
+Moreover, instead of a Kronecker delta kernel, kernels in the label space with non-zero and potentially learnable similarities between distinct labels may capture label correlations better than our original framework.
 Finally, our framework and algorithm is simple, and developments in establishing deeper connections and relationships with other kernel based models can be fruitful.

### 2017-10-08 AISTATS2018/cake_aistats2018.tex
Should be done with background on RC. Just need the lead up to the RCB main theorem from appendix and update the appendix

@@
 
-			The Rademacher complexity \citep{bartlett2002rademacher} measures the expressiveness of a function class $F$ by its ability to shatter, or fit, noise.
-They are data-dependent measures, and are thus particularly well suited to learning tasks where generalisation ability is vital, since complexity penalties that are not data dependent cannot be universally effective \citep{kearns1997experimental}.
+			Rademacher complexity \citep{bartlett2002rademacher} measures the expressiveness of a function class $F$ by its ability to shatter, or fit, noise.
+They are data-dependent measures, and are thus particularly well suited to learning tasks where generalization is vital, since complexity penalties that are not data dependent cannot be universally effective \citep{kearns1997experimental}.
 
-	%		For a linear class of predictors parametrised as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularisation to bound the Rademacher complexity, achieving tight generalisation bounds in the context of multi-label learning.
-The \gls{MCE} predictor \eqref{eq:empirical_decision_probability_vector} has the same linear form in the feature space, $\bvec{f}_{\theta, \lambda}(x) = \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \Phi_{\theta}^{T} \phi_{\theta}(x) = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$, where instead of learning the operator $W^{T}$ directory, we learn hyperparameters $\theta \in \Theta, \lambda \in \Lambda$ for the empirical conditional embedding map $\mathcal{U}^{(\theta, \lambda)}_{Y | X}$ and thus also the features $\phi_{\theta}(x)$.
-\cite{xu2016local} extends the trace norm regularisation approach by considering the local Rademacher complexity on a subset of the predictor class, where they instead minimise the tail sum of the predictor singular values.
-In the proof of \cref{thm:expected_risk_bound_hyperparameter_learning_copy}, $\theta \in \Theta$ and $\lambda \in \Lambda$ define subsets of $\Theta$ and $\Lambda$ where the Rademacher complexity is considered over.
+			In many cases, learning is usually done by minimizing some empirical loss over a class of models whose Rademacher complexity is bounded.
+For a linear class of predictors parametrized as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularization to bound the Rademacher complexity, achieving tight generalization bounds in the context of multi-label learning.
+\cite{xu2016local} extends the trace norm regularization approach by considering the local Rademacher complexity on a subset of the predictor class, where they instead minimize the tail sum of the predictor singular values.
+Local Rademacher complexity has also been employed for multiple kernel learning \citep{kloft2011local, cortes2013learning} to learn convex combinations of simpler preselected kernels for \glspl{SVC}.
+Similarly, \cite{pontil2013excess} also used trace norm regularization to bound the Rademacher complexity and minimizes the truncated hinge loss.
+Nevertheless, while Rademacher complexities have been employed to restrict the function class considered for learning weight parameters of linear models, they are usually not minimized along with the loss and have not yet been applied to learn hyperparameters.
+
+			% The \gls{MCE} predictor \eqref{eq:empirical_decision_probability_vector} has the same linear form in the feature space, $\bvec{f}_{\theta, \lambda}(x) = \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \Phi_{\theta}^{T} \phi_{\theta}(x) = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$, where instead of learning the operator $W^{T}$ directory, we learn hyperparameters $\theta \in \Theta, \lambda \in \Lambda$ for the empirical conditional embedding map $\mathcal{U}^{(\theta, \lambda)}_{Y | X}$ and thus also the features $\phi_{\theta}(x)$.
+
+			% In the proof of \cref{thm:expected_risk_bound_hyperparameter_learning_copy}, $\theta \in \Theta$ and $\lambda \in \Lambda$ define subsets of $\Theta$ and $\Lambda$ where the Rademacher complexity is considered over.
 By minimising $q(\theta, \lambda)$, we shrink the subset being considered, achieving localised Rademacher complexity based feature learning without selecting parameters that define the tail sum.
-Local Rademacher complexity has also been employed for multiple kernel learning \citep{kloft2011local, cortes2013learning} to learn convex combinations of simpler preselected kernels for a support vector machine.
-We extend its application to the probabilistic multiclass case, and use Rademacher complexity bounds to learn any general kernel for a conditional embedding.
 
-	- Difference between both \citep{rifkin2003regularized} and \citep{pahikkala2012unsupervised} is the loss function used and natural multiclass formulation and what we are optimising over (not the weights directly but the hyperparameter of the weights).
-	- Two problems: Hyperparam learning and pre-image
-	- By restricting it to discrete, pre-image is fine
-	- Then we propose hyperparam learning?
+%	- Two problems: Hyperparam learning and pre-image
+%	- By restricting it to discrete, pre-image is fine
+%	- Then we propose hyperparam learning?
 
@@
 As $\delta$ is an integrally strictly positive definite kernel on $\mathbb{N}_{m}$, it is therefore characteristic \citep[Theorem 7]{sriperumbudur2010hilbert}.
-As such, by definition of characteristic kernels \citep{fukumizu2004dimensionality}, $\delta$ uniquely defines a RKHS  $\mathcal{H}_{\delta} = \overline{\mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}}$, which is the closure of the span of its kernel induced features \citep{xu2009refinement}.
-For $\mathcal{Y} = \mathbb{N}_{m}$, this means that any real-valued function $g : \mathbb{N}_{m} \to \mathbb{R}$ that is bounded on its discrete domain $\mathbb{N}_{m}$ is in the RKHS of $\delta$, because we can always write $g = \sum_{y = 1}^{m} g(y) \delta(y, \cdot) \in \mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}$.
-In particular, indicator functions on $\mathbb{N}_{m}$ are in the RKHS $\mathcal{H}_{\delta}$, since
-		\begin{equation}
-		\mathbb{1}_{c}(y) := \mathbb{1}_{\{c\}}(y) := \begin{cases}
-		1 & \mathrm{if } \quad y \in \{c\} \\
-		0 & \mathrm{otherwise}
-		\end{cases} = \delta(c, y).
-		\label{eq:indicator_function}
-		\end{equation}
+As such, by definition \citep{fukumizu2004dimensionality}, $\delta$ uniquely defines a \gls{RKHS}  $\mathcal{H}_{\delta} = \overline{\mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}}$, which is the closure of the span of its kernel induced features \citep{xu2009refinement}.
+For $\mathcal{Y} = \mathbb{N}_{m}$, this means that any $g : \mathbb{N}_{m} \to \mathbb{R}$ that is bounded on its discrete domain $\mathbb{N}_{m}$ is in the \gls{RKHS} of $\delta$, because we can always write $g = \sum_{y = 1}^{m} g(y) \delta(y, \cdot) \in \mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}$.
+In particular, indicator functions on $\mathbb{N}_{m}$ are in $\mathcal{H}_{\delta}$, since $\mathbb{1}_{c}(y) := \mathbb{1}_{\{c\}}(y) = \delta(c, y)$.
+%		\begin{equation}
+%		\mathbb{1}_{c}(y) := \mathbb{1}_{\{c\}}(y) := \begin{cases}
+%		1 & \mathrm{if } \quad y \in \{c\} \\
+%		0 & \mathrm{otherwise}
+%		\end{cases} = \delta(c, y).
+%		\label{eq:indicator_function}
+%		\end{equation}
 		That is, indicator functions $\mathbb{1}_{c} = \delta(c, \cdot)$, $c \in \mathbb{N}_{m}$, are simply the canonical features of $\mathcal{H}_{\delta}$.
 Such properties do not necessarily hold for continuous domains in general.
-This convenient property in the case of a discrete domain $\mathcal{Y}$ with a Kronecker delta kernel $\delta$ is what allows consistent estimations of decision probabilities in multiclass settings.
+This convenient property in the case of a discrete domain is what allows consistent estimations of decision probabilities in multiclass settings.
 In fact, $\mathcal{H}_{\delta}$ can be identified with $\mathbb{R}^{m}$.
@@
 
+		Similar to \gls{RLSC}, \glspl{MCE} are solutions to a regularized least squares problem in a \gls{RKHS} \citep{lever2012conditional}, resulting in a similar system of linear equations.
+\glspl{RLSC} primarily differ in the way they handle the labels, in which binary labels $\{-1, 1\}$ appear directly in the squared loss instead of its kernel representation $\delta(y_{i}, \cdot)$ or, equivalently, its one hot encoded form $\bvec{y}_{i}$.
+Consequently, multiclass extensions for \gls{RLSC} either require using the \gls{OVA} scheme \citep{rifkin2003regularized}, or minimizing the summed losses across all binarized tasks instead \citep{pahikkala2012unsupervised}, producing separate classifiers for each class.
+As a result, multiclass \gls{RLSC} do not produce consistent estimates of class probabilities as in \cref{thm:probability_convergence_copy} for \glspl{MCE}.
+This property allows us to employ a probabilistic loss over the output of \glspl{MCE} to learn its hyperparameters, which is known to be difficult to tune in the case of \gls{RLSC} \citep{pahikkala2012unsupervised}.
+However, simply minimizing the empirical loss could lead to overfitting due to the flexibility of the nonparametric model.
+It is therefore essential to control the model complexity of \glspl{MCE}, which we turn to next.
+
 	\section{Hyperparameter Learning with Rademacher Complexity Bounds}
@@
 
-		In order to design a hyperparameter learning algorithm that maximizes generalization performance, we begin by defining a loss function as a measure for performance.
+		\begin{algorithm*}[tb]
+			\caption{\gls{MCE} Hyperparameter Learning with Batch Stochastic Gradient Updates}
+			\label{alg:multiclass_conditional_embedding_training}
+			\begin{algorithmic}[1]
+				\STATE {\bfseries Input:} kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial kernel parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
+				\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
+				\REPEAT
+				\STATE Sample the next batch $\mathcal{I}_{b} \subseteq \mathbb{N}_{n}$, $| \mathcal{I}_{b} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I}_{b} = \mathbb{N}_{n}$)
+				\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}_{b}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
+				\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathcal{I}_{b}, j \in \mathcal{I}_{b}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
+				\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n_{b} \lambda I_{n_{b}}) \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
+				\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Y) \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
+				\STATE $P_{\theta, \lambda} \leftarrow K_{\theta} V_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
+				\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n_{b}} \sum_{i = 1}^{n_{b}} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
+				\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
+				\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial q}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial q}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
+				\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
+			\end{algorithmic}
+		\end{algorithm*}
+
+		In order to design a hyperparameter learning algorithm that maximizes generalization performance without overfitting, we begin by defining a loss function as a measure for performance.
 For decision functions of the form $\bvec{f} : \mathcal{X} \to \mathcal{A} = \mathbb{R}^{m}$ whose entries are probability estimates, we employ the cross entropy loss,
@@
 		to express risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$.
+Note that we employ the loss on the raw probability estimates \eqref{eq:empirical_decision_probability_vector}, not the clipped version \eqref{eq:empirical_decision_probability_clip_normalised}.
 Under this loss, we prove that the expected risk for the \gls{MCE} $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a \gls{RCB} $r(\theta, \lambda)$ with high probability.
@@
 
-		\begin{algorithm*}[tb]
-			\caption{\gls{MCE} Hyperparameter Learning with Batch Stochastic Gradient Updates}
-			\label{alg:multiclass_conditional_embedding_training}
-			\begin{algorithmic}[1]
-				\STATE {\bfseries Input:} kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial kernel parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
-				\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
-				\REPEAT
-				\STATE Sample the next batch $\mathcal{I}_{b} \subseteq \mathbb{N}_{n}$, $| \mathcal{I}_{b} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I}_{b} = \mathbb{N}_{n}$)
-				\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}_{b}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
-				\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathcal{I}_{b}, j \in \mathcal{I}_{b}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
-				\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n_{b} \lambda I_{n_{b}}) \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
-				\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Y) \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-				\STATE $P_{\theta, \lambda} \leftarrow K_{\theta} V_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-				\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n_{b}} \sum_{i = 1}^{n_{b}} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
-				\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
-				\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial q}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial q}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
-				\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
-			\end{algorithmic}
-		\end{algorithm*}
+	\section{Extensions}
 
-	\section{Extensions}
+		\begin{figure*}[t]
+			\centering
+			\includegraphics[width=0.32\linewidth]{figures/iris_overfitted_model.eps}
+			\includegraphics[width=0.32\linewidth]{figures/iris_balanced_model.eps}
+			\includegraphics[width=0.32\linewidth]{figures/iris_underfitted_model.eps}
+			\includegraphics[width=0.48\linewidth]{figures/iris_rademacher_complexity_bound_lower_legend.eps}
+			%		\includegraphics[width=0.48\linewidth]{figures/iris_cross_entropy_loss.eps}
+			\includegraphics[width=0.48\linewidth]{figures/iris_accuracy.eps}
+			\caption{Rademacher complexity balanced learning of hyperparameters for an isotropic Gaussian \gls{MCE}, using the first two attributes of the iris dataset.}
+			\label{fig:iris}
+		\end{figure*}
 
@@
 	\paragraph{Toy Example}
-
-		\begin{figure*}[t]
-			\centering
-			\includegraphics[width=0.32\linewidth]{figures/iris_overfitted_model.eps}
-			\includegraphics[width=0.32\linewidth]{figures/iris_balanced_model.eps}
-			\includegraphics[width=0.32\linewidth]{figures/iris_underfitted_model.eps}
-			\includegraphics[width=0.48\linewidth]{figures/iris_rademacher_complexity_bound_lower_legend.eps}
-	%		\includegraphics[width=0.48\linewidth]{figures/iris_cross_entropy_loss.eps}
-			\includegraphics[width=0.48\linewidth]{figures/iris_accuracy.eps}
-			\caption{Rademacher complexity balanced learning of hyperparameters for an isotropic Gaussian \gls{MCE}, using the first two attributes of the iris dataset.}
-			\label{fig:iris}
-		\end{figure*}
 
@@
 Each model is trained on 9 out of 10 folds and tested on the remaining fold, which are shuffled over all 10 combinations to obtain the test accuracy average and deviation.
-We compare our results to \glspl{MCE} whose hyperparameters are tuned by \gls{ERM}, cross validation (CV), and the median heuristic (MED), as well as to other approaches using neural networks \citep[a; c]{kaya2016banknote, freire2009short}, probabilistic binary trees \citep[b]{horton1996probabilistic}, decision trees \citep[d]{zhou2004size}, and regularised discriminant analysis \citep[e]{aeberhard1992comparison}.
+We compare our results to \glspl{MCE} whose hyperparameters are tuned by \gls{ERM} (without the \gls{RCB} term in \eqref{eq:learning_objective}), cross validation (CV), and the median heuristic (MED), as well as to other approaches using neural networks \citep[a; c]{kaya2016banknote, freire2009short}, probabilistic binary trees \citep[b]{horton1996probabilistic}, decision trees \citep[d]{zhou2004size}, and regularised discriminant analysis \citep[e]{aeberhard1992comparison}.
 \Cref{tab:uci_experiments} shows that our learning algorithm outperforms other hyperparameter tuning algorithms, and performs similarly to competing methods.

### 2017-10-08 AISTATS2018/cake_aistats2018.tex
Starting to update the appendix now before adding the lead up

@@
 
-%			We begin by providing an overview of Hilbert space embeddings, where probability distributions are represented by mean embeddings in a reproducing kernel Hilbert space (RKHS) through positive definite kernels.
-Specifically, in the supervised learning context for which we are primarily interested in, we focus on conditional distributions and its representations in the RKHS.
-
 			To construct a conditional embedding operator $\mathcal{U}_{Y | X}$ corresponding to the distribution $\mathbb{P}_{Y | X}$, where $X : \Omega \to \mathcal{X}$ and $Y: \Omega \to \mathcal{Y}$ are measurable random variables, we first choose a kernel $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ for the input space $\mathcal{X}$ and another kernel $l : \mathcal{Y} \times \mathcal{Y} \to \mathbb{R}$ for the output space $\mathcal{Y}$.
@@
 In this case, $C_{YX} C_{XX}^{-1}$ becomes only an approximation to $\mathcal{U}_{Y | X}$, and we instead regularize the inversion and use $\mathcal{U}_{Y | X} = C_{YX} (C_{XX} + \lambda I)^{-1}$, which also serves to avoid overfitting \citep{song2013kernel}.
-\glspl{CME} are useful as for probabilistic inference as conditional expectations of a function $g \in \mathcal{H}_{l}$ can be expressed as inner products, $\mathbb{E}[g(Y) | X = x] = \langle \mu_{Y | X = x}, g \rangle$, provided $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$, \citet[Theorem 4]{song2009hilbert}.
+\glspl{CME} are useful for probabilistic inference as conditional expectations of a function $g \in \mathcal{H}_{l}$ can be expressed as inner products, $\mathbb{E}[g(Y) | X = x] = \langle \mu_{Y | X = x}, g \rangle$, provided $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$, \citet[Theorem 4]{song2009hilbert}.
 
@@
 
+			% % % Removed sentences
 			% The \gls{MCE} predictor \eqref{eq:empirical_decision_probability_vector} has the same linear form in the feature space, $\bvec{f}_{\theta, \lambda}(x) = \bvec{Y}^{T} (K_{\theta} + n \lambda I)^{-1} \Phi_{\theta}^{T} \phi_{\theta}(x) = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \phi_{\theta}(x)$, where instead of learning the operator $W^{T}$ directory, we learn hyperparameters $\theta \in \Theta, \lambda \in \Lambda$ for the empirical conditional embedding map $\mathcal{U}^{(\theta, \lambda)}_{Y | X}$ and thus also the features $\phi_{\theta}(x)$.
@@
 By minimising $q(\theta, \lambda)$, we shrink the subset being considered, achieving localised Rademacher complexity based feature learning without selecting parameters that define the tail sum.
-
-%	- Two problems: Hyperparam learning and pre-image
-%	- By restricting it to discrete, pre-image is fine
-%	- Then we propose hyperparam learning?
-
-	%From my literature review last year, the two primary challenges I identified within the kernel embeddings community are:
-	%
-	%- Hyperparameter Learning: How can we learn the hyperparameters of kernel embeddings in a principled manner that improves generlisation? And,
-	%- Pre-Image: How can we get back the distribution in probability space after we have embedded them into the Hilbert space?
-	%
-	%These problems have been heavily investigated for marginal embeddings. In January, by restricting the target of a conditional embedding to be discrete.
 

### 2017-10-11 AISTATS2018/cake_aistats2018.tex
Version before major revision

@@
 \newacronym{KRR}{KRR}{kernel ridged regressor}
-\newacronym{RLSC}{RLSC}{regularized least squares classification}
+\newacronym{RLSC}{RLSC}{regularized least squares classifier}
 \newacronym{ERM}{ERM}{empirical risk minimization}
@@
 \newacronym{CNN}{CNN}{convolutional neural network}
+\newacronym{ARD}{ARD}{automatic relevance determination}
+\newacronym{HS}{HS}{Hilbert-Schmidt}
 
@@
 
-	\aistatstitle{Hyperparameter Learning for Multiclass Conditional Embeddings \\ with Rademacher Complexity Bounds}
+	\aistatstitle{Hyperparameter Learning for Conditional Mean Embeddings \\ with Rademacher Complexity Bounds}
 
@@
 		How can we design a scalable learning objective for learning kernel hyperparameters of conditional mean embeddings?
-Conditional mean embeddings are nonparametric models that encodes conditional distributions in a reproducing kernel Hilbert space directly through observed data, resulting in a flexible and powerful framework for probabilistic inference.
+Conditional mean embeddings are nonparametric models that encode conditional expectations in a reproducing kernel Hilbert space directly through observed data, resulting in a flexible and powerful framework for probabilistic inference.
 However, their performance is greatly dependent on the choice of kernel hyperparameters and regularization, yet current approaches for hyperparameter tuning predominantly rely on cross validation and distance based heuristics.
-For conditional mean embeddings with multiclass targets but arbitrary inputs, we propose a hyperparameter learning framework based on Rademacher complexity bounds to prevent overfitting by balancing datafit against model complexity.
+For conditional mean embeddings with categorical targets but arbitrary inputs, we propose a hyperparameter learning framework based on Rademacher complexity bounds to prevent overfitting by balancing data fit against model complexity.
 The approach only requires batch updates, allowing scalable kernel learning without kernel approximations.
-Experiments demonstrate that our framework outperforms standard cross validation and heuristics, and can be further extended to incorporate and learn neural network weights to improve generalization.
+Experiments demonstrate that our framework outperforms standard cross validation, and can be further extended to incorporate and learn neural network weights improving generalization.
 
@@
 They are part of a broader class of models known as kernel embeddings, where nonparametric probabilistic inference can be carried out entirely within the \gls{RKHS} because difficult marginalization integrals become simple linear algebra \citep{muandet2016kernel}.
-This very general framework is core to modern kernel probabilistic methods, including kernel two-sample testing \citep{gretton2007kernel}, kernel Bayesian inference  \citep{fukumizu2013kernel}, nonparametric density estimation \citep{song2008tailoring, kanagawa2014recovering}, domain-invariant component analysis \citep{muandet2013domain}, dimensionality reduction \citep{fukumizu2004dimensionality}, feature discovery \citep{jitkrittum2016interpretable}, and state space filtering \citep{kanagawa2016filtering}.
+This very general framework is core to modern kernel probabilistic methods, including kernel two-sample testing \citep{gretton2007kernel}, kernel Bayesian inference  \citep{fukumizu2013kernel}, density estimation \citep{song2008tailoring, kanagawa2014recovering}, component analysis \citep{muandet2013domain}, dimensionality reduction \citep{fukumizu2004dimensionality}, feature discovery \citep{jitkrittum2016interpretable}, and state space filtering \citep{kanagawa2016filtering}.
 
@@
 		% % In this paper, we focus on a rarely investigated form of the CME...
-		\Glspl{MCE} are \glspl{CME} with discrete targets but arbitrary inputs, where on top of conditional expectations we can further infer conditional probabilities.
-As such, they are widely applicable to probabilistic inference in multiclass settings and learning probabilistic representations between arbitrary inputs and a discrete set of actions or outcomes.
-Unlike \glspl{SVM} \citep{scholkopf2002learning}, \glspl{GPC} \citep{rasmussen2006gaussian}, and multiclass \glspl{RLSC} \citep{rifkin2003regularized, pahikkala2012unsupervised}, \Glspl{MCE} do not require separately fitting binary classifiers for each class or each pair of classes for a final multiclass prediction.
-Instead, a single conditional embedding is sufficient for producing consistent multiclass probabilistic estimates.
+		For \glspl{CME} with categorical targets but arbitrary inputs, we can further infer conditional probabilities directly, and not just conditional expectations.
+As there can be more than two categories, we refer to these \glspl{CME} as \glspl{MCE} in this paper.
+In contrast, \glspl{SVM} \citep{scholkopf2002learning} do not naturally produce probabilities, while \glspl{GPC} \citep{rasmussen2006gaussian} require posterior approximations.
+As such, \glspl{MCE} are widely applicable to probabilistic inference in multiclass settings with categorical targets.
+Unlike \glspl{SVM}, \glspl{GPC}, and multiclass \glspl{RLSC} \citep{rifkin2003regularized, pahikkala2012unsupervised}, \glspl{MCE} do not require separately fitting multiple binary classifiers to obtain a final prediction.
+Instead, a single \gls{MCE} is sufficient for producing consistent multiclass probabilistic estimates.
 
@@
 
-		One notable success story in this domain are \gls{GPs} \citep{rasmussen2006gaussian}, which has long enjoyed the well celebrated marginal likelihood for hyperparameter learning.
-The marginal likelihood arises naturally from the Bayesian formulation of the model, and exhibits certain desirable properties -- in particular, the ability to automatically balance between data fit and model complexity.
+		One notable success story in this domain are \gls{GPs} \citep{rasmussen2006gaussian}, which have long enjoyed the well celebrated marginal likelihood for hyperparameter learning.
+The marginal likelihood arises naturally from the Bayesian formulation of \gls{GPs}, and exhibits certain desirable properties -- in particular, the ability to automatically balance between data fit and model complexity.
 On the other hand, \glspl{CME} are not necessarily Bayesian, and hence they do not benefit from a natural marginal likelihood formulation, yet such a balance is critical when generalizing the model beyond unseen examples.
@@
 In this paper, we present such a learning objective as our main contribution.
-In particular, we 1) derive a measure of model complexity for a specific \gls{MCE} based on the Rademacher complexity of a relevant class of \glspl{MCE}, 2) formulate a novel learning objective based on this complexity measure to control expected generalization risk by balancing data fit against model complexity, and 3) propose a scalable hyperparameter learning algorithm under this objective using batch updates.
-We show that this learning objective produces \glspl{MCE} that generalizes better than that learned from cross validation, \gls{ERM}, and median length heuristics on standard benchmarks, and apply such an algorithm to incorporate and learn neural network weights to improve generalization accuracy on the MNIST dataset.
+In particular, we (1) derive a measure of model complexity for a specific \gls{MCE} based on the Rademacher complexity of a relevant class of \glspl{MCE}, (2) formulate a novel learning objective based on this complexity measure to control expected generalization risk by balancing data fit against model complexity, and (3) propose a scalable hyperparameter learning algorithm under this objective using batch updates.
+We show that this learning objective produces \glspl{MCE} that generalizes better than that learned from cross validation, \gls{ERM}, and median length heuristics on standard benchmarks, and apply such an algorithm to incorporate and learn neural network weights improving generalization accuracy.
 % Finally, we also discuss some variations to the \gls{MCE} model.
@@
 In this case, $C_{YX} C_{XX}^{-1}$ becomes only an approximation to $\mathcal{U}_{Y | X}$, and we instead regularize the inversion and use $\mathcal{U}_{Y | X} = C_{YX} (C_{XX} + \lambda I)^{-1}$, which also serves to avoid overfitting \citep{song2013kernel}.
-\glspl{CME} are useful for probabilistic inference as conditional expectations of a function $g \in \mathcal{H}_{l}$ can be expressed as inner products, $\mathbb{E}[g(Y) | X = x] = \langle \mu_{Y | X = x}, g \rangle$, provided $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$, \citet[Theorem 4]{song2009hilbert}.
+\glspl{CME} are useful for probabilistic inference as conditional expectations of a function $g \in \mathcal{H}_{l}$ can be expressed as inner products, $\mathbb{E}[g(Y) | X = x] = \langle \mu_{Y | X = x}, g \rangle$, provided that $\mathbb{E}[g(Y) | X = \cdot] \in \mathcal{H}_{k}$ \citep[Theorem 4]{song2009hilbert}.
 
@@
 			\begin{equation}
-				\hat{\mathcal{E}}_{n, \lambda}[\mathcal{U}] = \frac{1}{n} \sum_{i = 1}^{n} \big\| l(y_{i}, \cdot) - \mathcal{U} k(x_{i}, \cdot) \big\|_{\mathcal{H}_{l}}^{2} + \lambda \| \mathcal{U} \|_{HS}.
+				\hat{\mathcal{E}}_{n, \lambda}[\mathcal{U}] = \frac{1}{n} \sum_{i = 1}^{n} \big\| l(y_{i}, \cdot) - \mathcal{U} k(x_{i}, \cdot) \big\|_{\mathcal{H}_{l}}^{2} + \lambda \| \mathcal{U} \|^{2}_{HS}.
 			\label{eq:lever_objective}
@@
 This could also be repeated over multiple folds for cross validation.
-\cite{song2013kernel} also uses this cross validation approach, but includes $\lambda \| \mathcal{U} \|_{HS}$ in the minimization.
+\cite{song2013kernel} also uses this cross validation approach, but includes $\lambda \| \mathcal{U} \|^{2}_{HS}$ in the minimization.
 This approach improves generalization of \glspl{CME} to unseen examples.
@@
 
-			When cross validation is too expensive, for many stationary kernels, the length scale parameter can be set by the median heuristic \citep{muandet2016kernel} via $\ell = \mathrm{median}_{i, j}(\| x_{i} - x_{j} \|_{2})$.
-However, they are restricted to length scale parameters only and cannot be used to set other hyperparameters, such as $\lambda$.
+			When cross validation is too expensive, the length scale parameter can be set by the median heuristic \citep{muandet2016kernel} via $\ell = \mathrm{median}_{i, j}(\| x_{i} - x_{j} \|_{2})$ for many stationary kernels.
+However, they cannot be used to set hyperparameters other than length scales, such as $\lambda$.
 In the setting of two sample testing, \cite{gretton2012optimal} also notes that they can possibly lead to poor performance.
@@
 
-			In many cases, learning is usually done by minimizing some empirical loss over a class of models whose Rademacher complexity is bounded.
-For a linear class of predictors parametrized as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularization to bound the Rademacher complexity, achieving tight generalization bounds in the context of multi-label learning.
+			In many cases, classifiers are trained by minimizing some empirical loss over a class of models whose Rademacher complexity is bounded.
+For a linear predictors parametrized as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularization to bound the Rademacher complexity, achieving tight generalization bounds in the context of multi-label learning.
 \cite{xu2016local} extends the trace norm regularization approach by considering the local Rademacher complexity on a subset of the predictor class, where they instead minimize the tail sum of the predictor singular values.
@@
 Similarly, \cite{pontil2013excess} also used trace norm regularization to bound the Rademacher complexity and minimizes the truncated hinge loss.
-Nevertheless, while Rademacher complexities have been employed to restrict the function class considered for learning weight parameters of linear models, they are usually not minimized along with the loss and have not yet been applied to learn hyperparameters.
+Nevertheless, while Rademacher complexities have been employed to restrict the function class considered for training weight parameters, they are usually not minimized along with the loss and have not yet been applied to learn hyperparameters.
 
@@
 
-		In particular, the assumption that $k(x, \cdot) \in \mathrm{image}(C_{XX})$ is on the input kernel $k$ not the output kernel $l$, which is a Kronecker delta $l = \delta$ for \glspl{MCE}.
+		In particular, the assumption $k(x, \cdot) \in \mathrm{image}(C_{XX})$ is on the input kernel $k$, not the output kernel $l$, which is a Kronecker delta $l = \delta$ for \glspl{MCE}.
 In practice, this assumption can be relaxed through introducing the regularization parameter $\lambda$ as in \eqref{eq:empirical_conditional_embedding} \citep{song2009hilbert}.
@@
 		While decision probability estimates \eqref{eq:empirical_decision_probability} do not necessarily form a normalized distribution for finite $n$, \cref{thm:probability_convergence_copy} guarantees that they approach one with increasing sample size.
-When normalized distributions are required, distribution estimates \eqref{eq:empirical_decision_probability} can be clip-normalized,
+When normalized distributions are required, clip-normalized estimates can be used \eqref{eq:empirical_decision_probability},
 		\begin{equation}
 		\tilde{p}_{c}(x) := \frac{\max\{\hat{p}_{c}(x), 0\}}{\sum_{j = 1}^{m} \max\{\hat{p}_{j}(x), 0\}}.
-		\label{eq:empirical_decision_probability_clip_normalised}
+		\label{eq:empirical_decision_probability_clip_normalized}
 		\end{equation}
-		Of course, classification $\hat{y}(x) = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x) = \argmax_{c \in \mathbb{N}_{m}} \tilde{p}_{c}(x)$ remains invariant.
-\Cref{thm:probability_convergence_copy} also implies the reducing effect of clip-normalisation as with increasing sample sizes, where $\tilde{p}_{c}(x)$ approaches to both $\hat{p}_{c}(x)$ and $p_{c}(x)$.
+		Classification $\hat{y}(x) = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x) = \argmax_{c \in \mathbb{N}_{m}} \tilde{p}_{c}(x)$ remains invariant.
+\Cref{thm:probability_convergence_copy} also implies that eventually the effect of clip-normalization vanishes, where $\tilde{p}_{c}(x)$ approaches to both $\hat{p}_{c}(x)$ and $p_{c}(x)$ with increasing sample sizes.
 
@@
 However, simply minimizing the empirical loss could lead to overfitting due to the flexibility of the nonparametric model.
-It is therefore essential to control the model complexity of \glspl{MCE}, which we turn to next.
+It is therefore essential to control the model complexity of \glspl{MCE}.
 
@@
 	\label{sec:hyperparameter_learning}
-
-		\begin{algorithm*}[tb]
-			\caption{\gls{MCE} Hyperparameter Learning with Batch Stochastic Gradient Updates}
-			\label{alg:multiclass_conditional_embedding_training}
-			\begin{algorithmic}[1]
-				\STATE {\bfseries Input:} kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial kernel parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
-				\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
-				\REPEAT
-				\STATE Sample the next batch $\mathcal{I}_{b} \subseteq \mathbb{N}_{n}$, $| \mathcal{I}_{b} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I}_{b} = \mathbb{N}_{n}$)
-				\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}_{b}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
-				\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathcal{I}_{b}, j \in \mathcal{I}_{b}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
-				\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n_{b} \lambda I_{n_{b}}) \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
-				\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Y) \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-				\STATE $P_{\theta, \lambda} \leftarrow K_{\theta} V_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-				\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n_{b}} \sum_{i = 1}^{n_{b}} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
-				\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
-				\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial q}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial q}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
-				\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
-			\end{algorithmic}
-		\end{algorithm*}
 
@@
 		to express risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$.
-Note that we employ the loss on the raw probability estimates \eqref{eq:empirical_decision_probability_vector}, not the clipped version \eqref{eq:empirical_decision_probability_clip_normalised}.
-Under this loss, we prove that the expected risk for the \gls{MCE} $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a \gls{RCB} $r(\theta, \lambda)$ with high probability.
+Note that we employ the loss on the raw probability estimates \eqref{eq:empirical_decision_probability_vector}, not the clipped version \eqref{eq:empirical_decision_probability_clip_normalized}.
 
-		\begin{theorem}[Expected Risk Bound for \gls{MCE} Hyperparameter Learning]
+		\cite{bartlett2002rademacher} showed that the expected risk can be bounded with high probability using the empirical risk and the Rademacher complexity of the loss composed with the function class.
+For a Lipchitz loss, \citet{ledoux2013probability} further showed that the latter can be bounded using the Rademacher complexity of the function class itself.
+However, the Rademacher complexity of \glspl{MCE} over all possible sets of kernel hyperparameters $\theta \in \Theta$ and regularization $\lambda \in \Lambda$ could be infinite.
+Moreover, it is more fruitful to quantify the model complexity for a specific set of hyperparameters $(\theta, \lambda)$, and not over all possible hyperparameters $\Theta \times \Lambda$.
+Since \glspl{MCE} are linear in the \gls{RKHS}, Rademacher complexities can be bounded by bounding the trace norm, similar to the case in \cite{yu2014large}.
+To quantify the model complexity for a specific set of hyperparameters $(\theta, \lambda)$, we consider the Rademacher complexity over all \glspl{MCE} whose trace norm is less than the chosen \gls{MCE} with hyperparameters $(\theta, \lambda)$.
+Since \glspl{MCE} operate in the \gls{RKHS}, we also require that the class of hyperparameters have bounded kernels with magnitude no more than that of the chosen \gls{MCE}.
+From this, we prove that the expected risk for a \gls{MCE} $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a \gls{RCB} $r(\theta, \lambda)$ with high probability.
+
+		\begin{theorem}[Expected Risk Bound for a choice of \gls{MCE} Hyperparameters]
 			\label{thm:expected_risk_bound_hyperparameter_learning_copy}
@@
 Mat\'{e}rn) with sensitivity and length scales $\theta = (\sigma_{f}, \Sigma)$, for example, have $\alpha(\theta) = \sigma_{f}$.
-Since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} is true with probability $1 - \beta$ when the random variables $X_{i}, Y_{i}$ are realised as the training observations $x_{i}, y_{i}$.
-We therefore employ this upper bound as the learning objective,
+Since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} is true with probability $1 - \beta$ when the random variables $(X_{i}, Y_{i})$ are realized as the training observations $(x_{i}, y_{i})$.
+We therefore employ this upper bound as the learning objective, and use gradient based optimizers such as Gradient descent or Adam \citep{kingma2014adam} for hyperparameter learning,
 		\begin{equation}
@@
 		\end{equation}
-		We employ gradient based optimisers such as Gradient descent or Adam \citep{kingma2014adam}.
 		Since \cref{thm:expected_risk_bound_hyperparameter_learning_copy} holds for any $n \in \mathbb{N}_{+}$ and any set of data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ from $\mathbb{P}_{X Y}$, with the trade-off of relaxing bound tightness through $\sqrt{8 \log{(2 / \beta)} / n}$, the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} also holds with high probability for a subset of the training data.
-This enables scalable hyperparameter learning through batch stochastic gradient updates, where each gradient update stochastically improves a different upper bound of the generalisation risk.
+This enables scalable hyperparameter learning through batch stochastic gradient updates, where each gradient update stochastically improves a different upper bound of the generalization risk.
 Because this bound holds with high probability over \textit{iid} samples, through randomly selecting a batch of training examples that comes from the same distribution, the resulting stochastic gradient will improve a strict upper bound with the same high probability.
 We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:multiclass_conditional_embedding_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size.
-The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is performed only once after learning instead of once every learning iteration, and can be avoided by using kernel herding \citep{chen2010super} or random Fourier features \citep{rahimi2008random} to estimate the already learned embedding.
-All further inference steps take $O(n^{2})$ time for back substitution.
+The Cholesky decomposition for the full training set requires $O(n^{3})$ time and required only for inference, instead of once every learning iteration.
+If necessary, it can be further avoided by using random Fourier features \citep{rahimi2008random} or kernel herding \citep{chen2010super} to approximate the already learned \gls{MCE}.
+All further inference take $O(n^{2})$ time, or potentially less with approximation, for back substitution.
+
+		%		\begin{algorithm*}[tb]
+		%			\caption{\gls{MCE} Hyperparameter Learning with Batch Stochastic Gradient Updates}
+		%			\label{alg:multiclass_conditional_embedding_training}
+		%			\begin{algorithmic}[1]
+		%				\STATE {\bfseries Input:} kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial kernel parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
+		%				\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
+		%				\REPEAT
+		%				\STATE Sample the next batch $\mathcal{I}_{b} \subseteq \mathbb{N}_{n}$, $| \mathcal{I}_{b} | = n_{b}$ \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I}_{b} = \mathbb{N}_{n}$)
+		%				\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}_{b}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
+		%				\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathcal{I}_{b}, j \in \mathcal{I}_{b}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
+		%				\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n_{b} \lambda I_{n_{b}}) \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
+		%				\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Y) \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
+		%				\STATE $P_{\theta, \lambda} \leftarrow K_{\theta} V_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
+		%				\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n_{b}} \sum_{i = 1}^{n_{b}} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
+		%				\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
+		%				\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial q}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial q}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
+		%				\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
+		%			\end{algorithmic}
+		%		\end{algorithm*}
+
+		\begin{algorithm}[tb]
+			\caption{\gls{MCE} Hyperparameter Learning with Batch Stochastic Gradient Updates}
+			\label{alg:multiclass_conditional_embedding_training}
+			\begin{algorithmic}[1]
+				\STATE {\bfseries Input:} kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial kernel parameters $\theta_{0}$, initial regularization parameter $\lambda_{0}$, learning rate $\eta$, cross entropy loss threshold $\epsilon$, batch size $n_{b}$
+				\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
+				\REPEAT
+				\STATE Sample the next batch $\mathcal{I}_{b} \subseteq \mathbb{N}_{n}$ s.t.
+$| \mathcal{I}_{b} | = n_{b}$ % \hspace{\fill} (For gradient descent, $n_{b} = n$ and $\mathcal{I}_{b} = \mathbb{N}_{n}$)
+				\STATE $Y \leftarrow \{\delta(y_{i}, c) : i \in \mathcal{I}_{b}, c \in \mathbb{N}_{m}\} \hspace{\fill} \in \{0, 1\}^{n_{b} \times m}$
+				\STATE $K_{\theta} \leftarrow \{k_{\theta}(x_{i}, x_{j}) : i \in \mathcal{I}_{b}, j \in \mathcal{I}_{b}\} \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
+				\STATE $L_{\theta, \lambda} \leftarrow \mathrm{cholesky}(K_{\theta} + n_{b} \lambda I_{n_{b}}) \hspace{\fill} \in \mathbb{R}^{n_{b} \times n_{b}}$
+				\STATE $V_{\theta, \lambda} \leftarrow L_{\theta, \lambda}^{T} \backslash (L_{\theta, \lambda} \backslash Y) \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
+				\STATE $P_{\theta, \lambda} \leftarrow K_{\theta} V_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
+				\STATE$r(\theta, \lambda) \leftarrow \alpha(\theta) \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda})}$
+				\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n_{b}} \sum_{i = 1}^{n_{b}} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; r(\theta, \lambda)$
+				\STATE $(\theta, \lambda) \leftarrow \mathrm{GradientBasedUpdate}(q, \theta, \lambda; \eta)$ % \hspace{\fill} (Or other gradient based updates such as Adam)
+				\UNTIL{maximum iterations reached} % \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
+				\STATE {\bfseries Output:} kernel parameters $\theta$, regularization $\lambda$
+			\end{algorithmic}
+		\end{algorithm}
 
 	\section{Extensions}
+	\label{sec:extensions}
 
@@
 
-		While we simply replaced instantiated $X_{i}$, $Y_{i}$ to be the training observations in \cref{thm:expected_risk_bound_hyperparameter_learning_copy} to obtain \cref{alg:multiclass_conditional_embedding_training}, this does not have to be the case for batch updates.
+		While we simply instantiated $(X_{i}, Y_{i})$ to be the training observations in \cref{thm:expected_risk_bound_hyperparameter_learning_copy} to obtain \cref{alg:multiclass_conditional_embedding_training}, this does not have to be the case for batch updates.
 Instead, in each learning iteration, we could further split the batch into two sub-batches - one for training and one for validation.
@@
 We evaluate the performance of the learning algorithm on a withheld test set using 20\% of the available 150 data samples.
-Attributes are scaled into the unit range $[0, 1]$ and decision probability maps are plotted for the region $[-0.5, 1.05]^{2}$, where the red, green, and blue colour channels represent the clip-normalized decision probability \eqref{eq:empirical_decision_probability_clip_normalised} for classes $c = 1, 2, 3$.
+Attributes are scaled into the unit range $[0, 1]$ and decision probability maps are plotted for the region $[-0.5, 1.05]^{2}$, where the red, green, and blue colour channels represent the clip-normalized decision probability \eqref{eq:empirical_decision_probability_clip_normalized} for classes $c = 1, 2, 3$.
 We begin from two initial scenarios, one originally overfitting ($\alpha_{o} = 0.01$, $\ell_{o} = 0.035$, $\lambda_{o} = 10^{-6}$) and another underfitting ($\alpha_{u} = 1$, $\ell_{u} = 1$, $\lambda_{u} = 1$) the training data.
@@
 
-		We apply \cref{alg:multiclass_conditional_embedding_training} to learn anisotropic length scales of Gaussian kernels on pixels of the MNIST digits dataset \citep{lecun1998gradient}.
+		We apply \cref{alg:multiclass_conditional_embedding_training} to learn length scales of anisotropic Gaussian, or \gls{ARD}, kernels on pixels of the MNIST digits dataset \citep{lecun1998gradient}.
 In the top left plot of \cref{fig:mnist_experiments}, we train on datasets of varying sizes, from 50 to 5000 images, and benchmark performance on the standard test set of 10000 images.
@@
 \glspl{MCE} also outperform \glspl{GPC} as more data becomes available.
-Under the \gls{OVA} scheme, a set of kernel hyperparameters are learned to distinguish each class against the rest, while for our algorithm learns a consistent set of hyperparameters for all classes.
-Consequently, for 5000 data points, the computational time required for hyperparameter learning of standard \glspl{GPC} is on the order of days, while \cref{alg:multiclass_conditional_embedding_training} is on the order of hours even without batch updates.
+Under the \gls{OVA} scheme, a set of kernel hyperparameters are learned to distinguish each class against the rest, while our approach learns a consistent set of hyperparameters for all classes.
+Consequently, for 5000 data points, the computational time required for hyperparameter learning of standard \glspl{GPC} is on the order of days even for learning isotropic Gaussian kernels, while \cref{alg:multiclass_conditional_embedding_training} is on the order of hours even without batch updates for learning anistropic Gaussian kernels.
 We also compare hyperparameter learning with and without the \gls{RCB}.
@@
 			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_0123456789_batch_1200.eps}
-			\caption{Top: Test accuracy by learning Gaussian kernels (left) and deep convolutional features (right). Bottom: Learned pixel length scales under anistropic Gaussian (ARD) kernels.}
+			\caption{Top: Test accuracy by learning Gaussian kernels (left) and deep convolutional features (right). Bottom: Learned pixel length scales under anistropic Gaussian, or \gls{ARD}, kernels.}
 			\label{fig:mnist_experiments}
@@
 
-		We now apply our learning algorithm to train \gls{CNN} on the MNIST dataset.
+		We now apply \cref{alg:multiclass_conditional_embedding_training} to train a \gls{CEN} with convolutional features on MNIST.
 We employ an example architecture from the TensorFlow tutorial on deep MNIST classification \citep{abadi2016tensorflow}.
-This ReLU activated architecture uses two convolutional layers, each with max pooling, followed by a fully connected layer with a drop out probability of 0.5.
-The original network then employs a final softmax regressor on the last hidden layer for classification.
+This ReLU activated \gls{CNN} uses two convolutional layers, each with max pooling, followed by a fully connected layer with a drop out probability of 0.5.
+The original \gls{CNN} then employs a final softmax regressor on the last hidden layer for classification.
 The \gls{CEN} instead employs a linear kernel on the last hidden layer to construct the conditional embedding.
-We then train both networks from the same initialization with batch updates using $n_{b} = 6000$ images at a time for 800 epochs, with learning rate $\eta = 0.01$.
+We then train both networks from the same initialization using batches updates with of $n_{b} = 6000$ images for 800 epochs, with learning rate $\eta = 0.01$.
 All biases and standard deviations of zero mean truncated normal distributed weights are initialized to 0.1.
@@
 After 800 epochs, \gls{CEN} reaches a test accuracy of 99.48\%, compared to 99.26\% from the original \gls{CNN}.
-This demonstrates that our learning algorithm can perform end-to-end learning with \glspl{CNN} from scratch, by simply replacing the softmax layer with an \gls{MCE}.
+This demonstrates that our learning algorithm can perform end-to-end learning with convolutional layers from scratch, by simply replacing the softmax layer with a \gls{MCE}.
 The resulting \gls{CEN} can outperform the original \gls{CNN} in both convergence rate and accuracy.

### 2017-10-12 AISTATS2018/cake_aistats2018.tex
Revised grammar from feedback. Now going for major restructuring

@@
 		% The goal is to motivate the problem here and outline our contribution
-		How can we design a scalable learning objective for learning kernel hyperparameters of conditional mean embeddings?
 		Conditional mean embeddings are nonparametric models that encode conditional expectations in a reproducing kernel Hilbert space directly through observed data, resulting in a flexible and powerful framework for probabilistic inference.
-However, their performance is greatly dependent on the choice of kernel hyperparameters and regularization, yet current approaches for hyperparameter tuning predominantly rely on cross validation and distance based heuristics.
-For conditional mean embeddings with categorical targets but arbitrary inputs, we propose a hyperparameter learning framework based on Rademacher complexity bounds to prevent overfitting by balancing data fit against model complexity.
+Their performance is greatly dependent on the choice of kernel hyperparameters and regularization.
+However, current approaches for hyperparameter tuning predominantly rely on cross validation and distance based heuristics.
+For conditional mean embeddings with categorical targets and arbitrary inputs, we propose a hyperparameter learning framework based on Rademacher complexity bounds to prevent overfitting by balancing data fit against model complexity.
 The approach only requires batch updates, allowing scalable kernel learning without kernel approximations.
@@
 		% % In this paper, we focus on a rarely investigated form of the CME...
-		For \glspl{CME} with categorical targets but arbitrary inputs, we can further infer conditional probabilities directly, and not just conditional expectations.
+		For \glspl{CME} with categorical targets and arbitrary inputs, we can further infer conditional probabilities directly, and not just conditional expectations.
 As there can be more than two categories, we refer to these \glspl{CME} as \glspl{MCE} in this paper.
@@
 In these settings, the model selection process usually begins by selecting a kernel, whose parameters become part of the model hyperparameters, which may further include noise or regularization parameters.
-Given a set of hyperparameters, training boils down to solving either a convex optimization problem, e.g.
-\glspl{SVM}, or a set of linear equations, e.g.
-\glspl{GPC}, \glspl{RLSC}, and \glspl{CME}.
+Given a set of hyperparameters, training is performed by solving either a convex optimization problem, such as for \glspl{SVM}, or a set of linear equations, such as for \glspl{GPC}, \glspl{RLSC}, and \glspl{CME}.
 Unfortunately, hyperparameter tuning is not straight forward, and various forms of cross validation \citep{song2013kernel} or heuristics such as the median length heuristic \citep{damien2017asymptotic, muandet2016kernel} remain as the primary approaches for this task.
@@
 
-		One notable success story in this domain are \gls{GPs} \citep{rasmussen2006gaussian}, which have long enjoyed the well celebrated marginal likelihood for hyperparameter learning.
-The marginal likelihood arises naturally from the Bayesian formulation of \gls{GPs}, and exhibits certain desirable properties -- in particular, the ability to automatically balance between data fit and model complexity.
+		One notable success story in this domain are \gls{GPs} \citep{rasmussen2006gaussian}, which utilizes the marginal likelihood for hyperparameter learning.
+The marginal likelihood arises naturally from a Bayesian formulation of \gls{GPs}, and exhibits certain desirable properties -- in particular, the ability to automatically balance between data fit and model complexity.
 On the other hand, \glspl{CME} are not necessarily Bayesian, and hence they do not benefit from a natural marginal likelihood formulation, yet such a balance is critical when generalizing the model beyond unseen examples.
@@
 In this paper, we present such a learning objective as our main contribution.
-In particular, we (1) derive a measure of model complexity for a specific \gls{MCE} based on the Rademacher complexity of a relevant class of \glspl{MCE}, (2) formulate a novel learning objective based on this complexity measure to control expected generalization risk by balancing data fit against model complexity, and (3) propose a scalable hyperparameter learning algorithm under this objective using batch updates.
-We show that this learning objective produces \glspl{MCE} that generalizes better than that learned from cross validation, \gls{ERM}, and median length heuristics on standard benchmarks, and apply such an algorithm to incorporate and learn neural network weights improving generalization accuracy.
+In particular, we: (1) derive a measure of model complexity for a specific \gls{MCE} based on the Rademacher complexity of a relevant class of \glspl{MCE}, (2) formulate a novel learning objective based on this complexity measure to control expected generalization risk by balancing data fit against model complexity, and (3) propose a scalable hyperparameter learning algorithm under this objective using batch updates.
+We show that this learning objective produces \glspl{MCE} that generalize better than that learned from cross validation, \gls{ERM}, or median length heuristics on standard benchmarks, and apply such an algorithm to incorporate and learn neural network weights improving generalization accuracy.
 % Finally, we also discuss some variations to the \gls{MCE} model.
@@
 This illustrates that the notion of model complexity during learning is especially important to ensure good generalization.
-\cite{lever2012conditional} proposes to hold out a validation set $\{k(x_{t_{j}}, \cdot), l(y_{t_{j}}, \cdot)\}_{j = 1}^{J}$ and minimize $\frac{1}{J} \sum_{j = 1}^{J} \big\| l(y_{t_{j}}, \cdot) - \hat{\mathcal{U}}_{Y | X} k(x_{t_{j}}, \cdot) \big\|_{\mathcal{H}_{l}}^{2}$ where $\hat{\mathcal{U}}_{Y | X}$ is estimated from the remaining training set using \eqref{eq:empirical_conditional_embedding}.
+\cite{lever2012conditional} proposed to hold out a validation set $\{k(x_{t_{j}}, \cdot), l(y_{t_{j}}, \cdot)\}_{j = 1}^{J}$ and minimize $\frac{1}{J} \sum_{j = 1}^{J} \big\| l(y_{t_{j}}, \cdot) - \hat{\mathcal{U}}_{Y | X} k(x_{t_{j}}, \cdot) \big\|_{\mathcal{H}_{l}}^{2}$ where $\hat{\mathcal{U}}_{Y | X}$ is estimated from the remaining training set using \eqref{eq:empirical_conditional_embedding}.
 This could also be repeated over multiple folds for cross validation.
@@
 In the setting of two sample testing, \cite{gretton2012optimal} also notes that they can possibly lead to poor performance.
-In the context of \glspl{CME}, they also do not take into account of labeled information.
+In the context of \glspl{CME}, they also do not take labeled information.
 \cite{flaxman2016bayesian} proposed a Bayesian learning framework for marginal embeddings via inducing points, though it is unclear how this can be extended to include \glspl{CME}.
@@
 			In many cases, classifiers are trained by minimizing some empirical loss over a class of models whose Rademacher complexity is bounded.
-For a linear predictors parametrized as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularization to bound the Rademacher complexity, achieving tight generalization bounds in the context of multi-label learning.
+For linear predictors parametrized as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularization to bound the Rademacher complexity, achieving tight generalization bounds in the context of multi-label learning.
 \cite{xu2016local} extends the trace norm regularization approach by considering the local Rademacher complexity on a subset of the predictor class, where they instead minimize the tail sum of the predictor singular values.
 Local Rademacher complexity has also been employed for multiple kernel learning \citep{kloft2011local, cortes2013learning} to learn convex combinations of simpler preselected kernels for \glspl{SVC}.
-Similarly, \cite{pontil2013excess} also used trace norm regularization to bound the Rademacher complexity and minimizes the truncated hinge loss.
+Similarly, \cite{pontil2013excess} also used trace norm regularization to bound the Rademacher complexity and minimize the truncated hinge loss.
 Nevertheless, while Rademacher complexities have been employed to restrict the function class considered for training weight parameters, they are usually not minimized along with the loss and have not yet been applied to learn hyperparameters.
@@
 
-		While decision probability estimates \eqref{eq:empirical_decision_probability} do not necessarily form a normalized distribution for finite $n$, \cref{thm:probability_convergence_copy} guarantees that they approach one with increasing sample size.
+		Note that for finite $n$ the probability estimates \eqref{eq:empirical_decision_probability} may not necessarily lie in the range $[0,1]$.
+Although decision probability estimates \eqref{eq:empirical_decision_probability} do not necessarily form a normalized distribution for finite $n$, \cref{thm:probability_convergence_copy} guarantees that they approach one with increasing sample size.
 When normalized distributions are required, clip-normalized estimates can be used \eqref{eq:empirical_decision_probability},
@@
 		\end{equation}
-		Classification $\hat{y}(x) = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x) = \argmax_{c \in \mathbb{N}_{m}} \tilde{p}_{c}(x)$ remains invariant.
+		Nevertheless, classification results remains invariant, since $\hat{y}(x) = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x) = \argmax_{c \in \mathbb{N}_{m}} \tilde{p}_{c}(x)$.
 \Cref{thm:probability_convergence_copy} also implies that eventually the effect of clip-normalization vanishes, where $\tilde{p}_{c}(x)$ approaches to both $\hat{p}_{c}(x)$ and $p_{c}(x)$ with increasing sample sizes.
@@
 Consequently, multiclass extensions for \gls{RLSC} either require using the \gls{OVA} scheme \citep{rifkin2003regularized}, or minimizing the summed losses across all binarized tasks instead \citep{pahikkala2012unsupervised}, producing separate classifiers for each class.
-As a result, multiclass \gls{RLSC} do not produce consistent estimates of class probabilities as in \cref{thm:probability_convergence_copy} for \glspl{MCE}.
+As a result, multiclass \gls{RLSC} does not produce consistent estimates of class probabilities as in \cref{thm:probability_convergence_copy} for \glspl{MCE}.
 This property allows us to employ a probabilistic loss over the output of \glspl{MCE} to learn its hyperparameters, which is known to be difficult to tune in the case of \gls{RLSC} \citep{pahikkala2012unsupervised}.
@@
 		to express risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$.
-Note that we employ the loss on the raw probability estimates \eqref{eq:empirical_decision_probability_vector}, not the clipped version \eqref{eq:empirical_decision_probability_clip_normalized}.
+Note that we employ the loss on the original probability estimates \eqref{eq:empirical_decision_probability_vector}, not the clip-normalized version \eqref{eq:empirical_decision_probability_clip_normalized}.
 
@@
 To quantify the model complexity for a specific set of hyperparameters $(\theta, \lambda)$, we consider the Rademacher complexity over all \glspl{MCE} whose trace norm is less than the chosen \gls{MCE} with hyperparameters $(\theta, \lambda)$.
-Since \glspl{MCE} operate in the \gls{RKHS}, we also require that the class of hyperparameters have bounded kernels with magnitude no more than that of the chosen \gls{MCE}.
+Since \glspl{MCE} operate in the \gls{RKHS}, we also require that the kernels are bonded with magnitude no more than that of the chosen \gls{MCE}.
 From this, we prove that the expected risk for a \gls{MCE} $\bvec{f} = \bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector} is bounded by the empirical risk and a \gls{RCB} $r(\theta, \lambda)$ with high probability.
@@
 Since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} is true with probability $1 - \beta$ when the random variables $(X_{i}, Y_{i})$ are realized as the training observations $(x_{i}, y_{i})$.
-We therefore employ this upper bound as the learning objective, and use gradient based optimizers such as Gradient descent or Adam \citep{kingma2014adam} for hyperparameter learning,
+We therefore employ this upper bound as the learning objective, and use gradient based optimizers such as gradient descent or Adam \citep{kingma2014adam} for hyperparameter learning,
 		\begin{equation}
@@
 We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:multiclass_conditional_embedding_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size.
-The Cholesky decomposition for the full training set requires $O(n^{3})$ time and required only for inference, instead of once every learning iteration.
-If necessary, it can be further avoided by using random Fourier features \citep{rahimi2008random} or kernel herding \citep{chen2010super} to approximate the already learned \gls{MCE}.
-All further inference take $O(n^{2})$ time, or potentially less with approximation, for back substitution.
+The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is necessary only for inference, instead of once every learning iteration.
+It can be further avoided by using random Fourier features \citep{rahimi2008random} or kernel herding \citep{chen2010super} to approximate the already learned \gls{MCE}.
+All further inference takes $O(n^{2})$ time, or potentially less with approximation, using back substitution.
 
@@
 We refer to \glspl{MCE} constructed this way as \glspl{CEN}.
-Similar to the spirit of \cite{wilson2016stochastic} where the neural network weights and biases are learned jointly under the \gls{GP} marginal likelihood objective, \glspl{CEN} also learn network weights and biases under \eqref{eq:learning_objective}.
+Similar to \cite{wilson2016stochastic} where the neural network weights and biases are learned jointly under the \gls{GP} marginal likelihood objective, \glspl{CEN} also learn network weights and biases under \eqref{eq:learning_objective}.
 These kernels benefit in both scalability and expressibility.
@@
 
-		The first two of four total attributes of the iris dataset \citep{fisher1936use} is known to have class labels that are not only not linearly separable, but also non-separable by any means, in that the same example $x \in \mathbb{R}^{2}$ may be assigned different output labels $y \in \mathbb{N}_{3} := \{1, 2, 3\}$ as they were only separable with the two remaining attributes.
+		The first two of four total attributes of the iris dataset \citep{fisher1936use} are known to have class labels that are non-separable by any means, in that the same example $x \in \mathbb{R}^{2}$ may be assigned different output labels $y \in \mathbb{N}_{3} := \{1, 2, 3\}$.
 In these difficult scenarios, the notion of model complexity is extremely important, and the success of a learning algorithm greatly depends on how it balances training performance and model complexity to avoid both underfitting and overfitting.
@@
 		\Cref{fig:iris} demonstrates \cref{alg:multiclass_conditional_embedding_training} with full gradient updates ($n_{b} = n$) to learn hyperparameters of the \gls{MCE} on the two attribute iris dataset.
-The kernel used is isotropic Gaussian with diagonal length scales $\Sigma = \ell^{2} I_{2}$ and sensitivity $\alpha = \sigma_{f}$, so the hyperparameters are $\theta = (\alpha, \ell)$ and $\lambda$.
+The kernel used is isotropic Gaussian with diagonal length scales $\Sigma = \ell^{2} I_{2}$ and sensitivity $\alpha = \sigma_{f}$, so that the hyperparameters are $\theta = (\alpha, \ell)$ and $\lambda$.
 We evaluate the performance of the learning algorithm on a withheld test set using 20\% of the available 150 data samples.
@@
 We begin from two initial scenarios, one originally overfitting ($\alpha_{o} = 0.01$, $\ell_{o} = 0.035$, $\lambda_{o} = 10^{-6}$) and another underfitting ($\alpha_{u} = 1$, $\ell_{u} = 1$, $\lambda_{u} = 1$) the training data.
-Initially, both models performs sub-optimally with a test accuracy of 56.67\%.
+Initially, both models perform sub-optimally with a test accuracy of 56.67\%.
 We see that the \gls{RCB} $r(\theta, \lambda)$ appropriately measures the amount of overfitting with $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = 4.33$ and $r((\alpha_{u}, \ell_{u}), \lambda_{u}) = 0.31$.
@@
 In particular, the initially overfitted model learns a simpler model at the expense of lower training performance, emphasizing the benefits of complexity based regularization, without which the learning would only maximize training performance at the cost of further overfitting.
-Meanwhile, the initially underfitted model learns to increase complexity to improve the unflattering performance on the training set.
+Meanwhile, the initially underfitted model learns to increase complexity to improve the sub-optimal performance on the training set.
 In both scenarios, our learning algorithm improved performance on the test set.
@@
 For all experiments, $\lambda$ is initialized to $1$ and is learned jointly with the kernel.
-Optimization is performed with the Adam optimizer \citep{kingma2014adam} in TensorFlow \citep{abadi2016tensorflow} with rate $\eta = 0.1$ and $\epsilon = 10^{-15}$ under the learning objective $q(\theta, \lambda)$ \eqref{eq:learning_objective}.
-Learning is ran for 1000 epochs, regardless of convergence, for direct comparison.
+Optimization is performed with the Adam optimizer \citep{kingma2014adam} in TensorFlow \citep{abadi2016tensorflow} with a rate of $\eta = 0.1$ and $\epsilon = 10^{-15}$ under the learning objective $q(\theta, \lambda)$ \eqref{eq:learning_objective}.
+Learning is run for 1000 epochs to allow direct comparison.
 All attributes are scaled to the unit range.
@@
 For \glspl{CEN}, we did not attempt to choose an optimal architecture for each dataset.
-The learning algorithm is to train the same simple untrained network for different datasets under only 1000 epochs, and still generates comparable performance.
+The learning algorithm is designed to train the same simple network for different datasets using 1000 epochs to generate comparable performance.
 
@@
 We train both \glspl{SVC} and \glspl{GPC} under the \gls{OVA} scheme, and use a Laplace approximation for the \gls{GPC} posterior.
-In all cases, \glspl{MCE} outperform \glspl{SVC}, as standard \gls{SVC} training cannot learn hyperparameters unless expensive cross validation is performed.
+In all cases \glspl{MCE} outperform \glspl{SVC}, as standard \gls{SVC} training cannot learn hyperparameters unless expensive cross validation is performed.
 \glspl{MCE} also outperform \glspl{GPC} as more data becomes available.
@@
 96.05\% and 95.3\% for $n= 5000$).
-This verifies that complexity based regularization becomes especially important as data size grows, when overfitting starts to hurt generalization performance.
+This verifies that complexity based regularization becomes especially important as data size grows, when overfitting starts to decrease generalization performance.
 Our bound is also tighter with larger $n$, so that generalization performance improves with more data.
@@
 The \gls{CEN} instead employs a linear kernel on the last hidden layer to construct the conditional embedding.
-We then train both networks from the same initialization using batches updates with of $n_{b} = 6000$ images for 800 epochs, with learning rate $\eta = 0.01$.
+We then train both networks from the same initialization using batch updates of $n_{b} = 6000$ images for 800 epochs, with learning rate $\eta = 0.01$.
 All biases and standard deviations of zero mean truncated normal distributed weights are initialized to 0.1.
@@
 The fully connected layer is trained with a drop out probability of 0.5 for both cases to allow direct comparison.
-The top right plot in \cref{fig:mnist_experiments} shows that \glspl{CEN} learns at a much faster rate, maintaining a higher test accuracy at all epochs.
+The top right plot in \cref{fig:mnist_experiments} shows that \glspl{CEN} learn at a much faster rate, maintaining a higher test accuracy at all epochs.
 After 800 epochs, \gls{CEN} reaches a test accuracy of 99.48\%, compared to 99.26\% from the original \gls{CNN}.
@@
 
-		This framework can incorporated and extended in many ways into techniques that requires appropriately learned conditional embeddings.
+		This framework can be incorporated and extended into techniques that require appropriately learned conditional embeddings.
 In particular, nonparametric probabilistic inference can be carried out in the \gls{RKHS} to obtain joint and reverse conditional embeddings, where mode decoding, density recovery, and sampling techniques can lead to effective generative models now that hyperparameters are learned.

### 2017-10-13 AISTATS2018/cake_aistats2018.tex
Major restructuring done

@@
 \newacronym{CME}{CME}{conditional mean embedding}
-\newacronym{MCE}{MCE}{multiclass conditional embedding}
+\newacronym{MCE}{MCE}{multi-categorical conditional embedding}
 \newacronym{CEN}{CEN}{conditional embedding network}
@@
 \newacronym{OVA}{OVA}{one versus all}
+\newacronym{OVO}{OVO}{one versus one}
 \newacronym{CNN}{CNN}{convolutional neural network}
@@
 		% The goal is to motivate the problem here and outline our contribution
-		Conditional mean embeddings are nonparametric models that encode conditional expectations in a reproducing kernel Hilbert space directly through observed data, resulting in a flexible and powerful framework for probabilistic inference.
-Their performance is greatly dependent on the choice of kernel hyperparameters and regularization.
+		Conditional mean embeddings are nonparametric models that encode conditional expectations in a reproducing kernel Hilbert space, creating a flexible and powerful framework for probabilistic inference.
+Their performance is greatly dependent on the choice of kernel hyperparameters and regularization parameter.
 However, current approaches for hyperparameter tuning predominantly rely on cross validation and distance based heuristics.
@@
 The approach only requires batch updates, allowing scalable kernel learning without kernel approximations.
-Experiments demonstrate that our framework outperforms standard cross validation, and can be further extended to incorporate and learn neural network weights improving generalization.
+Experiments demonstrate that our framework outperforms competing methods, and can be further extended to incorporate and learn neural network weights improving generalization.
 
@@
 
-		% % In this paper, we focus on a rarely investigated form of the CME...
-		For \glspl{CME} with categorical targets and arbitrary inputs, we can further infer conditional probabilities directly, and not just conditional expectations.
-As there can be more than two categories, we refer to these \glspl{CME} as \glspl{MCE} in this paper.
-In contrast, \glspl{SVM} \citep{scholkopf2002learning} do not naturally produce probabilities, while \glspl{GPC} \citep{rasmussen2006gaussian} require posterior approximations.
-As such, \glspl{MCE} are widely applicable to probabilistic inference in multiclass settings with categorical targets.
-Unlike \glspl{SVM}, \glspl{GPC}, and multiclass \glspl{RLSC} \citep{rifkin2003regularized, pahikkala2012unsupervised}, \glspl{MCE} do not require separately fitting multiple binary classifiers to obtain a final prediction.
-Instead, a single \gls{MCE} is sufficient for producing consistent multiclass probabilistic estimates.
-
 		% Paragraph: Why do we want to learn their hyperparameters?
@@
 		Nevertheless, like most kernel based models, their performance is highly dependent on the hyperparameters chosen.
-In these settings, the model selection process usually begins by selecting a kernel, whose parameters become part of the model hyperparameters, which may further include noise or regularization parameters.
-Given a set of hyperparameters, training is performed by solving either a convex optimization problem, such as for \glspl{SVM}, or a set of linear equations, such as for \glspl{GPC}, \glspl{RLSC}, and \glspl{CME}.
-Unfortunately, hyperparameter tuning is not straight forward, and various forms of cross validation \citep{song2013kernel} or heuristics such as the median length heuristic \citep{damien2017asymptotic, muandet2016kernel} remain as the primary approaches for this task.
+For these models, the model selection process usually begins by selecting a kernel, whose parameters become part of the model hyperparameters, which may further include noise or regularization parameters.
+Given a set of hyperparameters, training is performed by solving either a convex optimization problem, such as for \glspl{SVM} \citep{scholkopf2002learning}, or a set of linear equations, such as for \gls{GPs} \citep{rasmussen2006gaussian}, \glspl{RLSC} \citep{rifkin2003regularized}, and \glspl{CME}.
+Unfortunately, hyperparameter tuning is not straight forward, and often cross validation \citep{song2013kernel} or median length heuristics \citep{muandet2016kernel} remain as the primary approaches for this task.
 
@@
 
-		One notable success story in this domain are \gls{GPs} \citep{rasmussen2006gaussian}, which utilizes the marginal likelihood for hyperparameter learning.
-The marginal likelihood arises naturally from a Bayesian formulation of \gls{GPs}, and exhibits certain desirable properties -- in particular, the ability to automatically balance between data fit and model complexity.
+		One notable success story in this domain are \gls{GPs}, which utilizes the marginal likelihood for hyperparameter learning.
+The marginal likelihood arises from its Bayesian formulation, and exhibits certain desirable properties -- in particular, the ability to automatically balance between data fit and model complexity.
 On the other hand, \glspl{CME} are not necessarily Bayesian, and hence they do not benefit from a natural marginal likelihood formulation, yet such a balance is critical when generalizing the model beyond unseen examples.
@@
 
-		Can we formulate a learning objective for \glspl{MCE} that resembles the marginal likelihood of \gls{GPs} to balance data fit and model complexity?
-In this paper, we present such a learning objective as our main contribution.
-In particular, we: (1) derive a measure of model complexity for a specific \gls{MCE} based on the Rademacher complexity of a relevant class of \glspl{MCE}, (2) formulate a novel learning objective based on this complexity measure to control expected generalization risk by balancing data fit against model complexity, and (3) propose a scalable hyperparameter learning algorithm under this objective using batch updates.
-We show that this learning objective produces \glspl{MCE} that generalize better than that learned from cross validation, \gls{ERM}, or median length heuristics on standard benchmarks, and apply such an algorithm to incorporate and learn neural network weights improving generalization accuracy.
+		Can we formulate a learning objective for \glspl{CME} to balance data fit and model complexity, similar to the marginal likelihood of \gls{GPs}?
+For \glspl{CME} with categorical targets and arbitrary input, we present such a learning objective as our main contribution.
+In particular, we: (1) derive a measure $r(\theta, \lambda)$ to measure the model complexity of a \gls{CME} based on the Rademacher complexity of a relevant class of \glspl{CME}, (2) propose a novel learning objective based on this complexity measure to control generalization risk by balancing data fit against model complexity, and (3) propose a scalable hyperparameter learning algorithm under this objective using batch updates.
+We show that this learning objective produces \glspl{CME} that generalize better than that learned from cross validation, \gls{ERM}, or median length heuristics on standard benchmarks, and apply such an algorithm to incorporate and learn neural network weights improving generalization accuracy.
 % Finally, we also discuss some variations to the \gls{MCE} model.
@@
 
-			Hyperparameter learning for conditional embeddings is particularly difficult compared to marginal or joint embeddings, since the kernel $k_{\theta}$ with parameters $\theta \in \Theta$ is to be learned jointly with a regularization parameter $\lambda \in \Lambda = \mathbb{R}_{+}$.
-\cite{lever2012conditional} showed that $\mathcal{U} = \hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the solution to the regularized least squares problem in the RKHS from $k(x, \cdot) \in \mathcal{H}_{k}$ to $l(y, \cdot) \in \mathcal{H}_{l}$,
-			\begin{equation}
-				\hat{\mathcal{E}}_{n, \lambda}[\mathcal{U}] = \frac{1}{n} \sum_{i = 1}^{n} \big\| l(y_{i}, \cdot) - \mathcal{U} k(x_{i}, \cdot) \big\|_{\mathcal{H}_{l}}^{2} + \lambda \| \mathcal{U} \|^{2}_{HS}.
-			\label{eq:lever_objective}
-			\end{equation}
-			Minimizing this objective directly over $\theta \in \Theta, \lambda \in \Lambda$ for $\mathcal{U} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X}$ and $k = k_{\theta}$ would result in an overfitted model with small $\lambda$.
-This illustrates that the notion of model complexity during learning is especially important to ensure good generalization.
+			Hyperparameter learning for \glspl{CME} is particularly difficult compared to marginal or joint embeddings, since the kernel $k = k_{\theta}$ with parameters $\theta \in \Theta$ is to be learned jointly with a regularization parameter $\lambda \in \Lambda = \mathbb{R}_{+}$.
 \cite{lever2012conditional} proposed to hold out a validation set $\{k(x_{t_{j}}, \cdot), l(y_{t_{j}}, \cdot)\}_{j = 1}^{J}$ and minimize $\frac{1}{J} \sum_{j = 1}^{J} \big\| l(y_{t_{j}}, \cdot) - \hat{\mathcal{U}}_{Y | X} k(x_{t_{j}}, \cdot) \big\|_{\mathcal{H}_{l}}^{2}$ where $\hat{\mathcal{U}}_{Y | X}$ is estimated from the remaining training set using \eqref{eq:empirical_conditional_embedding}.
 This could also be repeated over multiple folds for cross validation.
-\cite{song2013kernel} also uses this cross validation approach, but includes $\lambda \| \mathcal{U} \|^{2}_{HS}$ in the minimization.
+\cite{song2013kernel} also uses this cross validation approach, but adds a regularization $\lambda \| \mathcal{U} \|^{2}_{HS}$ to the validation objective.
 This approach improves generalization of \glspl{CME} to unseen examples.
-However, they require the selection for the split and number of folds, and are not optimized for any particular prediction task.
+However, they require the selection for the split and number of folds.
+Moreover, they are not optimized for any particular prediction task.
 By fitting a separate model for each fold during learning, they also incur a large computational cost of $O(J n^{3})$ for $J$ folds, and becomes prohibitive with large datasets.
@@
 In the setting of two sample testing, \cite{gretton2012optimal} also notes that they can possibly lead to poor performance.
-In the context of \glspl{CME}, they also do not take labeled information.
-\cite{flaxman2016bayesian} proposed a Bayesian learning framework for marginal embeddings via inducing points, though it is unclear how this can be extended to include \glspl{CME}.
+In the context of \glspl{CME}, they also do not make use of label information.
+\cite{flaxman2016bayesian} proposed a Bayesian learning framework for marginal embeddings via inducing points, though it is unclear how this can be extended to \glspl{CME}.
 \cite{fukumizu2009kernel} also investigated the choice of kernel bandwidth for stationary kernels in the setting of binary classification and two sample testing using the \gls{MMD}, but has yet to generalize to \glspl{CME} or multiclass settings.
@@
 			In many cases, classifiers are trained by minimizing some empirical loss over a class of models whose Rademacher complexity is bounded.
-For linear predictors parametrized as $f(x; W) = W^{T} x$, $W \in \mathbb{R}^{d \times L}$, \cite{yu2014large} used trace norm regularization to bound the Rademacher complexity, achieving tight generalization bounds in the context of multi-label learning.
+In the context of multi-label learning, \cite{yu2014large} used trace norm regularization to bound the Rademacher complexity, achieving tight generalization bounds.
 \cite{xu2016local} extends the trace norm regularization approach by considering the local Rademacher complexity on a subset of the predictor class, where they instead minimize the tail sum of the predictor singular values.
-Local Rademacher complexity has also been employed for multiple kernel learning \citep{kloft2011local, cortes2013learning} to learn convex combinations of simpler preselected kernels for \glspl{SVC}.
+Local Rademacher complexity has also been employed for multiple kernel learning \citep{kloft2011local, cortes2013learning} to learn convex combinations of fixed kernels for \glspl{SVM}.
 Similarly, \cite{pontil2013excess} also used trace norm regularization to bound the Rademacher complexity and minimize the truncated hinge loss.
-Nevertheless, while Rademacher complexities have been employed to restrict the function class considered for training weight parameters, they are usually not minimized along with the loss and have not yet been applied to learn hyperparameters.
+Nevertheless, while Rademacher complexities have been employed to restrict the function class considered for training weight parameters, they have not been applied to learn kernel hyperparameters itself.
 
@@
 
-	\section{Multiclass Conditional Embeddings}
+	\section{Multi-Categorical Conditional Mean Embeddings}
 	\label{sec:multiclass_conditional_embedding}
 
-		In the multiclass setting, the output label space is finite and discrete, taking values only in $\mathcal{Y} = \mathbb{N}_{m} := \{1, \dots, m\}$.
+%		% % In this paper, we focus on a rarely investigated form of the CME...
+		In this section we present a particular type of \glspl{CME} that are suitable for prediction tasks with categorical targets.
+We show that for \glspl{CME} with categorical targets and arbitrary inputs, we can further infer conditional probabilities directly, and not just conditional expectations.
+As there can be more than two categories, we refer to these \glspl{CME} as \glspl{MCE} in this paper.
+
+		For categorical targets, the output label space is finite and discrete, taking values only in $\mathcal{Y} = \mathbb{N}_{m} := \{1, \dots, m\}$.
 Naturally, we choose the Kronecker delta kernel $\delta : \mathbb{N}_{m} \times \mathbb{N}_{m} \to \{0, 1\}$ as the output kernel $l$, where labels that are the same have unit similarity and labels that are different have no similarity.
@@
 As $\delta$ is an integrally strictly positive definite kernel on $\mathbb{N}_{m}$, it is therefore characteristic \citep[Theorem 7]{sriperumbudur2010hilbert}.
-As such, by definition \citep{fukumizu2004dimensionality}, $\delta$ uniquely defines a \gls{RKHS}  $\mathcal{H}_{\delta} = \overline{\mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}}$, which is the closure of the span of its kernel induced features \citep{xu2009refinement}.
+Therefore, by definition \citep{fukumizu2004dimensionality}, $\delta$ uniquely defines a \gls{RKHS}  $\mathcal{H}_{\delta} = \overline{\mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}}$, which is the closure of the span of its kernel induced features \citep{xu2009refinement}.
 For $\mathcal{Y} = \mathbb{N}_{m}$, this means that any $g : \mathbb{N}_{m} \to \mathbb{R}$ that is bounded on its discrete domain $\mathbb{N}_{m}$ is in the \gls{RKHS} of $\delta$, because we can always write $g = \sum_{y = 1}^{m} g(y) \delta(y, \cdot) \in \mathrm{span}\{\delta(y, \cdot) : y \in \mathcal{Y}\}$.
@@
 		That is, indicator functions $\mathbb{1}_{c} = \delta(c, \cdot)$, $c \in \mathbb{N}_{m}$, are simply the canonical features of $\mathcal{H}_{\delta}$.
-Such properties do not necessarily hold for continuous domains in general.
-This convenient property in the case of a discrete domain is what allows consistent estimations of decision probabilities in multiclass settings.
-In fact, $\mathcal{H}_{\delta}$ can be identified with $\mathbb{R}^{m}$.
-Note that there are no restrictions on the domain $\mathcal{X}$ as long as a kernel $k$ can be defined on it.
+Such properties do not necessarily hold for continuous target domains in general.
+For discrete target domains, this convenient property enables consistent estimations of decision probabilities.
 
 		Let $p_{c}(x) := \mathbb{P}[Y = c | X = x]$ be the \textit{decision probability function} for class $c \in \mathbb{N}_{m}$, which is the probability of the class label $Y$ being $c$ when the example $X$ is $x$.
+Note that there are no restrictions on the input domain $\mathcal{X}$ as long as a kernel $k$ can be defined on it.
+For example, $x$ could be a continuous variable in $\mathcal{X} = \mathbb{R}^{d}$.
 We begin by writing this probability as an expectation of indicator functions,
@@
 		\end{equation}
-		Therefore, the vector of empirical decision probability functions over the classes $c \in \mathbb{N}_{m}$ is
+		Let $\bvec{Y} := \begin{bmatrix} \bvec{1}_{1} & \bvec{1}_{2} & \cdots & \bvec{1}_{m} \end{bmatrix} \in \{0, 1\}^{n \times m}$ be the one hot encoded labels of $\{y_{i}\}_{i = 1}^{n}$.
+The vector of empirical decision probabilities over the classes $c \in \mathbb{N}_{m}$ is then
 		\begin{equation}
-		\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \bvec{k}(x) \in \mathbb{R}^{m},
+		\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \bvec{k}(x) \in \mathbb{R}^{m}.
 		\label{eq:empirical_decision_probability_vector}
 		\end{equation}
-		where $\bvec{Y} := \begin{bmatrix} \bvec{1}_{1} & \bvec{1}_{2} & \cdots & \bvec{1}_{m} \end{bmatrix} \in \{0, 1\}^{n \times m}$ is simply the one hot encoded labels $\{y_{i}\}_{i = 1}^{n}$.
-The \gls{MCE} is thus the multi-valued decision function $\bvec{f}(x)$ \eqref{eq:empirical_decision_probability_vector}.
-In fact, each row of the \gls{MCE} is a \gls{KRR} \citep{friedman2001elements} on binary $\{0, 1\}$-targets.
-As empirical embeddings converges, so do the empirical decision probabilities \eqref{eq:empirical_decision_probability}.
-		\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
+		Since $\mathcal{U} = \hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the solution to a regularized least squares problem in the RKHS from $k(x, \cdot) \in \mathcal{H}_{k}$ to $l(y, \cdot) \in \mathcal{H}_{l}$ \citep{lever2012conditional}, \glspl{CME} can be seen as \glspl{KRR} in the \gls{RKHS}.
+In this case, because $\mathcal{Y} = \mathbb{N}_{m}$ is discrete, $\mathcal{H}_{\delta}$ can be identified with $\mathbb{R}^{m}$.
+As a result, for discrete $\mathcal{Y} = \mathbb{N}_{m}$ the rows of the \gls{MCE} can also be seen $m$ \glspl{KRR} \citep{friedman2001elements} on binary $\{0, 1\}$-targets, where they all share the same input kernel.
+We now verify that the empirical decision probabilities \eqref{eq:empirical_decision_probability} do converge to the population decision probability.
+
+% so that we can identify $\bvec{f}(x)$ \eqref{eq:empirical_decision_probability_vector} with the empirical \gls{MCE}
+%		\begin{equation}
+%		\hat{\mathcal{E}}_{n, \lambda}[\mathcal{U}] = \frac{1}{n} \sum_{i = 1}^{n} \big\| l(y_{i}, \cdot) - \mathcal{U} k(x_{i}, \cdot) \big\|_{\mathcal{H}_{l}}^{2} + \lambda \| \mathcal{U} \|^{2}_{HS}.
+%		\label{eq:lever_objective}
+%		\end{equation}
+%		Minimizing this objective directly over $\theta \in \Theta, \lambda \in \Lambda$ for $\mathcal{U} = \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X}$ and $k = k_{\theta}$ would result in an overfitted model with small $\lambda$.
+This illustrates that the notion of model complexity during learning is especially important to ensure good generalization.
+
+		% For a \gls{CME} with discrete targets and discrete inputs, \cite{song2013kernel} showed that the population \gls{CME} simply becomes the population conditional probability.
+
+		\begin{theorem}
 			\label{thm:probability_convergence_copy}
 			Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
-See appendix A for proof and other convergence results.
+See Theorem A.2 of Appendix A for proof.
 		\end{theorem}
@@
 		\end{equation}
-		Nevertheless, classification results remains invariant, since $\hat{y}(x) = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x) = \argmax_{c \in \mathbb{N}_{m}} \tilde{p}_{c}(x)$.
+		This does not change the resulting prediction, since $\hat{y}(x) = \argmax_{c \in \mathbb{N}_{m}} \hat{p}_{c}(x) = \argmax_{c \in \mathbb{N}_{m}} \tilde{p}_{c}(x)$.
 \Cref{thm:probability_convergence_copy} also implies that eventually the effect of clip-normalization vanishes, where $\tilde{p}_{c}(x)$ approaches to both $\hat{p}_{c}(x)$ and $p_{c}(x)$ with increasing sample sizes.
 
+		This also allows \glspl{MCE} to be naturally applied to perform probabilistic classification in multiclass settings with categorical targets.
+In contrast, \glspl{SVC} do not naturally produce probabilities, while \glspl{GPC} require posterior approximations.
+Furthermore, as \glspl{SVC} and \glspl{GPC} are original binary classifiers, multiclass extensions often employ the \gls{OVA} or \gls{OVO} scheme \citep{aly2005survey}.
+Instead, fitting a single \gls{MCE} is sufficient for producing consistent multiclass probabilistic estimates.
+
 		Similar to \gls{RLSC}, \glspl{MCE} are solutions to a regularized least squares problem in a \gls{RKHS} \citep{lever2012conditional}, resulting in a similar system of linear equations.
-\glspl{RLSC} primarily differ in the way they handle the labels, in which binary labels $\{-1, 1\}$ appear directly in the squared loss instead of its kernel representation $\delta(y_{i}, \cdot)$ or, equivalently, its one hot encoded form $\bvec{y}_{i}$.
-Consequently, multiclass extensions for \gls{RLSC} either require using the \gls{OVA} scheme \citep{rifkin2003regularized}, or minimizing the summed losses across all binarized tasks instead \citep{pahikkala2012unsupervised}, producing separate classifiers for each class.
+\glspl{RLSC} primarily differ in the way they handle the labels, in which binary labels $\{-1, 1\}$ appear directly in the squared loss instead of its kernel feature $\delta(y_{i}, \cdot)$ or, equivalently, its one hot encoded form $\bvec{y}_{i}$.
+Consequently, multiclass extensions for \gls{RLSC} either require using the \gls{OVA} scheme \citep{rifkin2003regularized}, or using the summed losses across all binarized tasks for the overall least squares problem \citep{pahikkala2012unsupervised}, producing separate classifiers for each class.
 As a result, multiclass \gls{RLSC} does not produce consistent estimates of class probabilities as in \cref{thm:probability_convergence_copy} for \glspl{MCE}.
-This property allows us to employ a probabilistic loss over the output of \glspl{MCE} to learn its hyperparameters, which is known to be difficult to tune in the case of \gls{RLSC} \citep{pahikkala2012unsupervised}.
-However, simply minimizing the empirical loss could lead to overfitting due to the flexibility of the nonparametric model.
-It is therefore essential to control the model complexity of \glspl{MCE}.
 
@@
 
-		In order to design a hyperparameter learning algorithm that maximizes generalization performance without overfitting, we begin by defining a loss function as a measure for performance.
-For decision functions of the form $\bvec{f} : \mathcal{X} \to \mathcal{A} = \mathbb{R}^{m}$ whose entries are probability estimates, we employ the cross entropy loss,
+		In this section we derive learning theoretic bounds that motivates our proposed hyperparameter learning algorithm, and discuss how it can be extended in various ways to enhance scalability and performance.
+
+		We begin by defining a loss function as a measure for performance.
+For decision functions of the form $\bvec{f} : \mathcal{X} \to \mathcal{A} = \mathbb{R}^{m}$ whose entries are probability estimates, we employ a modified cross entropy loss,
 		\begin{equation}
@@
 		\end{equation}
-		to express risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$.
+		to express risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$ where usually $\epsilon << 1$.
 Note that we employ the loss on the original probability estimates \eqref{eq:empirical_decision_probability_vector}, not the clip-normalized version \eqref{eq:empirical_decision_probability_clip_normalized}.
+We employ this loss in virtue of \cref{thm:probability_convergence_copy}, where we expect $\bvec{f}(x)$ \eqref{eq:empirical_decision_probability_vector} to be close to the population decision probability.
+In contrast, direct outputs from \glspl{SVC}, \glspl{GPC}, or \glspl{RLSC} are not consistent probability estimates and cannot take advantage of \eqref{eq:cross_entropy_loss_copy} easily.
+
+		However, simply minimizing the empirical loss $\frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(y_{i}, \bvec{f}_{\theta, \lambda}(x_{i}))$ over the hyperparameters $(\theta, \lambda)$ could lead to an overfitted model.
+We therefore turn to using Rademacher complexity to control the model complexity of \glspl{MCE}.
+
+		Let $\Theta$ and $\Lambda$ be a space of kernel hyperparameters and regularization parameters respectively. We define the class of \glspl{MCE} over these hyperparameter spaces by
+
+		\begin{equation}
+			F_{n}(\Theta, \Lambda) := \{ \bvec{f}_{\theta, \lambda}(x) : \theta \in \Theta, \lambda \in \Lambda \}.
+			\label{eq:predictor_class_copy}
+		\end{equation}
+
+%		The Rademacher complexity \citep{bartlett2002rademacher} of the function class $F_{n}(\Theta, \Lambda)$ is
+%					
+%		\begin{equation}
+%			\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) := \mathbb{E}\bigg[\sup_{\theta \in \Theta, \lambda \in \Lambda} \Big\| \frac{2}{n} \sum_{i = 1}^{n} \sigma_{i}\bvec{f}_{\theta, \lambda}(X_{i}) \Big\|\bigg].
+%		\end{equation}
+
+		We denote $\hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \equiv W_{\theta, \lambda}^{T}$ to reflect the dependence on $(\theta, \lambda)$.
+We first restrict the space of hyperparameters by the norms of $W_{\theta, \lambda}$ and $k_{\theta}(x, x)$ to obtain an upper bound to the Rademacher complexity of $F_{n}(\Theta, \Lambda)$.
+
+		\begin{theorem}
+			\label{thm:rademacher_complexity_bound_copy}
+			Assume that $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
+Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$, $\alpha > 0$, is bounded in \gls{RKHS} norm for all $x \in \mathcal{X}, \theta \in \Theta$.
+For any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of \glspl{MCE} $F_{n}(\Theta, \Lambda)$ \eqref{eq:predictor_class_copy} defined over $\theta \in \Theta, \lambda \in \Lambda$ is bounded by
+			\begin{equation}
+			\mathcal{R}_{n}(F_{n}(\Theta, \Lambda)) \leq 2 \alpha \rho.
+			\label{eq:rademacher_complexity_bound_copy}
+			\end{equation}
+			See Theorem B.1 of Appendix B for proof.
+		\end{theorem}
 
 		\cite{bartlett2002rademacher} showed that the expected risk can be bounded with high probability using the empirical risk and the Rademacher complexity of the loss composed with the function class.
+For a Lipchitz loss, \citet{ledoux2013probability} further showed that the latter can be bounded using the Rademacher complexity of the function class itself.
+We use these two results to arrive at the following probabilistic upper bound to our expected loss.
+We refer the reader to Appendix B for detailed discussion.
+
+%		\begin{lemma}
+%			\label{thm:expected_loss_bound_for_multiclass_conditional_embedding}
+%			
+%			Suppose that $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
+Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$, $\alpha > 0$, is bounded in \gls{RKHS} norm for all $x \in \mathcal{X}, \theta \in \Theta$.
+Define $M_{\epsilon} = - \log{\epsilon}$.
+For any integer $n \in \mathbb{N}_{+}$, any $\epsilon \in (0, 1)$, and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability of at least $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
+%			
+%			\begin{equation}
+%			\begin{aligned}
+%				&\frac{1}{M_{\epsilon}} \mathbb{E}[\mathcal{L}_{\epsilon}(Y, f(X))] \leq \frac{1}{n M_{\epsilon}} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) \\
+%				&+ 4 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \alpha \rho + \sqrt{\frac{8}{n} \log{\frac{2}{\beta}}},
+%			\end{aligned}
+%			\label{eq:expected_loss_bound_for_multiclass_conditional_embedding_copy}
+%			\end{equation}
+%			
+%			See Lemma B.5 of Appendix B for proof.
+%		\end{lemma}
+
+		\begin{theorem}
+			\label{thm:specific_expected_loss_bound_for_multiclass_conditional_embedding_copy}
+
+			Assume the same assumptions as \cref{thm:rademacher_complexity_bound_copy}.
+For any integer $n \in \mathbb{N}_{+}$, any $\epsilon \in (0, e^{-1})$, and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability of at least $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
+
+			\begin{equation}
+			\begin{aligned}
+				&\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) \\
+				&+ 4 e \; \alpha \rho + \sqrt{\frac{8}{n} \log{\frac{2}{\beta}}}.
+			\end{aligned}
+			\label{eq:specific_expected_loss_bound_for_multiclass_conditional_embedding_copy}
+			\end{equation}
+
+			See Lemma B.6 of Appendix B for proof.
+		\end{theorem}
+
+		However, for hyperparameter learning, we would require a risk bound for specific choice of hyperparameters, not just for a set of hyperparameters.
+For some $\tilde{\theta} \in \Theta$ and $\tilde{\lambda} \in \Lambda$, we construct a subset of hyperparameters $\Xi(\tilde{\theta}, \tilde{\lambda}) \subseteq \Theta \times \Lambda$ defined by $\Xi(\tilde{\theta}, \tilde{\lambda}) := \{ (\theta, \lambda) \in \Theta \times \Lambda : \| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}, \; \sup_{x \in \mathcal{X}} k_{\theta}(x, x) \leq \alpha^{2}(\tilde{\theta}) := \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x) \}$.
+Clearly, this subset is non-empty, since $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ is itself an element of this subset.
+Thus, we can assert that $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ is bounded for all $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, and that $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$ is bounded for all $x \in \mathcal{X}, (\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$.
+
+		We can now apply \cref{thm:specific_expected_loss_bound_for_multiclass_conditional_embedding_copy} with the choice of $\rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ and $\alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$.
+The probabilistic statement \eqref{eq:specific_expected_loss_bound_for_multiclass_conditional_embedding_copy} then only holds for $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$.
+However, we know that $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, so we can choose $\theta \leftarrow \tilde{\theta}$ and $\lambda \leftarrow \tilde{\lambda}$.
+Since the only hyperparameters that appear now are $(\tilde{\theta}, \tilde{\lambda})$, we replace these symbols with a general $(\theta, \lambda)$ again to avoid cluttered notation.
+We now arrive at our final result.
+
+%		\cite{bartlett2002rademacher} showed that the expected risk can be bounded with high probability using the empirical risk and the Rademacher complexity of the loss composed with the function class.
 For a Lipchitz loss, \citet{ledoux2013probability} further showed that the latter can be bounded using the Rademacher complexity of the function class itself.
@@
 
-		\begin{theorem}[Expected Risk Bound for a choice of \gls{MCE} Hyperparameters]
+		\begin{theorem}
 			\label{thm:expected_risk_bound_hyperparameter_learning_copy}
@@
 			where $r(\theta, \lambda) := \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda}) \sup_{x \in \mathcal{X}} k_{\theta}(x, x)}$ and $V_{\theta, \lambda} := (K_{\theta} + n \lambda I)^{-1} \bvec{Y}$.
+			See Theorem B.8 of Appendix B for proof.
 		\end{theorem}
 
-		We refer the reader to appendix B for proof.
 		In order for the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} to be non-trivial, we focus on bounded kernels in the sense that $\alpha^{2}(\theta) := \sup_{x \in \mathcal{X}} k_{\theta}(x, x) < \infty$.
@@
 Mat\'{e}rn) with sensitivity and length scales $\theta = (\sigma_{f}, \Sigma)$, for example, have $\alpha(\theta) = \sigma_{f}$.
-Since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} is true with probability $1 - \beta$ when the random variables $(X_{i}, Y_{i})$ are realized as the training observations $(x_{i}, y_{i})$.
-We therefore employ this upper bound as the learning objective, and use gradient based optimizers such as gradient descent or Adam \citep{kingma2014adam} for hyperparameter learning,
+Since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} holds with probability $1 - \beta$ when the random variables $(X_{i}, Y_{i})$ are realized as the training observations $(x_{i}, y_{i})$.
+Motivated by this, we employ this upper bound as the learning objective for hyperparameter learning,
 		\begin{equation}
@@
 		\end{equation}
-		Since \cref{thm:expected_risk_bound_hyperparameter_learning_copy} holds for any $n \in \mathbb{N}_{+}$ and any set of data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ from $\mathbb{P}_{X Y}$, with the trade-off of relaxing bound tightness through $\sqrt{8 \log{(2 / \beta)} / n}$, the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} also holds with high probability for a subset of the training data.
-This enables scalable hyperparameter learning through batch stochastic gradient updates, where each gradient update stochastically improves a different upper bound of the generalization risk.
-Because this bound holds with high probability over \textit{iid} samples, through randomly selecting a batch of training examples that comes from the same distribution, the resulting stochastic gradient will improve a strict upper bound with the same high probability.
-We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:multiclass_conditional_embedding_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size.
-The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is necessary only for inference, instead of once every learning iteration.
-It can be further avoided by using random Fourier features \citep{rahimi2008random} or kernel herding \citep{chen2010super} to approximate the already learned \gls{MCE}.
-All further inference takes $O(n^{2})$ time, or potentially less with approximation, using back substitution.
 
@@
 
-	\section{Extensions}
+	\subsection{Extensions}
 	\label{sec:extensions}
+
+		\paragraph{Batch Stochastic Gradient Update} Since \cref{thm:expected_risk_bound_hyperparameter_learning_copy} holds for any $n \in \mathbb{N}_{+}$ and any set of data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ from $\mathbb{P}_{X Y}$, the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} also holds with high probability for a batch subset of the training data.
+However, the batch size cannot be too small, in order to keep the constant $\sqrt{8 \log{(2 / \beta)} / n}$ relatively small.
+We therefore propose to use only a random batch subset of the data to perform each gradient update.
+This enables scalable hyperparameter learning through batch stochastic gradient updates, where each gradient update stochastically improves a different probabilistic upper bound of the generalization risk.
+Note that without this bound, it is not straightforward to simply apply stochastic gradient updates to optimize $q$, since $r$ depends on the dataset but is not written in terms of a summation over the data.
+We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:multiclass_conditional_embedding_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size.
+The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is necessary only for inference, instead of once every learning iteration.
+It can be further avoided by using random Fourier features \citep{rahimi2008random} or kernel herding \citep{chen2010super} to approximate the already learned \gls{MCE}.
+All further inference takes $O(n^{2})$ time, or potentially less with approximation, using back substitution.
 
@@
 
-		Our learning algorithm does not restrict the way the kernel $k_{\theta}$ is constructed from its parameters $\theta \in \Theta$.
-One particularly useful class of \glspl{MCE} are those where the input kernel $k_{\theta}(x, x') = \langle \varphi_{\theta}(x), \varphi_{\theta}(x') \rangle$ is constructed from neural networks $\varphi_{\theta} : \mathcal{X} \to \mathbb{R}^{p}$ explicitly.
+		\paragraph{Conditional Embedding Network} Our learning algorithm does not restrict the way the kernel $k_{\theta}$ is constructed from its parameters $\theta \in \Theta$.
+One particularly useful type of \glspl{MCE} are those where the input kernel $k_{\theta}(x, x') = \langle \varphi_{\theta}(x), \varphi_{\theta}(x') \rangle$ is constructed from neural networks $\varphi_{\theta} : \mathcal{X} \to \mathbb{R}^{p}$ explicitly.
 We refer to \glspl{MCE} constructed this way as \glspl{CEN}.
-Similar to \cite{wilson2016stochastic} where the neural network weights and biases are learned jointly under the \gls{GP} marginal likelihood objective, \glspl{CEN} also learn network weights and biases under \eqref{eq:learning_objective}.
-These kernels benefit in both scalability and expressibility.
-For large datasets, the $n \times n$ Cholesky decomposition required for full gradient updates in \cref{alg:multiclass_conditional_embedding_training} can be transformed into a $p \times p$ decomposition by the Woodbury matrix inversion identity \citep{higham2002accuracy}, reducing the time complexity to $O(p^{3} + np^{2})$.
-This allows scalability for $n >> p$ without using stochastic gradient updates so that the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} can be as tight as possible for a given $n$.
+In these cases, the weights and biases of the neural network become the kernel parameters $\theta$ of the \glspl{CEN}.
+We can therefore network weights and biases jointly under \eqref{eq:learning_objective}.
+\glspl{CEN} can also scale easily, since the $n \times n$ Cholesky decomposition required for full gradient updates in \cref{alg:multiclass_conditional_embedding_training} can be transformed into a $p \times p$ decomposition by the Woodbury matrix inversion identity \citep{higham2002accuracy}, reducing the time complexity to $O(p^{3} + np^{2})$.
+This allows scalable learning for $n >> p$ even without using batch gradient updates.
 For inference, standard map reduce methods can be used.
-Neural networks are by construction compositional, and thus latent representations of deeper networks undergo more transformations to generate a smaller and explicit collection of expressive nonlinear features, leading to a deeper but narrower model architecture.
-This is in contrast to the potentially infinitely many implicit features from nonlinear kernels, which in turn define a shallower but wider model architecture.
 We direct the reader to appendix C for detailed discussion on the various \gls{MCE} architectures and their implementation as compared to \cref{alg:multiclass_conditional_embedding_training}.
 
-		While we simply instantiated $(X_{i}, Y_{i})$ to be the training observations in \cref{thm:expected_risk_bound_hyperparameter_learning_copy} to obtain \cref{alg:multiclass_conditional_embedding_training}, this does not have to be the case for batch updates.
+		%Neural networks are by construction compositional, and thus latent representations of deeper networks undergo more transformations to generate a smaller and explicit collection of expressive nonlinear features, leading to a deeper but narrower model architecture.
+This is in contrast to the potentially infinitely many implicit features from nonlinear kernels, which in turn define a shallower but wider model architecture.
+
+		\paragraph{Batch Validation} While we simply instantiated $(X_{i}, Y_{i})$ to be the training observations in \cref{thm:expected_risk_bound_hyperparameter_learning_copy} to obtain \eqref{eq:learning_objective}, this does not have to be the case for batch updates.
 Instead, in each learning iteration, we could further split the batch into two sub-batches - one for training and one for validation.
-The training batch is used to form the \gls{MCE} $\bvec{f}_{\theta, \lambda}$ and \gls{RCB} $r(\theta, \lambda)$, while we evaluate the \gls{MCE} on the validation batch,
+The training batch is used to form the \gls{MCE} $\bvec{f}_{\theta, \lambda}$ and \gls{RCB} $r(\theta, \lambda)$, while we evaluate the empirical risk on the validation batch,
 		\begin{equation}
@@
 Note that in contrast to standard cross validation, not all data is required for each update due to the presence of the \gls{RCB}.
-Furthermore, although the multiplier on the \gls{RCB} is $4 e$, in practice one can often obtain a tighter bound with a smaller multiplier.
-As such, generalization performance can improve if we uses a multiplier $\tau < 4 e$.
+Furthermore, although the multiplier on the \gls{RCB} is $4 e$, experiments show that generalization performance can improve if we uses a smaller multiplier $\tau < 4 e$.
 In practice, these two extensions work well together.
@@
 	\paragraph{Toy Example}
-
-		The first two of four total attributes of the iris dataset \citep{fisher1936use} are known to have class labels that are non-separable by any means, in that the same example $x \in \mathbb{R}^{2}$ may be assigned different output labels $y \in \mathbb{N}_{3} := \{1, 2, 3\}$.
-In these difficult scenarios, the notion of model complexity is extremely important, and the success of a learning algorithm greatly depends on how it balances training performance and model complexity to avoid both underfitting and overfitting.
-
-		\Cref{fig:iris} demonstrates \cref{alg:multiclass_conditional_embedding_training} with full gradient updates ($n_{b} = n$) to learn hyperparameters of the \gls{MCE} on the two attribute iris dataset.
-The kernel used is isotropic Gaussian with diagonal length scales $\Sigma = \ell^{2} I_{2}$ and sensitivity $\alpha = \sigma_{f}$, so that the hyperparameters are $\theta = (\alpha, \ell)$ and $\lambda$.
-We evaluate the performance of the learning algorithm on a withheld test set using 20\% of the available 150 data samples.
-Attributes are scaled into the unit range $[0, 1]$ and decision probability maps are plotted for the region $[-0.5, 1.05]^{2}$, where the red, green, and blue colour channels represent the clip-normalized decision probability \eqref{eq:empirical_decision_probability_clip_normalized} for classes $c = 1, 2, 3$.
-We begin from two initial scenarios, one originally overfitting ($\alpha_{o} = 0.01$, $\ell_{o} = 0.035$, $\lambda_{o} = 10^{-6}$) and another underfitting ($\alpha_{u} = 1$, $\ell_{u} = 1$, $\lambda_{u} = 1$) the training data.
-Initially, both models perform sub-optimally with a test accuracy of 56.67\%.
-We see that the \gls{RCB} $r(\theta, \lambda)$ appropriately measures the amount of overfitting with $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = 4.33$ and $r((\alpha_{u}, \ell_{u}), \lambda_{u}) = 0.31$.
-We then learn hyperparameters with \cref{alg:multiclass_conditional_embedding_training} for 500 iterations from both initializations at rate $\eta = 0.01$, where both models converges to a balanced model with appropriate \glspl{RCB} $r((\alpha_{o}, \ell_{o}), \lambda_{o}) = r((0.01, 0.24), 8.62 \times 10^{-7}) = 2.23 \approx 2.14 = r((\alpha_{u}, \ell_{u}), \lambda_{u}) = r((5.1, 0.24), 0.20)$ and an improved test accuracy of 73.33\%.
-In particular, the initially overfitted model learns a simpler model at the expense of lower training performance, emphasizing the benefits of complexity based regularization, without which the learning would only maximize training performance at the cost of further overfitting.
-Meanwhile, the initially underfitted model learns to increase complexity to improve the sub-optimal performance on the training set.
-In both scenarios, our learning algorithm improved performance on the test set.
-
-	\paragraph{UCI Datasets}
-
-		%	\begin{table*}[t]
-		%		\caption{Classification accuracy (\%) on UCI datasets}
-		%		\label{tab:uci_experiments}
-		%		\centering
-		%		\begin{tabular}{lcccccccc}	
-		%			Dataset \hspace{\fill} $(n, d, m)$ & G\gls{MCE} & G\gls{MCE}-SGD & KEN-1 & KEN-2 & ERM & CV & MED & Others \\
-		%			\midrule
-		%			\texttt{banknote} \hspace{\fill} (1372, 4, 2) & $\mathbf{99.9 \pm 0.2}$ & $98.8 \pm 0.9$ & $99.5 \pm 1.0$ & $99.4 \pm 0.9$ & $\mathbf{99.9 \pm 0.2}$ & $\mathbf{99.9 \pm 0.2}$ & $92.0 \pm 4.3$ & 99.78\textsuperscript{a} \\
-		%			\texttt{ecoli} \hspace{\fill} (336, 7, 8) & $\mathbf{87.5 \pm 4.4}$ & $84.5 \pm 5.0$ & $\mathbf{87.5 \pm 3.2}$ & $86.3 \pm 6.0$ & $72.1 \pm 20.5$ & $73.8 \pm 23.8$ & $42.1 \pm 47.7$ & 81.1\textsuperscript{b} \\
-		%			\texttt{robot} \hspace{\fill} (5456, 24, 4) & $\mathbf{96.7 \pm 0.9}$ & $95.5 \pm 0.9$ & $82.3 \pm 7.1$ & $94.5 \pm 0.8$ & $91.0 \pm 3.7$ & $90.9 \pm 3.4$ & $81.1 \pm 6.2$ & 97.59\textsuperscript{c} \\
-		%			\texttt{segment} \hspace{\fill} (2310, 19, 7) & $\mathbf{98.4 \pm 0.8}$ & $96.1 \pm 1.5$ & $94.6 \pm 1.6$ & $96.7 \pm 1.1$ & $98.1 \pm 1.1$ & $98.3 \pm 1.3$ & $27.3 \pm 26.4$ & 96.83\textsuperscript{d} \\
-		%			\texttt{wine} \hspace{\fill} (178, 13, 3) & $\mathbf{97.2 \pm 3.7}$ & $93.3 \pm 6.0$ & $96.1 \pm 5.0$ & $97.2 \pm 5.1$ & $93.9 \pm 5.2$ & $93.3 \pm 7.4$ & $93.3 \pm 7.8$ & 100\textsuperscript{e} \\
-		%			\texttt{yeast} \hspace{\fill} (1484, 8, 10) & $52.5 \pm 2.1$ & $\mathbf{60.3 \pm 4.4}$ & $55.8 \pm 5.0$ & $59.6 \pm 4.0$ & $45.9 \pm 6.4$ & $58.0 \pm 5.8$ & $31.2 \pm 14.1$ & 55.0\textsuperscript{b} \\
-		%		\end{tabular}
-		%	\end{table*}
 
@@
 		\end{table*}
+
+		The first two of four total attributes of the iris dataset \citep{fisher1936use} are known to have class labels that are non-separable by any means, in that the same example $x \in \mathbb{R}^{2}$ may be assigned different output labels $y \in \mathbb{N}_{3} := \{1, 2, 3\}$.
+In these difficult scenarios, the notion of model complexity is extremely important, and the success of a learning algorithm greatly depends on how it balances training performance and model complexity to avoid both underfitting and overfitting.
+
+		\Cref{fig:iris} demonstrates \cref{alg:multiclass_conditional_embedding_training} with full gradient updates ($n_{b} = n$) to learn hyperparameters of the \gls{MCE} on the two attribute iris dataset.
+The kernel used is isotropic Gaussian with diagonal length scales $\Sigma = \ell^{2} I_{2}$ and sensitivity $\alpha = \sigma_{f}$, so that the hyperparameters are $\theta = (\alpha, \ell)$ and $\lambda$.
+We evaluate the performance of the learning algorithm on a withheld test set using 20\% of the available 150 data samples.
+Attributes are scaled into the unit range $[0, 1]$ and decision probability maps are plotted for the region $[-0.5, 1.05]^{2}$, where the red, green, and blue color channels represent the clip-normalized decision probability \eqref{eq:empirical_decision_probability_clip_normalized} for classes $c = 1, 2, 3$.
+We begin from two initial sets of hyperparameters, one originally overfitting and another underfitting the training data.
+Initially, both models perform sub-optimally with a test accuracy of 56.67\%.
+We see that the \gls{RCB} $r(\theta, \lambda)$ appropriately measures the amount of overfitting with high (resp.
+low) values for the overfitted (resp.
+underfitted) model.
+We then learn hyperparameters with \cref{alg:multiclass_conditional_embedding_training} for 500 iterations from both initializations at rate $\eta = 0.01$, where both models converges to a balanced model with a moderate \gls{RCB} and an improved test accuracy of 73.33\%.
+In particular, the initially overfitted model learns a simpler model at the expense of lower training performance, emphasizing the benefits of complexity based regularization, without which the learning would only maximize training performance at the cost of further overfitting.
+Meanwhile, the initially underfitted model learns to increase complexity to improve the sub-optimal performance on the training set.
+
+	\paragraph{UCI Datasets}
 
@@
 
-	\paragraph{MNIST by learning pixel length scales}
-
-		We apply \cref{alg:multiclass_conditional_embedding_training} to learn length scales of anisotropic Gaussian, or \gls{ARD}, kernels on pixels of the MNIST digits dataset \citep{lecun1998gradient}.
-In the top left plot of \cref{fig:mnist_experiments}, we train on datasets of varying sizes, from 50 to 5000 images, and benchmark performance on the standard test set of 10000 images.
-All hyperparameters are initialized to 1 before learning.
-We train both \glspl{SVC} and \glspl{GPC} under the \gls{OVA} scheme, and use a Laplace approximation for the \gls{GPC} posterior.
-In all cases \glspl{MCE} outperform \glspl{SVC}, as standard \gls{SVC} training cannot learn hyperparameters unless expensive cross validation is performed.
-\glspl{MCE} also outperform \glspl{GPC} as more data becomes available.
-Under the \gls{OVA} scheme, a set of kernel hyperparameters are learned to distinguish each class against the rest, while our approach learns a consistent set of hyperparameters for all classes.
-Consequently, for 5000 data points, the computational time required for hyperparameter learning of standard \glspl{GPC} is on the order of days even for learning isotropic Gaussian kernels, while \cref{alg:multiclass_conditional_embedding_training} is on the order of hours even without batch updates for learning anistropic Gaussian kernels.
-We also compare hyperparameter learning with and without the \gls{RCB}.
-For small $n$ below 750 samples, the latter outperforms the former (e.g.
-86.69\% and 86.96\% for $n = 500$), while for large $n$ the former outperforms the latter (e.g.
-96.05\% and 95.3\% for $n= 5000$).
-This verifies that complexity based regularization becomes especially important as data size grows, when overfitting starts to decrease generalization performance.
-Our bound is also tighter with larger $n$, so that generalization performance improves with more data.
-The images at the bottom of \cref{fig:mnist_experiments} show the pixel length scales learned through batch stochastic gradient updates ($n_{b} = 1200$) on all available training images of different groups of digits, demonstrating the most discriminative regions for classification.
-%In particular, the most discriminative regions are usually around the edges of the digits, subject to slight intraclass translations.
-
-		% % % Removed sentences
-		% We first demonstrate the test performance of \glspl{MCE} as the training set increases in size, verifying \cref{thm:probability_convergence_copy} in that decision probabilities converge to the true and thus test distribution as $n$ increases.
-		% The MNIST dataset has $d = 28^{2} = 784$ pixel dimensions, yet with only $n = 50, 150, 250$ training samples, the \gls{MCE} achieves a test accuracy of 45.7\%, 70.09\%, and 79.37\% respectively, compared to 18.13\%, 37.43\%, and 53.81\% from SVCs.
-
-	\paragraph{MNIST by learning convolutional features}
+	\paragraph{Learning convolutional layers}
 
@@
 
-		We now apply \cref{alg:multiclass_conditional_embedding_training} to train a \gls{CEN} with convolutional features on MNIST.
+	\paragraph{Learning pixel relevance}
+
+		We apply \cref{alg:multiclass_conditional_embedding_training} to learn length scales of anisotropic Gaussian, or \gls{ARD}, kernels on pixels of the MNIST digits dataset \citep{lecun1998gradient}.
+In the top left plot of \cref{fig:mnist_experiments}, we train on datasets of varying sizes, from 50 to 5000 images, and show the accuracy on the standard test set of 10000 images.
+All hyperparameters are initialized to 1 before learning.
+We train both \glspl{SVC} and \glspl{GPC} under the \gls{OVA} scheme, and use a Laplace approximation for the \gls{GPC} posterior.
+In all cases \glspl{MCE} outperform \glspl{SVC} as it cannot learn hyperparameters without expensive cross validation.
+\glspl{MCE} also outperform \glspl{GPC} as more data becomes available.
+Under the \gls{OVA} scheme, the \gls{GPC} approach learns a set of kernel hyperparameters for each class, while our approach learns a consistent set of hyperparameters for all classes.
+Consequently, for 5000 data points, the computational time required for hyperparameter learning of \glspl{GPC} is on the order of days even for isotropic Gaussian kernels, while \cref{alg:multiclass_conditional_embedding_training} is on the order of hours for anistropic Gaussian kernels even without batch updates.
+We also compare hyperparameter learning with and without the \gls{RCB}.
+For small $n$ below 750 samples, the latter outperforms the former (e.g.
+86.69\% and 86.96\% for $n = 500$), while for large $n$ the former outperforms the latter (e.g.
+96.05\% and 95.3\% for $n= 5000$).
+This verifies that complexity based regularization becomes especially important as data size grows, when overfitting starts to decrease generalization performance.
+The images at the bottom of \cref{fig:mnist_experiments} show the pixel length scales learned through batch stochastic gradient updates ($n_{b} = 1200$) over all available training images the groups of digits shown, demonstrating the most discriminative regions.
+%In particular, the most discriminative regions are usually around the edges of the digits, subject to slight intraclass translations.
+
+		% % % Removed sentences
+		% We first demonstrate the test performance of \glspl{MCE} as the training set increases in size, verifying \cref{thm:probability_convergence_copy} in that decision probabilities converge to the true and thus test distribution as $n$ increases.
+		% The MNIST dataset has $d = 28^{2} = 784$ pixel dimensions, yet with only $n = 50, 150, 250$ training samples, the \gls{MCE} achieves a test accuracy of 45.7\%, 70.09\%, and 79.37\% respectively, compared to 18.13\%, 37.43\%, and 53.81\% from SVCs.
+
+		We now apply \cref{alg:multiclass_conditional_embedding_training} to train a \gls{CEN} with convolutional layers on MNIST.
 We employ an example architecture from the TensorFlow tutorial on deep MNIST classification \citep{abadi2016tensorflow}.
@@
 We then train both networks from the same initialization using batch updates of $n_{b} = 6000$ images for 800 epochs, with learning rate $\eta = 0.01$.
-All biases and standard deviations of zero mean truncated normal distributed weights are initialized to 0.1.
+All biases and weight standard deviations are initialized to 0.1.
 The network weights and biases of the \gls{CEN} are learned jointly with the regularization parameter, initialized to $\lambda = 10$, under our learning objective \eqref{eq:learning_objective}, while the original \gls{CNN} is trained under its usual cross entropy loss.
@@
 
-	\section{Conclusion}
+	\section{Conclusion and Future Work}
 
-		We propose a scalable hyperparameter learning framework for \glspl{MCE}.
-Because nonparametric models have infinite capacity and can potentially overfit, we derive learning-theoretic bounds to regularize the \gls{MCE} in a way that minimizes expected generalization risk.
-The resulting bound justifies the use of stochastic gradient updates for hyperparameter learning, which we verify experimentally.
-Our algorithm does not impose restrictions to the form of the positive definite kernel, and in particular can perform end-to-end learning on a neural network by replacing the softmax layer with a \gls{MCE}, which we demonstrate on UCI datasets and MNIST digits, where it outperforms the original convolutional neural network in the latter.
+		We developed a scalable hyperparameter learning framework for conditional mean embeddings with categorical targets based on Rademacher complexity bounds.
+These bounds reveal a novel data-dependent quantity $r(\theta, \lambda)$ which reflect the model complexity of \glspl{CME}, which we use as an regularization term in addition to the empirical loss for hyperparameter learning.
+Similar to a regularized least squares problem, it remains to be established what type of prior on the hyperparameters, if any, could correspond to such a regularizer, which would enable a Bayesian interpretation of our approach.
+We also envision that such a quantity could potentially be generalized to \glspl{CME} with arbitrary targets which would enable hyperparameter learning for general conditional mean embeddings in a way that is optimized for the loss relevant to the prediction task.
 
-		This framework can be incorporated and extended into techniques that require appropriately learned conditional embeddings.
+%		Because nonparametric models have infinite capacity and can potentially overfit, we use learning-theoretic bounds to derive a measure $r(\theta, \lambda)$ of model complexity.
+We propose a learning objective $q(\theta, \lambda)$ for hyperparameter learning, and derive a scalable learning algorithm that only requires batch gradient updates.
+Our algorithm does not impose restrictions to the form of the positive definite kernel, and in particular can perform end-to-end learning on a neural network by replacing the softmax layer with a \gls{MCE}, which we demonstrate on UCI datasets and MNIST, where it outperforms the original \gls{CNN} in the latter.
+
+%		This framework can be incorporated and extended into techniques that require appropriately learned conditional embeddings.
 In particular, nonparametric probabilistic inference can be carried out in the \gls{RKHS} to obtain joint and reverse conditional embeddings, where mode decoding, density recovery, and sampling techniques can lead to effective generative models now that hyperparameters are learned.

### 2018-03-29 AISTATS2018/cake_aistats2018.tex
Previous changes

@@
 \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage[colorlinks=true,linkcolor=green,citecolor=cyan]{hyperref}       % hyperlinks
+\usepackage[colorlinks=true,linkcolor=black,citecolor=black]{hyperref}       % hyperlinks
 \usepackage{url}            % simple URL typesetting
@@
 The marginal likelihood arises from its Bayesian formulation, and exhibits certain desirable properties -- in particular, the ability to automatically balance between data fit and model complexity.
-On the other hand, \glspl{CME} are not necessarily Bayesian, and hence they do not benefit from a natural marginal likelihood formulation, yet such a balance is critical when generalizing the model beyond unseen examples.
+On the other hand, \glspl{CME} are not necessarily Bayesian, and hence they do not benefit from a natural marginal likelihood formulation, yet such a balance is critical when generalizing the model beyond known examples.
 
@@
 In this case, because $\mathcal{Y} = \mathbb{N}_{m}$ is discrete, $\mathcal{H}_{\delta}$ can be identified with $\mathbb{R}^{m}$.
-As a result, for discrete $\mathcal{Y} = \mathbb{N}_{m}$ the rows of the \gls{MCE} can also be seen $m$ \glspl{KRR} \citep{friedman2001elements} on binary $\{0, 1\}$-targets, where they all share the same input kernel.
+As a result, for discrete $\mathcal{Y} = \mathbb{N}_{m}$ the rows of the \gls{MCE} can also be seen as $m$ \glspl{KRR} \citep{friedman2001elements} on binary $\{0, 1\}$-targets, where they all share the same input kernel.
 We now verify that the empirical decision probabilities \eqref{eq:empirical_decision_probability} do converge to the population decision probability.
@@
 In contrast, \glspl{SVC} do not naturally produce probabilities, while \glspl{GPC} require posterior approximations.
-Furthermore, as \glspl{SVC} and \glspl{GPC} are original binary classifiers, multiclass extensions often employ the \gls{OVA} or \gls{OVO} scheme \citep{aly2005survey}.
+Furthermore, multiclass extensions to \glspl{SVC} and \glspl{GPC} often employ the \gls{OVA} or \gls{OVO} scheme \citep{aly2005survey}, resulting in multiple separate binary classifiers.
 Instead, fitting a single \gls{MCE} is sufficient for producing consistent multiclass probabilistic estimates.
@@
 		In this section we derive learning theoretic bounds that motivates our proposed hyperparameter learning algorithm, and discuss how it can be extended in various ways to enhance scalability and performance.
+From here onwards, we denote $\theta$ as the kernel hyperparameters of the kernel $k = k_{\theta}$.
 
@@
 		However, simply minimizing the empirical loss $\frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(y_{i}, \bvec{f}_{\theta, \lambda}(x_{i}))$ over the hyperparameters $(\theta, \lambda)$ could lead to an overfitted model.
-We therefore turn to using Rademacher complexity to control the model complexity of \glspl{MCE}.
+We therefore employ Rademacher complexity bounds to control the model complexity of \glspl{MCE}.
 
 		Let $\Theta$ and $\Lambda$ be a space of kernel hyperparameters and regularization parameters respectively. We define the class of \glspl{MCE} over these hyperparameter spaces by	
-
 		\begin{equation}
@@
 		\end{equation}
+		We denote $W_{\theta, \lambda}^{T} \equiv \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X}$ and $\| W_{\theta, \lambda} \|_{\mathrm{tr}} = \| \hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \|_{HS}$ to reflect the dependence on $(\theta, \lambda)$ and for notational simplicity.
+We first restrict the space of hyperparameters by the norms of $W_{\theta, \lambda}$ and $k_{\theta}(x, x)$ to obtain an upper bound to the Rademacher complexity of $F_{n}(\Theta, \Lambda)$.
 
@@
 %		\end{equation}
-
-		We denote $\hat{\mathcal{U}}^{(\theta, \lambda)}_{Y | X} \equiv W_{\theta, \lambda}^{T}$ to reflect the dependence on $(\theta, \lambda)$.
-We first restrict the space of hyperparameters by the norms of $W_{\theta, \lambda}$ and $k_{\theta}(x, x)$ to obtain an upper bound to the Rademacher complexity of $F_{n}(\Theta, \Lambda)$.
 
@@
 		\cite{bartlett2002rademacher} showed that the expected risk can be bounded with high probability using the empirical risk and the Rademacher complexity of the loss composed with the function class.
-For a Lipchitz loss, \citet{ledoux2013probability} further showed that the latter can be bounded using the Rademacher complexity of the function class itself.
+For a Lipchitz loss, \citet{ledoux2013probability} further showed that the latter quantity can be bounded using the Rademacher complexity of the function class itself.
 We use these two results to arrive at the following probabilistic upper bound to our expected loss.
@@
 			\begin{aligned}
-				&\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) \\
-				&+ 4 e \; \alpha \rho + \sqrt{\frac{8}{n} \log{\frac{2}{\beta}}}.
+				&\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))]  \\
+				&\leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 e \; \alpha \rho + \sqrt{\frac{8}{n} \log{\frac{2}{\beta}}}.
 			\end{aligned}
@@
 
-			See Lemma B.6 of Appendix B for proof.
+			See Theorem B.6 of Appendix B for proof.
 		\end{theorem}
@@
 
-		We can now apply \cref{thm:specific_expected_loss_bound_for_multiclass_conditional_embedding_copy} with the choice of $\rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ and $\alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$.
-The probabilistic statement \eqref{eq:specific_expected_loss_bound_for_multiclass_conditional_embedding_copy} then only holds for $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$.
-However, we know that $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, so we can choose $\theta \leftarrow \tilde{\theta}$ and $\lambda \leftarrow \tilde{\lambda}$.
-Since the only hyperparameters that appear now are $(\tilde{\theta}, \tilde{\lambda})$, we replace these symbols with a general $(\theta, \lambda)$ again to avoid cluttered notation.
+		We can now choose $\tilde{\theta} \in \Theta$, $\tilde{\lambda} \in \Lambda$ and apply \cref{thm:specific_expected_loss_bound_for_multiclass_conditional_embedding_copy} with the choice of $\rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ and $\alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$ and by considering only the hyperparameters $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$.
+The probabilistic statement \eqref{eq:specific_expected_loss_bound_for_multiclass_conditional_embedding_copy} then only holds for $(\theta, \lambda)$ within $\Xi(\tilde{\theta}, \tilde{\lambda})$.
+In particular, since $(\tilde{\theta}, \tilde{\lambda}) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, it holds for $\theta = \tilde{\theta}$ and $\lambda = \tilde{\lambda}$.
+Applying this choice, the only variables that remain now are $(\tilde{\theta}, \tilde{\lambda})$.
+We then replace these symbols with a general $(\theta, \lambda)$ again to avoid cluttered notation.
 We now arrive at our final result.
@@
 
-		In order for the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} to be non-trivial, we focus on bounded kernels in the sense that $\alpha^{2}(\theta) := \sup_{x \in \mathcal{X}} k_{\theta}(x, x) < \infty$.
+		% In order for the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} to be non-trivial, we focus on bounded kernels in the sense that $\alpha^{2}(\theta) := \sup_{x \in \mathcal{X}} k_{\theta}(x, x) < \infty$.
 Gaussian kernels $k_{\theta}(x, x') = \sigma_{f}^{2} \exp{( - \frac{1}{2}(x - x') \Sigma^{-1} (x - x') )}$ and similar stationary kernels (e.g.
 Mat\'{e}rn) with sensitivity and length scales $\theta = (\sigma_{f}, \Sigma)$, for example, have $\alpha(\theta) = \sigma_{f}$.
+		In particular, $r(\theta, \lambda)$ is an upper bound to the Rademacher complexity of a relevant class of \glspl{MCE} based on the hyperparameters $\Xi(\theta, \lambda)$.
+We call $r(\theta, \lambda)$ the \gls{RCB} and use it to measure the model complexity of a \gls{MCE} with hyperparameters $(\theta, \lambda)$.
 Since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} holds with probability $1 - \beta$ when the random variables $(X_{i}, Y_{i})$ are realized as the training observations $(x_{i}, y_{i})$.
@@
 		\end{equation}
+
+		In particular, the first term is an empirical risk that measures data fit, and the second term is the \gls{RCB} that measures model complexity.
 
@@
 
-		\paragraph{Batch Stochastic Gradient Update} Since \cref{thm:expected_risk_bound_hyperparameter_learning_copy} holds for any $n \in \mathbb{N}_{+}$ and any set of data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ from $\mathbb{P}_{X Y}$, the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} also holds with high probability for a batch subset of the training data.
-However, the batch size cannot be too small, in order to keep the constant $\sqrt{8 \log{(2 / \beta)} / n}$ relatively small.
-We therefore propose to use only a random batch subset of the data to perform each gradient update.
-This enables scalable hyperparameter learning through batch stochastic gradient updates, where each gradient update stochastically improves a different probabilistic upper bound of the generalization risk.
-Note that without this bound, it is not straightforward to simply apply stochastic gradient updates to optimize $q$, since $r$ depends on the dataset but is not written in terms of a summation over the data.
-We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:multiclass_conditional_embedding_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size.
-The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is necessary only for inference, instead of once every learning iteration.
-It can be further avoided by using random Fourier features \citep{rahimi2008random} or kernel herding \citep{chen2010super} to approximate the already learned \gls{MCE}.
-All further inference takes $O(n^{2})$ time, or potentially less with approximation, using back substitution.
-
 		\begin{figure*}[t]
@@
 		\end{figure*}
+
+		\paragraph{Batch Stochastic Gradient Update} Since \cref{thm:expected_risk_bound_hyperparameter_learning_copy} holds for any $n \in \mathbb{N}_{+}$ and any set of data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ from $\mathbb{P}_{X Y}$, the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} also holds with high probability for a batch subset of the training data.
+However, the batch size cannot be too small, in order to keep the constant $\sqrt{8 \log{(2 / \beta)} / n}$ relatively small.
+We therefore propose to use only a random batch subset of the data to perform each gradient update.
+This enables scalable hyperparameter learning through batch stochastic gradient updates, where each gradient update stochastically improves a different probabilistic upper bound of the generalization risk.
+Note that without this bound, it is not straightforward to simply apply stochastic gradient updates to optimize $q$, since $r$ depends on the dataset but is not written in terms of a summation over the data.
+We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:multiclass_conditional_embedding_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size.
+The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is necessary only for inference, instead of once every learning iteration.
+It can be further avoided by using random Fourier features \citep{rahimi2008random} or kernel herding \citep{chen2010super} to approximate the already learned \gls{MCE}.
+All further inference takes $O(n^{2})$ time, or potentially less with approximation, using back substitution.
 
@@
 		\paragraph{Batch Validation} While we simply instantiated $(X_{i}, Y_{i})$ to be the training observations in \cref{thm:expected_risk_bound_hyperparameter_learning_copy} to obtain \eqref{eq:learning_objective}, this does not have to be the case for batch updates.
-Instead, in each learning iteration, we could further split the batch into two sub-batches - one for training and one for validation.
+Instead, in each learning iteration, we could further split the batch into two sub-batches -- one for training and one for validation.
 The training batch is used to form the \gls{MCE} $\bvec{f}_{\theta, \lambda}$ and \gls{RCB} $r(\theta, \lambda)$, while we evaluate the empirical risk on the validation batch,
@@
 
-	\paragraph{Learning convolutional layers}
-
 	\begin{figure*}[t]
@@
 
+	\paragraph{Learning convolutional layers}
+
 		We now apply \cref{alg:multiclass_conditional_embedding_training} to train a \gls{CEN} with convolutional layers on MNIST.
@@
 
-		We developed a scalable hyperparameter learning framework for conditional mean embeddings with categorical targets based on Rademacher complexity bounds.
-These bounds reveal a novel data-dependent quantity $r(\theta, \lambda)$ which reflect the model complexity of \glspl{CME}, which we use as an regularization term in addition to the empirical loss for hyperparameter learning.
-Similar to a regularized least squares problem, it remains to be established what type of prior on the hyperparameters, if any, could correspond to such a regularizer, which would enable a Bayesian interpretation of our approach.
-We also envision that such a quantity could potentially be generalized to \glspl{CME} with arbitrary targets which would enable hyperparameter learning for general conditional mean embeddings in a way that is optimized for the loss relevant to the prediction task.
+		We developed a scalable hyperparameter learning framework for \glspl{CME} with categorical targets based on Rademacher complexity bounds.
+These bounds reveal a novel data-dependent quantity $r(\theta, \lambda)$ which reflect its model complexity, which we use as an regularization term in addition to the empirical loss for hyperparameter learning.
+Similar to a regularized least squares problem, it remains to be established what type of prior on the hyperparameters, if any, could correspond to such a regularizer, resulting in a Bayesian interpretation of our approach.
+We also envision that such a quantity could potentially be generalized to \glspl{CME} with arbitrary targets, which would enable hyperparameter learning for general conditional mean embeddings in a way that is optimized for the prediction task.
 

### 2018-04-02 ECML2018/paper/mce_appendix_ecml2018.tex
Convert paper and appendix to ECML format

--- 2017-05-23 cake_appendix.tex
@@
-\documentclass{article}
-
-% if you need to pass options to natbib, use, e.g.:
-% \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading nips_2017
+% This is LLNCS.DEM the demonstration file of
+% the LaTeX macro package from Springer-Verlag
+% for Lecture Notes in Computer Science,
+% version 2.4 for LaTeX2e as of 16. April 2010
 %
-% to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{nips_2017}
-
-\usepackage{nips_2017}
-
-% to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[final]{nips_2017}
+\documentclass{llncs}
+%
+\usepackage{makeidx}  % allows for indexgeneration
+
+\bibliographystyle{apalike}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography
+\usepackage[square, authoryear, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
 
 % My Packages
+\usepackage{glossaries}
 \usepackage[nokeyprefix]{refstyle}
@@
 \usepackage{xr-hyper}
-\externaldocument[cake]{cake}
+\externaldocument[mce_ecml2018]{mce_ecml2018}
 % End My Packages
@@
 \usepackage{amssymb}
-\usepackage{amsthm}
+%\usepackage{amsthm}
 \usepackage{mathbbol}
@@
 \usepackage[dvipsnames]{xcolor}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{claim}[theorem]{Claim}
+%\newtheorem{theorem}{Theorem}[section]
+%\newtheorem{corollary}[theorem]{Corollary}
+%\newtheorem{lemma}[theorem]{Lemma}
+%\newtheorem{claim}[theorem]{Claim}
 \usepackage{multirow}
@@
 
+\newacronym{CME}{CME}{conditional mean embedding}
+\newacronym{MCE}{MCE}{multi-categorical conditional embedding}
+\newacronym{CEN}{CEN}{conditional embedding network}
+\newacronym{RKHS}{RKHS}{reproducing kernel Hilbert space}
+\newacronym{SVM}{SVM}{support vector machine}
+\newacronym{SVC}{SVC}{support vector classifier}
+\newacronym{GP}{GP}{Gaussian process}
+\newacronym{GPs}{GPs}{Gaussian processes}
+\newacronym{GPC}{GPC}{Gaussian process classifier}
+\newacronym{KRR}{KRR}{kernel ridged regressor}
+\newacronym{RLSC}{RLSC}{regularized least squares classification}
+\newacronym{ERM}{ERM}{empirical risk minimization}
+\newacronym{MMD}{MMD}{maximum mean discrepancy}
+\newacronym{RCB}{RCB}{Rademacher complexity bound}
+\newacronym{OVA}{OVA}{one versus all}
+\newacronym{CNN}{CNN}{convolutional neural network}
+
 % End My Packages
 
-\title{CAKE: Classification \textit{avec} Kernel Embeddings \\ using Rademacher Complexity Bounds: \\ Supplementary Material}
-
-\author{
-}
+\title{Hyperparameter Learning \\ for Conditional Mean Embeddings \\ with Rademacher Complexity Bounds : \\ Supplementary Material}
+
+\titlerunning{Hyperparameter Learning for Conditional Mean Embeddings}
+% abbreviated title (for running head), also used for the TOC unless \toctitle is used
+
+\author{Kelvin Hsu \inst{1, 2} \and
+	Richard Nock \inst{1, 2, 3} \and
+	Fabio Ramos \inst{1, 2}}
+%
+\authorrunning{Hsu et. al.} % abbreviated author list (for running head)
+%
+%%%% list of authors for the TOC (use if author list has to be modified)
+\tocauthor{Kelvin Hsu, Richard Nock, Fabio Ramos}
+%
+\institute{	University of Sydney, Sydney, Australia, \\ \and
+	Data61, CSIRO, Sydney, Australia \\ \and
+	Australian National University, Canberra, Australia}
 
@@
 
-	\section{Convergence Theorems for Kernel Embedding Classifiers}
+	\section{Convergence Theorems for Multi-Categorical Conditional Mean Embeddings}
 	\label{app:convergence_theorems}
 
-	In this section we provide theorems and derivations that establish convergence properties of kernel embedding classifiers.
-
-	We consider the case in which a dataset, represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$, is collected in a \textit{iid} fashion from some distribution $\mathbb{P}_{X Y}$.
-That is $\{X_{i}, Y_{i}\} \sim \mathbb{P}_{X Y}$ for all $i \in \mathbb{N}_{n}$ and each observed sample is independent from each other.
-Suppose we have an estimator function $\hat{f}^{(n)} : \mathcal{X} \to \mathbb{R}$ which is to estimate some target function  $f : \mathcal{X} \to \mathbb{R}$, usually but not necessarily derived from $\mathbb{P}_{Y |X }$, empirically using the collected dataset $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of size $n \in \mathbb{N}_{+}$.
-Here, we use the superscript $(n)$ to denote the estimator's dependence on the dataset.
-From this point on, we drop this superscript to avoid cluttered notation.
-However, one should keep in mind that $\hat{f}$ is estimated using the dataset $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ and is thus random over the possible data observation events $\omega \in \Omega$.
-We would like to provide a sense of the stochastic convergence of $\hat{f}$ to $f$ by providing an upper bound of their absolute pointwise difference $| \hat{f}(x) - f(x) |$, and show that such an upper bound converges to zero at some stochastic rate.
-Since the kernel embedding classifier is based on conditional embeddings (and, as we will show, is equivalent to a conditional embedding), this upper bound will be provided by the RKHS norm of the error between empirical and true conditional embeddings.
-Specifically, the empirical conditional embedding stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \cite[Theorem 6]{song2009hilbert}.
+	In this section we provide theorems and derivations that establish convergence properties of \glspl{MCE}.
+Most of the convergence results hold due to \glspl{MCE} being special cases of \glspl{CME}, whose empirical estimates are known to converge.
+We include this section for completeness.
+
+	Suppose $\{X_{i}, Y_{i}\} \sim \mathbb{P}_{X Y}$ are \textit{iid} for all $i \in \mathbb{N}_{n}$, with $X_{i} : \Omega \to \mathcal{X}$ and $Y_{i} : \Omega \to \mathcal{Y}$.
+We wish to estimate some target function $f : \mathcal{X} \to \mathbb{R}$ by $\hat{f} : \mathcal{X} \to \mathbb{R}$ empirically with a dataset $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of size $n \in \mathbb{N}_{+}$.
+Since $\hat{f}$ is empirically estimated, it is a random function over the possible data observation events $\omega \in \Omega$.
+The aim is to provide a sense of the stochastic convergence of $\hat{f}$ to $f$ by providing an upper bound of their absolute pointwise difference $| \hat{f}(x) - f(x) |$, and show that such an upper bound converges to zero at some stochastic rate.
+Such an upper bound is provided by the convergence properties of \glspl{CME}.
+In particular, the empirical \gls{CME} stochastically converges to the \gls{CME} at rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot) \in \mathrm{image}(C_{XX})$ \cite[Theorem 6]{song2009hilbert}.
 That is,
@@
 	\end{equation}
-
+	In practice, the assumption that $k(x, \cdot) \in \mathrm{image}(C_{XX})$ can be relaxed by replacing $\mathcal{U}_{Y | X} = C_{YX} C_{XX}^{-1}$ with $\mathcal{U}_{Y | X} = C_{YX} (C_{XX} + \lambda I)^{-1}$ \citep{song2013kernel}.
+This will apply to all the subsequent theorems in this section.
 	\begin{theorem}[Pointwise and Uniform Convergence of Estimators based on Conditional Embeddings]
@@
 
-	With \cref{thm:pointwise_uniform_convergence}, we can now show the convergence of various estimators based on the conditional embedding, as long as we can show that their estimator error is upper bounded by a multiple of the conditional embedding error in the RKHS norm.
+	With \cref{thm:pointwise_uniform_convergence}, we can now show the convergence of various estimators based on the conditional embedding, as long as we can show that their estimator error is upper bounded by a multiple of the conditional embedding error in the \gls{RKHS} norm.
 As such, we turn to the convergence of the empirical decision probability function \eqref[name= , xr=cake]{eq:empirical_decision_probability} below.
@@
 
-			From \eqref[name = , xr=cake]{eq:indicator_function}, since $\mathbb{1}_{c} = \delta(c, \cdot)$ and using the fact that $\delta$ is a reproducing kernel, we have that for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+			Since $\mathbb{1}_{c} = \delta(c, \cdot)$ and using the fact that $\delta$ is a reproducing kernel, we have that for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
 			\begin{equation}
@@
 			\big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}}^{2} = \langle \mathbb{1}_{c}, \mathbb{1}_{c} \rangle = \langle \delta(c, \cdot), \delta(c, \cdot) \rangle = \delta(c, c) = 1.
-			\label{eq:indicator_rkhs_norm}
+			\label{eq:indicator_RKHS_norm}
 			\end{aligned}
@@
 	The above proof is for uniform convergence over all $x \in \mathcal{X}$ at the stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$.
-Intuitively, however, for stationary zero-centred kernels like the Gaussian kernel, the convergence rate may be higher at regions of high data density, since the kernel effects, being centred around the training data, are stronger at these regions.
+Intuitively, however, for stationary zero-centered kernels like the Gaussian kernel, the convergence rate may be higher at regions of high data density, since the kernel effects, being centered around the training data, are stronger at these regions.
 The worse case convergence rate described here in the theorem would be a tight lower bound for regions in $\mathcal{X}$ with lower data density, where the kernel effects have decayed and most empirical probabilities are smaller and further from summing up to one.
 
-	Because the label space $\mathcal{Y} = \mathbb{N}_{m}$ is discrete and finite, \textit{bounded} functions $g \in \mathcal{H}_{\delta}$ in the RKHS are actually equivalent to their vector representations $\bvec{g} := \{g(c)\}_{c = 1}^{m}$, because one can always write $g = \sum_{c = 1}^{m} g(c) \delta(c, \cdot)$.
-This immediately implies that inner products in this space are simply the usual dot products in a Euclidean space, since
+	Because the label space $\mathcal{Y} = \mathbb{N}_{m}$ is discrete and finite, \textit{bounded} functions $g \in \mathcal{H}_{\delta}$ in the \gls{RKHS} are equivalent to their vector representations $\bvec{g} := \{g(c)\}_{c = 1}^{m}$, because one can always write $g = \sum_{c = 1}^{m} g(c) \delta(c, \cdot)$.
+In other words, there is an isomorphism between $\mathbb{H}_{\delta}$ and $\mathbb{R}^{m}$.
+A convenient consequence is that inner products in the \gls{RKHS} are simply the usual dot products in a Euclidean space, since
 
@@
 
-	Consequently, the RKHS norm for bounded functions $g \in \mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of its vector representation $\bvec{g}$,
+	Consequently, the \gls{RKHS} norm for bounded functions $g \in \mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of its vector representation $\bvec{g}$,
 
@@
 	\lVert g \rVert_{\mathcal{H}_{\delta}} = \lVert \bvec{g} \rVert_{\ell_{2}}.
-	\label{eq:rkhs_norm_is_l2_norm}
+	\label{eq:RKHS_norm_is_l2_norm}
 	\end{equation}
@@
 
-			Since indicator functions are the canonical features of the label RKHS $\mathcal{H}_{\delta}$, we employ the fact that expectations of indicator functions are probabilities to prove this claim,
+			Since indicator functions are the canonical features of the label \gls{RKHS} $\mathcal{H}_{\delta}$, we employ the fact that expectations of indicator functions are probabilities to prove this claim,
 
@@
 
-	\Cref{thm:empirical_probability_is_embedding} shows that the decision function $\bvec{f}(x)$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} of a kernel embedding classifier is no more than the empirical conditional embedding estimated from the data.
+	\Cref{thm:empirical_probability_is_embedding} shows that the decision function $\bvec{f}(x)$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} of a \gls{MCE} is no more than the empirical conditional embedding estimated from the data.
 
@@
 Since each entry converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the entire vector.
-More formally, from \eqref[name = ]{eq:decision_probability_error_upper_bound} and \eqref[name = ]{eq:indicator_rkhs_norm}, the $\ell_{1}$-norm of the difference can be bounded,
+More formally, from \eqref[name = ]{eq:decision_probability_error_upper_bound} and \eqref[name = ]{eq:indicator_RKHS_norm}, the $\ell_{1}$-norm of the difference can be bounded,
 
@@
 
-			For convergence in $\ell_{2}$, we show that the $\ell_{2}$-norm of the difference between the true and empirical decision probability vector functions is the same as the RKHS norm of the difference between the true and empirical conditional embedding, which converges to zero at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $x \in \mathcal{X}$ and $c \in \mathcal{Y} = \mathbb{N}_{m}$ by \eqref[name = ]{eq:empirical_conditional_embedding_stochastic_convergence}.
+			For convergence in $\ell_{2}$, we show that the $\ell_{2}$-norm of the difference between the true and empirical decision probability vector functions is the same as the \gls{RKHS} norm of the difference between the true and empirical conditional embedding, which converges to zero at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $x \in \mathcal{X}$ and $c \in \mathcal{Y} = \mathbb{N}_{m}$ by \eqref[name = ]{eq:empirical_conditional_embedding_stochastic_convergence}.
 To this end, we use \cref{thm:probability_is_embedding} and \cref{thm:empirical_probability_is_embedding} and write
@@
 
-			where the last equality comes from \eqref[name = ]{eq:rkhs_norm_is_l2_norm} and the fact that the empirical and true conditional embeddings are bounded functions in the RKHS.
+			where the last equality comes from \eqref[name = ]{eq:RKHS_norm_is_l2_norm} and the fact that the empirical and true conditional embeddings are bounded functions in the \gls{RKHS}.
 Again, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, we have uniform convergence in $\ell_{2}$.
@@
 
-	\subsection{Information Entropy of Kernel Embedding Classifiers}
+	\subsection{Information Entropy of \glspl{MCE}}
 	\label{app:information_entropy}
 
-		The kernel embedding classifier provides decision probabilities instead of just a single label prediction.
+	The \gls{MCE} provides decision probabilities instead of just a single label prediction.
 Such a probabilistic classifier allows us to quantify the uncertainty of its predictions for any given example $x \in \mathcal{X}$ through the information entropy \citep{shannon1951prediction, jaynes1957information}.
@@
 
-		The first approach is straight forward, which involves simply computing the information entropy with the clip normalised probabilities \eqref[name = , xr=cake]{eq:empirical_decision_probability_clip_normalised}, at the query point $x \in \mathcal{X}$,
+	The first approach is straight forward, which involves simply computing the information entropy with the clip normalized probabilities \eqref[name = , xr=cake]{eq:empirical_decision_probability_clip_normalized}, at the query point $x \in \mathcal{X}$,
 
@@
 	\tilde{h}(x) := - \sum_{c = 1}^{m} \tilde{p}_{c}(x) \log{\tilde{p}_{c}(x)}.
-		\label{eq:entropy_clip_normalise}
-		\end{equation}
-
-		We call \eqref[name = ]{eq:entropy_clip_normalise} the \textit{clip-normalised information entropy}.
+	\label{eq:entropy_clip_normalize}
+	\end{equation}
+
+	We call \eqref[name = ]{eq:entropy_clip_normalize} the \textit{clip-normalized information entropy}.
 Since $\tilde{p}_{c}(x)$ converges pointwise to $p_{c}(x)$ with increasing data, $\tilde{h}(x)$ also converges pointwise to $h(x)$.
@@
 Note that while $\mathbb{P}[Y = c | X = x]$ is a constant, we employ the shorthand notation $\mathbb{P}[Y| X = x]$ for the random variable $g(Y)$ where $g(y) := \mathbb{P}[Y = y | X = x]$.
-If $u_{x} : \mathbb{N}_{m} \to \mathbb{R}$ is in the RKHS $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by $\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle$.
+If $u_{x} : \mathbb{N}_{m} \to \mathbb{R}$ is in the \gls{RKHS} $\mathcal{H}_{\delta}$, then we know that this expectation can also be approximated by $\langle \hat{\mu}_{Y | X = x}, u_{x} \rangle$.
 This is the basis of our second approach.
@@
 	Assuming that $\mathbb{P}[Y = y | X = x]$ is never exactly zero for all labels $y \in \mathcal{Y}$ and examples $x \in \mathcal{X}$, then $u_{x}(y)$ is bounded on its discrete domain $\mathbb{N}_{m}$.
-We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the RKHS.
+We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the \gls{RKHS}.
 Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref[name = , xr=cake]{eq:empirical_conditional_expectation} and estimate $h(x)$ by
@@
 			where the we used the triangle inequality and Cauchy Schwarz inequality in a Hilbert space respectively.
-Since $l = \delta$ is bounded, so is $\hat{\mu}_{Y | X = x}(c) = \sum_{i = 1}^{n} w_{i} \delta(y_{i}, c)$ for some embedding weights $w_{i}$ and all $c \in \mathbb{N}_{m}$, and thus its RKHS norm is finite for all $n \in \mathbb{N}_{n}$.
-Similarly, assuming that $p_{c}(x)$ is never exactly zero, $u_{x}(c)$ is also finite for all $c \in \mathbb{N}_{m}$ and thus so is its RKHS norm.
+Since $l = \delta$ is bounded, so is $\hat{\mu}_{Y | X = x}(c) = \sum_{i = 1}^{n} w_{i} \delta(y_{i}, c)$ for some embedding weights $w_{i}$ and all $c \in \mathbb{N}_{m}$, and thus its \gls{RKHS} norm is finite for all $n \in \mathbb{N}_{n}$.
+Similarly, assuming that $p_{c}(x)$ is never exactly zero, $u_{x}(c)$ is also finite for all $c \in \mathbb{N}_{m}$ and thus so is its \gls{RKHS} norm.
 We already know that $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|_{\mathcal{H}_{\delta}}$ stochastically converges to zero at the rate $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ \eqref[name = ]{eq:empirical_conditional_embedding_stochastic_convergence}.
@@
 			where we define $\alpha_{x} := \max_{c \in \mathbb{N}_{m}} \frac{1}{| \mu_{Y | X = x}(c) |}$, which is well defined as the conditional embedding is bounded.
-Since the RKHS norm of bounded functions in $\mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of their vector representations \eqref[name = ]{eq:rkhs_norm_is_l2_norm}, we have
+Since the \gls{RKHS} norm of bounded functions in $\mathcal{H}_{\delta}$ is simply the $\ell_{2}$-norm of their vector representations \eqref[name = ]{eq:RKHS_norm_is_l2_norm}, we have
 
@@
 	\newpage
-\section{Learning Theoretic Bounds for Kernel Embedding Classifiers}
+	\section{Learning Theoretic Bounds for Multi-Categorical Conditional Mean Embeddings}
 	\label{app:learning_theoretic_bounds}
 
-	In this section we derive Rademacher complexity bounds for kernel embedding classifiers, and show that it can be used in conjunction with cross entropy loss to bound the expected risk with high probability.
+	In this section we derive \glspl{RCB} for \glspl{MCE}, and show that it can be used in conjunction with cross entropy loss to bound the expected risk with high probability.
 
@@
 Let $k_{\theta} : \mathcal{X} \times \mathcal{X} \to [0, \infty)$ be a family of positive definite kernels indexed by $\theta \in \Theta$.
-As before, we define the shorthand notation for the gram matrices $K_{\theta} := \{k_{\theta}(x_{i}, x_{j}) : i \in \mathbb{N}_{n}, j \in \mathbb{N}_{n}\}$ and $\bvec{k}_{\theta}(x) := \{k_{\theta}(x_{i}, x) : i \in \mathbb{N}_{n}\}$, and $\lambda$ denotes the regularisation parameter of the conditional embedding \eqref[name = , xr=cake]{eq:empirical_conditional_embedding}.
-The kernel embedding classifier has a predictor form $\hat{\bvec{p}}(x) = \bvec{f}_{\theta, \lambda}(x)$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} defined by
+As before, we define the shorthand notation for the gram matrices $K_{\theta} := \{k_{\theta}(x_{i}, x_{j}) : i \in \mathbb{N}_{n}, j \in \mathbb{N}_{n}\}$ and $\bvec{k}_{\theta}(x) := \{k_{\theta}(x_{i}, x) : i \in \mathbb{N}_{n}\}$, and $\lambda$ denotes the regularization parameter of the conditional embedding \eqref[name = , xr=cake]{eq:empirical_conditional_embedding}.
+The \gls{MCE} has a predictor form $\hat{\bvec{p}}(x) = \bvec{f}_{\theta, \lambda}(x)$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} defined by
 
@@
 	where each entry of the predictor $\bvec{f}_{\theta, \lambda}(x)$ is the decision probability estimate for $p_{c}(x)$.
-This defines the function class of the predictor over the kernel family and a set of regularisation parameters for any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$,
+This defines the function class of the predictor over the kernel family and a set of regularization parameters for any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$,
 
@@
 
-		\begin{theorem}[Rademacher Complexity Bound for Kernel Embedding Classifiers]
+	\begin{theorem}[Rademacher Complexity Bound for \glspl{MCE}]
 		\label{thm:rademacher_complexity_bound}
@@
 		Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
-Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$, $\alpha > 0$, is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
-For any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of kernel embedding classifiers $F_{n}(\Theta, \Lambda)$ \eqref[name = ]{eq:predictor_class} defined over $\theta \in \Theta, \lambda \in \Lambda$ is bounded by
+Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$, $\alpha > 0$, is bounded in \gls{RKHS} norm for all $x \in \mathcal{X}, \theta \in \Theta$.
+For any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of \glspl{MCE} $F_{n}(\Theta, \Lambda)$ \eqref[name = ]{eq:predictor_class} defined over $\theta \in \Theta, \lambda \in \Lambda$ is bounded by
 
@@
 			where we define the random operator $\bm{\Phi}_{\theta} := \begin{bmatrix} \phi(X_{1}) & \phi(X_{2}) & \cdots & \phi(X_{n}) \end{bmatrix}$.
-Note that this is distinct from $\Phi_{\theta}$, whose columns are the canonical RKHS features at the training observations and is not random.
-Now, random or not, $\bm{\sigma} := \{\sigma_{i}\}_{i = 1}^{n}$ is just a collection of values that are either $-1$ or $1$, so its norm is simply $\| \bm{\sigma} \| = \sqrt{n}$.
+Note that this is distinct from $\Phi_{\theta}$, whose columns are the canonical \gls{RKHS} features at the training observations and is not random.
+Now, random or not, entries of $\bm{\sigma} := \{\sigma_{i}\}_{i = 1}^{n}$ are either $-1$ or $1$, so its norm is simply $\| \bm{\sigma} \| = \sqrt{n}$.
 We can then also compute the trace norm of the other random component $\bm{\Phi}_{\theta}$,
@@
 
-				Using the assertion that $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ for all $\theta \in \Theta, \lambda \in \Lambda$, we can now bound Rademacher complexity,
+			Using the assertion that $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ for all $\theta \in \Theta, \lambda \in \Lambda$, we can now bound the Rademacher complexity,
 
@@
 
-		\Cref{thm:rademacher_complexity_bound} provides a generic Rademacher complexity bound for any type of kernel embedding classifier with a bounded positive definite kernel and bounded trace norm.
+	\Cref{thm:rademacher_complexity_bound} provides a generic Rademacher complexity bound for any type of \gls{MCE} with a bounded positive definite kernel and bounded trace norm.
 One of the most widely used kernels in practice are the family of stationary kernels.
@@
 Select $\tilde{\theta} \in \Theta$ and define $\Theta(\tilde{\theta})$ such that $k_{\theta}(0, 0) \leq k_{\tilde{\theta}}(0, 0)$ for all $\theta \in \Theta(\tilde{\theta})$.
-For any $\tilde{\theta} \in \Theta$ and set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the resulting class of kernel embedding classifiers $F_{n}(\Theta(\tilde{\theta}), \Lambda)$ defined over $\theta \in \Theta(\tilde{\theta}), \lambda \in \Lambda$ is bounded by
+For any $\tilde{\theta} \in \Theta$ and set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the resulting class of \glspl{MCE} $F_{n}(\Theta(\tilde{\theta}), \Lambda)$ defined over $\theta \in \Theta(\tilde{\theta}), \lambda \in \Lambda$ is bounded by
 
@@
 
-		In order to quantify the performance of the kernel embedding classifier, we specify a loss function $\mathcal{L} : \mathcal{Y} \times \mathcal{A} \to [0, \infty)$, where $\mathcal{L}(y, f(x))$ measures the loss of a decision function $f : \mathcal{X} \to \mathcal{A}$ on a paired example $x \in \mathcal{X}$ and label $y \in \mathcal{Y}$.
-In the kernel embedding classification context, the decision function is $\bvec{f}_{\theta, \lambda} : \mathcal{X} \to \mathbb{R}^{m}$, with $\mathcal{A} = \mathbb{R}^{m}$ and $\mathcal{Y} = \mathbb{N}_{m}$.
-The loss function is to capture the desire for $\bvec{y}^{T} \bvec{f}_{\theta, \lambda}(x) = \bvec{f}_{y}^{(\theta, \lambda)}(x)$ to be high for all likely test points $x \in \mathcal{X}$ and $y \in \mathcal{Y}$.
+	In order to quantify the performance of the \gls{MCE}, we specify a loss function $\mathcal{L} : \mathcal{Y} \times \mathcal{A} \to [0, \infty)$, where $\mathcal{L}(y, f(x))$ measures the loss of a decision function $f : \mathcal{X} \to \mathcal{A}$ on a paired example $x \in \mathcal{X}$ and label $y \in \mathcal{Y}$.
+In the \gls{MCE} context, the decision function is $\bvec{f}_{\theta, \lambda} : \mathcal{X} \to \mathbb{R}^{m}$, with $\mathcal{A} = \mathbb{R}^{m}$ and $\mathcal{Y} = \mathbb{N}_{m}$.
+The loss function is to capture the desire for $\bvec{y}^{T} \bvec{f}_{\theta, \lambda}(x) = f_{y}^{(\theta, \lambda)}(x)$ to be high for all likely test points $x \in \mathcal{X}$ and $y \in \mathcal{Y}$.
 
@@
 Since logarithms explode at zero, in practice the probability estimate is often clipped from below at a predetermined threshold $\epsilon \in (0, 1)$.
-Furthermore, it is also convenient to clip the probability estimate from above at one to avoid negative losses, as further reward for high prediction probabilities are not necessary.
-In other words, assigning a probability estimate greater than one to the correct label is really just correctly assigning a probability estimate of one but with slight approximation error.
+Furthermore, it is also convenient to clip the probability estimate from above at one to avoid negative losses.
 Consequently, with the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$, we define the effective cross entropy loss as
@@
 	\end{aligned}
-		\label{eq:normalised_cross_entropy_loss}
-		\end{equation}
-
-		We will refer to \eqref[name = ]{eq:normalised_cross_entropy_loss} as the normalised cross entropy loss. We then further define the centred normalised cross entropy loss,
+	\label{eq:normalized_cross_entropy_loss}
+	\end{equation}
+
+	We will refer to \eqref[name = ]{eq:normalized_cross_entropy_loss} as the normalized cross entropy loss. We then further define the centered normalized cross entropy loss,
 
@@
 	\tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) := \bar{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) - \bar{\mathcal{L}}_{\epsilon}(y, \bvec{0}) = - \frac{1}{M_{\epsilon}} \log{ [f_{y}(x)]_{\epsilon}^{1} } - 1.
-		\label{eq:centred_normalised_cross_entropy_loss}
-		\end{equation}
-
-		With the normalised cross entropy loss \eqref[name = ]{eq:normalised_cross_entropy_loss} as our loss function, we now employ Theorem 8 of \cite{bartlett2002rademacher} for this loss and provide a bound for the expected normalised cross entropy loss for an unseen test example.
+	\label{eq:centered_normalized_cross_entropy_loss}
+	\end{equation}
+
+	With the normalized cross entropy loss \eqref[name = ]{eq:normalized_cross_entropy_loss} as our loss function, we now employ Theorem 8 of \cite{bartlett2002rademacher} for this loss and provide a bound for the expected normalized cross entropy loss for an unseen test example.
 
 	\begin{lemma}[Expected Risk Bound]
-		\label{thm:expected_normalised_cross_entropy_loss_bound}
+		\label{thm:expected_normalized_cross_entropy_loss_bound}
 		For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
@@
 			Since $\bar{\mathcal{L}}_{\epsilon} : \mathcal{Y} \times \mathcal{A} \to [0, 1]$ has a unit range and dominates itself, $\bar{\mathcal{L}}_{\epsilon}(y, f(x)) \leq \bar{\mathcal{L}}_{\epsilon}(y, f(x))$, the result follows directly from Theorem 8 of \cite{bartlett2002rademacher}.
-We then use the definition \eqref[name = ]{eq:normalised_cross_entropy_loss} for the normalised cross entropy loss.
+We then use the definition \eqref[name = ]{eq:normalized_cross_entropy_loss} for the normalized cross entropy loss.
 		\end{proof}
@@
 	Equivalently, by definition \eqref[name = ]{eq:predictor_class}, this result holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
-The bound \eqref[name = ]{eq:expected_loss_bound} involves the Rademacher complexity $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda))$ of the centred normalised cross entropy loss applied onto the class of functions $F_{n}(\Theta, \Lambda)$, and not just the Rademacher complexity $\mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$ of the class of functions $F_{n}(\Theta, \Lambda)$ itself.
+The bound \eqref[name = ]{eq:expected_loss_bound} involves the Rademacher complexity $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda))$ of the centered normalized cross entropy loss applied onto the class of functions $F_{n}(\Theta, \Lambda)$, and not just the Rademacher complexity $\mathcal{R}_{n}(F_{n}(\Theta, \Lambda))$ of the class of functions $F_{n}(\Theta, \Lambda)$ itself.
 In \cref{thm:rademacher_complexity_bound}, we have bounded the latter.
-We now proceed to bound the former with the latter, so that the former is also bounded by the bound on the latter \eqref[name = ]{eq:rademacher_complexity_bound}.
+We now proceed to bound the former with the latter \eqref[name = ]{eq:rademacher_complexity_bound}, so that the upper bound in \cref{thm:expected_normalized_cross_entropy_loss_bound} can be written in terms of the latter.
 
@@
 
-			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of cross entropy loss applied onto the kernel embedding classifier is bounded by
+		For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, the Rademacher complexity of the class of cross entropy loss applied onto the \gls{MCE} is bounded by
 
@@
 			Let $\tilde{\psi}(z) := - \frac{1}{M_{\epsilon}} \log{[z]_{\epsilon}^{1}} - 1$ so that $\tilde{\psi} : \mathbb{R} \to \mathbb{R}$ satisfies $\tilde{\psi}(0) = 0$.
-Then, the centered normalised cross entropy loss can be written as $\tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) = \tilde{\psi}(f_{y}(x))$.
+Then, the centered normalized cross entropy loss can be written as $\tilde{\mathcal{L}}_{\epsilon}(y, \bvec{f}(x)) = \tilde{\psi}(f_{y}(x))$.
 In particular, $\tilde{\psi}(z)$ is piecewise differentiable.
@@
 	The bound \eqref[name = ]{eq:composed_rademacher_complexity_bound} in \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss} will be the bridge that relates the expected cross entropy loss over our function class to the Rademacher complexity of our function class.
-We now proceed to state the main theorem which forms the backbone of our learning algorithm for the kernel embedding classifier.
-
-		\begin{lemma}[General Expected Risk Bound for the Kernel Embedding Classifier]
-			\label{thm:expected_loss_bound_for_kec}
+We now proceed to state the main theorem which forms the backbone of our learning algorithm for the \gls{MCE}.
+
+	\begin{lemma}[$\epsilon$-General Expected Risk Bound for \glspl{MCE}]
+		\label{thm:expected_loss_bound_for_multiclass_conditional_embedding}
 
 		Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
-Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$, $\alpha > 0$, is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
-For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
+Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$, $\alpha > 0$, is bounded in \gls{RKHS} norm for all $x \in \mathcal{X}, \theta \in \Theta$.
+For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability of at least $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
 
@@
 		\frac{1}{M_{\epsilon}} \mathbb{E}[\mathcal{L}_{\epsilon}(Y, f(X))] \leq \frac{1}{n M_{\epsilon}} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
-			\label{eq:expected_loss_bound_for_kec}
+		\label{eq:expected_loss_bound_for_multiclass_conditional_embedding}
 		\end{equation}
@@
 		for any $\epsilon \in (0, 1)$.
-Equivalently, the bound \eqref[name = ]{eq:expected_loss_bound_for_kec} holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
+Equivalently, the bound \eqref[name = ]{eq:expected_loss_bound_for_multiclass_conditional_embedding} holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
 
@@
 These are both deterministic inequalities, leading to $\mathcal{R}_{n}(\tilde{\mathcal{L}}_{\epsilon} \circ F_{n}(\Theta, \Lambda)) \leq 4 \frac{1}{\epsilon \log{\frac{1}{\epsilon}}} \alpha \rho$.
-We then apply this inequality to \cref{thm:expected_normalised_cross_entropy_loss_bound}, which proves the claim.
+We then apply this inequality to \cref{thm:expected_normalized_cross_entropy_loss_bound}, which proves the claim.
 
@@
 
-		Similar to many learning theoretic bounds, the expected risk bound \eqref[name = ]{eq:expected_loss_bound_for_kec} is composed of three qualitatively different terms.
+	Similar to many learning theoretic bounds, the expected risk bound \eqref[name = ]{eq:expected_loss_bound_for_multiclass_conditional_embedding} is composed of three qualitatively different terms.
 The first term is a training loss or data fit term, which is a measure of how poorly the decision function $f$ is performing on a given training dataset.
-The second term is a model complexity or regularisation term, which measures how complicated the model is.
+The second term is a model complexity or regularization term, which measures how complicated the model is.
 In this case, the model complexity is measured by the Rademacher complexity, which captures the expressiveness of the function class by quantifying how well the function class is able to shatter noise.
@@
 
-		We will eventually be minimising the first two terms over some class of functions $f \in F_{n}(\Theta, \Lambda)$ with some approach, as a proxy to minimising the actual expected risk.
+	We will eventually be minimizing the first two terms over some class of functions $f \in F_{n}(\Theta, \Lambda)$ with some approach, as a proxy to minimizing the actual expected risk.
 It would be fruitful to develop an intuition for the tightness of the bound from the contributions of the training loss term and the model complexity term.
@@
 	Consider a clipped cross entropy loss with either a very small clipping factor $\epsilon \approx 0$, or a very large clipping factor $\epsilon \approx 1$.
-In this scenario, $\epsilon \log{\frac{1}{\epsilon}}$ would be very small, so that the coefficient on the complexity term would then be very large, regardless of what the complexity bound factors $\alpha$ and $\rho$ are.
+In these scenarios, $\epsilon \log{\frac{1}{\epsilon}}$ would be very small, so that the coefficient on the complexity term would then be very large, regardless of what the complexity bound factors $\alpha$ and $\rho$ are.
 As a result, intuitively, this bound is unlikely to be tight due to the large coefficient on the complexity term.
@@
 	Consequently, it would then be natural to consider a middle-ground choice of the cross entropy loss where this bound is the most tight by varying $\epsilon \in (0, 1)$.
-Since $\epsilon \log{\frac{1}{\epsilon}}$ is maximised at $\epsilon = \frac{1}{e}$ for a maximal value of $\frac{1}{e}$, such a choice in the clipping factor would indeed yield the tightest bound for the complexity bound in terms of the bounding slack of the result stated in \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss}.
+Since $\epsilon \log{\frac{1}{\epsilon}}$ is maximized at $\epsilon = \frac{1}{e}$ for a maximal value of $\frac{1}{e}$, such a choice in the clipping factor would indeed yield the tightest bound for the complexity bound in terms of the bounding slack of the result stated in \cref{thm:rademacher_complexity_bound_with_cross_entropy_loss}.
 
@@
 Furthermore, beyond the clipping point, assigning even lower probabilities to the observations does not result in a higher loss.
-In practice, the cross entropy loss is renowned for its rapidly growing penalty as the probability assignment gets lower, which is advantageous when using a gradient based optimisation scheme.
+In practice, the cross entropy loss is renowned for its rapidly growing penalty as the probability assignment gets lower, which is advantageous when using a gradient based optimization scheme.
 In this case, the gradients are large in magnitude and the classifier can adjust and fix these assignment errors relatively quickly.
@@
 
-		Nevertheless, observe that for such a clipping factor $\epsilon = e^{-1}$, the normalisation constant becomes $M_{e^{-1}} = - \log{\frac{1}{e}} = 1$, so that it is effectively removed.
+	Nevertheless, observe that for such a clipping factor $\epsilon = e^{-1}$, the normalization constant becomes $M_{e^{-1}} = - \log{\frac{1}{e}} = 1$, so that it is effectively removed.
 Furthermore, we also have the following simple upper bound for the cross entropy loss clipped at $\epsilon = e^{-1}$,
@@
 
-		\begin{theorem}[Specific Expected Risk Bound for the Kernel Embedding Classifier]
-			\label{thm:specific_expected_loss_bound_for_kec}
+	\begin{theorem}[$\epsilon$-Specific Expected Risk Bound for \glspl{MCE}]
+		\label{thm:specific_expected_loss_bound_for_multiclass_conditional_embedding}
 
 		Suppose that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho$ is bounded for all $\theta \in \Theta, \lambda \in \Lambda$.
-Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$, $\alpha > 0$, is bounded in RKHS norm for all $x \in \mathcal{X}, \theta \in \Theta$.
-For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
+Further suppose that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2}$, $\alpha > 0$, is bounded in \gls{RKHS} norm for all $x \in \mathcal{X}, \theta \in \Theta$.
+For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$, with probability of at least $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $f \in F_{n}(\Theta, \Lambda)$ satisfies
 
@@
 		\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 e \; \alpha \rho + \sqrt{\frac{8 \log{\frac{2}{\beta}}}{n}},
-			\label{eq:specific_expected_loss_bound_for_kec}
+		\label{eq:specific_expected_loss_bound_for_multiclass_conditional_embedding}
 		\end{equation}
@@
 		for any $\epsilon \in (0, e^{-1})$.
-Equivalently, the bound \eqref[name = ]{eq:specific_expected_loss_bound_for_kec} holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
-
-			\begin{proof}
-
-				We first apply \cref{thm:expected_loss_bound_for_kec} with $\epsilon = e^{-1}$,
+Equivalently, the bound \eqref[name = ]{eq:specific_expected_loss_bound_for_multiclass_conditional_embedding} holds for $f = \bvec{f}_{\theta, \lambda}(x)$ for every $\theta \in \Theta, \lambda \in \Lambda$.
+
+		\begin{proof}
+
+			We first apply \cref{thm:expected_loss_bound_for_multiclass_conditional_embedding} with $\epsilon = e^{-1}$,
 
@@
 
-		We are now ready to use the result of \cref{thm:specific_expected_loss_bound_for_kec} to derive a specific expected risk bound for a given choice of hyperparameters $\theta \in \Theta$ and $\lambda \in \Lambda$ of the kernel embedding classifier, and not just for a general set of hyperparameters.
+	We are now ready to use the result of \cref{thm:specific_expected_loss_bound_for_multiclass_conditional_embedding} to derive a specific expected risk bound for a given choice of hyperparameters $\theta \in \Theta$ and $\lambda \in \Lambda$ of the \gls{MCE}, and not just for a general set of hyperparameters.
 We focus on kernels $k_{\theta}$ that are bounded over the domain $\mathcal{X}$ in the sense that for each $\theta \in \Theta$, $k_{\theta}(x, x) < \infty$ for all $x \in \mathcal{X}$.
 
-		For some kernel parameters $\tilde{\theta} \in \Theta$ and regularisation parameter $\tilde{\lambda} \in \Lambda$, we construct a subset of hyperparameters (kernel parameters and regularisation parameters) $\Xi(\tilde{\theta}, \tilde{\lambda}) \subseteq \Theta \times \Lambda$ such that
+	For some kernel parameters $\tilde{\theta} \in \Theta$ and regularization parameter $\tilde{\lambda} \in \Lambda$, we construct a subset of hyperparameters (kernel parameters and regularization parameters) $\Xi(\tilde{\theta}, \tilde{\lambda}) \subseteq \Theta \times \Lambda$ such that
 
@@
 Note that $\alpha : \Theta \to \mathbb{R}_{+}$ must necessarily exist as the kernel family $k_{\theta}$ is assumed to be bounded over the domain $\mathcal{X}$.
-The class of kernel embedding classifiers over this subset of hyperparameters is
+The class of \glspl{MCE} over this subset of hyperparameters is
 
@@
 
-		Thus, we can assert that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ is bounded for all $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, and that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$ is bounded in RKHS norm for all $x \in \mathcal{X}, (\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$.
-By \cref{thm:specific_expected_loss_bound_for_kec}, we can now claim the following.
-
-		\begin{lemma}[General Expected Risk Bound for KEC Hyperparameter Learning]
+	Thus, we can assert that the trace norm $\| W_{\theta, \lambda} \|_{\mathrm{tr}} \leq \rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ is bounded for all $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$, and that the canonical feature map $\| \phi_{\theta}(x) \|_{\mathcal{H}_{k_{\theta}}}^{2} = k_{\theta}(x, x) \leq \alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$ is bounded in \gls{RKHS} norm for all $x \in \mathcal{X}, (\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$.
+By \cref{thm:specific_expected_loss_bound_for_multiclass_conditional_embedding}, we can now claim the following.
+
+	\begin{lemma}[Expected Risk Bound for a set of \gls{MCE} Hyperparameters]
 		\label{thm:general_expected_risk_bound_hyperparameter_learning}
@@
 		\begin{proof}
-				We first apply \cref{thm:specific_expected_loss_bound_for_kec} with the choice of $\rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ and $\alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$.
-The inequality \eqref[name = ]{eq:specific_expected_loss_bound_for_kec} then only holds for a subset of kernel parameters and regularisations $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ as defined by \eqref[name = ]{eq:hyperparameter_subset_definition}.
+			We first apply \cref{thm:specific_expected_loss_bound_for_multiclass_conditional_embedding} with the choice of $\rho = \| W_{\tilde{\theta}, \tilde{\lambda}} \|_{\mathrm{tr}}$ and $\alpha^{2} = \sup_{x \in \mathcal{X}} k_{\tilde{\theta}}(x, x)$.
+The inequality \eqref[name = ]{eq:specific_expected_loss_bound_for_multiclass_conditional_embedding} then only holds for a subset of kernel parameters and regularizations $(\theta, \lambda) \in \Xi(\tilde{\theta}, \tilde{\lambda})$ as defined by \eqref[name = ]{eq:hyperparameter_subset_definition}.
 		\end{proof}
@@
 
-		\begin{theorem}[Expected Risk Bound for KEC Hyperparameter Learning]
+	\begin{theorem}[Expected Risk Bound for a choice of \gls{MCE} Hyperparameters]
 		\label{thm:expected_risk_bound_hyperparameter_learning}
@@
 	\newpage
-\section{Special Cases of Kernel Embedding Classifiers}
+	\section{Special Cases of Multi-Categorical Conditional Mean Embeddings}
 	\label{app:special_cases}
 
-	For a kernel embedding classifier, the modelling lies in the choice of the kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ over the input space $\mathcal{X}$.
+	For \glspl{MCE}, the modelling lies in the choice of the kernel family $k_{\theta} : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ over the input space $\mathcal{X}$.
 The only requirement for the kernel $k$ is that it is symmetric and positive definite, and thus we may construct richer and more expressive kernel families in any way subject to such requirements.
-Once such a kernel family is constructed, the kernel parameters $\theta$, as well as the regularisation parameter $\lambda$, can be learned effectively using algorithm 1.
+Once such a kernel family is constructed, the kernel parameters $\theta$, as well as the regularization parameter $\lambda$, can be learned effectively using algorithm 1.
 
@@
 We can then construct the kernel family by incorporating such structural representations into the kernel.
-Even better, we can construct the kernel family so that it is capable or learning such structural representations by itself, by parametrising such representations into the kernel.
-
-	In this section, we focus on special cases of the kernel embedding classifier where the kernel family is constructed through explicit feature maps.
+Even better, we can construct the kernel family so that it is capable or learning such structural representations by itself, by parameterizing such representations into the kernel.
+
+	In this section, we focus on special cases of the \gls{MCE} where the kernel family is constructed through explicit feature maps.
 This construction allows the incorporation of trainable domain specific structures and enables scalability to larger datasets.
-We first begin by introducing the explicit kernel embedding classifier in \cref{app:explicit_kernel_embedding_classifier}, where explicit feature maps can be learned while enabling scalability to larger datasets.
-We then construct the kernel embedding network (KEN) in \cref{app:kernel_embedding_network}, where the kernel family is formed from multiple layers of learned representations before a simpler kernel encodes their similarity for inference.
-Finally, we marry both constructions into the explicit kernel embedding network in \cref{app:explicit_kernel_embedding_network}, which provides a scalable and more applicable version of the deep kernel embedding network by placing a linear kernel on the network features.
-
-	In essence, we can categorise the kernel embedding classifier using two properties: the model width and the model depth.
+We first begin by introducing the explicit \gls{MCE} in \cref{app:explicit_multiclass_conditional_embedding}, where explicit feature maps can be learned while enabling scalability to larger datasets.
+We then construct the \gls{CEN} in \cref{app:conditional_embedding_network}, where the kernel family is formed from multiple layers of learned representations before a simpler kernel encodes their similarity for inference.
+Finally, we marry both constructions into the explicit \gls{CEN} in \cref{app:explicit_conditional_embedding_network}, which provides a scalable and more applicable version of the deep \gls{CEN} by placing a linear kernel on the network features.
+
+	In essence, we can categorise the \gls{MCE} using two properties: the model width and the model depth.
 The model width represents the dimensionality of the feature space used to construct the linear decision boundaries.
 The model depth represents the number of transformations used to map examples from the input space to the feature space.
-By implicitly defining a high dimensional feature space through simple transformations, typical nonlinear kernels produces classifiers that have a shallow but wide architecture.
-In contrast, the three kernel embedding classifier variants to be introduced in this section form other combinations of model architecture in both depth and width.
-Of course, this characterisation of architecture is not mutually exclusive.
+By implicitly defining a high dimensional feature space through simple transformations, typical nonlinear kernels produce classifiers that have a shallow but wide architecture.
+In contrast, the three \gls{MCE} variants to be introduced in this section form other combinations of model architecture in both depth and width.
+Of course, this characterization of architecture is not mutually exclusive.
 For example, a polynomial kernel can be seen as a nonlinear kernel where higher order polynomial features are implicitly defined, or as a linear kernel on explicit polynomial features.
-We summarise those architectures in \cref{tab:kernel_embedding_classifier_variants}.
+We summarize those architectures in \cref{tab:multiclass_conditional_embedding_variants}.
 
 	\begin{table}[h]
-		\caption{Properties of kernel embedding classifier architectures}
-		\label{tab:kernel_embedding_classifier_variants}
+		\caption{Properties of \gls{MCE} architectures}
+		\label{tab:multiclass_conditional_embedding_variants}
 		\centering
 		\begin{tabular}{lccccc}
-			KEC Variant & Width & Depth & Scalability & Flexibility & Typical Datasets  \\
+			\gls{MCE} Variant & Width & Depth & Scalability & Flexibility & Typical Datasets  \\
 			\midrule
-			Implicit KEC & Wide & Shallow & Low & High & High or Low $d$, Low $n$ \\
-			Explicit KEC & Narrow & Shallow & High & Low & Low $d$, High $n$ \\
-			Implicit KEN &  Wide & Deep & Low & High & Structured $d$, Low $n$ \\
-			Explicit KEN & Narrow & Deep & High & High & Structured $d$, High $n$ \\ 
+			Implicit \gls{MCE} & Wide & Shallow & Low & High & High or Low $d$, Low $n$ \\
+			Explicit \gls{MCE} & Narrow & Shallow & High & Low & Low $d$, High $n$ \\
+			Implicit \gls{CEN} &  Wide & Deep & Low & High & Structured $d$, Low $n$ \\
+			Explicit \gls{CEN} & Narrow & Deep & High & High & Structured $d$, High $n$ \\ 
 		\end{tabular}
@@
 
-	\subsection{Explicit Kernel Embedding Classifier}
-	\label{app:explicit_kernel_embedding_classifier}
+	\subsection{Explicit Multi-Categorical Conditional Mean Embedding}
+	\label{app:explicit_multiclass_conditional_embedding}
 
@@
 For many kernels, such as the Gaussian kernel defined over the Euclidean space, the feature space $\mathcal{H}_{k}$ has dimensionality that is uncountably infinite.
-Nevertheless, by virtue of the Representer Theorem \citep{kimeldorf1971some}, the resulting decision functions can be represented by a finite linear combination of kernels centred at the training data, and the kernel embedding classifier is no exception.
+Nevertheless, by virtue of the Representer Theorem \citep{kimeldorf1971some}, the resulting decision functions can be represented by a finite linear combination of kernels centered at the training data, and the \gls{MCE} is no exception.
 This elegant and convenient result enables exact inference to be performed while only requiring a finite kernel gram matrix of the size of the dataset ($n \times n$) to be computed.
@@
 	However, this elegant property is also the very reason that prevents kernel-based methods from scaling to larger datasets, as the size of such a gram matrix grows very quickly by $O(n^{2})$.
-Many kernel-based methods also require the inversion of a regularised gram matrix, which has a time complexity of $O(n^{3})$, and cannot be easily parallelised like standard matrix multiplications.
+Many kernel-based methods also require the inversion of a regularized gram matrix, which has a time complexity of $O(n^{3})$, and cannot be easily parallelized like standard matrix multiplications.
 As such, inference on datasets beyond tens of thousands of observations quickly becomes impractical to perform with kernel-based techniques.
@@
 
-		By explicitly defining a finite dimensional feature space, the matrix to be inverted during both learning and inference in the kernel embedding classifier can be reduced from size $n \times n$ to size $p \times p$ by using the Woodbury matrix inversion identity \citep{higham2002accuracy}.
-We use this identity to modify algorithm 1 to \cref{alg:explicit_kernel_embedding_classifier_training} to exploit this computational speed up.
+	By explicitly defining a finite dimensional feature space, the matrix to be inverted during both learning and inference in the \gls{MCE} can be reduced from size $n \times n$ to size $p \times p$ by using the Woodbury matrix inversion identity \citep{higham2002accuracy}.
+We use this identity to modify algorithm 1 to \cref{alg:explicit_multiclass_conditional_embedding_training} to exploit this computational speed up.
 
@@
 	\begin{algorithm}[tb]
-			\caption{Explicit KEC Hyperparameter Learning with Batch Stochastic Gradient Updates}
-			\label{alg:explicit_kernel_embedding_classifier_training}
+		\caption{Explicit \gls{MCE} Hyperparameter Learning with Batch Stochastic Gradient Updates}
+		\label{alg:explicit_multiclass_conditional_embedding_training}
 		\begin{algorithmic}[1]
-				\STATE {\bfseries Input:} feature family $\varphi_{\theta} : \mathcal{X} \to \mathcal{Z} \subseteq \mathbb{R}^{p}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial feature parameters $\theta_{0}$, initial regularisation parameter $\lambda_{0}$, learning rate $\eta$, gradient error tolerance $\epsilon$, batch size $n_{b}$
+			\STATE {\bfseries Input:} feature family $\varphi_{\theta} : \mathcal{X} \to \mathcal{Z} \subseteq \mathbb{R}^{p}$, dataset $\{x_{i}, y_{i}\}_{i = 1}^{n}$, initial feature parameters $\theta_{0}$, initial regularization parameter $\lambda_{0}$, learning rate $\eta$, batch size $n_{b}$
 			\STATE $\theta \leftarrow \theta_{0}$, $\lambda \leftarrow \lambda_{0}$
@@
 			\STATE $P_{\theta, \lambda} \leftarrow Z_{\theta} W_{\theta, \lambda} \hspace{\fill} \in \mathbb{R}^{n_{b} \times m}$
-				\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n_{b}} \sum_{i \in \mathcal{I}_{b}} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; \alpha(\theta) \sqrt{\sum_{c = 1}^{m} \sum_{j = 1}^{p} (W_{\theta, \lambda})_{j, c}^{2}}$
-				\STATE $\theta \leftarrow \theta - \eta \frac{\partial q}{\partial \theta}(\theta, \lambda)$, $\lambda \leftarrow \lambda - \eta \frac{\partial q}{\partial \lambda}(\theta, \lambda)$ \hspace{\fill} (Or other gradient based updates such as Adam)
-				\UNTIL{$\big\lVert \begin{bmatrix} \frac{\partial q}{\partial \theta}(\theta, \lambda)^{T} & \frac{\partial q}{\partial \lambda}(\theta, \lambda)^{T} \end{bmatrix}^{T} \big\rVert_{\infty} < \epsilon$} \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
-				\STATE {\bfseries Output:} kernel parameters $\theta$, regularisation parameter $\lambda$
+			\STATE $r(\theta, \lambda) = \alpha(\theta) \sqrt{\sum_{c = 1}^{m} \sum_{j = 1}^{p} (W_{\theta, \lambda})_{j, c}^{2}}$
+			\STATE $q(\theta, \lambda) \leftarrow \frac{1}{n_{b}} \sum_{i = 1}^{n_{b}} \mathcal{L}_{\epsilon}((Y)_{i}, (P_{\theta, \lambda})_{i}) + 4 e \; r(\theta, \lambda)$
+			\STATE $(\theta, \lambda) \leftarrow \mathrm{GradientBasedUpdate}(q, \theta, \lambda; \eta)$ % \hspace{\fill} (Or other gradient based updates such as Adam)
+			\UNTIL{maximum iterations reached} % \hspace{\fill} (Stop if magnitude of all gradients are below $\epsilon$)
+			\STATE {\bfseries Output:} kernel parameters $\theta$, regularization parameter $\lambda$
 		\end{algorithmic}
@@
 
-	\subsection{Kernel Embedding Network}
-	\label{app:kernel_embedding_network}
+	\subsection{Conditional Embedding Network}
+	\label{app:conditional_embedding_network}
 
@@
 	Formally, let $\mathcal{F}_{0} := \mathcal{X}$ be the original input space.
-The $j^{\mathrm{th}}$ layer of the network $\varphi^{(j)}_{\theta_{j}} : \mathcal{F}_{j - 1} \to \mathcal{F}_{j}, j = 1, 2, \dots, L$ is to transform features from the previous layer to features in the current layer, where $L$ is the total number of such feature transformation layers, and $\theta_{j} \in \Theta_{j}$ parametrises each of those transformations.
+The $j^{\mathrm{th}}$ layer of the network $\varphi^{(j)}_{\theta_{j}} : \mathcal{F}_{j - 1} \to \mathcal{F}_{j}, j = 1, 2, \dots, L$ is to transform features from the previous layer to features in the current layer, where $L$ is the total number of such feature transformation layers, and $\theta_{j} \in \Theta_{j}$ parametrizes each of those transformations.
 
 	For example, in a typical multi-layer perceptron context, each layer can be written as $\varphi^{(j)}_{\theta_{j}}(x) = \sigma(W_{j} x + b_{j})$, where $W_{j}$ and $b_{j}$ are the weight and bias parameters of the layer, and $\sigma$ is an element-wise activation function, typically the rectified linear unit (ReLU) or the sigmoid.
-In this case, the layer is parametrised by $\theta_{j} = \{W_{j}, b_{j}\}$.
-
-		Let $\kappa_{\theta_{0}} : \mathcal{F}_{p} \times \mathcal{F}_{p} \to \mathbb{R}$ be parametrised by $\theta_{0} \in \Theta_{0}$. We will construct our kernel network $k$ by
+In this case, the layer is parametrized by $\theta_{j} = \{W_{j}, b_{j}\}$.
+
+	Let $\kappa_{\theta_{0}} : \mathcal{F}_{p} \times \mathcal{F}_{p} \to \mathbb{R}$ be parametrized by $\theta_{0} \in \Theta_{0}$. We will construct our kernel network $k$ by
 
@@
 	k_{\theta}(x, x') := \kappa_{\theta_{0}}\Bigg( \varphi^{(L)}_{\theta_{L}}\bigg(\varphi^{(L - 1)}_{\theta_{L - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x)\big)\Big)\bigg), \varphi^{(L)}_{\theta_{L}}\bigg(\varphi^{(L - 1)}_{\theta_{L - 1}}\Big(\dots\varphi^{(2)}_{\theta_{2}}\big(\varphi^{(1)}_{\theta_{1}}(x')\big)\Big)\bigg) \Bigg)
-		\label{eq:deep_kernel_embedding_network}
+	\label{eq:deep_conditional_embedding_network}
 	\end{equation}
@@
 	In order to train the multi-layered representations in an end-to-end fashion, we employ algorithm 1.
-With a deep architecture, the feature representations the kernel embedding network can learn are very flexible, and can work very well for structured data by employing suitable network architectures.
+With a deep architecture, the feature representations the \gls{CEN} can learn are very flexible, and can work very well for structured data by employing suitable network architectures.
 
@@
 
-	\subsection{Explicit Kernel Embedding Network}
-	\label{app:explicit_kernel_embedding_network}
-
-		The explicit kernel embedding network is simply a special case at the intersection of the explicit kernel embedding classifier and the kernel embedding network.
-From the explicit KEC perspective, we simply choose $\varphi_{\theta}(x) = \varphi^{(L)}_{\theta_{L}}\big(\varphi^{(L - 1)}_{\theta_{L - 1}}(\dots\varphi^{(2)}_{\theta_{2}}(\varphi^{(1)}_{\theta_{1}}(x)))\big)$.
-From the KEN perspective, we simply choose $\kappa(z, z') = z^{T} z'$ to be a linear kernel.
-
-		This model architecture is a very practical and powerful form of the kernel embedding classifier.
+	\subsection{Explicit Conditional Embedding Network}
+	\label{app:explicit_conditional_embedding_network}
+
+	The explicit \gls{CEN} is simply a special case at the intersection of the explicit \gls{MCE} and the \gls{CEN}.
+From the explicit \gls{MCE} perspective, we simply choose $\varphi_{\theta}(x) = \varphi^{(L)}_{\theta_{L}}\big(\varphi^{(L - 1)}_{\theta_{L - 1}}(\dots\varphi^{(2)}_{\theta_{2}}(\varphi^{(1)}_{\theta_{1}}(x)))\big)$.
+From the \gls{CEN} perspective, we simply choose $\kappa(z, z') = z^{T} z'$ to be a linear kernel.
+
+	This model architecture is a very practical and powerful form of the \gls{MCE}.
 By having a deep architecture, the classifier is still capable of learning flexible representations on structured data, while being able to scale to larger datasets due to the linear kernel at the output layer, provided that the dimensionality of the last layer is relatively small compared to the size of the dataset.
 
-		As a subclass of explicit KEC, we can employ \cref{alg:explicit_kernel_embedding_classifier_training} to learn the multi-layered features effectively.
+	As a subclass of explicit \gls{MCE}, we can employ \cref{alg:explicit_multiclass_conditional_embedding_training} to learn the multi-layered features effectively.
 In fact, by not mapping the multi-layered features into a nonlinear kernel, the gradients for each network weight and bias are usually more pronounced, and learning is usually faster in comparison.
@@
 
-\newpage
 	\bibliographystyle{apalike}

### 2018-04-02 ECML2018/paper/mce_ecml2018.tex
Convert paper and appendix to ECML format

--- 2018-03-29 AISTATS2018/cake_aistats2018.tex
@@
-\documentclass[twoside]{article}
-\usepackage{aistats2018}
-% If your paper is accepted, change the options for the package
-% aistats2018 as follows:
+% This is LLNCS.DEM the demonstration file of
+% the LaTeX macro package from Springer-Verlag
+% for Lecture Notes in Computer Science,
+% version 2.4 for LaTeX2e as of 16. April 2010
 %
-%\usepackage[accepted]{aistats2018}
+\documentclass{llncs}
 %
-% This option will print headings for the title of your paper and
-% headings for the authors names, plus a copyright note at the end of
-% the first column of the first page.
+\usepackage{makeidx}  % allows for indexgeneration
 
@@
 
+% Default packages
 \usepackage{glossaries}
-\usepackage{acronym}
 \usepackage[utf8]{inputenc} % allow utf-8 input
@@
 % My Packages
+\usepackage{acronym}
 \usepackage{amsmath}
 \usepackage{amssymb}
-\usepackage{amsthm}
+%\usepackage{amsthm}
 \usepackage{mathbbol}
@@
 
+%
+\title{Hyperparameter Learning \\ for Conditional Mean Embeddings \\ with Rademacher Complexity Bounds}
+
+\titlerunning{Hyperparameter Learning for Conditional Mean Embeddings}
+% abbreviated title (for running head), also used for the TOC unless \toctitle is used
+
+\author{Kelvin Hsu \inst{1, 2} \and
+		Richard Nock \inst{1, 2, 3} \and
+		Fabio Ramos \inst{1, 2}}
+%
+\authorrunning{Hsu et. al.} % abbreviated author list (for running head)
+%
+%%%% list of authors for the TOC (use if author list has to be modified)
+\tocauthor{Kelvin Hsu, Richard Nock, Fabio Ramos}
+%
+\institute{	University of Sydney, Sydney, Australia, \\ \and
+			Data61, CSIRO, Sydney, Australia \\ \and
+			Australian National University, Canberra, Australia}
+
 \begin{document}
-
-	\twocolumn[
-
-	\aistatstitle{Hyperparameter Learning for Conditional Mean Embeddings \\ with Rademacher Complexity Bounds}
-
-	\aistatsauthor{ Anonymous Author 1 \And Anonymous Author 2 \And Anonymous Author 3 }
-
-	\aistatsaddress{ Unknown Institution 1 \And Unknown Institution 2 \And Unknown Institution 3 } ]
+	%
+	\frontmatter          % for the preliminaries
+	\maketitle            % typeset the title of the contribution
+	%
 
@@
 For conditional mean embeddings with categorical targets and arbitrary inputs, we propose a hyperparameter learning framework based on Rademacher complexity bounds to prevent overfitting by balancing data fit against model complexity.
-The approach only requires batch updates, allowing scalable kernel learning without kernel approximations.
+The approach only requires batch updates, allowing scalable kernel hyperparameter tuning without kernel approximations.
 Experiments demonstrate that our framework outperforms competing methods, and can be further extended to incorporate and learn neural network weights improving generalization.
 
+		\keywords{Conditional Mean Embeddings, Kernel Mean Embeddings, Kernel Methods, Mean Embeddings, Hilbert Space Embeddings, Hyperparameter Learning, Rademacher Complexity}
 		% % % Original:
@@
 	\Glspl{CME} are attractive because they encode conditional expectations in a \gls{RKHS}, bypassing the need for a parametrized distribution \citep{song2013kernel}.
-They are part of a broader class of models known as kernel embeddings, where nonparametric probabilistic inference can be carried out entirely within the \gls{RKHS} because difficult marginalization integrals become simple linear algebra \citep{muandet2016kernel}.
+They are part of a broader class of techniques known as kernel mean embeddings, where nonparametric probabilistic inference can be carried out entirely within the \gls{RKHS} because difficult marginalization integrals become simple linear algebra \citep{muandet2016kernel}.
 This very general framework is core to modern kernel probabilistic methods, including kernel two-sample testing \citep{gretton2007kernel}, kernel Bayesian inference  \citep{fukumizu2013kernel}, density estimation \citep{song2008tailoring, kanagawa2014recovering}, component analysis \citep{muandet2013domain}, dimensionality reduction \citep{fukumizu2004dimensionality}, feature discovery \citep{jitkrittum2016interpretable}, and state space filtering \citep{kanagawa2016filtering}.
@@
 	Nevertheless, like most kernel based models, their performance is highly dependent on the hyperparameters chosen.
-For these models, the model selection process usually begins by selecting a kernel, whose parameters become part of the model hyperparameters, which may further include noise or regularization parameters.
+For these models, the model selection process usually begins by selecting a kernel, whose parameters become part of the model \textit{hyperparameters}, which may further include noise or regularization parameters.
 Given a set of hyperparameters, training is performed by solving either a convex optimization problem, such as for \glspl{SVM} \citep{scholkopf2002learning}, or a set of linear equations, such as for \gls{GPs} \citep{rasmussen2006gaussian}, \glspl{RLSC} \citep{rifkin2003regularized}, and \glspl{CME}.
 Unfortunately, hyperparameter tuning is not straight forward, and often cross validation \citep{song2013kernel} or median length heuristics \citep{muandet2016kernel} remain as the primary approaches for this task.
+The former can be expensive and sensitive to the selection and number of validation sets, while the latter heuristic only applies to hyperparameters with a length scale interpretation and makes no reference to the conditional inference problem involved.
 
@@
 
-		One notable success story in this domain are \gls{GPs}, which utilizes the marginal likelihood for hyperparameter learning.
+	One notable success story in this domain are \gls{GPs}, which utilizes the marginal likelihood objective for hyperparameter learning.
 The marginal likelihood arises from its Bayesian formulation, and exhibits certain desirable properties -- in particular, the ability to automatically balance between data fit and model complexity.
@@
 For \glspl{CME} with categorical targets and arbitrary input, we present such a learning objective as our main contribution.
-In particular, we: (1) derive a measure $r(\theta, \lambda)$ to measure the model complexity of a \gls{CME} based on the Rademacher complexity of a relevant class of \glspl{CME}, (2) propose a novel learning objective based on this complexity measure to control generalization risk by balancing data fit against model complexity, and (3) propose a scalable hyperparameter learning algorithm under this objective using batch updates.
+In particular, we: (1) derive a measure $r(\theta, \lambda)$ to measure the model complexity of a particular \gls{CME} based on the Rademacher complexity of a class of \glspl{CME} determined by that particular \gls{CME}, (2) propose a novel learning objective based on this complexity measure to control generalization risk by balancing data fit against model complexity, and (3) propose a scalable hyperparameter learning algorithm under this objective using batch updates.
 We show that this learning objective produces \glspl{CME} that generalize better than that learned from cross validation, \gls{ERM}, or median length heuristics on standard benchmarks, and apply such an algorithm to incorporate and learn neural network weights improving generalization accuracy.
@@
 This could also be repeated over multiple folds for cross validation.
-\cite{song2013kernel} also uses this cross validation approach, but adds a regularization $\lambda \| \mathcal{U} \|^{2}_{HS}$ to the validation objective.
-This approach improves generalization of \glspl{CME} to unseen examples.
-However, they require the selection for the split and number of folds.
-Moreover, they are not optimized for any particular prediction task.
+\cite[p.
+15]{song2013kernel} also uses this cross validation approach, but adds a regularization $\lambda \| \mathcal{U} \|^{2}_{HS}$ to the validation objective.
+Validation sets are necessary for improving generalization to unseen examples as the \gls{CME} is already the solution that minimizes the objective from \cite{lever2012conditional} over the operator space, so further optimization over the hyperparmeters using the same training set would lead to overfitting.
+Moreoever, they require the selection for the split and number of folds, and are not optimized for any particular inference task.
 By fitting a separate model for each fold during learning, they also incur a large computational cost of $O(J n^{3})$ for $J$ folds, and becomes prohibitive with large datasets.
+This spells a need for an alternative hyperparameter learning framework using a different objective.
 
@@
 	\end{equation}
-		Since $\mathcal{U} = \hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the solution to a regularized least squares problem in the RKHS from $k(x, \cdot) \in \mathcal{H}_{k}$ to $l(y, \cdot) \in \mathcal{H}_{l}$ \citep{lever2012conditional}, \glspl{CME} can be seen as \glspl{KRR} in the \gls{RKHS}.
+	Since $\mathcal{U} = \hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the solution to a regularized least squares problem in the RKHS from $k(x, \cdot) \in \mathcal{H}_{k}$ to $l(y, \cdot) \in \mathcal{H}_{l}$ \citep{lever2012conditional}, \glspl{CME} are essentially \glspl{KRR} in the \gls{RKHS}.
 In this case, because $\mathcal{Y} = \mathbb{N}_{m}$ is discrete, $\mathcal{H}_{\delta}$ can be identified with $\mathbb{R}^{m}$.
 As a result, for discrete $\mathcal{Y} = \mathbb{N}_{m}$ the rows of the \gls{MCE} can also be seen as $m$ \glspl{KRR} \citep{friedman2001elements} on binary $\{0, 1\}$-targets, where they all share the same input kernel.
-We now verify that the empirical decision probabilities \eqref{eq:empirical_decision_probability} do converge to the population decision probability.
+Because they all share the same kernel to form the \gls{MCE}, we can leverage this fact and show that the empirical decision probabilities \eqref{eq:empirical_decision_probability} do converge to the population decision probability.
 
@@
 	In particular, the assumption $k(x, \cdot) \in \mathrm{image}(C_{XX})$ is on the input kernel $k$, not the output kernel $l$, which is a Kronecker delta $l = \delta$ for \glspl{MCE}.
-In practice, this assumption can be relaxed through introducing the regularization parameter $\lambda$ as in \eqref{eq:empirical_conditional_embedding} \citep{song2009hilbert}.
+It is worthwhile to note that this assumption is common for \glspl{CME}, and is not as restrictive as it may first appear, as it can be relaxed through introducing the regularization parameter $\lambda$ \eqref{eq:empirical_conditional_embedding} in practice \citep[p.74-75, Sec.
+3 and 3.1 \textit{resp.}]{song2009hilbert, song2013kernel, muandet2016kernel}.
 
@@
 	to express risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$ where usually $\epsilon << 1$.
+It is worthwhile to point out that this choice only makes sense due to \cref{thm:probability_convergence_copy}, as it allows us to interpret the outputs of the \gls{CME} as asymptotic probability estimates.
 Note that we employ the loss on the original probability estimates \eqref{eq:empirical_decision_probability_vector}, not the clip-normalized version \eqref{eq:empirical_decision_probability_clip_normalized}.
@@
 		\begin{aligned}
-				&\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))]  \\
-				&\leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 e \; \alpha \rho + \sqrt{\frac{8}{n} \log{\frac{2}{\beta}}}.
+		\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 e \; \alpha \rho + \sqrt{\frac{8}{n} \log{\frac{2}{\beta}}}.
 		\end{aligned}
@@
 		\begin{aligned}
-			&\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \\
-			&\leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e \; r(\theta, \lambda) + \sqrt{\frac{8}{n} \log{\frac{2}{\beta}}},
+		\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e \; r(\theta, \lambda) + \sqrt{\frac{8}{n} \log{\frac{2}{\beta}}},
 		\label{eq:expected_risk_bound_hyperparameter_learning_copy}
@@
 
-	\newpage
+%	\begin{thebibliography}{}
+	\small{
 	\bibliography{kernel_embedding}
 	\bibliographystyle{apalike}
+	}
+%	\end{thebibliography}
 

### 2018-04-02 ECML2018/paper/mce_appendix_ecml2018.tex
Link external document properly in appendix

@@
 	With \cref{thm:pointwise_uniform_convergence}, we can now show the convergence of various estimators based on the conditional embedding, as long as we can show that their estimator error is upper bounded by a multiple of the conditional embedding error in the \gls{RKHS} norm.
-As such, we turn to the convergence of the empirical decision probability function \eqref[name= , xr=cake]{eq:empirical_decision_probability} below.
+As such, we turn to the convergence of the empirical decision probability function \eqref[name= , xr=mce_ecml2018]{eq:empirical_decision_probability} below.
 
@@
 		\label{thm:probability_convergence}
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref[name= , xr=cake]{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref[name= , xr=cake]{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref[name= , xr=mce_ecml2018]{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref[name= , xr=mce_ecml2018]{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
 
@@
 
-		The empirical decision probability \eqref[name = , xr=cake]{eq:empirical_decision_probability} for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the empirical conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,
+		The empirical decision probability \eqref[name = , xr=mce_ecml2018]{eq:empirical_decision_probability} for class $c \in \mathbb{N}_{m}$ given an example $x \in \mathcal{X}$ is the empirical conditional embedding with $l = \delta$ conditioned at example $x$ evaluated at label $c$,
 
@@
 
-	\Cref{thm:empirical_probability_is_embedding} shows that the decision function $\bvec{f}(x)$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} of a \gls{MCE} is no more than the empirical conditional embedding estimated from the data.
+	\Cref{thm:empirical_probability_is_embedding} shows that the decision function $\bvec{f}(x)$ \eqref[name = , xr=mce_ecml2018]{eq:empirical_decision_probability_vector} of a \gls{MCE} is no more than the empirical conditional embedding estimated from the data.
 
@@
 
-		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability vector function $\hat{\bvec{p}} : \mathcal{X} \to \mathbb{R}^{m}$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} converges uniformly to the true decision probability vector function $\bvec{p} : \mathcal{X} \to [0, 1]^{m}$ in the $\ell_{1}$-norm and $\ell_{2}$-norm, where $\bvec{p}(x) := \{p_{c}(x)\}_{c = 1}^{m}$, at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
+		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability vector function $\hat{\bvec{p}} : \mathcal{X} \to \mathbb{R}^{m}$ \eqref[name = , xr=mce_ecml2018]{eq:empirical_decision_probability_vector} converges uniformly to the true decision probability vector function $\bvec{p} : \mathcal{X} \to [0, 1]^{m}$ in the $\ell_{1}$-norm and $\ell_{2}$-norm, where $\bvec{p}(x) := \{p_{c}(x)\}_{c = 1}^{m}$, at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
 
@@
 
-	The first approach is straight forward, which involves simply computing the information entropy with the clip normalized probabilities \eqref[name = , xr=cake]{eq:empirical_decision_probability_clip_normalized}, at the query point $x \in \mathcal{X}$,
+	The first approach is straight forward, which involves simply computing the information entropy with the clip normalized probabilities \eqref[name = , xr=mce_ecml2018]{eq:empirical_decision_probability_clip_normalized}, at the query point $x \in \mathcal{X}$,
 
@@
 We can thus write $u_{x} = \sum_{c = 1}^{m} - \log{\mathbb{P}[Y = c | X = x]} \delta(c, \cdot)$ which shows that $u_{x}$ is in the span of the canonical kernel features and is thus in the \gls{RKHS}.
-Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref[name = , xr=cake]{eq:empirical_conditional_expectation} and estimate $h(x)$ by
+Hence, similar to the case with decision probabilities, with $u_{x} \in \mathcal{H}_{\delta}$ and $\bvec{u}_{x} := \{u_{x}(y_{i})\}_{i = 1}^{n}$ we let $g = u_{x}$ in \eqref[name = , xr=mce_ecml2018]{eq:empirical_conditional_expectation} and estimate $h(x)$ by
 
@@
 	where $\hat{\bvec{u}}_{x} := \{\hat{u}_{x}(y_{i})\}_{i = 1}^{n}$.
-Similar to the case with decision probabilities \eqref[name = , xr=cake]{eq:decision_probability}, the information entropy estimate \eqref[name = ]{eq:empirical_information_entropy} is not guaranteed to be non-negative.
+Similar to the case with decision probabilities \eqref[name = , xr=mce_ecml2018]{eq:decision_probability}, the information entropy estimate \eqref[name = ]{eq:empirical_information_entropy} is not guaranteed to be non-negative.
 However, in practice these negative values are close to zero.
@@
 Let $k_{\theta} : \mathcal{X} \times \mathcal{X} \to [0, \infty)$ be a family of positive definite kernels indexed by $\theta \in \Theta$.
-As before, we define the shorthand notation for the gram matrices $K_{\theta} := \{k_{\theta}(x_{i}, x_{j}) : i \in \mathbb{N}_{n}, j \in \mathbb{N}_{n}\}$ and $\bvec{k}_{\theta}(x) := \{k_{\theta}(x_{i}, x) : i \in \mathbb{N}_{n}\}$, and $\lambda$ denotes the regularization parameter of the conditional embedding \eqref[name = , xr=cake]{eq:empirical_conditional_embedding}.
-The \gls{MCE} has a predictor form $\hat{\bvec{p}}(x) = \bvec{f}_{\theta, \lambda}(x)$ \eqref[name = , xr=cake]{eq:empirical_decision_probability_vector} defined by
+As before, we define the shorthand notation for the gram matrices $K_{\theta} := \{k_{\theta}(x_{i}, x_{j}) : i \in \mathbb{N}_{n}, j \in \mathbb{N}_{n}\}$ and $\bvec{k}_{\theta}(x) := \{k_{\theta}(x_{i}, x) : i \in \mathbb{N}_{n}\}$, and $\lambda$ denotes the regularization parameter of the conditional embedding \eqref[name = , xr=mce_ecml2018]{eq:empirical_conditional_embedding}.
+The \gls{MCE} has a predictor form $\hat{\bvec{p}}(x) = \bvec{f}_{\theta, \lambda}(x)$ \eqref[name = , xr=mce_ecml2018]{eq:empirical_decision_probability_vector} defined by
 

### 2018-05-02 ECML2018/paper/mce_ecml2018.tex
Make references not start on a new page
Test commit for ECML final

@@
 \usepackage[square, authoryear, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
+\renewcommand\bibname{References}
+\usepackage{etoolbox}
+\patchcmd{\bibliography}{\chapter*}{\section*}{}{}
+\renewcommand\bibsection{\section*{\refname}}
 
@@
 The approach only requires batch updates, allowing scalable kernel hyperparameter tuning without kernel approximations.
-Experiments demonstrate that our framework outperforms competing methods, and can be further extended to incorporate and learn neural network weights improving generalization.
+Experiments demonstrate that our framework outperforms competing methods, and can be further extended to incorporate and learn deep neural network weights to improve generalization.
 
-		\keywords{Conditional Mean Embeddings, Kernel Mean Embeddings, Kernel Methods, Mean Embeddings, Hilbert Space Embeddings, Hyperparameter Learning, Rademacher Complexity}
+		\keywords{Hyperparameter Learning, Kernel Hyperparameters, Conditional Mean Embeddings, Kernel Mean Embeddings, Kernel Methods, Mean Embeddings, Hilbert Space Embeddings, Reproducing Kernel Hilbert Space, Nonparametric Inference, Rademacher Complexity}
 		% % % Original:
@@
 
-	\begin{figure*}[t]
-		\centering
-		\includegraphics[width=0.32\linewidth]{figures/iris_overfitted_model.eps}
-		\includegraphics[width=0.32\linewidth]{figures/iris_balanced_model.eps}
-		\includegraphics[width=0.32\linewidth]{figures/iris_underfitted_model.eps}
-		\includegraphics[width=0.48\linewidth]{figures/iris_rademacher_complexity_bound_lower_legend.eps}
-		%		\includegraphics[width=0.48\linewidth]{figures/iris_cross_entropy_loss.eps}
-		\includegraphics[width=0.48\linewidth]{figures/iris_accuracy.eps}
-		\caption{Rademacher complexity balanced learning of hyperparameters for an isotropic Gaussian \gls{MCE}, using the first two attributes of the iris dataset.}
-		\label{fig:iris}
-	\end{figure*}
-
 	\paragraph{Batch Stochastic Gradient Update} Since \cref{thm:expected_risk_bound_hyperparameter_learning_copy} holds for any $n \in \mathbb{N}_{+}$ and any set of data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ from $\mathbb{P}_{X Y}$, the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} also holds with high probability for a batch subset of the training data.
@@
 
-	\begin{table*}[t]
-		\caption{Test accuracy (\%) on UCI datasets}
-		\label{tab:uci_experiments}
+		\begin{figure*}[t]
 			\centering
-		\begin{tabular}{lcccccccc}
-			Dataset & G\gls{MCE} & G\gls{MCE}-SGD & \gls{CEN}-1 & \gls{CEN}-2 & ERM & CV & MED & Others \\
-			\midrule
-			\texttt{banknote} & $\mathbf{99.9 \pm 0.2}$ & $98.8 \pm 0.9$ & $99.5 \pm 1.0$ & $99.4 \pm 0.9$ & $\mathbf{99.9 \pm 0.2}$ & $\mathbf{99.9 \pm 0.2}$ & $92.0 \pm 4.3$ & 99.78\textsuperscript{a} \\
-			\texttt{ecoli} & $\mathbf{87.5 \pm 4.4}$ & $84.5 \pm 5.0$ & $\mathbf{87.5 \pm 3.2}$ & $86.3 \pm 6.0$ & $72.1 \pm 20.5$ & $73.8 \pm 23.8$ & $42.1 \pm 47.7$ & 81.1\textsuperscript{b} \\
-			\texttt{robot} & $\mathbf{96.7 \pm 0.9}$ & $95.5 \pm 0.9$ & $82.3 \pm 7.1$ & $94.5 \pm 0.8$ & $91.0 \pm 3.7$ & $90.9 \pm 3.4$ & $81.1 \pm 6.2$ & 97.59\textsuperscript{c} \\
-			\texttt{segment} & $\mathbf{98.4 \pm 0.8}$ & $96.1 \pm 1.5$ & $94.6 \pm 1.6$ & $96.7 \pm 1.1$ & $98.1 \pm 1.1$ & $98.3 \pm 1.3$ & $27.3 \pm 26.4$ & 96.83\textsuperscript{d} \\
-			\texttt{wine} & $\mathbf{97.2 \pm 3.7}$ & $93.3 \pm 6.0$ & $96.1 \pm 5.0$ & $97.2 \pm 5.1$ & $93.9 \pm 5.2$ & $93.3 \pm 7.4$ & $93.3 \pm 7.8$ & 100\textsuperscript{e} \\
-			\texttt{yeast} & $52.5 \pm 2.1$ & $\mathbf{60.3 \pm 4.4}$ & $55.8 \pm 5.0$ & $59.6 \pm 4.0$ & $45.9 \pm 6.4$ & $58.0 \pm 5.8$ & $31.2 \pm 14.1$ & 55.0\textsuperscript{b} \\
-		\end{tabular}
-	\end{table*}
+			\includegraphics[width=0.32\linewidth]{figures/iris_overfitted_model.eps}
+			\includegraphics[width=0.32\linewidth]{figures/iris_balanced_model.eps}
+			\includegraphics[width=0.32\linewidth]{figures/iris_underfitted_model.eps}
+			\includegraphics[width=0.48\linewidth]{figures/iris_rademacher_complexity_bound_lower_legend.eps}
+			%		\includegraphics[width=0.48\linewidth]{figures/iris_cross_entropy_loss.eps}
+			\includegraphics[width=0.48\linewidth]{figures/iris_accuracy.eps}
+			\caption{Rademacher complexity balanced learning of hyperparameters for an isotropic Gaussian \gls{MCE}, using the first two attributes of the iris dataset.}
+			\label{fig:iris}
+		\end{figure*}
 
@@
 
-	\begin{figure*}[t]
+%		\begin{table*}[t]
+%			\caption{Test accuracy (\%) on UCI datasets}
+%			\label{tab:uci_experiments}
+%			\centering
+%			\begin{tabular}{lcccccccc}	
+%				Dataset & G\gls{MCE} & G\gls{MCE}-SGD & \gls{CEN}-1 & \gls{CEN}-2 & ERM & CV & MED & Others \\
+%				\midrule
+%				\texttt{banknote} & $\mathbf{99.9 \pm 0.2}$ & $98.8 \pm 0.9$ & $99.5 \pm 1.0$ & $99.4 \pm 0.9$ & $\mathbf{99.9 \pm 0.2}$ & $\mathbf{99.9 \pm 0.2}$ & $92.0 \pm 4.3$ & 99.78\textsuperscript{a} \\
+%				\texttt{ecoli} & $\mathbf{87.5 \pm 4.4}$ & $84.5 \pm 5.0$ & $\mathbf{87.5 \pm 3.2}$ & $86.3 \pm 6.0$ & $72.1 \pm 20.5$ & $73.8 \pm 23.8$ & $42.1 \pm 47.7$ & 81.1\textsuperscript{b} \\
+%				\texttt{robot} & $\mathbf{96.7 \pm 0.9}$ & $95.5 \pm 0.9$ & $82.3 \pm 7.1$ & $94.5 \pm 0.8$ & $91.0 \pm 3.7$ & $90.9 \pm 3.4$ & $81.1 \pm 6.2$ & 97.59\textsuperscript{c} \\
+%				\texttt{segment} & $\mathbf{98.4 \pm 0.8}$ & $96.1 \pm 1.5$ & $94.6 \pm 1.6$ & $96.7 \pm 1.1$ & $98.1 \pm 1.1$ & $98.3 \pm 1.3$ & $27.3 \pm 26.4$ & 96.83\textsuperscript{d} \\
+%				\texttt{wine} & $\mathbf{97.2 \pm 3.7}$ & $93.3 \pm 6.0$ & $96.1 \pm 5.0$ & $97.2 \pm 5.1$ & $93.9 \pm 5.2$ & $93.3 \pm 7.4$ & $93.3 \pm 7.8$ & 100\textsuperscript{e} \\
+%				\texttt{yeast} & $52.5 \pm 2.1$ & $\mathbf{60.3 \pm 4.4}$ & $55.8 \pm 5.0$ & $59.6 \pm 4.0$ & $45.9 \pm 6.4$ & $58.0 \pm 5.8$ & $31.2 \pm 14.1$ & 55.0\textsuperscript{b} \\
+%			\end{tabular}
+%		\end{table*}
+
+		\begin{table*}[t]
+			\caption{Test accuracy (\%) on UCI datasets}
+			\label{tab:uci_experiments}
 			\centering
-		\includegraphics[width=0.49\linewidth]{figures/gaussian_mnist_test_performance_short.eps}
-		\includegraphics[width=0.49\linewidth]{figures/deep_mnist_test_performance_short.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_01_batch_1200.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_068_batch_1200.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_12_batch_1200.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_14_batch_1200.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_23_batch_1200.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_38_batch_1200.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_479_batch_1200.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_56_batch_1200.eps}
-		\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_0123456789_batch_1200.eps}
-		\caption{Top: Test accuracy by learning Gaussian kernels (left) and deep convolutional features (right). Bottom: Learned pixel length scales under anistropic Gaussian, or \gls{ARD}, kernels.}
-		\label{fig:mnist_experiments}
-	\end{figure*}
+			\begin{tabular}{lcccccc}	
+				Method         & \texttt{banknote}       & \texttt{ecoli}          & \texttt{robot}          & \texttt{segment}        & \texttt{wine}           & \texttt{yeast}          \\
+				\midrule
+				G\gls{MCE}     & $\mathbf{99.9 \pm 0.2}$ & $\mathbf{87.5 \pm 4.4}$ & $\mathbf{96.7 \pm 0.9}$ & $\mathbf{98.4 \pm 0.8}$ & $\mathbf{97.2 \pm 3.7}$ & $52.5 \pm 2.1$          \\
+				G\gls{MCE}-SGD & $98.8 \pm 0.9$          & $84.5 \pm 5.0$          & $95.5 \pm 0.9$          & $96.1 \pm 1.5$          & $93.3 \pm 6.0$          & $\mathbf{60.3 \pm 4.4}$ \\
+				\gls{CEN}-1    & $99.5 \pm 1.0$          & $\mathbf{87.5 \pm 3.2}$ & $82.3 \pm 7.1$          & $94.6 \pm 1.6$          & $96.1 \pm 5.0$          & $55.8 \pm 5.0$          \\
+				\gls{CEN}-2    & $99.4 \pm 0.9$          & $86.3 \pm 6.0$          & $94.5 \pm 0.8$          & $96.7 \pm 1.1$          & $97.2 \pm 5.1$          & $59.6 \pm 4.0$          \\
+				ERM            & $\mathbf{99.9 \pm 0.2}$ & $72.1 \pm 20.5$         & $91.0 \pm 3.7$          & $98.1 \pm 1.1$          & $93.9 \pm 5.2$          & $45.9 \pm 6.4$          \\
+				CV             & $\mathbf{99.9 \pm 0.2}$ & $73.8 \pm 23.8$         & $90.9 \pm 3.4$          & $98.3 \pm 1.3$          & $93.3 \pm 7.4$          & $58.0 \pm 5.8$          \\
+				MED            & $92.0 \pm 4.3$          & $42.1 \pm 47.7$         & $81.1 \pm 6.2$          & $27.3 \pm 26.4$         & $93.3 \pm 7.8$          & $31.2 \pm 14.1$         \\
+				Others         & 99.78\textsuperscript{a}& 81.1\textsuperscript{b} & 97.59\textsuperscript{c}& 96.83\textsuperscript{d}& 100\textsuperscript{e}  & 55.0\textsuperscript{b}
+
+				%				Dataset           & G\gls{MCE}              & G\gls{MCE}-SGD          & \gls{CEN}-1             & \gls{CEN}-2    & ERM                     & CV                      & MED             & Others \\
+				%				\midrule
+				%				\texttt{banknote} & $\mathbf{99.9 \pm 0.2}$ & $98.8 \pm 0.9$          & $99.5 \pm 1.0$          & $99.4 \pm 0.9$ & $\mathbf{99.9 \pm 0.2}$ & $\mathbf{99.9 \pm 0.2}$ & $92.0 \pm 4.3$  & 99.78\textsuperscript{a} \\
+				%				\texttt{ecoli}    & $\mathbf{87.5 \pm 4.4}$ & $84.5 \pm 5.0$          & $\mathbf{87.5 \pm 3.2}$ & $86.3 \pm 6.0$ & $72.1 \pm 20.5$         & $73.8 \pm 23.8$         & $42.1 \pm 47.7$ & 81.1\textsuperscript{b} \\
+				%				\texttt{robot}    & $\mathbf{96.7 \pm 0.9}$ & $95.5 \pm 0.9$          & $82.3 \pm 7.1$          & $94.5 \pm 0.8$ & $91.0 \pm 3.7$          & $90.9 \pm 3.4$          & $81.1 \pm 6.2$  & 97.59\textsuperscript{c} \\
+				%				\texttt{segment}  & $\mathbf{98.4 \pm 0.8}$ & $96.1 \pm 1.5$          & $94.6 \pm 1.6$          & $96.7 \pm 1.1$ & $98.1 \pm 1.1$          & $98.3 \pm 1.3$          & $27.3 \pm 26.4$ & 96.83\textsuperscript{d} \\
+				%				\texttt{wine}     & $\mathbf{97.2 \pm 3.7}$ & $93.3 \pm 6.0$          & $96.1 \pm 5.0$          & $97.2 \pm 5.1$ & $93.9 \pm 5.2$          & $93.3 \pm 7.4$          & $93.3 \pm 7.8$  & 100\textsuperscript{e} \\
+				%				\texttt{yeast}    & $52.5 \pm 2.1$          & $\mathbf{60.3 \pm 4.4}$ & $55.8 \pm 5.0$          & $59.6 \pm 4.0$ & $45.9 \pm 6.4$          & $58.0 \pm 5.8$          & $31.2 \pm 14.1$ & 55.0\textsuperscript{b} \\
+			\end{tabular}
+		\end{table*}
 
@@
 	\paragraph{Learning convolutional layers}
+
+		\begin{figure*}[t]
+			\centering 
+			\includegraphics[width=0.49\linewidth]{figures/gaussian_mnist_test_performance_short.eps}
+			\includegraphics[width=0.49\linewidth]{figures/deep_mnist_test_performance_short.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_01_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_068_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_12_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_14_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_23_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_38_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_479_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_56_batch_1200.eps}
+			\includegraphics[width=0.1\linewidth]{figures/pixel_relevance_0123456789_batch_1200.eps}
+			\caption{Top: Test accuracy by learning Gaussian kernels (left) and deep convolutional features (right). Bottom: Learned pixel length scales under anistropic Gaussian, or \gls{ARD}, kernels.}
+			\label{fig:mnist_experiments}
+		\end{figure*}
 
@@
 
-%	\begin{thebibliography}{}
+	\bibliographystyle{apalike}
 	\small{
 	\bibliography{kernel_embedding}
-	\bibliographystyle{apalike}
 	}
-%	\end{thebibliography}
 
